### 2022-11-20 data_analysis.Rmd
Started data analysis by wrangling the data, transforming the predictors, removing highly correlated variables, and figuring out how to properly represent model predictions in the graphs.

---
title: "Data Wrangling and Statistical Analysis of Assessment of Abundance, Aggregation, and Web Placement of *Agelenopsis pennsylvanica*"
author: "Brandi Pessman"
date: "`r Sys.Date()`"
output: html_document
---

## Setting the Working Directory and Global Code Chunk Options

```{r setup, include = FALSE}
knitr::opts_chunk$set(message = FALSE, warning = FALSE)
require("knitr")
opts_knit$set(root.dir = "/Users/bjpessman/Documents/phd_research_code/Agelenopsis_aggregation")
```

## Packages to Load

```{r packages, echo = FALSE}
library(tidyverse) # to use pipelines in data wrangling
library(ggpubr) # using ggarrange to make multi-panel figures
library(caret) # used to find correlations between predictor variables
library(PerformanceAnalytics) # used to make correlation plots
library(broom) # allows us to use augment when getting predicted values from the model
library(emmeans) # for calculating predictions for graphing
```

## Import Data

```{r import}
webs <- read.table(file = "data/webs.txt", header = TRUE) 
# includes data for every measured web (multiple per site)
```

## Data Wrangling

```{r webs_wrangling}
# Here, we rename some levels of factors Location and Land and put them in the order we want the categories to appear in a graph

webs <- webs %>% 
  mutate(ID = factor(ID),
         Location = factor(Location),
         Location = fct_recode(Location, 
                               "Urban Forest" = "Forest",
                               "Urban Center" = "Campus"),
         Location = fct_relevel(Location, 
                                "Urban Forest", "Urban Center"),
         Land = fct_recode(Land, 
                           "Urban, High" = "UrbanizedHighIntensity",
                           "Urban, Medium" = "UrbanizedMediumIntensity",
                           "Urban, Low" = "UrbanizedLowIntensity",
                           "Deciduous Forest" = "DeciduousForest",
                           "Woody Wetlands" = "WoodyWetlands"),
         Land = fct_relevel(Land, 
                            "Urban, High", 
                            "Urban, Medium", 
                            "Urban, Low", 
                            "Deciduous Forest", 
                            "Woody Wetlands"),
         patch_area_km = patch_area_mm * 1e-6) %>% 
  dplyr::rename("Impervious" = "Imperv", 
                "Dist_to_Road" = "road_dist_data", 
                "Traffic_Dist_Road" = "dist_traffic_road", 
                "Dist_to_Highway" = "highway_dist_m", 
                "Traffic_Dist_Highway" = "dist_traffic_highway")

sites <- webs %>% 
  filter(Web == "W001") 
# Restricted to site data only (only one data point per site)
```

```{r sites_wrangling}
# At one time, we tried scaling and centering the data in difference ways. I want to make mention of it here because it might be useful information for me to look back on in the future. Scaling is dividing each datum by the standard deviation of the data and centering is subtracting the mean of the data from each datum to try to normalize the data; a second type of centering and scaling involves subtracting the median and dividing by the interquartile range; need to remember to back transform when making figures; we didn't scale and center because log-transformations on zero-inflated variables were enough to remove convergence errors

sites <- sites %>% 
  mutate(patch_area_km = patch_area_mm * 1e-6)
```

```{r location_subsets}
webs_center <- webs %>% 
  filter(Location == "Urban Center")

webs_forest <- webs %>% 
  filter(Location == "Urban Forest")

sites_center <- sites %>% 
  filter(Location == "Urban Center")

sites_forest <- sites %>% 
  filter(Location == "Urban Forest")
```

## Transformation of Variables

Many data are zero-inflated or right skewed. We check the distribution of the data and check distributions after log-transformation for right-skewed data not containing zeros.

```{r graphing_predictor_distributions, echo = FALSE}
# Here, we graph the distribution of predictor variables in their raw distribution and after log-transformation since all variables are positive values, and many are zero-inflated; we also run shapiro-wilk tests to test for normality including the log-transformed variable if the log-transformed distribution looks better (less skewed)

# use as is, log won't work because some data are zero
ggplot(sites, aes(x = tree100m)) +
  geom_density()
shapiro.test(sites$tree100m) # not normal

# use as is, log won't work because some data are zero
ggplot(sites, aes(x = imperv100m)) +
  geom_density()
shapiro.test(sites$imperv100m) # not normal

# better log-transformed
ggarrange(ggplot(sites, aes(x = TotalSub)) + 
            geom_density(), 
          ggplot(sites, aes(x = log(TotalSub))) +
            geom_density(), 
          nrow = 1, 
          ncol = 2)
shapiro.test(sites$TotalSub) # not normal
shapiro.test(log(sites$TotalSub)) # normal

# better log-transformed
ggarrange(ggplot(sites, aes(x = Traffic_Dist_Road)) + 
            geom_density(), 
          ggplot(sites, aes(x = log(Traffic_Dist_Road))) + 
            geom_density(), 
          nrow = 1, 
          ncol = 2)
shapiro.test(sites$Traffic_Dist_Road) # not normal
shapiro.test(log(sites$Traffic_Dist_Road)) # normal

# better log-transformed
ggarrange(ggplot(sites, aes(x = Traffic_Dist_Highway)) + 
            geom_density(), 
          ggplot(sites, aes(x = log(Traffic_Dist_Highway))) + 
            geom_density(), 
          nrow = 1, 
          ncol = 2)
shapiro.test(sites$Traffic_Dist_Highway) # not normal
shapiro.test(log(sites$Traffic_Dist_Highway)) # almost normal

# looks similar either way
ggarrange(ggplot(sites, aes(x = spec_rad)) + 
            geom_density(), 
          ggplot(sites, aes(x = log(spec_rad))) + 
            geom_density(), 
          nrow = 1, 
          ncol = 2)
shapiro.test(sites$spec_rad) # not normal
shapiro.test(log(sites$spec_rad)) # not normal

# looks similar either way, but shapiro tests suggests as is is slightly better
ggarrange(ggplot(sites, aes(x = light_rad)) + 
            geom_density(), 
          ggplot(sites, aes(x = log(light_rad))) + 
            geom_density(), 
          nrow = 1, 
          ncol = 2)
shapiro.test(sites$light_rad) # not normal
shapiro.test(log(sites$light_rad)) # not normal

# better log-transformed
ggarrange(ggplot(sites, aes(x = patch_area_km)) +
            geom_density(), 
          ggplot(sites, aes(x = log(patch_area_km))) +
            geom_density(), 
          nrow = 1, 
          ncol = 2)
shapiro.test(sites$patch_area_km) # not normal
shapiro.test(log(sites$patch_area_km)) # almost normal

# use as is, log won't work because some data are zero
ggplot(sites, aes(x = road_length_m)) + 
  geom_density()
shapiro.test(sites$road_length_m) # not normal

# use as is, log won't work because some data are zero
ggplot(sites, aes(x = trail_length_m)) + 
  geom_density()
shapiro.test(sites$trail_length_m) # not normal

sites <- sites %>% 
  mutate(log_TotalSub = log(TotalSub),
         log_tdr = log(Traffic_Dist_Road),
         log_tdh = log(Traffic_Dist_Highway),
         log_patch = log(patch_area_km))

webs <- webs %>% 
  mutate(log_TotalSub = log(TotalSub),
         log_tdr = log(Traffic_Dist_Road),
         log_tdh = log(Traffic_Dist_Highway),
         log_patch = log(patch_area_km))
```

We conclude to use log-transformations for TotalSub, Traffic_Dist_Road, Traffic_Dist_Highway, and patch_area_km.

## Variable Reduction Based on Correlations

```{r correlations_overall}
corr <- sites %>% 
  select(tree100m, imperv100m, TotalSub, 
         Traffic_Dist_Road, Traffic_Dist_Highway, 
         spec_rad, light_rad, patch_area_km, road_length_m)
# We exclude trail length from global correlations because trail length can only collected in Wilderness Park, and not for UNL City Campus

# When running findCorrelations, we get a vector of variables to remove to reduce pairwise correlations.

findCorrelation(cor(corr, method = "spearman"), cutoff = .6, verbose = TRUE, names = TRUE)

# This suggests that we remove tree100m, imperv100, spec_rad, light_rad, patch_area_km, road_length_m
# That leaves us with TotalSub, Traffic_Dist_Road, and Traffic_Dist_Highway

chart.Correlation(corr, histogram = TRUE, method = "spearman") # kendall, spearman

corr <- sites %>% 
  select(TotalSub, Traffic_Dist_Road, Traffic_Dist_Highway)
chart.Correlation(corr, histogram = TRUE, method = "spearman") # kendall, spearman

# Let's also test the variables after transformation

corr_transformed <- sites %>% 
  select(tree100m, imperv100m, log_TotalSub, 
         log_tdr, log_tdh, 
         spec_rad, light_rad, log_patch, road_length_m)

findCorrelation(cor(corr_transformed, method = "spearman"), cutoff = .6, verbose = TRUE, names = TRUE)

# This suggests to remove tree100m, imperv100m, spec_rad, light_rad, log_patch, and road_length_m.

# This leaves us with log_TotalSub, log_tdr, and log_tdh, the same results as the non-transformed.

chart.Correlation(corr_transformed, histogram = TRUE, method = "spearman") # kendall, spearman

corr_transformed <- sites %>% 
  select(log_TotalSub, log_tdr, log_tdh)
chart.Correlation(corr_transformed, histogram = TRUE, method = "spearman") # kendall, spearman
```

```{r correlations_forest}
corr_forest <- sites %>% 
  filter(Location == "Urban Forest") %>% 
  select(tree100m, imperv100m, TotalSub, 
         Traffic_Dist_Road, Traffic_Dist_Highway, 
         spec_rad, light_rad, patch_area_km, road_length_m, trail_length_m)
# Notice trail length is included

findCorrelation(cor(corr_forest, method = "spearman"), cutoff = .6, verbose = TRUE, names = TRUE) 
# This suggests removing imperv100m, spec_rad, light_rad, road_length_m, and trail_length_m
# We will keep tree100m, TotalSub, Traffic_Dist_Road, Traffic_Dist_Highway, and patch_area_km
chart.Correlation(corr_forest, histogram = TRUE, method = "spearman")
corr_forest <- sites %>% 
  filter(Location == "Urban Forest") %>% 
  select(tree100m, TotalSub, Traffic_Dist_Road, patch_area_km, Traffic_Dist_Highway)
chart.Correlation(corr_forest, histogram = TRUE, method = "spearman")

# Let's try with the log-transformed
corr_forest_transformed <- sites %>% 
  filter(Location == "Wilderness Park") %>% 
  select(tree100m, imperv100m, log_TotalSub, 
         log_tdr, log_tdh, 
         spec_rad, light_rad, log_patch, road_length_m, trail_length_m)

findCorrelation(cor(corr_forest_transformed, method = "spearman"), cutoff = .6, verbose = TRUE, names = TRUE) 
# The same variables are dropped and kept

corr_forest_transformed <- sites %>% 
  filter(Location == "Urban Forest") %>% 
  select(tree100m, log_TotalSub, log_tdr, patch_area_km, log_tdh)
chart.Correlation(corr_forest_transformed, histogram = TRUE, method = "spearman")
```

```{r correlations_center}
corr_center <- sites %>% 
  filter(Location == "Urban Center") %>% 
  select(tree100m, imperv100m, TotalSub, Traffic_Dist_Road, Traffic_Dist_Highway, spec_rad, light_rad, patch_area_km, road_length_m)
# Trail length is removed because we could not measure trail length on campus

findCorrelation(cor(corr_center, method = "spearman"), cutoff = .6, verbose = TRUE, names = TRUE) 
# This suggests that we remove tree100m, imperv100m, and light_rad
# We will keep TotalSub, Traffic_Dist_Road, Traffic_Dist_Highway, spec_rad, patch_area_km, and road_length_m

chart.Correlation(corr_center, histogram = TRUE, method = "spearman")

# Let's try with the transformed
corr_center_transformed <- sites %>% 
  filter(Location == "Urban Center") %>% 
  select(tree100m, imperv100m, log_TotalSub, log_tdr, log_tdh, spec_rad, light_rad, log_patch, road_length_m)
findCorrelation(cor(corr_center_transformed, method = "spearman"), cutoff = .6, verbose = TRUE, names = TRUE) 
chart.Correlation(corr_center_transformed, histogram = TRUE, method = "pearson")
# The same variables are kept or removed
```

For overall analysis of predictors, we will include:

- log_TotalSub

- log_tdr

- log_tdh

For the urban forest subset, we will use:

- tree100m

- log_TotalSub

- log_tdr

- log_tdh

- log_patch

Finally, for the urban center subset, we will use:

- log_TotalSub

- log_tdr

- log_tdh

- spec_rad

- log_patch

- road_length_m

## Graphs and Stats Comparing Predictors by Location
```{r stats_graphs_tree}
tree100m <- glm(tree100m ~ Location, family = "poisson", data = sites)
summary(tree100m)

# The following line tells you the mean and standard error of the raw data for tree cover in a 100 m radius of the sites between the two locations
sites %>% 
  group_by(Location) %>% 
  summarize(mean = mean(tree100m),
            se = plotrix::std.error(tree100m))

predictions <- summary(emmeans(tree100m, ~Location),type = "response")

ggplot(sites, aes(x = Location, y = tree100m)) + 
  geom_jitter(color = "grey", width = 0.1, size = 1) +
  geom_point(aes(x = Location, y = rate, color = Location), size = 4, data = predictions) + 
  geom_errorbar(aes(x = Location, 
                  ymin = rate - SE, 
                  ymax = rate + SE,
                  color = Location), data = predictions, inherit.aes = FALSE, width = 0.25, linewidth = 2) +
  scale_color_manual(values = c("Urban Center" = "#d95f02", "Urban Forest" = "#1b9e77")) +
  scale_x_discrete(labels=c("Urban Forest" = "Urban \nForest \nN = 10", "Urban Center" = "Urban \nCenter \nN = 12")) +
  scale_y_continuous(limits=c(0, 100), breaks = c(0, 10, 20, 30, 40, 50, 60, 70, 80, 90, 100)) +
  theme_classic() +
  ylab("Percent Tree Cover \n[100m radius]") + 
  theme(text = element_text(size = 18)) + 
  theme(axis.text.x=element_text(colour="black", size=18)) + 
  theme(axis.text.y=element_text(colour="black", size=18),
        axis.title.x = element_blank()) +
  theme(legend.position = "none") +
  annotate(geom="text", x=1.5, y=100, label="***", color="black", size = 10)
```

### 2022-11-21 data_analysis.Rmd
Finished analyses around the response variable, search distance

@@
 
+Using include = FALSE means that this chunk will run, but the code and the results will not appear in the knitted document.
+We have set message and warning to FALSE for every chunk so the knitted document is not bombarded with messages and warnings.
+
 ```{r setup, include = FALSE}
@@
 
-```{r packages, echo = FALSE}
+There is a brief explanation of each package's purpose left as a comment following the library call.
+
+```{r packages, include = FALSE}
 library(tidyverse) # to use pipelines in data wrangling
@@
 library(emmeans) # for calculating predictions for graphing
+library(pander) # viewing AIC comparisons between models
+library(AICcmodavg) # also helps viewing AIC comparisons
+library(MuMIn) # to run the dredge function
 ```
@@
 
-```{r import}
+The document "webs" is a text file in the data folder of the repository/directory.
+
+```{r import, include = FALSE}
 webs <- read.table(file = "data/webs.txt", header = TRUE) 
@@
 
-```{r webs_wrangling}
-# Here, we rename some levels of factors Location and Land and put them in the order we want the categories to appear in a graph
+Here, we rename some levels of factors Location and Land and put them in the order we want the categories to appear in a graph.
+We also create another data set "sites" that restricts "webs" to just a single data point for each site.
+We use "sites" to compare search distance, the number of webs, and the number of spiders.
+We will use "webs" for web height and nearest neighbor analyses.
 
+```{r webs_wrangling, include = FALSE}
 webs <- webs %>% 
@@
   filter(Web == "W001") 
-# Restricted to site data only (only one data point per site)
 ```
 
-```{r sites_wrangling}
-# At one time, we tried scaling and centering the data in difference ways.
+At one time, we tried scaling and centering the data in difference ways.
 I want to make mention of it here because it might be useful information for me to look back on in the future.
@@
 
+```{r sites_wrangling, include = FALSE}
 sites <- sites %>% 
@@
 
-```{r location_subsets}
-webs_center <- webs %>% 
-  filter(Location == "Urban Center")
-
-webs_forest <- webs %>% 
-  filter(Location == "Urban Forest")
-
-sites_center <- sites %>% 
-  filter(Location == "Urban Center")
-
-sites_forest <- sites %>% 
-  filter(Location == "Urban Forest")
-```
-
 ## Transformation of Variables
 
-Many data are zero-inflated or right skewed. We check the distribution of the data and check distributions after log-transformation for right-skewed data not containing zeros.
+Many data are zero-inflated or right skewed.
+We check the distribution of the data and check distributions after log-transformation for right-skewed data not containing zeros.
+Echo = FALSE shows the results, but does not show the code used.
 
@@
 # better log-transformed
-ggarrange(ggplot(sites, aes(x = patch_area_km)) +
+ggarrange(ggplot(sites, aes(x = patch_area_mm)) +
             geom_density(), 
-          ggplot(sites, aes(x = log(patch_area_km))) +
+          ggplot(sites, aes(x = log(patch_area_mm))) +
             geom_density(), 
@@
           ncol = 2)
-shapiro.test(sites$patch_area_km) # not normal
-shapiro.test(log(sites$patch_area_km)) # almost normal
+shapiro.test(sites$patch_area_mm) # not normal
+shapiro.test(log(sites$patch_area_mm)) # almost normal
 
@@
          log_tdh = log(Traffic_Dist_Highway),
-         log_patch = log(patch_area_km))
+         log_patch = log(patch_area_mm))
+
+sites <- webs %>% 
+  filter(Web == "W001") 
 ```
@@
 
+Our analyses include looking at variation within each location. As such, this chunk subsets the "sites" and "webs" data by Location.
+
+```{r location_subsets, include  = FALSE}
+webs_center <- webs %>% 
+  filter(Location == "Urban Center")
+
+webs_forest <- webs %>% 
+  filter(Location == "Urban Forest")
+
+sites_center <- sites %>% 
+  filter(Location == "Urban Center")
+
+sites_forest <- sites %>% 
+  filter(Location == "Urban Forest")
+```
+
 ## Variable Reduction Based on Correlations
+
+Since many of these variables are likely highly correlated, we want to reduce the variables that we include in our model by removing variables that are highly correlated.
 
@@
          Traffic_Dist_Road, Traffic_Dist_Highway, 
-         spec_rad, light_rad, patch_area_km, road_length_m)
+         spec_rad, light_rad, patch_area_mm, road_length_m)
 # We exclude trail length from global correlations because trail length can only collected in Wilderness Park, and not for UNL City Campus
@@
 corr_forest_transformed <- sites %>% 
-  filter(Location == "Wilderness Park") %>% 
+  filter(Location == "Urban Forest") %>% 
   select(tree100m, imperv100m, log_TotalSub, 
@@
 
-## Graphs and Stats Comparing Predictors by Location
-```{r stats_graphs_tree}
+## Graphs, Stats, and Assumptions Comparing Predictors by Location
+
+Here, we just want to see if each predictor differs between the two Locations: urban forest and urban center. We build models, check assumptions of the model, and make graphs to represent differences.
+
+```{r stats_graphs_tree, echo = FALSE}
 tree100m <- glm(tree100m ~ Location, family = "poisson", data = sites)
@@
   geom_jitter(color = "grey", width = 0.1, size = 1) +
-  geom_point(aes(x = Location, y = rate, color = Location), size = 4, data = predictions) + 
+  geom_point(aes(x = Location, y = rate, color = Location), size = 2, data = predictions) + 
   geom_errorbar(aes(x = Location, 
@@
                   ymax = rate + SE,
-                  color = Location), data = predictions, inherit.aes = FALSE, width = 0.25, linewidth = 2) +
+                  color = Location), data = predictions, inherit.aes = FALSE, width = 0.15, linewidth = 1.5) +
   scale_color_manual(values = c("Urban Center" = "#d95f02", "Urban Forest" = "#1b9e77")) +
@@
 ```
+
+```{r tree_assumptions, echo = FALSE}
+test_tree <- augment(tree100m, data = sites)
+resid_tree <- ggplot(test_tree, aes(x = .fitted, y = .resid)) + 
+  geom_point() + 
+  geom_smooth() +
+  geom_hline(yintercept = 0) +
+  xlab("Fitted Values") +
+  ylab("Standardized \nResiduals") +
+  theme_classic() +
+  theme(text = element_text(size = 14, color = "black")) +
+  theme(axis.text.x=element_text(color="black", size=14)) + 
+  theme(axis.text.y=element_text(color="black", size=14))
+
+y <- quantile(test_tree$.resid, c(0.25, 0.75))
+x <- qnorm(c(0.25, 0.75))
+slope <- diff(y)/diff(x)
+int <- y[1L] - slope * x[1L]
+
+qq_tree <- ggplot(test_tree, aes(sample = .resid)) + 
+  stat_qq() + 
+  geom_abline(slope = slope, intercept = int) +
+  xlab("Theoretical Quantiles") +
+  ylab("Sample Quantiles") +
+  theme_classic() +
+  theme(text = element_text(size = 14, color = "black")) +
+  theme(axis.text.x=element_text(color="black", size=14)) + 
+  theme(axis.text.y=element_text(color="black", size=14))
+
+ggarrange(resid_tree, qq_tree, 
+          labels = c("A", "B"),
+          ncol = 2, nrow = 1)
+```
+
+Tree cover is *significantly higher in the urban forest* than the urban center (z = -14.50, df = 1, 20, p < 0.001).
+The means and SE's are 47.15 ± 2.17 % for the urban forest and 1.58 ± 0.36 % for the urban center.
+
+```{r stats_graphs_imperv, echo = FALSE}
+imperv100m <- glm(imperv100m ~ Location, family = "poisson", data = sites)
+summary(imperv100m)
+
+# The following line tells you the mean and standard error of the raw data for impervious cover in a 100 m radius of the sites between the two locations
+sites %>% 
+  group_by(Location) %>% 
+  summarize(mean = mean(imperv100m),
+            se = plotrix::std.error(imperv100m))
+
+predictions <- summary(emmeans(imperv100m, ~Location),type = "response")
+
+ggplot(sites, aes(x = Location, y = imperv100m)) + 
+  geom_jitter(color = "grey", width = 0.1, size = 1) +
+  geom_point(aes(x = Location, y = rate, color = Location), size = 2, data = predictions) + 
+  geom_errorbar(aes(x = Location, 
+                  ymin = rate - SE, 
+                  ymax = rate + SE,
+                  color = Location), data = predictions, inherit.aes = FALSE, width = 0.15, linewidth = 1.5) +
+  scale_color_manual(values = c("Urban Center" = "#d95f02", "Urban Forest" = "#1b9e77")) +
+  scale_x_discrete(labels=c("Urban Forest" = "Urban \nForest \nN = 10", "Urban Center" = "Urban \nCenter \nN = 12")) +
+  scale_y_continuous(limits=c(0, 100), breaks = c(0, 10, 20, 30, 40, 50, 60, 70, 80, 90, 100)) +
+  theme_classic() +
+  ylab("Percent Impervious Cover \n[100m radius]") + 
+  theme(text = element_text(size = 18)) + 
+  theme(axis.text.x=element_text(colour="black", size=18)) + 
+  theme(axis.text.y=element_text(colour="black", size=18),
+        axis.title.x = element_blank()) +
+  theme(legend.position = "none") +
+  annotate(geom="text", x=1.5, y=100, label="***", color="black", size = 10)
+```
+
+```{r imperv_assumptions, echo = FALSE}
+test_imperv <- augment(imperv100m, data = sites)
+resid_imperv <- ggplot(test_imperv, aes(x = .fitted, y = .resid)) + 
+  geom_point() + 
+  geom_smooth() +
+  geom_hline(yintercept = 0) +
+  xlab("Fitted Values") +
+  ylab("Standardized \nResiduals") +
+  theme_classic() +
+  theme(text = element_text(size = 14, color = "black")) +
+  theme(axis.text.x=element_text(color="black", size=14)) + 
+  theme(axis.text.y=element_text(color="black", size=14))
+
+y <- quantile(test_imperv$.resid, c(0.25, 0.75))
+x <- qnorm(c(0.25, 0.75))
+slope <- diff(y)/diff(x)
+int <- y[1L] - slope * x[1L]
+
+qq_imperv <- ggplot(test_imperv, aes(sample = .resid)) + 
+  stat_qq() + 
+  geom_abline(slope = slope, intercept = int) +
+  xlab("Theoretical Quantiles") +
+  ylab("Sample Quantiles") +
+  theme_classic() +
+  theme(text = element_text(size = 14, color = "black")) +
+  theme(axis.text.x=element_text(color="black", size=14)) + 
+  theme(axis.text.y=element_text(color="black", size=14))
+
+ggarrange(resid_imperv, qq_imperv, 
+          labels = c("A", "B"),
+          ncol = 2, nrow = 1)
+```
+
+Impervious cover is *significantly higher in the urban center* than the urban forest (z = 14.51, df = 1, 20, p < 0.001).
+The means and SE's are 1.27 ± 0.36 % for the urban forest and 76.52 ± 2.53 % for the urban center.
+
+```{r stats_graphs_tdr, echo = FALSE}
+tdr <- glm(log_tdr ~ Location, family = "poisson", data = sites)
+summary(tdr)
+
+sites %>% 
+  group_by(Location) %>% 
+  summarize(mean = mean(log_tdr),
+            se = plotrix::std.error(log_tdr))
+
+predictions <- summary(emmeans(tdr, ~Location),type = "response")
+
+ggplot(sites, aes(x = Location, y = exp(log_tdr))) + 
+  geom_jitter(color = "grey", width = 0.1, size = 1) +
+  geom_point(aes(x = Location, y = exp(rate), color = Location), size = 2, data = predictions) + 
+  geom_errorbar(aes(x = Location, 
+                  ymin = exp(rate - SE), 
+                  ymax = exp(rate + SE),
+                  color = Location), data = predictions, inherit.aes = FALSE, width = 0.15, linewidth = 1.5) +
+  scale_color_manual(values = c("Urban Center" = "#d95f02", "Urban Forest" = "#1b9e77")) +
+  scale_x_discrete(labels=c("Urban Forest" = "Urban \nForest \nN = 10", "Urban Center" = "Urban \nCenter \nN = 12")) +
+  scale_y_continuous(limits=c(0, 1400), breaks = c(0, 200, 400, 600, 800, 1000, 1200, 1400)) +
+  theme_classic() +
+  ylab("Road Disturbance \n[vehicles/day/m]") + 
+  theme(text = element_text(size = 18)) + 
+  theme(axis.text.x=element_text(colour="black", size=18)) + 
+  theme(axis.text.y=element_text(colour="black", size=18),
+        axis.title.x = element_blank()) +
+  theme(legend.position = "none") +
+  annotate(geom="text", x=1.5, y=1400, label="", color="black", size = 10)
+```
+
+```{r tdr_assumptions, echo = FALSE}
+test_tdr <- augment(tdr, data = sites)
+resid_tdr <- ggplot(test_tdr, aes(x = .fitted, y = .resid)) + 
+  geom_point() + 
+  geom_smooth() +
+  geom_hline(yintercept = 0) +
+  xlab("Fitted Values") +
+  ylab("Standardized \nResiduals") +
+  theme_classic() +
+  theme(text = element_text(size = 14, color = "black")) +
+  theme(axis.text.x=element_text(color="black", size=14)) + 
+  theme(axis.text.y=element_text(color="black", size=14))
+
+y <- quantile(test_tdr$.resid, c(0.25, 0.75))
+x <- qnorm(c(0.25, 0.75))
+slope <- diff(y)/diff(x)
+int <- y[1L] - slope * x[1L]
+
+qq_tdr <- ggplot(test_tdr, aes(sample = .resid)) + 
+  stat_qq() + 
+  geom_abline(slope = slope, intercept = int) +
+  xlab("Theoretical Quantiles") +
+  ylab("Sample Quantiles") +
+  theme_classic() +
+  theme(text = element_text(size = 14, color = "black")) +
+  theme(axis.text.x=element_text(color="black", size=14)) + 
+  theme(axis.text.y=element_text(color="black", size=14))
+
+ggarrange(resid_tdr, qq_tdr, 
+          labels = c("A", "B"),
+          ncol = 2, nrow = 1)
+```
+
+There is *no difference* in road disturbance between the urban forest and urban center (z = 1.403, df = 1, 20, p = 0.161).
+The means and SE's are 52.98 ± 1.88 vehicles/day/m for the urban forest and 194.42 ± 1.93 vehicles/day/m for the urban center.
+
+```{r stats_graphs_tdh, echo = FALSE}
+tdh <- glm(log_tdh ~ Location, family = "poisson", data = sites)
+summary(tdh)
+
+sites %>% 
+  group_by(Location) %>% 
+  summarize(mean = mean(log_tdh),
+            se = plotrix::std.error(log_tdh))
+
+predictions <- summary(emmeans(tdh, ~Location),type = "response")
+
+ggplot(sites, aes(x = Location, y = exp(log_tdh))) + 
+  geom_jitter(color = "grey", width = 0.1, size = 1) +
+  geom_point(aes(x = Location, y = exp(rate), color = Location), size = 2, data = predictions) + 
+  geom_errorbar(aes(x = Location, 
+                  ymin = exp(rate - SE), 
+                  ymax = exp(rate + SE),
+                  color = Location), data = predictions, inherit.aes = FALSE, width = 0.15, linewidth = 1.5) +
+  scale_color_manual(values = c("Urban Center" = "#d95f02", "Urban Forest" = "#1b9e77")) +
+  scale_x_discrete(labels=c("Urban Forest" = "Urban \nForest \nN = 10", "Urban Center" = "Urban \nCenter \nN = 12")) +
+  scale_y_continuous(limits=c(0, 250), breaks = c(0, 50, 100, 150, 200, 250)) +
+  theme_classic() +
+  ylab("Highway Disturbance \n[vehicles/day/m]") + 
+  theme(text = element_text(size = 18)) + 
+  theme(axis.text.x=element_text(colour="black", size=18)) + 
+  theme(axis.text.y=element_text(colour="black", size=18),
+        axis.title.x = element_blank()) +
+  theme(legend.position = "none") +
+  annotate(geom="text", x=1.5, y=250, label="", color="black", size = 10)
+```
+
+```{r tdh_assumptions, echo = FALSE}
+test_tdh <- augment(tdh, data = sites)
+resid_tdh <- ggplot(test_tdh, aes(x = .fitted, y = .resid)) + 
+  geom_point() + 
+  geom_smooth() +
+  geom_hline(yintercept = 0) +
+  xlab("Fitted Values") +
+  ylab("Standardized \nResiduals") +
+  theme_classic() +
+  theme(text = element_text(size = 14, color = "black")) +
+  theme(axis.text.x=element_text(color="black", size=14)) + 
+  theme(axis.text.y=element_text(color="black", size=14))
+
+y <- quantile(test_tdh$.resid, c(0.25, 0.75))
+x <- qnorm(c(0.25, 0.75))
+slope <- diff(y)/diff(x)
+int <- y[1L] - slope * x[1L]
+
+qq_tdh <- ggplot(test_tdh, aes(sample = .resid)) + 
+  stat_qq() + 
+  geom_abline(slope = slope, intercept = int) +
+  xlab("Theoretical Quantiles") +
+  ylab("Sample Quantiles") +
+  theme_classic() +
+  theme(text = element_text(size = 14, color = "black")) +
+  theme(axis.text.x=element_text(color="black", size=14)) + 
+  theme(axis.text.y=element_text(color="black", size=14))
+
+ggarrange(resid_tdh, qq_tdh, 
+          labels = c("A", "B"),
+          ncol = 2, nrow = 1)
+```
+
+There is *no difference* in highway disturbance between the urban forest and urban center (z = 0.530, df = 1, 20, p = 0.596).
+The means and SE's are 33.78 ± 1.80 vehicles/day/m for the urban forest and 52.46 ± 1.77 vehicles/day/m for the urban center.
+
+```{r stats_graphs_plant, echo = FALSE}
+plant <- glm(log_TotalSub ~ Location, family = "poisson", data = sites)
+summary(plant)
+
+sites %>% 
+  group_by(Location) %>% 
+  summarize(mean = mean(log_TotalSub),
+            se = plotrix::std.error(log_TotalSub))
+
+predictions <- summary(emmeans(plant, ~Location),type = "response")
+
+ggplot(sites, aes(x = Location, y = exp(log_TotalSub))) + 
+  geom_jitter(color = "grey", width = 0.1, size = 1) +
+  geom_point(aes(x = Location, y = exp(rate), color = Location), size = 2, data = predictions) + 
+  geom_errorbar(aes(x = Location, 
+                  ymin = exp(rate - SE), 
+                  ymax = exp(rate + SE),
+                  color = Location), data = predictions, inherit.aes = FALSE, width = 0.15, linewidth = 1.5) +
+  scale_color_manual(values = c("Urban Center" = "#d95f02", "Urban Forest" = "#1b9e77")) +
+  scale_x_discrete(labels=c("Urban Forest" = "Urban \nForest \nN = 10", "Urban Center" = "Urban \nCenter \nN = 12")) +
+  scale_y_continuous(limits=c(0, 25), breaks = c(0, 5, 10, 15, 20, 25)) +
+  theme_classic() +
+  ylab("Plant Species Richness \n[species/site]") + 
+  theme(text = element_text(size = 18)) + 
+  theme(axis.text.x=element_text(colour="black", size=18)) + 
+  theme(axis.text.y=element_text(colour="black", size=18),
+        axis.title.x = element_blank()) +
+  theme(legend.position = "none") +
+  annotate(geom="text", x=1.5, y=25, label="*", color="black", size = 10)
+```
+
+```{r plant_assumptions, echo = FALSE}
+test_plant <- augment(plant, data = sites)
+resid_plant <- ggplot(test_plant, aes(x = .fitted, y = .resid)) + 
+  geom_point() + 
+  geom_smooth() +
+  geom_hline(yintercept = 0) +
+  xlab("Fitted Values") +
+  ylab("Standardized \nResiduals") +
+  theme_classic() +
+  theme(text = element_text(size = 14, color = "black")) +
+  theme(axis.text.x=element_text(color="black", size=14)) + 
+  theme(axis.text.y=element_text(color="black", size=14))
+
+y <- quantile(test_plant$.resid, c(0.25, 0.75))
+x <- qnorm(c(0.25, 0.75))
+slope <- diff(y)/diff(x)
+int <- y[1L] - slope * x[1L]
+
+qq_plant <- ggplot(test_plant, aes(sample = .resid)) + 
+  stat_qq() + 
+  geom_abline(slope = slope, intercept = int) +
+  xlab("Theoretical Quantiles") +
+  ylab("Sample Quantiles") +
+  theme_classic() +
+  theme(text = element_text(size = 14, color = "black")) +
+  theme(axis.text.x=element_text(color="black", size=14)) + 
+  theme(axis.text.y=element_text(color="black", size=14))
+
+ggarrange(resid_plant, qq_plant, 
+          labels = c("A", "B"),
+          ncol = 2, nrow = 1)
+```
+
+Plant species richness is *significantly higher in the urban forest* than the urban center (z = -2.430, df = 1, 20, p = 0.015).
+The means and SE's are 12.18 ± 1.65 species for the urban forest and 2.97 ± 1.35 species for the urban center.
+
+```{r stats_graphs_spec, echo = FALSE}
+spec <- glm(spec_rad ~ Location, family = "poisson", data = sites)
+summary(spec)
+
+sites %>% 
+  group_by(Location) %>% 
+  summarize(mean = mean(spec_rad),
+            se = plotrix::std.error(spec_rad))
+
+predictions <- summary(emmeans(spec, ~Location),type = "response")
+
+ggplot(sites, aes(x = Location, y = spec_rad)) + 
+  geom_jitter(color = "grey", width = 0.1, size = 1) +
+  geom_point(aes(x = Location, y = rate, color = Location), size = 2, data = predictions) + 
+  geom_errorbar(aes(x = Location, 
+                  ymin = rate - SE, 
+                  ymax = rate + SE,
+                  color = Location), data = predictions, inherit.aes = FALSE, width = 0.15, linewidth = 1.5) +
+  scale_color_manual(values = c("Urban Center" = "#d95f02", "Urban Forest" = "#1b9e77")) +
+  scale_x_discrete(labels=c("Urban Forest" = "Urban \nForest \nN = 10", "Urban Center" = "Urban \nCenter \nN = 12")) +
+  scale_y_continuous(limits=c(130, 165), breaks = c(130, 135, 140, 145, 150, 155, 160, 165)) +
+  theme_classic() +
+  ylab("Spectral Radiance \n[Watts/(m² * sr * µm)]") + 
+  theme(text = element_text(size = 18)) + 
+  theme(axis.text.x=element_text(colour="black", size=18)) + 
+  theme(axis.text.y=element_text(colour="black", size=18),
+        axis.title.x = element_blank()) +
+  theme(legend.position = "none") +
+  annotate(geom="text", x=1.5, y=165, label="**", color="black", size = 10)
+```
+
+```{r spec_assumptions, echo = FALSE}
+test_spec <- augment(plant, data = sites)
+resid_spec <- ggplot(test_spec, aes(x = .fitted, y = .resid)) + 
+  geom_point() + 
+  geom_smooth() +
+  geom_hline(yintercept = 0) +
+  xlab("Fitted Values") +
+  ylab("Standardized \nResiduals") +
+  theme_classic() +
+  theme(text = element_text(size = 14, color = "black")) +
+  theme(axis.text.x=element_text(color="black", size=14)) + 
+  theme(axis.text.y=element_text(color="black", size=14))
+
+y <- quantile(test_spec$.resid, c(0.25, 0.75))
+x <- qnorm(c(0.25, 0.75))
+slope <- diff(y)/diff(x)
+int <- y[1L] - slope * x[1L]
+
+qq_spec <- ggplot(test_spec, aes(sample = .resid)) + 
+  stat_qq() + 
+  geom_abline(slope = slope, intercept = int) +
+  xlab("Theoretical Quantiles") +
+  ylab("Sample Quantiles") +
+  theme_classic() +
+  theme(text = element_text(size = 14, color = "black")) +
+  theme(axis.text.x=element_text(color="black", size=14)) + 
+  theme(axis.text.y=element_text(color="black", size=14))
+
+ggarrange(resid_spec, qq_spec, 
+          labels = c("A", "B"),
+          ncol = 2, nrow = 1)
+```
+
+Spectral radiance is *significantly higher in the urban center* than the urban forest (z = 3.079, df = 1, 20, p = 0.002).
+The means and SE's are 137.44 ± 3.71 Watts/(m² * sr * µm) for the urban forest and 153.39 ± 3.58 Watts/(m² * sr * µm) for the urban center.
+
+```{r stats_graphs_light, echo = FALSE}
+light <- glm(light_rad ~ Location, family = "poisson", data = sites)
+summary(light)
+
+sites %>% 
+  group_by(Location) %>% 
+  summarize(mean = mean(light_rad),
+            se = plotrix::std.error(light_rad))
+
+predictions <- summary(emmeans(light, ~Location),type = "response")
+
+ggplot(sites, aes(x = Location, y = light_rad)) + 
+  geom_jitter(color = "grey", width = 0.1, size = 1) +
+  geom_point(aes(x = Location, y = rate, color = Location), size = 2, data = predictions) + 
+  geom_errorbar(aes(x = Location, 
+                  ymin = rate - SE, 
+                  ymax = rate + SE,
+                  color = Location), data = predictions, inherit.aes = FALSE, width = 0.15, linewidth = 1.5) +
+  scale_color_manual(values = c("Urban Center" = "#d95f02", "Urban Forest" = "#1b9e77")) +
+  scale_x_discrete(labels=c("Urban Forest" = "Urban \nForest \nN = 10", "Urban Center" = "Urban \nCenter \nN = 12")) +
+  scale_y_continuous(limits=c(0, 175), breaks = c(0, 25, 50, 75, 100, 125, 150, 175)) +
+  theme_classic() +
+  ylab("Radiance [mcd/m²]") + 
+  theme(text = element_text(size = 18)) + 
+  theme(axis.text.x=element_text(colour="black", size=18)) + 
+  theme(axis.text.y=element_text(colour="black", size=18),
+        axis.title.x = element_blank()) +
+  theme(legend.position = "none") +
+  annotate(geom="text", x=1.5, y=175, label="***", color="black", size = 10)
+```
+
+```{r light_assumptions, echo = FALSE}
+test_light <- augment(plant, data = sites)
+resid_light <- ggplot(test_light, aes(x = .fitted, y = .resid)) + 
+  geom_point() + 
+  geom_smooth() +
+  geom_hline(yintercept = 0) +
+  xlab("Fitted Values") +
+  ylab("Standardized \nResiduals") +
+  theme_classic() +
+  theme(text = element_text(size = 14, color = "black")) +
+  theme(axis.text.x=element_text(color="black", size=14)) + 
+  theme(axis.text.y=element_text(color="black", size=14))
+
+y <- quantile(test_light$.resid, c(0.25, 0.75))
+x <- qnorm(c(0.25, 0.75))
+slope <- diff(y)/diff(x)
+int <- y[1L] - slope * x[1L]
+
+qq_light <- ggplot(test_light, aes(sample = .resid)) + 
+  stat_qq() + 
+  geom_abline(slope = slope, intercept = int) +
+  xlab("Theoretical Quantiles") +
+  ylab("Sample Quantiles") +
+  theme_classic() +
+  theme(text = element_text(size = 14, color = "black")) +
+  theme(axis.text.x=element_text(color="black", size=14)) + 
+  theme(axis.text.y=element_text(color="black", size=14))
+
+ggarrange(resid_light, qq_light, 
+          labels = c("A", "B"),
+          ncol = 2, nrow = 1)
+```
+
+Light radiance is *significantly higher in the urban center* than the urban forest (z = 22.46, df = 1, 20, p < 0.001).
+The means and SE's are 5.89 ± 0.77 mcd/m² for the urban forest and 116.90 ± 3.12 mcd/m² for the urban center.
+
+```{r stats_graphs_patch, echo = FALSE}
+patch <- glm(log_patch ~ Location, family = "poisson", data = sites)
+summary(patch)
+
+sites %>% 
+  group_by(Location) %>% 
+  summarize(mean = mean(log_patch),
+            se = plotrix::std.error(log_patch))
+
+predictions <- summary(emmeans(patch, ~Location),type = "response")
+
+ggplot(sites, aes(x = Location, y = exp(log_patch))) + 
+  geom_jitter(color = "grey", width = 0.1, size = 1) +
+  geom_point(aes(x = Location, y = exp(rate), color = Location), size = 2, data = predictions) + 
+  geom_errorbar(aes(x = Location, 
+                  ymin = exp(rate - SE), 
+                  ymax = exp(rate + SE),
+                  color = Location), data = predictions, inherit.aes = FALSE, width = 0.15, linewidth = 1.5) +
+  scale_color_manual(values = c("Urban Center" = "#d95f02", "Urban Forest" = "#1b9e77")) +
+  scale_x_discrete(labels=c("Urban Forest" = "Urban \nForest \nN = 10", "Urban Center" = "Urban \nCenter \nN = 12")) +
+  scale_y_continuous(limits=c(0, 130310), breaks = c(0, 20000, 40000, 60000, 80000, 100000, 120000)) +
+  theme_classic() +
+  ylab("Patch Area [mm²]") + 
+  theme(text = element_text(size = 18)) + 
+  theme(axis.text.x=element_text(colour="black", size=18)) + 
+  theme(axis.text.y=element_text(colour="black", size=18),
+        axis.title.x = element_blank()) +
+  theme(legend.position = "none") +
+  annotate(geom="text", x=1.5, y=130310, label="***", color="black", size = 10)
+```
+
+```{r patch_assumptions, echo = FALSE}
+test_patch <- augment(patch, data = sites)
+resid_patch <- ggplot(test_patch, aes(x = .fitted, y = .resid)) + 
+  geom_point() + 
+  geom_smooth() +
+  geom_hline(yintercept = 0) +
+  xlab("Fitted Values") +
+  ylab("Standardized \nResiduals") +
+  theme_classic() +
+  theme(text = element_text(size = 14, color = "black")) +
+  theme(axis.text.x=element_text(color="black", size=14)) + 
+  theme(axis.text.y=element_text(color="black", size=14))
+
+y <- quantile(test_patch$.resid, c(0.25, 0.75))
+x <- qnorm(c(0.25, 0.75))
+slope <- diff(y)/diff(x)
+int <- y[1L] - slope * x[1L]
+
+qq_patch <- ggplot(test_patch, aes(sample = .resid)) + 
+  stat_qq() + 
+  geom_abline(slope = slope, intercept = int) +
+  xlab("Theoretical Quantiles") +
+  ylab("Sample Quantiles") +
+  theme_classic() +
+  theme(text = element_text(size = 14, color = "black")) +
+  theme(axis.text.x=element_text(color="black", size=14)) + 
+  theme(axis.text.y=element_text(color="black", size=14))
+
+ggarrange(resid_patch, qq_patch, 
+          labels = c("A", "B"),
+          ncol = 2, nrow = 1)
+```
+
+Patch area is *significantly higher in the urban forest* than the urban center (z = -3.599, df = 1, 20, p < 0.001).
+The means and SE's are 37,049.12 ± 2.80 mm^2 for the urban forest and 437.03 ± 2.03 mm^2 for the urban center.
+
+```{r stats_graphs_road, echo = FALSE}
+road <- glm(road_length_m ~ Location, family = "poisson", data = sites)
+summary(road)
+
+sites %>% 
+  group_by(Location) %>% 
+  summarize(mean = mean(road_length_m),
+            se = plotrix::std.error(road_length_m))
+
+predictions <- summary(emmeans(road, ~Location),type = "response")
+
+ggplot(sites, aes(x = Location, y = road_length_m)) + 
+  geom_jitter(color = "grey", width = 0.1, size = 1) +
+  geom_point(aes(x = Location, y = rate, color = Location), size = 2, data = predictions) + 
+  geom_errorbar(aes(x = Location, 
+                  ymin = rate - SE, 
+                  ymax = rate + SE,
+                  color = Location), data = predictions, inherit.aes = FALSE, width = 0.15, linewidth = 1.5) +
+  scale_color_manual(values = c("Urban Center" = "#d95f02", "Urban Forest" = "#1b9e77")) +
+  scale_x_discrete(labels=c("Urban Forest" = "Urban \nForest \nN = 10", "Urban Center" = "Urban \nCenter \nN = 12")) +
+  scale_y_continuous(limits=c(0, 140), breaks = c(0, 20, 40, 60, 80, 100, 120, 140)) +
+  theme_classic() +
+  ylab("Total Length of Road \n[m, 100m radius]") + 
+  theme(text = element_text(size = 18)) + 
+  theme(axis.text.x=element_text(colour="black", size=18)) + 
+  theme(axis.text.y=element_text(colour="black", size=18),
+        axis.title.x = element_blank()) +
+  theme(legend.position = "none") +
+  annotate(geom="text", x=1.5, y=140, label="***", color="black", size = 10)
+```
+
+```{r road_assumptions, echo = FALSE}
+test_road <- augment(road, data = sites)
+resid_road <- ggplot(test_road, aes(x = .fitted, y = .resid)) + 
+  geom_point() + 
+  geom_smooth() +
+  geom_hline(yintercept = 0) +
+  xlab("Fitted Values") +
+  ylab("Standardized \nResiduals") +
+  theme_classic() +
+  theme(text = element_text(size = 14, color = "black")) +
+  theme(axis.text.x=element_text(color="black", size=14)) + 
+  theme(axis.text.y=element_text(color="black", size=14))
+
+y <- quantile(test_road$.resid, c(0.25, 0.75))
+x <- qnorm(c(0.25, 0.75))
+slope <- diff(y)/diff(x)
+int <- y[1L] - slope * x[1L]
+
+qq_road <- ggplot(test_road, aes(sample = .resid)) + 
+  stat_qq() + 
+  geom_abline(slope = slope, intercept = int) +
+  xlab("Theoretical Quantiles") +
+  ylab("Sample Quantiles") +
+  theme_classic() +
+  theme(text = element_text(size = 14, color = "black")) +
+  theme(axis.text.x=element_text(color="black", size=14)) + 
+  theme(axis.text.y=element_text(color="black", size=14))
+
+ggarrange(resid_road, qq_road, 
+          labels = c("A", "B"),
+          ncol = 2, nrow = 1)
+```
+
+Total road length is *significantly higher in the urban center* than the urban forest (z = 20.89, df = 1, 20, p < 0.001).
+The means and SE's are 15.67 ± 1.25 m for the urban forest and 93.03 ± 2.78 m for the urban center.
+
+## Response Variable: Search Distance
+
+### Search Distance by Location
+
+```{r search_location_stats}
+ggarrange(ggplot(sites, aes(x = WalkDist)) +
+            geom_density(),
+          ggplot(sites, aes(x = log(WalkDist))) +
+            geom_density(), ncol = 2)
+
+shapiro.test(sites$WalkDist) # not normal
+shapiro.test(log(sites$WalkDist)) # normal
+
+search <- glm(WalkDist ~ Location, data = sites, family = poisson)
+summary(search)
+
+search2 <- glm(log(WalkDist) ~ Location, data = sites)
+summary(search2)
+
+sites %>% 
+  group_by(Location) %>% 
+  summarize(mean = mean(WalkDist),
+            se = plotrix::std.error(WalkDist))
+```
+
+```{r search_location_assumptions, echo = FALSE}
+# As is, Poisson
+test_search <- augment(search, data = sites)
+resid_search <- ggplot(test_search, aes(x = .fitted, y = .resid)) + 
+  geom_point() + 
+  geom_smooth() +
+  geom_hline(yintercept = 0) +
+  xlab("Fitted Values") +
+  ylab("Standardized \nResiduals") +
+  theme_classic() +
+  theme(text = element_text(size = 14, color = "black")) +
+  theme(axis.text.x=element_text(color="black", size=14)) + 
+  theme(axis.text.y=element_text(color="black", size=14))
+
+y <- quantile(test_search$.resid, c(0.25, 0.75))
+x <- qnorm(c(0.25, 0.75))
+slope <- diff(y)/diff(x)
+int <- y[1L] - slope * x[1L]
+
+qq_search <- ggplot(test_search, aes(sample = .resid)) + 
+  stat_qq() + 
+  geom_abline(slope = slope, intercept = int) +
+  xlab("Theoretical Quantiles") +
+  ylab("Sample Quantiles") +
+  theme_classic() +
+  theme(text = element_text(size = 14, color = "black")) +
+  theme(axis.text.x=element_text(color="black", size=14)) + 
+  theme(axis.text.y=element_text(color="black", size=14))
+
+ggarrange(resid_search, qq_search, 
+          labels = c("A", "B"),
+          ncol = 2, nrow = 1)
+
+# Log-transformed, Normal
+test_search2 <- augment(search2, data = sites)
+resid_search2 <- ggplot(test_search2, aes(x = .fitted, y = .resid)) + 
+  geom_point() + 
+  geom_smooth() +
+  geom_hline(yintercept = 0) +
+  xlab("Fitted Values") +
+  ylab("Standardized \nResiduals") +
+  theme_classic() +
+  theme(text = element_text(size = 14, color = "black")) +
+  theme(axis.text.x=element_text(color="black", size=14)) + 
+  theme(axis.text.y=element_text(color="black", size=14))
+
+y <- quantile(test_search2$.resid, c(0.25, 0.75))
+x <- qnorm(c(0.25, 0.75))
+slope <- diff(y)/diff(x)
+int <- y[1L] - slope * x[1L]
+
+qq_search2 <- ggplot(test_search2, aes(sample = .resid)) + 
+  stat_qq() + 
+  geom_abline(slope = slope, intercept = int) +
+  xlab("Theoretical Quantiles") +
+  ylab("Sample Quantiles") +
+  theme_classic() +
+  theme(text = element_text(size = 14, color = "black")) +
+  theme(axis.text.x=element_text(color="black", size=14)) + 
+  theme(axis.text.y=element_text(color="black", size=14))
+
+ggarrange(resid_search2, qq_search2, 
+          labels = c("A", "B"),
+          ncol = 2, nrow = 1)
+```
+
+```{r search_location_graph, echo = FALSE}
+# Non-transformed, poisson distribution
+predictions <- summary(emmeans(search, ~Location),type = "response")
+
+ggplot(sites, aes(x = Location, y = WalkDist)) + 
+  geom_jitter(color = "grey", width = 0.1) +
+  geom_point(aes(x = Location, y = rate, color = Location), size = 2, data = predictions) + 
+  geom_errorbar(aes(x = Location, 
+                  ymin = rate - SE, 
+                  ymax = rate + SE,
+                  color = Location), data = predictions, inherit.aes = FALSE, width = 0.15, size = 1.5) +
+  scale_color_manual(values = c("Urban Center" = "#d95f02", "Urban Forest" = "#1b9e77")) +
+  scale_x_discrete(labels=c("Urban Forest" = "Urban \nForest \nN = 10", "Urban Center" = "Urban \nCenter \nN = 12")) +
+  theme_classic() +
+  scale_y_continuous(limits = c(0, 275), breaks = c(0, 50, 100, 150, 200, 250)) +
+  ylab("Search Distance [m]") + 
+  theme(text = element_text(size = 16)) + 
+  theme(axis.text.x = element_text(colour = "black", size = 16)) + 
+  theme(axis.text.y = element_text(colour = "black", size = 16),
+        axis.title.x = element_blank()) +
+  theme(legend.position = "none") +
+  annotate(geom = "text", x = 1.5, y = 275, label = "***", color = "black", size = 10)
+
+# Let's look at the log-transformed response variable since that is normal
+predictions2 <- summary(emmeans(search2, ~Location),type = "response")
+
+ggplot(sites, aes(x = Location, y = (WalkDist))) + 
+  geom_jitter(color = "grey", width = 0.1) +
+  geom_point(aes(x = Location, y = response, color = Location), size = 2, data = predictions2) + 
+  geom_errorbar(aes(x = Location, 
+                  ymin = response - SE, 
+                  ymax = response + SE,
+                  color = Location), data = predictions2, inherit.aes = FALSE, width = 0.15, size = 1.5) +
+  scale_color_manual(values = c("Urban Center" = "#d95f02", "Urban Forest" = "#1b9e77")) +
+  scale_x_discrete(labels=c("Urban Forest" = "Urban \nForest \nN = 10", "Urban Center" = "Urban \nCenter \nN = 12")) +
+  theme_classic() +
+  scale_y_continuous(limits = c(0, 275), breaks = c(0, 50, 100, 150, 200, 250)) +
+  ylab("Search Distance [m]") + 
+  theme(text = element_text(size = 16)) + 
+  theme(axis.text.x = element_text(colour = "black", size = 16)) + 
+  theme(axis.text.y = element_text(colour = "black", size = 16),
+        axis.title.x = element_blank()) +
+  theme(legend.position = "none") +
+  annotate(geom = "text", x = 1.5, y = 275, label = "***", color = "black", size = 10)
+```
+
+### Search Distance by Predictors
+
+```{r search_predictors_stats}
+# This is one way to look at the overall data, but I think I end up not using this information
+models = list(WalkDist ~ 1,
+              WalkDist ~ log_TotalSub, 
+              WalkDist ~ log_tdr, 
+              WalkDist ~ log_tdh,
+              WalkDist ~ log_TotalSub + log_tdr,
+              WalkDist ~ log_TotalSub + log_tdh,
+              WalkDist ~ log_tdr + log_tdh,
+              WalkDist ~ log_TotalSub + log_tdr + log_tdh)
+fits = lapply(models, glm, data = sites, family = "poisson")
+modnames = sapply(models, function(ff)deparse(ff[[3]]))
+pander(aictab(fits, modname = modnames), caption="Table 1. AICc model selection table for Search Distance to the Focal Web Overall.", split.tables = Inf)
+# The top model keeps all 3 variables and no other model is within 2 Model Likelihood Units
+summary(glm(WalkDist ~ log_TotalSub + log_tdr + log_tdh, data = sites, family = poisson))
+
+global <- glm(WalkDist ~ log_TotalSub + log_tdr + log_tdh, data = sites, family = poisson)
+options(na.action = "na.fail") # Required for dredge to run
+model_dredge <- dredge(global, beta = F, evaluate = T, rank = AICc)
+options(na.action = "na.omit") # set back to default
+top_model_wd_o <- get.models(model_dredge, subset = 1)[[1]]
+out <- summary(top_model_wd_o)
+info <- out[[12]]
+#TotalSub (log_TotalSub)
+exp(info[4, 1])
+exp(info[4, 2])
+#Traffic_Dist_Road (log_tdr)
+exp(info[3, 1])
+exp(info[3, 2])
+#Traffic_Dist_Highway (log_tdh)
+exp(info[2, 1])
+exp(info[2, 2])
+
+with(summary(top_model_wd_o), 1 - deviance/null.deviance) # This gives the R squared value
+#summary(model.avg(model_dredge, subset = delta <= 2))
+#summary(model.avg(model_dredge))
+model.sel(model_dredge) #estimates same signs
+car::vif(get.models(model_dredge, 1)[[1]]) #looking for less than 2
+
+# urban forest
+global <- glm(WalkDist ~ tree100m + log_TotalSub + log_tdh + log_patch + log_tdr, data = sites_forest, family = poisson)
+options(na.action = "na.fail") # Required for dredge to run
+model_dredge <- dredge(global, beta = F, evaluate = T, rank = AICc)
+options(na.action = "na.omit") # set back to default
+top_model_wd_f <- get.models(model_dredge, subset = 1)[[1]]
+out <- summary(top_model_wd_f)
+info <- out[[12]]
+#tree100m
+info[5, 1]
+info[5, 2]
+#TotalSub
+-exp(info[4, 1])
+exp(info[4, 2])
+#Traffic_Dist_Road
+exp(info[3, 1])
+exp(info[3, 2])
+#Traffic_Dist_Highway
+exp(info[2, 1])
+exp(info[2, 2])
+with(summary(top_model_wd_f), 1 - deviance/null.deviance) # This gives the R squared value
+model.sel(model_dredge) #estimates same signs
+#summary(model.avg(model_dredge, subset = delta <= 2))
+car::vif(get.models(model_dredge, 1)[[1]]) #looking for less than 2
+
+# urban center
+global <- glm(WalkDist ~ log_TotalSub + log_tdr + log_tdh + spec_rad + log_patch + road_length_m, data = sites_center, family = poisson)
+options(na.action = "na.fail") # Required for dredge to run
+model_dredge <- dredge(global, beta = F, evaluate = T, rank = AICc)
+options(na.action = "na.omit") # set back to default
+top_model_wd_c <- get.models(model_dredge, subset = 1)[[1]]
+out <- summary(top_model_wd_c)
+info <- out[[12]]
+#TotalSub
+exp(info[5, 1])
+exp(info[5, 2])
+#patch_area_km
+exp(info[2, 1])
+exp(info[2, 2])
+#spec_rad
+info[6, 1]
+info[6, 2]
+#Traffic_Dist_Road
+exp(info[4, 1])
+exp(info[4, 2])
+#Traffic_Dist_Highway
+exp(info[3, 1])
+exp(info[3, 2])
+with(summary(top_model_wd_c), 1 - deviance/null.deviance) # This gives the R squared value
+model.sel(model_dredge) #estimates same signs
+#summary(model.avg(model_dredge, subset = delta <= 2))
+car::vif(get.models(model_dredge, 1)[[1]]) # road and highway disturbance between 2 and 3
+```
+
+*Overall*
+Coefficients:
+             Estimate Std. Error z value Pr(>|z|)    
+(Intercept)   2.45699    0.24451  10.049  < 2e-16 ***
+log_tdh       0.21434    0.04469   4.796 1.62e-06 *** *positive*
+log_tdr       0.13279    0.01775   7.480 7.42e-14 *** *positive*
+log_TotalSub  0.31671    0.03252   9.740  < 2e-16 *** *positive*
+
+R-squared = 0.0821148
+
+*Urban Forest*
+Coefficients:
+              Estimate Std. Error z value Pr(>|z|)    
+(Intercept)  -2.962190   0.608574  -4.867 1.13e-06 ***
+log_tdh       1.354582   0.109952  12.320  < 2e-16 *** *positive*
+log_tdr       0.718623   0.038386  18.721  < 2e-16 *** *positive*
+log_TotalSub -1.010040   0.095179 -10.612  < 2e-16 *** *negative*
+tree100m      0.049914   0.004241  11.770  < 2e-16 *** *positive*
+
+R-squared = 0.5328974
+
+*Urban Center*
+Coefficients:
+              Estimate Std. Error z value Pr(>|z|)    
+(Intercept)  -26.90656    2.78649  -9.656  < 2e-16 ***
+log_patch      1.05254    0.05903  17.832  < 2e-16 *** *positive* 
+log_tdh        0.58001    0.09128   6.354 2.10e-10 *** *positive*
+log_tdr        0.45331    0.04386  10.335  < 2e-16 *** *positive*
+log_TotalSub   0.54581    0.08135   6.709 1.96e-11 *** *positive*
+spec_rad       0.12466    0.01458   8.549  < 2e-16 *** *positive*
+
+R-squared = 0.9399876
+
+```{r search_predictors_overall_graphs, echo = FALSE}
+colorc = "#d95f02" 
+colorf = "#1b9e77"
+coloro = "black"
+
+# Plant Species Richness
+nd <- data.frame(log_TotalSub = seq(0, 3.2, 0.03), 
+                 log_tdr = mean(sites$log_tdr), 
+                 log_tdh = mean(sites$log_tdh))
+predicted.distance <- augment(top_model_wd_o, 
+                              newdata = nd, 
+                              se_fit = TRUE)
+search_plant <- ggplot(sites, aes(x = log_TotalSub, y = log(WalkDist))) + 
+  geom_point(color = "grey", 
+             size = 1) +
+  geom_line(aes(x = log_TotalSub, y = .fitted), 
+            size = 1, 
+            color = coloro, 
+            data = predicted.distance) + 
+  geom_ribbon(aes(x = log_TotalSub, 
+                  ymin = .fitted - 1.96 * .se.fit, 
+                  ymax = .fitted + 1.96 * .se.fit), 
+              fill = coloro, 
+              data = predicted.distance, 
+              inherit.aes = FALSE, 
+              alpha = 0.25) +
+  scale_y_continuous(limits = c(min(log(sites$WalkDist)), max(log(sites$WalkDist)) + 0.1 * diff(range(log(sites$WalkDist))))) +  
+  theme_classic() +
+  xlab("Plant Species Richness [log()]") +
+  ylab("Search Distance [log(m)]") + 
+  theme(text = element_text(size = 10)) + 
+  theme(axis.text.x = element_text(colour = "black", size = 10)) + 
+  theme(axis.text.y = element_text(colour = "black", size = 10)) +
+  theme(axis.text.x = element_blank(), 
+        axis.title.x = element_blank(),
+        axis.text.y = element_blank(),
+        axis.title.y = element_blank()) +
+  annotate(geom = "text", x = min(predicted.distance$log_TotalSub) + diff(range(predicted.distance$log_TotalSub))/2, y = max(log(sites$WalkDist)), label = "***", color = "black", size = 4)
+
+# Road Disturbance
+nd <- data.frame(log_TotalSub = mean(sites$log_TotalSub), 
+                 log_tdr = seq(2.7, 7.3, 0.05), 
+                 log_tdh = mean(sites$log_tdh))
+predicted.distance <- augment(top_model_wd_o, 
+                              newdata = nd, 
+                              se_fit = TRUE)
+search_tdr <- ggplot(sites, aes(x = log_tdr, y = log(WalkDist))) + 
+  geom_point(color = "grey", 
+             size = 1) +
+  geom_line(aes(x = log_tdr, y = .fitted), 
+            size = 1, 
+            color = coloro, 
+            data = predicted.distance) + 
+  geom_ribbon(aes(x = log_tdr, 
+                  ymin = .fitted - 1.96 * .se.fit, 
+                  ymax = .fitted + 1.96 * .se.fit), 
+              fill = coloro, 
+              data = predicted.distance, 
+              inherit.aes = FALSE, 
+              alpha = 0.25) +
+  scale_y_continuous(limits = c(min(log(sites$WalkDist)), max(log(sites$WalkDist)) + 0.1 * diff(range(log(sites$WalkDist))))) +  
+  theme_classic() +
+  xlab("Road Disturbance [log(vehicles/day/m)]") +
+  ylab("Search Distance [log(m)]") + 
+  theme(text = element_text(size = 10)) + 
+  theme(axis.text.x = element_text(colour = "black", size = 10)) + 
+  theme(axis.text.y = element_text(colour = "black", size = 10)) +
+  theme(axis.text.x = element_blank(), 
+        axis.title.x = element_blank(),
+        axis.text.y = element_blank(),
+        axis.title.y = element_blank()) +
+  annotate(geom = "text", x = min((predicted.distance$log_tdr)) + diff(range((predicted.distance$log_tdr)))/2, y = max(log(sites$WalkDist)), label = "***", color = "black", size = 4)
+
+# Highway Disturbance
+nd <- data.frame(log_TotalSub = mean(sites$log_TotalSub), 
+                 log_tdr = mean(sites$log_tdr), 
+                 log_tdh = seq(2.7, 5.5, 0.03))
+predicted.distance <- augment(top_model_wd_o, 
+                              newdata = nd, 
+                              se_fit = TRUE)
+search_tdh <- ggplot(sites, aes(x = log_tdh, y = log(WalkDist))) + 
+  geom_point(color = "grey", 
+             size = 1) +
+  geom_line(aes(x = log_tdh, y = .fitted), 
+            size = 1, 
+            color = coloro, 
+            data = predicted.distance) + 
+  geom_ribbon(aes(x = log_tdh, 
+                  ymin = .fitted - 1.96 * .se.fit, 
+                  ymax = .fitted + 1.96 * .se.fit), 
+              fill = coloro, 
+              data = predicted.distance, 
+              inherit.aes = FALSE, 
+              alpha = 0.25) +
+  scale_y_continuous(limits = c(min(log(sites$WalkDist)), max(log(sites$WalkDist)) + 0.1 * diff(range(log(sites$WalkDist))))) +  
+  theme_classic() +
+  xlab("Highway Disturbance [log(vehicles/day/m)]") +
+  ylab("Search Distance [log(m)]") + 
+  theme(text = element_text(size = 10)) + 
+  theme(axis.text.x = element_text(colour = "black", size = 10)) + 
+  theme(axis.text.y = element_text(colour = "black", size = 10)) +
+  theme(axis.text.x = element_blank(), 
+        axis.title.x = element_blank(),
+        axis.text.y = element_blank(),
+        axis.title.y = element_blank()) +
+  annotate(geom = "text", x = min((predicted.distance$log_tdh)) + diff(range((predicted.distance$log_tdh)))/2, y = max(log(sites$WalkDist)), label = "***", color = "black", size = 4)
+
+search_plant
+search_tdr
+search_tdh
+```
+
+```{r search_predictors_forest_graphs, echo = FALSE}
+colorc = "#d95f02" 
+colorf = "#1b9e77"
+coloro = "black"
+
+# Tree
+nd <- data.frame(tree100m = seq(31, 66, 0.3),
+                 log_TotalSub = mean(sites_forest$log_TotalSub), 
+                 log_tdr = mean(sites_forest$log_tdr), 
+                 log_tdh = mean(sites_forest$log_tdh))
+predicted.distance <- augment(top_model_wd_f, 
+                              newdata = nd, 
+                              se_fit = TRUE)
+search_forest_tree <- ggplot(sites_forest, aes(x = log(tree100m), y = log(WalkDist))) + 
+  geom_point(color = "grey", 
+             size = 1) +
+  geom_line(aes(x = log(tree100m), y = .fitted), 
+            size = 1, 
+            color = colorf, 
+            data = predicted.distance) + 
+  geom_ribbon(aes(x = log(tree100m), 
+                  ymin = .fitted - 1.96 * .se.fit, 
+                  ymax = .fitted + 1.96 * .se.fit), 
+              fill = colorf, 
+              data = predicted.distance, 
+              inherit.aes = FALSE, 
+              alpha = 0.25) +
+  scale_y_continuous(limits = c(min(log(sites_forest$WalkDist)), max(log(sites_forest$WalkDist)) + 0.1 * diff(range(log(sites_forest$WalkDist))))) +  
+  theme_classic() +
+  xlab("Percent Tree Cover [log(%)]") +
+  ylab("Search Distance [log(m)]") + 
+  theme(text = element_text(size = 10)) + 
+  theme(axis.text.x = element_text(colour = "black", size = 10)) + 
+  theme(axis.text.y = element_text(colour = "black", size = 10)) +
+  theme(axis.text.x = element_blank(), 
+        axis.title.x = element_blank(),
+        axis.text.y = element_blank(),
+        axis.title.y = element_blank()) +
+  annotate(geom = "text", x = min(log(predicted.distance$tree100m)) + diff(range(log(predicted.distance$tree100m)))/2, y = max(log(sites_forest$WalkDist)), label = "***", color = "black", size = 4)
+
+# TotalSub
+nd <- data.frame(tree100m = mean(sites_forest$tree100m),
+                 log_TotalSub = seq(1.94, 3.14, 0.01), 
+                 log_tdr = mean(sites_forest$log_tdr), 
+                 log_tdh = mean(sites_forest$log_tdh))
+predicted.distance <- augment(top_model_wd_f, 
+                              newdata = nd, 
+                              se_fit = TRUE)
+search_forest_plant <- ggplot(sites_forest, aes(x = log_TotalSub, y = log(WalkDist))) + 
+  geom_point(color = "grey", 
+             size = 1) +
+  geom_line(aes(x = log_TotalSub, y = .fitted), 
+            size = 1, 
+            color = colorf, 
+            data = predicted.distance) + 
+  geom_ribbon(aes(x = log_TotalSub, 
+                  ymin = .fitted - 1.96 * .se.fit, 
+                  ymax = .fitted + 1.96 * .se.fit), 
+              fill = colorf, 
+              data = predicted.distance, 
+              inherit.aes = FALSE, 
+              alpha = 0.25) +
+  scale_y_continuous(limits = c(min(log(sites_forest$WalkDist)), max(log(sites_forest$WalkDist)) + 0.1 * diff(range(log(sites_forest$WalkDist))))) +  
+  theme_classic() +
+  xlab("Plant Species Richness [log()]") +
+  ylab("Search Distance [log(m)]") + 
+  theme(text = element_text(size = 10)) + 
+  theme(axis.text.x = element_text(colour = "black", size = 10)) + 
+  theme(axis.text.y = element_text(colour = "black", size = 10)) +
+  theme(axis.text.x = element_blank(), 
+        axis.title.x = element_blank(),
+        axis.text.y = element_blank(),
+        axis.title.y = element_blank()) +
+  annotate(geom = "text", x = min((predicted.distance$log_TotalSub)) + diff(range((predicted.distance$log_TotalSub)))/2, y = max(log(sites_forest$WalkDist)), label = "***", color = "black", size = 4)
+
+# Road Disturbance
+nd <- data.frame(tree100m = mean(sites_forest$tree100m),
+                 log_TotalSub = mean(sites_forest$log_TotalSub), 
+                 log_tdr = seq(2.73, 6.22, 0.03), 
+                 log_tdh = mean(sites_forest$log_tdh))
+predicted.distance <- augment(top_model_wd_f, 
+                              newdata = nd, 
+                              se_fit = TRUE)
+search_forest_tdr <- ggplot(sites_forest, aes(x = log_tdr, y = log(WalkDist))) + 
+  geom_point(color = "grey", 
+             size = 1) +
+  geom_line(aes(x = log_tdr, y = .fitted), 
+            size = 1, 
+            color = colorf, 
+            data = predicted.distance) + 
+  geom_ribbon(aes(x = log_tdr, 
+                  ymin = .fitted - 1.96 * .se.fit, 
+                  ymax = .fitted + 1.96 * .se.fit), 
+              fill = colorf, 
+              data = predicted.distance, 
+              inherit.aes = FALSE, 
+              alpha = 0.25) +
+  scale_y_continuous(limits = c(min(log(sites_forest$WalkDist)), max(log(sites_forest$WalkDist)) + 0.15 * diff(range(log(sites_forest$WalkDist))))) +  
+  theme_classic() +
+  xlab("Road Disturbance [log(vehicles/day/m)]") +
+  ylab("Search Distance [log(m)]") + 
+  theme(text = element_text(size = 10)) + 
+  theme(axis.text.x = element_text(colour = "black", size = 10)) + 
+  theme(axis.text.y = element_text(colour = "black", size = 10)) +
+  theme(axis.text.x = element_blank(), 
+        axis.title.x = element_blank(),
+        axis.text.y = element_blank(),
+        axis.title.y = element_blank()) +
+  annotate(geom = "text", x = min((predicted.distance$log_tdr)) + diff(range((predicted.distance$log_tdr)))/2, y = max(log(sites_forest$WalkDist)), label = "***", color = "black", size = 4)
+
+# Highway Disturbance
+nd <- data.frame(tree100m = mean(sites_forest$tree100m),
+                 log_TotalSub = mean(sites_forest$log_TotalSub), 
+                 log_tdr = mean(sites_forest$log_tdr), 
+                 log_tdh = seq(2.76, 3.89, 0.01))
+predicted.distance <- augment(top_model_wd_f, 
+                              newdata = nd, 
+                              se_fit = TRUE)
+search_forest_tdh <- ggplot(sites_forest, aes(x = log_tdh, y = log(WalkDist))) + 
+  geom_point(color = "grey", 
+             size = 1) +
+  geom_line(aes(x = log_tdh, y = .fitted), 
+            size = 1, 
+            color = colorf, 
+            data = predicted.distance) + 
+  geom_ribbon(aes(x = log_tdh, 
+                  ymin = .fitted - 1.96 * .se.fit, 
+                  ymax = .fitted + 1.96 * .se.fit), 
+              fill = colorf, 
+              data = predicted.distance, 
+              inherit.aes = FALSE, 
+              alpha = 0.25) +
+  scale_y_continuous(limits = c(min(log(sites_forest$WalkDist)), max(log(sites_forest$WalkDist)) + 0.1 * diff(range(log(sites_forest$WalkDist))))) +  
+  theme_classic() +
+  xlab("Highway Disturbance [log(vehicles/day/m)]") +
+  ylab("Search Distance [log(m)]") + 
+  theme(text = element_text(size = 10)) + 
+  theme(axis.text.x = element_text(colour = "black", size = 10)) + 
+  theme(axis.text.y = element_text(colour = "black", size = 10)) +
+  theme(axis.text.x = element_blank(), 
+        axis.title.x = element_blank(),
+        axis.text.y = element_blank(),
+        axis.title.y = element_blank()) +
+  annotate(geom = "text", x = min((predicted.distance$log_tdh)) + diff(range((predicted.distance$log_tdh)))/2, y = max(log(sites_forest$WalkDist)), label = "***", color = "black", size = 4)
+
+search_forest_tree
+search_forest_plant
+search_forest_tdr
+search_forest_tdh
+```
+
+```{r search_predictors_center_graphs, echo = FALSE}
+colorc = "#d95f02" 
+colorf = "#1b9e77"
+coloro = "black"
+
+# Plant Species Richness
+nd <- data.frame(log_TotalSub = seq(0, 1.8, 0.02), 
+                 log_patch = mean(sites_center$log_patch),
+                 spec_rad = mean(sites_center$spec_rad),
+                 log_tdr = mean(sites_center$log_tdr), 
+                 log_tdh = mean(sites_center$log_tdh))
+predicted.distance <- augment(top_model_wd_c, 
+                              newdata = nd, 
+                              se_fit = TRUE)
+search_center_plant <- ggplot(sites_center, aes(x = log_TotalSub, y = log(WalkDist))) + 
+  geom_point(color = "grey", 
+             size = 1) +
+  geom_line(aes(x = log_TotalSub, y = .fitted), 
+            size = 1, 
+            color = colorc, 
+            data = predicted.distance) + 
+  geom_ribbon(aes(x = log_TotalSub, 
+                  ymin = .fitted - 1.96 * .se.fit, 
+                  ymax = .fitted + 1.96 * .se.fit), 
+              fill = colorc, 
+              data = predicted.distance, 
+              inherit.aes = FALSE, 
+              alpha = 0.25) +
+  scale_y_continuous(limits = c(min(log(sites_center$WalkDist)), max(log(sites_center$WalkDist)) + 0.1 * diff(range(log(sites_center$WalkDist))))) +  
+  theme_classic() +
+  xlab("Plant Species Richness [log()]") +
+  ylab("Search Distance [log(m)]") + 
+  theme(text = element_text(size = 10)) + 
+  theme(axis.text.x = element_text(colour = "black", size = 10)) + 
+  theme(axis.text.y = element_text(colour = "black", size = 10)) +
+  theme(axis.text.x = element_blank(), 
+        axis.title.x = element_blank(),
+        axis.text.y = element_blank(),
+        axis.title.y = element_blank()) +
+  annotate(geom = "text", x = min((predicted.distance$log_TotalSub)) + diff(range((predicted.distance$log_TotalSub)))/2, y = max(log(sites_center$WalkDist)), label = "***", color = "black", size = 4)
+
+# Patch Area
+nd <- data.frame(log_TotalSub = mean(sites_center$log_TotalSub), 
+                 log_patch = seq(4.34, 7.52, 0.03),
+                 spec_rad = mean(sites_center$spec_rad),
+                 log_tdr = mean(sites_center$log_tdr), 
+                 log_tdh = mean(sites_center$log_tdh))
+predicted.distance <- augment(top_model_wd_c, 
+                              newdata = nd, 
+                              se_fit = TRUE)
+search_center_patch <- ggplot(sites_center, aes(x = log_patch, y = log(WalkDist))) + 
+  geom_point(color = "grey", 
+             size = 1) +
+  geom_line(aes(x = log_patch, y = .fitted), 
+            size = 1, 
+            color = colorc, 
+            data = predicted.distance) + 
+  geom_ribbon(aes(x = log_patch, 
+                  ymin = .fitted - 1.96 * .se.fit, 
+                  ymax = .fitted + 1.96 * .se.fit), 
+              fill = colorc, 
+              data = predicted.distance, 
+              inherit.aes = FALSE, 
+              alpha = 0.25) +
+  scale_y_continuous(limits = c(min(log(sites_center$WalkDist)) - 0.75, max(log(sites_center$WalkDist)) + 0.15 * diff(range(log(sites_center$WalkDist))))) +  
+  theme_classic() +
+  xlab("Patch Area [log(mm²)]") +
+  ylab("Search Distance [log(m)]") + 
+  theme(text = element_text(size = 10)) + 
+  theme(axis.text.x = element_text(colour = "black", size = 10)) + 
+  theme(axis.text.y = element_text(colour = "black", size = 10)) +
+  theme(axis.text.x = element_blank(), 
+        axis.title.x = element_blank(),
+        axis.text.y = element_blank(),
+        axis.title.y = element_blank()) +
+  annotate(geom = "text", x = min((predicted.distance$log_patch)) + diff(range((predicted.distance$log_patch)))/2, y = max(log(sites_center$WalkDist)), label = "***", color = "black", size = 4)
+
+# Spectral Radiance
+nd <- data.frame(log_TotalSub = mean(sites_center$log_TotalSub), 
+                 log_patch = mean(sites_center$log_patch),
+                 spec_rad = seq(144.36, 162.87, 0.1),
+                 log_tdr = mean(sites_center$log_tdr), 
+                 log_tdh = mean(sites_center$log_tdh))
+predicted.distance <- augment(top_model_wd_c, 
+                              newdata = nd, 
+                              se_fit = TRUE)
+search_center_spec <- ggplot(sites_center, aes(x = log(spec_rad), y = log(WalkDist))) + 
+  geom_point(color = "grey", 
+             size = 1) +
+  geom_line(aes(x = log(spec_rad), y = .fitted), 
+            size = 1, 
+            color = colorc, 
+            data = predicted.distance) + 
+  geom_ribbon(aes(x = log(spec_rad), 
+                  ymin = .fitted - 1.96 * .se.fit, 
+                  ymax = .fitted + 1.96 * .se.fit), 
+              fill = colorc, 
+              data = predicted.distance, 
+              inherit.aes = FALSE, 
+              alpha = 0.25) +
+  scale_y_continuous(limits = c(min(log(sites_center$WalkDist)), max(log(sites_center$WalkDist)) + 0.1 * diff(range(log(sites_center$WalkDist))))) +  
+  theme_classic() +
+  xlab("Spectral Radiance [log(Watts/(m² * sr * µm))]") +
+  ylab("Search Distance [log(m)]") + 
+  theme(text = element_text(size = 10)) + 
+  theme(axis.text.x = element_text(colour = "black", size = 10)) + 
+  theme(axis.text.y = element_text(colour = "black", size = 10)) +
+  theme(axis.text.x = element_blank(), 
+        axis.title.x = element_blank(),
+        axis.text.y = element_blank(),
+        axis.title.y = element_blank()) +
+  annotate(geom = "text", x = min(log(predicted.distance$spec_rad)) + diff(range(log(predicted.distance$spec_rad)))/2, y = max(log(sites_center$WalkDist)), label = "***", color = "black", size = 4)
+
+# Road Disturbance
+nd <- data.frame(log_TotalSub = mean(sites_center$log_TotalSub), 
+                 log_patch = mean(sites_center$log_patch),
+                 spec_rad = mean(sites_center$spec_rad),
+                 log_tdr = seq(3.00, 7.22, 0.04), 
+                 log_tdh = mean(sites_center$log_tdh))
+predicted.distance <- augment(top_model_wd_c, 
+                              newdata = nd, 
+                              se_fit = TRUE)
+ggplot(sites_center, aes(x = log_tdr, y = log(WalkDist))) + 
+  geom_point(color = "grey", 
+             size = 1) +
+  geom_line(aes(x = log_tdr, y = .fitted), 
+            size = 1, 
+            color = colorc, 
+            data = predicted.distance) + 
+  geom_ribbon(aes(x = log_tdr, 
+                  ymin = .fitted - 1.96 * .se.fit, 
+                  ymax = .fitted + 1.96 * .se.fit), 
+              fill = colorc, 
+              data = predicted.distance, 
+              inherit.aes = FALSE, 
+              alpha = 0.25) +
+  scale_y_continuous(limits = c(min(log(sites_center$WalkDist)), max(log(sites_center$WalkDist)) + 0.1 * diff(range(log(sites_center$WalkDist))))) +  
+  theme_classic() +
+  xlab("Road Disturbance [log(vehicles/day/m)]") +
+  ylab("Search Distance [log(m)]") + 
+  theme(text = element_text(size = 10)) + 
+  theme(axis.text.x = element_text(colour = "black", size = 10)) + 
+  theme(axis.text.y = element_text(colour = "black", size = 10)) +
+  theme(axis.text.x = element_blank(), 
+        axis.title.x = element_blank(),
+        axis.text.y = element_blank(),
+        axis.title.y = element_blank()) +
+  annotate(geom = "text", x = min((predicted.distance$log_tdr)) + diff(range((predicted.distance$log_tdr)))/2, y = max(log(sites_center$WalkDist)), label = "***", color = "black", size = 4)
+
+# Highway Disturbance
+nd <- data.frame(log_TotalSub = mean(sites_center$log_TotalSub), 
+                 log_patch = mean(sites_center$log_patch),
+                 spec_rad = mean(sites_center$spec_rad),
+                 log_tdr = mean(sites_center$log_tdr), 
+                 log_tdh = seq(3.32, 5.42, 0.02))
+predicted.distance <- augment(top_model_wd_c, 
+                              newdata = nd, 
+                              se_fit = TRUE)
+search_center_tdh <- ggplot(sites_center, aes(x = log_tdh, y = log(WalkDist))) + 
+  geom_point(color = "grey", 
+             size = 1) +
+  geom_line(aes(x = log_tdh, y = .fitted), 
+            size = 1, 
+            color = colorc, 
+            data = predicted.distance) + 
+  geom_ribbon(aes(x = log_tdh, 
+                  ymin = .fitted - 1.96 * .se.fit, 
+                  ymax = .fitted + 1.96 * .se.fit), 
+              fill = colorc, 
+              data = predicted.distance, 
+              inherit.aes = FALSE, 
+              alpha = 0.25) +
+  scale_y_continuous(limits = c(min(log(sites_center$WalkDist)), max(log(sites_center$WalkDist)) + 0.1 * diff(range(log(sites_center$WalkDist))))) +  
+  theme_classic() +
+  xlab("Highway Disturbance [log(vehicles/day/m)]") +
+  ylab("Search Distance [log(m)]") + 
+  theme(text = element_text(size = 10)) + 
+  theme(axis.text.x = element_text(colour = "black", size = 10)) + 
+  theme(axis.text.y = element_text(colour = "black", size = 10)) +
+  theme(axis.text.x = element_blank(), 
+        axis.title.x = element_blank(),
+        axis.text.y = element_blank(),
+        axis.title.y = element_blank()) +
+  annotate(geom = "text", x = min((predicted.distance$log_tdh)) + diff(range((predicted.distance$log_tdh)))/2, y = max(log(sites_center$WalkDist)), label = "***", color = "black", size = 4)
+
+search_center_plant
+search_center_patch
+search_center_spec
+search_center_tdr
+search_center_tdh
+```
+
+### Search Distance by Land
+
+```{r search_land_stats}
+search_land <- glm(WalkDist ~ Land, data = sites, family = poisson)
+summary(search_land)
+anova(search_land, test = "Chisq")
+comp <- glht(search_land, linfct = mcp(Land = "Tukey"))
+summary(comp)
+```
+
+```{r search_land_graph}
+sites <- sites %>% 
+  mutate(Land = fct_relevel(Land, "Deciduous Forest", 
+                            "Woody Wetlands", 
+                            "Urban, High", 
+                            "Urban, Medium", 
+                            "Urban, Low"))
+predictions <- summary(emmeans(search_land, ~Land),type = "response")
+
+ggplot(sites, aes(x = Land, y = WalkDist)) + 
+  geom_jitter(color = "grey", width = 0.1, size = 0.5) +
+  geom_point(aes(x = Land, y = rate, color = Land), size = 1, data = predictions) + 
+  geom_errorbar(aes(x = Land, 
+                  ymin = rate - SE, 
+                  ymax = rate + SE, color = Land), data = predictions, inherit.aes = FALSE, width = 0.25, size = 1) +
+  theme_classic() +
+  scale_color_manual(values = c("Deciduous Forest" = "#1b9e77", "Woody Wetlands" = "#1b9e77", "Urban, High" = "#d95f02", "Urban, Medium" = "#d95f02", "Urban, Low" = "#d95f02")) +
+  xlab("Land Cover Class") +
+  ylab("Search Distance [m]") + 
+  theme(text = element_text(size = 10)) + 
+  theme(axis.text.x=element_text(colour="black", size=10)) + 
+  theme(axis.text.y=element_text(colour="black", size=10)) +
+  theme(legend.position = "none") +
+  theme(axis.text.x = element_text(angle = 90, vjust = 1, hjust=1)) +
+  annotate(geom="text", x=1, y=max(sites$WalkDist), label="A", color="black", size = 3) +
+  annotate(geom="text", x=2, y=max(sites$WalkDist), label="B", color="black", size = 3) +
+  annotate(geom="text", x=3, y=max(sites$WalkDist), label="C", color="black", size = 3) +
+  annotate(geom="text", x=4, y=max(sites$WalkDist), label="A", color="black", size = 3) +
+  annotate(geom="text", x=5, y=max(sites$WalkDist), label="A", color="black", size = 3)
+```
+
+## Response Variable: Number of Webs
+
+### Number of Webs by Location
+
+### Number of Webs by Predictors
+
+### Number of Webs by Land

### 2022-11-23 data_analysis.Rmd
Almost finished adding the analysis for each variable; convergence issues occurring in web height by predictor analysis

@@
 library(MuMIn) # to run the dredge function
+library(lme4) # to run the glmer function for the web distance (random effects)
+library(broom.mixed) # for augment of the mixed effect models (web distance) to look at assumptions
 ```
@@
 We will use "webs" for web height and nearest neighbor analyses.
+The "web_dist" dataset looks at the distance from the focal web to the nearest and second nearest neighbors.
 
@@
   filter(Web == "W001")
+
+web_dist <- webs %>% 
+  filter(RetreatDist != 0,
+         RetreatDist < 1000,
+         Web == "W002" | Web == "W003") %>% 
+  mutate(Neighbor = ifelse(Web == "W002", "1", "2"))
 ```
@@
   filter(Location == "Urban Forest")
+
+web_dist_center <- web_dist %>% 
+  filter(Location == "Urban Center")
+
+web_dist_forest <- web_dist %>% 
+  filter(Location == "Urban Forest")
 ```
@@
 corr <- sites %>% 
-  select(tree100m, imperv100m, TotalSub, 
+  dplyr::select(tree100m, imperv100m, TotalSub, 
          Traffic_Dist_Road, Traffic_Dist_Highway, 
@@
   filter(Location == "Urban Forest") %>% 
-  select(tree100m, imperv100m, TotalSub, 
+  dplyr::select(tree100m, imperv100m, TotalSub, 
          Traffic_Dist_Road, Traffic_Dist_Highway, 
@@
   filter(Location == "Urban Center") %>% 
-  select(tree100m, imperv100m, TotalSub, Traffic_Dist_Road, Traffic_Dist_Highway, spec_rad, light_rad, patch_area_km, road_length_m)
+  dplyr::select(tree100m, imperv100m, TotalSub, Traffic_Dist_Road, Traffic_Dist_Highway, spec_rad, light_rad, patch_area_km, road_length_m)
 # Trail length is removed because we could not measure trail length on campus
@@
 
+For this variable, I've been going back and forth on whether I should log-transform the search distance (because it can be ran Guassian), or whether to use a log-link function (Poisson Distribution).
+The poisson glm more closely matches the mean, but the log-transformation is better at capturing the variance.
+Each step of the way, I have performed each test to try and gauge a best route forward.
+The poisson glm suggests a significant difference while the log-transformed shows no difference.
+
 ```{r search_location_stats}
@@
 
-ggarrange(resid_search, qq_search, 
-          labels = c("A", "B"),
-          ncol = 2, nrow = 1)
+scaleloc_search <- ggplot(test_search, aes(x = .fitted, y = sqrt(abs(.std.resid)))) + 
+  geom_point() + 
+  geom_smooth() + 
+  geom_hline(yintercept = 0.83) +
+  xlab("Fitted Values") +
+  ylab("Sqrt Standardized \nResiduals") +
+  theme_classic() +
+  theme(text = element_text(size = 14, color = "black")) +
+  theme(axis.text.x=element_text(color="black", size=14)) + 
+  theme(axis.text.y=element_text(color="black", size=14))
+
+lev_search <- ggplot(test_search, aes(.hat, .std.resid)) +
+ geom_vline(colour = "black", xintercept = 0) +
+  geom_hline(colour = "black", yintercept = 0) +
+  geom_point(aes(size = .cooksd)) + geom_smooth(se = FALSE) +
+  xlab("Theoretical Quantiles") +
+  ylab("Sample Quantiles") +
+  labs(size = "Cook's \nDistance") +
+  theme_classic() +
+  theme(text = element_text(size = 14, color = "black")) +
+  theme(axis.text.x=element_text(color="black", size=14)) + 
+  theme(axis.text.y=element_text(color="black", size=14))
+
+ggarrange(resid_search, qq_search, scaleloc_search, lev_search, 
+          labels = c("A", "B", "C", "D"),
+          ncol = 2, nrow = 2)
 
@@
 
-ggarrange(resid_search2, qq_search2, 
-          labels = c("A", "B"),
-          ncol = 2, nrow = 1)
+scaleloc_search2 <- ggplot(test_search2, aes(x = .fitted, y = sqrt(abs(.std.resid)))) + 
+  geom_point() + 
+  geom_smooth() + 
+  geom_hline(yintercept = 0.83) +
+  xlab("Fitted Values") +
+  ylab("Sqrt Standardized \nResiduals") +
+  theme_classic() +
+  theme(text = element_text(size = 14, color = "black")) +
+  theme(axis.text.x=element_text(color="black", size=14)) + 
+  theme(axis.text.y=element_text(color="black", size=14))
+
+lev_search2 <- ggplot(test_search2, aes(.hat, .std.resid)) +
+ geom_vline(colour = "black", xintercept = 0) +
+  geom_hline(colour = "black", yintercept = 0) +
+  geom_point(aes(size = .cooksd)) + geom_smooth(se = FALSE) +
+  xlab("Theoretical Quantiles") +
+  ylab("Sample Quantiles") +
+  labs(size = "Cook's \nDistance") +
+  theme_classic() +
+  theme(text = element_text(size = 14, color = "black")) +
+  theme(axis.text.x=element_text(color="black", size=14)) + 
+  theme(axis.text.y=element_text(color="black", size=14))
+
+ggarrange(resid_search2, qq_search2, scaleloc_search2, lev_search2, 
+          labels = c("A", "B", "C", "D"),
+          ncol = 2, nrow = 2)
 ```
@@
 ```{r search_location_graph, echo = FALSE}
+# raw data
+raw <- sites %>% 
+  group_by(Location) %>% 
+  summarise(mean = mean(WalkDist),
+            se = plotrix::std.error(WalkDist))
+
+raw_plot <- ggplot(sites, aes(x = Location, y = WalkDist)) + 
+  geom_jitter(color = "grey", width = 0.1) +
+  geom_point(aes(x = Location, y = mean, color = Location), size = 2, data = raw) +
+  geom_errorbar(aes(x= Location, 
+                    ymin = mean - se, 
+                    ymax = mean + se, 
+                    color = Location), data = raw, inherit.aes = FALSE, width = 0.15, size = 1.5) +
+    scale_color_manual(values = c("Urban Center" = "#d95f02", "Urban Forest" = "#1b9e77")) +
+    scale_x_discrete(labels=c("Urban Forest" = "Urban \nForest \nN = 10", "Urban Center" = "Urban \nCenter \nN = 12")) +
+    theme_classic() +
+    scale_y_continuous(limits = c(0, 275), breaks = c(0, 50, 100, 150, 200, 250)) +
+    ylab("Search Distance [m]") + 
+    theme(text = element_text(size = 16)) + 
+    theme(axis.text.x = element_text(colour = "black", size = 16)) + 
+    theme(axis.text.y = element_text(colour = "black", size = 16),
+        axis.title.x = element_blank()) +
+    theme(legend.position = "none") +
+    ggtitle("Raw Data")
+
 # Non-transformed, poisson distribution
-predictions <- summary(emmeans(search, ~Location),type = "response")
-
-ggplot(sites, aes(x = Location, y = WalkDist)) + 
+nd <- data.frame(Location = factor(levels(sites$Location)))
+predictions <- augment(search, newdata = nd, se_fit = TRUE, type.predict = "response")
+predictions <- predictions %>% 
+  rename("rate" = ".fitted", "SE" = ".se.fit")
+#predictions2 <- summary(emmeans(search, ~Location),type = "response")
+
+poisson_plot <- ggplot(sites, aes(x = Location, y = WalkDist)) + 
   geom_jitter(color = "grey", width = 0.1) +
@@
   theme(legend.position = "none") +
-  annotate(geom = "text", x = 1.5, y = 275, label = "***", color = "black", size = 10)
+  annotate(geom = "text", x = 1.5, y = 275, label = "***", color = "black", size = 10) +
+  ggtitle("Poisson Distribution")
 
 # Let's look at the log-transformed response variable since that is normal
-predictions2 <- summary(emmeans(search2, ~Location),type = "response")
-
-ggplot(sites, aes(x = Location, y = (WalkDist))) + 
+nd <- data.frame(Location = factor(levels(sites$Location)))
+predictions2 <- augment(search2, newdata = nd, se_fit = TRUE, type.predict = "response")
+predictions2 <- predictions2 %>% 
+  rename("response" = ".fitted", "SE" = ".se.fit")
+#predictions2 <- summary(emmeans(search2, ~Location),type = "response")
+
+log_plot <- ggplot(sites, aes(x = Location, y = (WalkDist))) + 
   geom_jitter(color = "grey", width = 0.1) +
-  geom_point(aes(x = Location, y = response, color = Location), size = 2, data = predictions2) + 
+  geom_point(aes(x = Location, y = exp(response), color = Location), size = 2, data = predictions2) + 
   geom_errorbar(aes(x = Location, 
-                  ymin = response - SE, 
-                  ymax = response + SE,
+                  ymin = exp(response - SE), 
+                  ymax = exp(response + SE),
                   color = Location), data = predictions2, inherit.aes = FALSE, width = 0.15, size = 1.5) +
@@
   theme(legend.position = "none") +
-  annotate(geom = "text", x = 1.5, y = 275, label = "***", color = "black", size = 10)
+  annotate(geom = "text", x = 1.5, y = 275, label = "", color = "black", size = 10) +
+  ggtitle("Log-Transformed")
+
+ggarrange(raw_plot, poisson_plot, log_plot, nrow = 1)
 ```
@@
 options(na.action = "na.omit") # set back to default
-top_model_wd_o <- get.models(model_dredge, subset = 1)[[1]]
-out <- summary(top_model_wd_o)
+top_model_sd_o <- get.models(model_dredge, subset = 1)[[1]]
+out <- summary(top_model_sd_o)
+out
 info <- out[[12]]
@@
 
-with(summary(top_model_wd_o), 1 - deviance/null.deviance) # This gives the R squared value
+with(summary(top_model_sd_o), 1 - deviance/null.deviance) # This gives the R squared value
 #summary(model.avg(model_dredge, subset = delta <= 2))
@@
 options(na.action = "na.omit") # set back to default
-top_model_wd_f <- get.models(model_dredge, subset = 1)[[1]]
-out <- summary(top_model_wd_f)
+top_model_sd_f <- get.models(model_dredge, subset = 1)[[1]]
+out <- summary(top_model_sd_f)
+out
 info <- out[[12]]
@@
 exp(info[2, 2])
-with(summary(top_model_wd_f), 1 - deviance/null.deviance) # This gives the R squared value
+with(summary(top_model_sd_f), 1 - deviance/null.deviance) # This gives the R squared value
 model.sel(model_dredge) #estimates same signs
@@
 options(na.action = "na.omit") # set back to default
-top_model_wd_c <- get.models(model_dredge, subset = 1)[[1]]
-out <- summary(top_model_wd_c)
+top_model_sd_c <- get.models(model_dredge, subset = 1)[[1]]
+out <- summary(top_model_sd_c)
+out
 info <- out[[12]]
@@
 exp(info[3, 2])
-with(summary(top_model_wd_c), 1 - deviance/null.deviance) # This gives the R squared value
+with(summary(top_model_sd_c), 1 - deviance/null.deviance) # This gives the R squared value
 model.sel(model_dredge) #estimates same signs
@@
                  log_tdh = mean(sites$log_tdh))
-predicted.distance <- augment(top_model_wd_o, 
+predicted.distance <- augment(top_model_sd_o, 
                               newdata = nd, 
@@
                  log_tdh = seq(2.7, 5.5, 0.03))
-predicted.distance <- augment(top_model_wd_o, 
+predicted.distance <- augment(top_model_sd_o, 
                               newdata = nd, 
@@
                  log_tdh = mean(sites_forest$log_tdh))
-predicted.distance <- augment(top_model_wd_f, 
+predicted.distance <- augment(top_model_sd_f, 
                               newdata = nd, 
                               se_fit = TRUE)
-search_forest_tree <- ggplot(sites_forest, aes(x = log(tree100m), y = log(WalkDist))) + 
+search_forest_tree <- ggplot(sites_forest, aes(x = (tree100m), y = log(WalkDist))) + 
   geom_point(color = "grey", 
              size = 1) +
-  geom_line(aes(x = log(tree100m), y = .fitted), 
+  geom_line(aes(x = (tree100m), y = .fitted), 
             size = 1, 
@@
             data = predicted.distance) + 
-  geom_ribbon(aes(x = log(tree100m), 
+  geom_ribbon(aes(x = (tree100m), 
                   ymin = .fitted - 1.96 * .se.fit, 
@@
   theme_classic() +
-  xlab("Percent Tree Cover [log(%)]") +
+  xlab("Percent Tree Cover [%]") +
   ylab("Search Distance [log(m)]") + 
@@
         axis.title.y = element_blank()) +
-  annotate(geom = "text", x = min(log(predicted.distance$tree100m)) + diff(range(log(predicted.distance$tree100m)))/2, y = max(log(sites_forest$WalkDist)), label = "***", color = "black", size = 4)
+  annotate(geom = "text", x = min((predicted.distance$tree100m)) + diff(range((predicted.distance$tree100m)))/2, y = max(log(sites_forest$WalkDist)), label = "***", color = "black", size = 4)
 
@@
                  log_tdh = mean(sites_forest$log_tdh))
-predicted.distance <- augment(top_model_wd_f, 
+predicted.distance <- augment(top_model_sd_f, 
                               newdata = nd, 
@@
                  log_tdh = seq(2.76, 3.89, 0.01))
-predicted.distance <- augment(top_model_wd_f, 
+predicted.distance <- augment(top_model_sd_f, 
                               newdata = nd, 
@@
                  log_tdh = mean(sites_center$log_tdh))
-predicted.distance <- augment(top_model_wd_c, 
+predicted.distance <- augment(top_model_sd_c, 
                               newdata = nd, 
@@
                  log_tdh = mean(sites_center$log_tdh))
-predicted.distance <- augment(top_model_wd_c, 
+predicted.distance <- augment(top_model_sd_c, 
                               newdata = nd, 
                               se_fit = TRUE)
-search_center_spec <- ggplot(sites_center, aes(x = log(spec_rad), y = log(WalkDist))) + 
+search_center_spec <- ggplot(sites_center, aes(x = (spec_rad), y = log(WalkDist))) + 
   geom_point(color = "grey", 
              size = 1) +
-  geom_line(aes(x = log(spec_rad), y = .fitted), 
+  geom_line(aes(x = (spec_rad), y = .fitted), 
             size = 1, 
@@
             data = predicted.distance) + 
-  geom_ribbon(aes(x = log(spec_rad), 
+  geom_ribbon(aes(x = (spec_rad), 
                   ymin = .fitted - 1.96 * .se.fit, 
@@
   theme_classic() +
-  xlab("Spectral Radiance [log(Watts/(m² * sr * µm))]") +
+  xlab("Spectral Radiance [Watts/(m² * sr * µm)]") +
   ylab("Search Distance [log(m)]") + 
@@
         axis.title.y = element_blank()) +
-  annotate(geom = "text", x = min(log(predicted.distance$spec_rad)) + diff(range(log(predicted.distance$spec_rad)))/2, y = max(log(sites_center$WalkDist)), label = "***", color = "black", size = 4)
+  annotate(geom = "text", x = min((predicted.distance$spec_rad)) + diff(range((predicted.distance$spec_rad)))/2, y = max(log(sites_center$WalkDist)), label = "***", color = "black", size = 4)
 
@@
                  log_tdh = seq(3.32, 5.42, 0.02))
-predicted.distance <- augment(top_model_wd_c, 
+predicted.distance <- augment(top_model_sd_c, 
                               newdata = nd, 
@@
                             "Urban, Low"))
-predictions <- summary(emmeans(search_land, ~Land),type = "response")
+nd <- data.frame(Land = factor(levels(sites$Land)))
+predictions <- augment(search_land, newdata = nd, se_fit = TRUE, type.predict = "response")
+predictions <- predictions %>% 
+  rename("rate" = ".fitted", "SE" = ".se.fit")
+#predictions <- summary(emmeans(search_land, ~Land),type = "response")
 
@@
 
+I also tested Poisson glm vs log-transformation here since log-transformed does help make the data more Gaussian. However, similar results arise in this case.
+
+```{r webs_location_stats}
+ggarrange(ggplot(sites, aes(x = NumWebs)) +
+            geom_density(),
+          ggplot(sites, aes(x = log(NumWebs))) +
+            geom_density(), ncol = 2)
+
+shapiro.test(sites$NumWebs) # not normal
+shapiro.test(log(sites$NumWebs)) # just normal
+
+web <- glm(NumWebs ~ Location, data = sites, family = poisson)
+summary(web)
+
+web2 <- glm(log(NumWebs) ~ Location, data = sites)
+summary(web)
+
+# Both methods yield similar results
+sites %>% 
+  group_by(Location) %>% 
+  summarize(mean = mean(NumWebs),
+            se = plotrix::std.error(NumWebs))
+```
+
+```{r webs_location_assumptions, echo = FALSE}
+# As is, Poisson
+test_webs <- augment(web, data = sites)
+resid_webs <- ggplot(test_webs, aes(x = .fitted, y = .resid)) + 
+  geom_point() + 
+  geom_smooth() +
+  geom_hline(yintercept = 0) +
+  xlab("Fitted Values") +
+  ylab("Standardized \nResiduals") +
+  theme_classic() +
+  theme(text = element_text(size = 14, color = "black")) +
+  theme(axis.text.x=element_text(color="black", size=14)) + 
+  theme(axis.text.y=element_text(color="black", size=14))
+
+y <- quantile(test_webs$.resid, c(0.25, 0.75))
+x <- qnorm(c(0.25, 0.75))
+slope <- diff(y)/diff(x)
+int <- y[1L] - slope * x[1L]
+
+qq_webs <- ggplot(test_webs, aes(sample = .resid)) + 
+  stat_qq() + 
+  geom_abline(slope = slope, intercept = int) +
+  xlab("Theoretical Quantiles") +
+  ylab("Sample Quantiles") +
+  theme_classic() +
+  theme(text = element_text(size = 14, color = "black")) +
+  theme(axis.text.x=element_text(color="black", size=14)) + 
+  theme(axis.text.y=element_text(color="black", size=14))
+
+scaleloc_webs <- ggplot(test_webs, aes(x = .fitted, y = sqrt(abs(.std.resid)))) + 
+  geom_point() + 
+  geom_smooth() + 
+  geom_hline(yintercept = 0.83) +
+  xlab("Fitted Values") +
+  ylab("Sqrt Standardized \nResiduals") +
+  theme_classic() +
+  theme(text = element_text(size = 14, color = "black")) +
+  theme(axis.text.x=element_text(color="black", size=14)) + 
+  theme(axis.text.y=element_text(color="black", size=14))
+
+lev_webs <- ggplot(test_webs, aes(.hat, .std.resid)) +
+ geom_vline(colour = "black", xintercept = 0) +
+  geom_hline(colour = "black", yintercept = 0) +
+  geom_point(aes(size = .cooksd)) + geom_smooth(se = FALSE) +
+  xlab("Theoretical Quantiles") +
+  ylab("Sample Quantiles") +
+  labs(size = "Cook's \nDistance") +
+  theme_classic() +
+  theme(text = element_text(size = 14, color = "black")) +
+  theme(axis.text.x=element_text(color="black", size=14)) + 
+  theme(axis.text.y=element_text(color="black", size=14))
+
+ggarrange(resid_webs, qq_webs, scaleloc_webs, lev_webs, 
+          labels = c("A", "B", "C", "D"),
+          ncol = 2, nrow = 2)
+
+# Log-transformed, Normal
+test_webs2 <- augment(webs2, data = sites)
+resid_webs2 <- ggplot(test_webs2, aes(x = .fitted, y = .resid)) + 
+  geom_point() + 
+  geom_smooth() +
+  geom_hline(yintercept = 0) +
+  xlab("Fitted Values") +
+  ylab("Standardized \nResiduals") +
+  theme_classic() +
+  theme(text = element_text(size = 14, color = "black")) +
+  theme(axis.text.x=element_text(color="black", size=14)) + 
+  theme(axis.text.y=element_text(color="black", size=14))
+
+y <- quantile(test_webs2$.resid, c(0.25, 0.75))
+x <- qnorm(c(0.25, 0.75))
+slope <- diff(y)/diff(x)
+int <- y[1L] - slope * x[1L]
+
+qq_webs2 <- ggplot(test_webs2, aes(sample = .resid)) + 
+  stat_qq() + 
+  geom_abline(slope = slope, intercept = int) +
+  xlab("Theoretical Quantiles") +
+  ylab("Sample Quantiles") +
+  theme_classic() +
+  theme(text = element_text(size = 14, color = "black")) +
+  theme(axis.text.x=element_text(color="black", size=14)) + 
+  theme(axis.text.y=element_text(color="black", size=14))
+
+scaleloc_webs2 <- ggplot(test_webs2, aes(x = .fitted, y = sqrt(abs(.std.resid)))) + 
+  geom_point() + 
+  geom_smooth() + 
+  geom_hline(yintercept = 0.83) +
+  xlab("Fitted Values") +
+  ylab("Sqrt Standardized \nResiduals") +
+  theme_classic() +
+  theme(text = element_text(size = 14, color = "black")) +
+  theme(axis.text.x=element_text(color="black", size=14)) + 
+  theme(axis.text.y=element_text(color="black", size=14))
+
+lev_webs2 <- ggplot(test_webs2, aes(.hat, .std.resid)) +
+ geom_vline(colour = "black", xintercept = 0) +
+  geom_hline(colour = "black", yintercept = 0) +
+  geom_point(aes(size = .cooksd)) + geom_smooth(se = FALSE) +
+  xlab("Theoretical Quantiles") +
+  ylab("Sample Quantiles") +
+  labs(size = "Cook's \nDistance") +
+  theme_classic() +
+  theme(text = element_text(size = 14, color = "black")) +
+  theme(axis.text.x=element_text(color="black", size=14)) + 
+  theme(axis.text.y=element_text(color="black", size=14))
+
+ggarrange(resid_webs2, qq_webs2, scaleloc_webs2, lev_webs2, 
+          labels = c("A", "B", "C", "D"),
+          ncol = 2, nrow = 2)
+```
+
+```{r webs_location_graph, echo = FALSE}
+# raw data
+raw <- sites %>% 
+  group_by(Location) %>% 
+  summarise(mean = mean(NumWebs),
+            se = plotrix::std.error(NumWebs))
+
+raw_plot <- ggplot(sites, aes(x = Location, y = NumWebs)) + 
+  geom_jitter(color = "grey", width = 0.1) +
+  geom_point(aes(x = Location, y = mean, color = Location), size = 2, data = raw) +
+  geom_errorbar(aes(x= Location, 
+                    ymin = mean - se, 
+                    ymax = mean + se, 
+                    color = Location), data = raw, inherit.aes = FALSE, width = 0.15, size = 1.5) +
+    scale_color_manual(values = c("Urban Center" = "#d95f02", "Urban Forest" = "#1b9e77")) +
+    scale_x_discrete(labels=c("Urban Forest" = "Urban \nForest \nN = 10", "Urban Center" = "Urban \nCenter \nN = 12")) +
+    theme_classic() +
+    scale_y_continuous(limits = c(0, 75), breaks = c(0, 15, 30, 45, 60, 75)) +
+    ylab("Number of Webs") + 
+    theme(text = element_text(size = 16)) + 
+    theme(axis.text.x = element_text(colour = "black", size = 16)) + 
+    theme(axis.text.y = element_text(colour = "black", size = 16),
+        axis.title.x = element_blank()) +
+    theme(legend.position = "none") +
+    ggtitle("Raw Data")
+
+# Non-transformed, poisson distribution
+nd <- data.frame(Location = factor(levels(sites$Location)))
+predictions <- augment(web, newdata = nd, se_fit = TRUE, type.predict = "response")
+predictions <- predictions %>% 
+  rename("rate" = ".fitted", "SE" = ".se.fit")
+#predictions <- summary(emmeans(web, ~Location),type = "response")
+
+poisson_plot <- ggplot(sites, aes(x = Location, y = NumWebs)) + 
+  geom_jitter(color = "grey", width = 0.1) +
+  geom_point(aes(x = Location, y = rate, color = Location), size = 2, data = predictions) + 
+  geom_errorbar(aes(x = Location, 
+                  ymin = rate - SE, 
+                  ymax = rate + SE,
+                  color = Location), data = predictions, inherit.aes = FALSE, width = 0.15, size = 1.5) +
+  scale_color_manual(values = c("Urban Center" = "#d95f02", "Urban Forest" = "#1b9e77")) +
+  scale_x_discrete(labels=c("Urban Forest" = "Urban \nForest \nN = 10", "Urban Center" = "Urban \nCenter \nN = 12")) +
+  theme_classic() +
+    scale_y_continuous(limits = c(0, 75), breaks = c(0, 15, 30, 45, 60, 75)) +
+  ylab("Number of Webs") + 
+  theme(text = element_text(size = 16)) + 
+  theme(axis.text.x = element_text(colour = "black", size = 16)) + 
+  theme(axis.text.y = element_text(colour = "black", size = 16),
+        axis.title.x = element_blank()) +
+  theme(legend.position = "none") +
+  annotate(geom = "text", x = 1.5, y = 75, label = "***", color = "black", size = 10) +
+  ggtitle("Poisson Distribution")
+
+# Let's look at the log-transformed response variable since that is normal
+nd <- data.frame(Location = factor(levels(sites$Location)))
+predictions <- augment(web2, newdata = nd, se_fit = TRUE, type.predict = "response")
+predictions <- predictions %>% 
+  rename("response" = ".fitted", "SE" = ".se.fit")
+#predictions2 <- summary(emmeans(webs2, ~Location),type = "response")
+
+log_plot <- ggplot(sites, aes(x = Location, y = (NumWebs))) + 
+  geom_jitter(color = "grey", width = 0.1) +
+  geom_point(aes(x = Location, y = exp(response), color = Location), size = 2, data = predictions) + 
+  geom_errorbar(aes(x = Location, 
+                  ymin = exp(response - SE), 
+                  ymax = exp(response + SE),
+                  color = Location), data = predictions, inherit.aes = FALSE, width = 0.15, size = 1.5) +
+  scale_color_manual(values = c("Urban Center" = "#d95f02", "Urban Forest" = "#1b9e77")) +
+  scale_x_discrete(labels=c("Urban Forest" = "Urban \nForest \nN = 10", "Urban Center" = "Urban \nCenter \nN = 12")) +
+  theme_classic() +
+    scale_y_continuous(limits = c(0, 75), breaks = c(0, 15, 30, 45, 60, 75)) +
+  ylab("Number of Webs") + 
+  theme(text = element_text(size = 16)) + 
+  theme(axis.text.x = element_text(colour = "black", size = 16)) + 
+  theme(axis.text.y = element_text(colour = "black", size = 16),
+        axis.title.x = element_blank()) +
+  theme(legend.position = "none") +
+  annotate(geom = "text", x = 1.5, y = 75, label = "**", color = "black", size = 10) +
+  ggtitle("Log-Transformed")
+
+ggarrange(raw_plot, poisson_plot, log_plot, nrow = 1)
+```
+
 ### Number of Webs by Predictors
 
+```{r webs_predictors_stats}
+# This is one way to look at the overall data, but I think I end up not using this information
+models = list(NumWebs ~ 1,
+              NumWebs ~ log_TotalSub, 
+              NumWebs ~ log_tdr, 
+              NumWebs ~ log_tdh,
+              NumWebs ~ log_TotalSub + log_tdr,
+              NumWebs ~ log_TotalSub + log_tdh,
+              NumWebs ~ log_tdr + log_tdh,
+              NumWebs ~ log_TotalSub + log_tdr + log_tdh)
+fits = lapply(models, glm, data = sites, family = "poisson")
+modnames = sapply(models, function(ff)deparse(ff[[3]]))
+pander(aictab(fits, modname = modnames), caption="Table 1. AICc model selection table for Search Distance to the Focal Web Overall.", split.tables = Inf)
+# The top model keeps all 3 variables and no other model is within 2 Model Likelihood Units
+summary(glm(NumWebs ~ log_TotalSub + log_tdr + log_tdh, data = sites, family = poisson))
+
+global <- glm(NumWebs ~ log_TotalSub + log_tdr + log_tdh, data = sites, family = poisson)
+options(na.action = "na.fail") # Required for dredge to run
+model_dredge <- dredge(global, beta = F, evaluate = T, rank = AICc)
+options(na.action = "na.omit") # set back to default
+top_model_nw_o <- get.models(model_dredge, subset = 1)[[1]]
+out <- summary(top_model_nw_o)
+out
+info <- out[[12]]
+#TotalSub (log_TotalSub)
+exp(info[4, 1])
+exp(info[4, 2])
+#Traffic_Dist_Road (log_tdr)
+exp(info[3, 1])
+exp(info[3, 2])
+#Traffic_Dist_Highway (log_tdh)
+exp(info[2, 1])
+exp(info[2, 2])
+
+with(summary(top_model_nw_o), 1 - deviance/null.deviance) # This gives the R squared value
+#summary(model.avg(model_dredge, subset = delta <= 2))
+#summary(model.avg(model_dredge))
+model.sel(model_dredge) #estimates same signs
+car::vif(get.models(model_dredge, 1)[[1]]) #looking for less than 2
+
+# urban forest
+global <- glm(NumWebs ~ tree100m + log_TotalSub + log_tdh + log_patch + log_tdr, data = sites_forest, family = poisson)
+options(na.action = "na.fail") # Required for dredge to run
+model_dredge <- dredge(global, beta = F, evaluate = T, rank = AICc)
+options(na.action = "na.omit") # set back to default
+top_model_nw_f <- get.models(model_dredge, subset = 1)[[1]]
+out <- summary(top_model_nw_f)
+out
+info <- out[[12]]
+with(summary(top_model_nw_f), 1 - deviance/null.deviance) # This gives the R squared value
+model.sel(model_dredge) #estimates same signs
+#summary(model.avg(model_dredge, subset = delta <= 2))
+#car::vif(get.models(model_dredge, 1)[[1]]) #looking for less than 2
+
+# urban center
+global <- glm(NumWebs ~ log_TotalSub + log_tdr + log_tdh + spec_rad + log_patch + road_length_m, data = sites_center, family = poisson)
+options(na.action = "na.fail") # Required for dredge to run
+model_dredge <- dredge(global, beta = F, evaluate = T, rank = AICc)
+options(na.action = "na.omit") # set back to default
+top_model_nw_c <- get.models(model_dredge, subset = 1)[[1]]
+out <- summary(top_model_nw_c)
+out
+info <- out[[12]]
+#TotalSub
+exp(info[4, 1])
+exp(info[4, 2])
+#patch_area_km
+exp(info[2, 1])
+exp(info[2, 2])
+#Traffic_Dist_Highway
+exp(info[3, 1])
+exp(info[3, 2])
+#road_length
+info[5, 1]
+info[5, 2]
+with(summary(top_model_nw_c), 1 - deviance/null.deviance) # This gives the R squared value
+model.sel(model_dredge) #estimates same signs
+summary(model.avg(model_dredge, subset = delta <= 2))
+# We'll use the conditional average
+#TotalSub
+-exp(0.659231)
+exp(0.186648)
+#patch_area_km
+-exp(0.293327)
+exp(0.113716)
+#Traffic_Dist_Highway
+-exp(1.560993)
+exp(0.192352)
+#road_length_m
+-0.021230 
+0.004766
+car::vif(get.models(model_dredge, 1)[[1]]) # looking for values < 2
+```
+
+*Overall*
+Coefficients:
+             Estimate Std. Error z value Pr(>|z|)    
+(Intercept)   7.55449    0.87254   8.658  < 2e-16 ***
+log_tdh      -1.26833    0.19726  -6.430 1.28e-10 *** *negative*
+log_tdr       0.18726    0.04729   3.960 7.49e-05 *** *positive*
+log_TotalSub -1.02619    0.09768 -10.505  < 2e-16 *** *negative*
+
+R-squared = 0.556197
+
+*Urban Forest*
+Coefficients:
+            Estimate Std. Error z value Pr(>|z|)    
+(Intercept)   1.0986     0.1826   6.017 1.77e-09 ***
+
+R-squared = -6.661338e-16
+
+*Urban Center*
+Coefficients:
+               Estimate Std. Error z value Pr(>|z|)    
+(Intercept)   13.145965   1.236110  10.635  < 2e-16 ***
+log_patch     -0.293327   0.113716  -2.579   0.0099 **  *negative*
+log_tdh       -1.539660   0.190172  -8.096 5.67e-16 *** *negative*
+log_TotalSub  -0.717109   0.183835  -3.901 9.59e-05 *** *negative*
+road_length_m -0.022553   0.004713  -4.785 1.71e-06 *** *negative*
+
+R-squared = 0.5814882
+
+(conditional average) 
+               Estimate Std. Error Adjusted SE z value Pr(>|z|)    
+(Intercept)   12.284984   1.481836    1.650697   7.442  < 2e-16 ***
+log_patch     -0.293327   0.113716    0.137194   2.138 0.032513 *   *negative*
+log_tdh       -1.560993   0.192352    0.229029   6.816  < 2e-16 *** *negative*
+log_TotalSub  -0.659231   0.186648    0.218846   3.012 0.002593 **  *negative*
+road_length_m -0.021230   0.004766    0.005608   3.786 0.000153 *** *negative*
+
+```{r webs_predictors_overall_graphs, echo = FALSE}
+colorc = "#d95f02" 
+colorf = "#1b9e77"
+coloro = "black"
+
+# Plant Species Richness
+nd <- data.frame(log_TotalSub = seq(0, 3.2, 0.03), 
+                 log_tdr = mean(sites$log_tdr), 
+                 log_tdh = mean(sites$log_tdh))
+predicted.distance <- augment(top_model_nw_o, 
+                              newdata = nd, 
+                              se_fit = TRUE)
+webs_plant <- ggplot(sites, aes(x = log_TotalSub, y = log(NumWebs))) + 
+  geom_point(color = "grey", 
+             size = 1) +
+  geom_line(aes(x = log_TotalSub, y = .fitted), 
+            size = 1, 
+            color = coloro, 
+            data = predicted.distance) + 
+  geom_ribbon(aes(x = log_TotalSub, 
+                  ymin = .fitted - 1.96 * .se.fit, 
+                  ymax = .fitted + 1.96 * .se.fit), 
+              fill = coloro, 
+              data = predicted.distance, 
+              inherit.aes = FALSE, 
+              alpha = 0.25) +
+  scale_y_continuous(limits = c(min(log(sites$NumWebs)), max(log(sites$NumWebs)) + 0.1 * diff(range(log(sites$NumWebs))))) +  
+  theme_classic() +
+  xlab("Plant Species Richness [log()]") +
+  ylab("Number of Webs [log()]") + 
+  theme(text = element_text(size = 10)) + 
+  theme(axis.text.x = element_text(colour = "black", size = 10)) + 
+  theme(axis.text.y = element_text(colour = "black", size = 10)) +
+  theme(axis.text.x = element_blank(), 
+        axis.title.x = element_blank(),
+        axis.text.y = element_blank(),
+        axis.title.y = element_blank()) +
+  annotate(geom = "text", x = min(predicted.distance$log_TotalSub) + diff(range(predicted.distance$log_TotalSub))/2, y = max(log(sites$NumWebs)), label = "***", color = "black", size = 4)
+
+# Road Disturbance
+nd <- data.frame(log_TotalSub = mean(sites$log_TotalSub), 
+                 log_tdr = seq(2.7, 7.3, 0.05), 
+                 log_tdh = mean(sites$log_tdh))
+predicted.distance <- augment(top_model_nw_o, 
+                              newdata = nd, 
+                              se_fit = TRUE)
+webs_tdr <- ggplot(sites, aes(x = log_tdr, y = log(NumWebs))) + 
+  geom_point(color = "grey", 
+             size = 1) +
+  geom_line(aes(x = log_tdr, y = .fitted), 
+            size = 1, 
+            color = coloro, 
+            data = predicted.distance) + 
+  geom_ribbon(aes(x = log_tdr, 
+                  ymin = .fitted - 1.96 * .se.fit, 
+                  ymax = .fitted + 1.96 * .se.fit), 
+              fill = coloro, 
+              data = predicted.distance, 
+              inherit.aes = FALSE, 
+              alpha = 0.25) +
+  scale_y_continuous(limits = c(min(log(sites$NumWebs)), max(log(sites$NumWebs)) + 0.1 * diff(range(log(sites$NumWebs))))) +  
+  theme_classic() +
+  xlab("Road Disturbance [log(vehicles/day/m)]") +
+  ylab("Number of Webs [log()]") + 
+  theme(text = element_text(size = 10)) + 
+  theme(axis.text.x = element_text(colour = "black", size = 10)) + 
+  theme(axis.text.y = element_text(colour = "black", size = 10)) +
+  theme(axis.text.x = element_blank(), 
+        axis.title.x = element_blank(),
+        axis.text.y = element_blank(),
+        axis.title.y = element_blank()) +
+  annotate(geom = "text", x = min((predicted.distance$log_tdr)) + diff(range((predicted.distance$log_tdr)))/2, y = max(log(sites$NumWebs)), label = "***", color = "black", size = 4)
+
+# Highway Disturbance
+nd <- data.frame(log_TotalSub = mean(sites$log_TotalSub), 
+                 log_tdr = mean(sites$log_tdr), 
+                 log_tdh = seq(2.7, 5.5, 0.03))
+predicted.distance <- augment(top_model_nw_o, 
+                              newdata = nd, 
+                              se_fit = TRUE)
+webs_tdh <- ggplot(sites, aes(x = log_tdh, y = log(NumWebs))) + 
+  geom_point(color = "grey", 
+             size = 1) +
+  geom_line(aes(x = log_tdh, y = .fitted), 
+            size = 1, 
+            color = coloro, 
+            data = predicted.distance) + 
+  geom_ribbon(aes(x = log_tdh, 
+                  ymin = .fitted - 1.96 * .se.fit, 
+                  ymax = .fitted + 1.96 * .se.fit), 
+              fill = coloro, 
+              data = predicted.distance, 
+              inherit.aes = FALSE, 
+              alpha = 0.25) +
+  scale_y_continuous(limits = c(min(log(sites$NumWebs)) - 1.2, max(log(sites$NumWebs)) + 0.1 * diff(range(log(sites$NumWebs))))) +  
+  theme_classic() +
+  xlab("Highway Disturbance [log(vehicles/day/m)]") +
+  ylab("Number of Webs [log()]") + 
+  theme(text = element_text(size = 10)) + 
+  theme(axis.text.x = element_text(colour = "black", size = 10)) + 
+  theme(axis.text.y = element_text(colour = "black", size = 10)) +
+  theme(axis.text.x = element_blank(), 
+        axis.title.x = element_blank(),
+        axis.text.y = element_blank(),
+        axis.title.y = element_blank()) +
+  annotate(geom = "text", x = min((predicted.distance$log_tdh)) + diff(range((predicted.distance$log_tdh)))/2, y = max(log(sites$NumWebs)), label = "***", color = "black", size = 4)
+
+webs_plant
+webs_tdr
+webs_tdh
+```
+
+```{r webs_predictors_center_graphs, echo = FALSE}
+colorc = "#d95f02" 
+colorf = "#1b9e77"
+coloro = "black"
+
+# Plant Species Richness
+nd <- data.frame(log_TotalSub = seq(0, 1.8, 0.02), 
+                 log_patch = mean(sites_center$log_patch),
+                 road_length_m = mean(sites_center$road_length_m),
+                 log_tdh = mean(sites_center$log_tdh))
+predicted.distance <- augment(top_model_nw_c, 
+                              newdata = nd, 
+                              se_fit = TRUE)
+webs_center_plant <- ggplot(sites_center, aes(x = log_TotalSub, y = log(NumWebs))) + 
+  geom_point(color = "grey", 
+             size = 1) +
+  geom_line(aes(x = log_TotalSub, y = .fitted), 
+            size = 1, 
+            color = colorc, 
+            data = predicted.distance) + 
+  geom_ribbon(aes(x = log_TotalSub, 
+                  ymin = .fitted - 1.96 * .se.fit, 
+                  ymax = .fitted + 1.96 * .se.fit), 
+              fill = colorc, 
+              data = predicted.distance, 
+              inherit.aes = FALSE, 
+              alpha = 0.25) +
+  scale_y_continuous(limits = c(min(log(sites_center$NumWebs)), max(log(sites_center$NumWebs)) + 0.1 * diff(range(log(sites_center$NumWebs))))) +  
+  theme_classic() +
+  xlab("Plant Species Richness [log()]") +
+  ylab("Number of Webs [log()]") + 
+  theme(text = element_text(size = 10)) + 
+  theme(axis.text.x = element_text(colour = "black", size = 10)) + 
+  theme(axis.text.y = element_text(colour = "black", size = 10)) +
+  theme(axis.text.x = element_blank(), 
+        axis.title.x = element_blank(),
+        axis.text.y = element_blank(),
+        axis.title.y = element_blank()) +
+  annotate(geom = "text", x = min((predicted.distance$log_TotalSub)) + diff(range((predicted.distance$log_TotalSub)))/2, y = max(log(sites_center$NumWebs)), label = "***", color = "black", size = 4)
+
+# Patch Area
+nd <- data.frame(log_TotalSub = mean(sites_center$log_TotalSub), 
+                 log_patch = seq(4.34, 7.52, 0.025),
+                 road_length_m = mean(sites_center$road_length_m),
+                 log_tdh = mean(sites_center$log_tdh))
+predicted.distance <- augment(top_model_nw_c, 
+                              newdata = nd, 
+                              se_fit = TRUE)
+webs_center_patch <- ggplot(sites_center, aes(x = log_patch, y = log(NumWebs))) + 
+  geom_point(color = "grey", 
+             size = 1) +
+  geom_line(aes(x = log_patch, y = .fitted), 
+            size = 1, 
+            color = colorc, 
+            data = predicted.distance) + 
+  geom_ribbon(aes(x = log_patch, 
+                  ymin = .fitted - 1.96 * .se.fit, 
+                  ymax = .fitted + 1.96 * .se.fit), 
+              fill = colorc, 
+              data = predicted.distance, 
+              inherit.aes = FALSE, 
+              alpha = 0.25) +
+  scale_y_continuous(limits = c(min(log(sites_center$NumWebs)) - 0.75, max(log(sites_center$NumWebs)) + 0.15 * diff(range(log(sites_center$NumWebs))))) +  
+  theme_classic() +
+  xlab("Patch Area [log(mm²)]") +
+  ylab("Number of Webs [log()]") + 
+  theme(text = element_text(size = 10)) + 
+  theme(axis.text.x = element_text(colour = "black", size = 10)) + 
+  theme(axis.text.y = element_text(colour = "black", size = 10)) +
+  theme(axis.text.x = element_blank(), 
+        axis.title.x = element_blank(),
+        axis.text.y = element_blank(),
+        axis.title.y = element_blank()) +
+  annotate(geom = "text", x = min((predicted.distance$log_patch)) + diff(range((predicted.distance$log_patch)))/2, y = max(log(sites_center$NumWebs)), label = "**", color = "black", size = 4)
+
+# Highway Disturbance
+nd <- data.frame(log_TotalSub = mean(sites_center$log_TotalSub), 
+                 log_patch = mean(sites_center$log_patch),
+                 road_length_m = mean(sites_center$road_length_m),
+                 log_tdh = seq(3.32, 5.42, 0.02))
+predicted.distance <- augment(top_model_nw_c, 
+                              newdata = nd, 
+                              se_fit = TRUE)
+webs_center_tdh <- ggplot(sites_center, aes(x = log_tdh, y = log(NumWebs))) + 
+  geom_point(color = "grey", 
+             size = 1) +
+  geom_line(aes(x = log_tdh, y = .fitted), 
+            size = 1, 
+            color = colorc, 
+            data = predicted.distance) + 
+  geom_ribbon(aes(x = log_tdh, 
+                  ymin = .fitted - 1.96 * .se.fit, 
+                  ymax = .fitted + 1.96 * .se.fit), 
+              fill = colorc, 
+              data = predicted.distance, 
+              inherit.aes = FALSE, 
+              alpha = 0.25) +
+  scale_y_continuous(limits = c(min(log(sites_center$NumWebs)) - 0.75, max(log(sites_center$NumWebs)) + 0.1 * diff(range(log(sites_center$NumWebs))))) +  
+  theme_classic() +
+  xlab("Highway Disturbance [log(vehicles/day/m)]") +
+  ylab("Number of Webs [log()]") + 
+  theme(text = element_text(size = 10)) + 
+  theme(axis.text.x = element_text(colour = "black", size = 10)) + 
+  theme(axis.text.y = element_text(colour = "black", size = 10)) +
+  theme(axis.text.x = element_blank(), 
+        axis.title.x = element_blank(),
+        axis.text.y = element_blank(),
+        axis.title.y = element_blank()) +
+  annotate(geom = "text", x = min((predicted.distance$log_tdh)) + diff(range((predicted.distance$log_tdh)))/2, y = max(log(sites_center$NumWebs)), label = "***", color = "black", size = 4)
+
+# Road Length
+nd <- data.frame(log_TotalSub = mean(sites_center$log_TotalSub), 
+                 log_patch = mean(sites_center$log_patch),
+                 road_length_m = seq(47, 136, 1),
+                 log_tdh = mean(sites_center$log_tdh))
+predicted.distance <- augment(top_model_nw_c, 
+                              newdata = nd, 
+                              se_fit = TRUE)
+webs_center_road <- ggplot(sites_center, aes(x = (road_length_m), y = log(NumWebs))) + 
+  geom_point(color = "grey", 
+             size = 1) +
+  geom_line(aes(x = (road_length_m), y = .fitted), 
+            size = 1, 
+            color = colorc, 
+            data = predicted.distance) + 
+  geom_ribbon(aes(x = (road_length_m), 
+                  ymin = .fitted - 1.96 * .se.fit, 
+                  ymax = .fitted + 1.96 * .se.fit), 
+              fill = colorc, 
+              data = predicted.distance, 
+              inherit.aes = FALSE, 
+              alpha = 0.25) +
+  scale_y_continuous(limits = c(min(log(sites_center$NumWebs)), max(log(sites_center$NumWebs)) + 0.1 * diff(range(log(sites_center$NumWebs))))) +  
+  theme_classic() +
+  xlab("Total Road Length [m]") +
+  ylab("Number of Webs [log()]") + 
+  theme(text = element_text(size = 10)) + 
+  theme(axis.text.x = element_text(colour = "black", size = 10)) + 
+  theme(axis.text.y = element_text(colour = "black", size = 10)) +
+  theme(axis.text.x = element_blank(), 
+        axis.title.x = element_blank(),
+        axis.text.y = element_blank(),
+        axis.title.y = element_blank()) +
+  annotate(geom = "text", x = min((predicted.distance$road_length_m)) + diff(range((predicted.distance$road_length_m)))/2, y = max(log(sites_center$NumWebs)), label = "***", color = "black", size = 4)
+
+webs_center_plant
+webs_center_patch
+webs_center_road
+webs_center_tdh
+```
+
 ### Number of Webs by Land
+
+```{r webs_land_stats}
+webs_land <- glm(NumWebs ~ Land, data = sites, family = poisson)
+summary(webs_land)
+anova(webs_land, test = "Chisq")
+comp <- glht(webs_land, linfct = mcp(Land = "Tukey"))
+summary(comp)
+```
+
+```{r webs_land_graph}
+sites <- sites %>% 
+  mutate(Land = fct_relevel(Land, "Deciduous Forest", 
+                            "Woody Wetlands", 
+                            "Urban, High", 
+                            "Urban, Medium", 
+                            "Urban, Low"))
+nd <- data.frame(Land = factor(levels(sites$Land)))
+predictions <- augment(webs_land, newdata = nd, se_fit = TRUE, type.predict = "response")
+predictions <- predictions %>% 
+  rename("rate" = ".fitted", "SE" = ".se.fit")
+#predictions <- summary(emmeans(webs_land, ~Land),type = "response")
+
+ggplot(sites, aes(x = Land, y = NumWebs)) + 
+  geom_jitter(color = "grey", width = 0.1, size = 0.5) +
+  geom_point(aes(x = Land, y = rate, color = Land), size = 1, data = predictions) + 
+  geom_errorbar(aes(x = Land, 
+                  ymin = rate - SE, 
+                  ymax = rate + SE, color = Land), data = predictions, inherit.aes = FALSE, width = 0.25, size = 1) +
+  theme_classic() +
+  scale_color_manual(values = c("Deciduous Forest" = "#1b9e77", "Woody Wetlands" = "#1b9e77", "Urban, High" = "#d95f02", "Urban, Medium" = "#d95f02", "Urban, Low" = "#d95f02")) +
+  xlab("Land Cover Class") +
+  ylab("Number of Webs") + 
+  theme(text = element_text(size = 10)) + 
+  theme(axis.text.x=element_text(colour="black", size=10)) + 
+  theme(axis.text.y=element_text(colour="black", size=10)) +
+  theme(legend.position = "none") +
+  theme(axis.text.x = element_text(angle = 90, vjust = 1, hjust=1)) +
+  annotate(geom="text", x=1, y=max(sites$NumWebs), label="A", color="black", size = 3) +
+  annotate(geom="text", x=2, y=max(sites$NumWebs), label="A", color="black", size = 3) +
+  annotate(geom="text", x=3, y=max(sites$NumWebs), label="B", color="black", size = 3) +
+  annotate(geom="text", x=4, y=max(sites$NumWebs), label="B", color="black", size = 3) +
+  annotate(geom="text", x=5, y=max(sites$NumWebs), label="B", color="black", size = 3)
+```
+
+## Response Variable: Number of Spiders
+
+### Number of Spiders by Location
+
+```{r spiders_location_stats}
+ggarrange(ggplot(sites, aes(x = NumSpiders)) +
+            geom_density(),
+          ggplot(sites, aes(x = log(NumSpiders))) +
+            geom_density(), ncol = 2)
+
+shapiro.test(sites$NumSpiders) # not normal
+shapiro.test(log(sites$NumSpiders)) # not normal
+
+spiders <- glm(NumSpiders ~ Location, data = sites, family = poisson)
+summary(spiders)
+
+spiders2 <- glm(log(NumSpiders) ~ Location, data = sites)
+summary(spiders2)
+
+# Both methods yield similar results
+sites %>% 
+  group_by(Location) %>% 
+  summarize(mean = mean(NumSpiders),
+            se = plotrix::std.error(NumSpiders))
+```
+
+```{r spiders_location_assumptions, echo = FALSE}
+# As is, Poisson
+test_spiders <- augment(spiders, data = sites)
+resid_spiders <- ggplot(test_spiders, aes(x = .fitted, y = .resid)) + 
+  geom_point() + 
+  geom_smooth() +
+  geom_hline(yintercept = 0) +
+  xlab("Fitted Values") +
+  ylab("Standardized \nResiduals") +
+  theme_classic() +
+  theme(text = element_text(size = 14, color = "black")) +
+  theme(axis.text.x=element_text(color="black", size=14)) + 
+  theme(axis.text.y=element_text(color="black", size=14))
+
+y <- quantile(test_spiders$.resid, c(0.25, 0.75))
+x <- qnorm(c(0.25, 0.75))
+slope <- diff(y)/diff(x)
+int <- y[1L] - slope * x[1L]
+
+qq_spiders <- ggplot(test_spiders, aes(sample = .resid)) + 
+  stat_qq() + 
+  geom_abline(slope = slope, intercept = int) +
+  xlab("Theoretical Quantiles") +
+  ylab("Sample Quantiles") +
+  theme_classic() +
+  theme(text = element_text(size = 14, color = "black")) +
+  theme(axis.text.x=element_text(color="black", size=14)) + 
+  theme(axis.text.y=element_text(color="black", size=14))
+
+scaleloc_spiders <- ggplot(test_spiders, aes(x = .fitted, y = sqrt(abs(.std.resid)))) + 
+  geom_point() + 
+  geom_smooth() + 
+  geom_hline(yintercept = 0.83) +
+  xlab("Fitted Values") +
+  ylab("Sqrt Standardized \nResiduals") +
+  theme_classic() +
+  theme(text = element_text(size = 14, color = "black")) +
+  theme(axis.text.x=element_text(color="black", size=14)) + 
+  theme(axis.text.y=element_text(color="black", size=14))
+
+lev_spiders <- ggplot(test_spiders, aes(.hat, .std.resid)) +
+ geom_vline(colour = "black", xintercept = 0) +
+  geom_hline(colour = "black", yintercept = 0) +
+  geom_point(aes(size = .cooksd)) + geom_smooth(se = FALSE) +
+  xlab("Theoretical Quantiles") +
+  ylab("Sample Quantiles") +
+  labs(size = "Cook's \nDistance") +
+  theme_classic() +
+  theme(text = element_text(size = 14, color = "black")) +
+  theme(axis.text.x=element_text(color="black", size=14)) + 
+  theme(axis.text.y=element_text(color="black", size=14))
+
+ggarrange(resid_spiders, qq_spiders, scaleloc_spiders, lev_spiders, 
+          labels = c("A", "B", "C", "D"),
+          ncol = 2, nrow = 2)
+
+# Log-transformed, Normal
+test_spiders2 <- augment(spiders2, data = sites)
+resid_spiders2 <- ggplot(test_spiders2, aes(x = .fitted, y = .resid)) + 
+  geom_point() + 
+  geom_smooth() +
+  geom_hline(yintercept = 0) +
+  xlab("Fitted Values") +
+  ylab("Standardized \nResiduals") +
+  theme_classic() +
+  theme(text = element_text(size = 14, color = "black")) +
+  theme(axis.text.x=element_text(color="black", size=14)) + 
+  theme(axis.text.y=element_text(color="black", size=14))
+
+y <- quantile(test_spiders2$.resid, c(0.25, 0.75))
+x <- qnorm(c(0.25, 0.75))
+slope <- diff(y)/diff(x)
+int <- y[1L] - slope * x[1L]
+
+qq_spiders2 <- ggplot(test_spiders2, aes(sample = .resid)) + 
+  stat_qq() + 
+  geom_abline(slope = slope, intercept = int) +
+  xlab("Theoretical Quantiles") +
+  ylab("Sample Quantiles") +
+  theme_classic() +
+  theme(text = element_text(size = 14, color = "black")) +
+  theme(axis.text.x=element_text(color="black", size=14)) + 
+  theme(axis.text.y=element_text(color="black", size=14))
+
+scaleloc_spiders2 <- ggplot(test_spiders2, aes(x = .fitted, y = sqrt(abs(.std.resid)))) + 
+  geom_point() + 
+  geom_smooth() + 
+  geom_hline(yintercept = 0.83) +
+  xlab("Fitted Values") +
+  ylab("Sqrt Standardized \nResiduals") +
+  theme_classic() +
+  theme(text = element_text(size = 14, color = "black")) +
+  theme(axis.text.x=element_text(color="black", size=14)) + 
+  theme(axis.text.y=element_text(color="black", size=14))
+
+lev_spiders2 <- ggplot(test_spiders2, aes(.hat, .std.resid)) +
+ geom_vline(colour = "black", xintercept = 0) +
+  geom_hline(colour = "black", yintercept = 0) +
+  geom_point(aes(size = .cooksd)) + geom_smooth(se = FALSE) +
+  xlab("Theoretical Quantiles") +
+  ylab("Sample Quantiles") +
+  labs(size = "Cook's \nDistance") +
+  theme_classic() +
+  theme(text = element_text(size = 14, color = "black")) +
+  theme(axis.text.x=element_text(color="black", size=14)) + 
+  theme(axis.text.y=element_text(color="black", size=14))
+
+ggarrange(resid_spiders2, qq_spiders2, scaleloc_spiders2, lev_spiders2, 
+          labels = c("A", "B", "C", "D"),
+          ncol = 2, nrow = 2)
+```
+
+```{r spiders_location_graph, echo = FALSE}
+# raw data
+raw <- sites %>% 
+  group_by(Location) %>% 
+  summarise(mean = mean(NumSpiders),
+            se = plotrix::std.error(NumSpiders))
+
+raw_plot <- ggplot(sites, aes(x = Location, y = NumSpiders)) + 
+  geom_jitter(color = "grey", width = 0.1) +
+  geom_point(aes(x = Location, y = mean, color = Location), size = 2, data = raw) +
+  geom_errorbar(aes(x= Location, 
+                    ymin = mean - se, 
+                    ymax = mean + se, 
+                    color = Location), data = raw, inherit.aes = FALSE, width = 0.15, size = 1.5) +
+    scale_color_manual(values = c("Urban Center" = "#d95f02", "Urban Forest" = "#1b9e77")) +
+    scale_x_discrete(labels=c("Urban Forest" = "Urban \nForest \nN = 10", "Urban Center" = "Urban \nCenter \nN = 12")) +
+    theme_classic() +
+    scale_y_continuous(limits = c(0, 25), breaks = c(0, 5, 10, 15, 20, 25)) +
+    ylab("Number of Spiders") + 
+    theme(text = element_text(size = 16)) + 
+    theme(axis.text.x = element_text(colour = "black", size = 16)) + 
+    theme(axis.text.y = element_text(colour = "black", size = 16),
+        axis.title.x = element_blank()) +
+    theme(legend.position = "none") +
+    ggtitle("Raw Data")
+
+# Non-transformed, poisson distribution
+nd <- data.frame(Location = factor(levels(sites$Location)))
+predictions <- augment(spiders, newdata = nd, se_fit = TRUE, type.predict = "response")
+predictions <- predictions %>% 
+  rename("rate" = ".fitted", "SE" = ".se.fit")
+#predictions <- summary(emmeans(spiders, ~Location),type = "response")
+
+poisson_plot <- ggplot(sites, aes(x = Location, y = NumSpiders)) + 
+  geom_jitter(color = "grey", width = 0.1) +
+  geom_point(aes(x = Location, y = rate, color = Location), size = 2, data = predictions) + 
+  geom_errorbar(aes(x = Location, 
+                  ymin = rate - SE, 
+                  ymax = rate + SE,
+                  color = Location), data = predictions, inherit.aes = FALSE, width = 0.15, size = 1.5) +
+  scale_color_manual(values = c("Urban Center" = "#d95f02", "Urban Forest" = "#1b9e77")) +
+  scale_x_discrete(labels=c("Urban Forest" = "Urban \nForest \nN = 10", "Urban Center" = "Urban \nCenter \nN = 12")) +
+  theme_classic() +
+    scale_y_continuous(limits = c(0, 25), breaks = c(0, 5, 10, 15, 20, 25)) +
+  ylab("Number of Spiders") + 
+  theme(text = element_text(size = 16)) + 
+  theme(axis.text.x = element_text(colour = "black", size = 16)) + 
+  theme(axis.text.y = element_text(colour = "black", size = 16),
+        axis.title.x = element_blank()) +
+  theme(legend.position = "none") +
+  annotate(geom = "text", x = 1.5, y = 25, label = "***", color = "black", size = 10) +
+  ggtitle("Poisson Distribution")
+
+# Let's look at the log-transformed response variable since that is normal
+nd <- data.frame(Location = factor(levels(sites$Location)))
+predictions <- augment(spiders2, newdata = nd, se_fit = TRUE, type.predict = "response")
+predictions <- predictions %>% 
+  rename("response" = ".fitted", "SE" = ".se.fit")
+#predictions2 <- summary(emmeans(webs2, ~Location),type = "response")
+
+log_plot <- ggplot(sites, aes(x = Location, y = (NumSpiders))) + 
+  geom_jitter(color = "grey", width = 0.1) +
+  geom_point(aes(x = Location, y = exp(response), color = Location), size = 2, data = predictions) + 
+  geom_errorbar(aes(x = Location, 
+                  ymin = exp(response - SE), 
+                  ymax = exp(response + SE),
+                  color = Location), data = predictions, inherit.aes = FALSE, width = 0.15, size = 1.5) +
+  scale_color_manual(values = c("Urban Center" = "#d95f02", "Urban Forest" = "#1b9e77")) +
+  scale_x_discrete(labels=c("Urban Forest" = "Urban \nForest \nN = 10", "Urban Center" = "Urban \nCenter \nN = 12")) +
+  theme_classic() +
+    scale_y_continuous(limits = c(0, 25), breaks = c(0, 5, 10, 15, 20, 25)) +
+  ylab("Number of Spiders") + 
+  theme(text = element_text(size = 16)) + 
+  theme(axis.text.x = element_text(colour = "black", size = 16)) + 
+  theme(axis.text.y = element_text(colour = "black", size = 16),
+        axis.title.x = element_blank()) +
+  theme(legend.position = "none") +
+  annotate(geom = "text", x = 1.5, y = 25, label = ".", color = "black", size = 10) +
+  ggtitle("Log-Transformed")
+
+ggarrange(raw_plot, poisson_plot, log_plot, nrow = 1)
+```
+
+### Number of Spiders by Predictors
+
+```{r spiders_predictors_stats}
+# This is one way to look at the overall data, but I think I end up not using this information
+models = list(NumSpiders ~ 1,
+              NumSpiders ~ log_TotalSub, 
+              NumSpiders ~ log_tdr, 
+              NumSpiders ~ log_tdh,
+              NumSpiders ~ log_TotalSub + log_tdr,
+              NumSpiders ~ log_TotalSub + log_tdh,
+              NumSpiders ~ log_tdr + log_tdh,
+              NumSpiders ~ log_TotalSub + log_tdr + log_tdh)
+fits = lapply(models, glm, data = sites, family = "poisson")
+modnames = sapply(models, function(ff)deparse(ff[[3]]))
+pander(aictab(fits, modname = modnames), caption="Table 1. AICc model selection table for Search Distance to the Focal Web Overall.", split.tables = Inf)
+# The top model keeps all 3 variables and no other model is within 2 Model Likelihood Units
+summary(glm(NumSpiders ~ log_TotalSub + log_tdr + log_tdh, data = sites, family = poisson))
+
+global <- glm(NumSpiders ~ log_TotalSub + log_tdr + log_tdh, data = sites, family = poisson)
+options(na.action = "na.fail") # Required for dredge to run
+model_dredge <- dredge(global, beta = F, evaluate = T, rank = AICc)
+options(na.action = "na.omit") # set back to default
+top_model_ns_o <- get.models(model_dredge, subset = 1)[[1]]
+out <- summary(top_model_ns_o)
+out
+info <- out[[12]]
+#TotalSub (log_TotalSub)
+exp(info[3, 1])
+exp(info[3, 2])
+#Traffic_Dist_Highway (log_tdh)
+exp(info[2, 1])
+exp(info[2, 2])
+
+with(summary(top_model_ns_o), 1 - deviance/null.deviance) # This gives the R squared value
+#summary(model.avg(model_dredge, subset = delta <= 2))
+#summary(model.avg(model_dredge))
+model.sel(model_dredge) #estimates same signs
+car::vif(get.models(model_dredge, 1)[[1]]) #looking for less than 2
+
+# urban forest
+global <- glm(NumSpiders ~ tree100m + log_TotalSub + log_tdh + log_patch + log_tdr, data = sites_forest, family = poisson)
+options(na.action = "na.fail") # Required for dredge to run
+model_dredge <- dredge(global, beta = F, evaluate = T, rank = AICc)
+options(na.action = "na.omit") # set back to default
+top_model_ns_f <- get.models(model_dredge, subset = 1)[[1]]
+out <- summary(top_model_ns_f)
+out
+info <- out[[12]]
+with(summary(top_model_ns_f), 1 - deviance/null.deviance) # This gives the R squared value
+model.sel(model_dredge) #estimates same signs
+#summary(model.avg(model_dredge, subset = delta <= 2))
+#car::vif(get.models(model_dredge, 1)[[1]]) #looking for less than 2
+
+# urban center
+global <- glm(NumSpiders ~ log_TotalSub + log_tdr + log_tdh + spec_rad + log_patch + road_length_m, data = sites_center, family = poisson)
+options(na.action = "na.fail") # Required for dredge to run
+model_dredge <- dredge(global, beta = F, evaluate = T, rank = AICc)
+options(na.action = "na.omit") # set back to default
+top_model_ns_c <- get.models(model_dredge, subset = 1)[[1]]
+out <- summary(top_model_ns_c)
+out
+info <- out[[12]]
+#TotalSub
+exp(info[4, 1])
+exp(info[4, 2])
+#patch_area_km
+exp(info[2, 1])
+exp(info[2, 2])
+#Traffic_Dist_Highway
+exp(info[3, 1])
+exp(info[3, 2])
+#road_length
+info[5, 1]
+info[5, 2]
+with(summary(top_model_ns_c), 1 - deviance/null.deviance) # This gives the R squared value
+model.sel(model_dredge) #estimates same signs
+#summary(model.avg(model_dredge, subset = delta <= 2))
+car::vif(get.models(model_dredge, 1)[[1]]) # looking for values < 2
+```
+
+*Overall*
+Coefficients:
+             Estimate Std. Error z value Pr(>|z|)    
+(Intercept)    7.3234     1.1068   6.617 3.67e-11 ***
+log_tdh       -1.1932     0.2785  -4.284 1.84e-05 *** *negative*
+log_TotalSub  -0.9523     0.1370  -6.952 3.61e-12 *** *negative*
+
+R-squared = 0.5363275
+
+*Urban Forest*
+Coefficients:
+            Estimate Std. Error z value Pr(>|z|)   
+(Intercept)   0.6419     0.2294   2.798  0.00515 **
+
+R-squared = -8.881784e-16
+
+*Urban Center*
+Coefficients:
+               Estimate Std. Error z value Pr(>|z|)    
+(Intercept)   14.516312   2.195703   6.611 3.81e-11 ***
+log_patch     -0.618055   0.205145  -3.013 0.002589 **  *negative*
+log_tdh       -1.393026   0.286317  -4.865 1.14e-06 *** *negative*
+log_TotalSub  -1.331282   0.357971  -3.719 0.000200 *** *negative*
+road_length_m -0.025605   0.007753  -3.303 0.000958 *** *negative*
+
+R-squared = 0.7582528
+
+```{r spiders_predictors_overall_graphs, echo = FALSE}
+colorc = "#d95f02" 
+colorf = "#1b9e77"
+coloro = "black"
+
+# Plant Species Richness
+nd <- data.frame(log_TotalSub = seq(0, 3.2, 0.03), 
+                 log_tdh = mean(sites$log_tdh))
+predicted.distance <- augment(top_model_ns_o, 
+                              newdata = nd, 
+                              se_fit = TRUE)
+spiders_plant <- ggplot(sites, aes(x = log_TotalSub, y = log(NumSpiders))) + 
+  geom_point(color = "grey", 
+             size = 1) +
+  geom_line(aes(x = log_TotalSub, y = .fitted), 
+            size = 1, 
+            color = coloro, 
+            data = predicted.distance) + 
+  geom_ribbon(aes(x = log_TotalSub, 
+                  ymin = .fitted - 1.96 * .se.fit, 
+                  ymax = .fitted + 1.96 * .se.fit), 
+              fill = coloro, 
+              data = predicted.distance, 
+              inherit.aes = FALSE, 
+              alpha = 0.25) +
+  scale_y_continuous(limits = c(min(log(sites$NumSpiders)) - 2, max(log(sites$NumSpiders)) + 0.1 * diff(range(log(sites$NumSpiders))))) +  
+  theme_classic() +
+  xlab("Plant Species Richness [log()]") +
+  ylab("Number of Spiders [log()]") + 
+  theme(text = element_text(size = 10)) + 
+  theme(axis.text.x = element_text(colour = "black", size = 10)) + 
+  theme(axis.text.y = element_text(colour = "black", size = 10)) +
+  theme(axis.text.x = element_blank(), 
+        axis.title.x = element_blank(),
+        axis.text.y = element_blank(),
+        axis.title.y = element_blank()) +
+  annotate(geom = "text", x = min(predicted.distance$log_TotalSub) + diff(range(predicted.distance$log_TotalSub))/2, y = max(log(sites$NumSpiders)), label = "***", color = "black", size = 4)
+
+# Highway Disturbance
+nd <- data.frame(log_TotalSub = mean(sites$log_TotalSub), 
+                 log_tdh = seq(2.7, 5.5, 0.03))
+predicted.distance <- augment(top_model_ns_o, 
+                              newdata = nd, 
+                              se_fit = TRUE)
+spiders_tdh <- ggplot(sites, aes(x = log_tdh, y = log(NumSpiders))) + 
+  geom_point(color = "grey", 
+             size = 1) +
+  geom_line(aes(x = log_tdh, y = .fitted), 
+            size = 1, 
+            color = coloro, 
+            data = predicted.distance) + 
+  geom_ribbon(aes(x = log_tdh, 
+                  ymin = .fitted - 1.96 * .se.fit, 
+                  ymax = .fitted + 1.96 * .se.fit), 
+              fill = coloro, 
+              data = predicted.distance, 
+              inherit.aes = FALSE, 
+              alpha = 0.25) +
+  scale_y_continuous(limits = c(min(log(sites$NumSpiders)) - 2, max(log(sites$NumSpiders)) + 0.1 * diff(range(log(sites$NumSpiders))))) +  
+  theme_classic() +
+  xlab("Highway Disturbance [log(vehicles/day/m)]") +
+  ylab("Number of Spiders [log()]") + 
+  theme(text = element_text(size = 10)) + 
+  theme(axis.text.x = element_text(colour = "black", size = 10)) + 
+  theme(axis.text.y = element_text(colour = "black", size = 10)) +
+  theme(axis.text.x = element_blank(), 
+        axis.title.x = element_blank(),
+        axis.text.y = element_blank(),
+        axis.title.y = element_blank()) +
+  annotate(geom = "text", x = min((predicted.distance$log_tdh)) + diff(range((predicted.distance$log_tdh)))/2, y = max(log(sites$NumSpiders)), label = "***", color = "black", size = 4)
+
+spiders_plant
+spiders_tdh
+```
+
+```{r spiders_predictors_center_graphs, echo = FALSE}
+colorc = "#d95f02" 
+colorf = "#1b9e77"
+coloro = "black"
+
+# Plant Species Richness
+nd <- data.frame(log_TotalSub = seq(0, 1.8, 0.02), 
+                 log_patch = mean(sites_center$log_patch),
+                 road_length_m = mean(sites_center$road_length_m),
+                 log_tdh = mean(sites_center$log_tdh))
+predicted.distance <- augment(top_model_ns_c, 
+                              newdata = nd, 
+                              se_fit = TRUE)
+spiders_center_plant <- ggplot(sites_center, aes(x = log_TotalSub, y = log(NumSpiders))) + 
+  geom_point(color = "grey", 
+             size = 1) +
+  geom_line(aes(x = log_TotalSub, y = .fitted), 
+            size = 1, 
+            color = colorc, 
+            data = predicted.distance) + 
+  geom_ribbon(aes(x = log_TotalSub, 
+                  ymin = .fitted - 1.96 * .se.fit, 
+                  ymax = .fitted + 1.96 * .se.fit), 
+              fill = colorc, 
+              data = predicted.distance, 
+              inherit.aes = FALSE, 
+              alpha = 0.25) +
+  scale_y_continuous(limits = c(min(log(sites_center$NumSpiders)) - 1, max(log(sites_center$NumSpiders)) + 0.1 * diff(range(log(sites_center$NumSpiders))))) +  
+  theme_classic() +
+  xlab("Plant Species Richness [log()]") +
+  ylab("Number of Spiders [log()]") + 
+  theme(text = element_text(size = 10)) + 
+  theme(axis.text.x = element_text(colour = "black", size = 10)) + 
+  theme(axis.text.y = element_text(colour = "black", size = 10)) +
+  theme(axis.text.x = element_blank(), 
+        axis.title.x = element_blank(),
+        axis.text.y = element_blank(),
+        axis.title.y = element_blank()) +
+  annotate(geom = "text", x = min((predicted.distance$log_TotalSub)) + diff(range((predicted.distance$log_TotalSub)))/2, y = max(log(sites_center$NumSpiders)), label = "***", color = "black", size = 4)
+
+# Patch Area
+nd <- data.frame(log_TotalSub = mean(sites_center$log_TotalSub), 
+                 log_patch = seq(4.34, 7.52, 0.025),
+                 road_length_m = mean(sites_center$road_length_m),
+                 log_tdh = mean(sites_center$log_tdh))
+predicted.distance <- augment(top_model_ns_c, 
+                              newdata = nd, 
+                              se_fit = TRUE)
+spiders_center_patch <- ggplot(sites_center, aes(x = log_patch, y = log(NumSpiders))) + 
+  geom_point(color = "grey", 
+             size = 1) +
+  geom_line(aes(x = log_patch, y = .fitted), 
+            size = 1, 
+            color = colorc, 
+            data = predicted.distance) + 
+  geom_ribbon(aes(x = log_patch, 
+                  ymin = .fitted - 1.96 * .se.fit, 
+                  ymax = .fitted + 1.96 * .se.fit), 
+              fill = colorc, 
+              data = predicted.distance, 
+              inherit.aes = FALSE, 
+              alpha = 0.25) +
+  scale_y_continuous(limits = c(min(log(sites_center$NumSpiders)) - 1, max(log(sites_center$NumSpiders)) + 0.15 * diff(range(log(sites_center$NumSpiders))))) +  
+  theme_classic() +
+  xlab("Patch Area [log(mm²)]") +
+  ylab("Number of Spiders [log()]") + 
+  theme(text = element_text(size = 10)) + 
+  theme(axis.text.x = element_text(colour = "black", size = 10)) + 
+  theme(axis.text.y = element_text(colour = "black", size = 10)) +
+  theme(axis.text.x = element_blank(), 
+        axis.title.x = element_blank(),
+        axis.text.y = element_blank(),
+        axis.title.y = element_blank()) +
+  annotate(geom = "text", x = min((predicted.distance$log_patch)) + diff(range((predicted.distance$log_patch)))/2, y = max(log(sites_center$NumSpiders)), label = "**", color = "black", size = 4)
+
+# Highway Disturbance
+nd <- data.frame(log_TotalSub = mean(sites_center$log_TotalSub), 
+                 log_patch = mean(sites_center$log_patch),
+                 road_length_m = mean(sites_center$road_length_m),
+                 log_tdh = seq(3.32, 5.42, 0.02))
+predicted.distance <- augment(top_model_ns_c, 
+                              newdata = nd, 
+                              se_fit = TRUE)
+spiders_center_tdh <- ggplot(sites_center, aes(x = log_tdh, y = log(NumSpiders))) + 
+  geom_point(color = "grey", 
+             size = 1) +
+  geom_line(aes(x = log_tdh, y = .fitted), 
+            size = 1, 
+            color = colorc, 
+            data = predicted.distance) + 
+  geom_ribbon(aes(x = log_tdh, 
+                  ymin = .fitted - 1.96 * .se.fit, 
+                  ymax = .fitted + 1.96 * .se.fit), 
+              fill = colorc, 
+              data = predicted.distance, 
+              inherit.aes = FALSE, 
+              alpha = 0.25) +
+  scale_y_continuous(limits = c(min(log(sites_center$NumSpiders)) - 2, max(log(sites_center$NumSpiders)) + 0.1 * diff(range(log(sites_center$NumSpiders))))) +  
+  theme_classic() +
+  xlab("Highway Disturbance [log(vehicles/day/m)]") +
+  ylab("Number of Spiders [log()]") + 
+  theme(text = element_text(size = 10)) + 
+  theme(axis.text.x = element_text(colour = "black", size = 10)) + 
+  theme(axis.text.y = element_text(colour = "black", size = 10)) +
+  theme(axis.text.x = element_blank(), 
+        axis.title.x = element_blank(),
+        axis.text.y = element_blank(),
+        axis.title.y = element_blank()) +
+  annotate(geom = "text", x = min((predicted.distance$log_tdh)) + diff(range((predicted.distance$log_tdh)))/2, y = max(log(sites_center$NumSpiders)), label = "***", color = "black", size = 4)
+
+# Road Length
+nd <- data.frame(log_TotalSub = mean(sites_center$log_TotalSub), 
+                 log_patch = mean(sites_center$log_patch),
+                 road_length_m = seq(47, 136, 1),
+                 log_tdh = mean(sites_center$log_tdh))
+predicted.distance <- augment(top_model_ns_c, 
+                              newdata = nd, 
+                              se_fit = TRUE)
+spiders_center_road <- ggplot(sites_center, aes(x = (road_length_m), y = log(NumSpiders))) + 
+  geom_point(color = "grey", 
+             size = 1) +
+  geom_line(aes(x = (road_length_m), y = .fitted), 
+            size = 1, 
+            color = colorc, 
+            data = predicted.distance) + 
+  geom_ribbon(aes(x = (road_length_m), 
+                  ymin = .fitted - 1.96 * .se.fit, 
+                  ymax = .fitted + 1.96 * .se.fit), 
+              fill = colorc, 
+              data = predicted.distance, 
+              inherit.aes = FALSE, 
+              alpha = 0.25) +
+  scale_y_continuous(limits = c(min(log(sites_center$NumSpiders)) - 1, max(log(sites_center$NumSpiders)) + 0.1 * diff(range(log(sites_center$NumSpiders))))) +  
+  theme_classic() +
+  xlab("Total Road Length [m]") +
+  ylab("Number of Spiders [log()]") + 
+  theme(text = element_text(size = 10)) + 
+  theme(axis.text.x = element_text(colour = "black", size = 10)) + 
+  theme(axis.text.y = element_text(colour = "black", size = 10)) +
+  theme(axis.text.x = element_blank(), 
+        axis.title.x = element_blank(),
+        axis.text.y = element_blank(),
+        axis.title.y = element_blank()) +
+  annotate(geom = "text", x = min((predicted.distance$road_length_m)) + diff(range((predicted.distance$road_length_m)))/2, y = max(log(sites_center$NumSpiders)), label = "***", color = "black", size = 4)
+
+spiders_center_plant
+spiders_center_patch
+spiders_center_road
+spiders_center_tdh
+```
+
+### Number of Spiders by Land
+
+```{r spiders_land_stats}
+spiders_land <- glm(NumSpiders ~ Land, data = sites, family = poisson)
+summary(spiders_land)
+anova(spiders_land, test = "Chisq")
+comp <- glht(spiders_land, linfct = mcp(Land = "Tukey"))
+summary(comp)
+```
+
+```{r spiders_land_graph}
+sites <- sites %>% 
+  mutate(Land = fct_relevel(Land, "Deciduous Forest", 
+                            "Woody Wetlands", 
+                            "Urban, High", 
+                            "Urban, Medium", 
+                            "Urban, Low"))
+nd <- data.frame(Land = factor(levels(sites$Land)))
+predictions <- augment(spiders_land, newdata = nd, se_fit = TRUE, type.predict = "response")
+predictions <- predictions %>% 
+  rename("rate" = ".fitted", "SE" = ".se.fit")
+#predictions <- summary(emmeans(spiders_land, ~Land),type = "response")
+
+ggplot(sites, aes(x = Land, y = NumSpiders)) + 
+  geom_jitter(color = "grey", width = 0.1, size = 0.5) +
+  geom_point(aes(x = Land, y = rate, color = Land), size = 1, data = predictions) + 
+  geom_errorbar(aes(x = Land, 
+                  ymin = rate - SE, 
+                  ymax = rate + SE, color = Land), data = predictions, inherit.aes = FALSE, width = 0.25, size = 1) +
+  theme_classic() +
+  scale_color_manual(values = c("Deciduous Forest" = "#1b9e77", "Woody Wetlands" = "#1b9e77", "Urban, High" = "#d95f02", "Urban, Medium" = "#d95f02", "Urban, Low" = "#d95f02")) +
+  xlab("Land Cover Class") +
+  ylab("Number of Spiders") + 
+  theme(text = element_text(size = 10)) + 
+  theme(axis.text.x=element_text(colour="black", size=10)) + 
+  theme(axis.text.y=element_text(colour="black", size=10)) +
+  theme(legend.position = "none") +
+  theme(axis.text.x = element_text(angle = 90, vjust = 1, hjust=1)) +
+  annotate(geom="text", x=1, y=max(sites$NumSpiders), label="A", color="black", size = 3) +
+  annotate(geom="text", x=2, y=max(sites$NumSpiders), label="A", color="black", size = 3) +
+  annotate(geom="text", x=3, y=max(sites$NumSpiders), label="B", color="black", size = 3) +
+  annotate(geom="text", x=4, y=max(sites$NumSpiders), label="B", color="black", size = 3) +
+  annotate(geom="text", x=5, y=max(sites$NumSpiders), label="B", color="black", size = 3)
+```
+
+## Response Variable: Web Distance
+
+### Web Distance by Location
+
+```{r dist_location_stats}
+ggarrange(ggplot(web_dist, aes(x = RetreatDist)) +
+            geom_density(),
+          ggplot(web_dist, aes(x = log(RetreatDist))) +
+            geom_density(), ncol = 2)
+
+shapiro.test(web_dist$RetreatDist) # not normal
+shapiro.test(log(web_dist$RetreatDist)) # not normal
+
+dist <- glmer(round(RetreatDist, 0) ~ Location * factor(Neighbor) + (1 | ID), data = web_dist, family = poisson)
+summary(dist)
+
+dist2 <- lmer(log(RetreatDist) ~ Location * factor(Neighbor) + (1 | ID), data = web_dist)
+coefs <- data.frame(coef(summary(dist2)))
+coefs$p.z <- 2 * (1 - pnorm(abs(coefs$t.value)))
+coefs
+
+# Both methods yield similar results
+web_dist %>% 
+  group_by(Location) %>% 
+  summarize(mean = mean(RetreatDist),
+            se = plotrix::std.error(RetreatDist))
+```
+
+```{r dist_location_assumptions, echo = FALSE}
+# As is, Poisson
+test_dist <- augment(dist, data = web_dist)
+resid_dist <- ggplot(test_dist, aes(x = .fitted, y = .resid)) + 
+  geom_point() + 
+  geom_smooth() +
+  geom_hline(yintercept = 0) +
+  xlab("Fitted Values") +
+  ylab("Standardized \nResiduals") +
+  theme_classic() +
+  theme(text = element_text(size = 14, color = "black")) +
+  theme(axis.text.x=element_text(color="black", size=14)) + 
+  theme(axis.text.y=element_text(color="black", size=14))
+
+y <- quantile(test_dist$.resid, c(0.25, 0.75))
+x <- qnorm(c(0.25, 0.75))
+slope <- diff(y)/diff(x)
+int <- y[1L] - slope * x[1L]
+
+qq_dist <- ggplot(test_dist, aes(sample = .resid)) + 
+  stat_qq() + 
+  geom_abline(slope = slope, intercept = int) +
+  xlab("Theoretical Quantiles") +
+  ylab("Sample Quantiles") +
+  theme_classic() +
+  theme(text = element_text(size = 14, color = "black")) +
+  theme(axis.text.x=element_text(color="black", size=14)) + 
+  theme(axis.text.y=element_text(color="black", size=14))
+
+scaleloc_dist <- ggplot(test_dist, aes(x = .fitted, y = sqrt(abs(.resid)))) + 
+  geom_point() + 
+  geom_smooth() + 
+  geom_hline(yintercept = 0.83) +
+  xlab("Fitted Values") +
+  ylab("Sqrt Standardized \nResiduals") +
+  theme_classic() +
+  theme(text = element_text(size = 14, color = "black")) +
+  theme(axis.text.x=element_text(color="black", size=14)) + 
+  theme(axis.text.y=element_text(color="black", size=14))
+
+lev_dist <- ggplot(test_dist, aes(.hat, .resid)) +
+ geom_vline(colour = "black", xintercept = 0) +
+  geom_hline(colour = "black", yintercept = 0) +
+  geom_point(aes(size = .cooksd)) + geom_smooth(se = FALSE) +
+  xlab("Theoretical Quantiles") +
+  ylab("Sample Quantiles") +
+  labs(size = "Cook's \nDistance") +
+  theme_classic() +
+  theme(text = element_text(size = 14, color = "black")) +
+  theme(axis.text.x=element_text(color="black", size=14)) + 
+  theme(axis.text.y=element_text(color="black", size=14))
+
+ggarrange(resid_dist, qq_dist, scaleloc_dist, lev_dist, 
+          labels = c("A", "B", "C", "D"),
+          ncol = 2, nrow = 2)
+
+# Log-transformed, Normal
+test_dist2 <- augment(dist2, data = web_dist)
+resid_dist2 <- ggplot(test_dist2, aes(x = .fitted, y = .resid)) + 
+  geom_point() + 
+  geom_smooth() +
+  geom_hline(yintercept = 0) +
+  xlab("Fitted Values") +
+  ylab("Standardized \nResiduals") +
+  theme_classic() +
+  theme(text = element_text(size = 14, color = "black")) +
+  theme(axis.text.x=element_text(color="black", size=14)) + 
+  theme(axis.text.y=element_text(color="black", size=14))
+
+y <- quantile(test_dist2$.resid, c(0.25, 0.75))
+x <- qnorm(c(0.25, 0.75))
+slope <- diff(y)/diff(x)
+int <- y[1L] - slope * x[1L]
+
+qq_dist2 <- ggplot(test_dist2, aes(sample = .resid)) + 
+  stat_qq() + 
+  geom_abline(slope = slope, intercept = int) +
+  xlab("Theoretical Quantiles") +
+  ylab("Sample Quantiles") +
+  theme_classic() +
+  theme(text = element_text(size = 14, color = "black")) +
+  theme(axis.text.x=element_text(color="black", size=14)) + 
+  theme(axis.text.y=element_text(color="black", size=14))
+
+scaleloc_dist2 <- ggplot(test_dist2, aes(x = .fitted, y = sqrt(abs(.resid)))) + 
+  geom_point() + 
+  geom_smooth() + 
+  geom_hline(yintercept = 0.83) +
+  xlab("Fitted Values") +
+  ylab("Sqrt Standardized \nResiduals") +
+  theme_classic() +
+  theme(text = element_text(size = 14, color = "black")) +
+  theme(axis.text.x=element_text(color="black", size=14)) + 
+  theme(axis.text.y=element_text(color="black", size=14))
+
+lev_dist2 <- ggplot(test_dist2, aes(.hat, .resid)) +
+ geom_vline(colour = "black", xintercept = 0) +
+  geom_hline(colour = "black", yintercept = 0) +
+  geom_point(aes(size = .cooksd)) + geom_smooth(se = FALSE) +
+  xlab("Theoretical Quantiles") +
+  ylab("Sample Quantiles") +
+  labs(size = "Cook's \nDistance") +
+  theme_classic() +
+  theme(text = element_text(size = 14, color = "black")) +
+  theme(axis.text.x=element_text(color="black", size=14)) + 
+  theme(axis.text.y=element_text(color="black", size=14))
+
+ggarrange(resid_dist2, qq_dist2, scaleloc_dist2, lev_dist2, 
+          labels = c("A", "B", "C", "D"),
+          ncol = 2, nrow = 2)
+```
+
+```{r dist_location_graph, echo = FALSE}
+# raw data
+raw <- web_dist %>% 
+  group_by(Location, Neighbor) %>% 
+  summarise(mean = mean(RetreatDist),
+            se = plotrix::std.error(RetreatDist))
+
+raw_plot <- ggplot(web_dist, aes(x = Neighbor, y = RetreatDist)) + 
+  geom_jitter(color = "grey", width = 0.1) +
+  geom_point(aes(x = Neighbor, y = mean, color = Location), size = 2, data = raw) +
+  geom_line(aes(x = Neighbor, y = mean, group = Location), size = 2, data = raw, color = "grey") +
+  geom_errorbar(aes(x= Neighbor, 
+                    ymin = mean - se, 
+                    ymax = mean + se, 
+                    color = Location), data = raw, inherit.aes = FALSE, width = 0.15, size = 1.5) +
+    scale_color_manual(values = c("Urban Center" = "#d95f02", "Urban Forest" = "#1b9e77")) +
+    scale_x_discrete(labels=c("Urban Forest" = "Urban \nForest \nN = 10", "Urban Center" = "Urban \nCenter \nN = 12")) +
+    theme_classic() +
+    scale_y_continuous(limits = c(0, 1000), breaks = c(0, 200, 400, 600, 800, 1000)) +
+    xlab("Nearest Neighbors") +
+    ylab("Distance from Focal Web \nto Neighbor Web [cm]") + 
+    theme(text = element_text(size = 16)) + 
+    theme(axis.text.x = element_text(colour = "black", size = 16)) + 
+    theme(axis.text.y = element_text(colour = "black", size = 16)) +
+    ggtitle("Raw Data")
+
+# Non-transformed, poisson distribution
+variable_names <- list("1" = "Nearest Neighbor",
+                       "2" = "2nd Nearest Neighbor")
+variable_labeller <- function(variable,value){
+  return(variable_names[value])
+}
+predictions <- expand.grid(Location = levels(factor(web_dist$Location)), Neighbor = levels(factor(web_dist$Neighbor)))
+predictions$response <- predict(dist, newdata = predictions, se.fit = TRUE, re.form = NA, type = "response")
+
+myFunc <- function(mm) {
+    predict(mm, newdata = predictions, re.form = ~0, type = "response")
+}
+#bigBoot_dist_location <- bootMer(dist, myFunc, nsim = 1000)
+#saveRDS(bigBoot_dist_location, file = "bootstrapping/bigBoot_dist_location.Rds")
+bigBoot_dist_location <- readRDS("bootstrapping/bigBoot_dist_location.Rds")
+predSE <- t(apply(bigBoot_dist_location$t, MARGIN = 2, FUN = sd))
+predictions$SE <- predSE[1, ]
+#predictions2 <- summary(emmeans(dist, ~Location | Neighbor,type = "response"))
+
+poisson_plot <- ggplot(web_dist, aes(x = Neighbor, y = RetreatDist)) + 
+  geom_jitter(color = "grey", width = 0.1) +
+  geom_point(aes(x = Neighbor, y = response, color = Location), size = 2, data = predictions) + 
+  geom_line(aes(x = Neighbor, y = response, group = Location), size = 2, data = predictions, color = "grey") +
+  geom_errorbar(aes(x = Neighbor, 
+                  ymin = response - SE, 
+                  ymax = response + SE,
+                  color = Location), data = predictions, inherit.aes = FALSE, width = 0.15, size = 1.5) +
+  scale_color_manual(values = c("Urban Center" = "#d95f02", "Urban Forest" = "#1b9e77")) +
+  scale_x_discrete(labels=c("Urban Forest" = "Urban \nForest \nN = 10", "Urban Center" = "Urban \nCenter \nN = 12")) +
+  theme_classic() +
+  scale_y_continuous(limits = c(0, 1000), breaks = c(0, 200, 400, 600, 800, 1000)) +
+  xlab("Nearest Neighbors") +
+  ylab("Distance from Focal Web \nto Neighbor Web [cm]") + 
+  theme(text = element_text(size = 16)) + 
+  theme(axis.text.x = element_text(colour = "black", size = 16)) + 
+  theme(axis.text.y = element_text(colour = "black", size = 16)) +
+  ggtitle("Poisson Distribution")
+
+# Let's look at the log-transformed response variable since that is normal
+variable_names <- list("1" = "Nearest Neighbor",
+                       "2" = "2nd Nearest Neighbor")
+variable_labeller <- function(variable,value){
+  return(variable_names[value])
+}
+predictions <- expand.grid(Location = levels(factor(web_dist$Location)), Neighbor = levels(factor(web_dist$Neighbor)))
+predictions$response <- predict(dist2, newdata = predictions, se.fit = TRUE, re.form = NA, type = "response")
+
+myFunc <- function(mm) {
+    predict(mm, newdata = predictions, re.form = ~0, type = "response")
+}
+#bigBoot_dist_location2 <- bootMer(dist2, myFunc, nsim = 1000)
+#saveRDS(bigBoot_dist_location2, file = "bootstrapping/bigBoot_dist_location2.Rds")
+bigBoot_dist_location2 <- readRDS("bootstrapping/bigBoot_dist_location2.Rds")
+predSE <- t(apply(bigBoot_dist_location2$t, MARGIN = 2, FUN = sd))
+predictions$SE <- predSE[1, ]
+#predictions2 <- summary(emmeans(dist2, ~Location | Neighbor,type = "response"))
+
+log_plot <- ggplot(web_dist, aes(x = Neighbor, y = (RetreatDist))) + 
+  geom_jitter(color = "grey", width = 0.1) +
+  geom_point(aes(x = Neighbor, y = exp(response), color = Location), size = 2, data = predictions) + 
+  geom_line(aes(x = Neighbor, y = exp(response), group = Location), size = 2, data = predictions, color = "grey") +
+  geom_errorbar(aes(x = Neighbor, 
+                  ymin = exp(response - SE), 
+                  ymax = exp(response + SE),
+                  color = Location), data = predictions, inherit.aes = FALSE, width = 0.15, size = 1.5) +
+  scale_color_manual(values = c("Urban Center" = "#d95f02", "Urban Forest" = "#1b9e77")) +
+  scale_x_discrete(labels=c("Urban Forest" = "Urban \nForest \nN = 10", "Urban Center" = "Urban \nCenter \nN = 12")) +
+  theme_classic() +
+  scale_y_continuous(limits = c(0, 1000), breaks = c(0, 200, 400, 600, 800, 1000)) +
+  xlab("Nearest Neighbors") +
+  ylab("Distance from Focal Web \nto Neighbor Web [cm]") + 
+  theme(text = element_text(size = 16)) + 
+  theme(axis.text.x = element_text(colour = "black", size = 16)) + 
+  theme(axis.text.y = element_text(colour = "black", size = 16)) +
+  ggtitle("Log-Transformed")
+
+ggarrange(raw_plot, poisson_plot, log_plot, nrow = 1, common.legend = TRUE)
+```
+
+### Web Distance by Predictors
+
+To look at the predictors, we will restrict to just the nearest neighbor instead of the nearest and second nearest neighbor.
+
+```{r dist_predictors_stats}
+near <- web_dist %>% 
+  filter(Neighbor == 1)
+
+#overall
+models = list(round(RetreatDist,0) ~ 1,
+              round(RetreatDist,0) ~ log_TotalSub,
+              round(RetreatDist,0) ~ log_tdr, 
+              round(RetreatDist,0) ~ log_tdh,
+              round(RetreatDist,0) ~ log_TotalSub + log_tdr,
+              round(RetreatDist,0) ~ log_TotalSub + log_tdh,
+              round(RetreatDist,0) ~ log_tdr + log_tdh,
+              round(RetreatDist,0) ~ log_TotalSub + log_tdr + log_tdh)
+fits = lapply(models, glm, data = near, family = "poisson")
+modnames = sapply(models, function(ff)deparse(ff[[3]]))
+pander(aictab(fits, modname = modnames), caption="Table 1. AICc model selection table for Search Distance to the Focal Web.", split.tables = Inf)
+
+global <- glm(round(RetreatDist, 0) ~ log_TotalSub + log_tdr + log_tdh, data = near, family = poisson)
+options(na.action = "na.fail") # Required for dredge to run
+model_dredge <- dredge(global, beta = F, evaluate = T, rank = AICc)
+options(na.action = "na.omit") # set back to default
+top_model_wd_o <- get.models(model_dredge, subset = 1)[[1]]
+out <- summary(top_model_wd_o)
+out
+info <- out[[12]]
+# TotalSub
+exp(info[3, 1])
+exp(info[3, 2])
+#Traffic_Dist_Road
+exp(info[2, 1])
+exp(info[2, 1])
+
+with(summary(top_model_wd_o), 1 - deviance/null.deviance)
+model.sel(model_dredge) #estimates same signs
+#summary(model.avg(model_dredge, subset = delta <= 2))
+car::vif(get.models(model_dredge, 5)[[1]]) # looking for less than 2
+
+# Urban Forest
+global <- glm(round(RetreatDist, 0) ~ tree100m + log_TotalSub + log_tdr + log_tdh + log_patch, data = near, family = poisson)
+options(na.action = "na.fail") # Required for dredge to run
+model_dredge <- dredge(global, beta = F, evaluate = T, rank = AICc)
+options(na.action = "na.omit") # set back to default
+top_model_wd_f <- get.models(model_dredge, subset = 1)[[1]]
+out <- summary(top_model_wd_f)
+out
+info <- out[[12]]
+#tree100m
+info[6, 1]
+info[6, 2]
+#TotalSub
+-exp(info[5, 1])
+exp(info[5, 2])
+#Road
+exp(info[4, 1])
+exp(info[4, 2])
+#Highway
+exp(info[3, 1])
+exp(info[3, 2])
+
+with(summary(top_model_wd_f), 1 - deviance/null.deviance)
+model.sel(model_dredge) #estimates same signs
+#summary(model.avg(model_dredge, subset = delta <= 2))
+car::vif(get.models(model_dredge, 1)[[1]]) # all but log_tdh over 2
+
+# This means there is quite a bit of multicollinearity. Let's try removing the variable with the highest vif.
+global2 <- update(global, .~. -tree100m)
+options(na.action = "na.fail") # Required for dredge to run
+model_dredge <- dredge(global2, beta = F, evaluate = T, rank = AICc)
+options(na.action = "na.omit") # set back to default
+top_model_wd_f <- get.models(model_dredge, subset = 1)[[1]]
+out <- summary(top_model_wd_f)
+out
+info <- out[[12]]
+# patch
+exp(info[2, 1])
+exp(info[2, 2])
+# tdr
+exp(info[4, 1])
+exp(info[4, 2])
+#tdh
+exp(info[3, 1])
+exp(info[3, 2])
+with(summary(top_model_wd_f), 1 - deviance/null.deviance)
+model.sel(model_dredge) #estimates same signs
+out <- summary(model.avg(model_dredge, subset = delta <= 2))
+out
+info <- out[[12]]
+#patch
+exp(info[2, 1])
+exp(info[2, 2])
+#tdh
+exp(info[3, 1])
+exp(info[3, 2])
+#tdr
+exp(info[4, 1])
+exp(info[4, 2])
+#TotalSub
+exp(info[5, 1])
+exp(info[5, 2])
+car::vif(get.models(model_dredge, 1)[[1]]) # looking for less than 2
+
+# Urban Center
+global <- glm(round(RetreatDist, 0) ~ log_TotalSub + log_tdr + log_tdh + spec_rad + log_patch + road_length_m, data = near, family = poisson)
+options(na.action = "na.fail") # Required for dredge to run
+model_dredge <- dredge(global, beta = F, evaluate = T, rank = AICc)
+options(na.action = "na.omit") # set back to default
+top_model_wd_c <- get.models(model_dredge, subset = 1)[[1]]
+out <- summary(top_model_wd_c)
+out
+info <- out[[12]]
+#TotalSub
+exp(info[5, 1])
+exp(info[5, 2])
+#tdr
+exp(info[4, 1])
+exp(info[4, 2])
+#tdh
+exp(info[3, 1])
+exp(info[3, 2])
+#log_patch
+exp(info[2, 1])
+exp(info[2, 2])
+#spec_rad
+info[7, 1]
+info[7, 2]
+#road_length_m
+info[6, 1]
+info[6, 2]
+
+with(summary(top_model_wd_c), 1 - deviance/null.deviance)
+model.sel(model_dredge) #estimates same signs
+#summary(model.avg(model_dredge, subset = delta <= 2))
+car::vif(get.models(model_dredge, 1)[[1]]) #all except tdh above 2
+
+# This means there is quite a bit of multicollinearity. Let's try removing the variable with the highest vif.
+
+global2 <- update(global, .~. -spec_rad)
+options(na.action = "na.fail") # Required for dredge to run
+model_dredge <- dredge(global2, beta = F, evaluate = T, rank = AICc)
+options(na.action = "na.omit") # set back to default
+top_model_wd_c <- get.models(model_dredge, subset = 1)[[1]]
+out <- summary(top_model_wd_c)
+out
+info <- out[[12]]
+car::vif(get.models(model_dredge, 1)[[1]])
+
+# Still pretty high VIF values. Let's remove another
+
+global3 <- update(global2, .~. -road_length_m)
+options(na.action = "na.fail") # Required for dredge to run
+model_dredge <- dredge(global3, beta = F, evaluate = T, rank = AICc)
+options(na.action = "na.omit") # set back to default
+top_model_wd_c <- get.models(model_dredge, subset = 1)[[1]]
+out <- summary(top_model_wd_c)
+out
+info <- out[[12]]
+# patch
+exp(info[2, 1])
+exp(info[2, 2])
+# tdh
+exp(info[3, 1])
+exp(info[3, 2])
+# tdr
+exp(info[4, 1])
+exp(info[4, 2])
+with(summary(top_model_wd_c), 1 - deviance/null.deviance)
+model.sel(model_dredge) #estimates same signs
+out <- summary(model.avg(model_dredge, subset = delta <= 2))
+out
+car::vif(get.models(model_dredge, 1)[[1]]) #looks better
+```
+
+*Overall*
+Coefficients:
+             Estimate Std. Error z value Pr(>|z|)    
+(Intercept)   5.38311    0.06200   86.83   <2e-16 ***
+log_tdr      -0.18279    0.01024  -17.84   <2e-16 *** *negative*
+log_TotalSub  0.57484    0.01653   34.78   <2e-16 *** *positive*
+
+R-squared = 0.3424213
+
+*Urban Forest*
+Coefficients:
+            Estimate Std. Error z value Pr(>|z|)    
+(Intercept) 0.236708   0.223087   1.061    0.289    
+log_patch   0.397613   0.009388  42.354  < 2e-16 *** *positive*
+log_tdh     0.422293   0.033427  12.633  < 2e-16 *** *positive*
+log_tdr     0.066877   0.012460   5.367 7.99e-08 *** *positive*
+
+R-squared = 0.5431401
+
+(conditional average) 
+             Estimate Std. Error Adjusted SE z value Pr(>|z|)    
+(Intercept)   0.21444    0.22610     0.24357   0.880    0.379    
+log_patch     0.40265    0.01246     0.01319  30.529   <2e-16 *** *positive*
+log_tdh       0.42115    0.03350     0.03612  11.660   <2e-16 *** *positive*
+log_tdr       0.06930    0.01307     0.01405   4.933    8e-07 *** *positive*
+log_TotalSub -0.03964    0.02482     0.02684   1.477    0.140     *negative*
+
+*Urban Center*
+Coefficients:
+            Estimate Std. Error z value Pr(>|z|)    
+(Intercept) 0.236708   0.223087   1.061    0.289    
+log_patch   0.397613   0.009388  42.354  < 2e-16 *** *positive*
+log_tdh     0.422293   0.033427  12.633  < 2e-16 *** *positive*
+log_tdr     0.066877   0.012460   5.367 7.99e-08 *** *positive*
+
+R-squared = 0.5431401
+
+(conditional average) 
+             Estimate Std. Error Adjusted SE z value Pr(>|z|)    
+(Intercept)   0.21444    0.22610     0.24357   0.880    0.379    
+log_patch     0.40265    0.01246     0.01319  30.529   <2e-16 *** *positive*
+log_tdh       0.42115    0.03350     0.03612  11.660   <2e-16 *** *positive*
+log_tdr       0.06930    0.01307     0.01405   4.933    8e-07 *** *positive*
+log_TotalSub -0.03964    0.02482     0.02684   1.477    0.140     *negative*
+
+```{r dist_predictors_overall_graphs, echo = FALSE}
+colorc = "#d95f02" 
+colorf = "#1b9e77"
+coloro = "black"
+
+# Plant Species Richness
+nd <- data.frame(log_TotalSub = seq(0, 3.2, 0.03), 
+                 log_tdr = mean(near$log_tdr))
+predicted.distance <- augment(top_model_wd_o, 
+                              newdata = nd, 
+                              se_fit = TRUE)
+dist_plant <- ggplot(near, aes(x = log_TotalSub, y = log(RetreatDist))) + 
+  geom_point(color = "grey", 
+             size = 1) +
+  geom_line(aes(x = log_TotalSub, y = .fitted), 
+            size = 1, 
+            color = coloro, 
+            data = predicted.distance) + 
+  geom_ribbon(aes(x = log_TotalSub, 
+                  ymin = .fitted - 1.96 * .se.fit, 
+                  ymax = .fitted + 1.96 * .se.fit), 
+              fill = coloro, 
+              data = predicted.distance, 
+              inherit.aes = FALSE, 
+              alpha = 0.25) +
+  scale_y_continuous(limits = c(min(log(near$RetreatDist)), max(log(near$RetreatDist)) + 0.1 * diff(range(log(near$RetreatDist))))) +  
+  theme_classic() +
+  xlab("Plant Species Richness [log()]") +
+  ylab("Distance from Focal Web \nto Neighbor Web [log(cm)]") + 
+  theme(text = element_text(size = 10)) + 
+  theme(axis.text.x = element_text(colour = "black", size = 10)) + 
+  theme(axis.text.y = element_text(colour = "black", size = 10)) +
+  theme(axis.text.x = element_blank(), 
+        axis.title.x = element_blank(),
+        axis.text.y = element_blank(),
+        axis.title.y = element_blank()) +
+  annotate(geom = "text", x = min(predicted.distance$log_TotalSub) + diff(range(predicted.distance$log_TotalSub))/2, y = max(log(near$RetreatDist)), label = "***", color = "black", size = 4)
+
+# Road Disturbance
+nd <- data.frame(log_TotalSub = mean(near$log_TotalSub), 
+                 log_tdr = seq(2.7, 7.3, 0.05))
+predicted.distance <- augment(top_model_wd_o, 
+                              newdata = nd, 
+                              se_fit = TRUE)
+dist_tdr <- ggplot(near, aes(x = log_tdr, y = log(RetreatDist))) + 
+  geom_point(color = "grey", 
+             size = 1) +
+  geom_line(aes(x = log_tdr, y = .fitted), 
+            size = 1, 
+            color = coloro, 
+            data = predicted.distance) + 
+  geom_ribbon(aes(x = log_tdr, 
+                  ymin = .fitted - 1.96 * .se.fit, 
+                  ymax = .fitted + 1.96 * .se.fit), 
+              fill = coloro, 
+              data = predicted.distance, 
+              inherit.aes = FALSE, 
+              alpha = 0.25) +
+  scale_y_continuous(limits = c(min(log(near$RetreatDist)), max(log(near$RetreatDist)) + 0.1 * diff(range(log(near$RetreatDist))))) +  
+  theme_classic() +
+  xlab("Road Disturbance [log(vehicles/day/m)]") +
+  ylab("Distance from Focal Web \nto Neighbor Web [log(cm)]") + 
+  theme(text = element_text(size = 10)) + 
+  theme(axis.text.x = element_text(colour = "black", size = 10)) + 
+  theme(axis.text.y = element_text(colour = "black", size = 10)) +
+  theme(axis.text.x = element_blank(), 
+        axis.title.x = element_blank(),
+        axis.text.y = element_blank(),
+        axis.title.y = element_blank()) +
+  annotate(geom = "text", x = min((predicted.distance$log_tdr)) + diff(range((predicted.distance$log_tdr)))/2, y = max(log(near$RetreatDist)), label = "***", color = "black", size = 4)
+
+dist_plant
+dist_tdr
+```
+
+```{r dist_predictors_forest_graphs, echo = FALSE}
+colorc = "#d95f02" 
+colorf = "#1b9e77"
+coloro = "black"
+
+# Patch Area
+nd <- data.frame(log_patch = seq(4.34, 11.78, 0.07), 
+                 log_tdr = mean(near$log_tdr),
+                 log_tdh = mean(near$log_tdh))
+predicted.distance <- augment(top_model_wd_f, 
+                              newdata = nd, 
+                              se_fit = TRUE)
+dist_forest_patch <- ggplot(near, aes(x = log_patch, y = log(RetreatDist))) + 
+  geom_point(color = "grey", 
+             size = 1) +
+  geom_line(aes(x = log_patch, y = .fitted), 
+            size = 1, 
+            color = colorf, 
+            data = predicted.distance) + 
+  geom_ribbon(aes(x = log_patch, 
+                  ymin = .fitted - 1.96 * .se.fit, 
+                  ymax = .fitted + 1.96 * .se.fit), 
+              fill = colorf, 
+              data = predicted.distance, 
+              inherit.aes = FALSE, 
+              alpha = 0.25) +
+  scale_y_continuous(limits = c(min(log(near$RetreatDist)), max(log(near$RetreatDist)) + 0.1 * diff(range(log(near$RetreatDist))))) +  
+  theme_classic() +
+  xlab("Patch Area [log(mm²)]") +
+  ylab("Distance from Focal Web \nto Neighbor Web [log(cm)]") + 
+  theme(text = element_text(size = 10)) + 
+  theme(axis.text.x = element_text(colour = "black", size = 10)) + 
+  theme(axis.text.y = element_text(colour = "black", size = 10)) +
+  theme(axis.text.x = element_blank(), 
+        axis.title.x = element_blank(),
+        axis.text.y = element_blank(),
+        axis.title.y = element_blank()) +
+  annotate(geom = "text", x = min(predicted.distance$log_patch) + diff(range(predicted.distance$log_patch))/2, y = max(log(near$RetreatDist)), label = "***", color = "black", size = 4)
+
+# Highway Disturbance
+nd <- data.frame(log_patch = mean(near$log_patch), 
+                 log_tdr = mean(near$log_tdr),
+                 log_tdh = seq(2.76, 5.42, 0.025))
+predicted.distance <- augment(top_model_wd_f, 
+                              newdata = nd, 
+                              se_fit = TRUE)
+dist_forest_tdh <- ggplot(near, aes(x = log_tdh, y = log(RetreatDist))) + 
+  geom_point(color = "grey", 
+             size = 1) +
+  geom_line(aes(x = log_tdh, y = .fitted), 
+            size = 1, 
+            color = colorf, 
+            data = predicted.distance) + 
+  geom_ribbon(aes(x = log_tdh, 
+                  ymin = .fitted - 1.96 * .se.fit, 
+                  ymax = .fitted + 1.96 * .se.fit), 
+              fill = colorf, 
+              data = predicted.distance, 
+              inherit.aes = FALSE, 
+              alpha = 0.25) +
+  scale_y_continuous(limits = c(min(log(near$RetreatDist)), max(log(near$RetreatDist)) + 0.1 * diff(range(log(near$RetreatDist))))) +  
+  theme_classic() +
+  xlab("Highway Disturbance [log(vehicles/day/m)]") +
+  ylab("Distance from Focal Web \nto Neighbor Web [log(cm)]") + 
+  theme(text = element_text(size = 10)) + 
+  theme(axis.text.x = element_text(colour = "black", size = 10)) + 
+  theme(axis.text.y = element_text(colour = "black", size = 10)) +
+  theme(axis.text.x = element_blank(), 
+        axis.title.x = element_blank(),
+        axis.text.y = element_blank(),
+        axis.title.y = element_blank()) +
+  annotate(geom = "text", x = min((predicted.distance$log_tdh)) + diff(range((predicted.distance$log_tdh)))/2, y = max(log(near$RetreatDist)), label = "***", color = "black", size = 4)
+
+# Road Disturbance
+nd <- data.frame(log_patch = mean(near$log_patch), 
+                 log_tdr = seq(2.73, 7.22, 0.05),
+                 log_tdh = mean(near$log_tdh))
+predicted.distance <- augment(top_model_wd_f, 
+                              newdata = nd, 
+                              se_fit = TRUE)
+dist_forest_tdr <- ggplot(near, aes(x = log_tdr, y = log(RetreatDist))) + 
+  geom_point(color = "grey", 
+             size = 1) +
+  geom_line(aes(x = log_tdr, y = .fitted), 
+            size = 1, 
+            color = colorf, 
+            data = predicted.distance) + 
+  geom_ribbon(aes(x = log_tdr, 
+                  ymin = .fitted - 1.96 * .se.fit, 
+                  ymax = .fitted + 1.96 * .se.fit), 
+              fill = colorf, 
+              data = predicted.distance, 
+              inherit.aes = FALSE, 
+              alpha = 0.25) +
+  scale_y_continuous(limits = c(min(log(near$RetreatDist)), max(log(near$RetreatDist)) + 0.1 * diff(range(log(near$RetreatDist))))) +  
+  theme_classic() +
+  xlab("Road Disturbance [log(vehicles/day/m)]") +
+  ylab("Distance from Focal Web \nto Neighbor Web [log(cm)]") + 
+  theme(text = element_text(size = 10)) + 
+  theme(axis.text.x = element_text(colour = "black", size = 10)) + 
+  theme(axis.text.y = element_text(colour = "black", size = 10)) +
+  theme(axis.text.x = element_blank(), 
+        axis.title.x = element_blank(),
+        axis.text.y = element_blank(),
+        axis.title.y = element_blank()) +
+  annotate(geom = "text", x = min((predicted.distance$log_tdr)) + diff(range((predicted.distance$log_tdr)))/2, y = max(log(near$RetreatDist)), label = "***", color = "black", size = 4)
+
+dist_forest_patch
+dist_forest_tdr
+dist_forest_tdh
+```
+
+```{r dist_predictors_center_graphs, echo = FALSE}
+colorc = "#d95f02" 
+colorf = "#1b9e77"
+coloro = "black"
+
+# Patch Area
+nd <- data.frame(log_patch = seq(4.34, 11.78, 0.07), 
+                 log_tdr = mean(near$log_tdr),
+                 log_tdh = mean(near$log_tdh))
+predicted.distance <- augment(top_model_wd_c, 
+                              newdata = nd, 
+                              se_fit = TRUE)
+dist_forest_patch <- ggplot(near, aes(x = log_patch, y = log(RetreatDist))) + 
+  geom_point(color = "grey", 
+             size = 1) +
+  geom_line(aes(x = log_patch, y = .fitted), 
+            size = 1, 
+            color = colorc, 
+            data = predicted.distance) + 
+  geom_ribbon(aes(x = log_patch, 
+                  ymin = .fitted - 1.96 * .se.fit, 
+                  ymax = .fitted + 1.96 * .se.fit), 
+              fill = colorc, 
+              data = predicted.distance, 
+              inherit.aes = FALSE, 
+              alpha = 0.25) +
+  scale_y_continuous(limits = c(min(log(near$RetreatDist)), max(log(near$RetreatDist)) + 0.1 * diff(range(log(near$RetreatDist))))) +  
+  theme_classic() +
+  xlab("Patch Area [log(mm²)]") +
+  ylab("Distance from Focal Web \nto Neighbor Web [log(cm)]") + 
+  theme(text = element_text(size = 10)) + 
+  theme(axis.text.x = element_text(colour = "black", size = 10)) + 
+  theme(axis.text.y = element_text(colour = "black", size = 10)) +
+  theme(axis.text.x = element_blank(), 
+        axis.title.x = element_blank(),
+        axis.text.y = element_blank(),
+        axis.title.y = element_blank()) +
+  annotate(geom = "text", x = min(predicted.distance$log_patch) + diff(range(predicted.distance$log_patch))/2, y = max(log(near$RetreatDist)), label = "***", color = "black", size = 4)
+
+# Highway Disturbance
+nd <- data.frame(log_patch = mean(near$log_patch), 
+                 log_tdr = mean(near$log_tdr),
+                 log_tdh = seq(2.76, 5.42, 0.025))
+predicted.distance <- augment(top_model_wd_c, 
+                              newdata = nd, 
+                              se_fit = TRUE)
+dist_forest_tdh <- ggplot(near, aes(x = log_tdh, y = log(RetreatDist))) + 
+  geom_point(color = "grey", 
+             size = 1) +
+  geom_line(aes(x = log_tdh, y = .fitted), 
+            size = 1, 
+            color = colorc, 
+            data = predicted.distance) + 
+  geom_ribbon(aes(x = log_tdh, 
+                  ymin = .fitted - 1.96 * .se.fit, 
+                  ymax = .fitted + 1.96 * .se.fit), 
+              fill = colorc, 
+              data = predicted.distance, 
+              inherit.aes = FALSE, 
+              alpha = 0.25) +
+  scale_y_continuous(limits = c(min(log(near$RetreatDist)), max(log(near$RetreatDist)) + 0.1 * diff(range(log(near$RetreatDist))))) +  
+  theme_classic() +
+  xlab("Highway Disturbance [log(vehicles/day/m)]") +
+  ylab("Distance from Focal Web \nto Neighbor Web [log(cm)]") + 
+  theme(text = element_text(size = 10)) + 
+  theme(axis.text.x = element_text(colour = "black", size = 10)) + 
+  theme(axis.text.y = element_text(colour = "black", size = 10)) +
+  theme(axis.text.x = element_blank(), 
+        axis.title.x = element_blank(),
+        axis.text.y = element_blank(),
+        axis.title.y = element_blank()) +
+  annotate(geom = "text", x = min((predicted.distance$log_tdh)) + diff(range((predicted.distance$log_tdh)))/2, y = max(log(near$RetreatDist)), label = "***", color = "black", size = 4)
+
+# Road Disturbance
+nd <- data.frame(log_patch = mean(near$log_patch), 
+                 log_tdr = seq(2.73, 7.22, 0.05),
+                 log_tdh = mean(near$log_tdh))
+predicted.distance <- augment(top_model_wd_c, 
+                              newdata = nd, 
+                              se_fit = TRUE)
+dist_forest_tdr <- ggplot(near, aes(x = log_tdr, y = log(RetreatDist))) + 
+  geom_point(color = "grey", 
+             size = 1) +
+  geom_line(aes(x = log_tdr, y = .fitted), 
+            size = 1, 
+            color = colorc, 
+            data = predicted.distance) + 
+  geom_ribbon(aes(x = log_tdr, 
+                  ymin = .fitted - 1.96 * .se.fit, 
+                  ymax = .fitted + 1.96 * .se.fit), 
+              fill = colorc, 
+              data = predicted.distance, 
+              inherit.aes = FALSE, 
+              alpha = 0.25) +
+  scale_y_continuous(limits = c(min(log(near$RetreatDist)), max(log(near$RetreatDist)) + 0.1 * diff(range(log(near$RetreatDist))))) +  
+  theme_classic() +
+  xlab("Road Disturbance [log(vehicles/day/m)]") +
+  ylab("Distance from Focal Web \nto Neighbor Web [log(cm)]") + 
+  theme(text = element_text(size = 10)) + 
+  theme(axis.text.x = element_text(colour = "black", size = 10)) + 
+  theme(axis.text.y = element_text(colour = "black", size = 10)) +
+  theme(axis.text.x = element_blank(), 
+        axis.title.x = element_blank(),
+        axis.text.y = element_blank(),
+        axis.title.y = element_blank()) +
+  annotate(geom = "text", x = min((predicted.distance$log_tdr)) + diff(range((predicted.distance$log_tdr)))/2, y = max(log(near$RetreatDist)), label = "***", color = "black", size = 4)
+
+dist_forest_patch
+dist_forest_tdr
+dist_forest_tdh
+```
+
+### Web Distance by Land
+
+```{r dist_land_stats}
+dist_land <- glm(round(RetreatDist, 0) ~ Land, data = near, family = poisson)
+summary(dist_land)
+anova(dist_land, test = "Chisq")
+comp <- glht(dist_land, linfct = mcp(Land = "Tukey"))
+summary(comp)
+```
+
+```{r dist_land_graph}
+near <- near %>% 
+  mutate(Land = fct_relevel(Land, "Deciduous Forest", 
+                            "Woody Wetlands", 
+                            "Urban, High", 
+                            "Urban, Medium", 
+                            "Urban, Low"))
+nd <- data.frame(Land = factor(levels(sites$Land)))
+predictions <- augment(dist_land, newdata = nd, se_fit = TRUE, type.predict = "response")
+predictions <- predictions %>% 
+  rename("response" = ".fitted", "SE" = ".se.fit")
+#predictions <- summary(emmeans(dist_land, ~Land),type = "response")
+
+ggplot(near, aes(x = Land, y = RetreatDist)) + 
+  geom_jitter(color = "grey", width = 0.1, size = 0.5) +
+  geom_point(aes(x = Land, y = response, color = Land), size = 1, data = predictions) + 
+  geom_errorbar(aes(x = Land, 
+                  ymin = response - SE, 
+                  ymax = response + SE, color = Land), data = predictions, inherit.aes = FALSE, width = 0.25, size = 1) +
+  theme_classic() +
+  scale_color_manual(values = c("Deciduous Forest" = "#1b9e77", "Woody Wetlands" = "#1b9e77", "Urban, High" = "#d95f02", "Urban, Medium" = "#d95f02", "Urban, Low" = "#d95f02")) +
+  xlab("Land Cover Class") +
+  ylab("Distance from Focal Web \nto Neighbor Web (cm)") + 
+  theme(text = element_text(size = 10)) + 
+  theme(axis.text.x=element_text(colour="black", size=10)) + 
+  theme(axis.text.y=element_text(colour="black", size=10)) +
+  theme(legend.position = "none") +
+  theme(axis.text.x = element_text(angle = 90, vjust = 1, hjust=1)) +
+  annotate(geom="text", x=1, y=max(sites$NumSpiders), label="A", color="black", size = 3) +
+  annotate(geom="text", x=2, y=max(sites$NumSpiders), label="B", color="black", size = 3) +
+  annotate(geom="text", x=3, y=max(sites$NumSpiders), label="C", color="black", size = 3) +
+  annotate(geom="text", x=4, y=max(sites$NumSpiders), label="D", color="black", size = 3) +
+  annotate(geom="text", x=5, y=max(sites$NumSpiders), label="E", color="black", size = 3)
+```
+
+## Response Variable: Web Height
+
+### Web Height by Location
+
+```{r height_location_stats}
+webs$RetreatHeight[webs$RetreatHeight == 0] <- 0.1
+ggarrange(ggplot(webs, aes(x = RetreatHeight)) +
+            geom_density(),
+          ggplot(webs, aes(x = log(RetreatHeight))) +
+            geom_density(), ncol = 2)
+
+shapiro.test(webs$RetreatHeight) # not normal
+shapiro.test(log(webs$RetreatHeight)) # not normal
+
+height <- glmer(round(RetreatHeight, 0) ~ Location + (1 | ID), data = webs, family = poisson)
+summary(height)
+height2 <- lmer(log(RetreatHeight) ~ Location + (1 | ID), data = webs)
+summary(height2)
+```
+
+```{r height_location_assumptions, echo = FALSE}
+# As is, Poisson
+test_height <- augment(height, data = webs)
+resid_height <- ggplot(test_height, aes(x = .fitted, y = .resid)) + 
+  geom_point() + 
+  geom_smooth() +
+  geom_hline(yintercept = 0) +
+  xlab("Fitted Values") +
+  ylab("Standardized \nResiduals") +
+  theme_classic() +
+  theme(text = element_text(size = 14, color = "black")) +
+  theme(axis.text.x=element_text(color="black", size=14)) + 
+  theme(axis.text.y=element_text(color="black", size=14))
+
+y <- quantile(test_height$.resid, c(0.25, 0.75))
+x <- qnorm(c(0.25, 0.75))
+slope <- diff(y)/diff(x)
+int <- y[1L] - slope * x[1L]
+
+qq_height <- ggplot(test_height, aes(sample = .resid)) + 
+  stat_qq() + 
+  geom_abline(slope = slope, intercept = int) +
+  xlab("Theoretical Quantiles") +
+  ylab("Sample Quantiles") +
+  theme_classic() +
+  theme(text = element_text(size = 14, color = "black")) +
+  theme(axis.text.x=element_text(color="black", size=14)) + 
+  theme(axis.text.y=element_text(color="black", size=14))
+
+scaleloc_height <- ggplot(test_height, aes(x = .fitted, y = sqrt(abs(.resid)))) + 
+  geom_point() + 
+  geom_smooth() + 
+  geom_hline(yintercept = 0.83) +
+  xlab("Fitted Values") +
+  ylab("Sqrt Standardized \nResiduals") +
+  theme_classic() +
+  theme(text = element_text(size = 14, color = "black")) +
+  theme(axis.text.x=element_text(color="black", size=14)) + 
+  theme(axis.text.y=element_text(color="black", size=14))
+
+lev_height <- ggplot(test_height, aes(.hat, .resid)) +
+ geom_vline(colour = "black", xintercept = 0) +
+  geom_hline(colour = "black", yintercept = 0) +
+  geom_point(aes(size = .cooksd)) + geom_smooth(se = FALSE) +
+  xlab("Theoretical Quantiles") +
+  ylab("Sample Quantiles") +
+  labs(size = "Cook's \nDistance") +
+  theme_classic() +
+  theme(text = element_text(size = 14, color = "black")) +
+  theme(axis.text.x=element_text(color="black", size=14)) + 
+  theme(axis.text.y=element_text(color="black", size=14))
+
+ggarrange(resid_height, qq_height, scaleloc_height, lev_height, 
+          labels = c("A", "B", "C", "D"),
+          ncol = 2, nrow = 2)
+
+# Log-transformed, Normal
+test_height2 <- augment(height2, data = webs)
+resid_height2 <- ggplot(test_height2, aes(x = .fitted, y = .resid)) + 
+  geom_point() + 
+  geom_smooth() +
+  geom_hline(yintercept = 0) +
+  xlab("Fitted Values") +
+  ylab("Standardized \nResiduals") +
+  theme_classic() +
+  theme(text = element_text(size = 14, color = "black")) +
+  theme(axis.text.x=element_text(color="black", size=14)) + 
+  theme(axis.text.y=element_text(color="black", size=14))
+
+y <- quantile(test_height2$.resid, c(0.25, 0.75))
+x <- qnorm(c(0.25, 0.75))
+slope <- diff(y)/diff(x)
+int <- y[1L] - slope * x[1L]
+
+qq_height2 <- ggplot(test_height2, aes(sample = .resid)) + 
+  stat_qq() + 
+  geom_abline(slope = slope, intercept = int) +
+  xlab("Theoretical Quantiles") +
+  ylab("Sample Quantiles") +
+  theme_classic() +
+  theme(text = element_text(size = 14, color = "black")) +
+  theme(axis.text.x=element_text(color="black", size=14)) + 
+  theme(axis.text.y=element_text(color="black", size=14))
+
+scaleloc_height2 <- ggplot(test_height2, aes(x = .fitted, y = sqrt(abs(.resid)))) + 
+  geom_point() + 
+  geom_smooth() + 
+  geom_hline(yintercept = 0.83) +
+  xlab("Fitted Values") +
+  ylab("Sqrt Standardized \nResiduals") +
+  theme_classic() +
+  theme(text = element_text(size = 14, color = "black")) +
+  theme(axis.text.x=element_text(color="black", size=14)) + 
+  theme(axis.text.y=element_text(color="black", size=14))
+
+lev_height2 <- ggplot(test_height2, aes(.hat, .resid)) +
+ geom_vline(colour = "black", xintercept = 0) +
+  geom_hline(colour = "black", yintercept = 0) +
+  geom_point(aes(size = .cooksd)) + geom_smooth(se = FALSE) +
+  xlab("Theoretical Quantiles") +
+  ylab("Sample Quantiles") +
+  labs(size = "Cook's \nDistance") +
+  theme_classic() +
+  theme(text = element_text(size = 14, color = "black")) +
+  theme(axis.text.x=element_text(color="black", size=14)) + 
+  theme(axis.text.y=element_text(color="black", size=14))
+
+ggarrange(resid_height2, qq_height2, scaleloc_height2, lev_height2, 
+          labels = c("A", "B", "C", "D"),
+          ncol = 2, nrow = 2)
+```
+
+```{r height_location_graph, echo = FALSE}
+# raw data
+raw <- webs %>% 
+  group_by(Location) %>% 
+  summarise(mean = mean(RetreatHeight),
+            se = plotrix::std.error(RetreatHeight))
+
+raw_plot <- ggplot(webs, aes(x = Location, y = RetreatHeight)) + 
+  geom_jitter(color = "grey", width = 0.1) +
+  geom_point(aes(x = Location, y = mean, color = Location), size = 2, data = raw) +
+  geom_errorbar(aes(x= Location, 
+                    ymin = mean - se, 
+                    ymax = mean + se, 
+                    color = Location), data = raw, inherit.aes = FALSE, width = 0.15, size = 1.5) +
+    scale_color_manual(values = c("Urban Center" = "#d95f02", "Urban Forest" = "#1b9e77")) +
+    scale_x_discrete(labels=c("Urban Forest" = "Urban \nForest \nN = 10", "Urban Center" = "Urban \nCenter \nN = 12")) +
+    theme_classic() +
+    scale_y_continuous(limits = c(0, 210), breaks = c(0, 35, 70, 105, 140, 175, 210)) +
+    ylab("Web Height [cm]") + 
+    theme(text = element_text(size = 16)) + 
+    theme(axis.text.x = element_text(colour = "black", size = 16)) + 
+    theme(axis.text.y = element_text(colour = "black", size = 16),
+        axis.title.x = element_blank()) +
+    theme(legend.position = "none") +
+    ggtitle("Raw Data")
+
+# Non-transformed, poisson distribution
+predictions <- expand.grid(Location = levels(factor(webs$Location)))
+predictions$response <- predict(height, newdata = predictions, se.fit = TRUE, re.form = NA, type = "response")
+
+myFunc <- function(mm) {
+    predict(mm, newdata = predictions, re.form = ~0, type = "response")
+}
+#bigBoot_height_location <- bootMer(height, myFunc, nsim = 1000)
+#saveRDS(bigBoot_height_location, file = "bootstrapping/bigBoot_height_location")
+bigBoot_height_location <- readRDS("bootstrapping/bigBoot_height_location")
+predSE <- t(apply(bigBoot_height_location$t, MARGIN = 2, FUN = sd))
+predictions$SE <- predSE[1, ]
+#predictions2 <- summary(emmeans(height, ~Location | Neighbor,type = "response"))
+
+poisson_plot <- ggplot(webs, aes(x = Location, y = RetreatHeight)) + 
+  geom_jitter(color = "grey", width = 0.1) +
+  geom_point(aes(x = Location, y = response, color = Location), size = 2, data = predictions) +
+  geom_errorbar(aes(x= Location, 
+                    ymin = response - SE, 
+                    ymax = response + SE, 
+                    color = Location), data = predictions, inherit.aes = FALSE, width = 0.15, size = 1.5) +
+    scale_color_manual(values = c("Urban Center" = "#d95f02", "Urban Forest" = "#1b9e77")) +
+    scale_x_discrete(labels=c("Urban Forest" = "Urban \nForest \nN = 10", "Urban Center" = "Urban \nCenter \nN = 12")) +
+    theme_classic() +
+    scale_y_continuous(limits = c(0, 210), breaks = c(0, 35, 70, 105, 140, 175, 210)) +
+    ylab("Web Height [cm]") + 
+    theme(text = element_text(size = 16)) + 
+    theme(axis.text.x = element_text(colour = "black", size = 16)) + 
+    theme(axis.text.y = element_text(colour = "black", size = 16),
+        axis.title.x = element_blank()) +
+    theme(legend.position = "none") +
+    ggtitle("Poisson Distribution")
+
+# Let's look at the log-transformed response variable since that is normal
+predictions <- expand.grid(Location = levels(factor(webs$Location)))
+predictions$response <- predict(height2, newdata = predictions, se.fit = TRUE, re.form = NA, type = "response")
+
+myFunc <- function(mm) {
+    predict(mm, newdata = predictions, re.form = ~0, type = "response")
+}
+#bigBoot_height_location2 <- bootMer(height2, myFunc, nsim = 1000)
+#saveRDS(bigBoot_height_location2, file = "bootstrapping/bigBoot_height_location2")
+bigBoot_height_location2 <- readRDS("bootstrapping/bigBoot_height_location2")
+predSE <- t(apply(bigBoot_height_location2$t, MARGIN = 2, FUN = sd))
+predictions$SE <- predSE[1, ]
+#predictions2 <- summary(emmeans(height2, ~Location | Neighbor,type = "response"))
+
+log_plot <- ggplot(webs, aes(x = Location, y = (RetreatHeight))) + 
+  geom_jitter(color = "grey", width = 0.1) +
+  geom_point(aes(x = Location, y = exp(response), color = Location), size = 2, data = predictions) +
+  geom_errorbar(aes(x= Location, 
+                    ymin = exp(response - SE), 
+                    ymax = exp(response + SE), 
+                    color = Location), data = predictions, inherit.aes = FALSE, width = 0.15, size = 1.5) +
+    scale_color_manual(values = c("Urban Center" = "#d95f02", "Urban Forest" = "#1b9e77")) +
+    scale_x_discrete(labels=c("Urban Forest" = "Urban \nForest \nN = 10", "Urban Center" = "Urban \nCenter \nN = 12")) +
+    theme_classic() +
+    scale_y_continuous(limits = c(0, 210), breaks = c(0, 35, 70, 105, 140, 175, 210)) +
+    ylab("Web Height [cm]") + 
+    theme(text = element_text(size = 16)) + 
+    theme(axis.text.x = element_text(colour = "black", size = 16)) + 
+    theme(axis.text.y = element_text(colour = "black", size = 16),
+        axis.title.x = element_blank()) +
+    theme(legend.position = "none") +
+    ggtitle("Log Transformation")
+
+ggarrange(raw_plot, poisson_plot, log_plot, nrow = 1, common.legend = TRUE)
+```
+
+### Web Height by Predictors
+
+Convergence issues that need addressed.
+
+```{r height_predictors_stats}
+#overall
+models = list(ceiling(RetreatHeight) ~ 1,
+              ceiling(RetreatHeight) ~ log_TotalSub,
+              ceiling(RetreatHeight) ~ log_tdr, 
+              ceiling(RetreatHeight) ~ log_tdh,
+              ceiling(RetreatHeight) ~ log_TotalSub + log_tdr,
+              ceiling(RetreatHeight) ~ log_TotalSub + log_tdh,
+              ceiling(RetreatHeight) ~ log_tdr + log_tdh,
+              ceiling(RetreatHeight) ~ log_TotalSub + log_tdr + log_tdh)
+fits = lapply(models, glm, data = webs, family = "poisson")
+modnames = sapply(models, function(ff)deparse(ff[[3]]))
+pander(aictab(fits, modname = modnames), caption="Table 1. AICc model selection table for Search Distance to the Focal Web.", split.tables = Inf)
+
+global <- glmer(ceiling(RetreatHeight) ~ log_TotalSub + log_tdr + log_tdh + (1 | ID), data = webs, family = poisson)
+options(na.action = "na.fail") # Required for dredge to run
+model_dredge <- dredge(global, beta = F, evaluate = T, rank = AICc)
+options(na.action = "na.omit") # set back to default
+top_model_wh_o <- get.models(model_dredge, subset = 1)[[1]]
+out <- summary(top_model_wh_o)
+out
+info <- out[[10]]
+# TotalSub
+exp(info[3, 1])
+exp(info[3, 2])
+#Traffic_Dist_Road
+exp(info[2, 1])
+exp(info[2, 1])
+
+r.squaredGLMM(top_model_wh_o) 
+model.sel(model_dredge) #estimates same signs
+out <- summary(model.avg(model_dredge, subset = delta <= 2))
+out
+info <- out[[10]]
+#tdr
+exp(info[2, 1])
+exp(info[2, 2])
+#TotalSub
+exp(info[3, 1])
+exp(info[3, 2])
+#tdh
+exp(info[4, 1])
+exp(info[4, 2])
+car::vif(get.models(model_dredge, 5)[[1]]) # looking for less than 2
+
+# Urban Forest
+global <- glmer(ceiling(RetreatHeight) ~ tree100m + log_TotalSub + log_tdr + log_tdh + log_patch + (1 | ID), data = webs, family = poisson)
+options(na.action = "na.fail") # Required for dredge to run
+model_dredge <- dredge(global, beta = F, evaluate = T, rank = AICc)
+options(na.action = "na.omit") # set back to default
+top_model_wh_f <- get.models(model_dredge, subset = 1)[[1]]
+out <- summary(top_model_wh_f)
+out
+info <- out[[10]]
+
+#TotalSub
+-exp(info[3, 1])
+exp(info[3, 2])
+#Road
+exp(info[2, 1])
+exp(info[2, 2])
+
+r.squaredGLMM(top_model_wh_f) 
+model.sel(model_dredge) #estimates same signs
+out <- summary(model.avg(model_dredge, subset = delta <= 2))
+out
+info <- out[[10]]
+#tdr
+exp(info[2, 1])
+exp(info[2, 2])
+#TotalSub
+exp(info[3, 1])
+exp(info[3, 2])
+#tdh
+exp(info[4, 1])
+exp(info[4, 2])
+#tree
+(info[5, 1])
+(info[5, 2])
+#patch
+exp(info[6, 1])
+exp(info[6, 2])
+car::vif(get.models(model_dredge, 1)[[1]]) # looking for less than 2
+
+# Urban Center
+global <- glmer(ceiling(RetreatHeight) ~ log_TotalSub + log_tdr + log_tdh + spec_rad + log_patch + road_length_m + (1 | ID), data = webs, family = poisson)
+options(na.action = "na.fail") # Required for dredge to run
+model_dredge <- dredge(global, beta = F, evaluate = T, rank = AICc)
+options(na.action = "na.omit") # set back to default
+top_model_wh_c <- get.models(model_dredge, subset = 1)[[1]]
+out <- summary(top_model_wh_c)
+out
+info <- out[[10]]
+#TotalSub
+exp(info[3, 1])
+exp(info[3, 2])
+#tdr
+exp(info[2, 1])
+exp(info[2, 2])
+
+r.squaredGLMM(top_model_wh_c) 
+model.sel(model_dredge) #estimates same signs
+out <- summary(model.avg(model_dredge, subset = delta <= 2))
+out
+info <- out[[10]]
+#tdr
+exp(info[2, 1])
+exp(info[2, 2])
+#TotalSub
+exp(info[3, 1])
+exp(info[3, 2])
+#tdh
+exp(info[4, 1])
+exp(info[4, 2])
+#patch
+exp(info[5, 1])
+exp(info[5, 2])
+#road length
+exp(info[6, 1])
+exp(info[6, 2])
+#spec_rad
+exp(info[7, 1])
+exp(info[7, 2])
+car::vif(get.models(model_dredge, 1)[[1]]) # looking for less than 2
+```
+
+*Overall* 
+Fixed effects:
+             Estimate Std. Error z value Pr(>|z|)    
+(Intercept)    3.1824     0.6117   5.202 1.97e-07 ***
+log_tdr       -0.1846     0.1007  -1.834  0.06665 .  
+log_TotalSub   0.4715     0.1633   2.888  0.00388 **
+
+R-squared = 0.3635599 (marginal - fixed) 0.9508324 (conditional - fixed and random)
+
+(conditional average) 
+             Estimate Std. Error Adjusted SE z value Pr(>|z|)   
+(Intercept)    3.3645     1.2653      1.2710   2.647  0.00812 **
+log_tdr       -0.1934     0.1006      0.1016   1.903  0.05703 . 
+log_TotalSub   0.4611     0.1784      0.1799   2.563  0.01038 * 
+log_tdh       -0.3226     0.2678      0.2704   1.193  0.23276
+
+*Urban Forest*
+Fixed effects:
+             Estimate Std. Error z value Pr(>|z|)    
+(Intercept)    3.1824     0.6117   5.202 1.97e-07 ***
+log_tdr       -0.1846     0.1007  -1.834  0.06665 .  
+log_TotalSub   0.4715     0.1633   2.888  0.00388 **
+
+R-squared = 0.3635599 (marginal - fixed) 0.9508324 (conditional - fixed and random)
+
+(conditional average) 
+              Estimate Std. Error Adjusted SE z value Pr(>|z|)  
+(Intercept)   3.479599   1.469543    1.475122   2.359   0.0183 *
+log_tdr      -0.213553   0.111308    0.112287   1.902   0.0572 .
+log_TotalSub  0.471545   0.218490    0.220246   2.141   0.0323 *
+log_tdh      -0.359085   0.274215    0.276807   1.297   0.1945  
+tree100m      0.015565   0.008560    0.008623   1.805   0.0711 .
+log_patch    -0.087858   0.099543    0.100463   0.875   0.3818
+
+*Urban Center*
+Fixed effects:
+             Estimate Std. Error z value Pr(>|z|)    
+(Intercept)    3.1824     0.6117   5.202 1.97e-07 ***
+log_tdr       -0.1846     0.1007  -1.834  0.06665 .  
+log_TotalSub   0.4715     0.1633   2.888  0.00388 **
+
+R-squared = 0.3635599 (marginal - fixed) 0.9508324 (conditional - fixed and random)
+
+(conditional average) 
+               Estimate Std. Error Adjusted SE z value Pr(>|z|)  
+(Intercept)    3.458641   2.160676    2.174189   1.591   0.1117  
+log_tdr       -0.212514   0.112355    0.113366   1.875   0.0609 .
+log_TotalSub   0.504709   0.216517    0.218399   2.311   0.0208 *
+log_tdh       -0.359085   0.274215    0.276807   1.297   0.1945  
+log_patch     -0.087858   0.099543    0.100463   0.875   0.3818  
+road_length_m  0.002237   0.004915    0.004962   0.451   0.6521  
+spec_rad       0.012420   0.030255    0.030548   0.407   0.6843
+
+### Web Height by Land

### 2022-11-23 data_analysis.Rmd
Finished analyzing the variables and fixing convergence issues; next step is to make the figures for the manuscript

@@
 options(na.action = "na.fail") # Required for dredge to run
-model_dredge <- dredge(global, beta = F, evaluate = T, rank = AICc)
+model_dredge <- dredge(global, beta = "none", evaluate = T, rank = AICc)
 options(na.action = "na.omit") # set back to default
@@
 options(na.action = "na.fail") # Required for dredge to run
-model_dredge <- dredge(global2, beta = F, evaluate = T, rank = AICc)
+model_dredge <- dredge(global2, beta = "none", evaluate = T, rank = AICc)
 options(na.action = "na.omit") # set back to default
@@
 options(na.action = "na.fail") # Required for dredge to run
-model_dredge <- dredge(global3, beta = F, evaluate = T, rank = AICc)
+model_dredge <- dredge(global3, beta = "none", evaluate = T, rank = AICc)
 options(na.action = "na.omit") # set back to default
@@
 #bigBoot_height_location <- bootMer(height, myFunc, nsim = 1000)
-#saveRDS(bigBoot_height_location, file = "bootstrapping/bigBoot_height_location")
-bigBoot_height_location <- readRDS("bootstrapping/bigBoot_height_location")
+#saveRDS(bigBoot_height_location, file = "bootstrapping/bigBoot_height_location.Rds")
+bigBoot_height_location <- readRDS("bootstrapping/bigBoot_height_location.Rds")
 predSE <- t(apply(bigBoot_height_location$t, MARGIN = 2, FUN = sd))
@@
 #bigBoot_height_location2 <- bootMer(height2, myFunc, nsim = 1000)
-#saveRDS(bigBoot_height_location2, file = "bootstrapping/bigBoot_height_location2")
-bigBoot_height_location2 <- readRDS("bootstrapping/bigBoot_height_location2")
+#saveRDS(bigBoot_height_location2, file = "bootstrapping/bigBoot_height_location2.Rds")
+bigBoot_height_location2 <- readRDS("bootstrapping/bigBoot_height_location2.Rds")
 predSE <- t(apply(bigBoot_height_location2$t, MARGIN = 2, FUN = sd))
@@
 
-global <- glmer(ceiling(RetreatHeight) ~ log_TotalSub + log_tdr + log_tdh + (1 | ID), data = webs, family = poisson)
+global <- glmer(round(RetreatHeight, 0) ~ log_TotalSub + log_tdr + log_tdh + (1 | ID), data = webs, family = poisson)
 options(na.action = "na.fail") # Required for dredge to run
-model_dredge <- dredge(global, beta = F, evaluate = T, rank = AICc)
+model_dredge <- dredge(global, beta = "none", evaluate = TRUE, rank = AICc)
 options(na.action = "na.omit") # set back to default
@@
 # Urban Forest
-global <- glmer(ceiling(RetreatHeight) ~ tree100m + log_TotalSub + log_tdr + log_tdh + log_patch + (1 | ID), data = webs, family = poisson)
+webs_forest <- webs_forest %>% 
+  mutate(tree100m_frac = I(tree100m/100))
+global <- glmer(round(RetreatHeight, 0) ~ tree100m_frac + log_TotalSub + log_tdr + log_tdh + log_patch + (1 | ID), data = webs_forest, family = poisson, control = glmerControl(optimizer = "bobyqa", optCtrl = list(maxfun = 2e4)))
 options(na.action = "na.fail") # Required for dredge to run
-model_dredge <- dredge(global, beta = F, evaluate = T, rank = AICc)
+model_dredge <- dredge(global, beta = "none", evaluate = TRUE, rank = AICc)
 options(na.action = "na.omit") # set back to default
@@
 
-#TotalSub
--exp(info[3, 1])
-exp(info[3, 2])
-#Road
+#tree
 exp(info[2, 1])
@@
 info <- out[[10]]
-#tdr
+#tree
 exp(info[2, 1])
@@
 exp(info[3, 2])
-#tdh
+#tdr
 exp(info[4, 1])
 exp(info[4, 2])
-#tree
-(info[5, 1])
-(info[5, 2])
-#patch
-exp(info[6, 1])
-exp(info[6, 2])
-car::vif(get.models(model_dredge, 1)[[1]]) # looking for less than 2
+
+#car::vif(get.models(model_dredge, 1)[[1]]) # looking for less than 2
 
 # Urban Center
-global <- glmer(ceiling(RetreatHeight) ~ log_TotalSub + log_tdr + log_tdh + spec_rad + log_patch + road_length_m + (1 | ID), data = webs, family = poisson)
+global <- glmer(round(RetreatHeight, 0) ~ log_TotalSub + log_tdr + log_tdh + scale(spec_rad, center = FALSE) + log_patch + scale(road_length_m, center = FALSE) + (1 | ID), data = webs_center, family = poisson,  control = glmerControl(optimizer = "bobyqa", optCtrl = list(maxfun = 2e4)))
 options(na.action = "na.fail") # Required for dredge to run
-model_dredge <- dredge(global, beta = F, evaluate = T, rank = AICc)
+model_dredge <- dredge(global, beta = "none", evaluate = T, rank = AICc)
 options(na.action = "na.omit") # set back to default
@@
 #TotalSub
-exp(info[3, 1])
-exp(info[3, 2])
-#tdr
 exp(info[2, 1])
@@
 info <- out[[10]]
-#tdr
+#TotalSub
 exp(info[2, 1])
 exp(info[2, 2])
-#TotalSub
+#road length
 exp(info[3, 1])
@@
 exp(info[4, 2])
-#patch
+#tdr
 exp(info[5, 1])
 exp(info[5, 2])
-#road length
+#patch
 exp(info[6, 1])
@@
 exp(info[7, 2])
-car::vif(get.models(model_dredge, 1)[[1]]) # looking for less than 2
+#car::vif(get.models(model_dredge, 1)[[1]]) # looking for less than 2
 ```
@@
              Estimate Std. Error z value Pr(>|z|)    
-(Intercept)    3.1824     0.6117   5.202 1.97e-07 ***
-log_tdr       -0.1846     0.1007  -1.834  0.06665 .  
-log_TotalSub   0.4715     0.1633   2.888  0.00388 **
-
-R-squared = 0.3635599 (marginal - fixed) 0.9508324 (conditional - fixed and random)
+(Intercept)    3.1686     0.6215   5.098 3.43e-07 ***
+log_tdr       -0.1896     0.1023  -1.854  0.06378 .   *negative*
+log_TotalSub   0.4812     0.1659   2.901  0.00372 **  *positive*
+
+R-squared = 0.3671774 (marginal - fixed) 0.9521663 (conditional - fixed and random)
 
@@
              Estimate Std. Error Adjusted SE z value Pr(>|z|)   
-(Intercept)    3.3645     1.2653      1.2710   2.647  0.00812 **
-log_tdr       -0.1934     0.1006      0.1016   1.903  0.05703 . 
-log_TotalSub   0.4611     0.1784      0.1799   2.563  0.01038 * 
-log_tdh       -0.3226     0.2678      0.2704   1.193  0.23276
+(Intercept)    3.3701     1.2954      1.3012   2.590  0.00959 **
+log_tdr       -0.1986     0.1022      0.1032   1.924  0.05432 .  
+log_TotalSub   0.4697     0.1814      0.1830   2.567  0.01026 * 
+log_tdh       -0.3307     0.2719      0.2745   1.205  0.22832
 
@@
               Estimate Std. Error z value Pr(>|z|)   
-(Intercept)    3.1824     0.6117   5.202 1.97e-07 ***
-log_tdr       -0.1846     0.1007  -1.834  0.06665 .  
-log_TotalSub   0.4715     0.1633   2.888  0.00388 **
-
-R-squared = 0.3635599 (marginal - fixed) 0.9508324 (conditional - fixed and random)
+(Intercept)     1.1283     0.8355   1.350  0.17687   
+tree100m_frac   5.0864     1.7266   2.946  0.00322 ** *positive*
+
+R-squared = 0.4787743 (marginal - fixed) 0.9596909 (conditional - fixed and random)
 
@@
               Estimate Std. Error Adjusted SE z value Pr(>|z|)   
-(Intercept)   3.479599   1.469543    1.475122   2.359   0.0183 *
-log_tdr      -0.213553   0.111308    0.112287   1.902   0.0572 .
-log_TotalSub  0.471545   0.218490    0.220246   2.141   0.0323 *
-log_tdh      -0.359085   0.274215    0.276807   1.297   0.1945  
-tree100m      0.015565   0.008560    0.008623   1.805   0.0711 .
-log_patch    -0.087858   0.099543    0.100463   0.875   0.3818
+(Intercept)     0.3764     1.3417      1.3881   0.271   0.7863   
+tree100m_frac   5.0033     1.7056      1.7823   2.807   0.0050 **
+log_TotalSub    0.6815     0.3801      0.3976   1.714   0.0865 . 
+log_tdr        -0.2415     0.1683      0.1769   1.365   0.1721
 
@@
              Estimate Std. Error z value Pr(>|z|)    
-(Intercept)    3.1824     0.6117   5.202 1.97e-07 ***
-log_tdr       -0.1846     0.1007  -1.834  0.06665 .  
-log_TotalSub   0.4715     0.1633   2.888  0.00388 **
-
-R-squared = 0.3635599 (marginal - fixed) 0.9508324 (conditional - fixed and random)
+(Intercept)    2.0705     0.4687   4.417    1e-05 ***
+log_TotalSub   0.6449     0.3921   1.645      0.1     *positive*
+
+R-squared = 0.1332201 (marginal - fixed) 0.9103755 (conditional - fixed and random)
 
@@
                                      Estimate Std. Error Adjusted SE z value Pr(>|z|)
-(Intercept)    3.458641   2.160676    2.174189   1.591   0.1117  
-log_tdr       -0.212514   0.112355    0.113366   1.875   0.0609 .
-log_TotalSub   0.504709   0.216517    0.218399   2.311   0.0208 *
-log_tdh       -0.359085   0.274215    0.276807   1.297   0.1945  
-log_patch     -0.087858   0.099543    0.100463   0.875   0.3818  
-road_length_m  0.002237   0.004915    0.004962   0.451   0.6521  
-spec_rad       0.012420   0.030255    0.030548   0.407   0.6843
+(Intercept)                            2.6980     2.7479      2.7626   0.977   0.3288
+log_TotalSub                           0.7725     0.4093      0.4138   1.867   0.0619
+scale(road_length_m, center = FALSE)   1.0413     0.7533      0.7625   1.366   0.1720
+log_tdh                               -0.3763     0.3175      0.3212   1.172   0.2413
+log_tdr                               -0.2307     0.1466      0.1483   1.555   0.1199
+log_patch                              0.2033     0.1934      0.1959   1.038   0.2994
+scale(spec_rad, center = FALSE)       -5.6099     6.2722      6.3531   0.883   0.3772
+
+```{r height_predictor_overall_graphs}
+colorc = "#d95f02" 
+colorf = "#1b9e77"
+coloro = "black"
+
+# Plant Species Richness
+predictions <- expand.grid(log_TotalSub = seq(0, 3.15, 0.03),
+                           log_tdr = mean(webs$log_tdr))
+predictions$response <- predict(top_model_wh_o, newdata = predictions, se.fit = TRUE, re.form = NA, type = "response")
+
+myFunc <- function(mm) {
+    predict(mm, newdata = predictions, re.form = ~0, type = "response")
+}
+#bigBoot_height_overall_plant <- bootMer(top_model_wh_o, myFunc, nsim = 1000)
+#saveRDS(bigBoot_height_overall_plant, file = "bootstrapping/bigBoot_height_overall_plant.Rds")
+bigBoot_height_overall_plant <- readRDS("bootstrapping/bigBoot_height_overall_plant.Rds")
+predSE <- t(apply(bigBoot_height_overall_plant$t, MARGIN = 2, FUN = sd))
+predictions$SE <- predSE[1, ]
+
+height_plant <- ggplot(webs, aes(x = log_TotalSub, y = log(RetreatHeight))) + 
+  geom_point(color = "grey", 
+             size = 1) +
+  geom_line(aes(x = log_TotalSub, y = log(response)), 
+            size = 1, 
+            color = coloro, 
+            data = predictions) + 
+  geom_ribbon(aes(x = log_TotalSub, 
+                  ymin = log(response - 1.96 * SE), 
+                  ymax = log(response + 1.96 * SE)), 
+              fill = coloro, 
+              data = predictions, 
+              inherit.aes = FALSE, 
+              alpha = 0.25) +
+  scale_y_continuous(limits = c(min(log(webs$RetreatHeight)), max(log(webs$RetreatHeight)) + 0.1 * diff(range(log(webs$RetreatHeight))))) +  
+  theme_classic() +
+  xlab("Plant Species Richness [log()]") +
+  ylab("Web Height [log(cm)]") + 
+  theme(text = element_text(size = 10)) + 
+  theme(axis.text.x = element_text(colour = "black", size = 10)) + 
+  theme(axis.text.y = element_text(colour = "black", size = 10)) +
+  theme(axis.text.x = element_blank(), 
+        axis.title.x = element_blank(),
+        axis.text.y = element_blank(),
+        axis.title.y = element_blank()) +
+  annotate(geom = "text", x = min(predictions$log_TotalSub) + diff(range(predictions$log_TotalSub))/2, y = max(log(webs$RetreatHeight)), label = "**", color = "black", size = 4)
+
+# Road Disturbance
+predictions <- expand.grid(log_TotalSub = mean(webs$log_TotalSub),
+                           log_tdr = seq(2.73, 7.22, 0.05))
+predictions$response <- predict(top_model_wh_o, newdata = predictions, se.fit = TRUE, re.form = NA, type = "response")
+
+myFunc <- function(mm) {
+    predict(mm, newdata = predictions, re.form = ~0, type = "response")
+}
+#bigBoot_height_overall_tdr <- bootMer(top_model_wh_o, myFunc, nsim = 1000)
+#saveRDS(bigBoot_height_overall_tdr, file = "bootstrapping/bigBoot_height_overall_tdr.Rds")
+bigBoot_height_overall_tdr <- readRDS("bootstrapping/bigBoot_height_overall_tdr.Rds")
+predSE <- t(apply(bigBoot_height_overall_tdr$t, MARGIN = 2, FUN = sd))
+predictions$SE <- predSE[1, ]
+
+height_tdr <- ggplot(webs, aes(x = log_tdr, y = log(RetreatHeight))) + 
+  geom_point(color = "grey", 
+             size = 1) +
+  geom_line(aes(x = log_tdr, y = log(response)), 
+            size = 1, 
+            color = coloro, 
+            data = predictions) + 
+  geom_ribbon(aes(x = log_tdr, 
+                  ymin = log(response - 1.96 * SE), 
+                  ymax = log(response + 1.96 * SE)), 
+              fill = coloro, 
+              data = predictions, 
+              inherit.aes = FALSE, 
+              alpha = 0.25) +
+  scale_y_continuous(limits = c(min(log(webs$RetreatHeight)), max(log(webs$RetreatHeight)) + 0.1 * diff(range(log(webs$RetreatHeight))))) +  
+  theme_classic() +
+  xlab("Road Disturbance [log(vehicles/day/m)]") +
+  ylab("Web Height [log(cm)]") + 
+  theme(text = element_text(size = 10)) + 
+  theme(axis.text.x = element_text(colour = "black", size = 10)) + 
+  theme(axis.text.y = element_text(colour = "black", size = 10)) +
+  theme(axis.text.x = element_blank(), 
+        axis.title.x = element_blank(),
+        axis.text.y = element_blank(),
+        axis.title.y = element_blank()) +
+  annotate(geom = "text", x = min(predictions$log_tdr) + diff(range(predictions$log_tdr))/2, y = max(log(webs$RetreatHeight)), label = ".", color = "black", size = 4)
+
+height_plant
+height_tdr
+```
+
+```{r height_predictor_forest_graphs}
+colorc = "#d95f02" 
+colorf = "#1b9e77"
+coloro = "black"
+
+# Tree
+predictions <- expand.grid(tree100m_frac = seq(0.31, 0.66, 0.003))
+predictions$response <- predict(top_model_wh_f, newdata = predictions, se.fit = TRUE, re.form = NA, type = "response")
+
+myFunc <- function(mm) {
+    predict(mm, newdata = predictions, re.form = ~0, type = "response")
+}
+#bigBoot_height_forest_tree <- bootMer(top_model_wh_f, myFunc, nsim = 1000)
+#saveRDS(bigBoot_height_forest_tree, file = "bootstrapping/bigBoot_height_forest_tree.Rds")
+bigBoot_height_forest_tree <- readRDS("bootstrapping/bigBoot_height_forest_tree.Rds")
+predSE <- t(apply(bigBoot_height_forest_tree$t, MARGIN = 2, FUN = sd))
+predictions$SE <- predSE[1, ]
+
+height_forest_tree <- ggplot(webs_forest, aes(x = log(tree100m_frac), y = log(RetreatHeight))) + 
+  geom_point(color = "grey", 
+             size = 1) +
+  geom_line(aes(x = log(tree100m_frac), y = log(response)), 
+            size = 1, 
+            color = colorf, 
+            data = predictions) + 
+  geom_ribbon(aes(x = log(tree100m_frac), 
+                  ymin = log(response - 1.96 * SE), 
+                  ymax = log(response + 1.96 * SE)), 
+              fill = colorf, 
+              data = predictions, 
+              inherit.aes = FALSE, 
+              alpha = 0.25) +
+  scale_y_continuous(limits = c(min(log(webs_forest$RetreatHeight)), max(log(webs_forest$RetreatHeight)) + 0.1 * diff(range(log(webs_forest$RetreatHeight))))) +  
+  theme_classic() +
+  xlab("Proportion of Tree Cover in 100-Meter Buffer of Site [log()]") +
+  ylab("Web Height [log(cm)]") + 
+  theme(text = element_text(size = 10)) + 
+  theme(axis.text.x = element_text(colour = "black", size = 10)) + 
+  theme(axis.text.y = element_text(colour = "black", size = 10)) +
+  theme(axis.text.x = element_blank(), 
+        axis.title.x = element_blank(),
+        axis.text.y = element_blank(),
+        axis.title.y = element_blank()) +
+  annotate(geom = "text", x = min(log(predictions$tree100m_frac)) + diff(range(log(predictions$tree100m_frac)))/2, y = max(log(webs_forest$RetreatHeight)), label = "**", color = "black", size = 4)
+
+height_forest_tree
+```
+
+```{r height_predictor_center_graphs}
+colorc = "#d95f02" 
+colorf = "#1b9e77"
+coloro = "black"
+
+# Plant Species Richness
+predictions <- expand.grid(log_TotalSub = seq(0, 1.80, 0.02))
+predictions$response <- predict(top_model_wh_c, newdata = predictions, se.fit = TRUE, re.form = NA, type = "response")
+
+myFunc <- function(mm) {
+    predict(mm, newdata = predictions, re.form = ~0, type = "response")
+}
+#bigBoot_height_center_plant <- bootMer(top_model_wh_c, myFunc, nsim = 1000)
+#saveRDS(bigBoot_height_center_plant, file = "bootstrapping/bigBoot_height_center_plant.Rds")
+bigBoot_height_center_plant <- readRDS("bootstrapping/bigBoot_height_center_plant.Rds")
+predSE <- t(apply(bigBoot_height_center_plant$t, MARGIN = 2, FUN = sd))
+predictions$SE <- predSE[1, ]
+
+height_center_plant <- ggplot(webs_center, aes(x = log_TotalSub, y = log(RetreatHeight))) + 
+  geom_point(color = "grey", 
+             size = 1) +
+  geom_line(aes(x = log_TotalSub, y = log(response)), 
+            size = 1, 
+            color = colorc, 
+            data = predictions) + 
+  geom_ribbon(aes(x = log_TotalSub, 
+                  ymin = log(response - 1.96 * SE), 
+                  ymax = log(response + 1.96 * SE)), 
+              fill = colorc, 
+              data = predictions, 
+              inherit.aes = FALSE, 
+              alpha = 0.25) +
+  scale_y_continuous(limits = c(min(log(webs_forest$RetreatHeight)) - 4, max(log(webs_forest$RetreatHeight)) + 0.1 * diff(range(log(webs_forest$RetreatHeight))))) +  
+  theme_classic() +
+  xlab("Plant Species Richness [log()]") +
+  ylab("Web Height [log(cm)]") + 
+  theme(text = element_text(size = 10)) + 
+  theme(axis.text.x = element_text(colour = "black", size = 10)) + 
+  theme(axis.text.y = element_text(colour = "black", size = 10)) +
+  theme(axis.text.x = element_blank(), 
+        axis.title.x = element_blank(),
+        axis.text.y = element_blank(),
+        axis.title.y = element_blank()) +
+  annotate(geom = "text", x = min((predictions$log_TotalSub)) + diff(range((predictions$log_TotalSub)))/2, y = max(log(webs_forest$RetreatHeight)), label = "N.S.", color = "black", size = 4)
+
+height_center_plant
+```
 
 ### Web Height by Land
+
+```{r height_land_stats}
+height_land <- glmer(round(RetreatHeight, 0) ~ Land + (1 | ID), data = webs, family = poisson)
+summary(height_land)
+car::Anova(height_land, type = 3)
+comp <- glht(height_land, linfct = mcp(Land = "Tukey"))
+summary(comp)
+```
+
+```{r height_land_graph}
+webs <- webs %>% 
+  mutate(Land = fct_relevel(Land, "Deciduous Forest", 
+                            "Woody Wetlands", 
+                            "Urban, High", 
+                            "Urban, Medium", 
+                            "Urban, Low"))
+predictions <- expand.grid(Land = levels(factor(webs$Land)))
+predictions$response <- predict(height_land, newdata = predictions, se.fit = TRUE, re.form = NA, type = "response")
+
+myFunc <- function(mm) {
+    predict(mm, newdata = predictions, re.form = ~0, type = "response")
+}
+#bigBoot_height_land <- bootMer(height_land, myFunc, nsim = 1000)
+#saveRDS(bigBoot_height_land, file = "bootstrapping/bigBoot_height_land.Rds")
+bigBoot_height_land <- readRDS("bootstrapping/bigBoot_height_land.Rds")
+predSE <- t(apply(bigBoot_height_land$t, MARGIN = 2, FUN = sd))
+predictions$SE <- predSE[1, ]
+#predictions2 <- summary(emmeans(height_land, ~Land,type = "response"))
+
+ggplot(webs, aes(x = Land, y = RetreatHeight)) + 
+  geom_jitter(color = "grey", width = 0.1, size = 0.5) +
+  geom_point(aes(x = Land, y = response, color = Land), size = 1, data = predictions) + 
+  geom_errorbar(aes(x = Land, 
+                  ymin = response - SE, 
+                  ymax = response + SE, color = Land), data = predictions, inherit.aes = FALSE, width = 0.25, size = 1) +
+  theme_classic() +
+  scale_color_manual(values = c("Deciduous Forest" = "#1b9e77", "Woody Wetlands" = "#1b9e77", "Urban, High" = "#d95f02", "Urban, Medium" = "#d95f02", "Urban, Low" = "#d95f02")) +
+  xlab("Land Cover Class") +
+  ylab("Web Height [log(cm)]") + 
+  theme(text = element_text(size = 10)) + 
+  theme(axis.text.x=element_text(colour="black", size=10)) + 
+  theme(axis.text.y=element_text(colour="black", size=10)) +
+  theme(legend.position = "none") +
+  theme(axis.text.x = element_text(angle = 90, vjust = 1, hjust=1)) +
+  annotate(geom="text", x=1, y=max(webs$RetreatHeight), label="A", color="black", size = 3) +
+  annotate(geom="text", x=2, y=max(webs$RetreatHeight), label="A", color="black", size = 3) +
+  annotate(geom="text", x=3, y=max(webs$RetreatHeight), label="A", color="black", size = 3) +
+  annotate(geom="text", x=4, y=max(webs$RetreatHeight), label="A", color="black", size = 3) +
+  annotate(geom="text", x=5, y=max(webs$RetreatHeight), label="A", color="black", size = 3)
+```

### 2022-11-25 data_analysis.Rmd
Data analysis should be about finished

@@
 library(broom.mixed) # for augment of the mixed effect models (web distance) to look at assumptions
+library(multcomp) # for pairwise comparisons of land cover categories
 ```
@@
 We use "sites" to compare search distance, the number of webs, and the number of spiders.
-We will use "webs" for web height and nearest neighbor analyses.
-The "web_dist" dataset looks at the distance from the focal web to the nearest and second nearest neighbors.
+We will use "webs" for web height.
+The "web_dist" data set is a subset of "webs" that looks at the distance from the focal web to the nearest and second nearest neighbors.
 
@@
   mutate(Neighbor = ifelse(Web == "W002", "1", "2"))
-```
-
-At one time, we tried scaling and centering the data in difference ways.
-I want to make mention of it here because it might be useful information for me to look back on in the future.
-Scaling is dividing each datum by the standard deviation of the data and centering is subtracting the mean of the data from each datum to try to normalize the data; a second type of centering and scaling involves subtracting the median and dividing by the interquartile range; need to remember to back transform when making figures; we didn't scale and center because log-transformations on zero-inflated variables were enough to remove convergence errors
+
+near <- web_dist %>% 
+  filter(Neighbor == 1)
+```
+
+At one time, we tried scaling and centering the data in difference ways. I want to make mention of it here because it might be useful information for me to look back on in the future.
+
+- Scaling is dividing each datum by the standard deviation of the data and centering is subtracting the mean of the data from each datum to try to normalize the data.
+
+- A second type of centering and scaling involves subtracting the median and dividing by the interquartile range.
+
+It's important to remember to back transform when making figures. We didn't scale and center because log-transformations on right-skewed variables were enough to remove convergence errors.
 
@@
 sites <- sites %>% 
-  mutate(patch_area_km = patch_area_mm * 1e-6)
+  mutate(patch_area_km = patch_area_mm * 1e-6,
+         tree100m_frac = as.numeric(tree100m/100),
+         imperv100m_frac = as.numeric(imperv100m/100))
 ```
@@
 
-Many data are zero-inflated or right skewed.
+Many data are right-skewed.
 We check the distribution of the data and check distributions after log-transformation for right-skewed data not containing zeros.
@@
 # use as is, log won't work because some data are zero
-ggplot(sites, aes(x = tree100m)) +
-  geom_density()
+ggarrange(ggplot(sites, aes(x = tree100m)) +
+  geom_density(), ggplot(sites, aes(x = tree100m_frac)) +
+  geom_density(), ncol = 2, nrow = 1)
 shapiro.test(sites$tree100m) # not normal
+shapiro.test(sites$tree100m_frac) # not normal
 
@@
   mutate(Neighbor = ifelse(Web == "W002", "1", "2"))
+
+near <- web_dist %>% 
+  filter(Neighbor == 1)
 ```
@@
   filter(Location == "Urban Forest")
+
+near_forest <- near %>% 
+  filter(Location == "Urban Forest")
+
+near_center <- near %>% 
+  filter(Location == "Urban Center")
 ```
@@
 corr <- sites %>% 
-  select(TotalSub, Traffic_Dist_Road, Traffic_Dist_Highway)
+  dplyr::select(TotalSub, Traffic_Dist_Road, Traffic_Dist_Highway)
 chart.Correlation(corr, histogram = TRUE, method = "spearman") # kendall, spearman
@@
 corr_transformed <- sites %>% 
-  select(tree100m, imperv100m, log_TotalSub, 
+  dplyr::select(tree100m, imperv100m, log_TotalSub, 
          log_tdr, log_tdh, 
@@
 corr_transformed <- sites %>% 
-  select(log_TotalSub, log_tdr, log_tdh)
+  dplyr::select(log_TotalSub, log_tdr, log_tdh)
 chart.Correlation(corr_transformed, histogram = TRUE, method = "spearman") # kendall, spearman
@@
   filter(Location == "Urban Forest") %>% 
-  select(tree100m, TotalSub, Traffic_Dist_Road, patch_area_km, Traffic_Dist_Highway)
+  dplyr::select(tree100m, TotalSub, Traffic_Dist_Road, patch_area_km, Traffic_Dist_Highway)
 chart.Correlation(corr_forest, histogram = TRUE, method = "spearman")
@@
   filter(Location == "Urban Forest") %>% 
-  select(tree100m, imperv100m, log_TotalSub, 
+  dplyr::select(tree100m, imperv100m, log_TotalSub, 
          log_tdr, log_tdh, 
@@
   filter(Location == "Urban Forest") %>% 
-  select(tree100m, log_TotalSub, log_tdr, patch_area_km, log_tdh)
+  dplyr::select(tree100m, log_TotalSub, log_tdr, patch_area_km, log_tdh)
 chart.Correlation(corr_forest_transformed, histogram = TRUE, method = "spearman")
@@
   filter(Location == "Urban Center") %>% 
-  select(tree100m, imperv100m, log_TotalSub, log_tdr, log_tdh, spec_rad, light_rad, log_patch, road_length_m)
+  dplyr::select(tree100m, imperv100m, log_TotalSub, log_tdr, log_tdh, spec_rad, light_rad, log_patch, road_length_m)
 findCorrelation(cor(corr_center_transformed, method = "spearman"), cutoff = .6, verbose = TRUE, names = TRUE) 
@@
 predictions <- summary(emmeans(tree100m, ~Location),type = "response")
+predictions
 
@@
 
-Tree cover is *significantly higher in the urban forest* than the urban center (z = -14.50, df = 1, 20, p < 0.001).
+Tree cover is **significantly higher in the urban forest** than the urban center (z = -14.50, df = 1, 20, p < 0.001).
 The means and SE's are 47.15 ± 2.17 % for the urban forest and 1.58 ± 0.36 % for the urban center.
@@
 predictions <- summary(emmeans(imperv100m, ~Location),type = "response")
+predictions
 
@@
 
-Impervious cover is *significantly higher in the urban center* than the urban forest (z = 14.51, df = 1, 20, p < 0.001).
+Impervious cover is **significantly higher in the urban center** than the urban forest (z = 14.51, df = 1, 20, p < 0.001).
 The means and SE's are 1.27 ± 0.36 % for the urban forest and 76.52 ± 2.53 % for the urban center.
@@
 predictions <- summary(emmeans(tdr, ~Location),type = "response")
+predictions
 
@@
   theme(legend.position = "none") +
-  annotate(geom="text", x=1.5, y=1400, label="", color="black", size = 10)
+  annotate(geom="text", x=1.5, y=1400, label="N. S.", color="black", size = 10)
 ```
@@
 
-There is *no difference* in road disturbance between the urban forest and urban center (z = 1.403, df = 1, 20, p = 0.161).
-The means and SE's are 52.98 ± 1.88 vehicles/day/m for the urban forest and 194.42 ± 1.93 vehicles/day/m for the urban center.
+There is **no difference** in road disturbance between the urban forest and urban center (z = 1.403, df = 1, 20, p = 0.161).
+The means and SE's are `r exp(3.97)` ± `r exp(0.630)` vehicles/day/m for the urban forest and `r exp(5.27)` ± `r exp(0.663)` vehicles/day/m for the urban center.
 
@@
 predictions <- summary(emmeans(tdh, ~Location),type = "response")
+predictions
 
@@
   theme(legend.position = "none") +
-  annotate(geom="text", x=1.5, y=250, label="", color="black", size = 10)
+  annotate(geom="text", x=1.5, y=250, label="N. S.", color="black", size = 10)
 ```
@@
 
-There is *no difference* in highway disturbance between the urban forest and urban center (z = 0.530, df = 1, 20, p = 0.596).
-The means and SE's are 33.78 ± 1.80 vehicles/day/m for the urban forest and 52.46 ± 1.77 vehicles/day/m for the urban center.
+There is **no difference** in highway disturbance between the urban forest and urban center (z = 0.530, df = 1, 20, p = 0.596).
+The means and SE's are `r exp(3.52)` ± `r exp(0.593)` vehicles/day/m for the urban forest and `r exp(3.96)` ± `r exp(0.574)` vehicles/day/m for the urban center.
 
@@
 predictions <- summary(emmeans(plant, ~Location),type = "response")
+predictions
 
@@
 
-Plant species richness is *significantly higher in the urban forest* than the urban center (z = -2.430, df = 1, 20, p = 0.015).
-The means and SE's are 12.18 ± 1.65 species for the urban forest and 2.97 ± 1.35 species for the urban center.
+Plant species richness is **significantly higher in the urban forest** than the urban center (z = -2.430, df = 1, 20, p = 0.015).
+The means and SE's are `r exp(2.50)` ± `r exp(0.500)` species for the urban forest and `r exp(1.09)` ± `r exp(0.302)` species for the urban center.
 
@@
 predictions <- summary(emmeans(spec, ~Location),type = "response")
+predictions
 
@@
 
-Spectral radiance is *significantly higher in the urban center* than the urban forest (z = 3.079, df = 1, 20, p = 0.002).
+Spectral radiance is **significantly higher in the urban center** than the urban forest (z = 3.079, df = 1, 20, p = 0.002).
 The means and SE's are 137.44 ± 3.71 Watts/(m² * sr * µm) for the urban forest and 153.39 ± 3.58 Watts/(m² * sr * µm) for the urban center.
@@
 predictions <- summary(emmeans(light, ~Location),type = "response")
+predictions
 
@@
 
-Light radiance is *significantly higher in the urban center* than the urban forest (z = 22.46, df = 1, 20, p < 0.001).
+Light radiance is **significantly higher in the urban center** than the urban forest (z = 22.46, df = 1, 20, p < 0.001).
 The means and SE's are 5.89 ± 0.77 mcd/m² for the urban forest and 116.90 ± 3.12 mcd/m² for the urban center.
@@
 predictions <- summary(emmeans(patch, ~Location),type = "response")
+predictions
 
@@
 
-Patch area is *significantly higher in the urban forest* than the urban center (z = -3.599, df = 1, 20, p < 0.001).
-The means and SE's are 37,049.12 ± 2.80 mm^2 for the urban forest and 437.03 ± 2.03 mm^2 for the urban center.
+Patch area is **significantly higher in the urban forest** than the urban center (z = -3.599, df = 1, 20, p < 0.001).
+The means and SE's are `r exp(10.52)` ± `r exp(1.026)` mm² for the urban forest and `r exp(6.08)` ± `r exp(0.712)` mm² for the urban center.
 
@@
 predictions <- summary(emmeans(road, ~Location),type = "response")
+predictions
 
@@
 
-Total road length is *significantly higher in the urban center* than the urban forest (z = 20.89, df = 1, 20, p < 0.001).
+Total road length is **significantly higher in the urban center** than the urban forest (z = 20.89, df = 1, 20, p < 0.001).
 The means and SE's are 15.67 ± 1.25 m for the urban forest and 93.03 ± 2.78 m for the urban center.
@@
 
-For this variable, I've been going back and forth on whether I should log-transform the search distance (because it can be ran Guassian), or whether to use a log-link function (Poisson Distribution).
+For this variable, I've gone back and forth on whether I should log-transform the search distance (because it can be ran Gaussian), or whether to use a log-link function (Poisson Distribution).
 The poisson glm more closely matches the mean, but the log-transformation is better at capturing the variance.
@@
 ```
+
+Using a Poisson distribution, we **searched significantly further at sites in the urban forest** than the urban center to reach the focal web (z = -10.1, df = 1, 20, p < 0.001).
 
@@
 (Intercept)   2.45699    0.24451  10.049  < 2e-16 ***
-log_tdh       0.21434    0.04469   4.796 1.62e-06 *** *positive*
-log_tdr       0.13279    0.01775   7.480 7.42e-14 *** *positive*
-log_TotalSub  0.31671    0.03252   9.740  < 2e-16 *** *positive*
+log_tdh       0.21434    0.04469   4.796 1.62e-06 *** **positive**
+log_tdr       0.13279    0.01775   7.480 7.42e-14 *** **positive**
+log_TotalSub  0.31671    0.03252   9.740  < 2e-16 *** **positive**
 
@@
 (Intercept)  -2.962190   0.608574  -4.867 1.13e-06 ***
-log_tdh       1.354582   0.109952  12.320  < 2e-16 *** *positive*
-log_tdr       0.718623   0.038386  18.721  < 2e-16 *** *positive*
-log_TotalSub -1.010040   0.095179 -10.612  < 2e-16 *** *negative*
-tree100m      0.049914   0.004241  11.770  < 2e-16 *** *positive*
+log_tdh       1.354582   0.109952  12.320  < 2e-16 *** **positive**
+log_tdr       0.718623   0.038386  18.721  < 2e-16 *** **positive**
+log_TotalSub -1.010040   0.095179 -10.612  < 2e-16 *** **negative**
+tree100m      0.049914   0.004241  11.770  < 2e-16 *** **positive**
 
@@
 (Intercept)  -26.90656    2.78649  -9.656  < 2e-16 ***
-log_patch      1.05254    0.05903  17.832  < 2e-16 *** *positive* 
-log_tdh        0.58001    0.09128   6.354 2.10e-10 *** *positive*
-log_tdr        0.45331    0.04386  10.335  < 2e-16 *** *positive*
-log_TotalSub   0.54581    0.08135   6.709 1.96e-11 *** *positive*
-spec_rad       0.12466    0.01458   8.549  < 2e-16 *** *positive*
+log_patch      1.05254    0.05903  17.832  < 2e-16 *** **positive** 
+log_tdh        0.58001    0.09128   6.354 2.10e-10 *** **positive**
+log_tdr        0.45331    0.04386  10.335  < 2e-16 *** **positive**
+log_TotalSub   0.54581    0.08135   6.709 1.96e-11 *** **positive**
+spec_rad       0.12466    0.01458   8.549  < 2e-16 *** **positive**
 
@@
                               se_fit = TRUE)
-ggplot(sites_center, aes(x = log_tdr, y = log(WalkDist))) + 
+search_center_tdr <- ggplot(sites_center, aes(x = log_tdr, y = log(WalkDist))) + 
   geom_point(color = "grey", 
@@
 summary(search_land)
-anova(search_land, test = "Chisq")
+car::Anova(search_land, test.statistic = "LR")
 comp <- glht(search_land, linfct = mcp(Land = "Tukey"))
@@
 
+**Search distance significantly varies** by land class (Chi = 340.32, df = 4, p < 0.001).
+
 ## Response Variable: Number of Webs
@@
 # Log-transformed, Normal
-test_webs2 <- augment(webs2, data = sites)
+test_webs2 <- augment(web2, data = sites)
 resid_webs2 <- ggplot(test_webs2, aes(x = .fitted, y = .resid)) + 
@@
 ```
+
+There were **significantly more webs at sites in the urban center** than the urban forest (z = 8.556, df = 1, 20, p < 0.001).
 
@@
 (Intercept)   7.55449    0.87254   8.658  < 2e-16 ***
-log_tdh      -1.26833    0.19726  -6.430 1.28e-10 *** *negative*
-log_tdr       0.18726    0.04729   3.960 7.49e-05 *** *positive*
-log_TotalSub -1.02619    0.09768 -10.505  < 2e-16 *** *negative*
+log_tdh      -1.26833    0.19726  -6.430 1.28e-10 *** **negative**
+log_tdr       0.18726    0.04729   3.960 7.49e-05 *** **positive**
+log_TotalSub -1.02619    0.09768 -10.505  < 2e-16 *** **negative**
 
@@
 (Intercept)   13.145965   1.236110  10.635  < 2e-16 ***
-log_patch     -0.293327   0.113716  -2.579   0.0099 **  *negative*
-log_tdh       -1.539660   0.190172  -8.096 5.67e-16 *** *negative*
-log_TotalSub  -0.717109   0.183835  -3.901 9.59e-05 *** *negative*
-road_length_m -0.022553   0.004713  -4.785 1.71e-06 *** *negative*
+log_patch     -0.293327   0.113716  -2.579   0.0099 **  **negative**
+log_tdh       -1.539660   0.190172  -8.096 5.67e-16 *** **negative**
+log_TotalSub  -0.717109   0.183835  -3.901 9.59e-05 *** **negative**
+road_length_m -0.022553   0.004713  -4.785 1.71e-06 *** **negative**
 
@@
 (Intercept)   12.284984   1.481836    1.650697   7.442  < 2e-16 ***
-log_patch     -0.293327   0.113716    0.137194   2.138 0.032513 *   *negative*
-log_tdh       -1.560993   0.192352    0.229029   6.816  < 2e-16 *** *negative*
-log_TotalSub  -0.659231   0.186648    0.218846   3.012 0.002593 **  *negative*
-road_length_m -0.021230   0.004766    0.005608   3.786 0.000153 *** *negative*
+log_patch     -0.293327   0.113716    0.137194   2.138 0.032513 *   **negative**
+log_tdh       -1.560993   0.192352    0.229029   6.816  < 2e-16 *** **negative**
+log_TotalSub  -0.659231   0.186648    0.218846   3.012 0.002593 **  **negative**
+road_length_m -0.021230   0.004766    0.005608   3.786 0.000153 *** **negative**
 
@@
 summary(webs_land)
-anova(webs_land, test = "Chisq")
+car::Anova(webs_land, test.statistic = "LR")
 comp <- glht(webs_land, linfct = mcp(Land = "Tukey"))
@@
 
+The **number of webs significantly varies** by land cover class (chi = 106.67, df = 4, p < 0.001).
+
 ## Response Variable: Number of Spiders
@@
 ```
+
+The **number of spiders present by site is significantly higher in the urban center** (z = 4.863, df = 1, 20, p < 0.001).
 
@@
 (Intercept)    7.3234     1.1068   6.617 3.67e-11 ***
-log_tdh       -1.1932     0.2785  -4.284 1.84e-05 *** *negative*
-log_TotalSub  -0.9523     0.1370  -6.952 3.61e-12 *** *negative*
+log_tdh       -1.1932     0.2785  -4.284 1.84e-05 *** **negative**
+log_TotalSub  -0.9523     0.1370  -6.952 3.61e-12 *** **negative**
 
@@
 (Intercept)   14.516312   2.195703   6.611 3.81e-11 ***
-log_patch     -0.618055   0.205145  -3.013 0.002589 **  *negative*
-log_tdh       -1.393026   0.286317  -4.865 1.14e-06 *** *negative*
-log_TotalSub  -1.331282   0.357971  -3.719 0.000200 *** *negative*
-road_length_m -0.025605   0.007753  -3.303 0.000958 *** *negative*
+log_patch     -0.618055   0.205145  -3.013 0.002589 **  **negative**
+log_tdh       -1.393026   0.286317  -4.865 1.14e-06 *** **negative**
+log_TotalSub  -1.331282   0.357971  -3.719 0.000200 *** **negative**
+road_length_m -0.025605   0.007753  -3.303 0.000958 *** **negative**
 
@@
               alpha = 0.25) +
-  scale_y_continuous(limits = c(min(log(sites_center$NumSpiders)) - 1, max(log(sites_center$NumSpiders)) + 0.1 * diff(range(log(sites_center$NumSpiders))))) +  
+  scale_y_continuous(limits = c(min(log(sites_center$NumSpiders)) - 1, max(log(sites_center$NumSpiders)) + 0.2 * diff(range(log(sites_center$NumSpiders))))) +  
   theme_classic() +
@@
 summary(spiders_land)
-anova(spiders_land, test = "Chisq")
+car::Anova(spiders_land, test.statistic = "LR")
 comp <- glht(spiders_land, linfct = mcp(Land = "Tukey"))
@@
 
+The **number of spiders per site significantly varies** across land cover class (Chi = 31.65, df = 4, p < 0.001).
+
 ## Response Variable: Web Distance
@@
 
+Spider neighbors were **significantly closer in the urban center** than the urban forest (z = -5.597, df = 1, 21, p < 0.001).
+The **second neighbor was always further from the focal web** than the first (z = 14.654, df = 1, 21, p < 0.001), as this is how we defined the first and second neighbor.
+We also found a **significant interaction between location and neighbor** (z = 9.860, df = 1, 21, p < 0.001) - the distance between the first and second neighbor differed to a higher degree in the urban center than the urban forest.
+
 ### Web Distance by Predictors
@@
 ```{r dist_predictors_stats}
-near <- web_dist %>% 
-  filter(Neighbor == 1)
-
 #overall
@@
 # Urban Forest
-global <- glm(round(RetreatDist, 0) ~ tree100m + log_TotalSub + log_tdr + log_tdh + log_patch, data = near, family = poisson)
+global <- glm(round(RetreatDist, 0) ~ tree100m + log_TotalSub + log_tdr + log_tdh + log_patch, data = near_forest, family = poisson)
 options(na.action = "na.fail") # Required for dredge to run
@@
 #tree100m
-info[6, 1]
-info[6, 2]
+info[5, 1]
+info[5, 2]
 #TotalSub
--exp(info[5, 1])
-exp(info[5, 2])
-#Road
 exp(info[4, 1])
 exp(info[4, 2])
-#Highway
+#Road
 exp(info[3, 1])
 exp(info[3, 2])
+#Highway
+exp(info[2, 1])
+exp(info[2, 2])
 
@@
 #summary(model.avg(model_dredge, subset = delta <= 2))
-car::vif(get.models(model_dredge, 1)[[1]]) # all but log_tdh over 2
-
-# This means there is quite a bit of multicollinearity. Let's try removing the variable with the highest vif.
-global2 <- update(global, .~. -tree100m)
-options(na.action = "na.fail") # Required for dredge to run
-model_dredge <- dredge(global2, beta = "none", evaluate = T, rank = AICc)
-options(na.action = "na.omit") # set back to default
-top_model_wd_f <- get.models(model_dredge, subset = 1)[[1]]
-out <- summary(top_model_wd_f)
-out
-info <- out[[12]]
-# patch
-exp(info[2, 1])
-exp(info[2, 2])
-# tdr
-exp(info[4, 1])
-exp(info[4, 2])
-#tdh
-exp(info[3, 1])
-exp(info[3, 2])
-with(summary(top_model_wd_f), 1 - deviance/null.deviance)
-model.sel(model_dredge) #estimates same signs
-out <- summary(model.avg(model_dredge, subset = delta <= 2))
-out
-info <- out[[12]]
-#patch
-exp(info[2, 1])
-exp(info[2, 2])
-#tdh
-exp(info[3, 1])
-exp(info[3, 2])
-#tdr
-exp(info[4, 1])
-exp(info[4, 2])
-#TotalSub
-exp(info[5, 1])
-exp(info[5, 2])
 car::vif(get.models(model_dredge, 1)[[1]]) # looking for less than 2
@@
 # Urban Center
-global <- glm(round(RetreatDist, 0) ~ log_TotalSub + log_tdr + log_tdh + spec_rad + log_patch + road_length_m, data = near, family = poisson)
+global <- glm(round(RetreatDist, 0) ~ log_TotalSub + log_tdr + log_tdh + spec_rad + log_patch + road_length_m, data = near_center, family = poisson)
 options(na.action = "na.fail") # Required for dredge to run
@@
 #TotalSub
-exp(info[5, 1])
-exp(info[5, 2])
-#tdr
-exp(info[4, 1])
-exp(info[4, 2])
-#tdh
-exp(info[3, 1])
-exp(info[3, 2])
-#log_patch
 exp(info[2, 1])
@@
 #spec_rad
-info[7, 1]
-info[7, 2]
+info[4, 1]
+info[4, 2]
 #road_length_m
-info[6, 1]
-info[6, 2]
-
-with(summary(top_model_wd_c), 1 - deviance/null.deviance)
-model.sel(model_dredge) #estimates same signs
-#summary(model.avg(model_dredge, subset = delta <= 2))
-car::vif(get.models(model_dredge, 1)[[1]]) #all except tdh above 2
-
-# This means there is quite a bit of multicollinearity. Let's try removing the variable with the highest vif.
-
-global2 <- update(global, .~. -spec_rad)
-options(na.action = "na.fail") # Required for dredge to run
-model_dredge <- dredge(global2, beta = "none", evaluate = T, rank = AICc)
-options(na.action = "na.omit") # set back to default
-top_model_wd_c <- get.models(model_dredge, subset = 1)[[1]]
-out <- summary(top_model_wd_c)
-out
-info <- out[[12]]
-car::vif(get.models(model_dredge, 1)[[1]])
-
-# Still pretty high VIF values. Let's remove another
-
-global3 <- update(global2, .~. -road_length_m)
-options(na.action = "na.fail") # Required for dredge to run
-model_dredge <- dredge(global3, beta = "none", evaluate = T, rank = AICc)
-options(na.action = "na.omit") # set back to default
-top_model_wd_c <- get.models(model_dredge, subset = 1)[[1]]
-out <- summary(top_model_wd_c)
-out
-info <- out[[12]]
-# patch
-exp(info[2, 1])
-exp(info[2, 2])
-# tdh
-exp(info[3, 1])
-exp(info[3, 2])
-# tdr
-exp(info[4, 1])
-exp(info[4, 2])
+info[3, 1]
+info[3, 2]
+
 with(summary(top_model_wd_c), 1 - deviance/null.deviance)
@@
 out
-car::vif(get.models(model_dredge, 1)[[1]]) #looks better
+info <- out[[10]]
+#TotalSub
+exp(info[2, 1])
+exp(info[2, 2])
+#spec_rad
+info[4, 1]
+info[4, 2]
+#road_length_m
+info[3, 1]
+info[3, 2]
+#log_patch
+exp(info[5, 1])
+exp(info[5, 2])
+car::vif(get.models(model_dredge, 1)[[1]]) # looking for less than 2
+
+# If any value is much greater than 2, this means there is quite a bit of multicollinearity, and we can try removing the variable with the highest vif.
+Here is the code you would run to accomplish this.
+
+#global2 <- update(global, .~. -spec_rad)
+#options(na.action = "na.fail") # Required for dredge to run
+#model_dredge <- dredge(global2, beta = "none", evaluate = T, rank = AICc)
+#options(na.action = "na.omit") # set back to default
+#top_model_wd_c <- get.models(model_dredge, subset = 1)[[1]]
+#out <- summary(top_model_wd_c)
+#out
+#info <- out[[12]]
+#car::vif(get.models(model_dredge, 1)[[1]]) 
 ```
@@
 (Intercept)   5.38311    0.06200   86.83   <2e-16 ***
-log_tdr      -0.18279    0.01024  -17.84   <2e-16 *** *negative*
-log_TotalSub  0.57484    0.01653   34.78   <2e-16 *** *positive*
+log_tdr      -0.18279    0.01024  -17.84   <2e-16 *** **negative**
+log_TotalSub  0.57484    0.01653   34.78   <2e-16 *** **positive**
 
@@
               Estimate Std. Error z value Pr(>|z|)    
-(Intercept) 0.236708   0.223087   1.061    0.289    
-log_patch   0.397613   0.009388  42.354  < 2e-16 *** *positive*
-log_tdh     0.422293   0.033427  12.633  < 2e-16 *** *positive*
-log_tdr     0.066877   0.012460   5.367 7.99e-08 *** *positive*
-
-R-squared = 0.5431401
-
-(conditional average) 
-             Estimate Std. Error Adjusted SE z value Pr(>|z|)    
-(Intercept)   0.21444    0.22610     0.24357   0.880    0.379    
-log_patch     0.40265    0.01246     0.01319  30.529   <2e-16 *** *positive*
-log_tdh       0.42115    0.03350     0.03612  11.660   <2e-16 *** *positive*
-log_tdr       0.06930    0.01307     0.01405   4.933    8e-07 *** *positive*
-log_TotalSub -0.03964    0.02482     0.02684   1.477    0.140     *negative*
+(Intercept)   5.247233   0.253935  20.664  < 2e-16 ***
+log_tdh       0.192623   0.045552   4.229 2.35e-05 *** **positive**
+log_tdr       0.097475   0.018717   5.208 1.91e-07 *** **positive**
+log_TotalSub -0.182147   0.037627  -4.841 1.29e-06 *** **negative**
+tree100m      0.007928   0.001747   4.540 5.64e-06 *** **positive**
+
+R-squared = 0.03720731
 
@@
                Estimate Std. Error z value Pr(>|z|)    
-(Intercept) 0.236708   0.223087   1.061    0.289    
-log_patch   0.397613   0.009388  42.354  < 2e-16 *** *positive*
-log_tdh     0.422293   0.033427  12.633  < 2e-16 *** *positive*
-log_tdr     0.066877   0.012460   5.367 7.99e-08 *** *positive*
-
-R-squared = 0.5431401
+(Intercept)   25.656433   1.978299  12.969   <2e-16 ***
+log_TotalSub  -0.949802   0.081234 -11.692   <2e-16 *** **negative**
+road_length_m -0.028700   0.001686 -17.019   <2e-16 *** **negative**
+spec_rad      -0.116126   0.013624  -8.523   <2e-16 *** **negative**
+
+R-squared = 0.8382736
 
@@
                Estimate Std. Error Adjusted SE z value Pr(>|z|)    
-(Intercept)   0.21444    0.22610     0.24357   0.880    0.379    
-log_patch     0.40265    0.01246     0.01319  30.529   <2e-16 *** *positive*
-log_tdh       0.42115    0.03350     0.03612  11.660   <2e-16 *** *positive*
-log_tdr       0.06930    0.01307     0.01405   4.933    8e-07 *** *positive*
-log_TotalSub -0.03964    0.02482     0.02684   1.477    0.140     *negative*
+(Intercept)   27.444071   3.180180    3.580799   7.664   <2e-16 ***
+log_TotalSub  -1.011887   0.119466    0.136311   7.423   <2e-16 ***
+road_length_m -0.028829   0.001723    0.002106  13.691   <2e-16 ***
+spec_rad      -0.124872   0.018357    0.021193   5.892   <2e-16 ***
+log_patch     -0.152072   0.060123    0.075060   2.026   0.0428 *
 
@@
 
-# Patch Area
-nd <- data.frame(log_patch = seq(4.34, 11.78, 0.07), 
-                 log_tdr = mean(near$log_tdr),
-                 log_tdh = mean(near$log_tdh))
+# Plant Species Richness
+nd <- data.frame(log_TotalSub = seq(1.94, 3.14, 0.015), 
+                 log_tdr = mean(near_forest$log_tdr),
+                 log_tdh = mean(near_forest$log_tdh),
+                 tree100m = mean(near_forest$tree100m))
 predicted.distance <- augment(top_model_wd_f, 
@@
                               se_fit = TRUE)
-dist_forest_patch <- ggplot(near, aes(x = log_patch, y = log(RetreatDist))) + 
+dist_forest_plant <- ggplot(near_forest, aes(x = log_TotalSub, y = log(RetreatDist))) + 
   geom_point(color = "grey", 
              size = 1) +
-  geom_line(aes(x = log_patch, y = .fitted), 
+  geom_line(aes(x = log_TotalSub, y = .fitted), 
             size = 1, 
@@
             data = predicted.distance) + 
-  geom_ribbon(aes(x = log_patch, 
+  geom_ribbon(aes(x = log_TotalSub, 
                   ymin = .fitted - 1.96 * .se.fit, 
@@
               alpha = 0.25) +
-  scale_y_continuous(limits = c(min(log(near$RetreatDist)), max(log(near$RetreatDist)) + 0.1 * diff(range(log(near$RetreatDist))))) +  
-  theme_classic() +
-  xlab("Patch Area [log(mm²)]") +
+  scale_y_continuous(limits = c(min(log(near_forest$RetreatDist)), max(log(near_forest$RetreatDist)) + 0.1 * diff(range(log(near_forest$RetreatDist))))) +  
+  theme_classic() +
+  xlab("Plant Species Richness [log()]") +
   ylab("Distance from Focal Web \nto Neighbor Web [log(cm)]") + 
@@
         axis.title.y = element_blank()) +
-  annotate(geom = "text", x = min(predicted.distance$log_patch) + diff(range(predicted.distance$log_patch))/2, y = max(log(near$RetreatDist)), label = "***", color = "black", size = 4)
+  annotate(geom = "text", x = min(predicted.distance$log_TotalSub) + diff(range(predicted.distance$log_TotalSub))/2, y = max(log(near_forest$RetreatDist)), label = "***", color = "black", size = 4)
 
 # Highway Disturbance
-nd <- data.frame(log_patch = mean(near$log_patch), 
-                 log_tdr = mean(near$log_tdr),
-                 log_tdh = seq(2.76, 5.42, 0.025))
+nd <- data.frame(log_TotalSub = mean(near_forest$log_TotalSub), 
+                 log_tdr = mean(near_forest$log_tdr),
+                 log_tdh = seq(2.76, 3.89, 0.01),
+                 tree100m = mean(near_forest$tree100m))
 predicted.distance <- augment(top_model_wd_f, 
@@
                               se_fit = TRUE)
-dist_forest_tdh <- ggplot(near, aes(x = log_tdh, y = log(RetreatDist))) + 
+dist_forest_tdh <- ggplot(near_forest, aes(x = log_tdh, y = log(RetreatDist))) + 
   geom_point(color = "grey", 
@@
               alpha = 0.25) +
-  scale_y_continuous(limits = c(min(log(near$RetreatDist)), max(log(near$RetreatDist)) + 0.1 * diff(range(log(near$RetreatDist))))) +  
+  scale_y_continuous(limits = c(min(log(near_forest$RetreatDist)), max(log(near_forest$RetreatDist)) + 0.1 * diff(range(log(near_forest$RetreatDist))))) +  
   theme_classic() +
@@
         axis.title.y = element_blank()) +
-  annotate(geom = "text", x = min((predicted.distance$log_tdh)) + diff(range((predicted.distance$log_tdh)))/2, y = max(log(near$RetreatDist)), label = "***", color = "black", size = 4)
+  annotate(geom = "text", x = min((predicted.distance$log_tdh)) + diff(range((predicted.distance$log_tdh)))/2, y = max(log(near_forest$RetreatDist)), label = "***", color = "black", size = 4)
 
 # Road Disturbance
-nd <- data.frame(log_patch = mean(near$log_patch), 
-                 log_tdr = seq(2.73, 7.22, 0.05),
-                 log_tdh = mean(near$log_tdh))
+nd <- data.frame(log_TotalSub = mean(near_forest$log_TotalSub), 
+                 log_tdr = seq(2.73, 6.22, 0.04),
+                 log_tdh = mean(near_forest$log_tdh),
+                 tree100m = mean(near_forest$tree100m))
 predicted.distance <- augment(top_model_wd_f, 
@@
                               se_fit = TRUE)
-dist_forest_tdr <- ggplot(near, aes(x = log_tdr, y = log(RetreatDist))) + 
+dist_forest_tdr <- ggplot(near_forest, aes(x = log_tdr, y = log(RetreatDist))) + 
   geom_point(color = "grey", 
@@
         axis.title.y = element_blank()) +
-  annotate(geom = "text", x = min((predicted.distance$log_tdr)) + diff(range((predicted.distance$log_tdr)))/2, y = max(log(near$RetreatDist)), label = "***", color = "black", size = 4)
-
-dist_forest_patch
-dist_forest_tdr
-dist_forest_tdh
-```
-
-```{r dist_predictors_center_graphs, echo = FALSE}
-colorc = "#d95f02" 
-colorf = "#1b9e77"
-coloro = "black"
-
-# Patch Area
-nd <- data.frame(log_patch = seq(4.34, 11.78, 0.07), 
-                 log_tdr = mean(near$log_tdr),
-                 log_tdh = mean(near$log_tdh))
-predicted.distance <- augment(top_model_wd_c, 
+  annotate(geom = "text", x = min((predicted.distance$log_tdr)) + diff(range((predicted.distance$log_tdr)))/2, y = max(log(near_forest$RetreatDist)), label = "***", color = "black", size = 4)
+
+# Tree
+nd <- data.frame(log_TotalSub = mean(near_forest$log_TotalSub), 
+                 log_tdr = mean(near_forest$log_tdr),
+                 log_tdh = mean(near_forest$log_tdh),
+                 tree100m = seq(31.37, 65.87, 0.35))
+predicted.distance <- augment(top_model_wd_f, 
                               newdata = nd, 
                               se_fit = TRUE)
-dist_forest_patch <- ggplot(near, aes(x = log_patch, y = log(RetreatDist))) + 
+dist_forest_tree <- ggplot(near_forest, aes(x = (tree100m), y = log(RetreatDist))) + 
   geom_point(color = "grey", 
              size = 1) +
-  geom_line(aes(x = log_patch, y = .fitted), 
+  geom_line(aes(x = (tree100m), y = .fitted), 
             size = 1, 
-            color = colorc, 
+            color = colorf, 
             data = predicted.distance) + 
-  geom_ribbon(aes(x = log_patch, 
+  geom_ribbon(aes(x = log(tree100m), 
                   ymin = .fitted - 1.96 * .se.fit, 
                   ymax = .fitted + 1.96 * .se.fit), 
-              fill = colorc, 
+              fill = colorf, 
               data = predicted.distance, 
@@
               alpha = 0.25) +
-  scale_y_continuous(limits = c(min(log(near$RetreatDist)), max(log(near$RetreatDist)) + 0.1 * diff(range(log(near$RetreatDist))))) +  
-  theme_classic() +
-  xlab("Patch Area [log(mm²)]") +
+  scale_y_continuous(limits = c(min(log(near_forest$RetreatDist)), max(log(near_forest$RetreatDist)) + 0.1 * diff(range(log(near_forest$RetreatDist))))) +  
+  theme_classic() +
+  xlab("Percent Tree Cover [%]") +
   ylab("Distance from Focal Web \nto Neighbor Web [log(cm)]") + 
@@
         axis.title.y = element_blank()) +
-  annotate(geom = "text", x = min(predicted.distance$log_patch) + diff(range(predicted.distance$log_patch))/2, y = max(log(near$RetreatDist)), label = "***", color = "black", size = 4)
-
-# Highway Disturbance
-nd <- data.frame(log_patch = mean(near$log_patch), 
-                 log_tdr = mean(near$log_tdr),
-                 log_tdh = seq(2.76, 5.42, 0.025))
+  annotate(geom = "text", x = min((predicted.distance$tree100m)) + diff(range((predicted.distance$tree100m)))/2, y = max(log(near_forest$RetreatDist)), label = "***", color = "black", size = 4)
+
+dist_forest_plant
+dist_forest_tdr
+dist_forest_tdh
+dist_forest_tree
+```
+
+```{r dist_predictors_center_graphs, echo = FALSE}
+colorc = "#d95f02" 
+colorf = "#1b9e77"
+coloro = "black"
+
+# Plant Species Richness
+nd <- data.frame(log_TotalSub = seq(0, 1.8, 0.02), 
+                 spec_rad = mean(near_center$spec_rad),
+                 road_length_m = mean(near_center$road_length_m))
 predicted.distance <- augment(top_model_wd_c, 
@@
                               se_fit = TRUE)
-dist_forest_tdh <- ggplot(near, aes(x = log_tdh, y = log(RetreatDist))) + 
+dist_center_plant <- ggplot(near_center, aes(x = log_TotalSub, y = log(RetreatDist))) + 
   geom_point(color = "grey", 
              size = 1) +
-  geom_line(aes(x = log_tdh, y = .fitted), 
+  geom_line(aes(x = log_TotalSub, y = .fitted), 
             size = 1, 
@@
             data = predicted.distance) + 
-  geom_ribbon(aes(x = log_tdh, 
+  geom_ribbon(aes(x = log_TotalSub, 
                   ymin = .fitted - 1.96 * .se.fit, 
@@
               alpha = 0.25) +
-  scale_y_continuous(limits = c(min(log(near$RetreatDist)), max(log(near$RetreatDist)) + 0.1 * diff(range(log(near$RetreatDist))))) +  
-  theme_classic() +
-  xlab("Highway Disturbance [log(vehicles/day/m)]") +
+  scale_y_continuous(limits = c(min(log(near_center$RetreatDist)), max(log(near_center$RetreatDist)) + 0.1 * diff(range(log(near_center$RetreatDist))))) +  
+  theme_classic() +
+  xlab("Plant Species Richness [log()]") +
   ylab("Distance from Focal Web \nto Neighbor Web [log(cm)]") + 
@@
         axis.title.y = element_blank()) +
-  annotate(geom = "text", x = min((predicted.distance$log_tdh)) + diff(range((predicted.distance$log_tdh)))/2, y = max(log(near$RetreatDist)), label = "***", color = "black", size = 4)
-
-# Road Disturbance
-nd <- data.frame(log_patch = mean(near$log_patch), 
-                 log_tdr = seq(2.73, 7.22, 0.05),
-                 log_tdh = mean(near$log_tdh))
+  annotate(geom = "text", x = min(predicted.distance$log_TotalSub) + diff(range(predicted.distance$log_TotalSub))/2, y = max(log(near_center$RetreatDist)), label = "***", color = "black", size = 4)
+
+# Spectral Radiance
+nd <- data.frame(log_TotalSub = mean(near_center$log_TotalSub), 
+                 spec_rad = seq(149, 163, 0.15),
+                 road_length_m = mean(near_center$road_length_m))
 predicted.distance <- augment(top_model_wd_c, 
@@
                               se_fit = TRUE)
-dist_forest_tdr <- ggplot(near, aes(x = log_tdr, y = log(RetreatDist))) + 
+dist_center_spec <- ggplot(near_center, aes(x = (spec_rad), y = log(RetreatDist))) + 
   geom_point(color = "grey", 
              size = 1) +
-  geom_line(aes(x = log_tdr, y = .fitted), 
+  geom_line(aes(x = (spec_rad), y = .fitted), 
             size = 1, 
@@
             data = predicted.distance) + 
-  geom_ribbon(aes(x = log_tdr, 
+  geom_ribbon(aes(x = (spec_rad), 
                   ymin = .fitted - 1.96 * .se.fit, 
@@
               alpha = 0.25) +
-  scale_y_continuous(limits = c(min(log(near$RetreatDist)), max(log(near$RetreatDist)) + 0.1 * diff(range(log(near$RetreatDist))))) +  
-  theme_classic() +
-  xlab("Road Disturbance [log(vehicles/day/m)]") +
+  scale_y_continuous(limits = c(min(log(near_center$RetreatDist)), max(log(near_center$RetreatDist)) + 0.1 * diff(range(log(near_center$RetreatDist))))) +  
+  theme_classic() +
+  xlab("Spectral Radiance \n[Watts/(m² * sr * µm)]") + 
   ylab("Distance from Focal Web \nto Neighbor Web [log(cm)]") + 
@@
         axis.title.y = element_blank()) +
-  annotate(geom = "text", x = min((predicted.distance$log_tdr)) + diff(range((predicted.distance$log_tdr)))/2, y = max(log(near$RetreatDist)), label = "***", color = "black", size = 4)
-
-dist_forest_patch
-dist_forest_tdr
-dist_forest_tdh
+  annotate(geom = "text", x = min((predicted.distance$spec_rad)) + diff(range((predicted.distance$spec_rad)))/2, y = max(log(near_center$RetreatDist)), label = "***", color = "black", size = 4)
+
+# Road Length
+nd <- data.frame(log_TotalSub = mean(near_center$log_TotalSub), 
+                 spec_rad = mean(near_center$spec_rad),
+                 road_length_m = seq(47, 117, 0.6))
+predicted.distance <- augment(top_model_wd_c, 
+                              newdata = nd, 
+                              se_fit = TRUE)
+dist_center_road <- ggplot(near_center, aes(x = (road_length_m), y = log(RetreatDist))) + 
+  geom_point(color = "grey", 
+             size = 1) +
+  geom_line(aes(x = (road_length_m), y = (.fitted)), 
+            size = 1, 
+            color = colorc, 
+            data = predicted.distance) + 
+  geom_ribbon(aes(x = (road_length_m), 
+                  ymin = .fitted - 1.96 * .se.fit, 
+                  ymax = .fitted + 1.96 * .se.fit), 
+              fill = colorc, 
+              data = predicted.distance, 
+              inherit.aes = FALSE, 
+              alpha = 0.25) +
+  scale_y_continuous(limits = c(min(log(near_center$RetreatDist)), max(log(near_center$RetreatDist)) + 0.1 * diff(range(log(near_center$RetreatDist))))) +  
+  theme_classic() +
+  xlab("Total Road Length [m]") +
+  ylab("Distance from Focal Web \nto Neighbor Web [log(cm)]") + 
+  theme(text = element_text(size = 10)) + 
+  theme(axis.text.x = element_text(colour = "black", size = 10)) + 
+  theme(axis.text.y = element_text(colour = "black", size = 10)) +
+  theme(axis.text.x = element_blank(), 
+        axis.title.x = element_blank(),
+        axis.text.y = element_blank(),
+        axis.title.y = element_blank()) +
+  annotate(geom = "text", x = min((predicted.distance$road_length_m)) + diff(range((predicted.distance$road_length_m)))/2, y = max(log(near_center$RetreatDist)), label = "***", color = "black", size = 4)
+
+dist_center_plant
+dist_center_spec
+dist_center_road
 ```
@@
 summary(dist_land)
-anova(dist_land, test = "Chisq")
+car::Anova(dist_land, test.statistic = "LR")
 comp <- glht(dist_land, linfct = mcp(Land = "Tukey"))
@@
 
+**Distance between webs significantly varies** by land cover class (Chi = 3629.3, df = 4, p < 0.001).
+
 ## Response Variable: Web Height
@@
 
+**Webs are significantly higher in the urban forest** than the urban center (z = -2.384, df = 1, 21, p = 0.017).
+
 ### Web Height by Predictors
-
-Convergence issues that need addressed.
 
@@
 (Intercept)    3.1686     0.6215   5.098 3.43e-07 ***
-log_tdr       -0.1896     0.1023  -1.854  0.06378 .   *negative*
-log_TotalSub   0.4812     0.1659   2.901  0.00372 **  *positive*
+log_tdr       -0.1896     0.1023  -1.854  0.06378 .   **negative**
+log_TotalSub   0.4812     0.1659   2.901  0.00372 **  **positive**
 
@@
 (Intercept)     1.1283     0.8355   1.350  0.17687   
-tree100m_frac   5.0864     1.7266   2.946  0.00322 ** *positive*
+tree100m_frac   5.0864     1.7266   2.946  0.00322 ** **positive**
 
@@
 (Intercept)    2.0705     0.4687   4.417    1e-05 ***
-log_TotalSub   0.6449     0.3921   1.645      0.1     *positive*
+log_TotalSub   0.6449     0.3921   1.645      0.1     **positive**
 
@@
 (Intercept)                            2.6980     2.7479      2.7626   0.977   0.3288
-log_TotalSub                           0.7725     0.4093      0.4138   1.867   0.0619
+log_TotalSub                           0.7725     0.4093      0.4138   1.867   0.0619 .
 scale(road_length_m, center = FALSE)   1.0413     0.7533      0.7625   1.366   0.1720
@@
         axis.title.y = element_blank()) +
-  annotate(geom = "text", x = min(predictions$log_tdr) + diff(range(predictions$log_tdr))/2, y = max(log(webs$RetreatHeight)), label = ".", color = "black", size = 4)
+  annotate(geom = "text", x = min(predictions$log_tdr) + diff(range(predictions$log_tdr))/2, y = max(log(webs$RetreatHeight)), label = "N. S.", color = "black", size = 4)
 
@@
 ```
+
+**Web height varies significantly** across land cover class (chi = 10.495, df = 4, p = 0.033).

### 2022-11-26 data_analysis.Rmd
Finished making figures and tables

@@
 library(multcomp) # for pairwise comparisons of land cover categories
+library(flextable) # making tables
 ```
@@
 # includes data for every measured web (multiple per site)
+land_cover <- read.table(file = "data/land_cover_table.txt", header = TRUE) # for land cover table
+pred_table <- read.table(file = "data/pred_table.txt", header = TRUE) # for predictor stats table
+substrates <- read.table(file = "data/substrate.txt", header = TRUE) # for substrate figure
+site_info <- read.table(file = "data/site_info.txt", header = TRUE) # for site information table
+pred_table_avg <- read.table(file = "data/pred_table_avg.txt", header = TRUE) # for predictor stats table
 ```
@@
   filter(Neighbor == 1)
+
+webs$RetreatHeight[webs$RetreatHeight == 0] <- 0.1
 ```
@@
 
-raw_plot <- ggplot(sites, aes(x = Location, y = WalkDist)) + 
+raw_plot_search <- ggplot(sites, aes(x = Location, y = WalkDist)) + 
   geom_jitter(color = "grey", width = 0.1) +
@@
     scale_y_continuous(limits = c(0, 275), breaks = c(0, 50, 100, 150, 200, 250)) +
+    xlab("Collection Location") +
     ylab("Search Distance [m]") + 
-    theme(text = element_text(size = 16)) + 
-    theme(axis.text.x = element_text(colour = "black", size = 16)) + 
-    theme(axis.text.y = element_text(colour = "black", size = 16),
+    theme(text = element_text(size = 10)) + 
+    theme(axis.text.x = element_text(colour = "black", size = 10)) + 
+    theme(axis.text.y = element_text(colour = "black", size = 10),
         axis.title.x = element_blank()) +
-    theme(legend.position = "none") +
-    ggtitle("Raw Data")
+    theme(legend.position = "none")
 
@@
 
-poisson_plot <- ggplot(sites, aes(x = Location, y = WalkDist)) + 
+poisson_plot_search <- ggplot(sites, aes(x = Location, y = WalkDist)) + 
   geom_jitter(color = "grey", width = 0.1) +
@@
   scale_y_continuous(limits = c(0, 275), breaks = c(0, 50, 100, 150, 200, 250)) +
+  xlab("Collection Location") +
   ylab("Search Distance [m]") + 
-  theme(text = element_text(size = 16)) + 
-  theme(axis.text.x = element_text(colour = "black", size = 16)) + 
-  theme(axis.text.y = element_text(colour = "black", size = 16),
+  theme(text = element_text(size = 10)) + 
+  theme(axis.text.x = element_text(colour = "black", size = 10)) + 
+  theme(axis.text.y = element_text(colour = "black", size = 10),
         axis.title.x = element_blank()) +
   theme(legend.position = "none") +
-  annotate(geom = "text", x = 1.5, y = 275, label = "***", color = "black", size = 10) +
-  ggtitle("Poisson Distribution")
+  annotate(geom = "text", x = 1.5, y = 275, label = "***", color = "black", size = 5)
 
@@
 
-log_plot <- ggplot(sites, aes(x = Location, y = (WalkDist))) + 
+log_plot_search <- ggplot(sites, aes(x = Location, y = (WalkDist))) + 
   geom_jitter(color = "grey", width = 0.1) +
@@
   scale_y_continuous(limits = c(0, 275), breaks = c(0, 50, 100, 150, 200, 250)) +
+  xlab("Collection Location") +
   ylab("Search Distance [m]") + 
-  theme(text = element_text(size = 16)) + 
-  theme(axis.text.x = element_text(colour = "black", size = 16)) + 
-  theme(axis.text.y = element_text(colour = "black", size = 16),
+  theme(text = element_text(size = 10)) + 
+  theme(axis.text.x = element_text(colour = "black", size = 10)) + 
+  theme(axis.text.y = element_text(colour = "black", size = 10),
         axis.title.x = element_blank()) +
   theme(legend.position = "none") +
-  annotate(geom = "text", x = 1.5, y = 275, label = "", color = "black", size = 10) +
-  ggtitle("Log-Transformed")
-
-ggarrange(raw_plot, poisson_plot, log_plot, nrow = 1)
+  annotate(geom = "text", x = 1.5, y = 275, label = "", color = "black", size = 5)
+
+ggarrange(raw_plot_search, 
+          poisson_plot_search, 
+          log_plot_search, 
+          labels = c("Raw Data", "Poisson Distribution", "Log-Transformed"),
+          nrow = 1)
 ```
@@
 
-ggplot(sites, aes(x = Land, y = WalkDist)) + 
+search_land_plot <- ggplot(sites, aes(x = Land, y = WalkDist)) + 
   geom_jitter(color = "grey", width = 0.1, size = 0.5) +
@@
   annotate(geom="text", x=5, y=max(sites$WalkDist), label="A", color="black", size = 3)
+
+search_land_plot
 ```
@@
 
-raw_plot <- ggplot(sites, aes(x = Location, y = NumWebs)) + 
+raw_plot_webs <- ggplot(sites, aes(x = Location, y = NumWebs)) + 
   geom_jitter(color = "grey", width = 0.1) +
@@
     ylab("Number of Webs") + 
-    theme(text = element_text(size = 16)) + 
-    theme(axis.text.x = element_text(colour = "black", size = 16)) + 
-    theme(axis.text.y = element_text(colour = "black", size = 16),
+    theme(text = element_text(size = 10)) + 
+    theme(axis.text.x = element_text(colour = "black", size = 10)) + 
+    theme(axis.text.y = element_text(colour = "black", size = 10),
         axis.title.x = element_blank()) +
-    theme(legend.position = "none") +
-    ggtitle("Raw Data")
+    theme(legend.position = "none")
 
@@
 
-poisson_plot <- ggplot(sites, aes(x = Location, y = NumWebs)) + 
+poisson_plot_webs <- ggplot(sites, aes(x = Location, y = NumWebs)) + 
   geom_jitter(color = "grey", width = 0.1) +
@@
   ylab("Number of Webs") + 
-  theme(text = element_text(size = 16)) + 
-  theme(axis.text.x = element_text(colour = "black", size = 16)) + 
-  theme(axis.text.y = element_text(colour = "black", size = 16),
+  theme(text = element_text(size = 10)) + 
+  theme(axis.text.x = element_text(colour = "black", size = 10)) + 
+  theme(axis.text.y = element_text(colour = "black", size = 10),
         axis.title.x = element_blank()) +
   theme(legend.position = "none") +
-  annotate(geom = "text", x = 1.5, y = 75, label = "***", color = "black", size = 10) +
-  ggtitle("Poisson Distribution")
+  annotate(geom = "text", x = 1.5, y = 75, label = "***", color = "black", size = 5)
 
@@
 
-log_plot <- ggplot(sites, aes(x = Location, y = (NumWebs))) + 
+log_plot_webs <- ggplot(sites, aes(x = Location, y = (NumWebs))) + 
   geom_jitter(color = "grey", width = 0.1) +
@@
   ylab("Number of Webs") + 
-  theme(text = element_text(size = 16)) + 
-  theme(axis.text.x = element_text(colour = "black", size = 16)) + 
-  theme(axis.text.y = element_text(colour = "black", size = 16),
+  theme(text = element_text(size = 10)) + 
+  theme(axis.text.x = element_text(colour = "black", size = 10)) + 
+  theme(axis.text.y = element_text(colour = "black", size = 10),
         axis.title.x = element_blank()) +
   theme(legend.position = "none") +
-  annotate(geom = "text", x = 1.5, y = 75, label = "**", color = "black", size = 10) +
-  ggtitle("Log-Transformed")
-
-ggarrange(raw_plot, poisson_plot, log_plot, nrow = 1)
+  annotate(geom = "text", x = 1.5, y = 75, label = "**", color = "black", size = 5)
+
+ggarrange(raw_plot_webs, 
+          poisson_plot_webs, 
+          log_plot_webs, 
+          labels = c("Raw Data", "Poisson Distribution", "Log-Transformed"),
+          nrow = 1)
 ```
@@
 
-ggplot(sites, aes(x = Land, y = NumWebs)) + 
+webs_land_plot <- ggplot(sites, aes(x = Land, y = NumWebs)) + 
   geom_jitter(color = "grey", width = 0.1, size = 0.5) +
@@
   annotate(geom="text", x=5, y=max(sites$NumWebs), label="B", color="black", size = 3)
+
+webs_land_plot_nox <- webs_land_plot + 
+  theme(axis.text.x = element_blank()) + 
+  theme(axis.title.x = element_blank())
+
+webs_land_plot
 ```
@@
 
-raw_plot <- ggplot(sites, aes(x = Location, y = NumSpiders)) + 
+raw_plot_spiders <- ggplot(sites, aes(x = Location, y = NumSpiders)) + 
   geom_jitter(color = "grey", width = 0.1) +
@@
     ylab("Number of Spiders") + 
-    theme(text = element_text(size = 16)) + 
-    theme(axis.text.x = element_text(colour = "black", size = 16)) + 
-    theme(axis.text.y = element_text(colour = "black", size = 16),
+    theme(text = element_text(size = 10)) + 
+    theme(axis.text.x = element_text(colour = "black", size = 10)) + 
+    theme(axis.text.y = element_text(colour = "black", size = 10),
         axis.title.x = element_blank()) +
-    theme(legend.position = "none") +
-    ggtitle("Raw Data")
+    theme(legend.position = "none")
 
@@
 
-poisson_plot <- ggplot(sites, aes(x = Location, y = NumSpiders)) + 
+poisson_plot_spiders <- ggplot(sites, aes(x = Location, y = NumSpiders)) + 
   geom_jitter(color = "grey", width = 0.1) +
@@
   ylab("Number of Spiders") + 
-  theme(text = element_text(size = 16)) + 
-  theme(axis.text.x = element_text(colour = "black", size = 16)) + 
-  theme(axis.text.y = element_text(colour = "black", size = 16),
+  theme(text = element_text(size = 10)) + 
+  theme(axis.text.x = element_text(colour = "black", size = 10)) + 
+  theme(axis.text.y = element_text(colour = "black", size = 10),
         axis.title.x = element_blank()) +
   theme(legend.position = "none") +
-  annotate(geom = "text", x = 1.5, y = 25, label = "***", color = "black", size = 10) +
-  ggtitle("Poisson Distribution")
+  annotate(geom = "text", x = 1.5, y = 25, label = "***", color = "black", size = 5)
 
@@
 
-log_plot <- ggplot(sites, aes(x = Location, y = (NumSpiders))) + 
+log_plot_spiders <- ggplot(sites, aes(x = Location, y = (NumSpiders))) + 
   geom_jitter(color = "grey", width = 0.1) +
@@
   ylab("Number of Spiders") + 
-  theme(text = element_text(size = 16)) + 
-  theme(axis.text.x = element_text(colour = "black", size = 16)) + 
-  theme(axis.text.y = element_text(colour = "black", size = 16),
+  theme(text = element_text(size = 10)) + 
+  theme(axis.text.x = element_text(colour = "black", size = 10)) + 
+  theme(axis.text.y = element_text(colour = "black", size = 10),
         axis.title.x = element_blank()) +
   theme(legend.position = "none") +
-  annotate(geom = "text", x = 1.5, y = 25, label = ".", color = "black", size = 10) +
-  ggtitle("Log-Transformed")
-
-ggarrange(raw_plot, poisson_plot, log_plot, nrow = 1)
+  annotate(geom = "text", x = 1.5, y = 25, label = ".", color = "black", size = 5)
+
+ggarrange(raw_plot_spiders, 
+          poisson_plot_spiders, 
+          log_plot_spiders, 
+          labels = c("Raw Data", "Poisson Distribution", "Log-Transformed"),
+          nrow = 1)
 ```
@@
 
-ggplot(sites, aes(x = Land, y = NumSpiders)) + 
+spiders_land_plot <- ggplot(sites, aes(x = Land, y = NumSpiders)) + 
   geom_jitter(color = "grey", width = 0.1, size = 0.5) +
@@
   annotate(geom="text", x=5, y=max(sites$NumSpiders), label="B", color="black", size = 3)
+
+spiders_land_plot_nox <- spiders_land_plot + 
+  theme(axis.text.x = element_blank()) + 
+  theme(axis.title.x = element_blank())
+
+spiders_land_plot
 ```
@@
 
-raw_plot <- ggplot(web_dist, aes(x = Neighbor, y = RetreatDist)) + 
+raw_plot_dist <- ggplot(web_dist, aes(x = Neighbor, y = RetreatDist)) + 
   geom_jitter(color = "grey", width = 0.1) +
@@
     ylab("Distance from Focal Web \nto Neighbor Web [cm]") + 
-    theme(text = element_text(size = 16)) + 
-    theme(axis.text.x = element_text(colour = "black", size = 16)) + 
-    theme(axis.text.y = element_text(colour = "black", size = 16)) +
-    ggtitle("Raw Data")
+    theme(text = element_text(size = 10)) + 
+    theme(axis.text.x = element_text(colour = "black", size = 10)) + 
+    theme(axis.text.y = element_text(colour = "black", size = 10)) +
+    theme(legend.position = "none")
 
@@
 
-poisson_plot <- ggplot(web_dist, aes(x = Neighbor, y = RetreatDist)) + 
+poisson_plot_dist <- ggplot(web_dist, aes(x = Neighbor, y = RetreatDist)) + 
   geom_jitter(color = "grey", width = 0.1) +
@@
   ylab("Distance from Focal Web \nto Neighbor Web [cm]") + 
-  theme(text = element_text(size = 16)) + 
-  theme(axis.text.x = element_text(colour = "black", size = 16)) + 
-  theme(axis.text.y = element_text(colour = "black", size = 16)) +
-  ggtitle("Poisson Distribution")
+  theme(text = element_text(size = 10)) + 
+  theme(axis.text.x = element_text(colour = "black", size = 10)) + 
+  theme(axis.text.y = element_text(colour = "black", size = 10)) +
+  theme(legend.position = "none")
 
@@
 
-log_plot <- ggplot(web_dist, aes(x = Neighbor, y = (RetreatDist))) + 
+log_plot_dist <- ggplot(web_dist, aes(x = Neighbor, y = (RetreatDist))) + 
   geom_jitter(color = "grey", width = 0.1) +
@@
   ylab("Distance from Focal Web \nto Neighbor Web [cm]") + 
-  theme(text = element_text(size = 16)) + 
-  theme(axis.text.x = element_text(colour = "black", size = 16)) + 
-  theme(axis.text.y = element_text(colour = "black", size = 16)) +
-  ggtitle("Log-Transformed")
-
-ggarrange(raw_plot, poisson_plot, log_plot, nrow = 1, common.legend = TRUE)
+  theme(text = element_text(size = 10)) + 
+  theme(axis.text.x = element_text(colour = "black", size = 10)) + 
+  theme(axis.text.y = element_text(colour = "black", size = 10))
+
+ggarrange(raw_plot_dist, 
+          poisson_plot_dist, 
+          log_plot_dist, 
+          labels = c("Raw Data", "Poisson Distribution", "Log-Transformed"),
+          nrow = 1, 
+          common.legend = TRUE)
 ```
@@
 
-ggplot(near, aes(x = Land, y = RetreatDist)) + 
+dist_land_plot <- ggplot(near, aes(x = Land, y = RetreatDist)) + 
   geom_jitter(color = "grey", width = 0.1, size = 0.5) +
@@
   xlab("Land Cover Class") +
-  ylab("Distance from Focal Web \nto Neighbor Web (cm)") + 
+  ylab("Distance from Focal \nWeb to Neighbor Web (cm)") + 
   theme(text = element_text(size = 10)) + 
@@
   theme(axis.text.x = element_text(angle = 90, vjust = 1, hjust=1)) +
-  annotate(geom="text", x=1, y=max(sites$NumSpiders), label="A", color="black", size = 3) +
-  annotate(geom="text", x=2, y=max(sites$NumSpiders), label="B", color="black", size = 3) +
-  annotate(geom="text", x=3, y=max(sites$NumSpiders), label="C", color="black", size = 3) +
-  annotate(geom="text", x=4, y=max(sites$NumSpiders), label="D", color="black", size = 3) +
-  annotate(geom="text", x=5, y=max(sites$NumSpiders), label="E", color="black", size = 3)
+  annotate(geom="text", x=1, y=max(near$RetreatDist), label="A", color="black", size = 3) +
+  annotate(geom="text", x=2, y=max(near$RetreatDist), label="B", color="black", size = 3) +
+  annotate(geom="text", x=3, y=max(near$RetreatDist), label="C", color="black", size = 3) +
+  annotate(geom="text", x=4, y=max(near$RetreatDist), label="D", color="black", size = 3) +
+  annotate(geom="text", x=5, y=max(near$RetreatDist), label="E", color="black", size = 3)
+
+dist_land_plot
 ```
@@
 
-raw_plot <- ggplot(webs, aes(x = Location, y = RetreatHeight)) + 
+raw_plot_height <- ggplot(webs, aes(x = Location, y = RetreatHeight)) + 
   geom_jitter(color = "grey", width = 0.1) +
@@
     ylab("Web Height [cm]") + 
-    theme(text = element_text(size = 16)) + 
-    theme(axis.text.x = element_text(colour = "black", size = 16)) + 
-    theme(axis.text.y = element_text(colour = "black", size = 16),
+    theme(text = element_text(size = 10)) + 
+    theme(axis.text.x = element_text(colour = "black", size = 10)) + 
+    theme(axis.text.y = element_text(colour = "black", size = 10),
         axis.title.x = element_blank()) +
-    theme(legend.position = "none") +
-    ggtitle("Raw Data")
+    theme(legend.position = "none")
 
@@
 
-poisson_plot <- ggplot(webs, aes(x = Location, y = RetreatHeight)) + 
+poisson_plot_height <- ggplot(webs, aes(x = Location, y = RetreatHeight)) + 
   geom_jitter(color = "grey", width = 0.1) +
@@
     ylab("Web Height [cm]") + 
-    theme(text = element_text(size = 16)) + 
-    theme(axis.text.x = element_text(colour = "black", size = 16)) + 
-    theme(axis.text.y = element_text(colour = "black", size = 16),
+    theme(text = element_text(size = 10)) + 
+    theme(axis.text.x = element_text(colour = "black", size = 10)) + 
+    theme(axis.text.y = element_text(colour = "black", size = 10),
         axis.title.x = element_blank()) +
     theme(legend.position = "none") +
-    ggtitle("Poisson Distribution")
+    annotate(geom = "text", x = 1.5, y = 210, label = "*", color = "black", size = 5)
 
@@
 
-log_plot <- ggplot(webs, aes(x = Location, y = (RetreatHeight))) + 
+log_plot_height <- ggplot(webs, aes(x = Location, y = (RetreatHeight))) + 
   geom_jitter(color = "grey", width = 0.1) +
@@
     ylab("Web Height [cm]") + 
-    theme(text = element_text(size = 16)) + 
-    theme(axis.text.x = element_text(colour = "black", size = 16)) + 
-    theme(axis.text.y = element_text(colour = "black", size = 16),
+    theme(text = element_text(size = 10)) + 
+    theme(axis.text.x = element_text(colour = "black", size = 10)) + 
+    theme(axis.text.y = element_text(colour = "black", size = 10),
         axis.title.x = element_blank()) +
     theme(legend.position = "none") +
-    ggtitle("Log Transformation")
-
-ggarrange(raw_plot, poisson_plot, log_plot, nrow = 1, common.legend = TRUE)
+    annotate(geom = "text", x = 1.5, y = 210, label = "*", color = "black", size = 5)
+
+ggarrange(raw_plot_height, 
+          poisson_plot_height, 
+          log_plot_height, 
+          labels = c("Raw Data", "Poisson Distribution", "Log-Transformed"),
+          nrow = 1, 
+          common.legend = TRUE)
 ```
@@
 
-ggplot(webs, aes(x = Land, y = RetreatHeight)) + 
+height_land_plot <- ggplot(webs, aes(x = Land, y = RetreatHeight)) + 
   geom_jitter(color = "grey", width = 0.1, size = 0.5) +
@@
   annotate(geom="text", x=5, y=max(webs$RetreatHeight), label="A", color="black", size = 3)
+
+height_land_plot
 ```
@@
 **Web height varies significantly** across land cover class (chi = 10.495, df = 4, p = 0.033).
+
+## Figures for Manuscript
+
+### Measurement by Location Figure
+
+```{r main}
+blankPlot <- ggplot() + 
+  geom_blank(aes(1,1)) + 
+  cowplot::theme_nothing()
+
+main_row1 <- ggarrange(poisson_plot_search, poisson_plot_webs, poisson_plot_spiders, labels = c("a", "b", "c"), nrow = 1, font.label = list(size = 10))
+main_row2 <- ggarrange(poisson_plot_dist, poisson_plot_height, blankPlot, labels = c("d", "e", ""), nrow = 1, font.label = list(size = 10))
+main <- ggarrange(main_row1, main_row2, nrow = 2, font.label = list(size = 10))
+
+#saveRDS(main, "manuscript/figures/main.Rds")
+```
+
+### Predictors of Web and Spider Abundance
+
+```{r predictors_abund}
+webs_text <- as_ggplot(text_grob(paste("Number of \nWebs \n[log()]"), size = 10))
+spiders_text <- as_ggplot(text_grob(paste("Number of \nSpiders \n[log()]"), size = 10))
+plant_text <- as_ggplot(text_grob(paste("Plant Species \nRichness \n[log()]"), size = 10))
+patch_text <-as_ggplot(text_grob(paste("Patch Area \n[log(km²)]"), size = 10))
+highway_text <- as_ggplot(text_grob(paste("Highway Disturb. \n[log(cars/\nday/m)]"), size = 10))
+rlength_text <- as_ggplot(text_grob(paste("Road \nLength [m]"), size = 10))
+blankPlot <- ggplot()+geom_blank(aes(1,1)) + 
+  cowplot::theme_nothing()
+
+pa <- ggarrange(webs_text, webs_center_plant, webs_center_patch, webs_center_tdh, webs_center_road,
+           spiders_text, spiders_center_plant, spiders_center_patch, spiders_center_tdh, spiders_center_road,
+          ncol = 5, nrow = 2, widths = c(0.1, 0.225, 0.225, 0.225, 0.225))
+
+labels <- ggarrange(blankPlot, plant_text, patch_text, highway_text, rlength_text, ncol = 5, nrow = 1, widths = c(0.1, 0.225, 0.225, 0.225, 0.225))
+
+predictors_abund <- ggarrange(pa, labels, nrow = 2, heights = c(0.8, 0.2))
+#saveRDS(predictors_abund, "manuscript/figures/predictors_abund.Rds")
+```
+
+### Predictors of Aggregation
+
+```{r predictors_agg}
+wd_text1 <- as_ggplot(text_grob(paste("Forest \nNearest \nNeighbor \nDist. [log(cm)]"), size = 10))
+wd_text2 <- as_ggplot(text_grob(paste("Center \nNearest \nNeighbor \nDist. [log(cm)]"), size = 10))
+tree_text <- as_ggplot(text_grob(paste("Tree Cover [%]"), size = 10))
+plant_text <- as_ggplot(text_grob(paste("Plant Species \nRichness \n[log()]"), size = 10))
+road_text <- as_ggplot(text_grob(paste("Road Disturb. \n[log(cars/day/m)]"), size = 10))
+highway_text <- as_ggplot(text_grob(paste("Highway Disturb. \n[log(cars/day/m)]"), size = 10))
+spec_text <- as_ggplot(text_grob(paste("Spectral \nRadiance \n[Watts/(m²*sr*µm)]"), size = 10))
+rlength_text <- as_ggplot(text_grob(paste("Road \nLength [m]"), size = 10))
+blankPlot <- ggplot()+geom_blank(aes(1,1)) + 
+  cowplot::theme_nothing()
+
+agg1 <- ggarrange(wd_text1, dist_forest_plant, dist_forest_tree, dist_forest_tdr, dist_forest_tdh,
+          ncol = 5, nrow = 1, widths = c(0.12, 0.22, 0.22, 0.22, 0.22))
+
+agg2 <- ggarrange(wd_text2, dist_center_plant, dist_center_spec, dist_center_road, blankPlot,
+          ncol = 5, nrow = 1, widths = c(0.12, 0.22, 0.22, 0.22, 0.22))
+
+labels1 <- ggarrange(blankPlot, plant_text, tree_text, road_text, highway_text, ncol = 5, nrow = 1, widths = c(0.1, 0.225, 0.225, 0.225, 0.225))
+
+labels2 <- ggarrange(blankPlot, plant_text, spec_text, rlength_text, blankPlot, ncol = 5, nrow = 1, widths = c(0.1, 0.225, 0.225, 0.225, 0.225))
+
+predictors_agg <- ggarrange(agg1, labels1, agg2, labels2, nrow = 4, heights = c(0.35, 0.15, 0.35, 0.15))
+#saveRDS(predictors_agg, "manuscript/figures/predictors_agg.Rds")
+```
+
+## Tables for Manuscript
+
+### Landscape Features by Location
+
+```{r landscape_table}
+rownames(land_cover) <- c("Area (sq.
+km)", "Tree Cover (%)", "Impervious Cover (%)", "Urban Cover (%)", "Urban, High Intensity (%)", "Urban, Medium Intensity (%)", "Urban, low Intensity (%)", "Urban, Open Space (%)", "Forest Cover (%)", "Deciduous Forest (%)", "Mixed Forest (%)", "Evergreen Forest (%)", "Woody Wetlands (%)", "Other Cover (%)", "Herbaceous Wetlands (%)", "Grassland Herbaceous (%)", "Pasture (%)", "Cultivated Crop (%)", "Open Water (%)")
+names <- rownames(land_cover)
+rownames(land_cover) <- seq(1:nrow(land_cover))
+land_cover <- cbind(names, land_cover)
+colnames(land_cover) <- c(" ", "Lincoln City Limits", "UNL City Campus \nUrban Center", "Wilderness Park \nUrban Forest")
+flextable(land_cover[ ,1:4]) %>% 
+  autofit() %>% 
+  hline(i = c("3", "4", "8", "9", "13", "14"), part = "body") %>% 
+  bg(i = c("4", "9", "14"), bg = "grey95") %>% 
+  bold(bold = TRUE, part = "header") %>% 
+  fontsize(size = 10, part = "all") %>% 
+  align(align = "center", part = "all") %>% 
+  set_caption("") %>% 
+  save_as_image(path = here::here("manuscript/figures/landscape.png"))
+```
+
+### Predictors by Location
+
+```{r pred_location, fig.width = 6.85, dpi = 300}
+mean_se1 <- c("Mean ± Std.
+Error", "Wilderness Park \nUrban Forest", "47.15 ± 2.17", "1.27 ± 0.36", "137.44 ± 3.71", "5.89 ± 0.77", "12.18 ± 1.65", "37,049.12 ± 2.79", "52.98 ± 1.88", "33.78 ± 1.81", "15.67 ± 1.25")
+mean_se2 <- c("Mean ± Std.
+Error", "UNL City Campus \n Urban Center", "1.58 ± 0.36", "76.52 ± 2.53", "153.39 ± 3.58", "116.90 ± 3.12", "2.97 ± 1.35", "437.03 ± 2.04", "194.42 ± 1.94", "52.46 ± 1.78", "93.03 ± 2.78")
+pred_location <- data.frame(mean_se1, mean_se2)
+rownames(pred_location) <- c("", " ", "Percent Tree Cover [%]", "Percent Impervious Cover [%]", "Spectral Radiance [Watts/(m² * sr * µm)]", "Artificial Night Sky Radiance [mcd/m²]", "Plant Species Richness", "Patch Area [m²]", "Road Disturbance [vehicles/day/m]", "Highway Disturbance [vehicles/day/m]", "Total Road Length [m]")
+names <- rownames(pred_location)
+rownames(pred_location) <- seq(1:nrow(pred_location))
+pred_location <- cbind(names, pred_location)
+colnames(pred_location) <- c(" ", "Mean ± Std. Error", "Mean ± Std. Error")
+flextable(pred_location[ ,1:3]) %>% 
+  delete_part(part = "header") %>% 
+  autofit() %>% 
+  merge_h(part = "body") %>% 
+  bold(bold = TRUE,i = c("1", "2"), part = "body") %>% 
+  hline(i = c("1", "2", "11"), part = "body", border = officer::fp_border(width = 2)) %>% 
+  hline_top(part = "body", border = officer::fp_border(width = 2)) %>% 
+  fontsize(size = 10, part = "all") %>% 
+  align(align = "center", part = "all") %>% 
+  set_caption("") %>% 
+  save_as_image(path = here::here("manuscript/figures/pred_location.png"))
+```
+
+### Predictor Stats Table
+
+```{r pred_table}
+pred_table <- read.table(file = "data/pred_table.txt", header = TRUE) # for predictor stats table
+
+pred_table <- pred_table %>% 
+  mutate(Variable = factor(Variable),
+         Variable = fct_recode(Variable, "Number of Webs" = "NumWebs",
+                               "Number of Spiders" = "NumSpiders",
+                               "Nearest Neighbor Distance" = "RetreatDist",
+                               "Web Height" = "RetreatHeight"),
+         Predictor = factor(Predictor),
+         Predictor = fct_recode(Predictor, "Plant Species Richness" = "plant",
+                                "Road Disturbance" = "tdr",
+                                "Highway Disturbance" = "tdh",
+                                "Patch Area" = "patch",
+                                "Total Road Length" = "road",
+                                "Spectral Radiance" = "spec",
+                                "Percent Tree Cover" = "tree",
+                                "Proportion Tree Cover" = "tree_frac"),
+         org_Estimate = round(org_Estimate, 3),
+         bt_Estimate = round(bt_Estimate, 3),
+         org_SE = round(org_SE, 3),
+         bt_SE = round(bt_SE, 3),
+         Z = round(Z, 3),
+         P = round(P, 3),
+         R = round(R, 3),
+         AICc = round(AICc, 3))
+
+pred_table[pred_table == 0] <- ""
+
+pred_table <- pred_table %>% 
+  mutate(P = fct_recode(P, "< 0.001 ***" = "0.001",
+                        "   0.010 **" = "0.01",
+                        "   0.003 **" = "0.003",
+                        "   0.004 **" = "0.004",
+                        "   0.064 ." = "0.064",
+                        "   0.100 ." = "0.1")) %>% 
+  dplyr::select(-bt_Estimate, -bt_SE)
+
+colnames(pred_table) <- c('Variable','Model','Predictor', 'Estimate', 'Standard \nError', 'Z-Value', 'P-Value', 'McFadden\'s \nR²', 'AICc \nWeight')
+
+flextable(pred_table[ , 1:9]) %>% 
+  autofit() %>% 
+  merge_v(j = c('Variable', 'Model', 'McFadden\'s \nR²', 'AICc \nWeight'), part = "body") %>% 
+  bold(bold = TRUE, part = "header") %>% 
+  hline_bottom(part = "body", border = officer::fp_border(width = 2)) %>% 
+  border(j = 'Variable', border.bottom = officer::fp_border(width = 2)) %>% 
+  hline(i = c("8", "15", "24"), part = "body", border = officer::fp_border(width = 2)) %>%     
+  fontsize(size = 10, part = "all") %>% 
+  align(align = "center", part = "all") %>% 
+  valign(valign = "top", part = "all") %>% 
+  set_caption("") %>% 
+  footnote(i = c(1:3, 5:7, 9:10, 12:14, 16:17, 19:22, 25:26, 28), j = 3, value = as_paragraph(
+    c("Predictors that were log-transformed prior to model evaluation. Estimate and standard errors are not back transformed.")), 
+    ref_symbols = c("a"), part = "body") %>% 
+    footnote(i = 27, j = 3, value = as_paragraph(
+    c("Tree cover is assessed as proportion (value from 0 to 1) rather than a percent (values 0 to 100) to avoid model convergence issues.")), 
+    ref_symbols = c("b"), part = "body") %>% 
+  save_as_image(path = here::here("manuscript/figures/pred_table.png"))
+```
+
+## Supplementary Figures and Tables
+
+### Substrate Figures
+
+```{r substrate}
+substrates %>% 
+  mutate(Location = fct_recode(Location, "Urban Center" = "Campus", "Urban Forest" = "Forest"),
+         Location = fct_relevel(Location, "Urban Forest", "Urban Center")) %>% 
+  ggplot(aes(x = Location, y = Number, fill = factor(Type, levels=c("Cement", "Metal", "Plastic", "Rocks", "Herb", "Litter", "Shrub", "Tree", "Vine")))) + 
+  geom_bar(position = "fill",stat = "identity", alpha=1.0) + 
+  scale_y_continuous(labels = scales::percent_format()) + 
+  theme(axis.title.x = element_blank()) + 
+  xlab("Collection Location") +
+  ylab("Percent of Web Substrates") + 
+  theme_classic() +
+  theme(text = element_text(size = 10)) + 
+  scale_fill_manual(values = c("#D94701", "#FD8D3C", "#FDBE85", "#FEEDDE", "#006D2C", "#31A354", "#74C476", "#BAE4B3", "#EDF8E9"), 
+                    labels = c("Cement", "Metal", "Plastic", "Rocks", "Herb", "Litter", "Shrub", "Tree", "Vine")) + 
+  labs(fill="Substrate Material") + 
+  theme(axis.text.x=element_text(colour="black", size=10)) + 
+  theme(axis.text.y=element_text(colour="black", size=10)) +
+  theme(legend.text=element_text(size=10))
+  ggsave("manuscript/figures/substrate_plot.png")
+```
+
+### Overall Predictor Plots
+```{r predictors_overall}
+dist_text <- as_ggplot(text_grob(paste("Search \nDistance \n[log(m)]"), size = 10))
+webs_text <- as_ggplot(text_grob(paste("Number of \nWebs \n[log()]"), size = 10))
+spiders_text <- as_ggplot(text_grob(paste("Number of \nSpiders \n[log()]"), size = 10))
+wd_text <- as_ggplot(text_grob(paste("Nearest \nNeighbor \nDist. [log(cm)]"), size = 10))
+wh_text <- as_ggplot(text_grob(paste("Web \nHeight \n[log(cm)]"), size = 10))
+plant_text <- as_ggplot(text_grob(paste("Plant Species \nRichness [log()]"), size = 10))
+road_text <- as_ggplot(text_grob(paste("Road Disturbance \n[log(vehicles/day/m)]"), size = 10))
+highway_text <- as_ggplot(text_grob(paste("Highway Disturbance \n[log(vehicles/day/m)]"), size = 10))
+blankPlot <- ggplot()+geom_blank(aes(1,1)) + 
+  cowplot::theme_nothing() 
+greyPlot <- ggplot()+geom_blank(aes(1,1)) + 
+  cowplot::theme_nothing() +
+  theme(panel.background = element_rect(fill = "grey", color = "white"))
+
+graphs <- ggarrange(webs_text, webs_plant, webs_tdr, webs_tdh,
+           spiders_text, spiders_plant, greyPlot, spiders_tdh,
+           wd_text, dist_plant, dist_tdr, greyPlot, 
+           wh_text, height_plant, height_tdr, greyPlot, 
+          ncol = 4, nrow = 4)
+
+labels <- ggarrange(blankPlot, plant_text, road_text, highway_text, ncol = 4, nrow = 1)
+
+predictors_overall <- ggarrange(graphs, labels, nrow = 2, heights = c(0.8, 0.2))
+#saveRDS(predictors_overall, "manuscript/figures/predictors_overall.Rds")
+```
+
+## Response Variables by Land Cover Class
+
+```{r land_plots}
+land_plots <- ggarrange(search_land_plot, ggarrange(webs_land_plot_nox, spiders_land_plot_nox,dist_land_plot, height_land_plot, labels = c("b", "c", "d", "e"), ncol = 2, nrow = 2, legend = "none", align = "hv"), labels = c("a"), widths = c(0.3, 0.7))
+
+land_plots
+#saveRDS(land_plots, "manuscript/figures/land_plots.Rds")
+```
+
+## Site Information Table
+
+```{r site_info}
+site_info <- site_info %>% 
+  mutate(Location = fct_recode(Location, "UNL City Campus - Urban Center" = "Campus", "Wilderness Park - Urban Forest" = "Forest"))
+colnames(site_info) <- c("Location", "Site ID", "Date", "Start Latitude", "Start Longitude", "Focal Web Latitude", "Focal Web Longitude", "Search Direction")
+flextable(site_info[ ,1:8]) %>% 
+  merge_v(j = "Location") %>% 
+  autofit(part = "body") %>% 
+  hline(i = c("12"), part = "body") %>% 
+  bold(bold = TRUE, part = "header") %>% 
+  fontsize(size = 10, part = "all") %>% 
+  set_caption("") %>% 
+  fontsize(size = 10, part = "all") %>% 
+  fix_border_issues(part = "all") %>% 
+  align(align = "center", part = "all") %>% 
+  save_as_image(path = here::here("manuscript/figures/site_info.png"))
+```
+
+## Table of Predictor Stats from Model Average
+
+```{r pred_table_avg}
+pred_table_avg <- read.table(file = "data/pred_table_avg.txt", header = TRUE) # for predictor stats table
+
+pred_table_avg <- pred_table_avg %>% 
+  mutate(Variable = factor(Variable),
+         Variable = fct_recode(Variable, "Number of Webs" = "NumWebs",
+                               "Nearest Neighbor Distance" = "RetreatDist",
+                               "Web Height" = "RetreatHeight"),
+         Predictor = factor(Predictor),
+         Predictor = fct_recode(Predictor, "Plant Species Richness" = "plant",
+                                "Road Disturbance" = "tdr",
+                                "Highway Disturbance" = "tdh",
+                                "Patch Area" = "patch",
+                                "Total Road Length" = "road",
+                                "Spectral Radiance" = "spec",
+                                "Percent Tree Cover" = "tree",
+                                "Proportion Tree Cover" = "tree_frac",
+                                "Spectral Radiance" = "spec_scale",
+                                "Total Road Length" = "road_scale"),
+         Model = factor(Model), 
+         Model = fct_recode(Model, "Center " = "Center2"),
+         Estimate = round(Estimate, 3),
+         SE = round(SE, 3),
+         Z = round(Z, 3),
+         P = round(P, 3),
+         AICc = round(AICc, 3))
+
+pred_table_avg <- pred_table_avg %>% 
+  mutate(P = factor(P),
+    P = fct_recode(P, "< 0.001 ***" = "0.001",
+                        "   0.033 *" = "0.033",
+                        "   0.003 **" = "0.003",
+                        "   0.043 *" = "0.043",
+                        "   0.010 *" = "0.01",
+                        "   0.054 ." = "0.054",
+                        "   0.228" = "0.228",
+                        "   0.005 **" = "0.005",
+                        "   0.086 ." = "0.086",
+                        "   0.172" = "0.172",
+                        "   0.062 ." = "0.062",
+                        "   0.299" = "0.299",
+                        "   0.377" = "0.377",
+                        "   0.120" = "0.12",
+                        "   0.241" = "0.241",
+                        "   0.172" = "0.172"))
+
+colnames(pred_table_avg) <- c('Variable','Model','Predictor', 'Estimate', 'Adj. Standard \nError', 'Z-Value', 'P-Value', 'AICc \nWeight')
+
+#saveRDS(pred_table_avg, file = "manuscript/figures/pred_table_avg.Rds")
+
+flextable(pred_table_avg[ , 1:8]) %>% 
+  autofit() %>% 
+  merge_v(j = c('Variable', 'Model', 'AICc \nWeight'), part = "body") %>% 
+  bold(bold = TRUE, part = "header") %>% 
+  hline_bottom(part = "body", border = officer::fp_border(width = 2)) %>% 
+  border(j = 'Variable', border.bottom = officer::fp_border(width = 2)) %>% 
+  hline(i = c("4", "8"), part = "body", border = officer::fp_border(width = 2)) %>%   
+  fix_border_issues(part = "all") %>% 
+  fontsize(size = 10, part = "all") %>% 
+  align(align = "center", part = "all") %>% 
+  valign(valign = "top", part = "all") %>% 
+  set_caption("") %>% 
+  footnote(i = c(1:3, 5:6, 9:11, 13:16, 18:19), j = 3, value = as_paragraph(
+    c("Predictors that were log-transformed prior to model evaluation. Estimate and standard errors are not back transformed.")), 
+    ref_symbols = c("a"), part = "body") %>% 
+    footnote(i = 12, j = 3, value = as_paragraph(
+    c("Tree cover is assessed as proportion (value from 0 to 1) rather than a percent (values 0 to 100) to avoid model convergence issues.")), 
+    ref_symbols = c("b"), part = "body") %>% 
+  footnote(i = c(17, 20), j = 3, value = as_paragraph(
+    c("Predictors were scaled (each value divided by the standard deviation) prior to model evaluation. Estimate and standard errors are not back transformed.")), 
+    ref_symbols = c("c"), part = "body")  %>% 
+  save_as_image(path = here::here("manuscript/figures/pred_table_avg.png"))
+```
+
+## Table of Land Stats
+
+```{r land_stats}
+Variable <- c("Search Distance", "Number of Webs", "Number of Spiders", "Neares Neighbor Distance", "Web Height")
+Chi <- c(340.32, 106.67, 31.65, 3629.30, 10.496)
+df <- c("4, 21", "4, 21", "4, 21", "4, 20", "4, 130")
+P <- c("< 0.001 ***", "< 0.001 ***", "< 0.001 ***", "< 0.001 ***", "  0.033 *")
+land_stats <- data.frame(Variable, Chi, df, P)
+colnames(land_stats) <- c('Variable','Likelihood Ratio \nChi-Squared','Degrees of Freedom', 'P-Value')
+
+flextable(land_stats[ , 1:4]) %>% 
+  autofit() %>% 
+  bold(bold = TRUE, part = "header") %>% 
+  fontsize(size = 10, part = "all") %>% 
+  align(align = "center", part = "all") %>% 
+  valign(valign = "top", part = "all") %>% 
+  set_caption("") %>% 
+  save_as_image(path = here::here("manuscript/figures/land_stats.png"))
+```

### 2022-11-26 manuscript/figures_tables.Rmd
Finished making figures and tables

---
output: 
  bookdown::word_document2:
    reference_docx: word_styles_reference_01.docx
    fig_caption: true
    number_sections: false
bibliography: [citations.bib]
csl: apa.csl
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
knitr::opts_knit$set(root.dir = "/Users/bjpessman/Documents/phd_research_code/Agelenopsis_aggregation/manuscript")
require(knitr)
```

```{r import, eval = FALSE, include = FALSE}
webs <- read.table(file = "data/webs.txt", header = TRUE) 
webs <- webs %>% 
  mutate(ID = factor(ID),
         Location = factor(Location), 
         Location = fct_recode(Location, 
                               "Urban Forest" = "Forest", 
                               "Urban Center" = "Campus"),
         Location = fct_relevel(Location, "Urban Forest", "Urban Center"),
         Land = fct_recode(Land, 
                           "Urban, High" = "UrbanizedHighIntensity",
                           "Urban, Medium" = "UrbanizedMediumIntensity",
                           "Urban, Low" = "UrbanizedLowIntensity",
                           "Deciduous Forest" = "DeciduousForest",
                           "Woody Wetlands" = "WoodyWetlands"),
         Land = fct_relevel(Land, 
                            "Urban, High", 
                            "Urban, Medium", 
                            "Urban, Low", 
                            "Deciduous Forest", 
                            "Woody Wetlands"),
                  patch_area_km = patch_area_mm * 1e-6) %>% 
  dplyr::rename("Impervious" = "Imperv", 
                "Dist_to_Road" = "road_dist_data", 
                "Traffic_Dist_Road" = "dist_traffic_road", 
                "Dist_to_Highway" = "highway_dist_m", 
                "Traffic_Dist_Highway" = "dist_traffic_highway") #data on individual webs

sites <- webs %>% 
  filter(Web == "W001")

web_dist <- webs %>% 
  mutate(Location = factor(Location)) %>% 
  filter(RetreatDist != 0,
         RetreatDist < 1000,
         Web == "W002" | Web == "W003") %>% 
  mutate(Neighbor = ifelse(Web == "W002", "1", "2"))

near <- webs %>% 
  mutate(Location = factor(Location)) %>% 
  filter(RetreatDist != 0,
         RetreatDist < 1000,
         Occ_Neigh == "1")

substrates <- read.table(file = "data/substrate.txt", header = TRUE)

site_info <- read.table(file = "data/site_info.txt", header = TRUE)

land_cover <- read.table(file = "data/land_cover_table.txt", header = TRUE) 
```

```{r spider, dpi = 300}
knitr::include_graphics("/Users/bjpessman/Documents/phd_research_code/Agelenopsis_aggregation/manuscript/figures/spider.png")
```

**Fig. 1**

\newpage

```{r land_location, fig.width = 6.85, dpi = 300}
knitr::include_graphics("/Users/bjpessman/Documents/phd_research_code/Agelenopsis_aggregation/manuscript/figures/land_locations.png")
```

**Fig. 2**

\newpage

```{r main, fig.width = 6.85, fig.height = 7, dpi = 300}
main <- readRDS("figures/main.Rds")
main
```

**Fig. 3**

\newpage

```{r pred_abund, fig.width = 6.85, fig.height = 7, dpi = 300}
predictors_abund <- readRDS("figures/predictors_abund.Rds")
predictors_abund
```

**Fig. 4**

\newpage

```{r pred_agg, fig.width = 6.85, fig.height = 7, dpi = 300}
predictors_agg <- readRDS("figures/predictors_agg.Rds")
predictors_agg
```

**Fig. 5**

\newpage

## Tables

**Table 1**

```{r landscape, fig.width = 3.77, dpi = 300, out.width="50%"}
knitr::include_graphics("/Users/bjpessman/Documents/phd_research_code/Agelenopsis_aggregation/manuscript/figures/landscape.png")
```

\newpage

**Table 2**

```{r pred_location, fig.width = 6.85, dpi = 300}
knitr::include_graphics("/Users/bjpessman/Documents/phd_research_code/Agelenopsis_aggregation/manuscript/figures/pred_location.png")
```

\newpage

**Table 3**

```{r pred_table, fig.width = 6.85, dpi = 300}
knitr::include_graphics("/Users/bjpessman/Documents/phd_research_code/Agelenopsis_aggregation/manuscript/figures/pred_table.png")
```

### 2022-11-26 manuscript/manuscript.Rmd
Finished making figures and tables

---
title: "Urbanization affects web abundance and aggregation of a funnel weaver, *Agelenopsis pennsylvanica*"
author: Brandi Pessman, Madison Hays, Earl Agpawa, Eileen Hebets
date: "`r Sys.Date()`"
output: 
  bookdown::word_document2:
    reference_docx: word_styles_reference_01.docx
    fig_caption: true
    number_sections: false
bibliography: [citations.bib]
csl: apa.csl
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
knitr::opts_knit$set(root.dir = "/Users/bjpessman/Documents/phd_research_code/Agelenopsis_aggregation/manuscript")
require(knitr)
```

```{r import data, eval=FALSE, include = FALSE}
webs <- read.table(file = "/Users/bjpessman/Documents/phd_research_code/Agelenopsis_aggregation/data/webs.txt", header = TRUE) 
webs <- webs %>% 
  mutate(ID = factor(ID),
         Location = factor(Location), 
         Location = fct_recode(Location, 
                               "Urban Forest" = "Forest", 
                               "Urban Center" = "Campus"),
         Location = fct_relevel(Location, "Urban Forest", "Urban Center"),
         Land = fct_recode(Land, 
                           "Urban, High" = "UrbanizedHighIntensity",
                           "Urban, Medium" = "UrbanizedMediumIntensity",
                           "Urban, Low" = "UrbanizedLowIntensity",
                           "Deciduous Forest" = "DeciduousForest",
                           "Woody Wetlands" = "WoodyWetlands"),
         Land = fct_relevel(Land, 
                            "Urban, High", 
                            "Urban, Medium", 
                            "Urban, Low", 
                            "Deciduous Forest", 
                            "Woody Wetlands"),
                  patch_area_km = patch_area_mm * 1e-6) %>% 
  dplyr::rename("Impervious" = "Imperv", 
                "Dist_to_Road" = "road_dist_data", 
                "Traffic_Dist_Road" = "dist_traffic_road", 
                "Dist_to_Highway" = "highway_dist_m", 
                "Traffic_Dist_Highway" = "dist_traffic_highway") #data on individual webs

sites <- webs %>% 
  filter(Web == "W001")

substrates <- read.table(file = "/Users/bjpessman/Documents/phd_research_code/Agelenopsis_aggregation/data/substrate.txt", header = TRUE) 
```

**Log line: Under increasing urbanization, generalist predators actively select web locations to effectively capitalize on more abundant prey as environmental conditions change.**

## Abstract

Animals distribute themselves within habitats based on a variety of environmental conditions, including those impacted by urbanization. In Lincoln, Nebraska, USA, funnel-weaving spiders (*Agelenopsis pennsylvanica*) are prevalent across urban habitats and actively choose web sites. We compared *A. pennsylvanica* abundance and distribution between two distinct urban habitats: an urban center and an urban forest. We searched along paths from randomly selected start sites in each habitat until we found the first occupied (focal) web. We measured web and spider abundance, distances between the focal and two nearest-neighbor webs, and web height in a ten-meter radius. We found that (i) search distances to focal webs were shorter, and both (ii) webs and (iii) spiders were more abundant in the urban center than in the urban forest, despite less diverse plants for web structures in the urban center. We also found (iv) shorter distances between webs and (v) lower web heights in the urban center. Our data suggest that *A. pennsylvanica* spatially distribute themselves differently across different urban habitats, and we discuss a variety of environmental variables that may predict this behavior.

## Introduction

Animal abundance and distribution are influenced by combinations of environmental factors, intra- and interspecific interactions, and dispersal capacity [@svamberkova_leps_2020; @diez_pulliam_2007]. Environmental factors -- including climatic conditions, land cover, habitat heterogeneity, and access to certain resources (like water and shelter) -- are suspected to relate to physiological constraints that limit the fundamental niche [@chase_leibold_2003]. Interactions within species (between conspecific competitors and mates) and across species (with predators, prey, and heterospecific competitors) further shape animal spatial patterns [@anderson_2017; @boulangeat_2012]. While dispersal capacity can determine a species’ range, barriers can limit dispersal and prevent animals from reaching suitable habitat  [@boulangeat_2012; @amundrud_2018]. Aggregations can form when suitable conditions and resources are not evenly distributed, leading to higher-quality patches [@churchill_2020]. For example, gaps in the tree canopy allow more sunlight to reach the understory -- thus, increasing plant height and soil moisture and decreasing leaf litter -- causing some invertebrate families to become more abundant in these patches [@perry_2018]. Clumping can also result from incomplete dispersal that occurs when barriers, often due to habitat structure, prevent adequate dispersal [@riechert_1974b]. The relative importance of different spatial predictors can vary by the type of taxon-specific spatial information being collected -- *i.e.* presence, abundance, aggregation, or vertical position [@boulangeat_2012].

Due to intense habitat disturbance and dense human presence, urbanization has drastically modified the land [@alberti_2020]; @mcdonnell_pickett_1990; @pickett_2001) which has altered environmental conditions, community dynamics, and dispersal capability as a result [@piano_2020]. As these factors determine animal spatial patterns, it is likely that urbanized landscapes have changed how animals spatially distribute themselves, in turn. Typically, city tree cover is reduced in areas where the potential natural vegetation is forested [@nowak_1996] and greater in areas with prairie, grassland, and desert origins [@mckinney_2006]. Urban environments are additionally characterized by decreased biodiversity [@mckinney_2002] and increased impervious cover [compacted soil from buildings and pavement; @nowak_greenfield_2020] and habitat patchiness [@cadenasso_2007]. These conditions can contribute to changes in climatic conditions, such as when impervious cover traps heat and increases the average temperatures in cities compared to surrounding areas –- *i.e.*, the Urban Heat Island Effect [@morabito_2021]. Disturbance from human presence can lead to air, water, and light pollution [@grimm_2008; @hopkins_2018], as well as air-borne, water-borne, and substrate-borne noise [@barber_2010; @slabbekoorn_2010; @wu_elias_2014]. There is growing evidence that urbanization changes species interactions, even reshaping whole food webs [@start_2020] and the landscape of parasite and disease transmission [@bradley_altizer_2007]. Further, habitat fragmentation and urban features often limit dispersal, which can cause higher degrees of aggregation for urban animals [@johnson_munshisouth_2017]. Urban ecosystems are extremely heterogeneous with unique and diverse habitats nested within [@rivkin_2019]. Habitats within urban ecosystems can vary considerably in feature, condition, and disturbance, resulting in variable access and distributions of resources that can differentially drive animal spatial patterns [@murray_2019; @trubl_2012].

Variation in the abundance and distribution of urban arthropods can have implications for ecosystem function due to the essential ecosystems services that arthropods provide, like pest control [@otoshi_2015] and pollination [@ivers_2022]. Arthropods are considered critical bioindicators of ecosystem health as their short generation time requires them to respond rapidly to human-induced change [@mcintyre_2000]. However, the impact of urbanization on arthropod ecology is still understudied [but see @kotze_2011; @fenoglio_2020], and the relationship between urban habitats and arthropod abundance and diversity remain controversial [@gippet_2017; @dale_frank_2018]. Such discrepancies are probably due to abundance and distributions being species- [@gippet_2017], habitat- [@bennett_lovell_2014], and scale-dependent [@philpott_2014]. While some animals benefit from urban conditions [@guenard_2015], many cannot survive the disturbance and change associated with cities [@wagner_2020]. Thus, it is important to determine how urban factors may be contributing to variation in arthropod abundance and spatial patterns for the conservation of arthropods and their essential services. Specifically, spiders play an important role in pest control and are predicted to collectively consume up to 800 million tons of arthropods each year [@nyffeler_birkhofer_2017]. Many web-building spiders are choosy in their web locations based on the distribution and abundance of other arthropod prey [@trubl_2012; @riechert_tracy_1975]. Territoriality is a form of intra-specific interactions that can also shape spatial distributions of web-builders [@riechert_1974b]. Further, previous studies have found environmental factors that vary across urban habitats may drive differences in spider spatial distribution, including noise [@bunkley_2017; @gomes_2020], pollution [@zmudzki_laskowski_2012], fragmentation [@stefani_delclaro_2015], microclimate conditions [@riechert_tracy_1975], vegetation structure [@peng_2020], and suitable web substrates [@chan_2009].

The mechanisms behind solitary spider aggregations are unclear despite reports of aggregations of spiders in urban habitats, such as web-builders *Lactrodectus hesperus* and *Brigittea civica*. This gap in knowledge is concerning as urban spider aggregations can have medical and aesthetic consequences, and implications for urban pest control services. Prey abundance seems to be an important driver because it has been shown to be directly and indirectly related to urban spider aggregations, the latter of which is shown through investigations as light sources at night as cues of prey aggregations. Random spacing in solitary spiders is typically maintained by territoriality and aggression over resources like prey and mates. Occassionally, conditions arise that allow solitary spiders to become more tolerant of neighbors, and understanding these contexts can help uncover the mechanisms of aggregative behavior. Aggregations have been shown to form as a result of dispersal limitations, predator release, lekking reproductive strategies, plant structure, and environmental stressors. The degree of aggregation in spiders can also change over time, often times more intense during juvenile stages when dispersal is limited, spreading over time as subadults and adults become more territorial []. Studies on mechanisms of aggregations in spiders are presented and discussed in Table 1.

Funnel weavers in the genus *Agelenopsis* actively select web locations based on experience of perceived quality of the site [@riechert_1976], and are thus likely impacted environmental conditions resulting from urbanization. Prey abundance, available web substrates, vegetation structure, and microclimate conditions have been shown to be indicators of a quality web site in a desert habitat for *A. aperta* [@riechert_1974; @riechert_1973]. In the same species, spatial patterns changed throughout life stages, although this may depend on environmental conditions and dispersal [@riechert_1974]. *Agelenopsis pennsylvanica* build webs that consist of a sheet that functions as a prey capture area and a retreat to escape from predators and unfavorable conditions (Fig. 1), like direct sunlight [@riechert_tracy_1975]. The horizontal sheet is not sticky, and the web is used solely for its vibratory properties to rapidly and accurately locate prey that fall upon or walk across the web [@singer_2000]. Occasionally, vertical silk strands are found that may function to capture flying prey or evade predators [@singer_2000]. The spider sits in the retreat until the prey is sensed and returns to the retreat immediately after capturing the prey. Juvenile males and females build semi-permanent webs, but males leave their web shortly after maturity in search of a receptive female [@singer_2000].

Understanding how urban spiders are affected by changes in environmental conditions and habitat structure brought on by processes of urbanization is vital as cities continue to densify and expand. Thus, we compared *A. pennsylvanica* spatial patterns between two urban habitats (an urban forest and an urban center) and explored what environmental factors are important determinants of web placement. In particular, we use *A. pennsylvanica* to address three questions: (*i*) How does web abundance, aggregation, and position vary between two urban habitats? (*ii*) How do environmental conditions vary between these two urban habitats? (*iii*) What environmental variables help predict spider spatial patterns in distinct urban habitats? Based on preliminary observations, we predicted that spiders would be more abundant and aggregated in the urban center than the urban forest. We further hypothesized that environmental conditions that vary between the two habitats would be correlated with the variation in the spatial patterns of *A. pennsylvanica*.

## Material and methods

### Urban Habitats

We conducted our study in September and October of 2020 in Lincoln, Nebraska, USA. Lincoln -- with a population of about 300,000 people [@census] -- has diverse urban habitats that vary in the degree of disturbance, management, and plant cover. We compared the abundance, aggregation, and position of funnel webs (*Agelenopsis pennsylvanica*) between two urban habitats: the University of Nebraska-Lincoln (UNL) City Campus (an urban center) and Wilderness Park (an urban forest) (Fig. 2, Fig. S1). These two habitats were selected due to their distinctive characteristics (described below), preliminary observations of potential differences in funnel weaver abundance and aggregation, and ease of access.

To first quantify differences in the environmental conditions between urban habitats, we gathered and analyzed Geographic Information Systems (GIS) data in QGIS (v. 3.16.3-Hannover, ESRI 102704). We obtained tree cover [@usfs_2016], impervious (building and pavement) cover [@usgs_2019_imperv], and land use class [@usgs_2019_land] from the National Land Cover Database (30-meter resolution). We used an image from path 28, row 32 of the Landsat-7 World Reference System-2 (Band 6) to collect spectral radiance -- a measure of thermal conditions on Earth's surface (30-meter resolution, taken on September 2, 2020). Finally, we assessed artificial light at night levels using the 2020 Visible Infrared Imaging Radiometer Suite (VIIRS) from https://www.lightpollutionmap.info/ (500-meter resolution). We polygonized the tiff files and calculated the average value for each factor by habitat: UNL City Campus, Wilderness Park, and Lincoln City Limits (see Fig. 2, Fig. S2-S5). We included measurements for Lincoln city limits to show how the two study habitats compare to the city of Lincoln overall. We calculated the averages using the following equation:

$$
average = \frac{\sum_{i = a}^{b}{i* x_i}}{100}
$$

Where *i*is the value indicated by the pixel (with range b-a) and *$x_i$* is the percent of the habitat covered by the *$i^(th)$* pixel category. These data are presented in Table 1 and summarized below.

We defined the study boundaries of UNL City Campus as Salt Creek Roadway, North Antelope Valley Parkway, North 10th Street, and Q Street (1.12 $km^2$, Fig. 2, Fig. S1). UNL City Campus is adjacent to, and just north of, downtown Lincoln (253.73 $km^2$). Impervious cover -- in the form of buildings and pavement -- dominates the land on UNL City Campus, considerably more than impervious cover across the city of Lincoln (Table 1, Fig. S2). Lawns are maintained by frequent mowing, and gardens and landscaping are regularly pruned. Tree cover on UNL City Campus and in Lincoln overall is low (< 6%, Table 1, Fig. S3). There was heavy foot traffic from UNL's 20,286 undergraduates enrolled in the 2020-2021 academic year, 37% of which lived in college-owned, -operated, or -affiliated housing [@iea_2021]. The entire area of UNL City Campus was categorized as urban with varying intensity (Table 1, Fig. 2). Over half of UNL City Campus was high intensity urban cover compared to only 13.16% for Lincoln overall. Further, UNL City Campus exhibits heighten spectral radiance (thermal conditions, Fig. S4) and artificial light at night radiance (Fig. S5), even above that of Lincoln as a whole (Table 1). Thus, we designated UNL City Campus as an *urban center* and refer to it as such hereafter.

Wilderness Park is a stretch of forested land (6.44 $km^2$, Fig. 2, Fig. S1) starting about 3.58 km southwest of UNL City Campus and downtown Lincoln, extending south and along Lincoln city limits. We found about two-fifths of Wilderness Park to be shrouded in trees (Table 1, Fig. S3), with less than 2% of its land imperviously covered (Table 1, Fig. S2). Over three quarters of Wilderness Park is categorized as forested land with only 5.44% labeled as urban (Table 1, Fig. 2). Wilderness Park has about 18 kilometers of dirt trails, dense deciduous tree growth, and variable undergrowth. The trails are open for recreational walking, running, biking, and horse riding. While we found no public records of the number of visitors to Wilderness Park, trail-goers were infrequent during data collection. Wilderness Park showed greatly reduced spectral radiance (Fig. S4) and artificial light at night radiance (Fig. S5) than the city of Lincoln (Table 1). Due to its proximity to Lincoln city limits, we designate Wilderness Park as an *urban forest* and refer to it as such hereafter.

### Study Sites and Field Measurements

Within the boundaries of the urban forest, we assigned numbers to intersections of three or more trails (Fig. S6). Similarly, we assigned numbers to each intersection of roads and sidewalks that meet from the four cardinal directions in the urban center (Fig. S6).  We used a random number generator to randomly select 10 intersections in the urban forest and 12 intersections in the urban center as start sites (Table S1). We marked the GPS coordinates of these locations using a GPS receiver (Magellan SporTrak Map, Model 980616-01, Parsippany, New Jersey, USA).

From each start site, we began walking along a path in a randomly selected direction (North, East, South, or West using a random number generator). We thoroughly searched the edges of the path for funnel webs as the GPS receiver tracked our movement (Fig. S7). We walked along pre-existing sidewalks, roads, and trails because paths were a common feature of both habitats along which we had previously found funnel weavers. We often find *A. pennsylvanica* in edge habitats in the study region, and this tendency to build webs at a habitat's edge is shared by other spider species [@cobbold_supp_2012]. Additionally, the thick undergrowth of the urban forest often restricted searches off the trails. To ensure equivalent search efforts, we took more time searching the edge of dense undergrowth in the urban forest.

When we reached a funnel web, we checked to see if the web was occupied by a spider by resting a toothpick secured to the bristled end of a vibrating toothbrush on the sheet of the web to simulate prey in the web. If a spider emerged, we noted this web as the *focal web*. If no spider emerged after 30 seconds, we continued searching until we found an occupied funnel web. We used the GPS receiver to mark the coordinates of the focal web. Although it is possible that other species of *Agelenopsis* are present in Lincoln, we have only found *A. pennsylvanica* during surveys in the area.

Search distance can often be used to estimate abundance [@buckland_2005], as spiders are likely less abundant in an area where we need to search further from the start site to the focal web. Thus, we use search distance as evidence for variation in abundance. To quantitatively determine the abundance of webs and spiders near each focal web, we measured a ten-meter radius around the focal web and counted the number of occupied and unoccupied webs determined in the same manner as the focal web. We also assessed nearest neighbor distances as a measure of aggregation behavior. Starting at the focal web and working outwards, we marked the locations of the two webs (occupied and unoccupied) nearest to the focal web within ten meters. We limited our measurements to the nearest two webs because we often found no more than three webs (including the focal web) per site in the urban forest. We measured the shortest distance from the retreat of the focal web to the retreat of the two nearest neighbor webs. To explore differences in web placement, we measured the web height from the ground to the web retreat. Differences in web height have been shown to vary by environmental factors associated with urbanization [@dahirel_2017]. To get an idea of plant species richness at each site, we recorded each unique plant species found in a ten-meter radius of the focal web (Fig. S8).

We collected data from September 23 to October 14, 2020. During these dates, all *A. pennsylvanica* have reached maturity [@guarisco_2014; unpublished data]. Of the 64 occupied webs, 61 were occupied by females indicating that males had likely abandoned their webs in search of females. The 67 unoccupied webs could be those once owned by males or those abandoned by females. While webs were found on many of the same plant types between sites in the urban forest and urban center in varying proportions, 15% of webs in urban center sites were built on non-plant substrates (Fig. S9).

### Environmental Predictors

To assess potential mechanisms behind variation in abundance, aggregation, and position, we looked for correlations between spider spatial patterns and environmental conditions -- collected in the field (plant species richness) or using GIS for each site. In QGIS, we created 100 meter buffers around focal web sites and processed the GIS variables mentioned above (tree cover, impervious cover, spectral radiance, and artificial light at night radiance) in the same manner as before. To these we added patch area, potential disturbance from nearby roads and highways, and road length in the 100 meter buffer. We used a 100 meter buffer to accommodate the resolution of the GIS data. We refrained from including a larger buffer region as the dispersal range of this system is unknown and may be dependent on barriers present in the habitat.

We measured patch area using satellite imagery to define the area of continuous vegetation around the focal web. Roads, sidewalks, and trails were defined as fragment boundaries. To determine the potential disturbance from road and highway traffic, we first measured the shortest distance from each focal web to the nearest road [GIS vector from: @centerlines] and highway [GIS vector from: @highways] using the NNJoin Plugin [@nnjoin] for QGIS. We used the 2021 Average Daily Traffic Volume report [@adtv_2021] to identify the average daily number of vehicles to travel on each nearest road and highway. We divided the average daily traffic by the shortest distance from the focal web to the nearest road and highway [as in @dooley_2020] for metrics of road disturbance and highway disturbance, respectively. Lastly, we measured the total length of road [@centerlines] within a 100 meter buffer of the focal web.

### Statistical Analysis

#### Web abundance, aggregation, and position between habitats

For the first set of models, we focused on whether web abundance, aggregation, and position differ between the two habitats (the urban center and urban forest). We used Poisson generalized linear models [*stats* package in R, @stats] for the response variables: search distance, number of webs, and number of spiders. We used Poisson generalized linear mixed effect models [*lme4* package in R, @lme4] with site as a random effect for the response variables: nearest neighbor distance and web height. For the model with nearest neighbor distance, we also included neighbor number (nearest and second nearest web) and its interaction with habitat. We used Poisson distributions because the response variables were not normally distributed according to Shapiro-Wilk Normality Tests, and all data were strictly positive with no upper limit.

#### Environmental variables between habitats

Since we found significant variation in distribution measures between habitats, we wanted to explore potential environmental mechanisms of such variation within habitats. We first tested whether the nine environmental predictors varied by habitat (Table 2). Each predictor was tested by habitat using Poisson generalized linear models as the predictors were positive and not normally distributed. Each environmental predictor significantly varied by habitat (Table 2), so we subset the data by habitat. Among the environmental predictors, we removed variables that were highly correlated (cutoff of 0.6) using the *caret* package in R [@caret]. Artificial light at night radiance was dropped from all analyses for being highly correlated. Only plant species richness, road disturbance, and highway disturbance remained for models using all data. We kept tree cover, plant species richness, patch area, and road and highway disturbance for the urban forest subset. The urban center subset includes plant species richness, patch area, spectral radiance, road and highway disturbance, and road length.

#### Model selection for environmental predictors of spatial patterns

We used the habitat subsets and the selected environmental predictor variables to assess correlations between predictor variables and spatial pattern measures. In the global models, we included the predictors that remained after removal for collinearity (no interactions) with the response variables: web and spider abundance, nearest neighbor distance, and web height for the complete data and habitat subsets. We assessed nearest neighbor distance and excluded second nearest neighbor distance because both were significantly different between habitats. We excluded search distance as a response variable because the predictors were collected from the site of the focal web and may vary along the search path. Several predictors (plant species richness, patch area, and road and highway disturbance) were highly skewed toward zero, so we used a natural log-transformation prior to model selection. We used Poisson generalized linear models for number of webs and spiders and nearest neighbor distance and Poisson generalized linear mixed-effect models for web height with site as a random effect. From these global models, we performed Akaike Information Criterion (AIC) model selection with the *MuMIn* package in R [@MuMIn], which ranks models produced from every combination of the predictors in the global model. We report here the results of each top model, as well as a model average of models within 2 delta AICc points of the top model. Reported estimates and standard error are back-transformed for variables that were natural log-transformed using the *exp()* function. We checked that the Variance of Inflation (VIF) stayed below a score of two for predictors in each top model using the *car* package in R [@car].

We also explore how land use may affect web abundance, aggregation, and position using the National Land Cover Database and QGIS to record the category of the land use type for the pixel that each site was located. We tested Poisson generalized linear models for each response variable with land cover as the only predictor. We include these results in supplemental material (Fig. S11, Table S3-7) as the sample sizes were small (deciduous forest = 7, woody wetlands = 3, urban high intensity = 4, urban medium intensity = 6, urban low intensity = 2).

We completed statistics and visualization using R 4.0.0 [@r] and RStudio 2022.2.0.443 [@rstudio]. All graphs show raw data and (top) model estimates (*broom* package in R)[@broom]. We used the *tidyverse* [@tidyverse], *ggpubr* [@ggpubr], and *broomExtra* [@broomExtra] packages in R to produce and customize the graphs. For Poisson generalized linear mixed effect models, we determined the 95% confidence intervals of the model estimates by completing 1000 bootstrap iterations using the function *bootMer()* in R package *lme4*. We used the package *sjPlot* [@sjPlot] in R to produce the land use tables in the supplemental material (Table S3-7). All R code and data are posted here: https://github.com/brandipessman.

## Results

### Web abundance, aggregation, and position between habitats

All abundance, aggregation, and position metrics -- search distance, the number of webs and spiders within 10 meters of the focal web, the distance from the focal web to the two nearest neighbor webs, and web height -- varied by habitat (Fig. 3).

We searched significantly less distance from the start site to the focal web in the urban center than the urban forest ($z_20$ = -10.10, *P* < 0.001, Fig. 3a, Fig. S7). Within a 10-meter radius of the focal web, we counted significantly more webs ($z_20$ = 8.56, *P* < 0.001, Fig. 3b) and spiders ($z_20$ = 4.86, *P* < 0.001, Fig. 3c) in the urban center than the urban forest. We also found that the distances between the focal web and the two nearest neighbors were significantly shorter in the urban center than the urban forest ($z_34$ = -5.60, *P* < 0.001, Fig. 3d). By definition, the second nearest web is further from the focal web than the nearest neighbor ($z_34$ = 14.654, *P* < 0.001). There was a significant interaction between neighbor number and habitat -- the increase in distance from the nearest to second nearest web was smaller in the urban center than the urban forest ($z_34$ = 9.86, *P* < 0.001, Fig. 3d). Lastly, webs were built lower in the urban center than the urban forest ($z_128$ = -2.38, *P* = 0.017, Fig. 3e). This difference was not due to differences in substrate height because we found no difference in substrate height between habitats ($z_128$ = -1.10, *P* = 0.273).

### Environmental differences between habitats

All environmental predictors assessed within a 100-meter radius of the focal web varied by habitat (Table 2). Site tree cover was lower in the urban center than the urban forest with five urban center sites with zero tree cover ($z_21$ = -14.50, *P* < 0.001). The urban center sites had higher impervious cover while all but four sites were zero in the urban forest ($z_21$ = 14.51, *P* < 0.001). The urban center sites also had higher spectral radiance ($z_21$ = 3.08, *P* = 0.002) and artificial light at night radiance ($z_21$ = 22.46, *P* < 0.001). Overall plant species richness was lower in the urban center than the urban forest ($z_21$ = -7.67, *P* < 0.001). Similarly, spiders used a lower diversity of plants as substrates in the urban center (mean ± se = 1.42 ± 0.15 species) than the urban forest (mean ± se = 2.7 ± 0.26 species, $z_21$ = -2.08, *P* = 0.037). Site patch area was smaller in the urban center ($z_21$ = -374.2, *P* < 0.001). Road disturbance ($z_21$ = 39.19, *P* < 0.001), highway disturbance ($z_21$ = 9.39, *P* < 0.001), and road density ($z_21$ = -374.2, *P* < 0.001) were higher for urban center sites than sites in the urban forest. The urban forest sites had an average total trail length of 113 ± 11.3 meters within 100 meters of the focal web.

### Environmental predictors of abundance, aggregation, and position

To explore potential mechanisms of variation in spatial patterns, we looked for correlations between response variables (number of webs, number of spiders, nearest neighbor distance, and web height) and environmental predictors overall and within each habitat (Table 3, Table S2, Fig. 4-5).

The top models for the number of webs and the number of spiders yielded similar results (Table 3, Fig. 4). For both measures of abundance, the urban forest subset retained no predictors (Table 3) while the urban center showed a decrease in abundance with increasing plant species richness, patch area, highway disturbance, and road length (Table 3, Fig. 4). The model average for the number of webs subset by urban center suggested similar results (Table S2). Plant species richness and highway disturbance both had a negative relationship with abundance measures for the overall data set (Table 3, Fig. S10). Interestingly, the top model of web abundance retained road disturbance and suggested a positive relationship overall (Table 3, Fig. S10).

Overall, spiders are closer together when plant species richness is low and when road disturbance is high (Table 3, Fig. S10). On the other hand, less tree cover, lower road and highway disturbance, and greater plant species richness are associated with nearness in the urban forest (Table 3, Fig. 5), however, this model was a poor fit ($R^2$ = 0.037). Urban center spiders are more aggregated where plant species richness, spectral radiance, and road length are high (Table 3, Fig. 5). The model average for the nearest neighbor distance in the urban center corroborates these findings and adds that webs are clumped when patch area is larger (Table S2).

Further, webs are built higher overall when the number of plant species is higher (Table 3, Fig. S10). A trend also suggests that lower webs are associated with higher road disturbance, although this result is not significant (Table 3, Fig. S10). In the urban forest, web height is positively related to tree cover (Table 3). While plant species richness was included in the top model, it did not vary by web height in the urban center (Table 3). We see similar results from the model averages for web height (Table S2). Despite the addition of predictors under the model averages, none of the added predictors varied by web height in their respective data sets (Table S2).

For statistical analysis and figures of response variables by land cover class, see supplemental material (Table S3-7, Fig. S11). There was no difference in search distance between deciduous forest, urban medium intensity and urban low intensity. However, we searched significantly further in woody wetlands and significantly shorter in urban high intensity. The number of webs and spiders only varied by habitat - urban low, medium, and high intensity had more webs and spiders than deciduous forest or woody wetlands. Nearest neighbor distance was shorter for woody wetlands than deciduous forest. For the urban intensities, web distance was shortest at low intensities and furthest at medium intensities. Lastly, deciduous forest and urban low intensity did not differ in web height. Woody wetlands had significantly higher webs and urban medium and high intensities had significantly lower webs.

## Discussion

### Spiders are more abundant in the urban center

Both webs and spiders of *A. pennsylvanica* were more abundant in the urban center than the urban forest. Shorter search distances to the focal web corroborates this finding, as previous studies have used search distance as an estimate of abundance [@buckland_2005, @kral_2018]. Tolerance of urban ecosystems is dependent on the ecology and behavior of the organism, such as being a generalist consumer [@sol_2013; @bang_2011], and the scale of the measurements being collected [@lowe_2018; @philpott_2014], resulting in conflicting findings in the literature. While arthropods are generally found to decline [@wagner_2020; @piano_2020], generalists and thermally flexible species are more likely to be urban exploiters than specialists or thermally inflexible species [@callaghan_2021]. For example, *Nephila plumipes*, a generalist predator, was found to abundantly occupy urban habitats where prey abundance supported greater numbers of spiders [@lowe_2016]. Prey abundance has been repeatedly found to be a strong predictor of spider abundance [@trubl_2012, @parkinson_2020, @harwood_2001]. While we did not measure intra- and interspecific interactions between the two urban habitats studied here -- although future research on this system should test these biotic factors -- , we did find several environmental factors that may predict spider abundance directly or indirectly through environmental effects on prey, predator, or competitor abundance or dispersal limitations.

**would like to add that Agelenopsis are generalists and widespread but CANNOT find citations**
**need to talk more about predator and competitor abundance? - I think not, mention in next paragraph.**

The environmental conditions assessed here only correlated with web and spider abundance in the urban center, with no strong environmental effects on abundance in the urban forest. Variation in abundance per urban forest site was low, only ranging from two to four webs and one to three spiders. On the other hand, abundance for webs ranged from one to 73 webs and one to 22 spiders per urban center site. Additionally, urban forest abundance may be better predicted by factors not assessed here, such as prey and predator abundance or dispersal limitation [CITE]. In the urban center, web and spider abundance was higher when plant species richness, patch area, highway disturbance, and road length were lower. *Agelenopsis pennsylvanica* rely heavily on vibrations to capture prey [CITE], court potential mates [CITE], and potentially evade predators [CITE]. Thus, vibratory noise may play a key role in web site selection, choosing sites that mitigate these effects [CITE]. We show that webs and spiders are more abundant in urban center sites that had lower highway disturbance and total length of road in a 100-meter radius. Although research on the effects of noise on arthorpod behavior has focused on acoustic rather than vibratory noise, studies have found strong negative effects of acoustic and vibratory noise on arthropod behavior [CITE]. A recent study shows that the orb-weaving spider, *Larinioides sclopetarius* is able to detect airborne sound that induces vibrations in the web [zhou et al. 2022].

Since different plants transmit vibrations differently [CITE], selective spiders in urban habitats may choose plants web substrates that reduce vibratory noise. Our results show that spiders are more abundant when plant species richness is lower. The urban center sites were covered in grass lawns and managed landscaping that usually had few plant species present. Sites with lower plant diversity may have few plant species that are highly preferred, leading to higher spider abundance. Greater plant diversity has been found to have both positive and negative affects on spider abundance, and some suggest that plant community composition tends to play a vital role [CITE]. To better understand the role that plant species play in abundance would require comparing plant communities between patches used by spiders versus those devoid of spiders. Additionally, smaller patches were associated with higher spider abundance. While arthropods overall tend to decrease in abundance as smaller patch sizes, habitat generalists and edge specialists can be found at greater abundance in smaller patches [CITE].

### Spiders are more aggregated in the urban center

Both the first and second nearest neighbor webs to the focal web were closer in the urban center than the urban forest. Multiple reports have found spider aggregations in urban habitats [], especially when related to the abundance of prey. Territoriality over mates and prey resources often drives random spacing of solitary species [], but aggregations can form when abundant resources allow for increased tolerance of neighbors []. Light at night in cities attracts insects creating pockets of increased prey abundance for spiders. As such, spiders have been found to aggregate under light sources. Although we did not measure microhabitat levels of light at night or prey abundance, *A. pennsylvanica* were more aggregated in the urban center where light at night radiance was higher than the urban forest. Future research should address both direct and indirect indicators of prey abundance in aggregations of spiders in urban habitats.

To determine whether nearness of neighbors in the urban center was the result of aggregation or just increased density from higher abundance, we completed calculations described by Clark and Evans [@clark_evans_1954]. This calculation compares the measured nearest neighbor distance to the expected distance if animals were evenly spaced within an area. A ratio value significantly below 1 suggests clumping, while values that do not significantly differ from 1 indicate random spacing. For each site, we estimated the total search area by adding the length of path searched multipled by four meters (for searching two meters on either side of the central path line) and the area of the 10 meter radius circular site. We subtracted the overlap in the search path and site by subtracting four * 10 meters. We find that webs are clumped in the urban center (R = 0.47, P < 0.01) and uniform in the urban forest (R = 1.24, P > 0.05). We conclude that aggregations formed for reasons other than increased spider density.

We found significant relationships between environmental predictors and nearest neighbor distance in both urban habitats. Urban center and forest spiders responded differently in aggregative behavior in response to vibratory noise measures -- urban forest spiders aggregated at lower road and highway disturbance and urban center spiders aggregated more there was more road within 100 meters of the focal web, but did not vary by road or highway disturbance. As a result, noise might affect urban forest spiders more than spiders reared in or that are decendents from the urban center where noise is greater. Spiders in the urban forest may exhibit increased nearest to neighbors if higher quality web locations are those that are further from road disturbance. Many spiders are thought to be plastic in the structure and tuning of their webs, and urban exploiters are often fast to adjust to changing conditions, so spiders in the urban center might be able to better tune their webs to decrease vibrations, although this hypothesis requires further testing. It will also be important to differentiate whether these differences in behavior between environments is based on developmental exposure, behavioral plasticity, or genetic differentiation.

Higher plant species richness led to greater aggregation for spiders in both the urban center and the urban forest. We speculate that greater aggregation on more diverse plant communities may suggest that *A. pennsylvanica* prefers a certain plant or type of plant, especially in urban centers where similar plants are often clumped in space for landscaping. In the urban forest, we also found nearer neighbors under less tree cover. A study that measured invertebrate abundance after manipulating tree cover found that newly formed tree gaps have greater vegetation height and coverage and increased soil moisture and temperature, all of which led to an overall increase in invertebrate abundance -- a result that had been corroborated by other studies. Since spider aggregations tend to occur where prey abundance is higher, we might predict that lower tree cover might indirectly increase spider aggregation through an increase in prey abundance. Lastly, spiders in the urban center were more aggregated at sites with higher spectral radiance (a measure of surface temperature). Urban centers tend to be warmer on average compared to surrounding areas due to heat trapping via pavement in a phenomenon called the Urban Heat Island Effect. Aggregation formation in warmer sites could be the result of limited shelter from excessive heat or from a preference for warmer areas.

### Web heights were lower in the urban center

We found that the height of the webs built by spiders in the urban center were built lower than webs in the urban forest, and this result was independent of the height of the substrate. Webs may vary in height based on the type of prey being ensnared. *Agelenopsis* spiders capture both flying and crawling insects []. Arthropod community structure is highly variable between urban habitats, and urban centers and urban forests may support different types of prey items for *A. pennsylvanica*. Lower webs in the urban center may be ideal for more crawling prey while higher webs in the urban forest may better trap flying insects. Alternatively, webs in different habitats may experience different levels of disturbance. In the urban center where lawns are mown frequently and ornamental plants are regularly pruned, spiders could maintain lower webs to conserve energy from constantly climbing up a substrate. Urban forests likely have abundant ground dwelling vertebrates whose movement along the forest floor could frequently damage lower webs. Greater tree coverage in the urban forest predict higher webs may further suggest that small mammal movement could destroy low wbes as areas with greater tree cover have been shown to have higher abundance of small mammals []. Future research should assess prey type available and small animal abundance and movement between these two habitats. We speculate that vibratory noise may promote lower web heights based on a trend that showed lower web heights overall at sites with higher road disturbance. Plant vibrations tend to be dampened nearer to the ground [] which could encourage spiders to build lower where noise is reduced.

## Conclusions

Our study shows that a solitary, generalist predator is more abundant and aggregated with lower web height in an urban center compared to an urban forest -- habitats that vary signficantly in environmental condition. While we did not measure community-level interactions among organisms, correlations between spatial pattern and environmental condition indirectly indicate that inter- and intraspecific interactions, especially prey abundance, are essential for predicting and monitoring spider aggregative behavior. Spider aggregations in urban centers can have medical consequences, such as dense *Lactrodectus hesperus* aggregations [], and aesthetic conerns, as is the case with aggregations of ** under archways of historic buildings []. On the other hand, spider aggregations could control pest outbreaks that threaten human health and food supply. We emphasize that elucidating the complex relationship between the arthropod abundance and the impacts of urbanization is essential for our understanding of how urbanization affects ecosystem services and food web interactions. Our variables that estimate the potential for vibratory noise negatively affected spider abundance while promoting lower web heights, potentially to reduce interference from vibratory noise. Noise variables had opposite affects on aggregative behavior of spiders in the different habitats that may indicate differences in tolerance to noise, but more research is necessary to test this hypothesis. Thus, urban habitats can vary in environmental conditions which can determine how animals distribute themselves in space and affect predator-prey interactions.

\newpage
## References {-}
<div id="refs"></div>
\newpage
## Figures
**Fig. 1** Study System - *Agelenopsis pennsylvanica* (a). The web consists of a retreat where the spider waits for prey to land, fall, or walk on the web sheet (b)

**Fig. 2** Land cover raster with borders for Lincoln, Nebraska, USA city limits (dashed border), University of Nebraska-Lincoln (UNL) City Campus (solid border, a), and Wilderness Park (solid border, b) using the 2019 National Land Cover Data on Land Cover and QGIS (v. 3.16.3-Hannover, ESRI 102704). For visualization and listing of study sites, see Figure S1 and Table S1, respectively

**Fig. 3** Comparison of search distance (a), the number of webs (b) and spiders (c) in a 10-meter radius of the focal web, the distance from the focal web to the first (d) and second (e) nearest neighbors, and web height (f) by habitat - urban forest vs urban center. Grey jittered points represent the raw data while black points and error bars represent the mean and 95% confidence intervals, respectively, from model predictions. Models were either Poisson Generalized Linear Models (a-c) or Poisson Generalized Linear Mixed Effect Models with site as a random factor (d-f). Asterisks (A-B) indicate significance level (*** *P* < 0.001; ** *P* < 0.01; * *P* < 0.05). We searched shorter distances from the start site to the focal web (a), found more webs (b) and spiders (c) in a 10-meter radius of the focal web, measured shorter distances between the focal web and the two nearest neighbors (d-e), and recorded shorter web heights (f) in the urban center than the urban forest

**Fig. 4** Significant correlations between measures of abundance (number of webs and spiders) and the environmental predictors for the urban center subset. Spectral radiance and road disturbance were dropped from both models of abundance for the urban center subset after AIC model selection. All environmental predictors of abundance were dropped from the urban forest subset. The regression lines and shaded regions represent the predictions and 95% confidence intervals (respectively) from the top Poisson Generalized Linear Model after AIC selection. The points represent the raw data. Asterisks indicate significance level (*** *P* < 0.001; ** *P* < 0.01; * *P* < 0.05)

**Fig. 5** Significant correlations between the aggregation measure (nearest neighbor distance) and the environmental predictors for the urban forest subset (plant species richness, tree cover, and road and highway disturbance) and the urban center subset (plant species richness, spectral radiance, and total road length). All other environmental predictors were dropped from models of nearest neighbor distance after AIC model selection. The regression lines and shaded regions represent the predictions and 95% confidence intervals (respectively) from the top Poisson Generalized Linear Model after AIC selection. The points represent the raw data. Asterisks indicate significance level (*** *P* < 0.001; ** *P* < 0.01; * *P* < 0.05)

## Tables
**Table. 1** Landscape variables for Lincoln (Nebraska, USA) City Limits, University of Nebraska-Lincoln (UNL) City Campus, and Wilderness Park collected from the National Land Cover Database (2016 Tree Cover, 2019 Impervious Cover, 2019 Land Cover), the Landsat-7 World Reference System-2 (Band 6, path 28, row 32, taken September 2, 2020), and the 2020 Visible Infrared Imaging Radiometer Suite (VIIRS) using QGIS (v. 3.16.3-Hannover, ESRI 102704)

**Table 2** Mean and standard error of environmental predictors collected in 100 meter buffers of each focal web by habitat

**Table.3** Results of the top models after AIC model selection from Poisson Generalized Linear Models with the environmental predictors for data overall and subset by habitat (urban forest and urban center). Asterisks indicate significance level (*** *P* < 0.001; ** *P* < 0.01; * *P* < 0.05)

### 2022-11-26 manuscript/supplemental.Rmd
Finished making figures and tables

---
output: 
  bookdown::word_document2:
    reference_docx: word_styles_reference_01.docx
    fig_caption: true
    number_sections: false
bibliography: [citations.bib]
csl: apa.csl
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
knitr::opts_knit$set(root.dir = "/Users/bjpessman/Documents/phd_research_code/Agelenopsis_aggregation/manuscript")
require(knitr)
require(kfigr) # devtools::install_github("github mkoohafkan/kfigr")
```

```{r libraries, include = FALSE}
library(tidyverse)
library(flextable)
```

## Supplemental Figures

```{r map, dpi = 300}
knitr::include_graphics("/Users/bjpessman/Documents/phd_research_code/Agelenopsis_aggregation/manuscript/figures/locations_sites.png")
```

**Fig. S1** Locations of data collection in Lincoln, Nebraska, USA (a). The University of Nebraska-Lincoln (UNL) City Campus (b) is located in downtown Lincoln. Wilderness Park (c) is an urban forest located southwest of downtown Lincoln and at the periphery of the city limits. Site markers indicate the site of the focal web. See table S1 for coordinates of start sites and focal web sites

\newpage

```{r map2, dpi = 300}
knitr::include_graphics("/Users/bjpessman/Documents/phd_research_code/Agelenopsis_aggregation/manuscript/figures/site_examples.png")
```

**Fig. S2** Wilderness Park and University of Nebraska-Lincoln (UNL) City Campus sites F01 (a) and C23 (b), respectively, where the circled flags indicate individiual webs of *Agelenopsis pennsylvanica*

\newpage

```{r imperv_location, fig.width = 6.85, dpi = 300}
knitr::include_graphics("/Users/bjpessman/Documents/phd_research_code/Agelenopsis_aggregation/manuscript/figures/imperv_locations.png")
```

**Fig. S2** Impervious cover raster with borders for Lincoln, Nebraska, USA city limits (dashed border), University of Nebraska-Lincoln (UNL) City Campus (solid border, a), and Wilderness Park (solid border, b) using the 2019 National Land Cover Data on Impervious Cover and QGIS (v. 3.16.3-Hannover, ESRI 102704)

\newpage

```{r tree_location, fig.width = 6.85, dpi = 300}
knitr::include_graphics("/Users/bjpessman/Documents/phd_research_code/Agelenopsis_aggregation/manuscript/figures/tree_locations.png")
```

**Fig. S3** Tree cover raster with borders for Lincoln, Nebraska, USA city limits (dashed border), University of Nebraska-Lincoln (UNL) City Campus (solid border, a), and Wilderness Park (solid border, b) using the 2016 National Land Cover Data on Tree Cover and QGIS (v. 3.16.3-Hannover, ESRI 102704)

\newpage

```{r spec_location, fig.width = 6.85, dpi = 300}
knitr::include_graphics("/Users/bjpessman/Documents/phd_research_code/Agelenopsis_aggregation/manuscript/figures/surf_locations.png")
```

**Fig. S4** Spectral radiance raster with borders for Lincoln, Nebraska, USA city limits (dashed border), University of Nebraska-Lincoln (UNL) City Campus (solid border, a), and Wilderness Park (solid border, b) using the satellite image of path 28, row 32 of the Landsat-7 World Reference System-2 (Band 6, September 2, 2020) and QGIS (v. 3.16.3-Hannover, ESRI 102704)

\newpage

```{r light_location, fig.width = 6.85, dpi = 300}
knitr::include_graphics("/Users/bjpessman/Documents/phd_research_code/Agelenopsis_aggregation/manuscript/figures/light_pollution_locations.png")
```

**Fig. S5** Artificial light at night radiance raster with borders for Lincoln, Nebraska, USA city limits (dashed border), University of Nebraska-Lincoln (UNL) City Campus (solid border, a), and Wilderness Park (solid border, b) using the 2020 Visible Infrared Imaging Radiometer Suite (VIIRS) and QGIS (v. 3.16.3-Hannover, ESRI 102704)

\newpage

```{r intersections, dpi = 300}
knitr::include_graphics("/Users/bjpessman/Documents/phd_research_code/Agelenopsis_aggregation/manuscript/figures/intersections.png")
```

**Fig. S6** Intersections randomly chosen from as starting sites. We selected Wilderness Park intersections (left) from trail intersections where 3 or more paths meet. The University of Nebraska-Lincoln (UNL) City Campus intersections (right) were selected from sidewalk and road intersections that met from the four cardinal directions. Sites that we used as starting sites are indicated in red

\newpage

```{r paths, dpi = 300}
knitr::include_graphics("/Users/bjpessman/Documents/phd_research_code/Agelenopsis_aggregation/manuscript/figures/paths.jpg")
```

**Fig. S7** Paths walked from the starting site until the first occupied web (the focal web). Site ID is labeled at the focal web site. Wilderness Park sites (left) are outlined in green, and University of Nebraska-Lincoln (UNL) City Campus sites (right) are outlined in orange

\newpage

```{r plants_image, fig.width = 6.85, dpi = 300}
knitr::include_graphics("/Users/bjpessman/Documents/phd_research_code/Agelenopsis_aggregation/manuscript/figures/plants.png")
```

**Fig. S8** Plant species found within a ten-meter radius of focal web at each site. Plant species at each site are underneath the colored and labeled site indicator (orange for University of Nebraska-Lincoln (UNL) City Campus and green for Wilderness Park). Plant species used as web substrates are highlighted in yellow. These data do not suggest equivalent prevalence of each species, but rather list available substrates for spiders

\newpage

```{r substrates, dpi = 300}
knitr::include_graphics("/Users/bjpessman/Documents/phd_research_code/Agelenopsis_aggregation/manuscript/figures/substrate_plot.png")
```

**Fig. S9** Representation of web substrates by class. Green shades indicate plant material classes, and orange indicates non-plant materials

\newpage

```{r pred_overall, fig.width = 6.85, fig.height = 7, dpi = 300}
predictors_overall <- readRDS("figures/predictors_overall.Rds")
predictors_overall
```

**Fig.S10** Significant correlations between response variables (number of webs, number of spiders, nearest neighbor distance, and web height) and the environmental predictors (plant species richness and road disturbance and highway disturbance) for the whole data set. The regression lines and shaded regions represent the predictions and 95% confidence intervals (respectively) from the top Poisson Generalized Linear Model after AIC selection. Predictor variables not included in the top model are shaded grey. The points represent the raw data. Asterisks indicate significance level (*** *P* < 0.001; ** *P* < 0.01; * *P* < 0.05)

\newpage

```{r land_plots, fig.width = 6.85, fig.height = 6.5, dpi = 300}
land_plots <- readRDS("figures/land_plots.Rds")
land_plots
```

**Fig. S11** Comparison of search distance (a), the number of webs (b) and spiders (c) in a 10-meter radius of the focal web, the distance from the focal web to the first (d) and second (e) nearest neighbors, and web height (f) by land cover class - deciduous forest, woody wetlands, urban high intensity, urban medium intensity, and urban low intensity. Land cover class was determined using the pixel category from the 2019 National Land Cover Data that the focal web site resides in. Grey jittered points represent the raw data while colored points (green = urban forest, orange = urban center) and error bars represent the mean and 95% confidence intervals, respectively, from Poisson Generalized Linear Model predictions. Unique letters indicate significance. See supplemental tables (S2-6) for statistical analysis

\newpage

## Supplemental Tables

**Table S1** Geographical information for the University of Nebraska-Lincoln (UNL) City Campus and Wilderness Park Sites

```{r site_info, fig.width = 5, dpi = 300}
knitr::include_graphics("/Users/bjpessman/Documents/phd_research_code/Agelenopsis_aggregation/manuscript/figures/site_info.png")
```

\newpage

**Table S2** Results of model averages (all models within 2 detla AICc points) from Poisson Generalized Linear Models with the environmental predictors for data overall and subset by habitat (urban forest and urban center), where applicable. Asterisks indicate significance level (*** *P* < 0.001; ** *P* < 0.01; * *P* < 0.05)

```{r mod_avg, fig.width = 5, dpi = 300}
knitr::include_graphics("/Users/bjpessman/Documents/phd_research_code/Agelenopsis_aggregation/manuscript/figures/pred_table_avg.png")
```

\newpage

**Table S3** Statistical results of Likelihood Ratio Tests following Poisson Generalized Linear Models for each response variable by land cover class. Significance indicated by asterisks (*** *P* < 0.001; ** *P* < 0.01; * *P* < 0.05).

```{r land_stats, fig.width = 5, dpi = 300}
knitr::include_graphics("/Users/bjpessman/Documents/phd_research_code/Agelenopsis_aggregation/manuscript/figures/land_stats.png")
```

### 2022-11-28 data_analysis.Rmd
More work on the manuscript

@@
 
-Tree cover is **significantly higher in the urban forest** than the urban center (z = -14.50, df = 1, 20, p < 0.001).
+Tree cover is **significantly higher in the urban forest** than the urban center (z = -14.50, df = 1, 21, p < 0.001).
 The means and SE's are 47.15 ± 2.17 % for the urban forest and 1.58 ± 0.36 % for the urban center.
@@
 
-Impervious cover is **significantly higher in the urban center** than the urban forest (z = 14.51, df = 1, 20, p < 0.001).
+Impervious cover is **significantly higher in the urban center** than the urban forest (z = 14.51, df = 1, 21, p < 0.001).
 The means and SE's are 1.27 ± 0.36 % for the urban forest and 76.52 ± 2.53 % for the urban center.
@@
 ```{r stats_graphs_tdr, echo = FALSE}
-tdr <- glm(log_tdr ~ Location, family = "poisson", data = sites)
+tdr <- glm(Traffic_Dist_Road ~ Location, family = "poisson", data = sites)
 summary(tdr)
@@
   group_by(Location) %>% 
-  summarize(mean = mean(log_tdr),
-            se = plotrix::std.error(log_tdr))
+  summarize(mean = mean(Traffic_Dist_Road),
+            se = plotrix::std.error(Traffic_Dist_Road))
 
@@
 
-ggplot(sites, aes(x = Location, y = exp(log_tdr))) + 
+ggplot(sites, aes(x = Location, y = Traffic_Dist_Road)) + 
   geom_jitter(color = "grey", width = 0.1, size = 1) +
-  geom_point(aes(x = Location, y = exp(rate), color = Location), size = 2, data = predictions) + 
+  geom_point(aes(x = Location, y = (rate), color = Location), size = 2, data = predictions) + 
   geom_errorbar(aes(x = Location, 
-                  ymin = exp(rate - SE), 
-                  ymax = exp(rate + SE),
+                  ymin = (rate - SE), 
+                  ymax = (rate + SE),
                   color = Location), data = predictions, inherit.aes = FALSE, width = 0.15, linewidth = 1.5) +
@@
   theme(legend.position = "none") +
-  annotate(geom="text", x=1.5, y=1400, label="N. S.", color="black", size = 10)
+  annotate(geom="text", x=1.5, y=1400, label="***", color="black", size = 10)
 ```
@@
 
-There is **no difference** in road disturbance between the urban forest and urban center (z = 1.403, df = 1, 20, p = 0.161).
-The means and SE's are `r exp(3.97)` ± `r exp(0.630)` vehicles/day/m for the urban forest and `r exp(5.27)` ± `r exp(0.663)` vehicles/day/m for the urban center.
+**Road disturbance is higher in the urban center** than the urban forest (z = 39.19, df = 1, 21, p < 0.001).
+The means and SE's are 104 ± 3.23 vehicles/day/m for the urban forest and 398 ± 5.76 vehicles/day/m for the urban center.
 
 ```{r stats_graphs_tdh, echo = FALSE}
-tdh <- glm(log_tdh ~ Location, family = "poisson", data = sites)
+tdh <- glm(Traffic_Dist_Highway ~ Location, family = "poisson", data = sites)
 summary(tdh)
@@
   group_by(Location) %>% 
-  summarize(mean = mean(log_tdh),
-            se = plotrix::std.error(log_tdh))
+  summarize(mean = mean(Traffic_Dist_Highway),
+            se = plotrix::std.error(Traffic_Dist_Highway))
 
@@
 
-ggplot(sites, aes(x = Location, y = exp(log_tdh))) + 
+ggplot(sites, aes(x = Location, y = (Traffic_Dist_Highway))) + 
   geom_jitter(color = "grey", width = 0.1, size = 1) +
-  geom_point(aes(x = Location, y = exp(rate), color = Location), size = 2, data = predictions) + 
+  geom_point(aes(x = Location, y = (rate), color = Location), size = 2, data = predictions) + 
   geom_errorbar(aes(x = Location, 
-                  ymin = exp(rate - SE), 
-                  ymax = exp(rate + SE),
+                  ymin = (rate - SE), 
+                  ymax = (rate + SE),
                   color = Location), data = predictions, inherit.aes = FALSE, width = 0.15, linewidth = 1.5) +
@@
   theme(legend.position = "none") +
-  annotate(geom="text", x=1.5, y=250, label="N. S.", color="black", size = 10)
+  annotate(geom="text", x=1.5, y=250, label="***", color="black", size = 10)
 ```
@@
 
-There is **no difference** in highway disturbance between the urban forest and urban center (z = 0.530, df = 1, 20, p = 0.596).
-The means and SE's are `r exp(3.52)` ± `r exp(0.593)` vehicles/day/m for the urban forest and `r exp(3.96)` ± `r exp(0.574)` vehicles/day/m for the urban center.
+**Highway disturbance is higher in the urban center** than the urban fores (z = 9.388, df = 1, 21, p < 0.001).
+The means and SE's are 35.6 ± 1.89 vehicles/day/m for the urban forest and 65.0 ± 2.33 vehicles/day/m for the urban center.
 
 ```{r stats_graphs_plant, echo = FALSE}
-plant <- glm(log_TotalSub ~ Location, family = "poisson", data = sites)
+plant <- glm(TotalSub ~ Location, family = "poisson", data = sites)
 summary(plant)
@@
   group_by(Location) %>% 
-  summarize(mean = mean(log_TotalSub),
-            se = plotrix::std.error(log_TotalSub))
+  summarize(mean = mean(TotalSub),
+            se = plotrix::std.error(TotalSub))
 
@@
 
-ggplot(sites, aes(x = Location, y = exp(log_TotalSub))) + 
+ggplot(sites, aes(x = Location, y = (TotalSub))) + 
   geom_jitter(color = "grey", width = 0.1, size = 1) +
-  geom_point(aes(x = Location, y = exp(rate), color = Location), size = 2, data = predictions) + 
+  geom_point(aes(x = Location, y = (rate), color = Location), size = 2, data = predictions) + 
   geom_errorbar(aes(x = Location, 
-                  ymin = exp(rate - SE), 
-                  ymax = exp(rate + SE),
+                  ymin = (rate - SE), 
+                  ymax = (rate + SE),
                   color = Location), data = predictions, inherit.aes = FALSE, width = 0.15, linewidth = 1.5) +
@@
   theme(legend.position = "none") +
-  annotate(geom="text", x=1.5, y=25, label="*", color="black", size = 10)
+  annotate(geom="text", x=1.5, y=25, label="***", color="black", size = 10)
 ```
@@
 
-Plant species richness is **significantly higher in the urban forest** than the urban center (z = -2.430, df = 1, 20, p = 0.015).
-The means and SE's are `r exp(2.50)` ± `r exp(0.500)` species for the urban forest and `r exp(1.09)` ± `r exp(0.302)` species for the urban center.
+Plant species richness is **significantly higher in the urban forest** than the urban center (z = -7.674, df = 1, 21, p < 0.001).
+The means and SE's are 13.30 ± 1.153 species for the urban forest and 3.33 ± 0.527 species for the urban center.
 
@@
 
-Spectral radiance is **significantly higher in the urban center** than the urban forest (z = 3.079, df = 1, 20, p = 0.002).
+Spectral radiance is **significantly higher in the urban center** than the urban forest (z = 3.079, df = 1, 21, p = 0.002).
 The means and SE's are 137.44 ± 3.71 Watts/(m² * sr * µm) for the urban forest and 153.39 ± 3.58 Watts/(m² * sr * µm) for the urban center.
@@
 
-Light radiance is **significantly higher in the urban center** than the urban forest (z = 22.46, df = 1, 20, p < 0.001).
+Light radiance is **significantly higher in the urban center** than the urban forest (z = 22.46, df = 1, 21, p < 0.001).
 The means and SE's are 5.89 ± 0.77 mcd/m² for the urban forest and 116.90 ± 3.12 mcd/m² for the urban center.
@@
 ```{r stats_graphs_patch, echo = FALSE}
-patch <- glm(log_patch ~ Location, family = "poisson", data = sites)
+patch <- glm(patch_area_mm ~ Location, family = "poisson", data = sites)
 summary(patch)
@@
   group_by(Location) %>% 
-  summarize(mean = mean(log_patch),
-            se = plotrix::std.error(log_patch))
+  summarize(mean = mean(patch_area_mm),
+            se = plotrix::std.error(patch_area_mm))
 
@@
 
-ggplot(sites, aes(x = Location, y = exp(log_patch))) + 
+ggplot(sites, aes(x = Location, y = (patch_area_mm))) + 
   geom_jitter(color = "grey", width = 0.1, size = 1) +
-  geom_point(aes(x = Location, y = exp(rate), color = Location), size = 2, data = predictions) + 
+  geom_point(aes(x = Location, y = (rate), color = Location), size = 2, data = predictions) + 
   geom_errorbar(aes(x = Location, 
-                  ymin = exp(rate - SE), 
-                  ymax = exp(rate + SE),
+                  ymin = (rate - SE), 
+                  ymax = (rate + SE),
                   color = Location), data = predictions, inherit.aes = FALSE, width = 0.15, linewidth = 1.5) +
@@
 
-Patch area is **significantly higher in the urban forest** than the urban center (z = -3.599, df = 1, 20, p < 0.001).
-The means and SE's are `r exp(10.52)` ± `r exp(1.026)` mm² for the urban forest and `r exp(6.08)` ± `r exp(0.712)` mm² for the urban center.
+Patch area is **significantly higher in the urban forest** than the urban center (z = -374.2, df = 1, 21, p < 0.001).
+The means and SE's are 46,294.7 ± 68.040 mm² for the urban forest and 653.8 ± 7.381 mm² for the urban center.
 
@@
 
-Total road length is **significantly higher in the urban center** than the urban forest (z = 20.89, df = 1, 20, p < 0.001).
+Total road length is **significantly higher in the urban center** than the urban forest (z = 20.89, df = 1, 21, p < 0.001).
 The means and SE's are 15.67 ± 1.25 m for the urban forest and 93.03 ± 2.78 m for the urban center.
@@
 mean_se1 <- c("Mean ± Std.
-Error", "Wilderness Park \nUrban Forest", "47.15 ± 2.17", "1.27 ± 0.36", "137.44 ± 3.71", "5.89 ± 0.77", "12.18 ± 1.65", "37,049.12 ± 2.79", "52.98 ± 1.88", "33.78 ± 1.81", "15.67 ± 1.25")
+Error", "Wilderness Park \nUrban Forest", "47.15 ± 2.17", "1.27 ± 0.36", "137.44 ± 3.71", "5.89 ± 0.77", "13.30 ± 1.15", "46,294.7 ± 68.040", "104 ± 3.23", "35.6 ± 1.89", "15.67 ± 1.25")
 mean_se2 <- c("Mean ± Std.
-Error", "UNL City Campus \n Urban Center", "1.58 ± 0.36", "76.52 ± 2.53", "153.39 ± 3.58", "116.90 ± 3.12", "2.97 ± 1.35", "437.03 ± 2.04", "194.42 ± 1.94", "52.46 ± 1.78", "93.03 ± 2.78")
+Error", "UNL City Campus \n Urban Center", "1.58 ± 0.36", "76.52 ± 2.53", "153.39 ± 3.58", "116.90 ± 3.12", "3.33 ± 0.53", "116.90 ± 3.12", "398 ± 5.76", "65.0 ± 2.33", "93.03 ± 2.78")
 pred_location <- data.frame(mean_se1, mean_se2)

### 2022-11-28 manuscript/manuscript.Rmd
More work on the manuscript

@@
 require(knitr)
-```
-
-```{r import data, eval=FALSE, include = FALSE}
-webs <- read.table(file = "/Users/bjpessman/Documents/phd_research_code/Agelenopsis_aggregation/data/webs.txt", header = TRUE) 
-webs <- webs %>% 
-  mutate(ID = factor(ID),
-         Location = factor(Location), 
-         Location = fct_recode(Location, 
-                               "Urban Forest" = "Forest", 
-                               "Urban Center" = "Campus"),
-         Location = fct_relevel(Location, "Urban Forest", "Urban Center"),
-         Land = fct_recode(Land, 
-                           "Urban, High" = "UrbanizedHighIntensity",
-                           "Urban, Medium" = "UrbanizedMediumIntensity",
-                           "Urban, Low" = "UrbanizedLowIntensity",
-                           "Deciduous Forest" = "DeciduousForest",
-                           "Woody Wetlands" = "WoodyWetlands"),
-         Land = fct_relevel(Land, 
-                            "Urban, High", 
-                            "Urban, Medium", 
-                            "Urban, Low", 
-                            "Deciduous Forest", 
-                            "Woody Wetlands"),
-                  patch_area_km = patch_area_mm * 1e-6) %>% 
-  dplyr::rename("Impervious" = "Imperv", 
-                "Dist_to_Road" = "road_dist_data", 
-                "Traffic_Dist_Road" = "dist_traffic_road", 
-                "Dist_to_Highway" = "highway_dist_m", 
-                "Traffic_Dist_Highway" = "dist_traffic_highway") #data on individual webs
-
-sites <- webs %>% 
-  filter(Web == "W001")
-
-substrates <- read.table(file = "/Users/bjpessman/Documents/phd_research_code/Agelenopsis_aggregation/data/substrate.txt", header = TRUE) 
 ```
@@
 While dispersal capacity can determine a species’ range, barriers can limit dispersal and prevent animals from reaching suitable habitat  [@boulangeat_2012; @amundrud_2018].
+
 Aggregations can form when suitable conditions and resources are not evenly distributed, leading to higher-quality patches [@churchill_2020].
@@
 These conditions can contribute to changes in climatic conditions, such as when impervious cover traps heat and increases the average temperatures in cities compared to surrounding areas –- *i.e.*, the Urban Heat Island Effect [@morabito_2021].
-Disturbance from human presence can lead to air, water, and light pollution [@grimm_2008; @hopkins_2018], as well as air-borne, water-borne, and substrate-borne noise [@barber_2010; @slabbekoorn_2010; @wu_elias_2014].
+
+Disturbance from human presence can also lead to air, water, and light pollution [@grimm_2008; @hopkins_2018], as well as air-borne, water-borne, and substrate-borne noise [@barber_2010; @slabbekoorn_2010; @wu_elias_2014].
 There is growing evidence that urbanization changes species interactions, even reshaping whole food webs [@start_2020] and the landscape of parasite and disease transmission [@bradley_altizer_2007].
@@
 Thus, it is important to determine how urban factors may be contributing to variation in arthropod abundance and spatial patterns for the conservation of arthropods and their essential services.
+
 Specifically, spiders play an important role in pest control and are predicted to collectively consume up to 800 million tons of arthropods each year [@nyffeler_birkhofer_2017].
@@
 
-The mechanisms behind solitary spider aggregations are unclear despite reports of aggregations of spiders in urban habitats, such as web-builders *Lactrodectus hesperus* and *Brigittea civica*.
+**This paragraph needs citations, but it will be easier after finishing the aggregation table**
+The mechanisms behind solitary spider aggregations are unclear despite reports of aggregations of spiders in urban habitats, such as web-builders *Lactrodectus hesperus* and *Brigittea civica* [@johnson_et_al_2012; @mammola_et_al_2018].
 This gap in knowledge is concerning as urban spider aggregations can have medical and aesthetic consequences, and implications for urban pest control services.
-Prey abundance seems to be an important driver because it has been shown to be directly and indirectly related to urban spider aggregations, the latter of which is shown through investigations as light sources at night as cues of prey aggregations.
-Random spacing in solitary spiders is typically maintained by territoriality and aggression over resources like prey and mates.
+Prey abundance seems to be an important driver because it has been shown to be directly [] and indirectly [] related to urban spider aggregations, the latter of which is shown through investigations as light sources at night as cues of prey aggregations [].
+Random spacing in solitary spiders is typically maintained by territoriality and aggression over resources like prey and mates [@riechert_1974b].
 Occassionally, conditions arise that allow solitary spiders to become more tolerant of neighbors, and understanding these contexts can help uncover the mechanisms of aggregative behavior.
-Aggregations have been shown to form as a result of dispersal limitations, predator release, lekking reproductive strategies, plant structure, and environmental stressors.
-The degree of aggregation in spiders can also change over time, often times more intense during juvenile stages when dispersal is limited, spreading over time as subadults and adults become more territorial [].
+Aggregations have been shown to form as a result of dispersal limitations [], predator release [], lekking reproductive strategies [], plant structure [], and environmental stressors [].
+The degree of aggregation in spiders can also change over time, often times more intense during juvenile stages when dispersal is limited, spreading over time as subadults and adults become more territorial [@riechert_1974b].
 Studies on mechanisms of aggregations in spiders are presented and discussed in Table 1.
 
-Funnel weavers in the genus *Agelenopsis* actively select web locations based on experience of perceived quality of the site [@riechert_1976], and are thus likely impacted environmental conditions resulting from urbanization.
+Funnel weavers in the genus *Agelenopsis* actively select web locations based on experience of perceived quality of the site [@riechert_1976], and are thus likely impacted by environmental conditions resulting from urbanization.
 Prey abundance, available web substrates, vegetation structure, and microclimate conditions have been shown to be indicators of a quality web site in a desert habitat for *A.
 aperta* [@riechert_1974; @riechert_1973].
-In the same species, spatial patterns changed throughout life stages, although this may depend on environmental conditions and dispersal [@riechert_1974].
 *Agelenopsis pennsylvanica* build webs that consist of a sheet that functions as a prey capture area and a retreat to escape from predators and unfavorable conditions (Fig.
@@
 S1).
-These two habitats were selected due to their distinctive characteristics (described below), preliminary observations of potential differences in funnel weaver abundance and aggregation, and ease of access.
+These two habitats were selected due to their distinctive characteristics (described below), preliminary observations of potential differences in funnel weaver abundance and aggregation (Fig.
+S2), and ease of access.
 
@@
 Finally, we assessed artificial light at night levels using the 2020 Visible Infrared Imaging Radiometer Suite (VIIRS) from https://www.lightpollutionmap.info/ (500-meter resolution).
-We polygonized the tiff files and calculated the average value for each factor by habitat: UNL City Campus, Wilderness Park, and Lincoln City Limits (see Fig.
+We polygonized the tiff files and calculated the average value for each factor by location: UNL City Campus, Wilderness Park, and Lincoln City Limits (see Fig.
 2, Fig.
-S2-S5).
-We included measurements for Lincoln city limits to show how the two study habitats compare to the city of Lincoln overall.
+S3-S6).
+We included measurements for Lincoln city limits to show how the two study locations compare to the city of Lincoln overall.
 We calculated the averages using the following equation:
@@
 Impervious cover -- in the form of buildings and pavement -- dominates the land on UNL City Campus, considerably more than impervious cover across the city of Lincoln (Table 1, Fig.
-S2).
+S3).
 Lawns are maintained by frequent mowing, and gardens and landscaping are regularly pruned.
 Tree cover on UNL City Campus and in Lincoln overall is low (< 6%, Table 1, Fig.
-S3).
+S4).
 There was heavy foot traffic from UNL's 20,286 undergraduates enrolled in the 2020-2021 academic year, 37% of which lived in college-owned, -operated, or -affiliated housing [@iea_2021].
@@
 Further, UNL City Campus exhibits heighten spectral radiance (thermal conditions, Fig.
-S4) and artificial light at night radiance (Fig.
-S5), even above that of Lincoln as a whole (Table 1).
+S5) and artificial light at night radiance (Fig.
+S6), even above that of Lincoln as a whole (Table 1).
 Thus, we designated UNL City Campus as an *urban center* and refer to it as such hereafter.
@@
 We found about two-fifths of Wilderness Park to be shrouded in trees (Table 1, Fig.
-S3), with less than 2% of its land imperviously covered (Table 1, Fig.
+S4), with less than 2% of its land imperviously covered (Table 1, Fig.
 S2).
@@
 Wilderness Park showed greatly reduced spectral radiance (Fig.
-S4) and artificial light at night radiance (Fig.
-S5) than the city of Lincoln (Table 1).
+S5) and artificial light at night radiance (Fig.
+S6) than the city of Lincoln (Table 1).
 Due to its proximity to Lincoln city limits, we designate Wilderness Park as an *urban forest* and refer to it as such hereafter.
@@
 Within the boundaries of the urban forest, we assigned numbers to intersections of three or more trails (Fig.
-S6).
+S7).
 Similarly, we assigned numbers to each intersection of roads and sidewalks that meet from the four cardinal directions in the urban center (Fig.
-S6).
+S7).
 We used a random number generator to randomly select 10 intersections in the urban forest and 12 intersections in the urban center as start sites (Table S1).
@@
 We thoroughly searched the edges of the path for funnel webs as the GPS receiver tracked our movement (Fig.
-S7).
+S8).
 We walked along pre-existing sidewalks, roads, and trails because paths were a common feature of both habitats along which we had previously found funnel weavers.
@@
 We also assessed nearest neighbor distances as a measure of aggregation behavior.
-Starting at the focal web and working outwards, we marked the locations of the two webs (occupied and unoccupied) nearest to the focal web within ten meters.
+Starting at the focal web and working outwards, we marked the locations of the two webs (including occupied and unoccupied) nearest to the focal web within ten meters.
 We limited our measurements to the nearest two webs because we often found no more than three webs (including the focal web) per site in the urban forest.
 We measured the shortest distance from the retreat of the focal web to the retreat of the two nearest neighbor webs.
-To explore differences in web placement, we measured the web height from the ground to the web retreat.
+To explore differences in web placement, we measured the web height from the ground to the web retreat for every web with the ten-meter radius.
 Differences in web height have been shown to vary by environmental factors associated with urbanization [@dahirel_2017].
@@
 During these dates, all *A.
-pennsylvanica* have reached maturity [@guarisco_2014; unpublished data].
+pennsylvanica* have reached maturity [@guarisco_2014; personal observation].
 Of the 64 occupied webs, 61 were occupied by females indicating that males had likely abandoned their webs in search of females.
@@
 To assess potential mechanisms behind variation in abundance, aggregation, and position, we looked for correlations between spider spatial patterns and environmental conditions -- collected in the field (plant species richness) or using GIS for each site.
-In QGIS, we created 100 meter buffers around focal web sites and processed the GIS variables mentioned above (tree cover, impervious cover, spectral radiance, and artificial light at night radiance) in the same manner as before.
+In QGIS, we created 100 meter buffers around each focal web location and processed the GIS variables mentioned above (tree cover, impervious cover, spectral radiance, and artificial light at night radiance) in the same manner as before.
 To these we added patch area, potential disturbance from nearby roads and highways, and road length in the 100 meter buffer.
@@
 We used Poisson generalized linear mixed effect models [*lme4* package in R, @lme4] with site as a random effect for the response variables: nearest neighbor distance and web height.
-For the model with nearest neighbor distance, we also included neighbor number (nearest and second nearest web) and its interaction with habitat.
-We used Poisson distributions because the response variables were not normally distributed according to Shapiro-Wilk Normality Tests, and all data were strictly positive with no upper limit.
+For the model with nearest neighbor distance, we also included neighbor number (nearest and second nearest web) and its interaction with habitat We used Poisson distributions because the response variables were not normally distributed according to Shapiro-Wilk Normality Tests, and all data were strictly positive with no upper limit.
 
@@
 
-Since we found significant variation in distribution measures between habitats, we wanted to explore potential environmental mechanisms of such variation within habitats.
+Since we found significant variation in distribution measures between habitats, we wanted to explore potential environmental mechanisms of such variation within the test habitats.
 We first tested whether the nine environmental predictors varied by habitat (Table 2).
@@
 We excluded search distance as a response variable because the predictors were collected from the site of the focal web and may vary along the search path.
-Several predictors (plant species richness, patch area, and road and highway disturbance) were highly skewed toward zero, so we used a natural log-transformation prior to model selection.
+Several predictors (plant species richness, patch area, and road and highway disturbance) were highly right-skewed, so we used a natural log-transformation prior to model selection.
 We used Poisson generalized linear models for number of webs and spiders and nearest neighbor distance and Poisson generalized linear mixed-effect models for web height with site as a random effect.
@@
 We report here the results of each top model, as well as a model average of models within 2 delta AICc points of the top model.
-Reported estimates and standard error are back-transformed for variables that were natural log-transformed using the *exp()* function.
-We checked that the Variance of Inflation (VIF) stayed below a score of two for predictors in each top model using the *car* package in R [@car].
+We reported the estimates and standard error from the models without back-transformations for the log-transformed variables.
+We checked that the Variance of Inflation (VIF) stayed at or below a score of two for predictors in each top model using the *car* package in R [@car].
 
@@
 We tested Poisson generalized linear models for each response variable with land cover as the only predictor.
+We used the *Anova()* function in the *car* package [@car] to get the Likelihood Ratio Chi-Squared values, then used the *glht()* funtion in the *multcomp* package [@multcomp] to perform pairwise comparisons among categories.
 We include these results in supplemental material (Fig.
-S11, Table S3-7) as the sample sizes were small (deciduous forest = 7, woody wetlands = 3, urban high intensity = 4, urban medium intensity = 6, urban low intensity = 2).
+S12, Table S3) as the sample sizes were small (deciduous forest = 7, woody wetlands = 3, urban high intensity = 4, urban medium intensity = 6, urban low intensity = 2).
 
-We completed statistics and visualization using R 4.0.0 [@r] and RStudio 2022.2.0.443 [@rstudio].
-All graphs show raw data and (top) model estimates (*broom* package in R)[@broom].
-We used the *tidyverse* [@tidyverse], *ggpubr* [@ggpubr], and *broomExtra* [@broomExtra] packages in R to produce and customize the graphs.
-For Poisson generalized linear mixed effect models, we determined the 95% confidence intervals of the model estimates by completing 1000 bootstrap iterations using the function *bootMer()* in R package *lme4*.
-We used the package *sjPlot* [@sjPlot] in R to produce the land use tables in the supplemental material (Table S3-7).
-All R code and data are posted here: https://github.com/brandipessman.
+We completed statistics and visualization using R 4.0.0 [@r] and RStudio 2022.07.2 [@rstudio].
+All graphs show raw data and (top) model estimates (*broom* package [@broom]; *emmeans* package [@emmeans]).
+We used the *tidyverse* [@tidyverse], *ggpubr* [@ggpubr], and *broom.mixed* [@broommixed] packages in R to produce and customize the graphs.
+The *flextable* package [@flextable] was used to produce the tables.
+For Poisson generalized linear mixed effect models, we determined the 95% confidence intervals of the model estimates by completing 1000 bootstrap iterations using the function *bootMer()* in R package *lme4* [@lme4].
+All R code and data are available in a GitHub repository at: https://github.com/brandipessman/Agelenopsis_aggregation.
 
@@
 3a, Fig.
-S7).
+S8).
 Within a 10-meter radius of the focal web, we counted significantly more webs ($z_20$ = 8.56, *P* < 0.001, Fig.
@@
 3d).
-By definition, the second nearest web is further from the focal web than the nearest neighbor ($z_34$ = 14.654, *P* < 0.001).
-There was a significant interaction between neighbor number and habitat -- the increase in distance from the nearest to second nearest web was smaller in the urban center than the urban forest ($z_34$ = 9.86, *P* < 0.001, Fig.
+By definition, the second nearest web is further from the focal web than the nearest neighbor ($z_34$ = 14.65, *P* < 0.001).
+There was a significant interaction between neighbor number and habitat -- the second nearest neighbor was significantly further from the focal web than the first nearest neighbor in the urban center, but not the urban forest ($z_34$ = 9.86, *P* < 0.001, Fig.
 3d).
@@
 Plant species richness and highway disturbance both had a negative relationship with abundance measures for the overall data set (Table 3, Fig.
-S10).
+S11).
 Interestingly, the top model of web abundance retained road disturbance and suggested a positive relationship overall (Table 3, Fig.
-S10).
+S11).
 
 Overall, spiders are closer together when plant species richness is low and when road disturbance is high (Table 3, Fig.
-S10).
+S11).
 On the other hand, less tree cover, lower road and highway disturbance, and greater plant species richness are associated with nearness in the urban forest (Table 3, Fig.
@@
 Further, webs are built higher overall when the number of plant species is higher (Table 3, Fig.
-S10).
+S11).
 A trend also suggests that lower webs are associated with higher road disturbance, although this result is not significant (Table 3, Fig.
-S10).
+S11).
 In the urban forest, web height is positively related to tree cover (Table 3).
@@
 
-For statistical analysis and figures of response variables by land cover class, see supplemental material (Table S3-7, Fig.
-S11).
+For statistical analysis and figures of response variables by land cover class, see supplemental material (Table S3, Fig.
+S12).
+Following Likelihood Ratio tests, we find that all response variables significantly vary by land cover class (Table S3).
 There was no difference in search distance between deciduous forest, urban medium intensity and urban low intensity.
-However, we searched significantly further in woody wetlands and significantly shorter in urban high intensity.
-The number of webs and spiders only varied by habitat - urban low, medium, and high intensity had more webs and spiders than deciduous forest or woody wetlands.
-Nearest neighbor distance was shorter for woody wetlands than deciduous forest.
-For the urban intensities, web distance was shortest at low intensities and furthest at medium intensities.
-Lastly, deciduous forest and urban low intensity did not differ in web height.
-Woody wetlands had significantly higher webs and urban medium and high intensities had significantly lower webs.
+However, we searched significantly further in woody wetlands and significantly shorter in urban high intensity (Fig.
+S12a).
+The number of webs and spiders only varied by habitat - urban low, medium, and high intensity had more webs and spiders than deciduous forest or woody wetlands (Fig.
+S12a-b).
+Nearest neighbor distance was shorter for woody wetlands than deciduous forest (Fig.
+S12d).
+For the urban intensities, web distance was shortest at low intensities and furthest at medium intensities with high urban intensity suggest web height between low and medium intensities (Fig.
+S12d).
+Lastly, web height showed no difference between land cover class with pairwise comparisons (Fig.
+S12e).
 
@@
 
-**would like to add that Agelenopsis are generalists and widespread but CANNOT find citations**
 **need to talk more about predator and competitor abundance? - I think not, mention in next paragraph.**
@@
 On the other hand, abundance for webs ranged from one to 73 webs and one to 22 spiders per urban center site.
-Additionally, urban forest abundance may be better predicted by factors not assessed here, such as prey and predator abundance or dispersal limitation [CITE].
+Additionally, urban forest abundance may be better predicted by factors not assessed here, such as prey and predator abundance or dispersal limitation [@harwood_2001; @bonte_et_al_2003].
 In the urban center, web and spider abundance was higher when plant species richness, patch area, highway disturbance, and road length were lower.
-*Agelenopsis pennsylvanica* rely heavily on vibrations to capture prey [CITE], court potential mates [CITE], and potentially evade predators [CITE].
-Thus, vibratory noise may play a key role in web site selection, choosing sites that mitigate these effects [CITE].
+*Agelenopsis pennsylvanica* rely heavily on vibrations to capture prey [@riechert_maupin_1998], court potential mates [@singer_2000], and potentially evade predators [@riechert_hedrick_1990].
+Thus, we suspect that vibratory noise may play a key role in web site selection, choosing sites that mitigate these effects.
 We show that webs and spiders are more abundant in urban center sites that had lower highway disturbance and total length of road in a 100-meter radius.
-Although research on the effects of noise on arthorpod behavior has focused on acoustic rather than vibratory noise, studies have found strong negative effects of acoustic and vibratory noise on arthropod behavior [CITE].
-A recent study shows that the orb-weaving spider, *Larinioides sclopetarius* is able to detect airborne sound that induces vibrations in the web [zhou et al.
-2022].
+Although research on the effects of noise on arthropod behavior has focused on acoustic rather than vibratory noise [@roberts_howard_2022], studies have found strong negative effects of acoustic and vibratory noise on arthropod behavior [@carosi_et_al_2019; @bunkley_et_al_2017].
+A recent study shows that the orb-weaving spider, *Larinioides sclopetarius* is able to detect airborne sound that induces vibrations in the web [@zhou_et_al_2022].
 

### 2022-11-28 manuscript/supplemental.Rmd
More work on the manuscript

@@
 **Fig.
-S2** Impervious cover raster with borders for Lincoln, Nebraska, USA city limits (dashed border), University of Nebraska-Lincoln (UNL) City Campus (solid border, a), and Wilderness Park (solid border, b) using the 2019 National Land Cover Data on Impervious Cover and QGIS (v.
+S3** Impervious cover raster with borders for Lincoln, Nebraska, USA city limits (dashed border), University of Nebraska-Lincoln (UNL) City Campus (solid border, a), and Wilderness Park (solid border, b) using the 2019 National Land Cover Data on Impervious Cover and QGIS (v.
 3.16.3-Hannover, ESRI 102704)
@@
 **Fig.
-S3** Tree cover raster with borders for Lincoln, Nebraska, USA city limits (dashed border), University of Nebraska-Lincoln (UNL) City Campus (solid border, a), and Wilderness Park (solid border, b) using the 2016 National Land Cover Data on Tree Cover and QGIS (v.
+S4** Tree cover raster with borders for Lincoln, Nebraska, USA city limits (dashed border), University of Nebraska-Lincoln (UNL) City Campus (solid border, a), and Wilderness Park (solid border, b) using the 2016 National Land Cover Data on Tree Cover and QGIS (v.
 3.16.3-Hannover, ESRI 102704)
@@
 **Fig.
-S4** Spectral radiance raster with borders for Lincoln, Nebraska, USA city limits (dashed border), University of Nebraska-Lincoln (UNL) City Campus (solid border, a), and Wilderness Park (solid border, b) using the satellite image of path 28, row 32 of the Landsat-7 World Reference System-2 (Band 6, September 2, 2020) and QGIS (v.
+S5** Spectral radiance raster with borders for Lincoln, Nebraska, USA city limits (dashed border), University of Nebraska-Lincoln (UNL) City Campus (solid border, a), and Wilderness Park (solid border, b) using the satellite image of path 28, row 32 of the Landsat-7 World Reference System-2 (Band 6, September 2, 2020) and QGIS (v.
 3.16.3-Hannover, ESRI 102704)
@@
 **Fig.
-S5** Artificial light at night radiance raster with borders for Lincoln, Nebraska, USA city limits (dashed border), University of Nebraska-Lincoln (UNL) City Campus (solid border, a), and Wilderness Park (solid border, b) using the 2020 Visible Infrared Imaging Radiometer Suite (VIIRS) and QGIS (v.
+S6** Artificial light at night radiance raster with borders for Lincoln, Nebraska, USA city limits (dashed border), University of Nebraska-Lincoln (UNL) City Campus (solid border, a), and Wilderness Park (solid border, b) using the 2020 Visible Infrared Imaging Radiometer Suite (VIIRS) and QGIS (v.
 3.16.3-Hannover, ESRI 102704)
@@
 **Fig.
-S6** Intersections randomly chosen from as starting sites.
+S7** Intersections randomly chosen from as starting sites.
 We selected Wilderness Park intersections (left) from trail intersections where 3 or more paths meet.
@@
 **Fig.
-S7** Paths walked from the starting site until the first occupied web (the focal web).
+S8** Paths walked from the starting site until the first occupied web (the focal web).
 Site ID is labeled at the focal web site.
@@
 **Fig.
-S8** Plant species found within a ten-meter radius of focal web at each site.
+S9** Plant species found within a ten-meter radius of focal web at each site.
 Plant species at each site are underneath the colored and labeled site indicator (orange for University of Nebraska-Lincoln (UNL) City Campus and green for Wilderness Park).
@@
 
-**Fig. S9** Representation of web substrates by class. Green shades indicate plant material classes, and orange indicates non-plant materials
+**Fig. S10** Representation of web substrates by class. Green shades indicate plant material classes, and orange indicates non-plant materials
 
@@
 
-**Fig.S10** Significant correlations between response variables (number of webs, number of spiders, nearest neighbor distance, and web height) and the environmental predictors (plant species richness and road disturbance and highway disturbance) for the whole data set.
+**Fig.S11** Significant correlations between response variables (number of webs, number of spiders, nearest neighbor distance, and web height) and the environmental predictors (plant species richness and road disturbance and highway disturbance) for the whole data set.
 The regression lines and shaded regions represent the predictions and 95% confidence intervals (respectively) from the top Poisson Generalized Linear Model after AIC selection.
@@
 **Fig.
-S11** Comparison of search distance (a), the number of webs (b) and spiders (c) in a 10-meter radius of the focal web, the distance from the focal web to the first (d) and second (e) nearest neighbors, and web height (f) by land cover class - deciduous forest, woody wetlands, urban high intensity, urban medium intensity, and urban low intensity.
+S12** Comparison of search distance (a), the number of webs (b) and spiders (c) in a 10-meter radius of the focal web, the distance from the focal web to the first (d) and second (e) nearest neighbors, and web height (f) by land cover class - deciduous forest, woody wetlands, urban high intensity, urban medium intensity, and urban low intensity.
 Land cover class was determined using the pixel category from the 2019 National Land Cover Data that the focal web site resides in.

### 2022-12-05 data_analysis.Rmd
Some more manuscript edits

@@
               alpha = 0.25) +
-  scale_y_continuous(limits = c(min(log(sites$NumWebs)), max(log(sites$NumWebs)) + 0.1 * diff(range(log(sites$NumWebs))))) +  
+#  scale_y_continuous(limits = c(min(log(sites$NumWebs)), max(log(sites$NumWebs)) + 0.1 * diff(range(log(sites$NumWebs))))) +  
+  scale_y_continuous(limits = c(-1.2, 5), breaks = c(-1, 0, 1, 2, 3, 4, 5)) +  
   theme_classic() +
@@
   theme(axis.text.y = element_text(colour = "black", size = 10)) +
-  theme(axis.text.x = element_blank(), 
-        axis.title.x = element_blank(),
-        axis.text.y = element_blank(),
-        axis.title.y = element_blank()) +
-  annotate(geom = "text", x = min(predicted.distance$log_TotalSub) + diff(range(predicted.distance$log_TotalSub))/2, y = max(log(sites$NumWebs)), label = "***", color = "black", size = 4)
+  theme(axis.title.x = element_blank(), 
+        axis.title.y = element_blank(),
+        axis.text.x = element_blank()) + 
+#  theme(axis.text.y = element_blank()) +
+#  annotate(geom = "text", x = min(predicted.distance$log_TotalSub) + diff(range(predicted.distance$log_TotalSub))/2, y = max(log(sites$NumWebs)), label = "***", color = "black", size = 4) +
+  annotate(geom = "text", x = min(predicted.distance$log_TotalSub) + diff(range(predicted.distance$log_TotalSub))/2, y = 4.8, label = "***", color = "black", size = 4)
 
@@
   theme(axis.text.y = element_text(colour = "black", size = 10)) +
-  theme(axis.text.x = element_blank(), 
-        axis.title.x = element_blank(),
+  theme(axis.title.x = element_blank(), 
+        axis.title.y = element_blank(), 
         axis.text.y = element_blank(),
-        axis.title.y = element_blank()) +
-  annotate(geom = "text", x = min((predicted.distance$log_tdr)) + diff(range((predicted.distance$log_tdr)))/2, y = max(log(sites$NumWebs)), label = "***", color = "black", size = 4)
+        axis.text.x = element_blank()) + 
+#  annotate(geom = "text", x = min((predicted.distance$log_tdr)) + diff(range((predicted.distance$log_tdr)))/2, y = max(log(sites$NumWebs)), label = "***", color = "black", size = 4) +
+    annotate(geom = "text", x = min((predicted.distance$log_tdr)) + diff(range((predicted.distance$log_tdr)))/2, y = 4.8, label = "***", color = "black", size = 4)
 
@@
               alpha = 0.25) +
-  scale_y_continuous(limits = c(min(log(sites$NumWebs)) - 1.2, max(log(sites$NumWebs)) + 0.1 * diff(range(log(sites$NumWebs))))) +  
+#  scale_y_continuous(limits = c(min(log(sites$NumWebs)) - 1.2, max(log(sites$NumWebs)) + 0.1 * diff(range(log(sites$NumWebs))))) +  
+  scale_y_continuous(limits = c(-1.2, 5), breaks = c(-1, 0, 1, 2, 3, 4, 5)) +  
   theme_classic() +
@@
   theme(axis.text.y = element_text(colour = "black", size = 10)) +
-  theme(axis.text.x = element_blank(), 
-        axis.title.x = element_blank(),
+  theme(axis.title.x = element_blank(), 
+        axis.title.y = element_blank(), 
         axis.text.y = element_blank(),
-        axis.title.y = element_blank()) +
-  annotate(geom = "text", x = min((predicted.distance$log_tdh)) + diff(range((predicted.distance$log_tdh)))/2, y = max(log(sites$NumWebs)), label = "***", color = "black", size = 4)
+        axis.text.x = element_blank()) + 
+#  annotate(geom = "text", x = min((predicted.distance$log_tdh)) + diff(range((predicted.distance$log_tdh)))/2, y = max(log(sites$NumWebs)), label = "***", color = "black", size = 4) +
+  annotate(geom = "text", x = min((predicted.distance$log_tdh)) + diff(range((predicted.distance$log_tdh)))/2, y = 4.8, label = "***", color = "black", size = 4)
 
@@
               alpha = 0.25) +
-  scale_y_continuous(limits = c(min(log(sites_center$NumWebs)), max(log(sites_center$NumWebs)) + 0.1 * diff(range(log(sites_center$NumWebs))))) +  
+#  scale_y_continuous(limits = c(min(log(sites_center$NumWebs)), max(log(sites_center$NumWebs)) + 0.1 * diff(range(log(sites_center$NumWebs))))) +  
+  scale_y_continuous(limits = c(-1.2, 5), breaks = c(-1, 0, 1, 2, 3, 4, 5)) +
   theme_classic() +
@@
   theme(axis.text.y = element_text(colour = "black", size = 10)) +
-  theme(axis.text.x = element_blank(), 
-        axis.title.x = element_blank(),
-        axis.text.y = element_blank(),
-        axis.title.y = element_blank()) +
-  annotate(geom = "text", x = min((predicted.distance$log_TotalSub)) + diff(range((predicted.distance$log_TotalSub)))/2, y = max(log(sites_center$NumWebs)), label = "***", color = "black", size = 4)
+  theme(axis.title.x = element_blank(), 
+        axis.title.y = element_blank(), 
+        axis.text.x = element_blank()) + 
+#  theme(axis.text.y = element_blank()) +
+#  annotate(geom = "text", x = min((predicted.distance$log_TotalSub)) + diff(range((predicted.distance$log_TotalSub)))/2, y = max(log(sites_center$NumWebs)), label = "***", color = "black", size = 4) +
+  annotate(geom = "text", x = min((predicted.distance$log_TotalSub)) + diff(range((predicted.distance$log_TotalSub)))/2, y = 5, label = "***", color = "black", size = 4)
 
@@
               alpha = 0.25) +
-  scale_y_continuous(limits = c(min(log(sites_center$NumWebs)) - 0.75, max(log(sites_center$NumWebs)) + 0.15 * diff(range(log(sites_center$NumWebs))))) +  
+#  scale_y_continuous(limits = c(min(log(sites_center$NumWebs)) - 0.75, max(log(sites_center$NumWebs)) + 0.15 * diff(range(log(sites_center$NumWebs))))) +  
+  scale_y_continuous(limits = c(-1.2, 5), breaks = c(-1, 0, 1, 2, 3, 4, 5)) +
   theme_classic() +
@@
   theme(axis.text.y = element_text(colour = "black", size = 10)) +
-  theme(axis.text.x = element_blank(), 
-        axis.title.x = element_blank(),
+  theme(axis.title.x = element_blank(), 
+        axis.title.y = element_blank(), 
         axis.text.y = element_blank(),
-        axis.title.y = element_blank()) +
-  annotate(geom = "text", x = min((predicted.distance$log_patch)) + diff(range((predicted.distance$log_patch)))/2, y = max(log(sites_center$NumWebs)), label = "**", color = "black", size = 4)
+        axis.text.x = element_blank()) + 
+#  annotate(geom = "text", x = min((predicted.distance$log_patch)) + diff(range((predicted.distance$log_patch)))/2, y = max(log(sites_center$NumWebs)), label = "**", color = "black", size = 4) +
+    annotate(geom = "text", x = min((predicted.distance$log_patch)) + diff(range((predicted.distance$log_patch)))/2, y = 5, label = "**", color = "black", size = 4)
 
@@
               alpha = 0.25) +
-  scale_y_continuous(limits = c(min(log(sites_center$NumWebs)) - 0.75, max(log(sites_center$NumWebs)) + 0.1 * diff(range(log(sites_center$NumWebs))))) +  
+#  scale_y_continuous(limits = c(min(log(sites_center$NumWebs)) - 0.75, max(log(sites_center$NumWebs)) + 0.1 * diff(range(log(sites_center$NumWebs))))) +  
+  scale_y_continuous(limits = c(-1.2, 5), breaks = c(-1, 0, 1, 2, 3, 4, 5)) +
   theme_classic() +
@@
   theme(axis.text.y = element_text(colour = "black", size = 10)) +
-  theme(axis.text.x = element_blank(), 
-        axis.title.x = element_blank(),
+  theme(axis.title.x = element_blank(), 
+        axis.title.y = element_blank(), 
         axis.text.y = element_blank(),
-        axis.title.y = element_blank()) +
-  annotate(geom = "text", x = min((predicted.distance$log_tdh)) + diff(range((predicted.distance$log_tdh)))/2, y = max(log(sites_center$NumWebs)), label = "***", color = "black", size = 4)
+        axis.text.x = element_blank()) + 
+#  annotate(geom = "text", x = min((predicted.distance$log_tdh)) + diff(range((predicted.distance$log_tdh)))/2, y = max(log(sites_center$NumWebs)), label = "***", color = "black", size = 4) +
+  annotate(geom = "text", x = min((predicted.distance$log_tdh)) + diff(range((predicted.distance$log_tdh)))/2, y = 5, label = "***", color = "black", size = 4)
 
@@
               alpha = 0.25) +
-  scale_y_continuous(limits = c(min(log(sites_center$NumWebs)), max(log(sites_center$NumWebs)) + 0.1 * diff(range(log(sites_center$NumWebs))))) +  
+#  scale_y_continuous(limits = c(min(log(sites_center$NumWebs)), max(log(sites_center$NumWebs)) + 0.1 * diff(range(log(sites_center$NumWebs))))) +
+  scale_y_continuous(limits = c(-1.2, 5), breaks = c(-1, 0, 1, 2, 3, 4, 5)) +
   theme_classic() +
@@
   theme(axis.text.y = element_text(colour = "black", size = 10)) +
-  theme(axis.text.x = element_blank(), 
-        axis.title.x = element_blank(),
+  theme(axis.title.x = element_blank(), 
+        axis.title.y = element_blank(), 
         axis.text.y = element_blank(),
-        axis.title.y = element_blank()) +
-  annotate(geom = "text", x = min((predicted.distance$road_length_m)) + diff(range((predicted.distance$road_length_m)))/2, y = max(log(sites_center$NumWebs)), label = "***", color = "black", size = 4)
+        axis.text.x = element_blank()) + 
+#  annotate(geom = "text", x = min((predicted.distance$road_length_m)) + diff(range((predicted.distance$road_length_m)))/2, y = max(log(sites_center$NumWebs)), label = "***", color = "black", size = 4) +
+  annotate(geom = "text", x = min((predicted.distance$road_length_m)) + diff(range((predicted.distance$road_length_m)))/2, y = 5, label = "***", color = "black", size = 4)
 
@@
               alpha = 0.25) +
-  scale_y_continuous(limits = c(min(log(sites$NumSpiders)) - 2, max(log(sites$NumSpiders)) + 0.1 * diff(range(log(sites$NumSpiders))))) +  
+#  scale_y_continuous(limits = c(min(log(sites$NumSpiders)) - 2, max(log(sites$NumSpiders)) + 0.1 * diff(range(log(sites$NumSpiders))))) +  
+  scale_y_continuous(limits = c(-2, 3.3), breaks = c(-2, -1, 0, 1, 2, 3)) +  
   theme_classic() +
@@
   theme(axis.text.y = element_text(colour = "black", size = 10)) +
-  theme(axis.text.x = element_blank(), 
-        axis.title.x = element_blank(),
-        axis.text.y = element_blank(),
-        axis.title.y = element_blank()) +
-  annotate(geom = "text", x = min(predicted.distance$log_TotalSub) + diff(range(predicted.distance$log_TotalSub))/2, y = max(log(sites$NumSpiders)), label = "***", color = "black", size = 4)
+  theme(axis.title.x = element_blank(), 
+        axis.title.y = element_blank(),
+        axis.text.x = element_blank()) + 
+#  theme(axis.text.y = element_blank()) +
+#  annotate(geom = "text", x = min(predicted.distance$log_TotalSub) + diff(range(predicted.distance$log_TotalSub))/2, y = max(log(sites$NumSpiders)), label = "***", color = "black", size = 4)
+    annotate(geom = "text", x = min(predicted.distance$log_TotalSub) + diff(range(predicted.distance$log_TotalSub))/2, y = 3, label = "***", color = "black", size = 4)
 
@@
   theme(axis.text.y = element_text(colour = "black", size = 10)) +
-  theme(axis.text.x = element_blank(), 
-        axis.title.x = element_blank(),
-        axis.text.y = element_blank(),
-        axis.title.y = element_blank()) +
-  annotate(geom = "text", x = min((predicted.distance$log_tdh)) + diff(range((predicted.distance$log_tdh)))/2, y = max(log(sites$NumSpiders)), label = "***", color = "black", size = 4)
+  theme(axis.title.x = element_blank(), 
+        axis.title.y = element_blank(), 
+        axis.text.y = element_blank()) + 
+#  theme(axis.text.x = element_blank()) +
+#  annotate(geom = "text", x = min((predicted.distance$log_tdh)) + diff(range((predicted.distance$log_tdh)))/2, y = max(log(sites$NumSpiders)), label = "***", color = "black", size = 4)
+  annotate(geom = "text", x = min((predicted.distance$log_tdh)) + diff(range((predicted.distance$log_tdh)))/2, y = 3, label = "***", color = "black", size = 4)
 
@@
               alpha = 0.25) +
-  scale_y_continuous(limits = c(min(log(sites_center$NumSpiders)) - 1, max(log(sites_center$NumSpiders)) + 0.2 * diff(range(log(sites_center$NumSpiders))))) +  
+#  scale_y_continuous(limits = c(min(log(sites_center$NumSpiders)) - 1, max(log(sites_center$NumSpiders)) + 0.2 * diff(range(log(sites_center$NumSpiders))))) +  
+  scale_y_continuous(limits = c(-2, 3.5), breaks = c(-2, -1, 0, 1, 2, 3)) +  
   theme_classic() +
@@
   theme(axis.text.y = element_text(colour = "black", size = 10)) +
-  theme(axis.text.x = element_blank(), 
-        axis.title.x = element_blank(),
-        axis.text.y = element_blank(),
+  theme(axis.title.x = element_blank(), 
         axis.title.y = element_blank()) + 
-  annotate(geom = "text", x = min((predicted.distance$log_TotalSub)) + diff(range((predicted.distance$log_TotalSub)))/2, y = max(log(sites_center$NumSpiders)), label = "***", color = "black", size = 4)
+#  theme(axis.text.x = element_blank(), 
+#        axis.text.y = element_blank()) +
+#  annotate(geom = "text", x = min((predicted.distance$log_TotalSub)) + diff(range((predicted.distance$log_TotalSub)))/2, y = max(log(sites_center$NumSpiders)), label = "***", color = "black", size = 4)
+  annotate(geom = "text", x = min((predicted.distance$log_TotalSub)) + diff(range((predicted.distance$log_TotalSub)))/2, y = 3.5, label = "***", color = "black", size = 4)
 
@@
               alpha = 0.25) +
-  scale_y_continuous(limits = c(min(log(sites_center$NumSpiders)) - 1, max(log(sites_center$NumSpiders)) + 0.15 * diff(range(log(sites_center$NumSpiders))))) +  
+#  scale_y_continuous(limits = c(min(log(sites_center$NumSpiders)) - 1, max(log(sites_center$NumSpiders)) + 0.15 * diff(range(log(sites_center$NumSpiders))))) +  
+  scale_y_continuous(limits = c(-2, 3.5), breaks = c(-2, -1, 0, 1, 2, 3)) +  
   theme_classic() +
@@
   theme(axis.text.y = element_text(colour = "black", size = 10)) +
-  theme(axis.text.x = element_blank(), 
-        axis.title.x = element_blank(),
-        axis.text.y = element_blank(),
-        axis.title.y = element_blank()) +
-  annotate(geom = "text", x = min((predicted.distance$log_patch)) + diff(range((predicted.distance$log_patch)))/2, y = max(log(sites_center$NumSpiders)), label = "**", color = "black", size = 4)
+  theme(axis.title.x = element_blank(), 
+        axis.title.y = element_blank(), 
+        axis.text.y = element_blank()) + 
+#  theme(axis.text.x = element_blank()) +
+#  annotate(geom = "text", x = min((predicted.distance$log_patch)) + diff(range((predicted.distance$log_patch)))/2, y = max(log(sites_center$NumSpiders)), label = "**", color = "black", size = 4) 
+  annotate(geom = "text", x = min((predicted.distance$log_patch)) + diff(range((predicted.distance$log_patch)))/2, y = 3.5, label = "**", color = "black", size = 4)
 
@@
               alpha = 0.25) +
-  scale_y_continuous(limits = c(min(log(sites_center$NumSpiders)) - 2, max(log(sites_center$NumSpiders)) + 0.1 * diff(range(log(sites_center$NumSpiders))))) +  
+#  scale_y_continuous(limits = c(min(log(sites_center$NumSpiders)) - 2, max(log(sites_center$NumSpiders)) + 0.1 * diff(range(log(sites_center$NumSpiders))))) +  
+  scale_y_continuous(limits = c(-2, 3.5), breaks = c(-2, -1, 0, 1, 2, 3)) +  
   theme_classic() +
@@
   theme(axis.text.y = element_text(colour = "black", size = 10)) +
-  theme(axis.text.x = element_blank(), 
-        axis.title.x = element_blank(),
-        axis.text.y = element_blank(),
-        axis.title.y = element_blank()) +
-  annotate(geom = "text", x = min((predicted.distance$log_tdh)) + diff(range((predicted.distance$log_tdh)))/2, y = max(log(sites_center$NumSpiders)), label = "***", color = "black", size = 4)
+  theme(axis.title.x = element_blank(), 
+        axis.title.y = element_blank(), 
+        axis.text.y = element_blank()) + 
+#  theme(axis.text.x = element_blank()) +
+#  annotate(geom = "text", x = min((predicted.distance$log_tdh)) + diff(range((predicted.distance$log_tdh)))/2, y = max(log(sites_center$NumSpiders)), label = "***", color = "black", size = 4) 
+  annotate(geom = "text", x = min((predicted.distance$log_tdh)) + diff(range((predicted.distance$log_tdh)))/2, y = 3.5, label = "***", color = "black", size = 4)
 
@@
               alpha = 0.25) +
-  scale_y_continuous(limits = c(min(log(sites_center$NumSpiders)) - 1, max(log(sites_center$NumSpiders)) + 0.1 * diff(range(log(sites_center$NumSpiders))))) +  
+#  scale_y_continuous(limits = c(min(log(sites_center$NumSpiders)) - 1, max(log(sites_center$NumSpiders)) + 0.1 * diff(range(log(sites_center$NumSpiders))))) +  
+  scale_y_continuous(limits = c(-2, 3.5), breaks = c(-2, -1, 0, 1, 2, 3)) +  
   theme_classic() +
@@
   theme(axis.text.y = element_text(colour = "black", size = 10)) +
-  theme(axis.text.x = element_blank(), 
-        axis.title.x = element_blank(),
-        axis.text.y = element_blank(),
-        axis.title.y = element_blank()) +
-  annotate(geom = "text", x = min((predicted.distance$road_length_m)) + diff(range((predicted.distance$road_length_m)))/2, y = max(log(sites_center$NumSpiders)), label = "***", color = "black", size = 4)
+  theme(axis.title.x = element_blank(), 
+        axis.title.y = element_blank(), 
+        axis.text.y = element_blank()) + 
+#  theme(axis.text.x = element_blank()) +
+#  annotate(geom = "text", x = min((predicted.distance$road_length_m)) + diff(range((predicted.distance$road_length_m)))/2, y = max(log(sites_center$NumSpiders)), label = "***", color = "black", size = 4)
+  annotate(geom = "text", x = min((predicted.distance$road_length_m)) + diff(range((predicted.distance$road_length_m)))/2, y = 3.5, label = "***", color = "black", size = 4)
 
@@
               alpha = 0.25) +
-  scale_y_continuous(limits = c(min(log(near$RetreatDist)), max(log(near$RetreatDist)) + 0.1 * diff(range(log(near$RetreatDist))))) +  
+#  scale_y_continuous(limits = c(min(log(near$RetreatDist)), max(log(near$RetreatDist)) + 0.1 * diff(range(log(near$RetreatDist))))) +  
+  scale_y_continuous(limits = c(2, 7), breaks = c(2, 3, 4, 5, 6, 7)) +  
   theme_classic() +
@@
   theme(axis.text.y = element_text(colour = "black", size = 10)) +
-  theme(axis.text.x = element_blank(), 
-        axis.title.x = element_blank(),
-        axis.text.y = element_blank(),
-        axis.title.y = element_blank()) +
-  annotate(geom = "text", x = min(predicted.distance$log_TotalSub) + diff(range(predicted.distance$log_TotalSub))/2, y = max(log(near$RetreatDist)), label = "***", color = "black", size = 4)
+  theme(axis.title.x = element_blank(), 
+        axis.title.y = element_blank(),
+        axis.text.x = element_blank()) + 
+#  theme(axis.text.y = element_blank()) +
+#  annotate(geom = "text", x = min(predicted.distance$log_TotalSub) + diff(range(predicted.distance$log_TotalSub))/2, y = max(log(near$RetreatDist)), label = "***", color = "black", size = 4)
+  annotate(geom = "text", x = min(predicted.distance$log_TotalSub) + diff(range(predicted.distance$log_TotalSub))/2, y = 6.8, label = "***", color = "black", size = 4)
 
@@
               alpha = 0.25) +
-  scale_y_continuous(limits = c(min(log(near$RetreatDist)), max(log(near$RetreatDist)) + 0.1 * diff(range(log(near$RetreatDist))))) +  
+#  scale_y_continuous(limits = c(min(log(near$RetreatDist)), max(log(near$RetreatDist)) + 0.1 * diff(range(log(near$RetreatDist))))) + 
+  scale_y_continuous(limits = c(2, 7), breaks = c(2, 3, 4, 5, 6, 7)) +  
   theme_classic() +
@@
   theme(axis.text.y = element_text(colour = "black", size = 10)) +
-  theme(axis.text.x = element_blank(), 
-        axis.title.x = element_blank(),
+  theme(axis.title.x = element_blank(), 
+        axis.title.y = element_blank(), 
         axis.text.y = element_blank(),
-        axis.title.y = element_blank()) +
-  annotate(geom = "text", x = min((predicted.distance$log_tdr)) + diff(range((predicted.distance$log_tdr)))/2, y = max(log(near$RetreatDist)), label = "***", color = "black", size = 4)
+        axis.text.x = element_blank()) + 
+#  annotate(geom = "text", x = min((predicted.distance$log_tdr)) + diff(range((predicted.distance$log_tdr)))/2, y = max(log(near$RetreatDist)), label = "***", color = "black", size = 4)
+    annotate(geom = "text", x = min((predicted.distance$log_tdr)) + diff(range((predicted.distance$log_tdr)))/2, y =6.8, label = "***", color = "black", size = 4)
 
@@
               alpha = 0.25) +
-  scale_y_continuous(limits = c(min(log(near_forest$RetreatDist)), max(log(near_forest$RetreatDist)) + 0.1 * diff(range(log(near_forest$RetreatDist))))) +  
+#  scale_y_continuous(limits = c(min(log(near_forest$RetreatDist)), max(log(near_forest$RetreatDist)) + 0.1 * diff(range(log(near_forest$RetreatDist))))) +  
+  scale_y_continuous(limits = c(4, 7), breaks = c(4, 5, 6, 7)) +  
   theme_classic() +
@@
   theme(axis.text.y = element_text(colour = "black", size = 10)) +
-  theme(axis.text.x = element_blank(), 
-        axis.title.x = element_blank(),
-        axis.text.y = element_blank(),
+  theme(axis.title.x = element_blank(), 
         axis.title.y = element_blank()) + 
-  annotate(geom = "text", x = min(predicted.distance$log_TotalSub) + diff(range(predicted.distance$log_TotalSub))/2, y = max(log(near_forest$RetreatDist)), label = "***", color = "black", size = 4)
+#  theme(axis.text.x = element_blank(), 
+#        axis.text.y = element_blank()) +
+#  annotate(geom = "text", x = min(predicted.distance$log_TotalSub) + diff(range(predicted.distance$log_TotalSub))/2, y = max(log(near_forest$RetreatDist)), label = "***", color = "black", size = 4)
+  annotate(geom = "text", x = min(predicted.distance$log_TotalSub) + diff(range(predicted.distance$log_TotalSub))/2, y = 7, label = "***", color = "black", size = 4)
 
@@
   theme(axis.text.y = element_text(colour = "black", size = 10)) +
-  theme(axis.text.x = element_blank(), 
-        axis.title.x = element_blank(),
-        axis.text.y = element_blank(),
-        axis.title.y = element_blank()) +
-  annotate(geom = "text", x = min((predicted.distance$log_tdh)) + diff(range((predicted.distance$log_tdh)))/2, y = max(log(near_forest$RetreatDist)), label = "***", color = "black", size = 4)
+  theme(axis.title.x = element_blank(), 
+        axis.title.y = element_blank(), 
+        axis.text.y = element_blank()) + 
+#  theme(axis.text.x = element_blank()) +
+#  annotate(geom = "text", x = min((predicted.distance$log_tdh)) + diff(range((predicted.distance$log_tdh)))/2, y = max(log(near_forest$RetreatDist)), label = "***", color = "black", size = 4)
+  annotate(geom = "text", x = min((predicted.distance$log_tdh)) + diff(range((predicted.distance$log_tdh)))/2, y = 7, label = "***", color = "black", size = 4)
 
@@
   theme(axis.text.y = element_text(colour = "black", size = 10)) +
-  theme(axis.text.x = element_blank(), 
-        axis.title.x = element_blank(),
-        axis.text.y = element_blank(),
-        axis.title.y = element_blank()) +
-  annotate(geom = "text", x = min((predicted.distance$log_tdr)) + diff(range((predicted.distance$log_tdr)))/2, y = max(log(near_forest$RetreatDist)), label = "***", color = "black", size = 4)
+  theme(axis.title.x = element_blank(), 
+        axis.title.y = element_blank(), 
+        axis.text.y = element_blank()) + 
+#  theme(axis.text.x = element_blank()) +
+#  annotate(geom = "text", x = min((predicted.distance$log_tdr)) + diff(range((predicted.distance$log_tdr)))/2, y = max(log(near_forest$RetreatDist)), label = "***", color = "black", size = 4)
+  annotate(geom = "text", x = min((predicted.distance$log_tdr)) + diff(range((predicted.distance$log_tdr)))/2, y = 7, label = "***", color = "black", size = 4)
 
@@
   theme(axis.text.y = element_text(colour = "black", size = 10)) +
-  theme(axis.text.x = element_blank(), 
-        axis.title.x = element_blank(),
-        axis.text.y = element_blank(),
-        axis.title.y = element_blank()) +
-  annotate(geom = "text", x = min((predicted.distance$tree100m)) + diff(range((predicted.distance$tree100m)))/2, y = max(log(near_forest$RetreatDist)), label = "***", color = "black", size = 4)
+  theme(axis.title.x = element_blank(), 
+        axis.title.y = element_blank(), 
+        axis.text.y = element_blank()) + 
+#  theme(axis.text.x = element_blank()) +
+#  annotate(geom = "text", x = min((predicted.distance$tree100m)) + diff(range((predicted.distance$tree100m)))/2, y = max(log(near_forest$RetreatDist)), label = "***", color = "black", size = 4)
+  annotate(geom = "text", x = min((predicted.distance$tree100m)) + diff(range((predicted.distance$tree100m)))/2, y = 7, label = "***", color = "black", size = 4)
 
@@
               alpha = 0.25) +
-  scale_y_continuous(limits = c(min(log(near_center$RetreatDist)), max(log(near_center$RetreatDist)) + 0.1 * diff(range(log(near_center$RetreatDist))))) +  
+#  scale_y_continuous(limits = c(min(log(near_center$RetreatDist)), max(log(near_center$RetreatDist)) + 0.1 * diff(range(log(near_center$RetreatDist))))) +  
+  scale_y_continuous(limits = c(2, 7), breaks = c(2, 3, 4, 5, 6, 7)) +  
   theme_classic() +
@@
   theme(axis.text.y = element_text(colour = "black", size = 10)) +
-  theme(axis.text.x = element_blank(), 
-        axis.title.x = element_blank(),
-        axis.text.y = element_blank(),
+  theme(axis.title.x = element_blank(), 
         axis.title.y = element_blank()) + 
-  annotate(geom = "text", x = min(predicted.distance$log_TotalSub) + diff(range(predicted.distance$log_TotalSub))/2, y = max(log(near_center$RetreatDist)), label = "***", color = "black", size = 4)
+#  theme(axis.text.x = element_blank(), 
+#        axis.text.y = element_blank()) +
+#  annotate(geom = "text", x = min(predicted.distance$log_TotalSub) + diff(range(predicted.distance$log_TotalSub))/2, y = max(log(near_center$RetreatDist)), label = "***", color = "black", size = 4)
+  annotate(geom = "text", x = min(predicted.distance$log_TotalSub) + diff(range(predicted.distance$log_TotalSub))/2, y = 7, label = "***", color = "black", size = 4)
 
@@
   theme(axis.text.y = element_text(colour = "black", size = 10)) +
-  theme(axis.text.x = element_blank(), 
-        axis.title.x = element_blank(),
-        axis.text.y = element_blank(),
-        axis.title.y = element_blank()) +
-  annotate(geom = "text", x = min((predicted.distance$spec_rad)) + diff(range((predicted.distance$spec_rad)))/2, y = max(log(near_center$RetreatDist)), label = "***", color = "black", size = 4)
+  theme(axis.title.x = element_blank(), 
+        axis.title.y = element_blank(), 
+        axis.text.y = element_blank()) + 
+#  theme(axis.text.x = element_blank()) +
+#  annotate(geom = "text", x = min((predicted.distance$spec_rad)) + diff(range((predicted.distance$spec_rad)))/2, y = max(log(near_center$RetreatDist)), label = "***", color = "black", size = 4)
+  annotate(geom = "text", x = min((predicted.distance$spec_rad)) + diff(range((predicted.distance$spec_rad)))/2, y = 7, label = "***", color = "black", size = 4)
 
@@
   theme(axis.text.y = element_text(colour = "black", size = 10)) +
-  theme(axis.text.x = element_blank(), 
-        axis.title.x = element_blank(),
-        axis.text.y = element_blank(),
-        axis.title.y = element_blank()) +
-  annotate(geom = "text", x = min((predicted.distance$road_length_m)) + diff(range((predicted.distance$road_length_m)))/2, y = max(log(near_center$RetreatDist)), label = "***", color = "black", size = 4)
+  theme(axis.title.x = element_blank(), 
+        axis.title.y = element_blank(), 
+        axis.text.y = element_blank()) + 
+#  theme(axis.text.x = element_blank()) +
+#  annotate(geom = "text", x = min((predicted.distance$road_length_m)) + diff(range((predicted.distance$road_length_m)))/2, y = max(log(near_center$RetreatDist)), label = "***", color = "black", size = 4)
+  annotate(geom = "text", x = min((predicted.distance$road_length_m)) + diff(range((predicted.distance$road_length_m)))/2, y = 7, label = "***", color = "black", size = 4)
 
@@
               alpha = 0.25) +
-  scale_y_continuous(limits = c(min(log(webs$RetreatHeight)), max(log(webs$RetreatHeight)) + 0.1 * diff(range(log(webs$RetreatHeight))))) +  
+#  scale_y_continuous(limits = c(min(log(webs$RetreatHeight)), max(log(webs$RetreatHeight)) + 0.1 * diff(range(log(webs$RetreatHeight))))) +  
+  scale_y_continuous(limits = c(-2.5, 6), breaks = c(-2, 0, 2, 4, 6)) +  
   theme_classic() +
@@
   theme(axis.text.y = element_text(colour = "black", size = 10)) +
-  theme(axis.text.x = element_blank(), 
-        axis.title.x = element_blank(),
-        axis.text.y = element_blank(),
+  theme(axis.title.x = element_blank(), 
         axis.title.y = element_blank()) + 
-  annotate(geom = "text", x = min(predictions$log_TotalSub) + diff(range(predictions$log_TotalSub))/2, y = max(log(webs$RetreatHeight)), label = "**", color = "black", size = 4)
+#  theme(axis.text.x = element_blank(), 
+#        axis.text.y = element_blank()) +
+#  annotate(geom = "text", x = min(predictions$log_TotalSub) + diff(range(predictions$log_TotalSub))/2, y = max(log(webs$RetreatHeight)), label = "**", color = "black", size = 4)
+    annotate(geom = "text", x = min(predictions$log_TotalSub) + diff(range(predictions$log_TotalSub))/2, y = 5.8, label = "**", color = "black", size = 4)
 
@@
   theme(axis.text.y = element_text(colour = "black", size = 10)) +
-  theme(axis.text.x = element_blank(), 
-        axis.title.x = element_blank(),
-        axis.text.y = element_blank(),
-        axis.title.y = element_blank()) +
-  annotate(geom = "text", x = min(predictions$log_tdr) + diff(range(predictions$log_tdr))/2, y = max(log(webs$RetreatHeight)), label = "N. S.", color = "black", size = 4)
+  theme(axis.title.x = element_blank(), 
+        axis.title.y = element_blank(), 
+        axis.text.y = element_blank()) + 
+#  theme(axis.text.x = element_blank()) +
+#  annotate(geom = "text", x = min(predictions$log_tdr) + diff(range(predictions$log_tdr))/2, y = max(log(webs$RetreatHeight)), label = "N. S.", color = "black", size = 4)
+    annotate(geom = "text", x = min(predictions$log_tdr) + diff(range(predictions$log_tdr))/2, y = 5.8, label = "N. S.", color = "black", size = 4)
 
@@
   theme(axis.text.y = element_text(colour = "black", size = 10)) +
-  theme(axis.text.x = element_blank(), 
-        axis.title.x = element_blank(),
-        axis.text.y = element_blank(),
+  theme(axis.title.x = element_blank(), 
         axis.title.y = element_blank()) + 
+#  theme(axis.text.x = element_blank(), 
+#        axis.text.y = element_blank()) +
   annotate(geom = "text", x = min(log(predictions$tree100m_frac)) + diff(range(log(predictions$tree100m_frac)))/2, y = max(log(webs_forest$RetreatHeight)), label = "**", color = "black", size = 4)
@@
   theme(axis.text.y = element_text(colour = "black", size = 10)) +
-  theme(axis.text.x = element_blank(), 
-        axis.title.x = element_blank(),
-        axis.text.y = element_blank(),
+  theme(axis.title.x = element_blank(), 
         axis.title.y = element_blank()) + 
+#  theme(axis.text.x = element_blank(), 
+#        axis.text.y = element_blank()) +
   annotate(geom = "text", x = min((predictions$log_TotalSub)) + diff(range((predictions$log_TotalSub)))/2, y = max(log(webs_forest$RetreatHeight)), label = "N.S.", color = "black", size = 4)
@@
 ```
+
+## Lit Review Table
+
+```{r references}
+mech <- c("Mechanisms of Aggregation", "Interspecific and Intraspecific Interactions", "Interspecific and Intraspecific Interactions", "Interspecific and Intraspecific Interactions", "Interspecific and Intraspecific Interactions", "Interspecific and Intraspecific Interactions", "Interspecific and Intraspecific Interactions", "Environmental Factors", "Environmental Factors", "Environmental Factors", "Dispersal", "Dispersal")
+
+mech2 <- c("Mechanisms of Aggregation", "Conspecific Attraction", "Lekking for Mates", "Heterospecific Attraction", "Predation Release", "Prey Chemical Cues", "Prey Abundance", "Light Cues", "Plant Cover", "Limited Shelter from Thermal Stress", "Limited Dispersal via Flooding", "Ontogenesis")
+
+rel <- c("Relationship with Spider Aggregation", "Following conspecific silk increased aggregation tendencies", "Larger female aggregations attract more males", "Spiders aggregate around heterospecific spiders", "Predation reduced when aggregated", "Spiders preferred areas with prey chemical cues", "Spider aggregations were denser in areas with more available prey", "Spiders were attracted to and gathered in areas with artificial light", "Spiders aggregated in an area dominated by cover of a specific plant", "Aggregations on  limited protective structures against high temperatures", "Flooding restricted ballooning to escape", "Temporary aggregation of sibblings following hatching from egg sac")
+
+urban <- c("Urban Habitat", "No", "No", "No", "No", "Yes", "Yes", "Yes", "No", "No", "No", "No")
+
+ref <- c("References", "Fitzgerald and Ives 2017; Hodge and Storfer-Isser 1997; Jeanson et al.
+2004", "Kasumovic and Jordan 2013; Lloyd and Elgar 1997", "Henaut and Machkour-M'Rabet 2010; Jeanson et al.
+2004", "Feree et al.
+2018; Lloyd and Elgar 1997", "Johnson et al.
+2011", "Trubl et al.
+2012", "Czaczkes et al.
+2018; Mammola et al.
+2018", "Petillon et al.
+2012", "Riechert 1974", "Piacentini et al.
+2021", "Marshall 1995; Mougenot et al.
+2012; Riechert 1974")
+
+references <- data.frame(mech, mech2, rel, urban, ref)
+
+flextable(references[ ,1:5]) %>% 
+  delete_part(part = "header") %>% 
+  autofit() %>% 
+  hline(i = c("1", "7", "10", "12"), part = "body", border = officer::fp_border(width = 2)) %>% 
+    hline(i = c("2", "3", "4", "5", "6", "8", "9", "11"), part = "body", border = officer::fp_border(width = 1)) %>% 
+  merge_h(part = "body") %>% 
+  merge_v(j = 1, part = "body") %>% 
+  bold(i = 1, bold = TRUE, part = "body") %>% 
+  fontsize(size = 14, part = "all") %>% 
+  align(align = "center", part = "all") %>% 
+  set_caption("") %>% 
+  save_as_image(path = here::here("manuscript/figures/references.png"))
+```

### 2022-12-05 manuscript/manuscript.Rmd
Some more manuscript edits

@@
 Interactions within species (between conspecific competitors and mates) and across species (with predators, prey, and heterospecific competitors) further shape animal spatial patterns [@anderson_2017; @boulangeat_2012].
-While dispersal capacity can determine a species’ range, barriers can limit dispersal and prevent animals from reaching suitable habitat  [@boulangeat_2012; @amundrud_2018].
+While dispersal capacity can determine a species’ range, barriers can limit dispersal and prevent animals from reaching suitable habitats  [@boulangeat_2012; @amundrud_2018].
 
@@
 
-Due to intense habitat disturbance and dense human presence, urbanization has drastically modified the land [@alberti_2020]; @mcdonnell_pickett_1990; @pickett_2001) which has altered environmental conditions, community dynamics, and dispersal capability as a result [@piano_2020].
+Due to intense habitat disturbance and dense human presence, urbanization has drastically modified the land [@alberti_2020; @mcdonnell_pickett_1990; @pickett_2001] which has altered environmental conditions, community dynamics, and dispersal capability as a result [@piano_2020].
 As these factors determine animal spatial patterns, it is likely that urbanized landscapes have changed how animals spatially distribute themselves, in turn.
 Typically, city tree cover is reduced in areas where the potential natural vegetation is forested [@nowak_1996] and greater in areas with prairie, grassland, and desert origins [@mckinney_2006].
-Urban environments are additionally characterized by decreased biodiversity [@mckinney_2002] and increased impervious cover [compacted soil from buildings and pavement; @nowak_greenfield_2020] and habitat patchiness [@cadenasso_2007].
+Urban environments are additionally characterized by decreased biodiversity [@mckinney_2002] and increased impervious cover (compacted soil from buildings and pavement; @nowak_greenfield_2020) and habitat patchiness [@cadenasso_2007].
 These conditions can contribute to changes in climatic conditions, such as when impervious cover traps heat and increases the average temperatures in cities compared to surrounding areas –- *i.e.*, the Urban Heat Island Effect [@morabito_2021].
@@
 
-**This paragraph needs citations, but it will be easier after finishing the aggregation table**
-The mechanisms behind solitary spider aggregations are unclear despite reports of aggregations of spiders in urban habitats, such as web-builders *Lactrodectus hesperus* and *Brigittea civica* [@johnson_et_al_2012; @mammola_et_al_2018].
+The mechanisms behind solitary spider aggregations - especially in urban habitats - are unclear despite reports of aggregations of spiders in urban habitats, such as web-builders *Lactrodectus hesperus* and *Brigittea civica* [@johnson_et_al_2012; @mammola_et_al_2018].
 This gap in knowledge is concerning as urban spider aggregations can have medical and aesthetic consequences, and implications for urban pest control services.
-Prey abundance seems to be an important driver because it has been shown to be directly [] and indirectly [] related to urban spider aggregations, the latter of which is shown through investigations as light sources at night as cues of prey aggregations [].
+Prey abundance seems to be an important driver because it has been shown to be directly and indirectly (for example, light sources at night as cues of prey clustering) related to urban spider aggregations (Table 1).
 Random spacing in solitary spiders is typically maintained by territoriality and aggression over resources like prey and mates [@riechert_1974b].
-Occassionally, conditions arise that allow solitary spiders to become more tolerant of neighbors, and understanding these contexts can help uncover the mechanisms of aggregative behavior.
-Aggregations have been shown to form as a result of dispersal limitations [], predator release [], lekking reproductive strategies [], plant structure [], and environmental stressors [].
-The degree of aggregation in spiders can also change over time, often times more intense during juvenile stages when dispersal is limited, spreading over time as subadults and adults become more territorial [@riechert_1974b].
-Studies on mechanisms of aggregations in spiders are presented and discussed in Table 1.
+Occasionally, conditions arise that allow solitary spiders to become more tolerant of neighbors, and understanding these contexts can help uncover the mechanisms of aggregative behavior.
+Aggregations have been shown to form as a result of inter- and intraspecific interactions, environmental factors, and dispersal limitations (Table 1).
 
@@
 In particular, we use *A.
-pennsylvanica* to address three questions: (*i*) How does web abundance, aggregation, and position vary between two urban habitats?
+pennsylvanica* to address three questions: (*i*) How do web abundance, aggregation, and position vary between two urban habitats?
 (*ii*) How do environmental conditions vary between these two urban habitats?
@@
 
-Where *i*is the value indicated by the pixel (with range b-a) and *$x_i$* is the percent of the habitat covered by the *$i^(th)$* pixel category.
-These data are presented in Table 1 and summarized below.
+Where *i* is the value indicated by the pixel (with range b-a) and *$x_i$* is the percent of the habitat covered by the *$i^(th)$* pixel category.
+These data are presented in Table 2 and summarized below.
 
@@
 UNL City Campus is adjacent to, and just north of, downtown Lincoln (253.73 $km^2$).
-Impervious cover -- in the form of buildings and pavement -- dominates the land on UNL City Campus, considerably more than impervious cover across the city of Lincoln (Table 1, Fig.
+Impervious cover -- in the form of buildings and pavement -- dominates the land on UNL City Campus, considerably more than impervious cover across the city of Lincoln (Table 2, Fig.
 S3).
 Lawns are maintained by frequent mowing, and gardens and landscaping are regularly pruned.
-Tree cover on UNL City Campus and in Lincoln overall is low (< 6%, Table 1, Fig.
+Tree cover on UNL City Campus and in Lincoln overall is low (< 6%, Table 2, Fig.
 S4).
 There was heavy foot traffic from UNL's 20,286 undergraduates enrolled in the 2020-2021 academic year, 37% of which lived in college-owned, -operated, or -affiliated housing [@iea_2021].
-The entire area of UNL City Campus was categorized as urban with varying intensity (Table 1, Fig.
+The entire area of UNL City Campus was categorized as urban with varying intensity (Table 2, Fig.
 2).
@@
 S5) and artificial light at night radiance (Fig.
-S6), even above that of Lincoln as a whole (Table 1).
+S6), even above that of Lincoln as a whole (Table 2).
 Thus, we designated UNL City Campus as an *urban center* and refer to it as such hereafter.
@@
 S1) starting about 3.58 km southwest of UNL City Campus and downtown Lincoln, extending south and along Lincoln city limits.
-We found about two-fifths of Wilderness Park to be shrouded in trees (Table 1, Fig.
-S4), with less than 2% of its land imperviously covered (Table 1, Fig.
+We found about two-fifths of Wilderness Park to be shrouded in trees (Table 2, Fig.
+S4), with less than 2% of its land imperviously covered (Table 2, Fig.
 S2).
-Over three quarters of Wilderness Park is categorized as forested land with only 5.44% labeled as urban (Table 1, Fig.
+Over three quarters of Wilderness Park is categorized as forested land with only 5.44% labeled as urban (Table 2, Fig.
 2).
@@
 S5) and artificial light at night radiance (Fig.
-S6) than the city of Lincoln (Table 1).
+S6) than the city of Lincoln (Table 2).
 Due to its proximity to Lincoln city limits, we designate Wilderness Park as an *urban forest* and refer to it as such hereafter.
@@
 For the first set of models, we focused on whether web abundance, aggregation, and position differ between the two habitats (the urban center and urban forest).
-We used Poisson generalized linear models [*stats* package in R, @stats] for the response variables: search distance, number of webs, and number of spiders.
+We used Poisson generalized linear models [*stats* package in R, @r] for the response variables: search distance, number of webs, and number of spiders.
 We used Poisson generalized linear mixed effect models [*lme4* package in R, @lme4] with site as a random effect for the response variables: nearest neighbor distance and web height.
@@
 Since we found significant variation in distribution measures between habitats, we wanted to explore potential environmental mechanisms of such variation within the test habitats.
-We first tested whether the nine environmental predictors varied by habitat (Table 2).
+We first tested whether the nine environmental predictors varied by habitat (Table 3).
 Each predictor was tested by habitat using Poisson generalized linear models as the predictors were positive and not normally distributed.
-Each environmental predictor significantly varied by habitat (Table 2), so we subset the data by habitat.
+Each environmental predictor significantly varied by habitat (Table 3), so we subset the data by habitat.
 Among the environmental predictors, we removed variables that were highly correlated (cutoff of 0.6) using the *caret* package in R [@caret].
@@
 We used the habitat subsets and the selected environmental predictor variables to assess correlations between predictor variables and spatial pattern measures.
-In the global models, we included the predictors that remained after removal for collinearity (no interactions) with the response variables: web and spider abundance, nearest neighbor distance, and web height for the complete data and habitat subsets.
+In the global models, we included the predictors (without interactions) that remained after removal for collinearity with the response variables: web and spider abundance, nearest neighbor distance, and web height for the complete data and habitat subsets.
 We assessed nearest neighbor distance and excluded second nearest neighbor distance because both were significantly different between habitats.
@@
 
-All environmental predictors assessed within a 100-meter radius of the focal web varied by habitat (Table 2).
+All environmental predictors assessed within a 100-meter radius of the focal web varied by habitat (Table 3).
 Site tree cover was lower in the urban center than the urban forest with five urban center sites with zero tree cover ($z_21$ = -14.50, *P* < 0.001).
@@
 
-To explore potential mechanisms of variation in spatial patterns, we looked for correlations between response variables (number of webs, number of spiders, nearest neighbor distance, and web height) and environmental predictors overall and within each habitat (Table 3, Table S2, Fig.
+To explore potential mechanisms of variation in spatial patterns, we looked for correlations between response variables (number of webs, number of spiders, nearest neighbor distance, and web height) and environmental predictors overall and within each habitat (Table 4, Table S2, Fig.
 4-5).
 
-The top models for the number of webs and the number of spiders yielded similar results (Table 3, Fig.
+The top models for the number of webs and the number of spiders yielded similar results (Table 4, Fig.
 4).
-For both measures of abundance, the urban forest subset retained no predictors (Table 3) while the urban center showed a decrease in abundance with increasing plant species richness, patch area, highway disturbance, and road length (Table 3, Fig.
+For both measures of abundance, the urban forest subset retained no predictors (Table 4) while the urban center showed a decrease in abundance with increasing plant species richness, patch area, highway disturbance, and road length (Table 4, Fig.
 4).
 The model average for the number of webs subset by urban center suggested similar results (Table S2).
-Plant species richness and highway disturbance both had a negative relationship with abundance measures for the overall data set (Table 3, Fig.
+Plant species richness and highway disturbance both had a negative relationship with abundance measures for the overall data set (Table 4, Fig.
 S11).
-Interestingly, the top model of web abundance retained road disturbance and suggested a positive relationship overall (Table 3, Fig.
+Interestingly, the top model of web abundance retained road disturbance and suggested a positive relationship overall (Table 4, Fig.
 S11).
 
-Overall, spiders are closer together when plant species richness is low and when road disturbance is high (Table 3, Fig.
+Overall, spiders are closer together when plant species richness is low and when road disturbance is high (Table 4, Fig.
 S11).
-On the other hand, less tree cover, lower road and highway disturbance, and greater plant species richness are associated with nearness in the urban forest (Table 3, Fig.
+On the other hand, less tree cover, lower road and highway disturbance, and greater plant species richness are associated with nearness in the urban forest (Table 4, Fig.
 5), however, this model was a poor fit ($R^2$ = 0.037).
-Urban center spiders are more aggregated where plant species richness, spectral radiance, and road length are high (Table 3, Fig.
+Urban center spiders are more aggregated where plant species richness, spectral radiance, and road length are high (Table 4, Fig.
 5).
@@
 
-Further, webs are built higher overall when the number of plant species is higher (Table 3, Fig.
+Further, webs are built higher overall when the number of plant species is higher (Table 4, Fig.
 S11).
-A trend also suggests that lower webs are associated with higher road disturbance, although this result is not significant (Table 3, Fig.
+A trend also suggests that lower webs are associated with higher road disturbance, although this result is not significant (Table 4, Fig.
 S11).
-In the urban forest, web height is positively related to tree cover (Table 3).
-While plant species richness was included in the top model, it did not vary by web height in the urban center (Table 3).
+In the urban forest, web height is positively related to tree cover (Table 4).
+While plant species richness was included in the top model, it did not vary by web height in the urban center (Table 4).
 We see similar results from the model averages for web height (Table S2).
@@
 
-**need to talk more about predator and competitor abundance? - I think not, mention in next paragraph.**
-
 The environmental conditions assessed here only correlated with web and spider abundance in the urban center, with no strong environmental effects on abundance in the urban forest.
@@
 
-Since different plants transmit vibrations differently [CITE], selective spiders in urban habitats may choose plants web substrates that reduce vibratory noise.
+Since different plants transmit vibrations differently [@cocroft_et_al_2006], selective spiders in urban habitats may choose plants as web substrates that reduce vibratory noise, either human-caused or natural.
 Our results show that spiders are more abundant when plant species richness is lower.
-The urban center sites were covered in grass lawns and managed landscaping that usually had few plant species present.
+The urban center sites were covered in grass lawns and managed landscaping that usually had few plant species present, but in high abundance.
 Sites with lower plant diversity may have few plant species that are highly preferred, leading to higher spider abundance.
-Greater plant diversity has been found to have both positive and negative affects on spider abundance, and some suggest that plant community composition tends to play a vital role [CITE].
+Research has shown mixed but often positive effects of plant diversity on spider abundance [@malumbres_et_al_2013; @koricheva_et_al_2000], suggesting that plant community composition may play a vital, yet context-specific role.
 To better understand the role that plant species play in abundance would require comparing plant communities between patches used by spiders versus those devoid of spiders.
-Additionally, smaller patches were associated with higher spider abundance.
-While arthropods overall tend to decrease in abundance as smaller patch sizes, habitat generalists and edge specialists can be found at greater abundance in smaller patches [CITE].
+We additionally found that smaller patches were associated with higher spider abundance.
+While arthropods overall tend to decrease in abundance as smaller patch sizes, habitat generalists and edge specialists can be found at greater abundance in smaller patches [@martinson_fagan_2014].
 
@@
 Both the first and second nearest neighbor webs to the focal web were closer in the urban center than the urban forest.
-Multiple reports have found spider aggregations in urban habitats [], especially when related to the abundance of prey.
-Territoriality over mates and prey resources often drives random spacing of solitary species [], but aggregations can form when abundant resources allow for increased tolerance of neighbors [].
-Light at night in cities attracts insects creating pockets of increased prey abundance for spiders.
-As such, spiders have been found to aggregate under light sources.
+Multiple reports have found spider aggregations in urban habitats [@trubl_2012; @mammola_et_al_2018], often related directly or indirectly to the abundance of prey.
+Territoriality, especially over prey resources, often drives regular (and non-random) spacing of solitary species [@riechert_1974b], but aggregations can form when abundant resources allow for increased tolerance of neighbors [@gillespie_1987].
+Light at night in cities attracts insects creating pockets of increased prey abundance for spiders that may lead to spiders aggregating under such light sources [@davies_et_al_2012].
 Although we did not measure microhabitat levels of light at night or prey abundance, *A.
@@
 We found significant relationships between environmental predictors and nearest neighbor distance in both urban habitats.
-Urban center and forest spiders responded differently in aggregative behavior in response to vibratory noise measures -- urban forest spiders aggregated at lower road and highway disturbance and urban center spiders aggregated more there was more road within 100 meters of the focal web, but did not vary by road or highway disturbance.
-As a result, noise might affect urban forest spiders more than spiders reared in or that are decendents from the urban center where noise is greater.
-Spiders in the urban forest may exhibit increased nearest to neighbors if higher quality web locations are those that are further from road disturbance.
-Many spiders are thought to be plastic in the structure and tuning of their webs, and urban exploiters are often fast to adjust to changing conditions, so spiders in the urban center might be able to better tune their webs to decrease vibrations, although this hypothesis requires further testing.
+Urban center and forest spiders responded differently in aggregative behavior in response to traffic measures that may reflect vibratory noise -- neighboring urban forest spiders were closer at lower road and highway disturbance and urban center spiders aggregated more when there was more road within 100 meters of the focal web, but did not vary by road or highway disturbance.
+Perhaps noise negatively affects urban forest spiders, encouraging spiders to inhabit areas further from noise sources and reducing space between neighbors.
+more than spiders reared in or descended from the urban center where noise is greater.
+Many spiders are thought to be plastic in the structure and tuning of their webs [@mortimer_2016; @blamires_2010], and urban exploiters are often fast to adjust to changing conditions [@kralj_2017], so spiders reared in or descended from spiders in the urban center might be better able to tune their webs to decrease vibrations, although this hypothesis requires further testing.
 It will also be important to differentiate whether these differences in behavior between environments is based on developmental exposure, behavioral plasticity, or genetic differentiation.
@@
 We speculate that greater aggregation on more diverse plant communities may suggest that *A.
-pennsylvanica* prefers a certain plant or type of plant, especially in urban centers where similar plants are often clumped in space for landscaping.
+pennsylvanica* prefers a certain plant or type of plant, especially in the urban center where we observed similar plants clumped in space.
 In the urban forest, we also found nearer neighbors under less tree cover.
-A study that measured invertebrate abundance after manipulating tree cover found that newly formed tree gaps have greater vegetation height and coverage and increased soil moisture and temperature, all of which led to an overall increase in invertebrate abundance -- a result that had been corroborated by other studies.
+A study that measured invertebrate abundance after manipulating tree cover found that newly formed tree gaps have greater vegetation height and coverage and increased soil moisture and temperature, all of which led to an overall increase in invertebrate abundance [@perry_2018].
+Similar results have been found with spider communities in particular [@vcernecka_2020].
 Since spider aggregations tend to occur where prey abundance is higher, we might predict that lower tree cover might indirectly increase spider aggregation through an increase in prey abundance.
 Lastly, spiders in the urban center were more aggregated at sites with higher spectral radiance (a measure of surface temperature).
-Urban centers tend to be warmer on average compared to surrounding areas due to heat trapping via pavement in a phenomenon called the Urban Heat Island Effect.
-Aggregation formation in warmer sites could be the result of limited shelter from excessive heat or from a preference for warmer areas.
+Urban centers tend to be warmer on average compared to surrounding areas due to heat trapping via pavement in a phenomenon called the Urban Heat Island Effect [@johnson_et_al_2020].
+Aggregation formation in warmer sites could be the result of preference for or acclimation to warmer areas [@meineke_et_al_2013] or perhaps aggregation occurs at limited thermal refuges [@riechert_1974b].
 
@@
 
-We found that the height of the webs built by spiders in the urban center were built lower than webs in the urban forest, and this result was independent of the height of the substrate.
+We found that the webs of urban center spiders were built lower than webs in the urban forest, and this result was independent of the height of the substrate.
 Webs may vary in height based on the type of prey being ensnared.
-*Agelenopsis* spiders capture both flying and crawling insects [].
-Arthropod community structure is highly variable between urban habitats, and urban centers and urban forests may support different types of prey items for *A.
+We have observed *Agelenopsis* spiders capture both flying, hopping, and crawling insects.
+Arthropod community structure can be highly variable between urban habitats [@bang_faeth_2011], and urban centers and urban forests may support different types of prey items for *A.
 pennsylvanica*.
@@
 Alternatively, webs in different habitats may experience different levels of disturbance.
-In the urban center where lawns are mown frequently and ornamental plants are regularly pruned, spiders could maintain lower webs to conserve energy from constantly climbing up a substrate.
-Urban forests likely have abundant ground dwelling vertebrates whose movement along the forest floor could frequently damage lower webs.
-Greater tree coverage in the urban forest predict higher webs may further suggest that small mammal movement could destroy low wbes as areas with greater tree cover have been shown to have higher abundance of small mammals [].
+In the urban center where lawns are mowed frequently and ornamental plants are regularly pruned, spiders could maintain lower webs to conserve energy  from frequent rebuilding.
+Urban forests likely support (and act as a refuge for) many ground dwelling vertebrates, whose movement along the forest floor could frequently damage lower webs.
+Greater tree coverage in the urban forest predict higher webs may further suggest that small mammal movement could destroy low webs as areas with greater tree cover may provide protection and food resources for small mammals [@sarkar_2022].
 Future research should assess prey type available and small animal abundance and movement between these two habitats.
 We speculate that vibratory noise may promote lower web heights based on a trend that showed lower web heights overall at sites with higher road disturbance.
-Plant vibrations tend to be dampened nearer to the ground [] which could encourage spiders to build lower where noise is reduced.
+Perhaps vibratory noise is dampened on a plant nearer to the ground, but this idea requires further testing.
 
@@
 
-Our study shows that a solitary, generalist predator is more abundant and aggregated with lower web height in an urban center compared to an urban forest -- habitats that vary signficantly in environmental condition.
-While we did not measure community-level interactions among organisms, correlations between spatial pattern and environmental condition indirectly indicate that inter- and intraspecific interactions, especially prey abundance, are essential for predicting and monitoring spider aggregative behavior.
-Spider aggregations in urban centers can have medical consequences, such as dense *Lactrodectus hesperus* aggregations [], and aesthetic conerns, as is the case with aggregations of ** under archways of historic buildings [].
+Our study shows that a solitary, generalist predator is more abundant and aggregated with lower web height in an urban center compared to an urban forest -- habitats that vary significantly in environmental condition.
+While we did not measure community-level interactions among organisms, correlations between spatial pattern and environmental condition indirectly indicate that inter- and intraspecific interactions, especially prey abundance, may be essential for predicting and monitoring spider aggregative behavior.
+Spider aggregations in urban centers can have medical consequences, such as dense *Lactrodectus hesperus* aggregations [@johnson_et_al_2011], and aesthetic concerns, as is the case with aggregations of *Brigittea civica* under archways of historic buildings [@mammola_et_al_2018].
 On the other hand, spider aggregations could control pest outbreaks that threaten human health and food supply.
@@
 Our variables that estimate the potential for vibratory noise negatively affected spider abundance while promoting lower web heights, potentially to reduce interference from vibratory noise.
-Noise variables had opposite affects on aggregative behavior of spiders in the different habitats that may indicate differences in tolerance to noise, but more research is necessary to test this hypothesis.
+Noise variables had opposite effects on aggregative behavior of spiders in the different habitats that may indicate differences in tolerance to noise, but more research is necessary to test this hypothesis.
 Thus, urban habitats can vary in environmental conditions which can determine how animals distribute themselves in space and affect predator-prey interactions.
@@
 ## Tables
+
 **Table.
-1** Landscape variables for Lincoln (Nebraska, USA) City Limits, University of Nebraska-Lincoln (UNL) City Campus, and Wilderness Park collected from the National Land Cover Database (2016 Tree Cover, 2019 Impervious Cover, 2019 Land Cover), the Landsat-7 World Reference System-2 (Band 6, path 28, row 32, taken September 2, 2020), and the 2020 Visible Infrared Imaging Radiometer Suite (VIIRS) using QGIS (v.
+1** Examples of studies elucidating the mechanisms behind spider aggregations.
+Mechanisms are categorized by inter- and intraspecific interactions, environmental factors, and dispersal, but it is important to note that these categories are likely inter-related.
+The table is meant to provide examples, rather than represent a full review of studies.
+Several aggregation mechanisms were studied in urban habitats.
+
+**Table.
+2** Landscape variables for Lincoln (Nebraska, USA) City Limits, University of Nebraska-Lincoln (UNL) City Campus, and Wilderness Park collected from the National Land Cover Database (2016 Tree Cover, 2019 Impervious Cover, 2019 Land Cover), the Landsat-7 World Reference System-2 (Band 6, path 28, row 32, taken September 2, 2020), and the 2020 Visible Infrared Imaging Radiometer Suite (VIIRS) using QGIS (v.
 3.16.3-Hannover, ESRI 102704)
 
-**Table 2** Mean and standard error of environmental predictors collected in 100 meter buffers of each focal web by habitat
+**Table 3** Mean and standard error of environmental predictors collected in 100 meter buffers of each focal web by habitat
 
-**Table.3** Results of the top models after AIC model selection from Poisson Generalized Linear Models with the environmental predictors for data overall and subset by habitat (urban forest and urban center).
+**Table.4** Results of the top models after AIC model selection from Poisson Generalized Linear Models with the environmental predictors for data overall and subset by habitat (urban forest and urban center).
 Asterisks indicate significance level (*** *P* < 0.001; ** *P* < 0.01; * *P* < 0.05)

### 2023-01-08 data_analysis.Rmd
Lots of changes

@@
          Location = fct_relevel(Location, 
-                                "Urban Forest", "Urban Center"),
+                                "Urban Center", "Urban Forest"),
          Land = fct_recode(Land, 
@@
 ```{r search_land_graph}
-sites <- sites %>% 
-  mutate(Land = fct_relevel(Land, "Deciduous Forest", 
-                            "Woody Wetlands", 
-                            "Urban, High", 
-                            "Urban, Medium", 
-                            "Urban, Low"))
+#sites <- sites %>% 
+#  mutate(Land = fct_relevel(Land, "Deciduous Forest", 
+#                            "Woody Wetlands", 
+#                            "Urban, High", 
+#                            "Urban, Medium", 
+#                            "Urban, Low"))
 nd <- data.frame(Land = factor(levels(sites$Land)))
@@
   annotate(geom="text", x=2, y=max(sites$WalkDist), label="B", color="black", size = 3) +
-  annotate(geom="text", x=3, y=max(sites$WalkDist), label="C", color="black", size = 3) +
-  annotate(geom="text", x=4, y=max(sites$WalkDist), label="A", color="black", size = 3) +
-  annotate(geom="text", x=5, y=max(sites$WalkDist), label="A", color="black", size = 3)
+  annotate(geom="text", x=3, y=max(sites$WalkDist), label="B", color="black", size = 3) +
+  annotate(geom="text", x=4, y=max(sites$WalkDist), label="B", color="black", size = 3) +
+  annotate(geom="text", x=5, y=max(sites$WalkDist), label="C", color="black", size = 3)
 
@@
 ```{r webs_land_graph}
-sites <- sites %>% 
-  mutate(Land = fct_relevel(Land, "Deciduous Forest", 
-                            "Woody Wetlands", 
-                            "Urban, High", 
-                            "Urban, Medium", 
-                            "Urban, Low"))
+#sites <- sites %>% 
+#  mutate(Land = fct_relevel(Land, "Deciduous Forest", 
+#                            "Woody Wetlands", 
+#                            "Urban, High", 
+#                            "Urban, Medium", 
+#                            "Urban, Low"))
 nd <- data.frame(Land = factor(levels(sites$Land)))
@@
   annotate(geom="text", x=2, y=max(sites$NumWebs), label="A", color="black", size = 3) +
-  annotate(geom="text", x=3, y=max(sites$NumWebs), label="B", color="black", size = 3) +
+  annotate(geom="text", x=3, y=max(sites$NumWebs), label="A", color="black", size = 3) +
   annotate(geom="text", x=4, y=max(sites$NumWebs), label="B", color="black", size = 3) +
@@
 ```{r spiders_land_graph}
-sites <- sites %>% 
-  mutate(Land = fct_relevel(Land, "Deciduous Forest", 
-                            "Woody Wetlands", 
-                            "Urban, High", 
-                            "Urban, Medium", 
-                            "Urban, Low"))
+#sites <- sites %>% 
+#  mutate(Land = fct_relevel(Land, "Deciduous Forest", 
+#                            "Woody Wetlands", 
+#                            "Urban, High", 
+#                            "Urban, Medium", 
+#                            "Urban, Low"))
 nd <- data.frame(Land = factor(levels(sites$Land)))
@@
   annotate(geom="text", x=2, y=max(sites$NumSpiders), label="A", color="black", size = 3) +
-  annotate(geom="text", x=3, y=max(sites$NumSpiders), label="B", color="black", size = 3) +
+  annotate(geom="text", x=3, y=max(sites$NumSpiders), label="A", color="black", size = 3) +
   annotate(geom="text", x=4, y=max(sites$NumSpiders), label="B", color="black", size = 3) +
@@
     theme_classic() +
-    scale_y_continuous(limits = c(0, 1000), breaks = c(0, 200, 400, 600, 800, 1000)) +
+    scale_y_continuous(limits = c(-50, 1000), breaks = c(0, 200, 400, 600, 800, 1000)) +
     xlab("Nearest Neighbors") +
@@
   theme_classic() +
-  scale_y_continuous(limits = c(0, 1000), breaks = c(0, 200, 400, 600, 800, 1000)) +
+  scale_y_continuous(limits = c(-50, 1000), breaks = c(0, 200, 400, 600, 800, 1000)) +
   xlab("Nearest Neighbors") +
@@
 ```{r dist_land_graph}
-near <- near %>% 
-  mutate(Land = fct_relevel(Land, "Deciduous Forest", 
-                            "Woody Wetlands", 
-                            "Urban, High", 
-                            "Urban, Medium", 
-                            "Urban, Low"))
+#near <- near %>% 
+#  mutate(Land = fct_relevel(Land, "Deciduous Forest", 
+#                            "Woody Wetlands", 
+#                            "Urban, High", 
+#                            "Urban, Medium", 
+#                            "Urban, Low"))
 nd <- data.frame(Land = factor(levels(sites$Land)))
@@
 ```{r height_land_graph}
-webs <- webs %>% 
-  mutate(Land = fct_relevel(Land, "Deciduous Forest", 
-                            "Woody Wetlands", 
-                            "Urban, High", 
-                            "Urban, Medium", 
-                            "Urban, Low"))
+#webs <- webs %>% 
+#  mutate(Land = fct_relevel(Land, "Deciduous Forest", 
+#                            "Woody Wetlands", 
+#                            "Urban, High", 
+#                            "Urban, Medium", 
+#                            "Urban, Low"))
 predictions <- expand.grid(Land = levels(factor(webs$Land)))
@@
 
-predictors_agg <- ggarrange(agg1, labels1, agg2, labels2, nrow = 4, heights = c(0.35, 0.15, 0.35, 0.15))
+predictors_agg <- ggarrange(agg2, labels2, agg1, labels1, nrow = 4, heights = c(0.35, 0.15, 0.35, 0.15))
 #saveRDS(predictors_agg, "manuscript/figures/predictors_agg.Rds")
@@
 land_cover <- cbind(names, land_cover)
-colnames(land_cover) <- c(" ", "Lincoln City Limits", "UNL City Campus \nUrban Center", "Wilderness Park \nUrban Forest")
+colnames(land_cover) <- c(" ", "Urban Center \n(UNL City Campus)", "Urban Forest \n(Wilderness Park)", "Lincoln City Limits")
 flextable(land_cover[ ,1:4]) %>% 
@@
 mean_se1 <- c("Mean ± Std.
-Error", "Wilderness Park \nUrban Forest", "47.15 ± 2.17", "1.27 ± 0.36", "137.44 ± 3.71", "5.89 ± 0.77", "13.30 ± 1.15", "46,294.7 ± 68.040", "104 ± 3.23", "35.6 ± 1.89", "15.67 ± 1.25")
+Error", "Urban Forest \n(Wilderness Park)", "47.15 ± 2.17", "1.27 ± 0.36", "137.44 ± 3.71", "5.89 ± 0.77", "13.30 ± 1.15", "46,294.7 ± 68.040", "104 ± 3.23", "35.6 ± 1.89", "15.67 ± 1.25")
 mean_se2 <- c("Mean ± Std.
-Error", "UNL City Campus \n Urban Center", "1.58 ± 0.36", "76.52 ± 2.53", "153.39 ± 3.58", "116.90 ± 3.12", "3.33 ± 0.53", "116.90 ± 3.12", "398 ± 5.76", "65.0 ± 2.33", "93.03 ± 2.78")
-pred_location <- data.frame(mean_se1, mean_se2)
+Error", "Urban Center \n(UNL City Campus)", "1.58 ± 0.36", "76.52 ± 2.53", "153.39 ± 3.58", "116.90 ± 3.12", "3.33 ± 0.53", "116.90 ± 3.12", "398 ± 5.76", "65.0 ± 2.33", "93.03 ± 2.78")
+pred_location <- data.frame(mean_se2, mean_se1)
 rownames(pred_location) <- c("", " ", "Percent Tree Cover [%]", "Percent Impervious Cover [%]", "Spectral Radiance [Watts/(m² * sr * µm)]", "Artificial Night Sky Radiance [mcd/m²]", "Plant Species Richness", "Patch Area [m²]", "Road Disturbance [vehicles/day/m]", "Highway Disturbance [vehicles/day/m]", "Total Road Length [m]")
@@
   mutate(Location = fct_recode(Location, "Urban Center" = "Campus", "Urban Forest" = "Forest"),
-         Location = fct_relevel(Location, "Urban Forest", "Urban Center")) %>% 
+         Location = fct_relevel(Location, "Urban Center", "Urban Forest")) %>% 
   ggplot(aes(x = Location, y = Number, fill = factor(Type, levels=c("Cement", "Metal", "Plastic", "Rocks", "Herb", "Litter", "Shrub", "Tree", "Vine")))) + 

### 2023-01-08 manuscript/figures_tables.Rmd
Some more manuscript edits
Lots of changes

@@
 
+```{r references, fig.width = 3.77, dpi = 300, out.width="50%", include = FALSE}
+#Examples of studies elucidating the mechanisms behind spider aggregations.
+Mechanisms are categorized by inter- and intraspecific interactions, environmental factors, and dispersal, but it is important to note that these categories are likely inter-related.
+The table is meant to provide examples, rather than represent a full review of studies.
+Several aggregation mechanisms were studied in urban habitats.
+
+knitr::include_graphics("/Users/bjpessman/Documents/phd_research_code/Agelenopsis_aggregation/manuscript/figures/references.png")
+```
+
 **Table 1**

### 2023-01-08 manuscript/manuscript.Rmd
Lots of changes

@@
 ---
-title: "Urbanization affects web abundance and aggregation of a funnel weaver, *Agelenopsis pennsylvanica*"
-author: Brandi Pessman, Madison Hays, Earl Agpawa, Eileen Hebets
-date: "`r Sys.Date()`"
+title: "Urbanization affects web abundance and aggregation of a funnel-weaving spider, *Agelenopsis pennsylvanica*"
 output: 
@@
 
-**Log line: Under increasing urbanization, generalist predators actively select web locations to effectively capitalize on more abundant prey as environmental conditions change.**
+Brandi J. Pessman ^1\*^, Madison Hays ^1^, Earl Agpawa ^2^, Eileen A. Hebets ^1^
+
+^1^ University of Nebraska-Lincoln, Department of Biological Sciences, Lincoln, Nebraska, United States
+
+^2^ University of Nebraska-Lincoln, Department of Entomology, Lincoln, Nebraska, United States
+
+^\*^ Corresponding Author Email: [bjpessman\@gmail.com](mailto:bjpessman@gmail.com){.email}
 
@@
 Animals distribute themselves within habitats based on a variety of environmental conditions, including those impacted by urbanization.
-In Lincoln, Nebraska, USA, funnel-weaving spiders (*Agelenopsis pennsylvanica*) are prevalent across urban habitats and actively choose web sites.
+Throughout North America, funnel-weaving spiders (*Agelenopsis*) are prevalent across urban habitats and actively choose sites to build webs.
 We compared *A.
-pennsylvanica* abundance and distribution between two distinct urban habitats: an urban center and an urban forest.
+pennsylvanica* abundance and distribution between two distinct urban habitats: an urban center (university campus) and an urban forest (city park).
+These urban habitats differ significantly in terms of plant diversity and disturbance from nearby roads and highways, among other factors.
+We wanted to know how these urban habitats and their associated environmental conditions affect *A.
+pennsylvanica* spatial patterns.
 We searched along paths from randomly selected start sites in each habitat until we found the first occupied (focal) web.
@@
 We also found (iv) shorter distances between webs and (v) lower web heights in the urban center.
+Generally, spiders were more abundant and aggregated at sites that had lower plant diversity and greater disturbance from road and highway traffic.
 Our data suggest that *A.
-pennsylvanica* spatially distribute themselves differently across different urban habitats, and we discuss a variety of environmental variables that may predict this behavior.
+pennsylvanica* spatially distribute themselves differently across different urban habitats, and this variation relates, in part, to differences in environmental conditions.
+
+## Keywords
+Arachnids, Arthropods, Spatial Distribution, Environmental Predictors
+
+## Acknowledgments
+
+We thank Morgan Ryan for his advice about processing the GIS data in QGIS.
+We are grateful for past and present members of the Hebets, Shizuka, and Keesey labs (UNL Behavior Group) for their feedback on data analysis and earlier drafts of the manuscript.
+We also thank conference attendees that have visited posters and oral talks about this project, as those conversations have helped to improve many aspects of the research presented here.
+
+\newpage
 
@@
 Animal abundance and distribution are influenced by combinations of environmental factors, intra- and interspecific interactions, and dispersal capacity [@svamberkova_leps_2020; @diez_pulliam_2007].
-Environmental factors -- including climatic conditions, land cover, habitat heterogeneity, and access to certain resources (like water and shelter) -- are suspected to relate to physiological constraints that limit the fundamental niche [@chase_leibold_2003].
+Environmental factors, including climatic conditions, land cover, habitat heterogeneity, and access to certain resources (like water and shelter), are suspected to relate to physiological constraints that limit the fundamental niche [@chase_leibold_2003].
 Interactions within species (between conspecific competitors and mates) and across species (with predators, prey, and heterospecific competitors) further shape animal spatial patterns [@anderson_2017; @boulangeat_2012].
-While dispersal capacity can determine a species’ range, barriers can limit dispersal and prevent animals from reaching suitable habitats  [@boulangeat_2012; @amundrud_2018].
+While dispersal capacity can determine a species' range, barriers can limit dispersal and prevent animals from reaching suitable habitats [@boulangeat_2012; @amundrud_2018].
 
@@
 Clumping can also result from incomplete dispersal that occurs when barriers, often due to habitat structure, prevent adequate dispersal [@riechert_1974b].
-The relative importance of different spatial predictors can vary by the type of taxon-specific spatial information being collected -- *i.e.* presence, abundance, aggregation, or vertical position [@boulangeat_2012].
+Scientists have found differences in the relative importance of different spatial predictors based on the type of taxon-specific spatial information collected -- *i.e.* presence, abundance, aggregation, or vertical position [@boulangeat_2012].
 
-Due to intense habitat disturbance and dense human presence, urbanization has drastically modified the land [@alberti_2020; @mcdonnell_pickett_1990; @pickett_2001] which has altered environmental conditions, community dynamics, and dispersal capability as a result [@piano_2020].
-As these factors determine animal spatial patterns, it is likely that urbanized landscapes have changed how animals spatially distribute themselves, in turn.
-Typically, city tree cover is reduced in areas where the potential natural vegetation is forested [@nowak_1996] and greater in areas with prairie, grassland, and desert origins [@mckinney_2006].
-Urban environments are additionally characterized by decreased biodiversity [@mckinney_2002] and increased impervious cover (compacted soil from buildings and pavement; @nowak_greenfield_2020) and habitat patchiness [@cadenasso_2007].
-These conditions can contribute to changes in climatic conditions, such as when impervious cover traps heat and increases the average temperatures in cities compared to surrounding areas –- *i.e.*, the Urban Heat Island Effect [@morabito_2021].
+Due to intense habitat disturbance and dense human presence, urbanization has drastically modified the land [@alberti_2020; @mcdonnell_pickett_1990; @pickett_2001].
+These land changes lead to altered environmental conditions, community dynamics, and dispersal capability as a result [@piano_2020].
+Urban environments are characterized by decreased biodiversity [@mckinney_2002], increased impervious cover [compacted soil from buildings and pavement, @nowak_greenfield_2020], habitat patchiness [@cadenasso_2007], pollution [air, water, and light, @grimm_2008; @hopkins_2018], and noise [air-, water-, and substrate-borne, @barber_2010; @slabbekoorn_2010; @wu_elias_2014].
+These conditions can contribute to changes in local climatic conditions, such as when impervious cover traps heat and increases the average temperatures in cities compared to surrounding areas --- *i.e.*, the Urban Heat Island Effect [@morabito_2021].
+There is growing evidence that urbanization changes species interactions, even reshaping whole food webs [@start_2020] and altering the landscape of parasite and disease transmission [@bradley_altizer_2007].
+As many of these conditions and dynamics determine animal spatial patterns, it is likely that urbanized landscapes have changed how animals spatially distribute themselves.
 
-Disturbance from human presence can also lead to air, water, and light pollution [@grimm_2008; @hopkins_2018], as well as air-borne, water-borne, and substrate-borne noise [@barber_2010; @slabbekoorn_2010; @wu_elias_2014].
-There is growing evidence that urbanization changes species interactions, even reshaping whole food webs [@start_2020] and the landscape of parasite and disease transmission [@bradley_altizer_2007].
-Further, habitat fragmentation and urban features often limit dispersal, which can cause higher degrees of aggregation for urban animals [@johnson_munshisouth_2017].
-Urban ecosystems are extremely heterogeneous with unique and diverse habitats nested within [@rivkin_2019].
-Habitats within urban ecosystems can vary considerably in feature, condition, and disturbance, resulting in variable access and distributions of resources that can differentially drive animal spatial patterns [@murray_2019; @trubl_2012].
+Urban ecosystems can also be extremely heterogeneous with unique and diverse habitats nested within [@rivkin_2019].
+For example, habitats within urban ecosystems can differ considerably in landscape features (e.g.
+tree and building cover), weather conditions (e.g.
+temperature, humidity, and wind speed), and disturbance, resulting in variable access and distributions of resources and opportunities for certain species to thrive.
+These factors can also differentially drive animal spatial patterns [@murray_2019; @trubl_2012], sometimes leading to higher degrees of aggregation for urban animals [@johnson_munshisouth_2017].
 
-Variation in the abundance and distribution of urban arthropods can have implications for ecosystem function due to the essential ecosystems services that arthropods provide, like pest control [@otoshi_2015] and pollination [@ivers_2022].
+Variation in the abundance and distribution of urban arthropods can have implications for ecosystem function due to the essential ecosystem services that arthropods provide, like pest control [@otoshi_2015] and pollination [@ivers_2022].
 Arthropods are considered critical bioindicators of ecosystem health as their short generation time requires them to respond rapidly to human-induced change [@mcintyre_2000].
 However, the impact of urbanization on arthropod ecology is still understudied [but see @kotze_2011; @fenoglio_2020], and the relationship between urban habitats and arthropod abundance and diversity remain controversial [@gippet_2017; @dale_frank_2018].
-Such discrepancies are probably due to abundance and distributions being species- [@gippet_2017], habitat- [@bennett_lovell_2014], and scale-dependent [@philpott_2014].
+Such discrepancies are most likely due to abundance and distributions being species- [@gippet_2017], habitat- [@bennett_lovell_2014], and scale-dependent [@philpott_2014].
 While some animals benefit from urban conditions [@guenard_2015], many cannot survive the disturbance and change associated with cities [@wagner_2020].
-Thus, it is important to determine how urban factors may be contributing to variation in arthropod abundance and spatial patterns for the conservation of arthropods and their essential services.
+Thus, it is important to determine how urban factors contribute to variation in arthropod abundance and spatial patterns for the conservation of arthropods and their essential services.
 
-Specifically, spiders play an important role in pest control and are predicted to collectively consume up to 800 million tons of arthropods each year [@nyffeler_birkhofer_2017].
-Many web-building spiders are choosy in their web locations based on the distribution and abundance of other arthropod prey [@trubl_2012; @riechert_tracy_1975].
-Territoriality is a form of intra-specific interactions that can also shape spatial distributions of web-builders [@riechert_1974b].
-Further, previous studies have found environmental factors that vary across urban habitats may drive differences in spider spatial distribution, including noise [@bunkley_2017; @gomes_2020], pollution [@zmudzki_laskowski_2012], fragmentation [@stefani_delclaro_2015], microclimate conditions [@riechert_tracy_1975], vegetation structure [@peng_2020], and suitable web substrates [@chan_2009].
+Spiders, specifically, play an important role in pest control.
+They are predicted to collectively consume up to 800 million tons of arthropods each year [@nyffeler_birkhofer_2017].
+Previous studies have found that factors that vary across urban habitats may drive differences in spider spatial distribution, including prey abundance [@trubl_2012; @riechert_tracy_1975], noise [@bunkley_2017; @gomes_2020], pollution [@zmudzki_laskowski_2012], fragmentation [@stefani_delclaro_2015], microclimate conditions [@riechert_tracy_1975], vegetation structure [@peng_2020], and suitable web substrates [@chan_2009].
+Random spacing in solitary spiders is typically maintained by territoriality and aggression over resources like prey and mates [@riechert_1974b], but occasionally, conditions arise that allow solitary spiders to become more tolerant of neighbors.
+The mechanisms behind non-social spider aggregations - especially in urban habitats - are unclear.
+Nonetheless, there are reports of aggregations of spiders in urban habitats, such as the web-building spiders *Lactrodectus hesperus* and *Brigittea civica* [@johnson_et_al_2012; @mammola_et_al_2018].
+A more thorough understanding of how and why various species of spiders might distribute themselves differently in urban settings is important, as urban spider aggregations can have medical and aesthetic consequences, as well as implications for urban pest control services.
 
-The mechanisms behind solitary spider aggregations - especially in urban habitats - are unclear despite reports of aggregations of spiders in urban habitats, such as web-builders *Lactrodectus hesperus* and *Brigittea civica* [@johnson_et_al_2012; @mammola_et_al_2018].
-This gap in knowledge is concerning as urban spider aggregations can have medical and aesthetic consequences, and implications for urban pest control services.
-Prey abundance seems to be an important driver because it has been shown to be directly and indirectly (for example, light sources at night as cues of prey clustering) related to urban spider aggregations (Table 1).
-Random spacing in solitary spiders is typically maintained by territoriality and aggression over resources like prey and mates [@riechert_1974b].
-Occasionally, conditions arise that allow solitary spiders to become more tolerant of neighbors, and understanding these contexts can help uncover the mechanisms of aggregative behavior.
-Aggregations have been shown to form as a result of inter- and intraspecific interactions, environmental factors, and dispersal limitations (Table 1).
-
-Funnel weavers in the genus *Agelenopsis* actively select web locations based on experience of perceived quality of the site [@riechert_1976], and are thus likely impacted by environmental conditions resulting from urbanization.
+Funnel-weaving spiders in the genus *Agelenopsis* are found across North America and can be locally very common.
+They actively select web locations based on experience of perceived quality of the site [@riechert_1976] and are thus likely impacted by environmental conditions resulting from urbanization.
 Prey abundance, available web substrates, vegetation structure, and microclimate conditions have been shown to be indicators of a quality web site in a desert habitat for *A.
 aperta* [@riechert_1974; @riechert_1973].
-*Agelenopsis pennsylvanica* build webs that consist of a sheet that functions as a prey capture area and a retreat to escape from predators and unfavorable conditions (Fig.
-1), like direct sunlight [@riechert_tracy_1975].
-The horizontal sheet is not sticky, and the web is used solely for its vibratory properties to rapidly and accurately locate prey that fall upon or walk across the web [@singer_2000].
-Occasionally, vertical silk strands are found that may function to capture flying prey or evade predators [@singer_2000].
-The spider sits in the retreat until the prey is sensed and returns to the retreat immediately after capturing the prey.
-Juvenile males and females build semi-permanent webs, but males leave their web shortly after maturity in search of a receptive female [@singer_2000].
+*Agelenopsis pennsylvanica* is a non-desert dwelling relative that similarly builds webs consisting of a sheet that functions as a prey capture area and a retreat to escape from predators and unfavorable conditions (Fig.
+1), such as direct sunlight [@riechert_tracy_1975].
+The horizontal sheet is not sticky, and the web is used solely for its vibratory properties to rapidly and accurately alert the spider to prey that fall upon or walk across the web [@singer_2000].
 
-Understanding how urban spiders are affected by changes in environmental conditions and habitat structure brought on by processes of urbanization is vital as cities continue to densify and expand.
-Thus, we compared *A.
-pennsylvanica* spatial patterns between two urban habitats (an urban forest and an urban center) and explored what environmental factors are important determinants of web placement.
-In particular, we use *A.
-pennsylvanica* to address three questions: (*i*) How do web abundance, aggregation, and position vary between two urban habitats?
-(*ii*) How do environmental conditions vary between these two urban habitats?
+```{r spider, dpi = 300}
+knitr::include_graphics("/Users/bjpessman/Documents/phd_research_code/Agelenopsis_aggregation/manuscript/figures/spider.png")
+```
+
+**Fig. 1** Study System - *Agelenopsis pennsylvanica* (a). The web consists of a retreat where the spider waits for prey to land, fall, or walk on the web sheet (b)
+
+To understand habitat characteristics that might influence the distribution of *A pennsylvanica* across urban environments, we compared *A.
+pennsylvanica* spatial patterns between two urban habitats (an urban center and an urban forest).
+In particular, we asked the following three questions: (*i*) How do environmental conditions vary between two urban habitats?
+(*ii*) How do *A.
+pennsylvanica* web abundance, aggregation, and position vary between these two urban habitats?
 (*iii*) What environmental variables help predict spider spatial patterns in distinct urban habitats?
-Based on preliminary observations, we predicted that spiders would be more abundant and aggregated in the urban center than the urban forest.
-We further hypothesized that environmental conditions that vary between the two habitats would be correlated with the variation in the spatial patterns of *A.
+Based on preliminary observations, we predicted that *A.
+pennsylvanica* would be more abundant and aggregated in the urban center than the urban forest.
+We further expected that specific environmental conditions that vary between the two habitats (e.g.
+tree cover, plant species richness, and disturbance from roads) would be correlated with the variation in the spatial patterns of *A.
 pennsylvanica*.
@@
 
-### Urban Habitats
-
 We conducted our study in September and October of 2020 in Lincoln, Nebraska, USA.
 Lincoln -- with a population of about 300,000 people [@census] -- has diverse urban habitats that vary in the degree of disturbance, management, and plant cover.
-We compared the abundance, aggregation, and position of funnel webs (*Agelenopsis pennsylvanica*) between two urban habitats: the University of Nebraska-Lincoln (UNL) City Campus (an urban center) and Wilderness Park (an urban forest) (Fig.
+We compared the abundance, aggregation, and position of funnel webs of the spider *Agelenopsis pennsylvanica* between two urban habitats: the University of Nebraska-Lincoln (UNL) City Campus (an urban center) and Wilderness Park (an urban forest) (Fig.
 2, Fig.
 S1).
-These two habitats were selected due to their distinctive characteristics (described below), preliminary observations of potential differences in funnel weaver abundance and aggregation (Fig.
+These two habitats were selected due to their distinctive characteristics (described below), preliminary observations of potential differences in funnel-weaving spider abundance and aggregation (Fig.
 S2), and ease of access.
 
-To first quantify differences in the environmental conditions between urban habitats, we gathered and analyzed Geographic Information Systems (GIS) data in QGIS (v.
+*Urban Center* - We defined the study boundaries of UNL City Campus as Salt Creek Roadway, North Antelope Valley Parkway, North 10th Street, and Q Street (1.12 $km^2$, Fig.
+2, Fig.
+S1).
+UNL City Campus is adjacent to, and just north of, downtown Lincoln (253.73 $km^2$).
+Lawns are maintained by frequent mowing, and gardens and landscaping are regularly pruned.
+There was heavy foot traffic from UNL's 20,286 undergraduates enrolled in the 2020-2021 academic year, 37% of which lived in college-owned, -operated, or -affiliated housing [@iea_2021].
+
+*Urban Forest* - Wilderness Park is a stretch of forested land (6.44 $km^2$, Fig.
+2, Fig.
+S1) starting about 3.58 km southwest of UNL City Campus and downtown Lincoln, extending south and along Lincoln city limits.
+Wilderness Park has about 18 kilometers of dirt trails, dense deciduous tree growth, and variable undergrowth.
+The trails are open for recreational walking, running, biking, and horse riding.
+While we found no public records of the number of visitors to Wilderness Park, trail-goers were infrequent during data collection.
+
+```{r land_location, fig.width = 6.85, dpi = 300}
+knitr::include_graphics("/Users/bjpessman/Documents/phd_research_code/Agelenopsis_aggregation/manuscript/figures/land_locations.png")
+```
+
+**Fig.
+2** Land cover raster with borders for Lincoln, Nebraska, USA city limits (dashed border), University of Nebraska-Lincoln (UNL) City Campus (Urban Center, solid border, a), and Wilderness Park (Urban Forest, solid border, b) using the 2019 National Land Cover Data on Land Cover and QGIS (v.
 3.16.3-Hannover, ESRI 102704).
-We obtained tree cover [@usfs_2016], impervious (building and pavement) cover [@usgs_2019_imperv], and land use class [@usgs_2019_land] from the National Land Cover Database (30-meter resolution).
-We used an image from path 28, row 32 of the Landsat-7 World Reference System-2 (Band 6) to collect spectral radiance -- a measure of thermal conditions on Earth's surface (30-meter resolution, taken on September 2, 2020).
-Finally, we assessed artificial light at night levels using the 2020 Visible Infrared Imaging Radiometer Suite (VIIRS) from https://www.lightpollutionmap.info/ (500-meter resolution).
-We polygonized the tiff files and calculated the average value for each factor by location: UNL City Campus, Wilderness Park, and Lincoln City Limits (see Fig.
+For visualization and listing of study sites, see Figure S1 and Table S1, respectively
+
+### Study sites
+
+To select random survey sites in each of the two habitats, we assigned numbers to each intersection of roads and sidewalks that meet from the four cardinal directions in the urban center and to intersections of three or more trails in the urban forest (Fig.
+S3).
+We used a random number generator to randomly select 12 intersections in the urban center and 10 intersections in the urban forest as start sites (Table S1).
+We marked the GPS coordinates of these locations using a GPS receiver (Magellan SporTrak Map, Model 980616-01, Parsippany, New Jersey, USA).
+
+From each start site, we began walking along a path in a randomly selected direction (North, East, South, or West using a random number generator).
+We conducted a thorough visual search of the edges of the path for *A.
+pennsylvanica* funnel webs as the GPS receiver tracked our movement (Fig.
+S4).
+We walked along pre-existing sidewalks, roads, and trails because paths were a common feature of both habitats along which we had previously found funnel-weaving spiders.
+We often found *A.
+pennsylvanica* in edge habitats in the study region, and this tendency to build webs at a habitat's edge is shared by other spider species [@cobbold_supp_2012].
+Additionally, the thick undergrowth of the urban forest often restricted searches off the trails.
+To ensure equivalent search efforts, we took more time searching the edge of dense undergrowth in the urban forest.
+
+*Focal web* -- When we reached a funnel web, we checked to see if the web was occupied by a spider.
+We did this by resting a toothpick secured to the bristled end of a vibrating toothbrush on the sheet of the web.
+We turned on the electric toothbrush to simulate prey in the web.
+If a spider emerged, we noted this web as the *focal web*.
+If no spider emerged after 30 seconds, we continued searching until we found an occupied funnel web.
+Preliminary trials demonstrated this to be an effective means of enticing a spider out of its retreat and onto its sheet web.
+We used the GPS receiver to mark the coordinates of the focal web.
+Although it is possible that other species of *Agelenopsis* are present in Lincoln, we have only found *A.
+pennsylvanica* during surveys in the area.
+
+### Urban habitat characteristics
+
+*Environmental conditions of the habitats and Lincoln* -- We first compared differences in environmental conditions across our two selected urban habitats and Lincoln city limits.
+We chose tree cover, impervious cover, and land cover class for this initial analysis to capture the degree of variation between the habitats as compared to the entire city.
+We gathered and analyzed Geographic Information Systems (GIS) data in QGIS (v.
+3.16.3-Hannover, ESRI 102704).
+We obtained tree cover [@usfs_2016], impervious cover [building and pavement, @usgs_2019_imperv], and land cover class [@usgs_2019_land] from the National Land Cover Database (30-meter resolution).
+We polygonized the tiff files and calculated the average value for each factor by location using the boundaries described above: urban center (UNL City Campus), urban forest (Wilderness Park), and Lincoln City Limits (see Fig.
 2, Fig.
-S3-S6).
-We included measurements for Lincoln city limits to show how the two study locations compare to the city of Lincoln overall.
+S5-S8).
 We calculated the averages using the following equation:
@@
 
-Where *i* is the value indicated by the pixel (with range b-a) and *$x_i$* is the percent of the habitat covered by the *$i^(th)$* pixel category.
-These data are presented in Table 2 and summarized below.
+Where *i* is the value indicated by the pixel (with range b-a) and $x_i$ is the percent of the habitat covered by the $i^(th)$ pixel category.
 
-We defined the study boundaries of UNL City Campus as Salt Creek Roadway, North Antelope Valley Parkway, North 10th Street, and Q Street (1.12 $km^2$, Fig.
-2, Fig.
-S1).
-UNL City Campus is adjacent to, and just north of, downtown Lincoln (253.73 $km^2$).
-Impervious cover -- in the form of buildings and pavement -- dominates the land on UNL City Campus, considerably more than impervious cover across the city of Lincoln (Table 2, Fig.
-S3).
-Lawns are maintained by frequent mowing, and gardens and landscaping are regularly pruned.
-Tree cover on UNL City Campus and in Lincoln overall is low (< 6%, Table 2, Fig.
-S4).
-There was heavy foot traffic from UNL's 20,286 undergraduates enrolled in the 2020-2021 academic year, 37% of which lived in college-owned, -operated, or -affiliated housing [@iea_2021].
-The entire area of UNL City Campus was categorized as urban with varying intensity (Table 2, Fig.
-2).
-Over half of UNL City Campus was high intensity urban cover compared to only 13.16% for Lincoln overall.
-Further, UNL City Campus exhibits heighten spectral radiance (thermal conditions, Fig.
-S5) and artificial light at night radiance (Fig.
-S6), even above that of Lincoln as a whole (Table 2).
-Thus, we designated UNL City Campus as an *urban center* and refer to it as such hereafter.
+*Environmental variables between habitats* -- To add environmental variables for a more detailed comparison of these two habitats, we collected nine total environmental predictors from each study site: (1) tree cover, (2) impervious cover (percent developed surface), (3) thermal conditions (spectral radiance), (4) light at night radiance, (5) plant species richness, (6) patch area (area of continuous vegetation), (7) disturbance from roads, (8) disturbance from highways, and (9) total road length.
+All measurements except plant species richness were completed in QGIS (v.
+3.16.3-Hannover, ESRI 102704).
 
-Wilderness Park is a stretch of forested land (6.44 $km^2$, Fig.
-2, Fig.
-S1) starting about 3.58 km southwest of UNL City Campus and downtown Lincoln, extending south and along Lincoln city limits.
-We found about two-fifths of Wilderness Park to be shrouded in trees (Table 2, Fig.
-S4), with less than 2% of its land imperviously covered (Table 2, Fig.
-S2).
-Over three quarters of Wilderness Park is categorized as forested land with only 5.44% labeled as urban (Table 2, Fig.
-2).
-Wilderness Park has about 18 kilometers of dirt trails, dense deciduous tree growth, and variable undergrowth.
-The trails are open for recreational walking, running, biking, and horse riding.
-While we found no public records of the number of visitors to Wilderness Park, trail-goers were infrequent during data collection.
-Wilderness Park showed greatly reduced spectral radiance (Fig.
-S5) and artificial light at night radiance (Fig.
-S6) than the city of Lincoln (Table 2).
-Due to its proximity to Lincoln city limits, we designate Wilderness Park as an *urban forest* and refer to it as such hereafter.
+We recorded the percent tree cover (1) and impervious cover (2) at each site using the polyganized tiff files described above.
+To collect spectral radiance (3) -- a measure of thermal conditions on Earth's surface, we used an image from path 28, row 32 of the Landsat-7 World Reference System-2 (Band 6, 30-meter resolution, taken on September 2, 2020).
+We assessed artificial light at night levels (4) using the 2020 Visible Infrared Imaging Radiometer Suite (VIIRS) from <https://www.lightpollutionmap.info/> (500-meter resolution).
+We analyzed these measures in 100-meter buffers around each focal web.
+We used a 100-meter buffer to accommodate the resolution of the GIS data.
+We refrained from including a larger buffer region as the dispersal range of this system is unknown and may be dependent on barriers present in the habitat.
 
-### Study Sites and Field Measurements
+We collected plant species richness (5) on-site by recording each unique plant species (using a plant identification phone application - PictureThis) found in a ten-meter radius of the focal web at each study site (Fig.
+S9).
+We measured patch area (6) using satellite imagery to define the area of continuous vegetation at each study site.
+Roads, sidewalks, and trails were defined as fragment boundaries.
+To determine the potential disturbance from road (7) and highway traffic (8), we first measured the shortest distance from each focal web to the nearest road [GIS vector from: @centerlines] and highway [GIS vector from: @highways] using the NNJoin Plugin [@nnjoin] for QGIS.
+We used the 2021 Average Daily Traffic Volume report [@adtv_2021] to identify the average daily number of vehicles to travel on each nearest road and highway.
+We divided the average daily traffic by the shortest distance from the focal web to the nearest road and highway [as in @dooley_2020] for metrics of road disturbance and highway disturbance, respectively.
+Lastly, we measured the total length of road [9, @centerlines] within a 100-meter buffer of each study site.
 
-Within the boundaries of the urban forest, we assigned numbers to intersections of three or more trails (Fig.
-S7).
-Similarly, we assigned numbers to each intersection of roads and sidewalks that meet from the four cardinal directions in the urban center (Fig.
-S7).
-We used a random number generator to randomly select 10 intersections in the urban forest and 12 intersections in the urban center as start sites (Table S1).
-We marked the GPS coordinates of these locations using a GPS receiver (Magellan SporTrak Map, Model 980616-01, Parsippany, New Jersey, USA).
+### Spider web abundance, patterns, and positions
 
-From each start site, we began walking along a path in a randomly selected direction (North, East, South, or West using a random number generator).
-We thoroughly searched the edges of the path for funnel webs as the GPS receiver tracked our movement (Fig.
-S8).
-We walked along pre-existing sidewalks, roads, and trails because paths were a common feature of both habitats along which we had previously found funnel weavers.
-We often find *A.
-pennsylvanica* in edge habitats in the study region, and this tendency to build webs at a habitat's edge is shared by other spider species [@cobbold_supp_2012].
-Additionally, the thick undergrowth of the urban forest often restricted searches off the trails.
-To ensure equivalent search efforts, we took more time searching the edge of dense undergrowth in the urban forest.
+To determine differences in spider web abundance, aggregation, and position between the two urban habitats, we completed each of the following measurements at each study site within a ten-meter radius of the focal web.
 
-When we reached a funnel web, we checked to see if the web was occupied by a spider by resting a toothpick secured to the bristled end of a vibrating toothbrush on the sheet of the web to simulate prey in the web.
-If a spider emerged, we noted this web as the *focal web*.
-If no spider emerged after 30 seconds, we continued searching until we found an occupied funnel web.
-We used the GPS receiver to mark the coordinates of the focal web.
-Although it is possible that other species of *Agelenopsis* are present in Lincoln, we have only found *A.
-pennsylvanica* during surveys in the area.
+*Spider Abundance* -- Search distance can often be used to estimate abundance [@buckland_2005], as spiders are likely less abundant in an area where we need to search further from the path intersection to the focal web.
+Thus, we use search distance as evidence for variation in abundance.
+To quantitatively determine the abundance of webs and spiders near each focal web, we measured a ten-meter radius around the focal web and counted the number of occupied and unoccupied webs.
+We used the same methods (using the electric toothbrush) as those used for determining the presence/absence of the focal spider.
 
-Search distance can often be used to estimate abundance [@buckland_2005], as spiders are likely less abundant in an area where we need to search further from the start site to the focal web.
-Thus, we use search distance as evidence for variation in abundance.
-To quantitatively determine the abundance of webs and spiders near each focal web, we measured a ten-meter radius around the focal web and counted the number of occupied and unoccupied webs determined in the same manner as the focal web.
-We also assessed nearest neighbor distances as a measure of aggregation behavior.
-Starting at the focal web and working outwards, we marked the locations of the two webs (including occupied and unoccupied) nearest to the focal web within ten meters.
+*Spider Aggregation* -- We assessed nearest neighbor distances as a measure of aggregation behavior.
+Starting at the focal web and working outwards, we marked the locations of the two webs (including occupied and unoccupied) nearest to the focal web and within ten meters.
 We limited our measurements to the nearest two webs because we often found no more than three webs (including the focal web) per site in the urban forest.
 We measured the shortest distance from the retreat of the focal web to the retreat of the two nearest neighbor webs.
-To explore differences in web placement, we measured the web height from the ground to the web retreat for every web with the ten-meter radius.
+
+To determine whether nearness of neighbors in the urban center was the result of aggregation or increased density from higher abundance, we completed calculations described by Clark and Evans [@clark_evans_1954].
+This calculation compares the measured nearest neighbor distance to the expected distance if animals were evenly spaced within an area.
+For each site, we estimated the total search area by adding the length of path searched multiplied by four meters (for searching two meters on either side of the central path line) and the area of the 10-meter radius circular site.
+We subtracted the overlap in the search path and site by subtracting four \* 10 meters.
+
+*Web Position* -- To explore differences in web placement, we measured the web height from the ground to the web retreat for every web within the ten-meter radius.
 Differences in web height have been shown to vary by environmental factors associated with urbanization [@dahirel_2017].
-To get an idea of plant species richness at each site, we recorded each unique plant species found in a ten-meter radius of the focal web (Fig.
-S8).
 
-We collected data from September 23 to October 14, 2020.
-During these dates, all *A.
-pennsylvanica* have reached maturity [@guarisco_2014; personal observation].
-Of the 64 occupied webs, 61 were occupied by females indicating that males had likely abandoned their webs in search of females.
-The 67 unoccupied webs could be those once owned by males or those abandoned by females.
-While webs were found on many of the same plant types between sites in the urban forest and urban center in varying proportions, 15% of webs in urban center sites were built on non-plant substrates (Fig.
-S9).
+We collected data from September 23 to October 14, 2020. During these dates, all *A. pennsylvanica* had reached maturity [personal observation, @guarisco_2014].
 
-### Environmental Predictors
+### Environmental predictors of spider spatial patterns
 
-To assess potential mechanisms behind variation in abundance, aggregation, and position, we looked for correlations between spider spatial patterns and environmental conditions -- collected in the field (plant species richness) or using GIS for each site.
-In QGIS, we created 100 meter buffers around each focal web location and processed the GIS variables mentioned above (tree cover, impervious cover, spectral radiance, and artificial light at night radiance) in the same manner as before.
-To these we added patch area, potential disturbance from nearby roads and highways, and road length in the 100 meter buffer.
-We used a 100 meter buffer to accommodate the resolution of the GIS data.
-We refrained from including a larger buffer region as the dispersal range of this system is unknown and may be dependent on barriers present in the habitat.
-
-We measured patch area using satellite imagery to define the area of continuous vegetation around the focal web.
-Roads, sidewalks, and trails were defined as fragment boundaries.
-To determine the potential disturbance from road and highway traffic, we first measured the shortest distance from each focal web to the nearest road [GIS vector from: @centerlines] and highway [GIS vector from: @highways] using the NNJoin Plugin [@nnjoin] for QGIS.
-We used the 2021 Average Daily Traffic Volume report [@adtv_2021] to identify the average daily number of vehicles to travel on each nearest road and highway.
-We divided the average daily traffic by the shortest distance from the focal web to the nearest road and highway [as in @dooley_2020] for metrics of road disturbance and highway disturbance, respectively.
-Lastly, we measured the total length of road [@centerlines] within a 100 meter buffer of the focal web.
+To assess potential environmental influences on variation in abundance, aggregation, and position, we looked for correlations between spider spatial patterns and the nine environmental conditions described earlier.
+In addition to exploring relationships across the data set overall, we subset the data by habitat to explore within habitats.
+We reduced the number of environmental predictors by removing variables that had a pairwise correlation above 0.6 using the *caret* package in R [@caret].
+As a result of this analysis, artificial light at night radiance was dropped from all subsequent analyses.
+Only plant species richness, road disturbance, and highway disturbance remained for analyses of overall data.
+The urban center subset includes plant species richness, patch area, spectral radiance, road and highway disturbance, and road length.
+We kept tree cover, plant species richness, patch area, and road and highway disturbance for the urban forest subset.
 
@@
 
+#### Environmental variables between habitats
+
+To quantify similarities/differences between our habitats with respect to variables we thought might influence spider abundance, distribution, and web height, we first tested whether the nine environmental predictors varied by habitat.
+Each predictor was tested by habitat using Poisson generalized linear models because the predictors were positive and not normally distributed.
+
 #### Web abundance, aggregation, and position between habitats
 
-For the first set of models, we focused on whether web abundance, aggregation, and position differ between the two habitats (the urban center and urban forest).
+For the second set of models, we focused on whether web abundance, aggregation, and/or position differed between the two habitats (the urban center and urban forest).
 We used Poisson generalized linear models [*stats* package in R, @r] for the response variables: search distance, number of webs, and number of spiders.
 We used Poisson generalized linear mixed effect models [*lme4* package in R, @lme4] with site as a random effect for the response variables: nearest neighbor distance and web height.
-For the model with nearest neighbor distance, we also included neighbor number (nearest and second nearest web) and its interaction with habitat We used Poisson distributions because the response variables were not normally distributed according to Shapiro-Wilk Normality Tests, and all data were strictly positive with no upper limit.
-
-#### Environmental variables between habitats
-
-Since we found significant variation in distribution measures between habitats, we wanted to explore potential environmental mechanisms of such variation within the test habitats.
-We first tested whether the nine environmental predictors varied by habitat (Table 3).
-Each predictor was tested by habitat using Poisson generalized linear models as the predictors were positive and not normally distributed.
-Each environmental predictor significantly varied by habitat (Table 3), so we subset the data by habitat.
-Among the environmental predictors, we removed variables that were highly correlated (cutoff of 0.6) using the *caret* package in R [@caret].
-Artificial light at night radiance was dropped from all analyses for being highly correlated.
-Only plant species richness, road disturbance, and highway disturbance remained for models using all data.
-We kept tree cover, plant species richness, patch area, and road and highway disturbance for the urban forest subset.
-The urban center subset includes plant species richness, patch area, spectral radiance, road and highway disturbance, and road length.
+For the model with nearest neighbor distance, we also included neighbor number (nearest and second nearest web) and its interaction with habitat.
+We used Poisson distributions because the response variables were not normally distributed according to Shapiro-Wilk Normality Tests, and all data were strictly positive with no upper limit.
 
@@
 
-We used the habitat subsets and the selected environmental predictor variables to assess correlations between predictor variables and spatial pattern measures.
+Since we found significant variation in distribution measures between habitats (see Results: Urban habitat characteristics), we wanted to explore environmental correlations with our findings.
+Specifically, we used the habitat subsets and the selected (non-correlated) environmental predictor variables to assess relationships between predictor variables and spatial pattern measures.
 In the global models, we included the predictors (without interactions) that remained after removal for collinearity with the response variables: web and spider abundance, nearest neighbor distance, and web height for the complete data and habitat subsets.
-We assessed nearest neighbor distance and excluded second nearest neighbor distance because both were significantly different between habitats.
+We restricted these nearest neighbor analyses to first nearest neighbor distance (*i.e.* excluded second nearest neighbor distance) because the first and second nearest neighbor distance both significantly differed between habitats, and including both would complicate the analysis.
 We excluded search distance as a response variable because the predictors were collected from the site of the focal web and may vary along the search path.
+
 Several predictors (plant species richness, patch area, and road and highway disturbance) were highly right-skewed, so we used a natural log-transformation prior to model selection.
@@
 From these global models, we performed Akaike Information Criterion (AIC) model selection with the *MuMIn* package in R [@MuMIn], which ranks models produced from every combination of the predictors in the global model.
-We report here the results of each top model, as well as a model average of models within 2 delta AICc points of the top model.
+We reported the results of each top model, as well as a model average of models within 2 delta AICc points of the top model.
 We reported the estimates and standard error from the models without back-transformations for the log-transformed variables.
@@
 
-We also explore how land use may affect web abundance, aggregation, and position using the National Land Cover Database and QGIS to record the category of the land use type for the pixel that each site was located.
+We also explored how land cover may affect web abundance, aggregation, and position using the National Land Cover Database and QGIS to record the category of the land cover class for the pixel that each site was located.
 We tested Poisson generalized linear models for each response variable with land cover as the only predictor.
@@
 We include these results in supplemental material (Fig.
-S12, Table S3) as the sample sizes were small (deciduous forest = 7, woody wetlands = 3, urban high intensity = 4, urban medium intensity = 6, urban low intensity = 2).
+S10, Table S2) as the sample sizes were small (deciduous forest = 7, woody wetlands = 3, urban high-intensity = 4, urban medium-intensity = 6, urban low-intensity = 2).
 
 We completed statistics and visualization using R 4.0.0 [@r] and RStudio 2022.07.2 [@rstudio].
-All graphs show raw data and (top) model estimates (*broom* package [@broom]; *emmeans* package [@emmeans]).
+All graphs show raw data and (top) model estimates [*broom* package, @broom; *emmeans* package, @emmeans].
 We used the *tidyverse* [@tidyverse], *ggpubr* [@ggpubr], and *broom.mixed* [@broommixed] packages in R to produce and customize the graphs.
@@
 For Poisson generalized linear mixed effect models, we determined the 95% confidence intervals of the model estimates by completing 1000 bootstrap iterations using the function *bootMer()* in R package *lme4* [@lme4].
-All R code and data are available in a GitHub repository at: https://github.com/brandipessman/Agelenopsis_aggregation.
+All R code and data are available in a GitHub repository at: <https://github.com/brandipessman/Agelenopsis_aggregation>.
 
@@
 
+### Urban habitat characteristics
+
+*Urban Center* -- Impervious cover -- in the form of buildings and pavement -- dominates the urban center, considerably more than impervious cover across the city of Lincoln (Table 1, Fig.
+S5).
+Tree cover in the urban center and in Lincoln overall is low (\< 6%, Table 1, Fig.
+S6).
+Over half of the urban center was high-intensity urban cover compared to only 13.16% for Lincoln overall.
+Further, the urban center exhibits heighten spectral radiance (thermal conditions, Fig.
+S7) and artificial light at night radiance (Fig.
+S8), even above that of Lincoln as a whole (Table 1).
+
+*Urban Forest* -- We found about two-fifths of the urban forest to be shrouded in trees (Table 1, Fig.
+S6), with less than 2% of its land imperviously covered (Table 1, Fig.
+S5).
+Over three-quarters of the urban forest is categorized as forested land with only 5.44% labeled as urban (Table 1, Fig.
+2).
+The urban forest showed greatly reduced spectral radiance (Fig.
+S7) and artificial light at night radiance (Fig.
+S8) than the city of Lincoln (Table 1).
+
+**Table 1** Landscape variables for the urban center (UNL City Campus), the urban forest (Wilderness Park), and Lincoln (Nebraska, USA) City Limits,  collected from the National Land Cover Database (2016 Tree Cover, 2019 Impervious Cover, 2019 Land Cover), the Landsat-7 World Reference System-2 (Band 6, path 28, row 32, taken September 2, 2020), and the 2020 Visible Infrared Imaging Radiometer Suite (VIIRS) using QGIS (v.
+3.16.3-Hannover, ESRI 102704)
+
+```{r landscape, fig.width = 3.77, dpi = 300, out.width="50%"}
+knitr::include_graphics("/Users/bjpessman/Documents/phd_research_code/Agelenopsis_aggregation/manuscript/figures/landscape.png")
+```
+
+All environmental predictors assessed within a 100-meter radius of the focal web varied by habitat (Table 2).
+Site tree cover was lower in the urban center than the urban forest with five urban center sites measuring zero tree cover ($z_21$ = -14.50, *P* \< 0.001).
+The urban center sites had higher impervious cover, with all but four sites being zero in the urban forest ($z_21$ = 14.51, *P* \< 0.001).
+The urban center sites also had higher spectral radiance ($z_21$ = 3.08, *P* = 0.002) and artificial light at night radiance ($z_21$ = 22.46, *P* \< 0.001).
+Overall plant species richness was lower in the urban center than the urban forest ($z_21$ = -7.67, *P* \< 0.001).
+Similarly, spiders used a lower diversity of plants as substrates in the urban center (mean ± se = 1.42 ± 0.15 species) than the urban forest (mean ± se = 2.7 ± 0.26 species, $z_21$ = -2.08, *P* = 0.037).
+Site patch area was smaller in the urban center ($z_21$ = -374.2, *P* \< 0.001).
+Road disturbance ($z_21$ = 39.19, *P* \< 0.001), highway disturbance ($z_21$ = 9.39, *P* \< 0.001), and road length ($z_21$ = -374.2, *P* \< 0.001) were higher for urban center sites than sites in the urban forest.
+
+**Table 2** Mean and standard error of environmental predictors collected in 100-meter buffers of each focal web by habitat
+
+```{r pred_location, fig.width = 6.85, dpi = 300}
+knitr::include_graphics("/Users/bjpessman/Documents/phd_research_code/Agelenopsis_aggregation/manuscript/figures/pred_location.png")
+```
+
 ### Web abundance, aggregation, and position between habitats
+
+Over the course of the study, we identified 131 funnel webs as being occupied or unoccupied.
+Of the 64 occupied webs, 61 were occupied by females indicating that males had likely abandoned their webs in search of females.
+The 67 unoccupied webs could be those once owned by males or those abandoned by females.
+While webs were found on many of the same plant types between sites in the urban center and urban forest in varying proportions, 15% of webs in urban center sites were built on non-plant substrates (Fig.
+S11).
 
@@
 
-We searched significantly less distance from the start site to the focal web in the urban center than the urban forest ($z_20$ = -10.10, *P* < 0.001, Fig.
+We searched significantly less distance from the start site to the focal web in the urban center than the urban forest ($z_20$ = -10.10, *P* \< 0.001, Fig.
 3a, Fig.
-S8).
-Within a 10-meter radius of the focal web, we counted significantly more webs ($z_20$ = 8.56, *P* < 0.001, Fig.
-3b) and spiders ($z_20$ = 4.86, *P* < 0.001, Fig.
+S4).
+Within a 10-meter radius of the focal web, we counted significantly more webs ($z_20$ = 8.56, *P* \< 0.001, Fig.
+3b) and spiders ($z_20$ = 4.86, *P* \< 0.001, Fig.
 3c) in the urban center than the urban forest.
-We also found that the distances between the focal web and the two nearest neighbors were significantly shorter in the urban center than the urban forest ($z_34$ = -5.60, *P* < 0.001, Fig.
+We also found that the distances between the focal web and the two nearest neighbors were significantly shorter in the urban center than the urban forest ($z_34$ = -5.60, *P* \< 0.001, Fig.
 3d).
-By definition, the second nearest web is further from the focal web than the nearest neighbor ($z_34$ = 14.65, *P* < 0.001).
-There was a significant interaction between neighbor number and habitat -- the second nearest neighbor was significantly further from the focal web than the first nearest neighbor in the urban center, but not the urban forest ($z_34$ = 9.86, *P* < 0.001, Fig.
+By definition, the second nearest web is further from the focal web than the nearest neighbor ($z_34$ = 14.65, *P* \< 0.001).
+There was a significant interaction between neighbor number and habitat -- the second nearest neighbor was significantly further from the focal web than the first nearest neighbor in the urban center, but not the urban forest ($z_34$ = 9.86, *P* \< 0.001, Fig.
 3d).
@@
 
-### Environmental differences between habitats
+```{r main, fig.width = 6.85, fig.height = 7, dpi = 300}
+main <- readRDS("figures/main.Rds")
+main
+```
 
-All environmental predictors assessed within a 100-meter radius of the focal web varied by habitat (Table 3).
-Site tree cover was lower in the urban center than the urban forest with five urban center sites with zero tree cover ($z_21$ = -14.50, *P* < 0.001).
-The urban center sites had higher impervious cover while all but four sites were zero in the urban forest ($z_21$ = 14.51, *P* < 0.001).
-The urban center sites also had higher spectral radiance ($z_21$ = 3.08, *P* = 0.002) and artificial light at night radiance ($z_21$ = 22.46, *P* < 0.001).
-Overall plant species richness was lower in the urban center than the urban forest ($z_21$ = -7.67, *P* < 0.001).
-Similarly, spiders used a lower diversity of plants as substrates in the urban center (mean ± se = 1.42 ± 0.15 species) than the urban forest (mean ± se = 2.7 ± 0.26 species, $z_21$ = -2.08, *P* = 0.037).
-Site patch area was smaller in the urban center ($z_21$ = -374.2, *P* < 0.001).
-Road disturbance ($z_21$ = 39.19, *P* < 0.001), highway disturbance ($z_21$ = 9.39, *P* < 0.001), and road density ($z_21$ = -374.2, *P* < 0.001) were higher for urban center sites than sites in the urban forest.
-The urban forest sites had an average total trail length of 113 ± 11.3 meters within 100 meters of the focal web.
+**Fig.
+3** Comparison of search distance (a), the number of webs (b) and spiders (c) in a 10-meter radius of the focal web, the distance from the focal web to the first and second (d) nearest neighbors, and web height (e) by habitat - urban center vs urban forest.
+Grey jittered points represent the raw data while black points and error bars represent the mean and 95% confidence intervals, respectively, from model predictions.
+Models were either Poisson Generalized Linear Models (a-c) or Poisson Generalized Linear Mixed Effect Models with site as a random factor (d-f).
+Asterisks indicate significance level (\*\*\* *P* \< 0.001; \*\* *P* \< 0.01; \* *P* \< 0.05).
+We searched shorter distances from the start site to the focal web (a), found more webs (b) and spiders (c) in a 10-meter radius of the focal web, measured shorter distances between the focal web and the two nearest neighbors (d), and recorded shorter web heights (e) in the urban center than the urban forest
+
+We completed a Clark and Evans test [@clark_evans_1954] that determines whether aggregation is due to increased density or clumping of individuals.
+A ratio value significantly below 1 suggests clumping, while values that do not significantly differ from 1 indicate random spacing.
+We found that webs are aggregated in the urban center (R = 0.47, P \< 0.01) and uniform in the urban forest (R = 1.24, P \> 0.05).
+We conclude that aggregations formed for reasons other than increased spider density.
 
@@
 
-To explore potential mechanisms of variation in spatial patterns, we looked for correlations between response variables (number of webs, number of spiders, nearest neighbor distance, and web height) and environmental predictors overall and within each habitat (Table 4, Table S2, Fig.
+To explore potential environmental factors that might influence our observed variation in spatial patterns, we looked for correlations between response variables (number of webs, number of spiders, nearest neighbor distance, and web height) and environmental predictors overall and within each habitat (Table 3, Table S3, Fig.
 4-5).
 
-The top models for the number of webs and the number of spiders yielded similar results (Table 4, Fig.
+**Table 3** Results of the top models after AIC model selection from Poisson Generalized Linear Models with the environmental predictors for data overall and subset by habitat (urban center and urban forest).
+Asterisks indicate significance level (\*\*\* *P* \< 0.001; \*\* *P* \< 0.01; \* *P* \< 0.05)
+
+```{r pred_table, fig.width = 6.85, dpi = 300}
+knitr::include_graphics("/Users/bjpessman/Documents/phd_research_code/Agelenopsis_aggregation/manuscript/figures/pred_table.png")
+```
+
+*Abundance* -- The top models for the number of webs and the number of spiders yielded similar results (Table 3, Fig.
 4).
-For both measures of abundance, the urban forest subset retained no predictors (Table 4) while the urban center showed a decrease in abundance with increasing plant species richness, patch area, highway disturbance, and road length (Table 4, Fig.
+For both measures of abundance, the urban forest subset retained no predictors (Table 3) while the urban center showed a decrease in abundance with increasing plant species richness, patch area, highway disturbance, and road length (Table 3, Fig.
 4).
-The model average for the number of webs subset by urban center suggested similar results (Table S2).
-Plant species richness and highway disturbance both had a negative relationship with abundance measures for the overall data set (Table 4, Fig.
-S11).
-Interestingly, the top model of web abundance retained road disturbance and suggested a positive relationship overall (Table 4, Fig.
-S11).
+The model average for the number of webs subset by urban center suggested similar results (Table S3).
+Plant species richness and highway disturbance both had a negative relationship with abundance measures for the overall data set (Table 3, Fig.
+S12).
+Interestingly, the top model of web abundance retained road disturbance and suggested a positive relationship overall (Table 3, Fig.
+S12).
 
-Overall, spiders are closer together when plant species richness is low and when road disturbance is high (Table 4, Fig.
-S11).
-On the other hand, less tree cover, lower road and highway disturbance, and greater plant species richness are associated with nearness in the urban forest (Table 4, Fig.
+```{r pred_abund, fig.width = 6.85, fig.height = 7, dpi = 300}
+predictors_abund <- readRDS("figures/predictors_abund.Rds")
+predictors_abund
+```
+
+**Fig.
+4** Significant correlations between measures of abundance (number of webs and spiders) and the environmental predictors for the urban center subset.
+Spectral radiance and road disturbance were dropped from both models of abundance for the urban center subset after AIC model selection.
+All environmental predictors of abundance were dropped from the urban forest subset.
+The regression lines and shaded regions represent the predictions and 95% confidence intervals (respectively) from the top Poisson Generalized Linear Model after AIC selection.
+The points represent the raw data.
+Asterisks indicate significance level (\*\*\* *P* \< 0.001; \*\* *P* \< 0.01; \* *P* \< 0.05)
+
+*Aggregation* -- Spiders were closer together across habitats when plant species richness was low and when road disturbance was high (Table 3, Fig.
+S12).
+In the urban forest subset, less tree cover, lower road and highway disturbance, and greater plant species richness were associated with nearness (Table 3, Fig.
 5), however, this model was a poor fit ($R^2$ = 0.037).
-Urban center spiders are more aggregated where plant species richness, spectral radiance, and road length are high (Table 4, Fig.
+Urban center spiders were more aggregated where plant species richness, spectral radiance, and road length are high (Table 3, Fig.
 5).
-The model average for the nearest neighbor distance in the urban center corroborates these findings and adds that webs are clumped when patch area is larger (Table S2).
+The relationship between nearest neighbor distance and plant species richness is opposite when analyzed across habitats and within the urban subset.
+This is likely do to the differences in plant species richness and aggregation between habitats -- the urban center had low neighbor distance and plant diversity while the urban forest had high neighbor distance and plant diversity.
+The model average for the nearest neighbor distance in the urban center corroborates the findings of the top model and adds that webs were clumped when patch area was larger (Table S3).
 
-Further, webs are built higher overall when the number of plant species is higher (Table 4, Fig.
-S11).
-A trend also suggests that lower webs are associated with higher road disturbance, although this result is not significant (Table 4, Fig.
-S11).
-In the urban forest, web height is positively related to tree cover (Table 4).
-While plant species richness was included in the top model, it did not vary by web height in the urban center (Table 4).
-We see similar results from the model averages for web height (Table S2).
-Despite the addition of predictors under the model averages, none of the added predictors varied by web height in their respective data sets (Table S2).
+```{r pred_agg, fig.width = 6.85, fig.height = 7, dpi = 300}
+predictors_agg <- readRDS("figures/predictors_agg.Rds")
+predictors_agg
+```
 
-For statistical analysis and figures of response variables by land cover class, see supplemental material (Table S3, Fig.
+**Fig.
+5** Significant correlations between the aggregation measure (nearest neighbor distance) and the environmental predictors for the urban center subset (plant species richness, spectral radiance, and total road length) and the urban forest subset (plant species richness, tree cover, and road and highway disturbance).
+All other environmental predictors were dropped from models of nearest neighbor distance after AIC model selection.
+The regression lines and shaded regions represent the predictions and 95% confidence intervals (respectively) from the top Poisson Generalized Linear Model after AIC selection.
+The points represent the raw data.
+Asterisks indicate significance level (\*\*\* *P* \< 0.001; \*\* *P* \< 0.01; \* *P* \< 0.05)
+
+*Web Height* -- Webs were built higher overall when the number of plant species is higher (Table 3, Fig.
 S12).
-Following Likelihood Ratio tests, we find that all response variables significantly vary by land cover class (Table S3).
-There was no difference in search distance between deciduous forest, urban medium intensity and urban low intensity.
-However, we searched significantly further in woody wetlands and significantly shorter in urban high intensity (Fig.
-S12a).
-The number of webs and spiders only varied by habitat - urban low, medium, and high intensity had more webs and spiders than deciduous forest or woody wetlands (Fig.
-S12a-b).
+A trend also suggests that lower webs were associated with higher road disturbance, although this result is not significant (Table 3, Fig.
+S12).
+In the urban forest, web height is positively related to tree cover (Table 3).
+While plant species richness was included in the top model, it did not vary by web height in the urban center (Table 3).
+We see similar results from the model averages for web height (Table S3).
+Despite the addition of predictors under the model averages, none of the added predictors varied by web height in their respective data sets (Table S3).
+
+For statistical analysis and figures of response variables by land cover class, see supplemental material (Table S2, Fig.
+S10).
+Following Likelihood Ratio tests, we find that all response variables significantly vary by land cover class (Table S2).
+There was no difference in search distance between urban medium-intensity, urban low-intensity, and deciduous forest.
+However, we searched significantly shorter in urban high-intensity and significantly further in woody wetlands (Fig.
+S10a).
+The number of webs and spiders only varied by habitat - urban low-, medium-, and high-intensity had more webs and spiders than deciduous forest or woody wetlands (Fig.
+S10b-c).
+For the urban intensities, web distance was shortest at low intensities and furthest at medium intensities with high urban intensity suggest web height between low and medium intensities (Fig.
+S10d).
 Nearest neighbor distance was shorter for woody wetlands than deciduous forest (Fig.
-S12d).
-For the urban intensities, web distance was shortest at low intensities and furthest at medium intensities with high urban intensity suggest web height between low and medium intensities (Fig.
-S12d).
+S10d).
 Lastly, web height showed no difference between land cover class with pairwise comparisons (Fig.
-S12e).
+S10e).
 
@@
 
-### Spiders are more abundant in the urban center
+The two urban habitats that we studied here -- an urban forest and an urban center -- significantly differed by the selected environmental conditions.
+The urban forest sites had higher tree cover, plant diversity, and patch area.
+On the other hand, the urban center exhibited higher impervious cover, light at night, surface temperature, road and highway disturbance, and total road length.
+These urban habitats each host *Agelenopsis pennsylvanica*, but the spatial patterns displayed by this funnel-weaving spider vary considerably.
+The spiders are more abundant, aggregated, and build lower webs in the urban center.
+We hypothesized that many of the environmental conditions that are distinct between the habitats may also be influencing such differences.
+We found that spatial patterns were often retlated to plant species richness and disturbance from road and highway traffic.
+
+### Spiders are more abundant and aggregated with lower webs in the urban center
 
 Both webs and spiders of *A.
-pennsylvanica* were more abundant in the urban center than the urban forest.
+pennsylvanica* were more abundant and aggregated in the urban center than the urban forest.
 Shorter search distances to the focal web corroborates this finding, as previous studies have used search distance as an estimate of abundance [@buckland_2005, @kral_2018].
+
+Higher abundance of animals in urban habitats may reflect a higher tolerance of urban conditions and disturbances.
 Tolerance of urban ecosystems is dependent on the ecology and behavior of the organism, such as being a generalist consumer [@sol_2013; @bang_2011], and the scale of the measurements being collected [@lowe_2018; @philpott_2014], resulting in conflicting findings in the literature.
-While arthropods are generally found to decline [@wagner_2020; @piano_2020], generalists and thermally flexible species are more likely to be urban exploiters than specialists or thermally inflexible species [@callaghan_2021].
+We have observed *A pennsylvanica* attacking a wide variety of arthropod prey with no evidence of specialization of a particular type (personal observations).
+Thus, we suggest that *A.
+pennsylvanica* is a generalist predator.
+While arthropods are generally found to decline in urban environments [@wagner_2020; @piano_2020], generalists are more likely to be urban exploiters than specialists [@callaghan_2021].
 For example, *Nephila plumipes*, a generalist predator, was found to abundantly occupy urban habitats where prey abundance supported greater numbers of spiders [@lowe_2016].
+
 Prey abundance has been repeatedly found to be a strong predictor of spider abundance [@trubl_2012, @parkinson_2020, @harwood_2001].
-While we did not measure intra- and interspecific interactions between the two urban habitats studied here -- although future research on this system should test these biotic factors -- , we did find several environmental factors that may predict spider abundance directly or indirectly through environmental effects on prey, predator, or competitor abundance or dispersal limitations.
+Although we might hypothesize higher prey availability in the urban forest, we observed far greater potential for competition from other spider species in the urban forest than the urban center.
+In the urban center, *A.
+pennsylvanica* appear to dominate spider communities.
+Prey abundance, then, may play a role in our observed differences in spider abundance between the urban center and the urban forest.
 
-The environmental conditions assessed here only correlated with web and spider abundance in the urban center, with no strong environmental effects on abundance in the urban forest.
-Variation in abundance per urban forest site was low, only ranging from two to four webs and one to three spiders.
-On the other hand, abundance for webs ranged from one to 73 webs and one to 22 spiders per urban center site.
-Additionally, urban forest abundance may be better predicted by factors not assessed here, such as prey and predator abundance or dispersal limitation [@harwood_2001; @bonte_et_al_2003].
-In the urban center, web and spider abundance was higher when plant species richness, patch area, highway disturbance, and road length were lower.
-*Agelenopsis pennsylvanica* rely heavily on vibrations to capture prey [@riechert_maupin_1998], court potential mates [@singer_2000], and potentially evade predators [@riechert_hedrick_1990].
-Thus, we suspect that vibratory noise may play a key role in web site selection, choosing sites that mitigate these effects.
-We show that webs and spiders are more abundant in urban center sites that had lower highway disturbance and total length of road in a 100-meter radius.
-Although research on the effects of noise on arthropod behavior has focused on acoustic rather than vibratory noise [@roberts_howard_2022], studies have found strong negative effects of acoustic and vibratory noise on arthropod behavior [@carosi_et_al_2019; @bunkley_et_al_2017].
-A recent study shows that the orb-weaving spider, *Larinioides sclopetarius* is able to detect airborne sound that induces vibrations in the web [@zhou_et_al_2022].
-
-Since different plants transmit vibrations differently [@cocroft_et_al_2006], selective spiders in urban habitats may choose plants as web substrates that reduce vibratory noise, either human-caused or natural.
-Our results show that spiders are more abundant when plant species richness is lower.
-The urban center sites were covered in grass lawns and managed landscaping that usually had few plant species present, but in high abundance.
-Sites with lower plant diversity may have few plant species that are highly preferred, leading to higher spider abundance.
-Research has shown mixed but often positive effects of plant diversity on spider abundance [@malumbres_et_al_2013; @koricheva_et_al_2000], suggesting that plant community composition may play a vital, yet context-specific role.
-To better understand the role that plant species play in abundance would require comparing plant communities between patches used by spiders versus those devoid of spiders.
-We additionally found that smaller patches were associated with higher spider abundance.
-While arthropods overall tend to decrease in abundance as smaller patch sizes, habitat generalists and edge specialists can be found at greater abundance in smaller patches [@martinson_fagan_2014].
-
-### Spiders are more aggregated in the urban center
-
-Both the first and second nearest neighbor webs to the focal web were closer in the urban center than the urban forest.
-Multiple reports have found spider aggregations in urban habitats [@trubl_2012; @mammola_et_al_2018], often related directly or indirectly to the abundance of prey.
+Multiple reports have found spider aggregations in urban habitats [@trubl_2012; @mammola_et_al_2018], another spatial measure that is often related directly or indirectly to the abundance of prey.
 Territoriality, especially over prey resources, often drives regular (and non-random) spacing of solitary species [@riechert_1974b], but aggregations can form when abundant resources allow for increased tolerance of neighbors [@gillespie_1987].
@@
 pennsylvanica* were more aggregated in the urban center where light at night radiance was higher than the urban forest.
-Future research should address both direct and indirect indicators of prey abundance in aggregations of spiders in urban habitats.
+Thus, future research should test the impact of prey abundance and competition on spider abundance and aggregation in urban habitats.
 
-To determine whether nearness of neighbors in the urban center was the result of aggregation or just increased density from higher abundance, we completed calculations described by Clark and Evans [@clark_evans_1954].
-This calculation compares the measured nearest neighbor distance to the expected distance if animals were evenly spaced within an area.
-A ratio value significantly below 1 suggests clumping, while values that do not significantly differ from 1 indicate random spacing.
-For each site, we estimated the total search area by adding the length of path searched multipled by four meters (for searching two meters on either side of the central path line) and the area of the 10 meter radius circular site.
-We subtracted the overlap in the search path and site by subtracting four * 10 meters.
-We find that webs are clumped in the urban center (R = 0.47, P < 0.01) and uniform in the urban forest (R = 1.24, P > 0.05).
-We conclude that aggregations formed for reasons other than increased spider density.
-
-We found significant relationships between environmental predictors and nearest neighbor distance in both urban habitats.
-Urban center and forest spiders responded differently in aggregative behavior in response to traffic measures that may reflect vibratory noise -- neighboring urban forest spiders were closer at lower road and highway disturbance and urban center spiders aggregated more when there was more road within 100 meters of the focal web, but did not vary by road or highway disturbance.
-Perhaps noise negatively affects urban forest spiders, encouraging spiders to inhabit areas further from noise sources and reducing space between neighbors.
-more than spiders reared in or descended from the urban center where noise is greater.
-Many spiders are thought to be plastic in the structure and tuning of their webs [@mortimer_2016; @blamires_2010], and urban exploiters are often fast to adjust to changing conditions [@kralj_2017], so spiders reared in or descended from spiders in the urban center might be better able to tune their webs to decrease vibrations, although this hypothesis requires further testing.
-It will also be important to differentiate whether these differences in behavior between environments is based on developmental exposure, behavioral plasticity, or genetic differentiation.
-
-Higher plant species richness led to greater aggregation for spiders in both the urban center and the urban forest.
-We speculate that greater aggregation on more diverse plant communities may suggest that *A.
-pennsylvanica* prefers a certain plant or type of plant, especially in the urban center where we observed similar plants clumped in space.
-In the urban forest, we also found nearer neighbors under less tree cover.
-A study that measured invertebrate abundance after manipulating tree cover found that newly formed tree gaps have greater vegetation height and coverage and increased soil moisture and temperature, all of which led to an overall increase in invertebrate abundance [@perry_2018].
-Similar results have been found with spider communities in particular [@vcernecka_2020].
-Since spider aggregations tend to occur where prey abundance is higher, we might predict that lower tree cover might indirectly increase spider aggregation through an increase in prey abundance.
-Lastly, spiders in the urban center were more aggregated at sites with higher spectral radiance (a measure of surface temperature).
-Urban centers tend to be warmer on average compared to surrounding areas due to heat trapping via pavement in a phenomenon called the Urban Heat Island Effect [@johnson_et_al_2020].
-Aggregation formation in warmer sites could be the result of preference for or acclimation to warmer areas [@meineke_et_al_2013] or perhaps aggregation occurs at limited thermal refuges [@riechert_1974b].
-
-### Web heights were lower in the urban center
-
-We found that the webs of urban center spiders were built lower than webs in the urban forest, and this result was independent of the height of the substrate.
+We also found that the webs of urban center spiders were built lower than webs in the urban forest, and this result was independent of the height of the substrate.
 Webs may vary in height based on the type of prey being ensnared.
-We have observed *Agelenopsis* spiders capture both flying, hopping, and crawling insects.
+We have observed *Agelenopsis* spiders capture flying, hopping, and crawling insects.
 Arthropod community structure can be highly variable between urban habitats [@bang_faeth_2011], and urban centers and urban forests may support different types of prey items for *A.
@@
 In the urban center where lawns are mowed frequently and ornamental plants are regularly pruned, spiders could maintain lower webs to conserve energy from frequent rebuilding.
-Urban forests likely support (and act as a refuge for) many ground dwelling vertebrates, whose movement along the forest floor could frequently damage lower webs.
-Greater tree coverage in the urban forest predict higher webs may further suggest that small mammal movement could destroy low webs as areas with greater tree cover may provide protection and food resources for small mammals [@sarkar_2022].
+
+Additionally, urban forests likely support (and act as a refuge for) many ground dwelling vertebrates, whose movement along the forest floor could frequently damage lower webs.
+Greater tree coverage in the urban forest predicted higher webs, which may further suggest that small mammal movement could destroy low webs as areas with greater tree cover may provide protection and food resources for small mammals [@sarkar_2022].
 Future research should assess prey type available and small animal abundance and movement between these two habitats.
@@
 
+### Several environmental predictors relate to spatial patterns
+
+We found that webs and spiders were more abundant (in the urban center) and more aggregated as plant species richness decreased.
+The urban center sites were covered in grass lawns and managed landscaping that usually had few plant species present, but in high abundance.
+Sites with lower plant diversity may have few plant species that are highly preferred, leading to higher spider abundance.
+Research has shown mixed but often positive effects of plant diversity on spider abundance [@malumbres_et_al_2013; @koricheva_et_al_2000], suggesting that plant community composition may play a vital, yet context-specific role.
+To better understand the role that plant species play in abundance would require comparing plant communities between patches used by spiders versus those devoid of spiders.
+We speculate that greater aggregation on more diverse plant communities may suggest that *A.
+pennsylvanica* prefers a certain plant or type of plant, especially in the urban center where we observed similar plants clumped in space.
+
+We found further support for the importance of plant life as urban forest spiders were more aggregated at sites with less tree cover.
+A study that measured invertebrate abundance after manipulating tree cover found that newly formed tree gaps have greater vegetation height and coverage and increased soil moisture and temperature, all of which led to an overall increase in invertebrate abundance [@perry_2018].
+Similar results have been found with spider communities in particular [@vcernecka_2020].
+Since spider aggregations tend to occur where prey abundance is higher, we might predict that lower tree cover indirectly increases spider aggregation through an increase in prey abundance.
+
+Disturbance from roads and highways also seemed to play a role in spider spatial patterns.
+We show that webs and spiders are more abundant in urban center sites that had lower highway disturbance.
+Living in close proximity to high-traffic roads is likely to affect the vibratory environment that the spider is exposed to.
+*Agelenopsis pennsylvanica* rely heavily on vibrations to capture prey [@riechert_maupin_1998], court potential mates [@singer_2000], and potentially evade predators [@riechert_hedrick_1990].
+Thus, we suspect that vibratory noise may impact web site selection, choosing sites that mitigate these effects.
+Also, selective spiders in urban habitats may choose plants as web substrates that reduce vibratory noise since different plants transmit vibrations differently [@cocroft_et_al_2006].
+Although most research on the effects of noise on arthropod behavior has focused on acoustic rather than vibratory noise [@roberts_howard_2022], some studies have found strong negative effects of acoustic and vibratory noise on arthropod behavior [@carosi_et_al_2019; @bunkley_et_al_2017].
+A recent study shows that the orb-weaving spider, *Larinioides sclopetarius* is able to detect airborne sound that induces vibrations in the web [@zhou_et_al_2022].
+
+Lower road and highway disturbance was associated with larger spider aggregations in the urban forest, but had no effect on urban center spiders.
+Perhaps noise negatively affects urban forest spiders -- encouraging spiders to inhabit areas further from noise sources and reducing space between neighbors.
+Many spiders are thought to be plastic in the structure and tuning of their webs [@mortimer_2016; @blamires_2010], and urban exploiters are often fast to adjust to changing conditions [@kralj_2017], so spiders reared in or descended from spiders in the urban center might be better able to tune their webs to decrease vibrations, although this hypothesis requires further testing.
+It will also be important to differentiate whether these differences in behavior between environments is based on developmental exposure, behavioral plasticity, or genetic differentiation.
+
+More road length in the 100-meter radius resulted in fewer but more aggregated urban center webs and spiders.
+Total road length could be another indirect measure of vibratory noise and/or represent dispersal barriers.
+High traffic roads may increase mortality of dispersing spiders via collisions with vehicles, or passing cars may influence wind currents making aerial dispersal difficult [@martin_et_al_2019].
+Higher spider abundance in smaller patches may be more evidence for the role of environmental barriers.
+Furthermore, small patch areas may be a preferred habitat of edge specialists [@martinson_fagan_2014], as we suspect *A.
+pennsylvanica* may be.
+
+We note that urban forest web and spider abundance did not correlate with any of the selected environmental conditions, potentially due to low variation.
+For example, only two to four webs and one to three spiders were found per site in the urban forest compared to one to 73 webs and one to 22 spiders in the urban center.
+Alternatively, urban forest abundance may be better predicted by factors not assessed here, such as prey and predator abundance or dispersal limitation [@harwood_2001; @bonte_et_al_2003].
+
+Lastly, spiders in the urban center were more aggregated at sites with higher spectral radiance (a measure of surface temperature).
+Urban centers tend to be warmer on average compared to surrounding areas due to heat trapping via pavement in a phenomenon called the Urban Heat Island Effect [@johnson_et_al_2020].
+Aggregation formation in warmer sites could be the result of preference for or acclimation to warmer areas [@meineke_et_al_2013] or perhaps aggregation occurs at limited thermal refuges [@riechert_1974b].
+We have shown that human-caused environmental changes correlate with spider spatial patterns, but there are likely many other forms of human disturbance than those tested here.
+
 ## Conclusions
 
-Our study shows that a solitary, generalist predator is more abundant and aggregated with lower web height in an urban center compared to an urban forest -- habitats that vary significantly in environmental condition.
-While we did not measure community-level interactions among organisms, correlations between spatial pattern and environmental condition indirectly indicate that inter- and intraspecific interactions, especially prey abundance, may be essential for predicting and monitoring spider aggregative behavior.
+Our study shows that a solitary, generalist predator is more abundant and aggregated with lower web height in an urban center compared to an urban forest -- habitats that vary significantly in environmental conditions.
+We did not measure community-level interactions among organisms, such as the effects of prey abundance.
+However, correlations between spatial pattern and environmental condition indirectly indicate that such interspecific interactions may be essential for monitoring spider aggregations.
 Spider aggregations in urban centers can have medical consequences, such as dense *Lactrodectus hesperus* aggregations [@johnson_et_al_2011], and aesthetic concerns, as is the case with aggregations of *Brigittea civica* under archways of historic buildings [@mammola_et_al_2018].
@@
 \newpage
-## References {-}
-<div id="refs"></div>
+
+## References {.unnumbered}
+
+::: {#refs}
+:::
+
 \newpage
-## Figures
-**Fig. 1** Study System - *Agelenopsis pennsylvanica* (a). The web consists of a retreat where the spider waits for prey to land, fall, or walk on the web sheet (b)
 
-**Fig.
-2** Land cover raster with borders for Lincoln, Nebraska, USA city limits (dashed border), University of Nebraska-Lincoln (UNL) City Campus (solid border, a), and Wilderness Park (solid border, b) using the 2019 National Land Cover Data on Land Cover and QGIS (v.
-3.16.3-Hannover, ESRI 102704).
-For visualization and listing of study sites, see Figure S1 and Table S1, respectively
+## Statements and Declarations
 
-**Fig.
-3** Comparison of search distance (a), the number of webs (b) and spiders (c) in a 10-meter radius of the focal web, the distance from the focal web to the first (d) and second (e) nearest neighbors, and web height (f) by habitat - urban forest vs urban center.
-Grey jittered points represent the raw data while black points and error bars represent the mean and 95% confidence intervals, respectively, from model predictions.
-Models were either Poisson Generalized Linear Models (a-c) or Poisson Generalized Linear Mixed Effect Models with site as a random factor (d-f).
-Asterisks (A-B) indicate significance level (*** *P* < 0.001; ** *P* < 0.01; * *P* < 0.05).
-We searched shorter distances from the start site to the focal web (a), found more webs (b) and spiders (c) in a 10-meter radius of the focal web, measured shorter distances between the focal web and the two nearest neighbors (d-e), and recorded shorter web heights (f) in the urban center than the urban forest
+### Funding
 
-**Fig.
-4** Significant correlations between measures of abundance (number of webs and spiders) and the environmental predictors for the urban center subset.
-Spectral radiance and road disturbance were dropped from both models of abundance for the urban center subset after AIC model selection.
-All environmental predictors of abundance were dropped from the urban forest subset.
-The regression lines and shaded regions represent the predictions and 95% confidence intervals (respectively) from the top Poisson Generalized Linear Model after AIC selection.
-The points represent the raw data.
-Asterisks indicate significance level (*** *P* < 0.001; ** *P* < 0.01; * *P* < 0.05)
+This material is based upon work supported by the National Science Foundation Graduate Research Fellowship under Grant No. 25-0506-0233-001 awarded to BP.
 
-**Fig.
-5** Significant correlations between the aggregation measure (nearest neighbor distance) and the environmental predictors for the urban forest subset (plant species richness, tree cover, and road and highway disturbance) and the urban center subset (plant species richness, spectral radiance, and total road length).
-All other environmental predictors were dropped from models of nearest neighbor distance after AIC model selection.
-The regression lines and shaded regions represent the predictions and 95% confidence intervals (respectively) from the top Poisson Generalized Linear Model after AIC selection.
-The points represent the raw data.
-Asterisks indicate significance level (*** *P* < 0.001; ** *P* < 0.01; * *P* < 0.05)
+### Competing Interests
 
-## Tables
+The authors have no relevant financial or non-financial interests to disclose.
 
-**Table.
-1** Examples of studies elucidating the mechanisms behind spider aggregations.
-Mechanisms are categorized by inter- and intraspecific interactions, environmental factors, and dispersal, but it is important to note that these categories are likely inter-related.
-The table is meant to provide examples, rather than represent a full review of studies.
-Several aggregation mechanisms were studied in urban habitats.
-
-**Table.
-2** Landscape variables for Lincoln (Nebraska, USA) City Limits, University of Nebraska-Lincoln (UNL) City Campus, and Wilderness Park collected from the National Land Cover Database (2016 Tree Cover, 2019 Impervious Cover, 2019 Land Cover), the Landsat-7 World Reference System-2 (Band 6, path 28, row 32, taken September 2, 2020), and the 2020 Visible Infrared Imaging Radiometer Suite (VIIRS) using QGIS (v.
-3.16.3-Hannover, ESRI 102704)
-
-**Table 3** Mean and standard error of environmental predictors collected in 100 meter buffers of each focal web by habitat
-
-**Table.4** Results of the top models after AIC model selection from Poisson Generalized Linear Models with the environmental predictors for data overall and subset by habitat (urban forest and urban center).
-Asterisks indicate significance level (*** *P* < 0.001; ** *P* < 0.01; * *P* < 0.05)
+### Author Contributions

### 2023-01-08 manuscript/supplemental.Rmd
Lots of changes

@@
 ---
+# Urbanization affects web abundance and aggregation of a funnel-weaving spider, *Agelenopsis pennsylvanica*
+
+Urban Ecosystems
+
+Brandi J. Pessman ^1\*^, Madison Hays ^1^, Earl Agpawa ^2^, Eileen A. Hebets ^1^
+
+^1^ University of Nebraska-Lincoln, Department of Biological Sciences, Lincoln, Nebraska, United States
+
+^2^ University of Nebraska-Lincoln, Department of Entomology, Lincoln, Nebraska, United States
+
+^\*^ Corresponding Author Email: [bjpessman\@gmail.com](mailto:bjpessman@gmail.com){.email}
 
@@
 **Fig.
-S2** Wilderness Park and University of Nebraska-Lincoln (UNL) City Campus sites F01 (a) and C23 (b), respectively, where the circled flags indicate individiual webs of *Agelenopsis pennsylvanica*
+S2** University of Nebraska-Lincoln (UNL) City Campus (urban center) and Wilderness Park (urban forest) sites C23 (a) and F01 (b), respectively, where the circled flags indicate individual webs of *Agelenopsis pennsylvanica*
+
+\newpage
+
+```{r intersections, dpi = 300}
+knitr::include_graphics("/Users/bjpessman/Documents/phd_research_code/Agelenopsis_aggregation/manuscript/figures/intersections.png")
+```
+
+**Fig.
+S3** Intersections randomly chosen from as starting sites.
+The University of Nebraska-Lincoln (UNL) City Campus intersections (a) were selected from sidewalk and road intersections that met from the four cardinal directions.
+We selected Wilderness Park intersections (b) from trail intersections where 3 or more paths meet.
+Sites that we used as starting sites are indicated in red
+
+\newpage
+
+```{r paths, dpi = 300}
+knitr::include_graphics("/Users/bjpessman/Documents/phd_research_code/Agelenopsis_aggregation/manuscript/figures/paths.png")
+```
+
+**Fig.
+S4** Paths walked from the starting site until the first occupied web (the focal web).
+Site ID is labeled at the focal web site.
+University of Nebraska-Lincoln (UNL) City Campus sites (Urban Center, a) are outlined in orange and Wilderness Park sites (Urban Forest, b) are outlined in green
 
@@
 **Fig.
-S3** Impervious cover raster with borders for Lincoln, Nebraska, USA city limits (dashed border), University of Nebraska-Lincoln (UNL) City Campus (solid border, a), and Wilderness Park (solid border, b) using the 2019 National Land Cover Data on Impervious Cover and QGIS (v.
+S5** Impervious cover raster with borders for Lincoln, Nebraska, USA city limits (dashed border), University of Nebraska-Lincoln (UNL) City Campus (Urban Center, solid border, a), and Wilderness Park (Urban Forest, solid border, b) using the 2019 National Land Cover Data on Impervious Cover and QGIS (v.
 3.16.3-Hannover, ESRI 102704)
@@
 **Fig.
-S4** Tree cover raster with borders for Lincoln, Nebraska, USA city limits (dashed border), University of Nebraska-Lincoln (UNL) City Campus (solid border, a), and Wilderness Park (solid border, b) using the 2016 National Land Cover Data on Tree Cover and QGIS (v.
+S6** Tree cover raster with borders for Lincoln, Nebraska, USA city limits (dashed border), University of Nebraska-Lincoln (UNL) City Campus (Urban Center, solid border, a), and Wilderness Park (Urban Forest, solid border, b) using the 2016 National Land Cover Data on Tree Cover and QGIS (v.
 3.16.3-Hannover, ESRI 102704)
@@
 **Fig.
-S5** Spectral radiance raster with borders for Lincoln, Nebraska, USA city limits (dashed border), University of Nebraska-Lincoln (UNL) City Campus (solid border, a), and Wilderness Park (solid border, b) using the satellite image of path 28, row 32 of the Landsat-7 World Reference System-2 (Band 6, September 2, 2020) and QGIS (v.
+S7** Spectral radiance raster with borders for Lincoln, Nebraska, USA city limits (dashed border), University of Nebraska-Lincoln (UNL) City Campus (Urban Center, solid border, a), and Wilderness Park (Urban Forest, solid border, b) using the satellite image of path 28, row 32 of the Landsat-7 World Reference System-2 (Band 6, September 2, 2020) and QGIS (v.
 3.16.3-Hannover, ESRI 102704)
@@
 **Fig.
-S6** Artificial light at night radiance raster with borders for Lincoln, Nebraska, USA city limits (dashed border), University of Nebraska-Lincoln (UNL) City Campus (solid border, a), and Wilderness Park (solid border, b) using the 2020 Visible Infrared Imaging Radiometer Suite (VIIRS) and QGIS (v.
+S8** Artificial light at night radiance raster with borders for Lincoln, Nebraska, USA city limits (dashed border), University of Nebraska-Lincoln (UNL) City Campus (Urban Center, solid border, a), and Wilderness Park (Urban Forest, solid border, b) using the 2020 Visible Infrared Imaging Radiometer Suite (VIIRS) and QGIS (v.
 3.16.3-Hannover, ESRI 102704)
-
-\newpage
-
-```{r intersections, dpi = 300}
-knitr::include_graphics("/Users/bjpessman/Documents/phd_research_code/Agelenopsis_aggregation/manuscript/figures/intersections.png")
-```
-
-**Fig.
-S7** Intersections randomly chosen from as starting sites.
-We selected Wilderness Park intersections (left) from trail intersections where 3 or more paths meet.
-The University of Nebraska-Lincoln (UNL) City Campus intersections (right) were selected from sidewalk and road intersections that met from the four cardinal directions.
-Sites that we used as starting sites are indicated in red
-
-\newpage
-
-```{r paths, dpi = 300}
-knitr::include_graphics("/Users/bjpessman/Documents/phd_research_code/Agelenopsis_aggregation/manuscript/figures/paths.jpg")
-```
-
-**Fig.
-S8** Paths walked from the starting site until the first occupied web (the focal web).
-Site ID is labeled at the focal web site.
-Wilderness Park sites (left) are outlined in green, and University of Nebraska-Lincoln (UNL) City Campus sites (right) are outlined in orange
 
@@
 S9** Plant species found within a ten-meter radius of focal web at each site.
-Plant species at each site are underneath the colored and labeled site indicator (orange for University of Nebraska-Lincoln (UNL) City Campus and green for Wilderness Park).
+Plant species at each site are underneath the colored and labeled site indicator (orange for the urban center (UNL City Campus) and green for the urban forest (Wilderness Park)).
 Plant species used as web substrates are highlighted in yellow.
 These data do not suggest equivalent prevalence of each species, but rather list available substrates for spiders
-
-\newpage
-
-```{r substrates, dpi = 300}
-knitr::include_graphics("/Users/bjpessman/Documents/phd_research_code/Agelenopsis_aggregation/manuscript/figures/substrate_plot.png")
-```
-
-**Fig. S10** Representation of web substrates by class. Green shades indicate plant material classes, and orange indicates non-plant materials
-
-\newpage
-
-```{r pred_overall, fig.width = 6.85, fig.height = 7, dpi = 300}
-predictors_overall <- readRDS("figures/predictors_overall.Rds")
-predictors_overall
-```
-
-**Fig.S11** Significant correlations between response variables (number of webs, number of spiders, nearest neighbor distance, and web height) and the environmental predictors (plant species richness and road disturbance and highway disturbance) for the whole data set.
-The regression lines and shaded regions represent the predictions and 95% confidence intervals (respectively) from the top Poisson Generalized Linear Model after AIC selection.
-Predictor variables not included in the top model are shaded grey.
-The points represent the raw data.
-Asterisks indicate significance level (*** *P* < 0.001; ** *P* < 0.01; * *P* < 0.05)
 
@@
 **Fig.
-S12** Comparison of search distance (a), the number of webs (b) and spiders (c) in a 10-meter radius of the focal web, the distance from the focal web to the first (d) and second (e) nearest neighbors, and web height (f) by land cover class - deciduous forest, woody wetlands, urban high intensity, urban medium intensity, and urban low intensity.
+S10** Comparison of search distance (a), the number of webs (b) and spiders (c) in a 10-meter radius of the focal web, the distance from the focal web to the first nearest neighbor (d), and web height (e) by land cover class - urban high-intensity, urban medium-intensity, urban low-intensity, deciduous forest, woody wetlands.
 Land cover class was determined using the pixel category from the 2019 National Land Cover Data that the focal web site resides in.
-Grey jittered points represent the raw data while colored points (green = urban forest, orange = urban center) and error bars represent the mean and 95% confidence intervals, respectively, from Poisson Generalized Linear Model predictions.
+Grey jittered points represent the raw data while colored points (orange = urban center, green = urban forest) and error bars represent the mean and 95% confidence intervals, respectively, from Poisson Generalized Linear Model predictions.
 Unique letters indicate significance.
-See supplemental tables (S2-6) for statistical analysis
+See table S2 for statistical analysis
+
+\newpage
+
+```{r substrates, dpi = 300}
+knitr::include_graphics("/Users/bjpessman/Documents/phd_research_code/Agelenopsis_aggregation/manuscript/figures/substrate_plot.png")
+```
+
+**Fig. S11** Representation of web substrates by class. Orange indicates non-plant materials and green shades indicate plant material classes
+
+\newpage
+
+```{r pred_overall, fig.width = 6.85, fig.height = 7, dpi = 300}
+predictors_overall <- readRDS("figures/predictors_overall.Rds")
+predictors_overall
+```
+
+**Fig.S12** Significant correlations between response variables (number of webs, number of spiders, nearest neighbor distance, and web height) and the environmental predictors (plant species richness, road disturbance, and highway disturbance) for the whole data set.
+The regression lines and shaded regions represent the predictions and 95% confidence intervals (respectively) from the top Poisson Generalized Linear Model after AIC selection.
+Predictor variables not included in the top model are shaded grey.
+The points represent the raw data.
+Asterisks indicate significance level (*** *P* < 0.001; ** *P* < 0.01; * *P* < 0.05)
 
@@
 
-**Table S2** Results of model averages (all models within 2 detla AICc points) from Poisson Generalized Linear Models with the environmental predictors for data overall and subset by habitat (urban forest and urban center), where applicable.
+**Table S2** Statistical results of Likelihood Ratio Tests following Poisson Generalized Linear Models for each response variable by land cover class.
+Significance indicated by asterisks (*** *P* < 0.001; ** *P* < 0.01; * *P* < 0.05).
+
+```{r land_stats, fig.width = 5, dpi = 300}
+knitr::include_graphics("/Users/bjpessman/Documents/phd_research_code/Agelenopsis_aggregation/manuscript/figures/land_stats.png")
+```
+
+\newpage
+
+**Table S3** Results of model averages (all models within 2 delta AICc points) from Poisson Generalized Linear Models with the environmental predictors for data overall and subset by habitat (urban center and urban forest), where applicable.
 Asterisks indicate significance level (*** *P* < 0.001; ** *P* < 0.01; * *P* < 0.05)
@@
 ```
-
-\newpage
-
-**Table S3** Statistical results of Likelihood Ratio Tests following Poisson Generalized Linear Models for each response variable by land cover class.
-Significance indicated by asterisks (*** *P* < 0.001; ** *P* < 0.01; * *P* < 0.05).
-
-```{r land_stats, fig.width = 5, dpi = 300}
-knitr::include_graphics("/Users/bjpessman/Documents/phd_research_code/Agelenopsis_aggregation/manuscript/figures/land_stats.png")
-```

### 2023-01-09 manuscript/manuscript.Rmd
Final edits before submitting

@@
 
+We completed a Clark and Evans test [@clark_evans_1954] that determines whether aggregation is due to increased density or clumping of individuals.
+A ratio value significantly below 1 suggests clumping, while values that do not significantly differ from 1 indicate random spacing.
+We found that webs are aggregated in the urban center (R = 0.47, P \< 0.01) and uniform in the urban forest (R = 1.24, P \> 0.05).
+We conclude that aggregations formed for reasons other than increased spider density.
+
 ```{r main, fig.width = 6.85, fig.height = 7, dpi = 300}
@@
 We searched shorter distances from the start site to the focal web (a), found more webs (b) and spiders (c) in a 10-meter radius of the focal web, measured shorter distances between the focal web and the two nearest neighbors (d), and recorded shorter web heights (e) in the urban center than the urban forest
-
-We completed a Clark and Evans test [@clark_evans_1954] that determines whether aggregation is due to increased density or clumping of individuals.
-A ratio value significantly below 1 suggests clumping, while values that do not significantly differ from 1 indicate random spacing.
-We found that webs are aggregated in the urban center (R = 0.47, P \< 0.01) and uniform in the urban forest (R = 1.24, P \> 0.05).
-We conclude that aggregations formed for reasons other than increased spider density.
 
@@
 
+*Web Height* -- Webs were built higher overall when the number of plant species is higher (Table 3, Fig.
+S12).
+A trend also suggests that lower webs were associated with higher road disturbance, although this result is not significant (Table 3, Fig.
+S12).
+In the urban forest, web height is positively related to tree cover (Table 3).
+While plant species richness was included in the top model, it did not vary by web height in the urban center (Table 3).
+We see similar results from the model averages for web height (Table S3).
+Despite the addition of predictors under the model averages, none of the added predictors varied by web height in their respective data sets (Table S3).
+
 ```{r pred_agg, fig.width = 6.85, fig.height = 7, dpi = 300}
@@
 Asterisks indicate significance level (\*\*\* *P* \< 0.001; \*\* *P* \< 0.01; \* *P* \< 0.05)
-
-*Web Height* -- Webs were built higher overall when the number of plant species is higher (Table 3, Fig.
-S12).
-A trend also suggests that lower webs were associated with higher road disturbance, although this result is not significant (Table 3, Fig.
-S12).
-In the urban forest, web height is positively related to tree cover (Table 3).
-While plant species richness was included in the top model, it did not vary by web height in the urban center (Table 3).
-We see similar results from the model averages for web height (Table S3).
-Despite the addition of predictors under the model averages, none of the added predictors varied by web height in their respective data sets (Table S3).
 
@@
 
-The two urban habitats that we studied here -- an urban forest and an urban center -- significantly differed by the selected environmental conditions.
-The urban forest sites had higher tree cover, plant diversity, and patch area.
-On the other hand, the urban center exhibited higher impervious cover, light at night, surface temperature, road and highway disturbance, and total road length.
+The two urban habitats that we studied here -- an urban center and an urban forest -- significantly differed by the selected environmental conditions.
+The urban center exhibited higher impervious cover, light at night, surface temperature, road and highway disturbance, and total road length.
+On the other hand, the urban forest sites had higher tree cover, plant diversity, and patch area.
 These urban habitats each host *Agelenopsis pennsylvanica*, but the spatial patterns displayed by this funnel-weaving spider vary considerably.
@@
 We hypothesized that many of the environmental conditions that are distinct between the habitats may also be influencing such differences.
-We found that spatial patterns were often retlated to plant species richness and disturbance from road and highway traffic.
+We found that spatial patterns were often related to plant species richness and disturbance from road and highway traffic.
 
@@
 pennsylvanica* were more abundant and aggregated in the urban center than the urban forest.
-Shorter search distances to the focal web corroborates this finding, as previous studies have used search distance as an estimate of abundance [@buckland_2005, @kral_2018].
+Shorter search distances to the focal web corroborate this finding, as previous studies have used search distance as an estimate of abundance [@buckland_2005, @kral_2018].
 
 Higher abundance of animals in urban habitats may reflect a higher tolerance of urban conditions and disturbances.
-Tolerance of urban ecosystems is dependent on the ecology and behavior of the organism, such as being a generalist consumer [@sol_2013; @bang_2011], and the scale of the measurements being collected [@lowe_2018; @philpott_2014], resulting in conflicting findings in the literature.
+Tolerance of urban ecosystems is dependent on the ecology and behavior of the organism, such as being a generalist consumer [@sol_2013; @bang_2011], and the scale of the measurements being collected [@lowe_2018; @philpott_2014].
 We have observed *A pennsylvanica* attacking a wide variety of arthropod prey with no evidence of specialization of a particular type (personal observations).
@@
 For example, *Nephila plumipes*, a generalist predator, was found to abundantly occupy urban habitats where prey abundance supported greater numbers of spiders [@lowe_2016].
-
-Prey abundance has been repeatedly found to be a strong predictor of spider abundance [@trubl_2012, @parkinson_2020, @harwood_2001].
+Prey abundance has been repeatedly found to be a strong predictor of spider abundance [@harwood_2001; @parkinson_2020; @trubl_2012].
 Although we might hypothesize higher prey availability in the urban forest, we observed far greater potential for competition from other spider species in the urban forest than the urban center.
@@
 Territoriality, especially over prey resources, often drives regular (and non-random) spacing of solitary species [@riechert_1974b], but aggregations can form when abundant resources allow for increased tolerance of neighbors [@gillespie_1987].
-Light at night in cities attracts insects creating pockets of increased prey abundance for spiders that may lead to spiders aggregating under such light sources [@davies_et_al_2012].
+Light at night in cities attracts insects, creating pockets of increased prey abundance for spiders that may lead to spiders aggregating under such light sources [@davies_et_al_2012].
 Although we did not measure microhabitat levels of light at night or prey abundance, *A.
@@
 We also found that the webs of urban center spiders were built lower than webs in the urban forest, and this result was independent of the height of the substrate.
-Webs may vary in height based on the type of prey being ensnared.
+One possible explanation for this pattern is that vibratory noise promotes lower web heights.
+Vibratory noise might, for example, be dampened on a plant nearer to the ground.
+We did find a trend that showed lower web heights overall at sites with higher road disturbance, but this idea requires further testing.
+Another potential explanation is that webs may vary in height based on the type of prey being ensnared.
 We have observed *Agelenopsis* spiders capture flying, hopping, and crawling insects.
@@
 pennsylvanica*.
-Lower webs in the urban center may be ideal for more crawling prey while higher webs in the urban forest may better trap flying insects.
+Lower webs in the urban center may be ideal for more crawling prey while higher webs in the urban forest may intercept more flying insects.
 Alternatively, webs in different habitats may experience different levels of disturbance.
 In the urban center where lawns are mowed frequently and ornamental plants are regularly pruned, spiders could maintain lower webs to conserve energy from frequent rebuilding.
-
 Additionally, urban forests likely support (and act as a refuge for) many ground dwelling vertebrates, whose movement along the forest floor could frequently damage lower webs.
 Greater tree coverage in the urban forest predicted higher webs, which may further suggest that small mammal movement could destroy low webs as areas with greater tree cover may provide protection and food resources for small mammals [@sarkar_2022].
-Future research should assess prey type available and small animal abundance and movement between these two habitats.
-We speculate that vibratory noise may promote lower web heights based on a trend that showed lower web heights overall at sites with higher road disturbance.
-Perhaps vibratory noise is dampened on a plant nearer to the ground, but this idea requires further testing.
+Future research should assess the prey types available and small animal abundance and movement between these two habitats.
 
@@
 Sites with lower plant diversity may have few plant species that are highly preferred, leading to higher spider abundance.
-Research has shown mixed but often positive effects of plant diversity on spider abundance [@malumbres_et_al_2013; @koricheva_et_al_2000], suggesting that plant community composition may play a vital, yet context-specific role.
+Research has shown mixed but often positive effects of plant diversity on spider abundance [@malumbres_et_al_2013; @koricheva_et_al_2000], suggesting that plant community composition may play a vital, yet context-specific role in spider spatial patterns.
 To better understand the role that plant species play in abundance would require comparing plant communities between patches used by spiders versus those devoid of spiders.
@@
 *Agelenopsis pennsylvanica* rely heavily on vibrations to capture prey [@riechert_maupin_1998], court potential mates [@singer_2000], and potentially evade predators [@riechert_hedrick_1990].
-Thus, we suspect that vibratory noise may impact web site selection, choosing sites that mitigate these effects.
-Also, selective spiders in urban habitats may choose plants as web substrates that reduce vibratory noise since different plants transmit vibrations differently [@cocroft_et_al_2006].
+Thus, we suspect that vibratory noise may impact web site selection, with spiders choosing sites that mitigate these effects.
+Also, selective spiders in urban habitats may choose plants as web substrates that reduce vibratory noise since various plants transmit vibrations differently [@cocroft_et_al_2006].
 Although most research on the effects of noise on arthropod behavior has focused on acoustic rather than vibratory noise [@roberts_howard_2022], some studies have found strong negative effects of acoustic and vibratory noise on arthropod behavior [@carosi_et_al_2019; @bunkley_et_al_2017].
@@
 Perhaps noise negatively affects urban forest spiders -- encouraging spiders to inhabit areas further from noise sources and reducing space between neighbors.
-Many spiders are thought to be plastic in the structure and tuning of their webs [@mortimer_2016; @blamires_2010], and urban exploiters are often fast to adjust to changing conditions [@kralj_2017], so spiders reared in or descended from spiders in the urban center might be better able to tune their webs to decrease vibrations, although this hypothesis requires further testing.
-It will also be important to differentiate whether these differences in behavior between environments is based on developmental exposure, behavioral plasticity, or genetic differentiation.
+Many spiders are thought to be plastic in the structure and tuning of their webs [@mortimer_2016; @blamires_2010], and urban exploiters are often fast to adjust to changing conditions [@kralj_2017].
+As such, spiders reared in or descended from spiders in the urban center might be better able to tune their webs to decrease vibrations, although this hypothesis requires further testing.
+It will also be important to differentiate whether these differences in behavior between environments are based on developmental exposure, behavioral plasticity, or genetic differentiation.
 
-More road length in the 100-meter radius resulted in fewer but more aggregated urban center webs and spiders.
+More road length in the 100-meter radius correlated with fewer but more aggregated urban center webs and spiders.
 Total road length could be another indirect measure of vibratory noise and/or represent dispersal barriers.
-High traffic roads may increase mortality of dispersing spiders via collisions with vehicles, or passing cars may influence wind currents making aerial dispersal difficult [@martin_et_al_2019].
+High-traffic roads may increase mortality of dispersing spiders via collisions with vehicles, or passing cars may influence wind currents making aerial dispersal difficult [@martin_et_al_2019].
 Higher spider abundance in smaller patches may be more evidence for the role of environmental barriers.
@@
 Lastly, spiders in the urban center were more aggregated at sites with higher spectral radiance (a measure of surface temperature).
-Urban centers tend to be warmer on average compared to surrounding areas due to heat trapping via pavement in a phenomenon called the Urban Heat Island Effect [@johnson_et_al_2020].
+Urban centers tend to be warmer on average compared to surrounding areas due to heat-trapping via pavement in a phenomenon called the Urban Heat Island Effect [@johnson_et_al_2020].
 Aggregation formation in warmer sites could be the result of preference for or acclimation to warmer areas [@meineke_et_al_2013] or perhaps aggregation occurs at limited thermal refuges [@riechert_1974b].
-We have shown that human-caused environmental changes correlate with spider spatial patterns, but there are likely many other forms of human disturbance than those tested here.
 
@@
 
-Our study shows that a solitary, generalist predator is more abundant and aggregated with lower web height in an urban center compared to an urban forest -- habitats that vary significantly in environmental conditions.
-We did not measure community-level interactions among organisms, such as the effects of prey abundance.
-However, correlations between spatial pattern and environmental condition indirectly indicate that such interspecific interactions may be essential for monitoring spider aggregations.
-Spider aggregations in urban centers can have medical consequences, such as dense *Lactrodectus hesperus* aggregations [@johnson_et_al_2011], and aesthetic concerns, as is the case with aggregations of *Brigittea civica* under archways of historic buildings [@mammola_et_al_2018].
+We have shown that human-caused environmental changes correlate with spider spatial patterns, but there are likely many other forms of human disturbance than those tested here.
+Our study shows that a solitary, generalist predator (*A.
+pennsylvanica*) is more abundant and aggregated with lower web height in an urban center compared to an urban forest -- habitats that vary significantly in environmental conditions.
+We did not measure community-level interactions among organisms, such as the effects of prey abundance; however, correlations between spatial pattern and environmental conditions indirectly indicate that such interspecific interactions may be important influencers of spider aggregations.
+Noise may also greatly influence spider spatial patterns.
+Our variables that estimate the potential for vibratory noise negatively affected spider abundance while promoting lower web heights, potentially to reduce interference from vibratory noise.
+Noise variables also had opposite effects on aggregative behavior of spiders in the different habitats.
+These differences may indicate variability in tolerance to noise, but more research is necessary to test this hypothesis.
+
+Spider aggregations in urban centers are important to understand, as they can have medical consequences -- e.g., dense black widow (*Lactrodectus hesperus*) aggregations [@johnson_et_al_2011] -- and aesthetic concerns -- e.g., aggregations of the civic meshweaver (*Brigittea civica*) under archways of historic buildings [@mammola_et_al_2018].
 On the other hand, spider aggregations could control pest outbreaks that threaten human health and food supply.
-We emphasize that elucidating the complex relationship between the arthropod abundance and the impacts of urbanization is essential for our understanding of how urbanization affects ecosystem services and food web interactions.
-Our variables that estimate the potential for vibratory noise negatively affected spider abundance while promoting lower web heights, potentially to reduce interference from vibratory noise.
-Noise variables had opposite effects on aggregative behavior of spiders in the different habitats that may indicate differences in tolerance to noise, but more research is necessary to test this hypothesis.
-Thus, urban habitats can vary in environmental conditions which can determine how animals distribute themselves in space and affect predator-prey interactions.
-
-\newpage
+We emphasize that elucidating the complex relationship between arthropod abundance and the impacts of urbanization is essential for our understanding of how urbanization affects ecosystem services and food web interactions.
 
@@
 
-The authors have no relevant financial or non-financial interests to disclose.
+The authors have no competing interests to declare that are relevant to the content of this article.
 
 ### Author Contributions
+
+All authors contributed to the study conception and design.
+Data collection was performed by Brandi Pessman, Madison Hays, and Earl Agpawa under the supervision of Eileen Hebets.
+Formal analysis and the first draft of the manuscript were completed by Brandi Pessman.
+All authors reviewed and edited subsequent versions of the manuscript and approved its final draft.

### 2023-01-14 manuscript/manuscript.Rmd
These are the versions that I submitted

@@
 ## Keywords
-Arachnids, Arthropods, Spatial Distribution, Environmental Predictors
+
+Arthropods, Environmental Predictors, Human-Induced Rapid Environmental Change (HIREC), Nearest Neighbor, Spatial Distribution
 
@@
 We are grateful for past and present members of the Hebets, Shizuka, and Keesey labs (UNL Behavior Group) for their feedback on data analysis and earlier drafts of the manuscript.
-We also thank conference attendees that have visited posters and oral talks about this project, as those conversations have helped to improve many aspects of the research presented here.
+We are also thankful for conversations with Chad Johnson about urban ecology.
+We thank conference attendees that have visited posters and oral talks about this project, as those conversations have helped to improve many aspects of the research presented here.
 
@@
 Clumping can also result from incomplete dispersal that occurs when barriers, often due to habitat structure, prevent adequate dispersal [@riechert_1974b].
-Scientists have found differences in the relative importance of different spatial predictors based on the type of taxon-specific spatial information collected -- *i.e.* presence, abundance, aggregation, or vertical position [@boulangeat_2012].
+Scientists have found differences in the relative importance of different spatial predictors based on the type of taxon-specific spatial information collected -- *i.e.,* presence, abundance, aggregation, or vertical position [@boulangeat_2012].
 
@@
 Urban environments are characterized by decreased biodiversity [@mckinney_2002], increased impervious cover [compacted soil from buildings and pavement, @nowak_greenfield_2020], habitat patchiness [@cadenasso_2007], pollution [air, water, and light, @grimm_2008; @hopkins_2018], and noise [air-, water-, and substrate-borne, @barber_2010; @slabbekoorn_2010; @wu_elias_2014].
-These conditions can contribute to changes in local climatic conditions, such as when impervious cover traps heat and increases the average temperatures in cities compared to surrounding areas --- *i.e.*, the Urban Heat Island Effect [@morabito_2021].
+These conditions can contribute to changes in local climatic conditions, such as when impervious cover traps heat and increases the average temperatures in cities compared to surrounding areas --- *i.e.,* the Urban Heat Island Effect [@morabito_2021].
 There is growing evidence that urbanization changes species interactions, even reshaping whole food webs [@start_2020] and altering the landscape of parasite and disease transmission [@bradley_altizer_2007].
@@
 
-Urban ecosystems can also be extremely heterogeneous with unique and diverse habitats nested within [@rivkin_2019].
-For example, habitats within urban ecosystems can differ considerably in landscape features (e.g.
-tree and building cover), weather conditions (e.g.
-temperature, humidity, and wind speed), and disturbance, resulting in variable access and distributions of resources and opportunities for certain species to thrive.
+Urban ecosystems can also be extremely heterogeneous, with unique and diverse habitats nested within [@rivkin_2019].
+For example, habitats within urban ecosystems can differ considerably in landscape features (e.g., tree and building cover), weather conditions (e.g., temperature, humidity, and wind speed), and disturbance, resulting in variable access and distributions of resources and opportunities for certain species to thrive.
 These factors can also differentially drive animal spatial patterns [@murray_2019; @trubl_2012], sometimes leading to higher degrees of aggregation for urban animals [@johnson_munshisouth_2017].
@@
 Arthropods are considered critical bioindicators of ecosystem health as their short generation time requires them to respond rapidly to human-induced change [@mcintyre_2000].
-However, the impact of urbanization on arthropod ecology is still understudied [but see @kotze_2011; @fenoglio_2020], and the relationship between urban habitats and arthropod abundance and diversity remain controversial [@gippet_2017; @dale_frank_2018].
+However, the impact of urbanization on arthropod ecology is still understudied [but see @kotze_2011; @fenoglio_2020], and the relationship between urban habitats and arthropod abundance and diversity remains controversial [@gippet_2017; @dale_frank_2018].
 Such discrepancies are most likely due to abundance and distributions being species- [@gippet_2017], habitat- [@bennett_lovell_2014], and scale-dependent [@philpott_2014].
@@
 pennsylvanica* would be more abundant and aggregated in the urban center than the urban forest.
-We further expected that specific environmental conditions that vary between the two habitats (e.g.
-tree cover, plant species richness, and disturbance from roads) would be correlated with the variation in the spatial patterns of *A.
+We further expected that specific environmental conditions that vary between the two habitats (e.g., tree cover, plant species richness, and disturbance from roads) would be correlated with the variation in the spatial patterns of *A.
 pennsylvanica*.
@@
 S4).
-We walked along pre-existing sidewalks, roads, and trails because paths were a common feature of both habitats along which we had previously found funnel-weaving spiders.
+We walked along pre-existing sidewalks, roads, and trails because paths were a common feature of both habitats, along which we had previously found funnel-weaving spiders.
 We often found *A.
@@
 
-### Statistical Analysis
+### Statistical analysis
 
@@
 In the global models, we included the predictors (without interactions) that remained after removal for collinearity with the response variables: web and spider abundance, nearest neighbor distance, and web height for the complete data and habitat subsets.
-We restricted these nearest neighbor analyses to first nearest neighbor distance (*i.e.* excluded second nearest neighbor distance) because the first and second nearest neighbor distance both significantly differed between habitats, and including both would complicate the analysis.
+We restricted these nearest neighbor analyses to first nearest neighbor distance (*i.e.,* excluded second nearest neighbor distance) because the first and second nearest neighbor distances both significantly differed between habitats, and including both would complicate the analysis.
 We excluded search distance as a response variable because the predictors were collected from the site of the focal web and may vary along the search path.
@@
 Several predictors (plant species richness, patch area, and road and highway disturbance) were highly right-skewed, so we used a natural log-transformation prior to model selection.
-We used Poisson generalized linear models for number of webs and spiders and nearest neighbor distance and Poisson generalized linear mixed-effect models for web height with site as a random effect.
+We used Poisson generalized linear models for the number of webs and spiders and nearest neighbor distance and Poisson generalized linear mixed-effect models for web height with site as a random effect.
 From these global models, we performed Akaike Information Criterion (AIC) model selection with the *MuMIn* package in R [@MuMIn], which ranks models produced from every combination of the predictors in the global model.
@@
 We tested Poisson generalized linear models for each response variable with land cover as the only predictor.
-We used the *Anova()* function in the *car* package [@car] to get the Likelihood Ratio Chi-Squared values, then used the *glht()* funtion in the *multcomp* package [@multcomp] to perform pairwise comparisons among categories.
+We used the *Anova()* function in the *car* package [@car] to get the Likelihood Ratio Chi-Squared values, then used the *glht()* function in the *multcomp* package [@multcomp] to perform pairwise comparisons among categories.
 We include these results in supplemental material (Fig.
@@
 
-**Table 1** Landscape variables for the urban center (UNL City Campus), the urban forest (Wilderness Park), and Lincoln (Nebraska, USA) City Limits,  collected from the National Land Cover Database (2016 Tree Cover, 2019 Impervious Cover, 2019 Land Cover), the Landsat-7 World Reference System-2 (Band 6, path 28, row 32, taken September 2, 2020), and the 2020 Visible Infrared Imaging Radiometer Suite (VIIRS) using QGIS (v.
+**Table 1** Landscape variables for the urban center (UNL City Campus), the urban forest (Wilderness Park), and Lincoln (Nebraska, USA) City Limits,  collected from the National Land Cover Database (2016 Tree Cover, 2019 Impervious Cover, 2019 Land Cover) using QGIS (v.
 3.16.3-Hannover, ESRI 102704)
@@
 All environmental predictors assessed within a 100-meter radius of the focal web varied by habitat (Table 2).
-Site tree cover was lower in the urban center than the urban forest with five urban center sites measuring zero tree cover ($z_21$ = -14.50, *P* \< 0.001).
+Site tree cover was lower in the urban center than the urban forest, with five urban center sites measuring zero tree cover ($z_21$ = -14.50, *P* \< 0.001).
 The urban center sites had higher impervious cover, with all but four sites being zero in the urban forest ($z_21$ = 14.51, *P* \< 0.001).
 The urban center sites also had higher spectral radiance ($z_21$ = 3.08, *P* = 0.002) and artificial light at night radiance ($z_21$ = 22.46, *P* \< 0.001).
-Overall plant species richness was lower in the urban center than the urban forest ($z_21$ = -7.67, *P* \< 0.001).
+Overall, plant species richness was lower in the urban center than the urban forest ($z_21$ = -7.67, *P* \< 0.001).
 Similarly, spiders used a lower diversity of plants as substrates in the urban center (mean ± se = 1.42 ± 0.15 species) than the urban forest (mean ± se = 2.7 ± 0.26 species, $z_21$ = -2.08, *P* = 0.037).
@@
 
-**Table 2** Mean and standard error of environmental predictors collected in 100-meter buffers of each focal web by habitat
+**Table 2** Mean and standard error of the collected environmental predictors by habitat.
+Percent tree and impervious cover, spectral radiance, artificial night sky radiance, and total road length were collected in a 100-meter buffer of each focal web, while plant species richness was recorded in a 10-meter buffer of each focal web.
+We used the nearest road or highway for disturbance measures.
+Patch area was defined as the area of continuous vegetation that includes the focal web
 
@@
 **Fig.
-3** Comparison of search distance (a), the number of webs (b) and spiders (c) in a 10-meter radius of the focal web, the distance from the focal web to the first and second (d) nearest neighbors, and web height (e) by habitat - urban center vs urban forest.
-Grey jittered points represent the raw data while black points and error bars represent the mean and 95% confidence intervals, respectively, from model predictions.
-Models were either Poisson Generalized Linear Models (a-c) or Poisson Generalized Linear Mixed Effect Models with site as a random factor (d-f).
+3** Comparison of search distance (a), the number of webs (b) and spiders (c) in a 10-meter radius of the focal web, the distance from the focal web to the first and second (d) nearest neighbors, and web height (e) by habitat - urban center vs.
+urban forest.
+Grey jittered points represent the raw data, while black points and error bars represent the mean and 95% confidence intervals, respectively, from model predictions.
+Models were either Poisson Generalized Linear Models (a-c) or Poisson Generalized Linear Mixed Effect Models with site as a random factor (d-e).
 Asterisks indicate significance level (\*\*\* *P* \< 0.001; \*\* *P* \< 0.01; \* *P* \< 0.05).
@@
 4).
-For both measures of abundance, the urban forest subset retained no predictors (Table 3) while the urban center showed a decrease in abundance with increasing plant species richness, patch area, highway disturbance, and road length (Table 3, Fig.
+For both measures of abundance, the urban forest subset retained no predictors (Table 3), while the urban center showed a decrease in abundance with increasing plant species richness, patch area, highway disturbance, and road length (Table 3, Fig.
 4).
@@
 In the urban forest subset, less tree cover, lower road and highway disturbance, and greater plant species richness were associated with nearness (Table 3, Fig.
-5), however, this model was a poor fit ($R^2$ = 0.037).
+5); however, this model was a poor fit ($R^2$ = 0.037).
 Urban center spiders were more aggregated where plant species richness, spectral radiance, and road length are high (Table 3, Fig.
@@
 The relationship between nearest neighbor distance and plant species richness is opposite when analyzed across habitats and within the urban subset.
-This is likely do to the differences in plant species richness and aggregation between habitats -- the urban center had low neighbor distance and plant diversity while the urban forest had high neighbor distance and plant diversity.
+This is likely do to the differences in plant species richness and aggregation between habitats -- the urban center had low neighbor distance and plant diversity, while the urban forest had high neighbor distance and plant diversity.
 The model average for the nearest neighbor distance in the urban center corroborates the findings of the top model and adds that webs were clumped when patch area was larger (Table S3).
@@
 S10b-c).
-For the urban intensities, web distance was shortest at low intensities and furthest at medium intensities with high urban intensity suggest web height between low and medium intensities (Fig.
+For the urban intensities, web distance was shortest at low intensities and furthest at medium intensities with high urban intensity exhibiting web height between low and medium intensities (Fig.
 S10d).
@@
 pennsylvanica*.
-Lower webs in the urban center may be ideal for more crawling prey while higher webs in the urban forest may intercept more flying insects.
+Lower webs in the urban center may be ideal for more crawling prey, while higher webs in the urban forest may intercept more flying insects.
 Alternatively, webs in different habitats may experience different levels of disturbance.
-In the urban center where lawns are mowed frequently and ornamental plants are regularly pruned, spiders could maintain lower webs to conserve energy from frequent rebuilding.
-Additionally, urban forests likely support (and act as a refuge for) many ground dwelling vertebrates, whose movement along the forest floor could frequently damage lower webs.
+In the urban center, where lawns are mowed frequently and ornamental plants are regularly pruned, spiders could maintain lower webs to conserve energy from frequent rebuilding.
+Additionally, urban forests likely support (and act as a refuge for) many ground-dwelling vertebrates, whose movement along the forest floor could frequently damage lower webs.
 Greater tree coverage in the urban forest predicted higher webs, which may further suggest that small mammal movement could destroy low webs as areas with greater tree cover may provide protection and food resources for small mammals [@sarkar_2022].
@@
 We found that webs and spiders were more abundant (in the urban center) and more aggregated as plant species richness decreased.
-The urban center sites were covered in grass lawns and managed landscaping that usually had few plant species present, but in high abundance.
+The urban center sites were covered in grass lawns and managed landscaping that usually had few plant species present but in high abundance.
 Sites with lower plant diversity may have few plant species that are highly preferred, leading to higher spider abundance.
@@
 
-Lower road and highway disturbance was associated with larger spider aggregations in the urban forest, but had no effect on urban center spiders.
+Lower road and highway disturbance was associated with larger spider aggregations in the urban forest but had no effect on urban center spiders.
 Perhaps noise negatively affects urban forest spiders -- encouraging spiders to inhabit areas further from noise sources and reducing space between neighbors.
@@
 Urban centers tend to be warmer on average compared to surrounding areas due to heat-trapping via pavement in a phenomenon called the Urban Heat Island Effect [@johnson_et_al_2020].
-Aggregation formation in warmer sites could be the result of preference for or acclimation to warmer areas [@meineke_et_al_2013] or perhaps aggregation occurs at limited thermal refuges [@riechert_1974b].
+Aggregation formation in warmer sites could be the result of preference for or acclimation to warmer areas [@meineke_et_al_2013], or perhaps aggregation occurs at limited thermal refuges [@riechert_1974b].
 
@@
 pennsylvanica*) is more abundant and aggregated with lower web height in an urban center compared to an urban forest -- habitats that vary significantly in environmental conditions.
-We did not measure community-level interactions among organisms, such as the effects of prey abundance; however, correlations between spatial pattern and environmental conditions indirectly indicate that such interspecific interactions may be important influencers of spider aggregations.
+We did not measure community-level interactions among organisms, such as the effects of prey abundance; however, correlations between spatial patterns and environmental conditions indirectly indicate that such interspecific interactions may be important influencers of spider aggregations.
 Noise may also greatly influence spider spatial patterns.

### 2023-03-13 data_analysis.Rmd
Edits based on reviewers' comments

@@
 library(flextable) # making tables
+library(MASS) # negative binomial tests
+library(glmmTMB) # for proportion test
+library(jpeg) # save pictures
 ```
@@
 shapiro.test(sites$TotalSub) # not normal
-shapiro.test(log(sites$TotalSub)) # normal
+shapiro.test(log10(sites$TotalSub)) # normal
 
@@
 
+tree100m.nb <- glm.nb(tree100m ~ Location, data = sites)
+summary(tree100m.nb)
+
 # The following line tells you the mean and standard error of the raw data for tree cover in a 100 m radius of the sites between the two locations
@@
 
-predictions <- summary(emmeans(tree100m, ~Location),type = "response")
+predictions <- summary(emmeans(tree100m.nb, ~Location),type = "response")
 predictions
@@
 ```{r tree_assumptions, echo = FALSE}
-test_tree <- augment(tree100m, data = sites)
+test_tree <- augment(tree100m.nb, data = sites)
 resid_tree <- ggplot(test_tree, aes(x = .fitted, y = .resid)) + 
@@
 
-Tree cover is **significantly higher in the urban forest** than the urban center (z = -14.50, df = 1, 21, p < 0.001).
-The means and SE's are 47.15 ± 2.17 % for the urban forest and 1.58 ± 0.36 % for the urban center.
+Tree cover is **significantly higher in the urban forest** than the urban center (z = 13.77, df = 1, 21, p < 0.001).
+The means and SE's are 47.15 ± 3.46 % for the urban forest and 1.58 ± 0.37 % for the urban center.
 
@@
 summary(imperv100m)
+
+imperv100m.nb <- glm.nb(imperv100m ~ Location, data = sites)
+summary(imperv100m.nb)
 
@@
 
-predictions <- summary(emmeans(imperv100m, ~Location),type = "response")
+predictions <- summary(emmeans(imperv100m.nb, ~Location),type = "response")
 predictions
@@
 ```{r imperv_assumptions, echo = FALSE}
-test_imperv <- augment(imperv100m, data = sites)
+test_imperv <- augment(imperv100m.nb, data = sites)
 resid_imperv <- ggplot(test_imperv, aes(x = .fitted, y = .resid)) + 
@@
 
-Impervious cover is **significantly higher in the urban center** than the urban forest (z = 14.51, df = 1, 21, p < 0.001).
-The means and SE's are 1.27 ± 0.36 % for the urban forest and 76.52 ± 2.53 % for the urban center.
+Impervious cover is **significantly higher in the urban center** than the urban forest (z = -14.49, df = 1, 21, p < 0.001).
+The means and SE's are 1.27 ± 0.36 % for the urban forest and 76.52 ± 2.63 % for the urban center.
 
@@
 summary(tdr)
+
+tdr.nb <- glm.nb(Traffic_Dist_Road ~ Location, data = sites)
+summary(tdr.nb)
 
@@
 
-predictions <- summary(emmeans(tdr, ~Location),type = "response")
+predictions <- summary(emmeans(tdr.nb, ~Location),type = "response")
 predictions
@@
 ```{r tdr_assumptions, echo = FALSE}
-test_tdr <- augment(tdr, data = sites)
+test_tdr <- augment(tdr.nb, data = sites)
 resid_tdr <- ggplot(test_tdr, aes(x = .fitted, y = .resid)) + 
@@
 
-**Road disturbance is higher in the urban center** than the urban forest (z = 39.19, df = 1, 21, p < 0.001).
-The means and SE's are 104 ± 3.23 vehicles/day/m for the urban forest and 398 ± 5.76 vehicles/day/m for the urban center.
+**Road disturbance is higher in the urban center** than the urban forest (z = -2.87, df = 1, 21, p = 0.004).
+The means and SE's are 104 ± 36 vehicles/day/m for the urban forest and 398 ± 125 vehicles/day/m for the urban center.
 
@@
 summary(tdh)
+
+tdh.nb <- glm.nb(Traffic_Dist_Highway ~ Location, data = sites)
+summary(tdh.nb)
 
@@
 
-predictions <- summary(emmeans(tdh, ~Location),type = "response")
+predictions <- summary(emmeans(tdh.nb, ~Location),type = "response")
 predictions
@@
 ```{r tdh_assumptions, echo = FALSE}
-test_tdh <- augment(tdh, data = sites)
+test_tdh <- augment(tdh.nb, data = sites)
 resid_tdh <- ggplot(test_tdh, aes(x = .fitted, y = .resid)) + 
@@
 
-**Highway disturbance is higher in the urban center** than the urban fores (z = 9.388, df = 1, 21, p < 0.001).
-The means and SE's are 35.6 ± 1.89 vehicles/day/m for the urban forest and 65.0 ± 2.33 vehicles/day/m for the urban center.
+**Highway disturbance is higher in the urban center** than the urban fores (z = -2.64, df = 1, 21, p = 0.008).
+The means and SE's are 35.6 ± 6.04 vehicles/day/m for the urban forest and 65.0 ± 9.82 vehicles/day/m for the urban center.
 
@@
 summary(plant)
+
+plant.nb <- glm.nb(TotalSub ~ Location, data = sites)
+summary(plant.nb)
+
+predictions <- summary(emmeans(plant.nb, ~Location),type = "response")
+predictions
+
+plant_used.nb <- glm.nb(SubUsed ~ Location, data = sites)
+summary(plant_used.nb)
+
+predictions <- summary(emmeans(plant_used.nb, ~Location),type = "response")
+predictions
 
@@
             se = plotrix::std.error(TotalSub))
-
-predictions <- summary(emmeans(plant, ~Location),type = "response")
-predictions
 
@@
 ```{r plant_assumptions, echo = FALSE}
-test_plant <- augment(plant, data = sites)
+test_plant <- augment(plant.nb, data = sites)
 resid_plant <- ggplot(test_plant, aes(x = .fitted, y = .resid)) + 
@@
 
-Plant species richness is **significantly higher in the urban forest** than the urban center (z = -7.674, df = 1, 21, p < 0.001).
-The means and SE's are 13.30 ± 1.153 species for the urban forest and 3.33 ± 0.527 species for the urban center.
+Plant species richness is **significantly higher in the urban forest** than the urban center (z = 6.61, df = 1, 21, p < 0.001).
+The means and SE's are 13.30 ± 1.56 species for the urban forest and 3.33 ± 0.58 species for the urban center.
 
@@
 summary(spec)
+
+spec.nb <- glm.nb(spec_rad ~ Location, data = sites)
+summary(spec.nb)
 
@@
 
-predictions <- summary(emmeans(spec, ~Location),type = "response")
+predictions <- summary(emmeans(spec.nb, ~Location),type = "response")
 predictions
@@
 ```{r spec_assumptions, echo = FALSE}
-test_spec <- augment(plant, data = sites)
+test_spec <- augment(spec.nb, data = sites)
 resid_spec <- ggplot(test_spec, aes(x = .fitted, y = .resid)) + 
@@
 
-Spectral radiance is **significantly higher in the urban center** than the urban forest (z = 3.079, df = 1, 21, p = 0.002).
-The means and SE's are 137.44 ± 3.71 Watts/(m² * sr * µm) for the urban forest and 153.39 ± 3.58 Watts/(m² * sr * µm) for the urban center.
+Spectral radiance is **significantly higher in the urban center** than the urban forest (z = -3.079, df = 1, 21, p = 0.002).
+The means and SE's are 137 ± 3.71 Watts/(m² * sr * µm) for the urban forest and 153 ± 3.58 Watts/(m² * sr * µm) for the urban center.
 
@@
 summary(light)
+
+light.nb <- glm.nb(light_rad ~ Location, data = sites)
+summary(light.nb)
 
@@
 
-predictions <- summary(emmeans(light, ~Location),type = "response")
+predictions <- summary(emmeans(light.nb, ~Location),type = "response")
 predictions
@@
 ```{r light_assumptions, echo = FALSE}
-test_light <- augment(plant, data = sites)
+test_light <- augment(light.nb, data = sites)
 resid_light <- ggplot(test_light, aes(x = .fitted, y = .resid)) + 
@@
 
-Light radiance is **significantly higher in the urban center** than the urban forest (z = 22.46, df = 1, 21, p < 0.001).
-The means and SE's are 5.89 ± 0.77 mcd/m² for the urban forest and 116.90 ± 3.12 mcd/m² for the urban center.
+Light radiance is **significantly higher in the urban center** than the urban forest (z = -17.17, df = 1, 21, p < 0.001).
+The means and SE's are 5.89 ± 0.91 mcd/m² for the urban forest and 116.90 ± 9.39 mcd/m² for the urban center.
 
@@
 summary(patch)
+
+patch.nb <- glm.nb(patch_area_mm ~ Location, data = sites)
+summary(patch.nb)
 
@@
 
-predictions <- summary(emmeans(patch, ~Location),type = "response")
+predictions <- summary(emmeans(patch.nb, ~Location),type = "response")
 predictions
@@
 ```{r patch_assumptions, echo = FALSE}
-test_patch <- augment(patch, data = sites)
+test_patch <- augment(patch.nb, data = sites)
 resid_patch <- ggplot(test_patch, aes(x = .fitted, y = .resid)) + 
@@
 
-Patch area is **significantly higher in the urban forest** than the urban center (z = -374.2, df = 1, 21, p < 0.001).
-The means and SE's are 46,294.7 ± 68.040 mm² for the urban forest and 653.8 ± 7.381 mm² for the urban center.
+Patch area is **significantly higher in the urban forest** than the urban center (z = 13.08, df = 1, 21, p < 0.001).
+The means and SE's are 46,295 ± 11,128 mm² for the urban forest and 654 ± 144 mm² for the urban center.
 
@@
 summary(road)
+
+road.nb <- glm.nb(road_length_m ~ Location, data = sites)
+summary(road.nb)
 
@@
 
-predictions <- summary(emmeans(road, ~Location),type = "response")
+predictions <- summary(emmeans(road.nb, ~Location),type = "response")
 predictions
@@
 ```{r road_assumptions, echo = FALSE}
-test_road <- augment(road, data = sites)
+test_road <- augment(road.nb, data = sites)
 resid_road <- ggplot(test_road, aes(x = .fitted, y = .resid)) + 
@@
 
-Total road length is **significantly higher in the urban center** than the urban forest (z = 20.89, df = 1, 21, p < 0.001).
-The means and SE's are 15.67 ± 1.25 m for the urban forest and 93.03 ± 2.78 m for the urban center.
+Total road length is **significantly higher in the urban center** than the urban forest (z = -2.74, df = 1, 21, p = 0.006).
+The means and SE's are 15.6 ± 7.54 m for the urban forest and 93.0 ± 40.60 m for the urban center.
 
@@
 
+search.nb <- glm.nb(WalkDist ~ Location, data = sites)
+summary(search.nb)
+
 search2 <- glm(log(WalkDist) ~ Location, data = sites)
@@
 # As is, Poisson
-test_search <- augment(search, data = sites)
+test_search <- augment(search.nb, data = sites)
 resid_search <- ggplot(test_search, aes(x = .fitted, y = .resid)) + 
@@
 ```{r search_location_graph, echo = FALSE}
+# negative binomial 
+nd <- data.frame(Location = factor(levels(sites$Location)))
+predictions <- augment(search.nb, newdata = nd, se_fit = TRUE, type.predict = "response")
+predictions <- predictions %>% 
+  rename("rate" = ".fitted", "SE" = ".se.fit")
+
+nb_plot_search <- ggplot(sites, aes(x = Location, y = WalkDist)) + 
+  geom_jitter(color = "grey", width = 0.1) +
+  geom_point(aes(x = Location, y = rate, color = Location), size = 2, data = predictions) + 
+  geom_errorbar(aes(x = Location, 
+                  ymin = rate - SE, 
+                  ymax = rate + SE,
+                  color = Location), data = predictions, inherit.aes = FALSE, width = 0.15, size = 1) +
+  scale_color_manual(values = c("Urban Center" = "#d95f02", "Urban Forest" = "#1b9e77")) +
+  scale_x_discrete(labels=c("Urban Forest" = "Urban \nForest \nN = 10", "Urban Center" = "Urban \nCenter \nN = 12")) +
+  theme_classic() +
+  scale_y_continuous(limits = c(0, 275), breaks = c(0, 50, 100, 150, 200, 250)) +
+  xlab("Collection Location") +
+  ylab("Search Distance [m]") + 
+  theme(text = element_text(size = 10)) + 
+  theme(axis.text.x = element_text(colour = "black", size = 10)) + 
+  theme(axis.text.y = element_text(colour = "black", size = 10),
+        axis.title.x = element_blank()) +
+  theme(legend.position = "none") +
+  annotate(geom = "text", x = 1.5, y = 275, label = "N.S.", color = "black", size = 3)
+
 # raw data
@@
           log_plot_search, 
-          labels = c("Raw Data", "Poisson Distribution", "Log-Transformed"),
+          nb_plot_search,
+          labels = c("Raw Data", "Poisson Distribution", "Log-Transformed", "Negative Binamial"),
           nrow = 1)
@@
 
-Using a Poisson distribution, we **searched significantly further at sites in the urban forest** than the urban center to reach the focal web (z = -10.1, df = 1, 20, p < 0.001).
+Using a negative binomial regression,  **search distance did not significantly differ between habitats** (z = -1.15, df = 1, 20, p = 0.251).
 
@@
 summary(comp)
+
+search_land.nb <- glm.nb(WalkDist ~ Land, data = sites)
+summary(search_land.nb)
+car::Anova(search_land.nb, test.statistic = "LR")
+comp <- glht(search_land.nb, linfct = mcp(Land = "Tukey"))
+summary(comp)
 ```
@@
 nd <- data.frame(Land = factor(levels(sites$Land)))
-predictions <- augment(search_land, newdata = nd, se_fit = TRUE, type.predict = "response")
+predictions <- augment(search_land.nb, newdata = nd, se_fit = TRUE, type.predict = "response")
 predictions <- predictions %>% 
@@
   geom_jitter(color = "grey", width = 0.1, size = 0.5) +
-  geom_point(aes(x = Land, y = rate, color = Land), size = 1, data = predictions) + 
+  geom_point(aes(x = Land, y = rate, color = Land), size = 2, data = predictions) + 
   geom_errorbar(aes(x = Land, 
@@
   theme(legend.position = "none") +
-  theme(axis.text.x = element_text(angle = 90, vjust = 1, hjust=1)) +
-  annotate(geom="text", x=1, y=max(sites$WalkDist), label="A", color="black", size = 3) +
-  annotate(geom="text", x=2, y=max(sites$WalkDist), label="B", color="black", size = 3) +
-  annotate(geom="text", x=3, y=max(sites$WalkDist), label="B", color="black", size = 3) +
-  annotate(geom="text", x=4, y=max(sites$WalkDist), label="B", color="black", size = 3) +
-  annotate(geom="text", x=5, y=max(sites$WalkDist), label="C", color="black", size = 3)
+  theme(axis.text.x = element_text(angle = 90, vjust = 1, hjust=1)) #+
+  #annotate(geom="text", x=1, y=max(sites$WalkDist), label="A", color="black", size = 3) +
+  #annotate(geom="text", x=2, y=max(sites$WalkDist), label="B", color="black", size = 3) +
+  #annotate(geom="text", x=3, y=max(sites$WalkDist), label="B", color="black", size = 3) +
+  #annotate(geom="text", x=4, y=max(sites$WalkDist), label="B", color="black", size = 3) +
+  #annotate(geom="text", x=5, y=max(sites$WalkDist), label="C", color="black", size = 3)
 
@@
 
-**Search distance significantly varies** by land class (Chi = 340.32, df = 4, p < 0.001).
+**Search distance does not significantly differ** by land class (Chi = 6.37, df = 4, p = 0.173).
 
@@
 
+web.nb <- glm.nb(NumWebs ~ Location, data = sites)
+summary(web.nb)
+
 web2 <- glm(log(NumWebs) ~ Location, data = sites)
@@
 # As is, Poisson
-test_webs <- augment(web, data = sites)
+test_webs <- augment(web.nb, data = sites)
 resid_webs <- ggplot(test_webs, aes(x = .fitted, y = .resid)) + 
@@
 ```{r webs_location_graph, echo = FALSE}
+# negative binomial
+nd <- data.frame(Location = factor(levels(sites$Location)))
+predictions <- augment(web.nb, newdata = nd, se_fit = TRUE, type.predict = "response")
+predictions <- predictions %>% 
+  rename("rate" = ".fitted", "SE" = ".se.fit")
+#predictions <- summary(emmeans(web, ~Location),type = "response")
+
+nb_plot_webs <- ggplot(sites, aes(x = Location, y = NumWebs)) + 
+  geom_jitter(color = "grey", width = 0.1) +
+  geom_point(aes(x = Location, y = rate, color = Location), size = 2, data = predictions) + 
+  geom_errorbar(aes(x = Location, 
+                  ymin = rate - SE, 
+                  ymax = rate + SE,
+                  color = Location), data = predictions, inherit.aes = FALSE, width = 0.15, size = 1) +
+  scale_color_manual(values = c("Urban Center" = "#d95f02", "Urban Forest" = "#1b9e77")) +
+  scale_x_discrete(labels=c("Urban Forest" = "Urban \nForest \nN = 10", "Urban Center" = "Urban \nCenter \nN = 12")) +
+  theme_classic() +
+    scale_y_continuous(limits = c(0, 75), breaks = c(0, 15, 30, 45, 60, 75)) +
+  ylab("Number of Webs") + 
+  theme(text = element_text(size = 10)) + 
+  theme(axis.text.x = element_text(colour = "black", size = 10)) + 
+  theme(axis.text.y = element_text(colour = "black", size = 10),
+        axis.title.x = element_blank()) +
+  theme(legend.position = "none") +
+  annotate(geom = "text", x = 1.5, y = 75, label = "***", color = "black", size = 5)
+
 # raw data
@@
           log_plot_webs,
-          labels = c("Raw Data", "Poisson Distribution", "Log-Transformed"),
+          nb_plot_webs,
+          labels = c("Raw Data", "Poisson Distribution", "Log-Transformed", "Negative Binomial"),
           nrow = 1)
@@
 
-There were **significantly more webs at sites in the urban center** than the urban forest (z = 8.556, df = 1, 20, p < 0.001).
+There were **significantly more webs at sites in the urban center** than the urban forest (z = 4.45, df = 1, 20, p < 0.001).
 
@@
 out
-info <- out[[12]]
+info <- out[[11]]
 with(summary(top_model_nw_f), 1 - deviance/null.deviance) # This gives the R squared value
@@
 
+```{r webs_predictors_stats_nb}
+global <- glm.nb(NumWebs ~ log_TotalSub + log_tdr + log_tdh, data = sites)
+options(na.action = "na.fail") # Required for dredge to run
+model_dredge <- dredge(global, beta = "none", evaluate = T, rank = AICc)
+options(na.action = "na.omit") # set back to default
+top_model_nw_o <- get.models(model_dredge, subset = 1)[[1]]
+out <- summary(top_model_nw_o)
+out
+info <- out[[12]]
+#TotalSub (log_TotalSub)
+#exp(info[4, 1])
+#exp(info[4, 2])
+#Traffic_Dist_Road (log_tdr)
+#exp(info[3, 1])
+#exp(info[3, 2])
+#Traffic_Dist_Highway (log_tdh)
+#exp(info[2, 1])
+#exp(info[2, 2])
+
+with(summary(top_model_nw_o), 1 - deviance/null.deviance) # This gives the R squared value
+#summary(model.avg(model_dredge, subset = delta <= 2))
+#summary(model.avg(model_dredge))
+model.sel(model_dredge) #estimates same signs
+car::vif(get.models(model_dredge, 1)[[1]]) #looking for less than 2
+
+# urban forest
+global <- glm.nb(NumWebs ~ tree100m + log_TotalSub + log_tdh + log_patch + log_tdr, data = sites_forest)
+options(na.action = "na.fail") # Required for dredge to run
+model_dredge <- dredge(global, beta = "none", evaluate = T, rank = AICc)
+options(na.action = "na.omit") # set back to default
+top_model_nw_f <- get.models(model_dredge, subset = 1)[[1]]
+out <- summary(top_model_nw_f)
+out
+info <- out[[12]]
+with(summary(top_model_nw_f), 1 - deviance/null.deviance) # This gives the R squared value
+model.sel(model_dredge) #estimates same signs
+#summary(model.avg(model_dredge, subset = delta <= 2))
+#car::vif(get.models(model_dredge, 1)[[1]]) #looking for less than 2
+
+# urban center
+global <- glm.nb(NumWebs ~ log_TotalSub + log_tdr + log_tdh + spec_rad + log_patch + road_length_m, data = sites_center)
+options(na.action = "na.fail") # Required for dredge to run
+model_dredge <- dredge(global, beta = "none", evaluate = T, rank = AICc)
+options(na.action = "na.omit") # set back to default
+top_model_nw_c <- get.models(model_dredge, subset = 1)[[1]]
+out <- summary(top_model_nw_c)
+out
+info <- out[[12]]
+#TotalSub
+#exp(info[4, 1])
+#exp(info[4, 2])
+#patch_area_km
+#exp(info[2, 1])
+#exp(info[2, 2])
+#Traffic_Dist_Highway
+#exp(info[3, 1])
+#exp(info[3, 2])
+#road_length
+#info[5, 1]
+#info[5, 2]
+with(summary(top_model_nw_c), 1 - deviance/null.deviance) # This gives the R squared value
+model.sel(model_dredge) #estimates same signs
+summary(model.avg(model_dredge, subset = delta <= 2))
+# We'll use the conditional average
+#TotalSub
+#-exp(0.659231)
+#exp(0.186648)
+#patch_area_km
+#-exp(0.293327)
+#exp(0.113716)
+#Traffic_Dist_Highway
+#-exp(1.560993)
+#exp(0.192352)
+#road_length_m
+#-0.021230 
+#0.004766
+#car::vif(get.models(model_dredge, 1)[[1]]) # looking for values < 2
+```
+
 ```{r webs_predictors_overall_graphs, echo = FALSE}
@@
 nd <- data.frame(log_TotalSub = seq(0, 3.2, 0.03), 
-                 log_tdr = mean(sites$log_tdr), 
                  log_tdh = mean(sites$log_tdh))
@@
 webs_plant <- ggplot(sites, aes(x = log_TotalSub, y = log(NumWebs))) + 
-  geom_point(color = "grey", 
+  geom_point(aes(color = Location), alpha = 0.7,  
              size = 1) +
@@
 #  scale_y_continuous(limits = c(min(log(sites$NumWebs)), max(log(sites$NumWebs)) + 0.1 * diff(range(log(sites$NumWebs))))) +  
-  scale_y_continuous(limits = c(-1.2, 5), breaks = c(-1, 0, 1, 2, 3, 4, 5)) +  
-  theme_classic() +
-  xlab("Plant Species Richness [log()]") +
-  ylab("Number of Webs [log()]") + 
+  scale_y_continuous(limits = c(-2, 5), breaks = c(-2, 0, 2, 4)) +  
+  scale_color_manual(values = c("Urban Center" = "#d95f02", "Urban Forest" = "#1b9e77")) +
+  theme_classic() +
+  xlab("Plant Species Richness [ln()]") +
+  ylab("Number of Webs [ln()]") + 
   theme(text = element_text(size = 10)) + 
@@
         axis.title.y = element_blank(),
-        axis.text.x = element_blank()) + 
+        #axis.text.x = element_blank(),
+        legend.position = "none") + 
 #  theme(axis.text.y = element_blank()) +
@@
 # Road Disturbance
-nd <- data.frame(log_TotalSub = mean(sites$log_TotalSub), 
-                 log_tdr = seq(2.7, 7.3, 0.05), 
-                 log_tdh = mean(sites$log_tdh))
-predicted.distance <- augment(top_model_nw_o, 
-                              newdata = nd, 
-                              se_fit = TRUE)
-webs_tdr <- ggplot(sites, aes(x = log_tdr, y = log(NumWebs))) + 
-  geom_point(color = "grey", 
-             size = 1) +
-  geom_line(aes(x = log_tdr, y = .fitted), 
-            size = 1, 
-            color = coloro, 
-            data = predicted.distance) + 
-  geom_ribbon(aes(x = log_tdr, 
-                  ymin = .fitted - 1.96 * .se.fit, 
-                  ymax = .fitted + 1.96 * .se.fit), 
-              fill = coloro, 
-              data = predicted.distance, 
-              inherit.aes = FALSE, 
-              alpha = 0.25) +
+#nd <- data.frame(log_TotalSub = mean(sites$log_TotalSub), 
+#                 log_tdr = seq(2.7, 7.3, 0.05), 
+#                 log_tdh = mean(sites$log_tdh))
+#predicted.distance <- augment(top_model_nw_o, 
+#                              newdata = nd, 
+#                              se_fit = TRUE)
+#webs_tdr <- ggplot(sites, aes(x = log_tdr, y = log(NumWebs))) + 
+#  geom_point(color = "grey", 
+#             size = 1) +
+#  geom_line(aes(x = log_tdr, y = .fitted), 
+#            size = 1, 
+#            color = coloro, 
+#            data = predicted.distance) + 
+#  geom_ribbon(aes(x = log_tdr, 
+#                  ymin = .fitted - 1.96 * .se.fit, 
+#                  ymax = .fitted + 1.96 * .se.fit), 
+#              fill = coloro, 
+#              data = predicted.distance, 
+#              inherit.aes = FALSE, 
+#              alpha = 0.25) +
 #  scale_y_continuous(limits = c(min(log(sites$NumWebs)), max(log(sites$NumWebs)) + 0.1 * diff(range(log(sites$NumWebs))))) +  
-  scale_y_continuous(limits = c(-1.2, 5), breaks = c(-1, 0, 1, 2, 3, 4, 5)) +  
-  theme_classic() +
-  xlab("Road Disturbance [log(vehicles/day/m)]") +
-  ylab("Number of Webs [log()]") + 
-  theme(text = element_text(size = 10)) + 
-  theme(axis.text.x = element_text(colour = "black", size = 10)) + 
-  theme(axis.text.y = element_text(colour = "black", size = 10)) +
-  theme(axis.title.x = element_blank(), 
-        axis.title.y = element_blank(), 
-        axis.text.y = element_blank(),
-        axis.text.x = element_blank()) + 
+#  scale_y_continuous(limits = c(-1.2, 5), breaks = c(-1, 0, 1, 2, 3, 4, 5)) +  
+#  theme_classic() +
+#  xlab("Road Disturbance [log(vehicles/day/m)]") +
+#  ylab("Number of Webs [log()]") + 
+#  theme(text = element_text(size = 10)) + 
+#  theme(axis.text.x = element_text(colour = "black", size = 10)) + 
+#  theme(axis.text.y = element_text(colour = "black", size = 10)) +
+#  theme(axis.title.x = element_blank(), 
+#        axis.title.y = element_blank(), 
+#        axis.text.y = element_blank(),
+#        axis.text.x = element_blank()) + 
 #  annotate(geom = "text", x = min((predicted.distance$log_tdr)) + diff(range((predicted.distance$log_tdr)))/2, y = max(log(sites$NumWebs)), label = "***", color = "black", size = 4) +
-    annotate(geom = "text", x = min((predicted.distance$log_tdr)) + diff(range((predicted.distance$log_tdr)))/2, y = 4.8, label = "***", color = "black", size = 4)
+#    annotate(geom = "text", x = min((predicted.distance$log_tdr)) + diff(range((predicted.distance$log_tdr)))/2, y = 4.8, label = "***", color = "black", size = 4)
 
@@
 nd <- data.frame(log_TotalSub = mean(sites$log_TotalSub), 
-                 log_tdr = mean(sites$log_tdr), 
                  log_tdh = seq(2.7, 5.5, 0.03))
@@
 webs_tdh <- ggplot(sites, aes(x = log_tdh, y = log(NumWebs))) + 
-  geom_point(color = "grey", 
+  geom_point(aes(color = Location), alpha = 0.7, 
              size = 1) +
@@
 #  scale_y_continuous(limits = c(min(log(sites$NumWebs)) - 1.2, max(log(sites$NumWebs)) + 0.1 * diff(range(log(sites$NumWebs))))) +  
-  scale_y_continuous(limits = c(-1.2, 5), breaks = c(-1, 0, 1, 2, 3, 4, 5)) +  
-  theme_classic() +
-  xlab("Highway Disturbance [log(vehicles/day/m)]") +
-  ylab("Number of Webs [log()]") + 
+  scale_y_continuous(limits = c(-2, 5), breaks = c(-2, 0, 2, 4)) +  
+  scale_x_continuous(breaks = c(3, 4, 5)) +  
+  scale_color_manual(values = c("Urban Center" = "#d95f02", "Urban Forest" = "#1b9e77")) +
+  theme_classic() +
+  xlab("Highway Disturbance [ln(vehicles/day/m)]") +
+  ylab("Number of Webs [ln()]") + 
   theme(text = element_text(size = 10)) + 
@@
         axis.title.y = element_blank(), 
-        axis.text.y = element_blank(),
-        axis.text.x = element_blank()) + 
+        #axis.text.y = element_blank(),
+        #axis.text.x = element_blank(),
+        legend.position = "none") + 
 #  annotate(geom = "text", x = min((predicted.distance$log_tdh)) + diff(range((predicted.distance$log_tdh)))/2, y = max(log(sites$NumWebs)), label = "***", color = "black", size = 4) +
-  annotate(geom = "text", x = min((predicted.distance$log_tdh)) + diff(range((predicted.distance$log_tdh)))/2, y = 4.8, label = "***", color = "black", size = 4)
+  annotate(geom = "text", x = min((predicted.distance$log_tdh)) + diff(range((predicted.distance$log_tdh)))/2, y = 4.8, label = "**", color = "black", size = 4)
 
 webs_plant
-webs_tdr
+#webs_tdr
 webs_tdh
@@
 # Plant Species Richness
-nd <- data.frame(log_TotalSub = seq(0, 1.8, 0.02), 
-                 log_patch = mean(sites_center$log_patch),
-                 road_length_m = mean(sites_center$road_length_m),
-                 log_tdh = mean(sites_center$log_tdh))
+#nd <- data.frame(log_TotalSub = seq(0, 1.8, 0.02), 
+#                 log_patch = mean(sites_center$log_patch),
+#                 road_length_m = mean(sites_center$road_length_m),
+#                 log_tdh = mean(sites_center$log_tdh))
+#predicted.distance <- augment(top_model_nw_c, 
+#                              newdata = nd, 
+#                              se_fit = TRUE)
+#webs_center_plant <- ggplot(sites_center, aes(x = log_TotalSub, y = log(NumWebs))) + 
+#  geom_point(color = "grey", 
+#             size = 1) +
+#  geom_line(aes(x = log_TotalSub, y = .fitted), 
+#            size = 1, 
+#            color = colorc, 
+#            data = predicted.distance) + 
+#  geom_ribbon(aes(x = log_TotalSub, 
+#                  ymin = .fitted - 1.96 * .se.fit, 
+#                  ymax = .fitted + 1.96 * .se.fit), 
+#              fill = colorc, 
+#              data = predicted.distance, 
+#              inherit.aes = FALSE, 
+#              alpha = 0.25) +
+##  scale_y_continuous(limits = c(min(log(sites_center$NumWebs)), max(log(sites_center$NumWebs)) + 0.1 * diff(range(log(sites_center$NumWebs))))) +  
+#  scale_y_continuous(limits = c(-1.2, 5), breaks = c(-1, 0, 1, 2, 3, 4, 5)) +
+#  theme_classic() +
+#  xlab("Plant Species Richness [log()]") +
+#  ylab("Number of Webs [log()]") + 
+#  theme(text = element_text(size = 10)) + 
+#  theme(axis.text.x = element_text(colour = "black", size = 10)) + 
+#  theme(axis.text.y = element_text(colour = "black", size = 10)) +
+#  theme(axis.title.x = element_blank(), 
+#        axis.title.y = element_blank(), 
+#        axis.text.x = element_blank()) + 
+##  theme(axis.text.y = element_blank()) +
+##  annotate(geom = "text", x = min((predicted.distance$log_TotalSub)) + diff(range((predicted.distance$log_TotalSub)))/2, y = max(log(sites_center$NumWebs)), label = "***", color = "black", size = 4) +
+#  annotate(geom = "text", x = min((predicted.distance$log_TotalSub)) + diff(range((predicted.distance$log_TotalSub)))/2, y = 5, label = "***", color = "black", size = 4)
+
+# Patch Area
+#nd <- data.frame(log_TotalSub = mean(sites_center$log_TotalSub), 
+#                 log_patch = seq(4.34, 7.52, 0.025),
+#                 road_length_m = mean(sites_center$road_length_m),
+#                 log_tdh = mean(sites_center$log_tdh))
+#predicted.distance <- augment(top_model_nw_c, 
+#                              newdata = nd, 
+#                              se_fit = TRUE)
+#webs_center_patch <- ggplot(sites_center, aes(x = log_patch, y = log(NumWebs))) + 
+#  geom_point(color = "grey", 
+#             size = 1) +
+#  geom_line(aes(x = log_patch, y = .fitted), 
+#            size = 1, 
+#            color = colorc, 
+#            data = predicted.distance) + 
+#  geom_ribbon(aes(x = log_patch, 
+#                  ymin = .fitted - 1.96 * .se.fit, 
+#                  ymax = .fitted + 1.96 * .se.fit), 
+#              fill = colorc, 
+#              data = predicted.distance, 
+#              inherit.aes = FALSE, 
+#              alpha = 0.25) +
+##  scale_y_continuous(limits = c(min(log(sites_center$NumWebs)) - 0.75, max(log(sites_center$NumWebs)) + 0.15 * diff(range(log(sites_center$NumWebs))))) +  
+#  scale_y_continuous(limits = c(-1.2, 5), breaks = c(-1, 0, 1, 2, 3, 4, 5)) +
+#  theme_classic() +
+#  xlab("Patch Area [log(mm²)]") +
+#  ylab("Number of Webs [log()]") + 
+#  theme(text = element_text(size = 10)) + 
+#  theme(axis.text.x = element_text(colour = "black", size = 10)) + 
+#  theme(axis.text.y = element_text(colour = "black", size = 10)) +
+#  theme(axis.title.x = element_blank(), 
+#        axis.title.y = element_blank(), 
+#        axis.text.y = element_blank(),
+#        axis.text.x = element_blank()) + 
+##  annotate(geom = "text", x = min((predicted.distance$log_patch)) + diff(range((predicted.distance$log_patch)))/2, y = max(log(sites_center$NumWebs)), label = "**", color = "black", size = 4) +
+#    annotate(geom = "text", x = min((predicted.distance$log_patch)) + diff(range((predicted.distance$log_patch)))/2, y = 5, label = "**", color = "black", size = 4)
+
+# Highway Disturbance
+nd <- data.frame(log_tdh = seq(3.32, 5.42, 0.02))
 predicted.distance <- augment(top_model_nw_c, 
@@
                               se_fit = TRUE)
-webs_center_plant <- ggplot(sites_center, aes(x = log_TotalSub, y = log(NumWebs))) + 
-  geom_point(color = "grey", 
-             size = 1) +
-  geom_line(aes(x = log_TotalSub, y = .fitted), 
-            size = 1, 
-            color = colorc, 
-            data = predicted.distance) + 
-  geom_ribbon(aes(x = log_TotalSub, 
-                  ymin = .fitted - 1.96 * .se.fit, 
-                  ymax = .fitted + 1.96 * .se.fit), 
-              fill = colorc, 
-              data = predicted.distance, 
-              inherit.aes = FALSE, 
-              alpha = 0.25) +
-#  scale_y_continuous(limits = c(min(log(sites_center$NumWebs)), max(log(sites_center$NumWebs)) + 0.1 * diff(range(log(sites_center$NumWebs))))) +  
-  scale_y_continuous(limits = c(-1.2, 5), breaks = c(-1, 0, 1, 2, 3, 4, 5)) +
-  theme_classic() +
-  xlab("Plant Species Richness [log()]") +
-  ylab("Number of Webs [log()]") + 
-  theme(text = element_text(size = 10)) + 
-  theme(axis.text.x = element_text(colour = "black", size = 10)) + 
-  theme(axis.text.y = element_text(colour = "black", size = 10)) +
-  theme(axis.title.x = element_blank(), 
-        axis.title.y = element_blank(), 
-        axis.text.x = element_blank()) + 
-#  theme(axis.text.y = element_blank()) +
-#  annotate(geom = "text", x = min((predicted.distance$log_TotalSub)) + diff(range((predicted.distance$log_TotalSub)))/2, y = max(log(sites_center$NumWebs)), label = "***", color = "black", size = 4) +
-  annotate(geom = "text", x = min((predicted.distance$log_TotalSub)) + diff(range((predicted.distance$log_TotalSub)))/2, y = 5, label = "***", color = "black", size = 4)
-
-# Patch Area
-nd <- data.frame(log_TotalSub = mean(sites_center$log_TotalSub), 
-                 log_patch = seq(4.34, 7.52, 0.025),
-                 road_length_m = mean(sites_center$road_length_m),
-                 log_tdh = mean(sites_center$log_tdh))
-predicted.distance <- augment(top_model_nw_c, 
-                              newdata = nd, 
-                              se_fit = TRUE)
-webs_center_patch <- ggplot(sites_center, aes(x = log_patch, y = log(NumWebs))) + 
-  geom_point(color = "grey", 
-             size = 1) +
-  geom_line(aes(x = log_patch, y = .fitted), 
-            size = 1, 
-            color = colorc, 
-            data = predicted.distance) + 
-  geom_ribbon(aes(x = log_patch, 
-                  ymin = .fitted - 1.96 * .se.fit, 
-                  ymax = .fitted + 1.96 * .se.fit), 
-              fill = colorc, 
-              data = predicted.distance, 
-              inherit.aes = FALSE, 
-              alpha = 0.25) +
-#  scale_y_continuous(limits = c(min(log(sites_center$NumWebs)) - 0.75, max(log(sites_center$NumWebs)) + 0.15 * diff(range(log(sites_center$NumWebs))))) +  
-  scale_y_continuous(limits = c(-1.2, 5), breaks = c(-1, 0, 1, 2, 3, 4, 5)) +
-  theme_classic() +
-  xlab("Patch Area [log(mm²)]") +
-  ylab("Number of Webs [log()]") + 
-  theme(text = element_text(size = 10)) + 
-  theme(axis.text.x = element_text(colour = "black", size = 10)) + 
-  theme(axis.text.y = element_text(colour = "black", size = 10)) +
-  theme(axis.title.x = element_blank(), 
-        axis.title.y = element_blank(), 
-        axis.text.y = element_blank(),
-        axis.text.x = element_blank()) + 
-#  annotate(geom = "text", x = min((predicted.distance$log_patch)) + diff(range((predicted.distance$log_patch)))/2, y = max(log(sites_center$NumWebs)), label = "**", color = "black", size = 4) +
-    annotate(geom = "text", x = min((predicted.distance$log_patch)) + diff(range((predicted.distance$log_patch)))/2, y = 5, label = "**", color = "black", size = 4)
-
-# Highway Disturbance
-nd <- data.frame(log_TotalSub = mean(sites_center$log_TotalSub), 
-                 log_patch = mean(sites_center$log_patch),
-                 road_length_m = mean(sites_center$road_length_m),
-                 log_tdh = seq(3.32, 5.42, 0.02))
-predicted.distance <- augment(top_model_nw_c, 
-                              newdata = nd, 
-                              se_fit = TRUE)
-webs_center_tdh <- ggplot(sites_center, aes(x = log_tdh, y = log(NumWebs))) + 
-  geom_point(color = "grey", 
+webs_center_tdh <- ggplot(sites, aes(x = log_tdh, y = log(NumWebs))) + 
+  geom_point(aes(color = Location), alpha = 0.5, 
              size = 1) +
@@
 #  scale_y_continuous(limits = c(min(log(sites_center$NumWebs)) - 0.75, max(log(sites_center$NumWebs)) + 0.1 * diff(range(log(sites_center$NumWebs))))) +  
-  scale_y_continuous(limits = c(-1.2, 5), breaks = c(-1, 0, 1, 2, 3, 4, 5)) +
-  theme_classic() +
-  xlab("Highway Disturbance [log(vehicles/day/m)]") +
-  ylab("Number of Webs [log()]") + 
+  scale_y_continuous(limits = c(-2, 5), breaks = c(-2, 0, 2, 4)) +  
+  scale_x_continuous(breaks = c(3, 4, 5)) +  
+  scale_color_manual(values = c("Urban Center" = "#d95f02", "Urban Forest" = "#1b9e77")) +
+  theme_classic() +
+  xlab("Highway Disturbance [ln(vehicles/day/m)]") +
+  ylab("Number of Webs [ln()]") + 
   theme(text = element_text(size = 10)) + 
@@
         axis.title.y = element_blank(),
-        axis.text.y = element_blank(),
-        axis.text.x = element_blank()) + 
+        legend.position = "none") + 
+        #axis.text.y = element_blank(),
+        #axis.text.x = element_blank()) + 
 #  annotate(geom = "text", x = min((predicted.distance$log_tdh)) + diff(range((predicted.distance$log_tdh)))/2, y = max(log(sites_center$NumWebs)), label = "***", color = "black", size = 4) +
-  annotate(geom = "text", x = min((predicted.distance$log_tdh)) + diff(range((predicted.distance$log_tdh)))/2, y = 5, label = "***", color = "black", size = 4)
+  annotate(geom = "text", x = 4, y = 5, label = "*", color = "black", size = 4)
 
 # Road Length
-nd <- data.frame(log_TotalSub = mean(sites_center$log_TotalSub), 
-                 log_patch = mean(sites_center$log_patch),
-                 road_length_m = seq(47, 136, 1),
-                 log_tdh = mean(sites_center$log_tdh))
-predicted.distance <- augment(top_model_nw_c, 
-                              newdata = nd, 
-                              se_fit = TRUE)
-webs_center_road <- ggplot(sites_center, aes(x = (road_length_m), y = log(NumWebs))) + 
-  geom_point(color = "grey", 
-             size = 1) +
-  geom_line(aes(x = (road_length_m), y = .fitted), 
-            size = 1, 
-            color = colorc, 
-            data = predicted.distance) + 
-  geom_ribbon(aes(x = (road_length_m), 
-                  ymin = .fitted - 1.96 * .se.fit, 
-                  ymax = .fitted + 1.96 * .se.fit), 
-              fill = colorc, 
-              data = predicted.distance, 
-              inherit.aes = FALSE, 
-              alpha = 0.25) +
-#  scale_y_continuous(limits = c(min(log(sites_center$NumWebs)), max(log(sites_center$NumWebs)) + 0.1 * diff(range(log(sites_center$NumWebs))))) +
-  scale_y_continuous(limits = c(-1.2, 5), breaks = c(-1, 0, 1, 2, 3, 4, 5)) +
-  theme_classic() +
-  xlab("Total Road Length [m]") +
-  ylab("Number of Webs [log()]") + 
-  theme(text = element_text(size = 10)) + 
-  theme(axis.text.x = element_text(colour = "black", size = 10)) + 
-  theme(axis.text.y = element_text(colour = "black", size = 10)) +
-  theme(axis.title.x = element_blank(), 
-        axis.title.y = element_blank(), 
-        axis.text.y = element_blank(),
-        axis.text.x = element_blank()) + 
-#  annotate(geom = "text", x = min((predicted.distance$road_length_m)) + diff(range((predicted.distance$road_length_m)))/2, y = max(log(sites_center$NumWebs)), label = "***", color = "black", size = 4) +
-  annotate(geom = "text", x = min((predicted.distance$road_length_m)) + diff(range((predicted.distance$road_length_m)))/2, y = 5, label = "***", color = "black", size = 4)
-
-webs_center_plant
-webs_center_patch
-webs_center_road
+#nd <- data.frame(log_TotalSub = mean(sites_center$log_TotalSub), 
+#                 log_patch = mean(sites_center$log_patch),
+#                 road_length_m = seq(47, 136, 1),
+#                 log_tdh = mean(sites_center$log_tdh))
+#predicted.distance <- augment(top_model_nw_c, 
+#                              newdata = nd, 
+#                              se_fit = TRUE)
+#webs_center_road <- ggplot(sites_center, aes(x = (road_length_m), y = log(NumWebs))) + 
+#  geom_point(color = "grey", 
+#             size = 1) +
+#  geom_line(aes(x = (road_length_m), y = .fitted), 
+#            size = 1, 
+#            color = colorc, 
+#            data = predicted.distance) + 
+#  geom_ribbon(aes(x = (road_length_m), 
+#                  ymin = .fitted - 1.96 * .se.fit, 
+#                  ymax = .fitted + 1.96 * .se.fit), 
+#              fill = colorc, 
+#              data = predicted.distance, 
+#              inherit.aes = FALSE, 
+#              alpha = 0.25) +
+##  scale_y_continuous(limits = c(min(log(sites_center$NumWebs)), max(log(sites_center$NumWebs)) + 0.1 * diff(range(log(sites_center$NumWebs))))) +
+#  scale_y_continuous(limits = c(-1.2, 5), breaks = c(-1, 0, 1, 2, 3, 4, 5)) +
+#  theme_classic() +
+#  xlab("Total Road Length [m]") +
+#  ylab("Number of Webs [log()]") + 
+#  theme(text = element_text(size = 10)) + 
+#  theme(axis.text.x = element_text(colour = "black", size = 10)) + 
+#  theme(axis.text.y = element_text(colour = "black", size = 10)) +
+#  theme(axis.title.x = element_blank(), 
+#        axis.title.y = element_blank(), 
+#        axis.text.y = element_blank(),
+#        axis.text.x = element_blank()) + 
+##  annotate(geom = "text", x = min((predicted.distance$road_length_m)) + diff(range((predicted.distance$road_length_m)))/2, y = max(log(sites_center$NumWebs)), label = "***", color = "black", size = 4) +
+#  annotate(geom = "text", x = min((predicted.distance$road_length_m)) + diff(range((predicted.distance$road_length_m)))/2, y = 5, label = "***", color = "black", size = 4)
+
+#webs_center_plant
+#webs_center_patch
+#webs_center_road
 webs_center_tdh
@@
 comp <- glht(webs_land, linfct = mcp(Land = "Tukey"))
+summary(comp)
+
+webs_land_nb <- glm.nb(NumWebs ~ Land, data = sites)
+summary(webs_land_nb)
+car::Anova(webs_land_nb, test.statistic = "LR")
+comp <- glht(webs_land_nb, linfct = mcp(Land = "Tukey"))
 summary(comp)
@@
 nd <- data.frame(Land = factor(levels(sites$Land)))
-predictions <- augment(webs_land, newdata = nd, se_fit = TRUE, type.predict = "response")
+predictions <- augment(webs_land_nb, newdata = nd, se_fit = TRUE, type.predict = "response")
 predictions <- predictions %>% 
@@
   theme(legend.position = "none") +
-  theme(axis.text.x = element_text(angle = 90, vjust = 1, hjust=1)) +
-  annotate(geom="text", x=1, y=max(sites$NumWebs), label="A", color="black", size = 3) +
-  annotate(geom="text", x=2, y=max(sites$NumWebs), label="A", color="black", size = 3) +
-  annotate(geom="text", x=3, y=max(sites$NumWebs), label="A", color="black", size = 3) +
-  annotate(geom="text", x=4, y=max(sites$NumWebs), label="B", color="black", size = 3) +
-  annotate(geom="text", x=5, y=max(sites$NumWebs), label="B", color="black", size = 3)
+  theme(axis.text.x = element_text(angle = 90, vjust = 1, hjust=1))# +
+  #annotate(geom="text", x=1, y=max(sites$NumWebs), label="A", color="black", size = 3) +
+  #annotate(geom="text", x=2, y=max(sites$NumWebs), label="A", color="black", size = 3) +
+  #annotate(geom="text", x=3, y=max(sites$NumWebs), label="A", color="black", size = 3) +
+  #annotate(geom="text", x=4, y=max(sites$NumWebs), label="B", color="black", size = 3) +
+  #annotate(geom="text", x=5, y=max(sites$NumWebs), label="B", color="black", size = 3)
 
@@
 
-The **number of webs significantly varies** by land cover class (chi = 106.67, df = 4, p < 0.001).
+The **number of webs significantly varies** by land cover class (chi = 19.13, df = 4, p < 0.001).
 
@@
 
+spiders.nb <- glm.nb(NumSpiders ~ Location, data = sites)
+summary(spiders.nb)
+
 spiders2 <- glm(log(NumSpiders) ~ Location, data = sites)
@@
 # As is, Poisson
-test_spiders <- augment(spiders, data = sites)
+test_spiders <- augment(spiders.nb, data = sites)
 resid_spiders <- ggplot(test_spiders, aes(x = .fitted, y = .resid)) + 
@@
 ```{r spiders_location_graph, echo = FALSE}
+# Negative Binomial
+nd <- data.frame(Location = factor(levels(sites$Location)))
+predictions <- augment(spiders.nb, newdata = nd, se_fit = TRUE, type.predict = "response")
+predictions <- predictions %>% 
+  rename("rate" = ".fitted", "SE" = ".se.fit")
+#predictions <- summary(emmeans(spiders, ~Location),type = "response")
+
+nb_plot_spiders <- ggplot(sites, aes(x = Location, y = NumSpiders)) + 
+  geom_jitter(color = "grey", width = 0.1) +
+  geom_point(aes(x = Location, y = rate, color = Location), size = 2, data = predictions) + 
+  geom_errorbar(aes(x = Location, 
+                  ymin = rate - SE, 
+                  ymax = rate + SE,
+                  color = Location), data = predictions, inherit.aes = FALSE, width = 0.15, size = 1) +
+  scale_color_manual(values = c("Urban Center" = "#d95f02", "Urban Forest" = "#1b9e77")) +
+  scale_x_discrete(labels=c("Urban Forest" = "Urban \nForest \nN = 10", "Urban Center" = "Urban \nCenter \nN = 12")) +
+  theme_classic() +
+    scale_y_continuous(limits = c(0, 25), breaks = c(0, 5, 10, 15, 20, 25)) +
+  ylab("Number of Spiders") + 
+  theme(text = element_text(size = 10)) + 
+  theme(axis.text.x = element_text(colour = "black", size = 10)) + 
+  theme(axis.text.y = element_text(colour = "black", size = 10),
+        axis.title.x = element_blank()) +
+  theme(legend.position = "none") +
+  annotate(geom = "text", x = 1.5, y = 25, label = "**", color = "black", size = 5)
+
 # raw data
@@
           log_plot_spiders, 
-          labels = c("Raw Data", "Poisson Distribution", "Log-Transformed"),
+          nb_plot_spiders,
+          labels = c("Raw Data", "Poisson Distribution", "Log-Transformed", "Negative Binomial"),
           nrow = 1)
@@
 
-The **number of spiders present by site is significantly higher in the urban center** (z = 4.863, df = 1, 20, p < 0.001).
+The **number of spiders present by site is significantly higher in the urban center** (z = 3.13, df = 1, 20, p = 0.002).
 
@@
 
+```{r spiders_predictors_stats_nb}
+global <- glm.nb(NumSpiders ~ log_TotalSub + log_tdr + log_tdh, data = sites)
+options(na.action = "na.fail") # Required for dredge to run
+model_dredge <- dredge(global, beta = "none", evaluate = T, rank = AICc)
+options(na.action = "na.omit") # set back to default
+top_model_ns_o <- get.models(model_dredge, subset = 1)[[1]]
+out <- summary(top_model_ns_o)
+out
+info <- out[[11]]
+#TotalSub (log_TotalSub)
+#exp(info[3, 1])
+#exp(info[3, 2])
+#Traffic_Dist_Highway (log_tdh)
+#exp(info[2, 1])
+#exp(info[2, 2])
+
+with(summary(top_model_ns_o), 1 - deviance/null.deviance) # This gives the R squared value
+#summary(model.avg(model_dredge, subset = delta <= 2))
+#summary(model.avg(model_dredge))
+model.sel(model_dredge) #estimates same signs
+car::vif(get.models(model_dredge, 1)[[1]]) #looking for less than 2
+
+# urban forest
+global <- glm.nb(NumSpiders ~ tree100m + log_TotalSub + log_tdh + log_patch + log_tdr, data = sites_forest)
+options(na.action = "na.fail") # Required for dredge to run
+model_dredge <- dredge(global, beta = "none", evaluate = T, rank = AICc)
+options(na.action = "na.omit") # set back to default
+top_model_ns_f <- get.models(model_dredge, subset = 1)[[1]]
+out <- summary(top_model_ns_f)
+out
+info <- out[[11]]
+with(summary(top_model_ns_f), 1 - deviance/null.deviance) # This gives the R squared value
+model.sel(model_dredge) #estimates same signs
+#summary(model.avg(model_dredge, subset = delta <= 2))
+#car::vif(get.models(model_dredge, 1)[[1]]) #looking for less than 2
+
+# urban center
+global <- glm.nb(NumSpiders ~ log_TotalSub + log_tdr + log_tdh + spec_rad + log_patch + road_length_m, data = sites_center)
+options(na.action = "na.fail") # Required for dredge to run
+model_dredge <- dredge(global, beta = "none", evaluate = T, rank = AICc)
+options(na.action = "na.omit") # set back to default
+top_model_ns_c <- get.models(model_dredge, subset = 1)[[1]]
+out <- summary(top_model_ns_c)
+out
+info <- out[[11]]
+#TotalSub
+#exp(info[4, 1])
+#exp(info[4, 2])
+#patch_area_km
+#exp(info[2, 1])
+#exp(info[2, 2])
+#Traffic_Dist_Highway
+#exp(info[3, 1])
+#exp(info[3, 2])
+#road_length
+#info[5, 1]
+#info[5, 2]
+with(summary(top_model_ns_c), 1 - deviance/null.deviance) # This gives the R squared value
+model.sel(model_dredge) #estimates same signs
+summary(model.avg(model_dredge, subset = delta <= 2))
+#car::vif(get.models(model_dredge, 1)[[1]]) # looking for values < 2
+```
+
 ```{r spiders_predictors_overall_graphs, echo = FALSE}
@@
 spiders_plant <- ggplot(sites, aes(x = log_TotalSub, y = log(NumSpiders))) + 
-  geom_point(color = "grey", 
+  geom_point(aes(color = Location), alpha = 0.7, 
              size = 1) +
@@
 #  scale_y_continuous(limits = c(min(log(sites$NumSpiders)) - 2, max(log(sites$NumSpiders)) + 0.1 * diff(range(log(sites$NumSpiders))))) +  
-  scale_y_continuous(limits = c(-2, 3.3), breaks = c(-2, -1, 0, 1, 2, 3)) +  
-  theme_classic() +
-  xlab("Plant Species Richness [log()]") +
-  ylab("Number of Spiders [log()]") + 
+  scale_y_continuous(limits = c(-2, 5), breaks = c(-2, 0, 2, 4)) +  
+  scale_color_manual(values = c("Urban Center" = "#d95f02", "Urban Forest" = "#1b9e77")) +
+  theme_classic() +
+  xlab("Plant Species Richness [ln()]") +
+  ylab("Number of Spiders [ln()]") + 
   theme(text = element_text(size = 10)) + 
@@
         axis.title.y = element_blank(),
-        axis.text.x = element_blank()) + 
+        #axis.text.x = element_blank(),
+        legend.position = "none") + 
 #  theme(axis.text.y = element_blank()) +
 #  annotate(geom = "text", x = min(predicted.distance$log_TotalSub) + diff(range(predicted.distance$log_TotalSub))/2, y = max(log(sites$NumSpiders)), label = "***", color = "black", size = 4)
-    annotate(geom = "text", x = min(predicted.distance$log_TotalSub) + diff(range(predicted.distance$log_TotalSub))/2, y = 3, label = "***", color = "black", size = 4)
+    annotate(geom = "text", x = min(predicted.distance$log_TotalSub) + diff(range(predicted.distance$log_TotalSub))/2, y = 5, label = "***", color = "black", size = 4)
 
@@
 spiders_tdh <- ggplot(sites, aes(x = log_tdh, y = log(NumSpiders))) + 
-  geom_point(color = "grey", 
+  geom_point(aes(color = Location), alpha = 0.7, 
              size = 1) +
@@
 #  scale_y_continuous(limits = c(min(log(sites$NumSpiders)) - 2, max(log(sites$NumSpiders)) + 0.1 * diff(range(log(sites$NumSpiders))))) +  
-  scale_y_continuous(limits = c(-2, 3.3), breaks = c(-2, -1, 0, 1, 2, 3)) +  
-  theme_classic() +
-  xlab("Highway Disturbance [log(vehicles/day/m)]") +
-  ylab("Number of Spiders [log()]") + 
+  scale_y_continuous(limits = c(-2, 5), breaks = c(-2, 0, 2, 4)) +  
+  scale_x_continuous(breaks = c(3, 4, 5)) +  
+  scale_color_manual(values = c("Urban Center" = "#d95f02", "Urban Forest" = "#1b9e77")) +
+  theme_classic() +
+  xlab("Highway Disturbance [ln(vehicles/day/m)]") +
+  ylab("Number of Spiders [ln()]") + 
   theme(text = element_text(size = 10)) + 
@@
         axis.title.y = element_blank(), 
-        axis.text.y = element_blank()) + 
+        #axis.text.y = element_blank(),
+        legend.position = "none") + 
 #  theme(axis.text.x = element_blank()) +
 #  annotate(geom = "text", x = min((predicted.distance$log_tdh)) + diff(range((predicted.distance$log_tdh)))/2, y = max(log(sites$NumSpiders)), label = "***", color = "black", size = 4)
-  annotate(geom = "text", x = min((predicted.distance$log_tdh)) + diff(range((predicted.distance$log_tdh)))/2, y = 3, label = "***", color = "black", size = 4)
+  annotate(geom = "text", x = min((predicted.distance$log_tdh)) + diff(range((predicted.distance$log_tdh)))/2, y = 5, label = "*", color = "black", size = 4)
 
@@
 # Plant Species Richness
-nd <- data.frame(log_TotalSub = seq(0, 1.8, 0.02), 
-                 log_patch = mean(sites_center$log_patch),
-                 road_length_m = mean(sites_center$road_length_m),
-                 log_tdh = mean(sites_center$log_tdh))
+#nd <- data.frame(log_TotalSub = seq(0, 1.8, 0.02), 
+#                 log_patch = mean(sites_center$log_patch),
+#                 road_length_m = mean(sites_center$road_length_m),
+#                 log_tdh = mean(sites_center$log_tdh))
+#predicted.distance <- augment(top_model_ns_c, 
+#                              newdata = nd, 
+#                              se_fit = TRUE)
+#spiders_center_plant <- ggplot(sites_center, aes(x = log_TotalSub, y = log(NumSpiders))) + 
+#  geom_point(color = "grey", 
+#             size = 1) +
+#  geom_line(aes(x = log_TotalSub, y = .fitted), 
+#            size = 1, 
+#            color = colorc, 
+#            data = predicted.distance) + 
+#  geom_ribbon(aes(x = log_TotalSub, 
+#                  ymin = .fitted - 1.96 * .se.fit, 
+#                  ymax = .fitted + 1.96 * .se.fit), 
+#              fill = colorc, 
+#              data = predicted.distance, 
+#              inherit.aes = FALSE, 
+#              alpha = 0.25) +
+##  scale_y_continuous(limits = c(min(log(sites_center$NumSpiders)) - 1, max(log(sites_center$NumSpiders)) + 0.2 * diff(range(log(sites_center$NumSpiders))))) +  
+#  scale_y_continuous(limits = c(-2, 3.5), breaks = c(-2, -1, 0, 1, 2, 3)) +  
+#  theme_classic() +
+#  xlab("Plant Species Richness [log()]") +
+#  ylab("Number of Spiders [log()]") + 
+#  theme(text = element_text(size = 10)) + 
+#  theme(axis.text.x = element_text(colour = "black", size = 10)) + 
+#  theme(axis.text.y = element_text(colour = "black", size = 10)) +
+#  theme(axis.title.x = element_blank(), 
+#        axis.title.y = element_blank()) + 
+##  theme(axis.text.x = element_blank(), 
+##        axis.text.y = element_blank()) +
+##  annotate(geom = "text", x = min((predicted.distance$log_TotalSub)) + diff(range((predicted.distance$log_TotalSub)))/2, y = max(log(sites_center$NumSpiders)), label = "***", color = "black", size = 4)
+#  annotate(geom = "text", x = min((predicted.distance$log_TotalSub)) + diff(range((predicted.distance$log_TotalSub)))/2, y = 3.5, label = "***", color = "black", size = 4)
+
+# Patch Area
+#nd <- data.frame(log_TotalSub = mean(sites_center$log_TotalSub), 
+#                 log_patch = seq(4.34, 7.52, 0.025),
+#                 road_length_m = mean(sites_center$road_length_m),
+#                 log_tdh = mean(sites_center$log_tdh))
+#predicted.distance <- augment(top_model_ns_c, 
+#                              newdata = nd, 
+#                              se_fit = TRUE)
+#spiders_center_patch <- ggplot(sites_center, aes(x = log_patch, y = log(NumSpiders))) + 
+#  geom_point(color = "grey", 
+#             size = 1) +
+#  geom_line(aes(x = log_patch, y = .fitted), 
+#            size = 1, 
+#            color = colorc, 
+#            data = predicted.distance) + 
+#  geom_ribbon(aes(x = log_patch, 
+#                  ymin = .fitted - 1.96 * .se.fit, 
+#                  ymax = .fitted + 1.96 * .se.fit), 
+#              fill = colorc, 
+#              data = predicted.distance, 
+#              inherit.aes = FALSE, 
+#              alpha = 0.25) +
+##  scale_y_continuous(limits = c(min(log(sites_center$NumSpiders)) - 1, max(log(sites_center$NumSpiders)) + 0.15 * diff(range(log(sites_center$NumSpiders))))) +  
+#  scale_y_continuous(limits = c(-2, 3.5), breaks = c(-2, -1, 0, 1, 2, 3)) +  
+#  theme_classic() +
+#  xlab("Patch Area [log(mm²)]") +
+#  ylab("Number of Spiders [log()]") + 
+#  theme(text = element_text(size = 10)) + 
+#  theme(axis.text.x = element_text(colour = "black", size = 10)) + 
+#  theme(axis.text.y = element_text(colour = "black", size = 10)) +
+#  theme(axis.title.x = element_blank(), 
+#        axis.title.y = element_blank(), 
+#        axis.text.y = element_blank()) + 
+##  theme(axis.text.x = element_blank()) +
+##  annotate(geom = "text", x = min((predicted.distance$log_patch)) + diff(range((predicted.distance$log_patch)))/2, y = max(log(sites_center$NumSpiders)), label = "**", color = "black", size = 4) 
+#  annotate(geom = "text", x = min((predicted.distance$log_patch)) + diff(range((predicted.distance$log_patch)))/2, y = 3.5, label = "**", color = "black", size = 4)
+
+# Highway Disturbance
+nd <- data.frame(log_tdh = seq(3.32, 5.42, 0.02))
 predicted.distance <- augment(top_model_ns_c, 
@@
                               se_fit = TRUE)
-spiders_center_plant <- ggplot(sites_center, aes(x = log_TotalSub, y = log(NumSpiders))) + 
-  geom_point(color = "grey", 
-             size = 1) +
-  geom_line(aes(x = log_TotalSub, y = .fitted), 
-            size = 1, 
-            color = colorc, 
-            data = predicted.distance) + 
-  geom_ribbon(aes(x = log_TotalSub, 
-                  ymin = .fitted - 1.96 * .se.fit, 
-                  ymax = .fitted + 1.96 * .se.fit), 
-              fill = colorc, 
-              data = predicted.distance, 
-              inherit.aes = FALSE, 
-              alpha = 0.25) +
-#  scale_y_continuous(limits = c(min(log(sites_center$NumSpiders)) - 1, max(log(sites_center$NumSpiders)) + 0.2 * diff(range(log(sites_center$NumSpiders))))) +  
-  scale_y_continuous(limits = c(-2, 3.5), breaks = c(-2, -1, 0, 1, 2, 3)) +  
-  theme_classic() +
-  xlab("Plant Species Richness [log()]") +
-  ylab("Number of Spiders [log()]") + 
-  theme(text = element_text(size = 10)) + 
-  theme(axis.text.x = element_text(colour = "black", size = 10)) + 
-  theme(axis.text.y = element_text(colour = "black", size = 10)) +
-  theme(axis.title.x = element_blank(), 
-        axis.title.y = element_blank()) + 
-#  theme(axis.text.x = element_blank(), 
-#        axis.text.y = element_blank()) +
-#  annotate(geom = "text", x = min((predicted.distance$log_TotalSub)) + diff(range((predicted.distance$log_TotalSub)))/2, y = max(log(sites_center$NumSpiders)), label = "***", color = "black", size = 4)
-  annotate(geom = "text", x = min((predicted.distance$log_TotalSub)) + diff(range((predicted.distance$log_TotalSub)))/2, y = 3.5, label = "***", color = "black", size = 4)
-
-# Patch Area
-nd <- data.frame(log_TotalSub = mean(sites_center$log_TotalSub), 
-                 log_patch = seq(4.34, 7.52, 0.025),
-                 road_length_m = mean(sites_center$road_length_m),
-                 log_tdh = mean(sites_center$log_tdh))
-predicted.distance <- augment(top_model_ns_c, 
-                              newdata = nd, 
-                              se_fit = TRUE)
-spiders_center_patch <- ggplot(sites_center, aes(x = log_patch, y = log(NumSpiders))) + 
-  geom_point(color = "grey", 
-             size = 1) +
-  geom_line(aes(x = log_patch, y = .fitted), 
-            size = 1, 
-            color = colorc, 
-            data = predicted.distance) + 
-  geom_ribbon(aes(x = log_patch, 
-                  ymin = .fitted - 1.96 * .se.fit, 
-                  ymax = .fitted + 1.96 * .se.fit), 
-              fill = colorc, 
-              data = predicted.distance, 
-              inherit.aes = FALSE, 
-              alpha = 0.25) +
-#  scale_y_continuous(limits = c(min(log(sites_center$NumSpiders)) - 1, max(log(sites_center$NumSpiders)) + 0.15 * diff(range(log(sites_center$NumSpiders))))) +  
-  scale_y_continuous(limits = c(-2, 3.5), breaks = c(-2, -1, 0, 1, 2, 3)) +  
-  theme_classic() +
-  xlab("Patch Area [log(mm²)]") +
-  ylab("Number of Spiders [log()]") + 
-  theme(text = element_text(size = 10)) + 
-  theme(axis.text.x = element_text(colour = "black", size = 10)) + 
-  theme(axis.text.y = element_text(colour = "black", size = 10)) +
-  theme(axis.title.x = element_blank(), 
-        axis.title.y = element_blank(), 
-        axis.text.y = element_blank()) + 
-#  theme(axis.text.x = element_blank()) +
-#  annotate(geom = "text", x = min((predicted.distance$log_patch)) + diff(range((predicted.distance$log_patch)))/2, y = max(log(sites_center$NumSpiders)), label = "**", color = "black", size = 4) 
-  annotate(geom = "text", x = min((predicted.distance$log_patch)) + diff(range((predicted.distance$log_patch)))/2, y = 3.5, label = "**", color = "black", size = 4)
-
-# Highway Disturbance
-nd <- data.frame(log_TotalSub = mean(sites_center$log_TotalSub), 
-                 log_patch = mean(sites_center$log_patch),
-                 road_length_m = mean(sites_center$road_length_m),
-                 log_tdh = seq(3.32, 5.42, 0.02))
-predicted.distance <- augment(top_model_ns_c, 
-                              newdata = nd, 
-                              se_fit = TRUE)
-spiders_center_tdh <- ggplot(sites_center, aes(x = log_tdh, y = log(NumSpiders))) + 
-  geom_point(color = "grey", 
+spiders_center_tdh <- ggplot(sites, aes(x = log_tdh, y = log(NumSpiders))) + 
+  geom_point(aes(color = Location), alpha = 0.5, 
              size = 1) +
@@
 #  scale_y_continuous(limits = c(min(log(sites_center$NumSpiders)) - 2, max(log(sites_center$NumSpiders)) + 0.1 * diff(range(log(sites_center$NumSpiders))))) +  
-  scale_y_continuous(limits = c(-2, 3.5), breaks = c(-2, -1, 0, 1, 2, 3)) +  
-  theme_classic() +
-  xlab("Highway Disturbance [log(vehicles/day/m)]") +
-  ylab("Number of Spiders [log()]") + 
+  scale_y_continuous(limits = c(-2, 5), breaks = c(-2, 0, 2, 4)) +  
+  scale_x_continuous(breaks = c(3, 4, 5)) +  
+  scale_color_manual(values = c("Urban Center" = "#d95f02", "Urban Forest" = "#1b9e77")) +
+  theme_classic() +
+  xlab("Highway Disturbance [ln(vehicles/day/m)]") +
+  ylab("Number of Spiders [ln()]") + 
   theme(text = element_text(size = 10)) + 
@@
         axis.title.y = element_blank(),
-        axis.text.y = element_blank()) + 
+        legend.position = "none") + 
+        #axis.text.y = element_blank()) + 
 #  theme(axis.text.x = element_blank()) +
 #  annotate(geom = "text", x = min((predicted.distance$log_tdh)) + diff(range((predicted.distance$log_tdh)))/2, y = max(log(sites_center$NumSpiders)), label = "***", color = "black", size = 4) 
-  annotate(geom = "text", x = min((predicted.distance$log_tdh)) + diff(range((predicted.distance$log_tdh)))/2, y = 3.5, label = "***", color = "black", size = 4)
+  annotate(geom = "text", x = 4, y = 5, label = "*", color = "black", size = 4)
 
 # Road Length
-nd <- data.frame(log_TotalSub = mean(sites_center$log_TotalSub), 
-                 log_patch = mean(sites_center$log_patch),
-                 road_length_m = seq(47, 136, 1),
-                 log_tdh = mean(sites_center$log_tdh))
-predicted.distance <- augment(top_model_ns_c, 
-                              newdata = nd, 
-                              se_fit = TRUE)
-spiders_center_road <- ggplot(sites_center, aes(x = (road_length_m), y = log(NumSpiders))) + 
-  geom_point(color = "grey", 
-             size = 1) +
-  geom_line(aes(x = (road_length_m), y = .fitted), 
-            size = 1, 
-            color = colorc, 
-            data = predicted.distance) + 
-  geom_ribbon(aes(x = (road_length_m), 
-                  ymin = .fitted - 1.96 * .se.fit, 
-                  ymax = .fitted + 1.96 * .se.fit), 
-              fill = colorc, 
-              data = predicted.distance, 
-              inherit.aes = FALSE, 
-              alpha = 0.25) +
-#  scale_y_continuous(limits = c(min(log(sites_center$NumSpiders)) - 1, max(log(sites_center$NumSpiders)) + 0.1 * diff(range(log(sites_center$NumSpiders))))) +  
-  scale_y_continuous(limits = c(-2, 3.5), breaks = c(-2, -1, 0, 1, 2, 3)) +  
-  theme_classic() +
-  xlab("Total Road Length [m]") +
-  ylab("Number of Spiders [log()]") + 
-  theme(text = element_text(size = 10)) + 
-  theme(axis.text.x = element_text(colour = "black", size = 10)) + 
-  theme(axis.text.y = element_text(colour = "black", size = 10)) +
-  theme(axis.title.x = element_blank(), 
-        axis.title.y = element_blank(), 
-        axis.text.y = element_blank()) + 
-#  theme(axis.text.x = element_blank()) +
-#  annotate(geom = "text", x = min((predicted.distance$road_length_m)) + diff(range((predicted.distance$road_length_m)))/2, y = max(log(sites_center$NumSpiders)), label = "***", color = "black", size = 4)
-  annotate(geom = "text", x = min((predicted.distance$road_length_m)) + diff(range((predicted.distance$road_length_m)))/2, y = 3.5, label = "***", color = "black", size = 4)
-
-spiders_center_plant
-spiders_center_patch
-spiders_center_road
+#nd <- data.frame(log_TotalSub = mean(sites_center$log_TotalSub), 
+#                 log_patch = mean(sites_center$log_patch),
+#                 road_length_m = seq(47, 136, 1),
+#                 log_tdh = mean(sites_center$log_tdh))
+#predicted.distance <- augment(top_model_ns_c, 
+#                              newdata = nd, 
+#                              se_fit = TRUE)
+#spiders_center_road <- ggplot(sites_center, aes(x = (road_length_m), y = log(NumSpiders))) + 
+#  geom_point(color = "grey", 
+#             size = 1) +
+#  geom_line(aes(x = (road_length_m), y = .fitted), 
+#            size = 1, 
+#            color = colorc, 
+#            data = predicted.distance) + 
+#  geom_ribbon(aes(x = (road_length_m), 
+#                  ymin = .fitted - 1.96 * .se.fit, 
+#                  ymax = .fitted + 1.96 * .se.fit), 
+#              fill = colorc, 
+#              data = predicted.distance, 
+#              inherit.aes = FALSE, 
+#              alpha = 0.25) +
+##  scale_y_continuous(limits = c(min(log(sites_center$NumSpiders)) - 1, max(log(sites_center$NumSpiders)) + 0.1 * diff(range(log(sites_center$NumSpiders))))) +  
+#  scale_y_continuous(limits = c(-2, 3.5), breaks = c(-2, -1, 0, 1, 2, 3)) +  
+#  theme_classic() +
+#  xlab("Total Road Length [m]") +
+#  ylab("Number of Spiders [log()]") + 
+#  theme(text = element_text(size = 10)) + 
+#  theme(axis.text.x = element_text(colour = "black", size = 10)) + 
+#  theme(axis.text.y = element_text(colour = "black", size = 10)) +
+#  theme(axis.title.x = element_blank(), 
+#        axis.title.y = element_blank(), 
+#        axis.text.y = element_blank()) + 
+##  theme(axis.text.x = element_blank()) +
+##  annotate(geom = "text", x = min((predicted.distance$road_length_m)) + diff(range((predicted.distance$road_length_m)))/2, y = max(log(sites_center$NumSpiders)), label = "***", color = "black", size = 4)
+#  annotate(geom = "text", x = min((predicted.distance$road_length_m)) + diff(range((predicted.distance$road_length_m)))/2, y = 3.5, label = "***", color = "black", size = 4)
+
+#spiders_center_plant
+#spiders_center_patch
+#spiders_center_road
 spiders_center_tdh
@@
 comp <- glht(spiders_land, linfct = mcp(Land = "Tukey"))
+summary(comp)
+
+spiders_land_nb <- glm.nb(NumSpiders ~ Land, data = sites)
+summary(spiders_land_nb)
+car::Anova(spiders_land_nb, test.statistic = "LR")
+comp <- glht(spiders_land_nb, linfct = mcp(Land = "Tukey"))
 summary(comp)
@@
 nd <- data.frame(Land = factor(levels(sites$Land)))
-predictions <- augment(spiders_land, newdata = nd, se_fit = TRUE, type.predict = "response")
+predictions <- augment(spiders_land_nb, newdata = nd, se_fit = TRUE, type.predict = "response")
 predictions <- predictions %>% 
@@
   theme(legend.position = "none") +
-  theme(axis.text.x = element_text(angle = 90, vjust = 1, hjust=1)) +
-  annotate(geom="text", x=1, y=max(sites$NumSpiders), label="A", color="black", size = 3) +
-  annotate(geom="text", x=2, y=max(sites$NumSpiders), label="A", color="black", size = 3) +
-  annotate(geom="text", x=3, y=max(sites$NumSpiders), label="A", color="black", size = 3) +
-  annotate(geom="text", x=4, y=max(sites$NumSpiders), label="B", color="black", size = 3) +
-  annotate(geom="text", x=5, y=max(sites$NumSpiders), label="B", color="black", size = 3)
+  theme(axis.text.x = element_text(angle = 90, vjust = 1, hjust=1))# +
+  #annotate(geom="text", x=1, y=max(sites$NumSpiders), label="A", color="black", size = 3) +
+  #annotate(geom="text", x=2, y=max(sites$NumSpiders), label="A", color="black", size = 3) +
+  #annotate(geom="text", x=3, y=max(sites$NumSpiders), label="A", color="black", size = 3) +
+  #annotate(geom="text", x=4, y=max(sites$NumSpiders), label="A", color="black", size = 3) +
+  #annotate(geom="text", x=5, y=max(sites$NumSpiders), label="A", color="black", size = 3)
 
@@
 
-The **number of spiders per site significantly varies** across land cover class (Chi = 31.65, df = 4, p < 0.001).
+The **number of spiders per site significantly varies** across land cover class (Chi = 10.91, df = 4, p = 0.028).
 
@@
 
+dist.nb <- glmer.nb(round(RetreatDist, 0) ~ Location * factor(Neighbor) + (1 | ID), data = web_dist)
+summary(dist.nb)
+
 dist2 <- lmer(log(RetreatDist) ~ Location * factor(Neighbor) + (1 | ID), data = web_dist)
@@
 # As is, Poisson
-test_dist <- augment(dist, data = web_dist)
+test_dist <- augment(dist.nb, data = web_dist)
 resid_dist <- ggplot(test_dist, aes(x = .fitted, y = .resid)) + 
@@
 ```{r dist_location_graph, echo = FALSE}
+# Negative Binomial
+variable_names <- list("1" = "Nearest Neighbor",
+                       "2" = "2nd Nearest Neighbor")
+variable_labeller <- function(variable,value){
+  return(variable_names[value])
+}
+predictions <- expand.grid(Location = levels(factor(web_dist$Location)), Neighbor = levels(factor(web_dist$Neighbor)))
+predictions$response <- predict(dist.nb, newdata = predictions, se.fit = TRUE, re.form = NA, type = "response")
+
+myFunc <- function(mm) {
+    predict(mm, newdata = predictions, re.form = ~0, type = "response")
+}
+#bigBoot_dist_location_nb <- bootMer(dist.nb, myFunc, nsim = 1000)
+#saveRDS(bigBoot_dist_location_nb, file = "bootstrapping/bigBoot_dist_location_nb.Rds")
+bigBoot_dist_location_nb <- readRDS("bootstrapping/bigBoot_dist_location_nb.Rds") 
+predSE <- t(apply(bigBoot_dist_location_nb$t, MARGIN = 2, FUN = sd, na.rm = TRUE))
+predictions$SE <- predSE[1, ]
+#predictions2 <- summary(emmeans(dist, ~Location | Neighbor,type = "response"))
+
+nb_plot_dist <- ggplot(web_dist, aes(x = Neighbor, y = RetreatDist)) + 
+  geom_jitter(aes(color = Location), alpha = 0.5, width = 0.1) +
+    geom_line(aes(x = Neighbor, y = response, group = Location), size = 2, data = predictions, color = "grey") +
+  geom_point(aes(x = Neighbor, y = response, color = Location), size = 2, data = predictions) + 
+  geom_errorbar(aes(x = Neighbor, 
+                  ymin = response - SE, 
+                  ymax = response + SE,
+                  color = Location), data = predictions, inherit.aes = FALSE, width = 0.15, size = 1) +
+  scale_color_manual(values = c("Urban Center" = "#d95f02", "Urban Forest" = "#1b9e77")) +
+  scale_x_discrete(labels=c("Urban Forest" = "Urban \nForest \nN = 10", "Urban Center" = "Urban \nCenter \nN = 12")) +
+  theme_classic() +
+  scale_y_continuous(limits = c(-50, 1000), breaks = c(0, 200, 400, 600, 800, 1000)) +
+  xlab("Nearest Neighbors") +
+  ylab("Distance from Focal Web \nto Neighbor Web [cm]") + 
+  theme(text = element_text(size = 10)) + 
+  theme(axis.text.x = element_text(colour = "black", size = 10)) + 
+  theme(axis.text.y = element_text(colour = "black", size = 10)) +
+  theme(legend.position = "none")
+
 # raw data
@@
           log_plot_dist, 
-          labels = c("Raw Data", "Poisson Distribution", "Log-Transformed"),
+          nb_plot_dist,
+          labels = c("Raw Data", "Poisson Distribution", "Log-Transformed", "Negative Binomial"),
           nrow = 1, 
@@
 
-Spider neighbors were **significantly closer in the urban center** than the urban forest (z = -5.597, df = 1, 21, p < 0.001).
-The **second neighbor was always further from the focal web** than the first (z = 14.654, df = 1, 21, p < 0.001), as this is how we defined the first and second neighbor.
-We also found a **significant interaction between location and neighbor** (z = 9.860, df = 1, 21, p < 0.001) - the distance between the first and second neighbor differed to a higher degree in the urban center than the urban forest.
+Spider neighbors were **significantly closer in the urban center** than the urban forest (z = -1.83, df = 1, 21, p < 0.001).
+The **second neighbor was always further from the focal web** than the first (z = 2.83, df = 1, 21, p = 0.005), as this is how we defined the first and second neighbor.
+There was **no interaction between location and neighbor** (z = -1.09, df = 1, 21, p = 0.276) - the distance between the first and second neighbor did not differ between the urban center and the urban forest.
 
@@
 
+```{r dist_predictors_stats_nb}
+#overall
+global <- glm.nb(round(RetreatDist, 0) ~ log_TotalSub + log_tdr + log_tdh, data = near)
+options(na.action = "na.fail") # Required for dredge to run
+model_dredge <- dredge(global, beta = "none", evaluate = T, rank = AICc)
+options(na.action = "na.omit") # set back to default
+top_model_wd_o <- get.models(model_dredge, subset = 1)[[1]]
+out <- summary(top_model_wd_o)
+out
+info <- out[[11]]
+# TotalSub
+#exp(info[3, 1])
+#exp(info[3, 2])
+#Traffic_Dist_Road
+#exp(info[2, 1])
+#exp(info[2, 1])
+
+with(summary(top_model_wd_o), 1 - deviance/null.deviance)
+model.sel(model_dredge) #estimates same signs
+summary(model.avg(model_dredge, subset = delta <= 2))
+#car::vif(get.models(model_dredge, 5)[[1]]) # looking for less than 2
+
+# Urban Forest
+global <- glm.nb(round(RetreatDist, 0) ~ tree100m + log_TotalSub + log_tdr + log_tdh + log_patch, data = near_forest)
+options(na.action = "na.fail") # Required for dredge to run
+model_dredge <- dredge(global, beta = "none", evaluate = T, rank = AICc)
+options(na.action = "na.omit") # set back to default
+top_model_wd_f <- get.models(model_dredge, subset = 1)[[1]]
+out <- summary(top_model_wd_f)
+out
+info <- out[[11]]
+#tree100m
+#info[5, 1]
+#info[5, 2]
+#TotalSub
+#exp(info[4, 1])
+#exp(info[4, 2])
+#Road
+#exp(info[3, 1])
+#exp(info[3, 2])
+#Highway
+#exp(info[2, 1])
+#exp(info[2, 2])
+
+with(summary(top_model_wd_f), 1 - deviance/null.deviance)
+model.sel(model_dredge) #estimates same signs
+#summary(model.avg(model_dredge, subset = delta <= 2))
+#car::vif(get.models(model_dredge, 1)[[1]]) # looking for less than 2
+
+# Urban Center
+global <- glm.nb(round(RetreatDist, 0) ~ log_TotalSub + log_tdr + log_tdh + spec_rad + log_patch + road_length_m, data = near_center)
+options(na.action = "na.fail") # Required for dredge to run
+model_dredge <- dredge(global, beta = "none", evaluate = T, rank = AICc)
+options(na.action = "na.omit") # set back to default
+top_model_wd_c <- get.models(model_dredge, subset = 1)[[1]]
+out <- summary(top_model_wd_c)
+out
+info <- out[[11]]
+#TotalSub
+#exp(info[2, 1])
+#exp(info[2, 2])
+#spec_rad
+#info[4, 1]
+#info[4, 2]
+#road_length_m
+#info[3, 1]
+#info[3, 2]
+
+with(summary(top_model_wd_c), 1 - deviance/null.deviance)
+model.sel(model_dredge) #estimates same signs
+summary(model.avg(model_dredge, subset = delta <= 2))
+
+#TotalSub
+#exp(info[2, 1])
+#exp(info[2, 2])
+#spec_rad
+#info[4, 1]
+#info[4, 2]
+#road_length_m
+#info[3, 1]
+#info[3, 2]
+#log_patch
+#exp(info[5, 1])
+#exp(info[5, 2])
+#car::vif(get.models(model_dredge, 1)[[1]]) # looking for less than 2
+
+# If any value is much greater than 2, this means there is quite a bit of multicollinearity, and we can try removing the variable with the highest vif.
+Here is the code you would run to accomplish this.
+
+#global2 <- update(global, .~. -spec_rad)
+#options(na.action = "na.fail") # Required for dredge to run
+#model_dredge <- dredge(global2, beta = "none", evaluate = T, rank = AICc)
+#options(na.action = "na.omit") # set back to default
+#top_model_wd_c <- get.models(model_dredge, subset = 1)[[1]]
+#out <- summary(top_model_wd_c)
+#out
+#info <- out[[12]]
+#car::vif(get.models(model_dredge, 1)[[1]]) 
+```
+
 ```{r dist_predictors_overall_graphs, echo = FALSE}
@@
 # Plant Species Richness
-nd <- data.frame(log_TotalSub = seq(0, 3.2, 0.03), 
-                 log_tdr = mean(near$log_tdr))
+nd <- data.frame(log_TotalSub = seq(0, 3.2, 0.03))
 predicted.distance <- augment(top_model_wd_o, 
@@
 dist_plant <- ggplot(near, aes(x = log_TotalSub, y = log(RetreatDist))) + 
-  geom_point(color = "grey", 
+  geom_point(aes(color = Location), alpha = 0.7, 
              size = 1) +
@@
 #  scale_y_continuous(limits = c(min(log(near$RetreatDist)), max(log(near$RetreatDist)) + 0.1 * diff(range(log(near$RetreatDist))))) +  
-  scale_y_continuous(limits = c(2, 7), breaks = c(2, 3, 4, 5, 6, 7)) +  
-  theme_classic() +
-  xlab("Plant Species Richness [log()]") +
-  ylab("Distance from Focal Web \nto Neighbor Web [log(cm)]") + 
+  scale_y_continuous(limits = c(2, 7.3), breaks = c(2, 3, 4, 5, 6, 7)) +  
+  scale_color_manual(values = c("Urban Center" = "#d95f02", "Urban Forest" = "#1b9e77")) +
+  theme_classic() +
+  xlab("Plant Species Richness [ln()]") +
+  ylab("Distance from Focal Web \nto Neighbor Web [ln(cm)]") + 
   theme(text = element_text(size = 10)) + 
@@
         axis.title.y = element_blank(),
-        axis.text.x = element_blank()) + 
+        legend.position = "none") +
+        #axis.text.x = element_blank()) + 
 #  theme(axis.text.y = element_blank()) +
 #  annotate(geom = "text", x = min(predicted.distance$log_TotalSub) + diff(range(predicted.distance$log_TotalSub))/2, y = max(log(near$RetreatDist)), label = "***", color = "black", size = 4)
-  annotate(geom = "text", x = min(predicted.distance$log_TotalSub) + diff(range(predicted.distance$log_TotalSub))/2, y = 6.8, label = "***", color = "black", size = 4)
+  annotate(geom = "text", x = min(predicted.distance$log_TotalSub) + diff(range(predicted.distance$log_TotalSub))/2, y = 7, label = "**", color = "black", size = 4)
 
 # Road Disturbance
-nd <- data.frame(log_TotalSub = mean(near$log_TotalSub), 
-                 log_tdr = seq(2.7, 7.3, 0.05))
-predicted.distance <- augment(top_model_wd_o, 
-                              newdata = nd, 
-                              se_fit = TRUE)
-dist_tdr <- ggplot(near, aes(x = log_tdr, y = log(RetreatDist))) + 
-  geom_point(color = "grey", 
-             size = 1) +
-  geom_line(aes(x = log_tdr, y = .fitted), 
-            size = 1, 
-            color = coloro, 
-            data = predicted.distance) + 
-  geom_ribbon(aes(x = log_tdr, 
-                  ymin = .fitted - 1.96 * .se.fit, 
-                  ymax = .fitted + 1.96 * .se.fit), 
-              fill = coloro, 
-              data = predicted.distance, 
-              inherit.aes = FALSE, 
-              alpha = 0.25) +
-#  scale_y_continuous(limits = c(min(log(near$RetreatDist)), max(log(near$RetreatDist)) + 0.1 * diff(range(log(near$RetreatDist))))) + 
-  scale_y_continuous(limits = c(2, 7), breaks = c(2, 3, 4, 5, 6, 7)) +  
-  theme_classic() +
-  xlab("Road Disturbance [log(vehicles/day/m)]") +
-  ylab("Distance from Focal Web \nto Neighbor Web [log(cm)]") + 
-  theme(text = element_text(size = 10)) + 
-  theme(axis.text.x = element_text(colour = "black", size = 10)) + 
-  theme(axis.text.y = element_text(colour = "black", size = 10)) +
-  theme(axis.title.x = element_blank(), 
-        axis.title.y = element_blank(), 
-        axis.text.y = element_blank(),
-        axis.text.x = element_blank()) + 
-#  annotate(geom = "text", x = min((predicted.distance$log_tdr)) + diff(range((predicted.distance$log_tdr)))/2, y = max(log(near$RetreatDist)), label = "***", color = "black", size = 4)
-    annotate(geom = "text", x = min((predicted.distance$log_tdr)) + diff(range((predicted.distance$log_tdr)))/2, y =6.8, label = "***", color = "black", size = 4)
+#nd <- data.frame(log_TotalSub = mean(near$log_TotalSub), 
+#                 log_tdr = seq(2.7, 7.3, 0.05))
+#predicted.distance <- augment(top_model_wd_o, 
+#                              newdata = nd, 
+#                              se_fit = TRUE)
+#dist_tdr <- ggplot(near, aes(x = log_tdr, y = log(RetreatDist))) + 
+#  geom_point(color = "grey", 
+#             size = 1) +
+#  geom_line(aes(x = log_tdr, y = .fitted), 
+#            size = 1, 
+#            color = coloro, 
+#            data = predicted.distance) + 
+#  geom_ribbon(aes(x = log_tdr, 
+#                  ymin = .fitted - 1.96 * .se.fit, 
+#                  ymax = .fitted + 1.96 * .se.fit), 
+#              fill = coloro, 
+#              data = predicted.distance, 
+#              inherit.aes = FALSE, 
+#              alpha = 0.25) +
+##  scale_y_continuous(limits = c(min(log(near$RetreatDist)), max(log(near$RetreatDist)) + 0.1 * diff(range(log(near$RetreatDist))))) + 
+#  scale_y_continuous(limits = c(2, 7), breaks = c(2, 3, 4, 5, 6, 7)) +  
+#  theme_classic() +
+#  xlab("Road Disturbance [log(vehicles/day/m)]") +
+#  ylab("Distance from Focal Web \nto Neighbor Web [log(cm)]") + 
+#  theme(text = element_text(size = 10)) + 
+#  theme(axis.text.x = element_text(colour = "black", size = 10)) + 
+#  theme(axis.text.y = element_text(colour = "black", size = 10)) +
+#  theme(axis.title.x = element_blank(), 
+#        axis.title.y = element_blank(), 
+#        axis.text.y = element_blank(),
+#        axis.text.x = element_blank()) + 
+##  annotate(geom = "text", x = min((predicted.distance$log_tdr)) + diff(range((predicted.distance$log_tdr)))/2, y = max(log(near$RetreatDist)), label = "***", color = "black", size = 4)
+#    annotate(geom = "text", x = min((predicted.distance$log_tdr)) + diff(range((predicted.distance$log_tdr)))/2, y =6.8, label = "***", color = "black", size = 4)
 
 dist_plant
-dist_tdr
+#dist_tdr
 ```
@@
                               se_fit = TRUE)
-dist_forest_plant <- ggplot(near_forest, aes(x = log_TotalSub, y = log(RetreatDist))) + 
-  geom_point(color = "grey", 
+dist_forest_plant <- ggplot(near, aes(x = log_TotalSub, y = log(RetreatDist))) + 
+  geom_point(aes(color = Location), alpha = 0.5, 
              size = 1) +
@@
   scale_y_continuous(limits = c(4, 7), breaks = c(4, 5, 6, 7)) +  
+  scale_color_manual(values = c("Urban Center" = "#d95f02", "Urban Forest" = "#1b9e77")) +
   theme_classic() +
@@
   theme(axis.title.x = element_blank(), 
-        axis.title.y = element_blank()) + 
+        axis.title.y = element_blank(),
+        legend.position = "none") + 
 #  theme(axis.text.x = element_blank(), 
@@
                               se_fit = TRUE)
-dist_forest_tdh <- ggplot(near_forest, aes(x = log_tdh, y = log(RetreatDist))) + 
+dist_forest_tdh <- ggplot(near, aes(x = log_tdh, y = log(RetreatDist))) + 
   geom_point(color = "grey", 
@@
 # Plant Species Richness
-nd <- data.frame(log_TotalSub = seq(0, 1.8, 0.02), 
-                 spec_rad = mean(near_center$spec_rad),
-                 road_length_m = mean(near_center$road_length_m))
+#nd <- data.frame(log_TotalSub = seq(0, 1.8, 0.02), 
+#                 spec_rad = mean(near_center$spec_rad),
+#                 road_length_m = mean(near_center$road_length_m))
+#predicted.distance <- augment(top_model_wd_c, 
+#                              newdata = nd, 
+#                              se_fit = TRUE)
+#dist_center_plant <- ggplot(near_center, aes(x = log_TotalSub, y = log(RetreatDist))) + 
+#  geom_point(color = "grey", 
+#             size = 1) +
+#  geom_line(aes(x = log_TotalSub, y = .fitted), 
+#            size = 1, 
+#            color = colorc, 
+#            data = predicted.distance) + 
+#  geom_ribbon(aes(x = log_TotalSub, 
+#                  ymin = .fitted - 1.96 * .se.fit, 
+#                  ymax = .fitted + 1.96 * .se.fit), 
+#              fill = colorc, 
+#              data = predicted.distance, 
+#              inherit.aes = FALSE, 
+#              alpha = 0.25) +
+##  scale_y_continuous(limits = c(min(log(near_center$RetreatDist)), max(log(near_center$RetreatDist)) + 0.1 * diff(range(log(near_center$RetreatDist))))) +  
+#  scale_y_continuous(limits = c(2, 7), breaks = c(2, 3, 4, 5, 6, 7)) +  
+#  theme_classic() +
+#  xlab("Plant Species Richness [log()]") +
+#  ylab("Distance from Focal Web \nto Neighbor Web [log(cm)]") + 
+#  theme(text = element_text(size = 10)) + 
+#  theme(axis.text.x = element_text(colour = "black", size = 10)) + 
+#  theme(axis.text.y = element_text(colour = "black", size = 10)) +
+#  theme(axis.title.x = element_blank(), 
+#        axis.title.y = element_blank()) + 
+##  theme(axis.text.x = element_blank(), 
+##        axis.text.y = element_blank()) +
+##  annotate(geom = "text", x = min(predicted.distance$log_TotalSub) + diff(range(predicted.distance$log_TotalSub))/2, y = max(log(near_center$RetreatDist)), label = "***", color = "black", size = 4)
+#  annotate(geom = "text", x = min(predicted.distance$log_TotalSub) + diff(range(predicted.distance$log_TotalSub))/2, y = 7, label = "***", color = "black", size = 4)
+
+# Spectral Radiance
+#nd <- data.frame(log_TotalSub = mean(near_center$log_TotalSub), 
+#                 spec_rad = seq(149, 163, 0.15),
+#                 road_length_m = mean(near_center$road_length_m))
+#predicted.distance <- augment(top_model_wd_c, 
+#                              newdata = nd, 
+#                              se_fit = TRUE)
+#dist_center_spec <- ggplot(near_center, aes(x = (spec_rad), y = log(RetreatDist))) + 
+#  geom_point(color = "grey", 
+#             size = 1) +
+#  geom_line(aes(x = (spec_rad), y = .fitted), 
+#            size = 1, 
+#            color = colorc, 
+#            data = predicted.distance) + 
+#  geom_ribbon(aes(x = (spec_rad), 
+#                  ymin = .fitted - 1.96 * .se.fit, 
+#                  ymax = .fitted + 1.96 * .se.fit), 
+#              fill = colorc, 
+#              data = predicted.distance, 
+#              inherit.aes = FALSE, 
+#              alpha = 0.25) +
+##  scale_y_continuous(limits = c(min(log(near_center$RetreatDist)), max(log(near_center$RetreatDist)) + 0.1 * diff(range(log(near_center$RetreatDist))))) +  
+#  scale_y_continuous(limits = c(2, 7), breaks = c(2, 3, 4, 5, 6, 7)) +  
+#  theme_classic() +
+#  xlab("Spectral Radiance \n[Watts/(m² * sr * µm)]") + 
+#  ylab("Distance from Focal Web \nto Neighbor Web [log(cm)]") + 
+#  theme(text = element_text(size = 10)) + 
+#  theme(axis.text.x = element_text(colour = "black", size = 10)) + 
+#  theme(axis.text.y = element_text(colour = "black", size = 10)) +
+#  theme(axis.title.x = element_blank(), 
+#        axis.title.y = element_blank(), 
+#        axis.text.y = element_blank()) + 
+##  theme(axis.text.x = element_blank()) +
+##  annotate(geom = "text", x = min((predicted.distance$spec_rad)) + diff(range((predicted.distance$spec_rad)))/2, y = max(log(near_center$RetreatDist)), label = "***", color = "black", size = 4)
+#  annotate(geom = "text", x = min((predicted.distance$spec_rad)) + diff(range((predicted.distance$spec_rad)))/2, y = 7, label = "***", color = "black", size = 4)
+
+# Road Length
+nd <- data.frame(road_length_m = seq(47, 117, 0.6))
 predicted.distance <- augment(top_model_wd_c, 
@@
                               se_fit = TRUE)
-dist_center_plant <- ggplot(near_center, aes(x = log_TotalSub, y = log(RetreatDist))) + 
-  geom_point(color = "grey", 
-             size = 1) +
-  geom_line(aes(x = log_TotalSub, y = .fitted), 
-            size = 1, 
-            color = colorc, 
-            data = predicted.distance) + 
-  geom_ribbon(aes(x = log_TotalSub, 
-                  ymin = .fitted - 1.96 * .se.fit, 
-                  ymax = .fitted + 1.96 * .se.fit), 
-              fill = colorc, 
-              data = predicted.distance, 
-              inherit.aes = FALSE, 
-              alpha = 0.25) +
-#  scale_y_continuous(limits = c(min(log(near_center$RetreatDist)), max(log(near_center$RetreatDist)) + 0.1 * diff(range(log(near_center$RetreatDist))))) +  
-  scale_y_continuous(limits = c(2, 7), breaks = c(2, 3, 4, 5, 6, 7)) +  
-  theme_classic() +
-  xlab("Plant Species Richness [log()]") +
-  ylab("Distance from Focal Web \nto Neighbor Web [log(cm)]") + 
-  theme(text = element_text(size = 10)) + 
-  theme(axis.text.x = element_text(colour = "black", size = 10)) + 
-  theme(axis.text.y = element_text(colour = "black", size = 10)) +
-  theme(axis.title.x = element_blank(), 
-        axis.title.y = element_blank()) + 
-#  theme(axis.text.x = element_blank(), 
-#        axis.text.y = element_blank()) +
-#  annotate(geom = "text", x = min(predicted.distance$log_TotalSub) + diff(range(predicted.distance$log_TotalSub))/2, y = max(log(near_center$RetreatDist)), label = "***", color = "black", size = 4)
-  annotate(geom = "text", x = min(predicted.distance$log_TotalSub) + diff(range(predicted.distance$log_TotalSub))/2, y = 7, label = "***", color = "black", size = 4)
-
-# Spectral Radiance
-nd <- data.frame(log_TotalSub = mean(near_center$log_TotalSub), 
-                 spec_rad = seq(149, 163, 0.15),
-                 road_length_m = mean(near_center$road_length_m))
-predicted.distance <- augment(top_model_wd_c, 
-                              newdata = nd, 
-                              se_fit = TRUE)
-dist_center_spec <- ggplot(near_center, aes(x = (spec_rad), y = log(RetreatDist))) + 
-  geom_point(color = "grey", 
-             size = 1) +
-  geom_line(aes(x = (spec_rad), y = .fitted), 
-            size = 1, 
-            color = colorc, 
-            data = predicted.distance) + 
-  geom_ribbon(aes(x = (spec_rad), 
-                  ymin = .fitted - 1.96 * .se.fit, 
-                  ymax = .fitted + 1.96 * .se.fit), 
-              fill = colorc, 
-              data = predicted.distance, 
-              inherit.aes = FALSE, 
-              alpha = 0.25) +
-#  scale_y_continuous(limits = c(min(log(near_center$RetreatDist)), max(log(near_center$RetreatDist)) + 0.1 * diff(range(log(near_center$RetreatDist))))) +  
-  scale_y_continuous(limits = c(2, 7), breaks = c(2, 3, 4, 5, 6, 7)) +  
-  theme_classic() +
-  xlab("Spectral Radiance \n[Watts/(m² * sr * µm)]") + 
-  ylab("Distance from Focal Web \nto Neighbor Web [log(cm)]") + 
-  theme(text = element_text(size = 10)) + 
-  theme(axis.text.x = element_text(colour = "black", size = 10)) + 
-  theme(axis.text.y = element_text(colour = "black", size = 10)) +
-  theme(axis.title.x = element_blank(), 
-        axis.title.y = element_blank(), 
-        axis.text.y = element_blank()) + 
-#  theme(axis.text.x = element_blank()) +
-#  annotate(geom = "text", x = min((predicted.distance$spec_rad)) + diff(range((predicted.distance$spec_rad)))/2, y = max(log(near_center$RetreatDist)), label = "***", color = "black", size = 4)
-  annotate(geom = "text", x = min((predicted.distance$spec_rad)) + diff(range((predicted.distance$spec_rad)))/2, y = 7, label = "***", color = "black", size = 4)
-
-# Road Length
-nd <- data.frame(log_TotalSub = mean(near_center$log_TotalSub), 
-                 spec_rad = mean(near_center$spec_rad),
-                 road_length_m = seq(47, 117, 0.6))
-predicted.distance <- augment(top_model_wd_c, 
-                              newdata = nd, 
-                              se_fit = TRUE)
-dist_center_road <- ggplot(near_center, aes(x = (road_length_m), y = log(RetreatDist))) + 
-  geom_point(color = "grey", 
+dist_center_road <- ggplot(near, aes(x = (road_length_m), y = log(RetreatDist))) + 
+  geom_point(aes(color = Location), alpha = 0.5, 
              size = 1) +
@@
   scale_y_continuous(limits = c(2, 7), breaks = c(2, 3, 4, 5, 6, 7)) +  
+  scale_color_manual(values = c("Urban Center" = "#d95f02", "Urban Forest" = "#1b9e77")) +
   theme_classic() +
   xlab("Total Road Length [m]") +
-  ylab("Distance from Focal Web \nto Neighbor Web [log(cm)]") + 
+  ylab("Distance from Focal Web \nto Neighbor Web [ln(cm)]") + 
   theme(text = element_text(size = 10)) + 
@@
         axis.title.y = element_blank(), 
-        axis.text.y = element_blank()) + 
+        #axis.text.y = element_blank(),
+        legend.position = "none") + 
 #  theme(axis.text.x = element_blank()) +
 #  annotate(geom = "text", x = min((predicted.distance$road_length_m)) + diff(range((predicted.distance$road_length_m)))/2, y = max(log(near_center$RetreatDist)), label = "***", color = "black", size = 4)
-  annotate(geom = "text", x = min((predicted.distance$road_length_m)) + diff(range((predicted.distance$road_length_m)))/2, y = 7, label = "***", color = "black", size = 4)
-
-dist_center_plant
-dist_center_spec
+  annotate(geom = "text", x = 55, y = 6.8, label = "*", color = "black", size = 4)
+
+#dist_center_plant
+#dist_center_spec
 dist_center_road
@@
 comp <- glht(dist_land, linfct = mcp(Land = "Tukey"))
+summary(comp)
+
+dist_land_nb <- glm.nb(round(RetreatDist, 0) ~ Land, data = near)
+summary(dist_land_nb)
+car::Anova(dist_land_nb, test.statistic = "LR")
+comp <- glht(dist_land_nb, linfct = mcp(Land = "Tukey"))
 summary(comp)
@@
 nd <- data.frame(Land = factor(levels(sites$Land)))
-predictions <- augment(dist_land, newdata = nd, se_fit = TRUE, type.predict = "response")
+predictions <- augment(dist_land_nb, newdata = nd, se_fit = TRUE, type.predict = "response")
 predictions <- predictions %>% 
@@
   geom_jitter(color = "grey", width = 0.1, size = 0.5) +
-  geom_point(aes(x = Land, y = response, color = Land), size = 1, data = predictions) + 
+  geom_point(aes(x = Land, y = response, color = Land), size = 2, data = predictions) + 
   geom_errorbar(aes(x = Land, 
@@
   xlab("Land Cover Class") +
-  ylab("Distance from Focal \nWeb to Neighbor Web (cm)") + 
+  ylab("Distance from Focal \nWeb to Neighbor Web [cm]") + 
   theme(text = element_text(size = 10)) + 
@@
   theme(legend.position = "none") +
-  theme(axis.text.x = element_text(angle = 90, vjust = 1, hjust=1)) +
-  annotate(geom="text", x=1, y=max(near$RetreatDist), label="A", color="black", size = 3) +
-  annotate(geom="text", x=2, y=max(near$RetreatDist), label="B", color="black", size = 3) +
-  annotate(geom="text", x=3, y=max(near$RetreatDist), label="C", color="black", size = 3) +
-  annotate(geom="text", x=4, y=max(near$RetreatDist), label="D", color="black", size = 3) +
-  annotate(geom="text", x=5, y=max(near$RetreatDist), label="E", color="black", size = 3)
+  theme(axis.text.x = element_text(angle = 90, vjust = 1, hjust=1))# +
+  #annotate(geom="text", x=1, y=max(near$RetreatDist), label="A", color="black", size = 3) +
+  #annotate(geom="text", x=2, y=max(near$RetreatDist), label="A", color="black", size = 3) +
+  #annotate(geom="text", x=3, y=max(near$RetreatDist), label="AC", color="black", size = 3) +
+  #nnotate(geom="text", x=4, y=max(near$RetreatDist), label="B", color="black", size = 3) +
+  #annotate(geom="text", x=5, y=max(near$RetreatDist), label="B", color="black", size = 3)
 
@@
 summary(height)
+
+height.nb <- glmer.nb(round(RetreatHeight, 0) ~ Location + (1 | ID), data = webs)
+summary(height.nb)
+
+subheight.nb <- glmer.nb(round(SubHeight, 0) ~ Location + (1 | ID), data = webs)
+summary(subheight.nb)
+
 height2 <- lmer(log(RetreatHeight) ~ Location + (1 | ID), data = webs)
 summary(height2)
+
+height_prop <- glmmTMB(Proportion ~ Location + (1|ID), data = webs, family = "beta")
+summary(height_prop)
 ```
@@
 # As is, Poisson
-test_height <- augment(height, data = webs)
+test_height <- augment(height.nb, data = webs)
 resid_height <- ggplot(test_height, aes(x = .fitted, y = .resid)) + 
@@
 ```{r height_location_graph, echo = FALSE}
+# Negative Binomial
+predictions <- expand.grid(Location = levels(factor(webs$Location)))
+predictions$response <- predict(height.nb, newdata = predictions, se.fit = TRUE, re.form = NA, type = "response")
+
+myFunc <- function(mm) {
+    predict(mm, newdata = predictions, re.form = ~0, type = "response")
+}
+#bigBoot_height_location_nb <- bootMer(height.nb, myFunc, nsim = 1000)
+#saveRDS(bigBoot_height_location_nb, file = "bootstrapping/bigBoot_height_location_nb.Rds")
+bigBoot_height_location_nb <- readRDS("bootstrapping/bigBoot_height_location_nb.Rds")
+predSE <- t(apply(bigBoot_height_location_nb$t, MARGIN = 2, FUN = sd))
+predictions$SE <- predSE[1, ]
+#predictions2 <- summary(emmeans(height, ~Location | Neighbor,type = "response"))
+
+nb_plot_height <- ggplot(webs, aes(x = Location, y = RetreatHeight)) + 
+  geom_jitter(color = "grey", width = 0.1) +
+  geom_point(aes(x = Location, y = response, color = Location), size = 2, data = predictions) +
+  geom_errorbar(aes(x= Location, 
+                    ymin = response - SE, 
+                    ymax = response + SE, 
+                    color = Location), data = predictions, inherit.aes = FALSE, width = 0.15, size = 1) +
+    scale_color_manual(values = c("Urban Center" = "#d95f02", "Urban Forest" = "#1b9e77")) +
+    scale_x_discrete(labels=c("Urban Forest" = "Urban \nForest \nN = 10", "Urban Center" = "Urban \nCenter \nN = 12")) +
+    theme_classic() +
+    scale_y_continuous(limits = c(0, 210), breaks = c(0, 35, 70, 105, 140, 175, 210)) +
+    ylab("Web Height [cm]") + 
+    theme(text = element_text(size = 10)) + 
+    theme(axis.text.x = element_text(colour = "black", size = 10)) + 
+    theme(axis.text.y = element_text(colour = "black", size = 10),
+        axis.title.x = element_blank()) +
+    theme(legend.position = "none") +
+    annotate(geom = "text", x = 1.5, y = 210, label = "*", color = "black", size = 5)
+
 # raw data
@@
           log_plot_height,
-          labels = c("Raw Data", "Poisson Distribution", "Log-Transformed"),
+          nb_plot_height,
+          labels = c("Raw Data", "Poisson Distribution", "Log-Transformed", "Negative Binomial"),
           nrow = 1, 
@@
 
-**Webs are significantly higher in the urban forest** than the urban center (z = -2.384, df = 1, 21, p = 0.017).
+**Webs are significantly higher in the urban forest** than the urban center (z = -2.44, df = 1, 21, p = 0.015).
 
@@
 
+```{r height_predictors_stats_nb}
+#overall
+global <- glmer.nb(round(RetreatHeight, 0) ~ log_TotalSub + log_tdr + log_tdh + (1 | ID), data = webs)
+options(na.action = "na.fail") # Required for dredge to run
+model_dredge <- dredge(global, beta = "none", evaluate = TRUE, rank = AICc)
+options(na.action = "na.omit") # set back to default
+top_model_wh_o <- get.models(model_dredge, subset = 1)[[1]]
+out <- summary(top_model_wh_o)
+out
+info <- out[[10]]
+# TotalSub
+#exp(info[3, 1])
+#exp(info[3, 2])
+#Traffic_Dist_Road
+#exp(info[2, 1])
+#exp(info[2, 1])
+
+r.squaredGLMM(top_model_wh_o) # trigamma R2m
+model.sel(model_dredge) #estimates same signs
+summary(model.avg(model_dredge, subset = delta <= 2))
+
+#tdr
+#exp(info[2, 1])
+#exp(info[2, 2])
+#TotalSub
+#exp(info[3, 1])
+#exp(info[3, 2])
+#tdh
+#exp(info[4, 1])
+#exp(info[4, 2])
+car::vif(get.models(model_dredge, 5)[[1]]) # looking for less than 2
+
+# Urban Forest
+webs_forest <- webs_forest %>% 
+  mutate(tree100m_frac = I(tree100m/100))
+global <- glmer.nb(round(RetreatHeight, 0) ~ tree100m_frac + log_TotalSub + log_tdr + log_tdh + log_patch + (1 | ID), data = webs_forest, control = glmerControl(optimizer = "bobyqa", optCtrl = list(maxfun = 2e4)))
+options(na.action = "na.fail") # Required for dredge to run
+model_dredge <- dredge(global, beta = "none", evaluate = TRUE, rank = AICc)
+options(na.action = "na.omit") # set back to default
+top_model_wh_f <- get.models(model_dredge, subset = 1)[[1]]
+out <- summary(top_model_wh_f)
+out
+info <- out[[10]]
+
+#tree
+#exp(info[2, 1])
+#exp(info[2, 2])
+
+r.squaredGLMM(top_model_wh_f) #trigamma R2m
+model.sel(model_dredge) #estimates same signs
+summary(model.avg(model_dredge, subset = delta <= 2))
+
+#tree
+#exp(info[2, 1])
+#exp(info[2, 2])
+#TotalSub
+#exp(info[3, 1])
+#exp(info[3, 2])
+#tdr
+#exp(info[4, 1])
+#exp(info[4, 2])
+
+#car::vif(get.models(model_dredge, 1)[[1]]) # looking for less than 2
+
+webs_center$road_length_m_sc <- scale(webs_center$road_length_m, center = FALSE)
+
+# Urban Center
+global <- glmer.nb(round(RetreatHeight, 0) ~ log_TotalSub + log_tdr + log_tdh + scale(spec_rad, center = FALSE) + log_patch + road_length_m_sc + (1 | ID), data = webs_center)#, control = glmerControl(optimizer = "bobyqa", optCtrl = list(maxfun = 2e4)))
+options(na.action = "na.fail") # Required for dredge to run
+model_dredge <- dredge(global, beta = "none", evaluate = T, rank = AICc)
+options(na.action = "na.omit") # set back to default
+top_model_wh_c <- get.models(model_dredge, subset = 1)[[1]]
+out <- summary(top_model_wh_c)
+out
+info <- out[[10]]
+#TotalSub
+#exp(info[2, 1])
+#exp(info[2, 2])
+
+r.squaredGLMM(top_model_wh_c) 
+model.sel(model_dredge) #estimates same signs
+summary(model.avg(model_dredge, subset = delta <= 2))
+
+#TotalSub
+#exp(info[2, 1])
+#exp(info[2, 2])
+#road length
+#exp(info[3, 1])
+#exp(info[3, 2])
+#tdh
+#exp(info[4, 1])
+#exp(info[4, 2])
+#tdr
+#exp(info[5, 1])
+#exp(info[5, 2])
+#patch
+#exp(info[6, 1])
+#exp(info[6, 2])
+#spec_rad
+#exp(info[7, 1])
+#exp(info[7, 2])
+#car::vif(get.models(model_dredge, 1)[[1]]) # looking for less than 2
+```
+
 ```{r height_predictor_overall_graphs}
@@
 }
-#bigBoot_height_overall_plant <- bootMer(top_model_wh_o, myFunc, nsim = 1000)
-#saveRDS(bigBoot_height_overall_plant, file = "bootstrapping/bigBoot_height_overall_plant.Rds")
-bigBoot_height_overall_plant <- readRDS("bootstrapping/bigBoot_height_overall_plant.Rds")
-predSE <- t(apply(bigBoot_height_overall_plant$t, MARGIN = 2, FUN = sd))
+#bigBoot_height_overall_plant_nb <- bootMer(top_model_wh_o, myFunc, nsim = 1000)
+#saveRDS(bigBoot_height_overall_plant_nb, file = "bootstrapping/bigBoot_height_overall_plant_nb.Rds")
+bigBoot_height_overall_plant_nb <- readRDS("bootstrapping/bigBoot_height_overall_plant_nb.Rds")
+predSE <- t(apply(bigBoot_height_overall_plant_nb$t, MARGIN = 2, FUN = sd))
 predictions$SE <- predSE[1, ]
@@
 height_plant <- ggplot(webs, aes(x = log_TotalSub, y = log(RetreatHeight))) + 
-  geom_point(color = "grey", 
+  geom_point(aes(color = Location), alpha = 0.7, 
              size = 1) +
@@
   scale_y_continuous(limits = c(-2.5, 6), breaks = c(-2, 0, 2, 4, 6)) + 
-  theme_classic() +
-  xlab("Plant Species Richness [log()]") +
-  ylab("Web Height [log(cm)]") + 
+  scale_color_manual(values = c("Urban Center" = "#d95f02", "Urban Forest" = "#1b9e77")) +
+  theme_classic() +
+  xlab("Plant Species Richness [ln()]") +
+  ylab("Web Height [ln(cm)]") + 
   theme(text = element_text(size = 10)) + 
@@
 }
-#bigBoot_height_overall_tdr <- bootMer(top_model_wh_o, myFunc, nsim = 1000)
-#saveRDS(bigBoot_height_overall_tdr, file = "bootstrapping/bigBoot_height_overall_tdr.Rds")
-bigBoot_height_overall_tdr <- readRDS("bootstrapping/bigBoot_height_overall_tdr.Rds")
-predSE <- t(apply(bigBoot_height_overall_tdr$t, MARGIN = 2, FUN = sd))
+#bigBoot_height_overall_tdr_nb <- bootMer(top_model_wh_o, myFunc, nsim = 1000)
+#saveRDS(bigBoot_height_overall_tdr_nb, file = "bootstrapping/bigBoot_height_overall_tdr_nb.Rds")
+bigBoot_height_overall_tdr_nb <- readRDS("bootstrapping/bigBoot_height_overall_tdr_nb.Rds")
+predSE <- t(apply(bigBoot_height_overall_tdr_nb$t, MARGIN = 2, FUN = sd))
 predictions$SE <- predSE[1, ]
@@
 height_tdr <- ggplot(webs, aes(x = log_tdr, y = log(RetreatHeight))) + 
-  geom_point(color = "grey", 
+  geom_point(aes(color = Location), alpha = 0.7, 
              size = 1) +
@@
   scale_y_continuous(limits = c(-2.5, 6), breaks = c(-2, 0, 2, 4, 6)) +  
-  theme_classic() +
-  xlab("Road Disturbance [log(vehicles/day/m)]") +
-  ylab("Web Height [log(cm)]") + 
+  scale_color_manual(values = c("Urban Center" = "#d95f02", "Urban Forest" = "#1b9e77")) +
+  theme_classic() +
+  xlab("Road Disturbance [ln(vehicles/day/m)]") +
+  ylab("Web Height [ln(cm)]") + 
   theme(text = element_text(size = 10)) + 
@@
         axis.title.y = element_blank(), 
-        axis.text.y = element_blank()) + 
+        #axis.text.y = element_blank(),
+        legend.position = "none") + 
 #  theme(axis.text.x = element_blank()) +
 #  annotate(geom = "text", x = min(predictions$log_tdr) + diff(range(predictions$log_tdr))/2, y = max(log(webs$RetreatHeight)), label = "N. S.", color = "black", size = 4)
-    annotate(geom = "text", x = min(predictions$log_tdr) + diff(range(predictions$log_tdr))/2, y = 5.8, label = "N. S.", color = "black", size = 4)
+    annotate(geom = "text", x = min(predictions$log_tdr) + diff(range(predictions$log_tdr))/2, y = 5.8, label = "N. S.", color = "black", size = 3)
 
@@
 
+webs <- webs %>% 
+  mutate(tree100m_frac = I(tree100m/100))
+
 # Tree
@@
 }
-#bigBoot_height_forest_tree <- bootMer(top_model_wh_f, myFunc, nsim = 1000)
-#saveRDS(bigBoot_height_forest_tree, file = "bootstrapping/bigBoot_height_forest_tree.Rds")
-bigBoot_height_forest_tree <- readRDS("bootstrapping/bigBoot_height_forest_tree.Rds")
-predSE <- t(apply(bigBoot_height_forest_tree$t, MARGIN = 2, FUN = sd))
+#bigBoot_height_forest_tree_nb <- bootMer(top_model_wh_f, myFunc, nsim = 1000)
+#saveRDS(bigBoot_height_forest_tree_nb, file = "bootstrapping/bigBoot_height_forest_tree_nb.Rds")
+bigBoot_height_forest_tree_nb <- readRDS("bootstrapping/bigBoot_height_forest_tree_nb.Rds")
+predSE <- t(apply(bigBoot_height_forest_tree_nb$t, MARGIN = 2, FUN = sd))
 predictions$SE <- predSE[1, ]
 
-height_forest_tree <- ggplot(webs_forest, aes(x = log(tree100m_frac), y = log(RetreatHeight))) + 
-  geom_point(color = "grey", 
+height_forest_tree <- ggplot(webs, aes(x = (tree100m_frac), y = log(RetreatHeight))) + 
+  geom_point(aes(color = Location), alpha = 0.5, 
              size = 1) +
-  geom_line(aes(x = log(tree100m_frac), y = log(response)), 
+  geom_line(aes(x = (tree100m_frac), y = log(response)), 
             size = 1, 
@@
             data = predictions) + 
-  geom_ribbon(aes(x = log(tree100m_frac), 
+  geom_ribbon(aes(x = (tree100m_frac), 
                   ymin = log(response - 1.96 * SE), 
@@
               alpha = 0.25) +
-  scale_y_continuous(limits = c(min(log(webs_forest$RetreatHeight)), max(log(webs_forest$RetreatHeight)) + 0.1 * diff(range(log(webs_forest$RetreatHeight))))) +  
-  theme_classic() +
-  xlab("Proportion of Tree Cover in 100-Meter Buffer of Site [log()]") +
-  ylab("Web Height [log(cm)]") + 
+  scale_y_continuous(limits = c(0, 5.2), breaks = c(0, 1, 2, 3, 4, 5)) +  
+  scale_color_manual(values = c("Urban Center" = "#d95f02", "Urban Forest" = "#1b9e77")) +
+  theme_classic() +
+  xlab("Proportion of Tree Cover in 100-Meter Buffer of Site [ln()]") +
+  ylab("Web Height [ln(cm)]") + 
   theme(text = element_text(size = 10)) + 
@@
   theme(axis.title.x = element_blank(), 
-        axis.title.y = element_blank()) + 
+        axis.title.y = element_blank(),
+        legend.position = "none") + 
 #  theme(axis.text.x = element_blank(), 
 #        axis.text.y = element_blank()) +
-  annotate(geom = "text", x = min(log(predictions$tree100m_frac)) + diff(range(log(predictions$tree100m_frac)))/2, y = max(log(webs_forest$RetreatHeight)), label = "**", color = "black", size = 4)
+  annotate(geom = "text", x = 0.33, y = 5, label = "**", color = "black", size = 4)
 
@@
 
+webs$road_length_m_sc <- scale(webs$road_length_m, center = FALSE)
+
 # Plant Species Richness
-predictions <- expand.grid(log_TotalSub = seq(0, 1.80, 0.02))
+predictions <- expand.grid(log_TotalSub = seq(0, 1.80, 0.02),
+                           road_length_m_sc = mean(webs_center$road_length_m_sc))
 predictions$response <- predict(top_model_wh_c, newdata = predictions, se.fit = TRUE, re.form = NA, type = "response")
@@
 }
-#bigBoot_height_center_plant <- bootMer(top_model_wh_c, myFunc, nsim = 1000)
-#saveRDS(bigBoot_height_center_plant, file = "bootstrapping/bigBoot_height_center_plant.Rds")
-bigBoot_height_center_plant <- readRDS("bootstrapping/bigBoot_height_center_plant.Rds")
-predSE <- t(apply(bigBoot_height_center_plant$t, MARGIN = 2, FUN = sd))
+#bigBoot_height_center_plant_nb <- bootMer(top_model_wh_c, myFunc, nsim = 1000)
+#saveRDS(bigBoot_height_center_plant_nb, file = "bootstrapping/bigBoot_height_center_plant_nb.Rds")
+bigBoot_height_center_plant_nb <- readRDS("bootstrapping/bigBoot_height_center_plant_nb.Rds")
+predSE <- t(apply(bigBoot_height_center_plant_nb$t, MARGIN = 2, FUN = sd))
 predictions$SE <- predSE[1, ]
 
-height_center_plant <- ggplot(webs_center, aes(x = log_TotalSub, y = log(RetreatHeight))) + 
-  geom_point(color = "grey", 
+height_center_plant <- ggplot(webs, aes(x = log_TotalSub, y = log(RetreatHeight))) + 
+  geom_point(aes(color = Location), alpha = 0.5, 
              size = 1) +
@@
               alpha = 0.25) +
-  scale_y_continuous(limits = c(min(log(webs_forest$RetreatHeight)) - 4, max(log(webs_forest$RetreatHeight)) + 0.1 * diff(range(log(webs_forest$RetreatHeight))))) +  
-  theme_classic() +
-  xlab("Plant Species Richness [log()]") +
-  ylab("Web Height [log(cm)]") + 
+  scale_y_continuous(limits = c(0, 5.2), breaks = c(0, 1, 2, 3, 4, 5)) +  
+  scale_color_manual(values = c("Urban Center" = "#d95f02", "Urban Forest" = "#1b9e77")) +
+  theme_classic() +
+  xlab("Plant Species Richness [ln()]") +
+  ylab("Web Height [ln(cm)]") + 
   theme(text = element_text(size = 10)) + 
@@
   theme(axis.title.x = element_blank(), 
-        axis.title.y = element_blank()) + 
+        axis.title.y = element_blank(),
+        legend.position = "none") + 
 #  theme(axis.text.x = element_blank(), 
 #        axis.text.y = element_blank()) +
-  annotate(geom = "text", x = min((predictions$log_TotalSub)) + diff(range((predictions$log_TotalSub)))/2, y = max(log(webs_forest$RetreatHeight)), label = "N.S.", color = "black", size = 4)
+  annotate(geom = "text", x = 1.6, y = 5, label = "N.S.", color = "black", size = 4)
+
+# Road Length
+predictions <- expand.grid(log_TotalSub = mean(webs_center$log_TotalSub),
+                           road_length_m_sc = seq(0.5, 1.50, 0.01))
+predictions$response <- predict(top_model_wh_c, newdata = predictions, se.fit = TRUE, re.form = NA, type = "response")
+
+myFunc <- function(mm) {
+    predict(mm, newdata = predictions, re.form = ~0, type = "response")
+}
+#bigBoot_height_center_road_nb <- bootMer(top_model_wh_c, myFunc, nsim = 1000)
+#saveRDS(bigBoot_height_center_road_nb, file = "bootstrapping/bigBoot_height_center_road_nb.Rds")
+bigBoot_height_center_road_nb <- readRDS("bootstrapping/bigBoot_height_center_road_nb.Rds")
+predSE <- t(apply(bigBoot_height_center_road_nb$t, MARGIN = 2, FUN = sd))
+predictions$SE <- predSE[1, ]
+
+height_center_road <- ggplot(webs, aes(x = road_length_m_sc, y = log(RetreatHeight))) + 
+  geom_point(aes(color = Location), alpha = 0.5, 
+             size = 1) +
+  geom_line(aes(x = road_length_m_sc, y = log(response)), 
+            size = 1, 
+            color = colorc, 
+            data = predictions) + 
+  geom_ribbon(aes(x = road_length_m_sc, 
+                  ymin = log(response - 1.96 * SE), 
+                  ymax = log(response + 1.96 * SE)), 
+              fill = colorc, 
+              data = predictions, 
+              inherit.aes = FALSE, 
+              alpha = 0.25) +
+  scale_y_continuous(limits = c(-2.5, 6), breaks = c(-2, 0, 2, 4, 6)) +  
+  scale_color_manual(values = c("Urban Center" = "#d95f02", "Urban Forest" = "#1b9e77")) +  theme_classic() +
+  xlab("Plant Species Richness [ln()]") +
+  ylab("Web Height [ln(cm)]") + 
+  theme(text = element_text(size = 10)) + 
+  theme(axis.text.x = element_text(colour = "black", size = 10)) + 
+  theme(axis.text.y = element_text(colour = "black", size = 10)) +
+  theme(axis.title.x = element_blank(), 
+        axis.title.y = element_blank(),
+        legend.position = "none") + 
+#  theme(axis.text.x = element_blank(), 
+#        axis.text.y = element_blank()) +
+  annotate(geom = "text", x = 0.9, y = 5.8, label = "N.S.", color = "black", size = 3)
 
 height_center_plant
+height_center_road
 ```
@@
 comp <- glht(height_land, linfct = mcp(Land = "Tukey"))
+summary(comp)
+
+height_land_nb <- glmer.nb(round(RetreatHeight, 0) ~ Land + (1 | ID), data = webs)
+summary(height_land_nb)
+car::Anova(height_land_nb, type = 3)
+comp <- glht(height_land_nb, linfct = mcp(Land = "Tukey"))
 summary(comp)
@@
 predictions <- expand.grid(Land = levels(factor(webs$Land)))
-predictions$response <- predict(height_land, newdata = predictions, se.fit = TRUE, re.form = NA, type = "response")
+predictions$response <- predict(height_land_nb, newdata = predictions, se.fit = TRUE, re.form = NA, type = "response")
 
@@
 }
-#bigBoot_height_land <- bootMer(height_land, myFunc, nsim = 1000)
-#saveRDS(bigBoot_height_land, file = "bootstrapping/bigBoot_height_land.Rds")
-bigBoot_height_land <- readRDS("bootstrapping/bigBoot_height_land.Rds")
-predSE <- t(apply(bigBoot_height_land$t, MARGIN = 2, FUN = sd))
+#bigBoot_height_land_nb <- bootMer(height_land_nb, myFunc, nsim = 1000)
+#saveRDS(bigBoot_height_land_nb, file = "bootstrapping/bigBoot_height_land_nb.Rds")
+bigBoot_height_land_nb <- readRDS("bootstrapping/bigBoot_height_land_nb.Rds")
+predSE <- t(apply(bigBoot_height_land_nb$t, MARGIN = 2, FUN = sd))
 predictions$SE <- predSE[1, ]
@@
   xlab("Land Cover Class") +
-  ylab("Web Height [log(cm)]") + 
+  ylab("Web Height [cm]") + 
   theme(text = element_text(size = 10)) + 
@@
   theme(legend.position = "none") +
-  theme(axis.text.x = element_text(angle = 90, vjust = 1, hjust=1)) +
-  annotate(geom="text", x=1, y=max(webs$RetreatHeight), label="A", color="black", size = 3) +
-  annotate(geom="text", x=2, y=max(webs$RetreatHeight), label="A", color="black", size = 3) +
-  annotate(geom="text", x=3, y=max(webs$RetreatHeight), label="A", color="black", size = 3) +
-  annotate(geom="text", x=4, y=max(webs$RetreatHeight), label="A", color="black", size = 3) +
-  annotate(geom="text", x=5, y=max(webs$RetreatHeight), label="A", color="black", size = 3)
+  theme(axis.text.x = element_text(angle = 90, vjust = 1, hjust=1))# +
+  #annotate(geom="text", x=1, y=max(webs$RetreatHeight), label="A", color="black", size = 3) +
+  #annotate(geom="text", x=2, y=max(webs$RetreatHeight), label="A", color="black", size = 3) +
+  #annotate(geom="text", x=3, y=max(webs$RetreatHeight), label="A", color="black", size = 3) +
+  #annotate(geom="text", x=4, y=max(webs$RetreatHeight), label="A", color="black", size = 3) +
+  #annotate(geom="text", x=5, y=max(webs$RetreatHeight), label="A", color="black", size = 3)
 
@@
 
-main_row1 <- ggarrange(poisson_plot_search, poisson_plot_webs, poisson_plot_spiders, labels = c("a", "b", "c"), nrow = 1, font.label = list(size = 10))
-main_row2 <- ggarrange(poisson_plot_dist, poisson_plot_height, blankPlot, labels = c("d", "e", ""), nrow = 1, font.label = list(size = 10))
+main_row1 <- ggarrange(nb_plot_search, nb_plot_webs, nb_plot_spiders, labels = c("a", "b", "c"), nrow = 1, font.label = list(size = 10))
+main_row2 <- ggarrange(nb_plot_dist, nb_plot_height, blankPlot, labels = c("d", "e", ""), nrow = 1, font.label = list(size = 10))
+
 main <- ggarrange(main_row1, main_row2, nrow = 2, font.label = list(size = 10))
-
+main
+jpeg(filename = "manuscript/figures/main.jpeg", units = "cm", width = 17.4, height = 17.4, res = 300)
+print(main)
+dev.off()
 #saveRDS(main, "manuscript/figures/main.Rds")
+```
+
+### Predictors Plant
+
+```{r predictors_plant}
+webs_text <- as_ggplot(text_grob(paste("Number of \nWebs \n[ln()]"), size = 10))
+spiders_text <- as_ggplot(text_grob(paste("Number of \nSpiders \n[ln()]"), size = 10))
+dist_text <- as_ggplot(text_grob(paste("Nearest \nNeighbor \nDist. [ln(cm)]"), size = 10))
+height_text <- as_ggplot(text_grob(paste("Web \nHeight \n[ln(cm)]"), size = 10))
+plant_text <- as_ggplot(text_grob(paste("Plant Species Richness [ln()]"), size = 10))
+blankPlot <- ggplot()+geom_blank(aes(1,1)) + 
+  cowplot::theme_nothing()
+
+pred_plant <- ggarrange(webs_text, webs_plant, 
+                spiders_text, spiders_plant, 
+                dist_text, dist_plant, 
+                height_text, height_plant,
+                blankPlot, plant_text,
+                ncol = 2, nrow = 5, 
+                widths = c(0.3, 0.7), 
+                heights = c(0.24, 0.24, 0.24, 0.24, 0.04))
+
+jpeg(filename = "manuscript/figures/pred_plant.jpeg", units = "cm", width = 8.4, height = 17.4, res = 300)
+print(pred_plant)
+dev.off()
+```
+
+### Predictors Traffic Impact
+
+```{r predictors_traffic}
+webs_text <- as_ggplot(text_grob(paste("Number of \nWebs \n[ln()]"), size = 10))
+spiders_text <- as_ggplot(text_grob(paste("Number of \nSpiders \n[ln()]"), size = 10))
+dist_text <- as_ggplot(text_grob(paste("Nearest \nNeighbor \nDist. [ln(cm)]"), size = 10))
+height_text <- as_ggplot(text_grob(paste("Web \nHeight \n[ln(cm)]"), size = 10))
+tdr_text <- as_ggplot(text_grob(paste("Road-Traffic \nImpact \n[ln(cars/day/m)]"), size = 10))
+tdh_text <- as_ggplot(text_grob(paste("Highway-Traffic \nImpact \n[ln(cars/day/m)]"), size = 10))
+road_text <- as_ggplot(text_grob(paste("Road \nLength [m]"), size = 10))
+overall_text <- as_ggplot(text_grob(paste("Overall"), size = 10))
+center_text <- as_ggplot(text_grob(paste("Urban Center Subset"), size = 10))
+blankPlot <- ggplot()+geom_blank(aes(1,1)) + 
+  cowplot::theme_nothing() 
+greyPlot <- ggplot()+geom_blank(aes(1,1)) + 
+  cowplot::theme_nothing() +
+  theme(panel.background = element_rect(fill = "grey", color = "white"))
+
+pred_traffic <- ggarrange(webs_text, greyPlot, webs_tdh, blankPlot, webs_center_tdh, greyPlot,
+                spiders_text, greyPlot, spiders_tdh, blankPlot, spiders_center_tdh, greyPlot, 
+                dist_text, greyPlot, greyPlot, blankPlot, greyPlot, dist_center_road, 
+                height_text, height_tdr, greyPlot, blankPlot, greyPlot, height_center_road,
+                blankPlot, tdr_text, tdh_text, blankPlot, tdh_text, road_text,
+                ncol = 6, nrow = 5, 
+                widths = c(0.16, 0.20, 0.20, 0.04, 0.20, 0.20), 
+                heights = c(0.22, 0.22, 0.22, 0.22, 0.12))
+
+jpeg(filename = "manuscript/figures/pred_traffic.jpeg", units = "cm", width = 17.4, height = 17.4, res = 300)
+print(pred_traffic)
+dev.off()
 ```
@@
 mean_se1 <- c("Mean ± Std.
-Error", "Urban Forest \n(Wilderness Park)", "47.15 ± 2.17", "1.27 ± 0.36", "137.44 ± 3.71", "5.89 ± 0.77", "13.30 ± 1.15", "46,294.7 ± 68.040", "104 ± 3.23", "35.6 ± 1.89", "15.67 ± 1.25")
+Error", "Urban Forest \n(Wilderness Park)", "47.15 ± 3.46", "1.27 ± 0.36", "137.44 ± 3.71", "5.89 ± 0.91", "13.30 ± 1.56", "46,295 ± 11,128", "104 ± 36", "35.6 ± 6.04", "15.67 ± 7.54")
 mean_se2 <- c("Mean ± Std.
-Error", "Urban Center \n(UNL City Campus)", "1.58 ± 0.36", "76.52 ± 2.53", "153.39 ± 3.58", "116.90 ± 3.12", "3.33 ± 0.53", "116.90 ± 3.12", "398 ± 5.76", "65.0 ± 2.33", "93.03 ± 2.78")
+Error", "Urban Center \n(UNL City Campus)", "1.58 ± 0.37", "76.52 ± 2.63", "153.39 ± 3.58", "116.90 ± 9.39", "3.33 ± 0.58", "654 ± 144", "398 ± 125", "65.0 ± 9.82", "93.03 ± 40.60")
 pred_location <- data.frame(mean_se2, mean_se1)
-rownames(pred_location) <- c("", " ", "Percent Tree Cover [%]", "Percent Impervious Cover [%]", "Spectral Radiance [Watts/(m² * sr * µm)]", "Artificial Night Sky Radiance [mcd/m²]", "Plant Species Richness", "Patch Area [m²]", "Road Disturbance [vehicles/day/m]", "Highway Disturbance [vehicles/day/m]", "Total Road Length [m]")
+rownames(pred_location) <- c("", " ", "Percent Tree Cover [%]", "Percent Impervious Cover [%]", "Spectral Radiance [Watts/(m² * sr * µm)]", "Artificial Night Sky Radiance [mcd/m²]", "Plant Species Richness", "Patch Area [m²]", "Road-Traffic Impact [vehicles/day/m]", "Highway-Traffic Impact [vehicles/day/m]", "Total Road Length [m]")
 names <- rownames(pred_location)
@@
 ```{r pred_table}
-pred_table <- read.table(file = "data/pred_table.txt", header = TRUE) # for predictor stats table
-
-pred_table <- pred_table %>% 
+pred_table_nb <- read.table(file = "data/pred_table_nb.txt", header = TRUE) # for predictor stats table
+
+pred_table_nb <- pred_table_nb %>% 
   mutate(Variable = factor(Variable),
@@
          Predictor = fct_recode(Predictor, "Plant Species Richness" = "plant",
-                                "Road Disturbance" = "tdr",
-                                "Highway Disturbance" = "tdh",
-                                "Patch Area" = "patch",
+                                "Road-Traffic Impact" = "tdr",
+                                "Highway-Traffic Impact" = "tdh",
                                 "Total Road Length" = "road",
-                                "Spectral Radiance" = "spec",
                                 "Percent Tree Cover" = "tree",
-                                "Proportion Tree Cover" = "tree_frac"),
-         org_Estimate = round(org_Estimate, 3),
-         bt_Estimate = round(bt_Estimate, 3),
-         org_SE = round(org_SE, 3),
-         bt_SE = round(bt_SE, 3),
+                                "Proportion Tree Cover" = "tree_frac",
+                                "Total Road Length (Scaled)" = "road_scale"),
+         Estimate = round(Estimate, 3),
+         SE = round(SE, 3),
          Z = round(Z, 3),
@@
 
-pred_table[pred_table == 0] <- ""
-
-pred_table <- pred_table %>% 
+pred_table_nb[pred_table_nb == 0] <- ""
+
+pred_table_nb <- pred_table_nb %>% 
   mutate(P = fct_recode(P, "< 0.001 ***" = "0.001",
+                        "   0.003 **" = "0.003",
+                        "   0.005 **" = "0.005",
+                        "   0.009 **" = "0.009",
                         "   0.010 **" = "0.01",
-                        "   0.003 **" = "0.003",
-                        "   0.004 **" = "0.004",
-                        "   0.064 ." = "0.064",
-                        "   0.100 ." = "0.1")) %>% 
-  dplyr::select(-bt_Estimate, -bt_SE)
-
-colnames(pred_table) <- c('Variable','Model','Predictor', 'Estimate', 'Standard \nError', 'Z-Value', 'P-Value', 'McFadden\'s \nR²', 'AICc \nWeight')
-
-flextable(pred_table[ , 1:9]) %>% 
+                        "   0.012 *" = "0.012",
+                        "   0.013 *" = "0.013",
+                        "   0.027 *" = "0.027",
+                        "   0.058 ." = "0.058",
+                        "   0.076 ." = "0.076",
+                        "   0.086 ." = "0.086"))
+
+colnames(pred_table_nb) <- c('Variable','Model','Predictor', 'Estimate', 'Standard \nError', 'Z-Value', 'P-Value', 'McFadden\'s \nR²', 'AICc \nWeight')
+
+flextable(pred_table_nb[ , 1:9]) %>% 
   autofit() %>% 
@@
   border(j = 'Variable', border.bottom = officer::fp_border(width = 2)) %>% 
-  hline(i = c("8", "15", "24"), part = "body", border = officer::fp_border(width = 2)) %>%     
+  hline(i = c("4", "8", "11"), part = "body", border = officer::fp_border(width = 2)) %>%     
   fontsize(size = 10, part = "all") %>% 
@@
   set_caption("") %>% 
-  footnote(i = c(1:3, 5:7, 9:10, 12:14, 16:17, 19:22, 25:26, 28), j = 3, value = as_paragraph(
-    c("Predictors that were log-transformed prior to model evaluation. Estimate and standard errors are not back transformed.")), 
+  footnote(i = c(1:3, 5:7, 9, 12:14), j = 3, value = as_paragraph(
+    c("Predictors that were natural log-transformed prior to model evaluation. Estimate and standard errors are not back transformed.")), 
     ref_symbols = c("a"), part = "body") %>% 
-    footnote(i = 27, j = 3, value = as_paragraph(
+      footnote(i = 15, j = 3, value = as_paragraph(
+    c("Total road Length was scaled (without centering) by dividing each value of road length by the root mean square prior to model evaluation to avoid model convergence issues.")),
+    ref_symbols = c("b"), part = "body") %>% 
+    footnote(i = 16, j = 3, value = as_paragraph(
     c("Tree cover is assessed as proportion (value from 0 to 1) rather than a percent (values 0 to 100) to avoid model convergence issues.")), 
-    ref_symbols = c("b"), part = "body") %>% 
-  save_as_image(path = here::here("manuscript/figures/pred_table.png"))
+    ref_symbols = c("c"), part = "body") %>% 
+  save_as_image(path = here::here("manuscript/figures/pred_table_nb.png"))
 ```
@@
 ```{r land_plots}
-land_plots <- ggarrange(search_land_plot, ggarrange(webs_land_plot_nox, spiders_land_plot_nox,dist_land_plot, height_land_plot, labels = c("b", "c", "d", "e"), ncol = 2, nrow = 2, legend = "none", align = "hv"), labels = c("a"), widths = c(0.3, 0.7))
+land_plots <- ggarrange(search_land_plot, ggarrange(webs_land_plot, spiders_land_plot, dist_land_plot, height_land_plot, labels = c("b", "c", "d", "e"), ncol = 2, nrow = 2, legend = "none", align = "hv"), labels = c("a"), widths = c(0.3, 0.7))
 
 land_plots
+
+jpeg(filename = "manuscript/figures/land_plots.jpeg", units = "cm", width = 17.4, height = 17.4, res = 300)
+print(land_plots)
+dev.off()
 #saveRDS(land_plots, "manuscript/figures/land_plots.Rds")
@@
 ```{r pred_table_avg}
-pred_table_avg <- read.table(file = "data/pred_table_avg.txt", header = TRUE) # for predictor stats table
-
-pred_table_avg <- pred_table_avg %>% 
+pred_table_avg_nb <- read.table(file = "data/pred_table_avg_nb.txt", header = TRUE) # for predictor stats table
+
+pred_table_avg_nb <- pred_table_avg_nb %>% 
   mutate(Variable = factor(Variable),
@@
          Predictor = fct_recode(Predictor, "Plant Species Richness" = "plant",
-                                "Road Disturbance" = "tdr",
-                                "Highway Disturbance" = "tdh",
+                                "Road-Traffic Impact" = "tdr",
+                                "Highway-Traffic Impact" = "tdh",
                                 "Patch Area" = "patch",
@@
                                 "Proportion Tree Cover" = "tree_frac",
-                                "Spectral Radiance" = "spec_scale",
-                                "Total Road Length" = "road_scale"),
+                                "Spectral Radiance (Scaled)" = "spec_scale",
+                                "Total Road Length (Scaled)" = "road_scale"),
          Model = factor(Model), 
@@
 
-pred_table_avg <- pred_table_avg %>% 
+pred_table_avg_nb <- pred_table_avg_nb %>% 
   mutate(P = factor(P),
     P = fct_recode(P, "< 0.001 ***" = "0.001",
+                        "   0.007 **" = "0.007",
+                        "   0.009 **" = "0.009",
+                        "   0.017 *" = "0.017",
+                        "   0.019 *" = "0.019",
+                        "   0.029 *" = "0.029",
                         "   0.033 *" = "0.033",
-                        "   0.003 **" = "0.003",
-                        "   0.043 *" = "0.043",
-                        "   0.010 *" = "0.01",
+                        "   0.036 *" = "0.036",
+                        "   0.039 *" = "0.039",
                         "   0.054 ." = "0.054",
-                        "   0.228" = "0.228",
-                        "   0.005 **" = "0.005",
+                        "   0.055 ." = "0.055",
+                        "   0.078 ." = "0.078",
                         "   0.086 ." = "0.086",
-                        "   0.172" = "0.172",
-                        "   0.062 ." = "0.062",
-                        "   0.299" = "0.299",
-                        "   0.377" = "0.377",
-                        "   0.120" = "0.12",
-                        "   0.241" = "0.241",
-                        "   0.172" = "0.172"))
-
-colnames(pred_table_avg) <- c('Variable','Model','Predictor', 'Estimate', 'Adj. Standard \nError', 'Z-Value', 'P-Value', 'AICc \nWeight')
+                        "   0.088 ." = "0.088",
+                        "   0.092 ." = "0.092",
+                        "   0.119" = "0.119",
+                        "   0.122" = "0.122",
+                        "   0.137" = "0.137",
+                        "   0.143" = "0.143",
+                        "   0.162" = "0.162",
+                        "   0.301" = "0.301"))
+
+colnames(pred_table_avg_nb) <- c('Variable','Model','Predictor', 'Estimate', 'Adj. Standard \nError', 'Z-Value', 'P-Value', 'AICc \nWeight')
 
@@
 
-flextable(pred_table_avg[ , 1:8]) %>% 
+flextable(pred_table_avg_nb[ , 1:8]) %>% 
   autofit() %>% 
@@
   border(j = 'Variable', border.bottom = officer::fp_border(width = 2)) %>% 
-  hline(i = c("4", "8"), part = "body", border = officer::fp_border(width = 2)) %>%   
+  hline(i = c("1", "4", "8"), part = "body", border = officer::fp_border(width = 2)) %>%   
   fix_border_issues(part = "all") %>% 
@@
   set_caption("") %>% 
-  footnote(i = c(1:3, 5:6, 9:11, 13:16, 18:19), j = 3, value = as_paragraph(
-    c("Predictors that were log-transformed prior to model evaluation. Estimate and standard errors are not back transformed.")), 
+  footnote(i = c(1:3, 5:6, 9:13, 15:16, 19:20), j = 3, value = as_paragraph(
+    c("Predictors that were natural log-transformed prior to model evaluation. Estimate and standard errors are not back transformed.")), 
     ref_symbols = c("a"), part = "body") %>% 
-    footnote(i = 12, j = 3, value = as_paragraph(
+  footnote(i = c(14, 17), j = 3, value = as_paragraph(
+    c("Spectral radiance and total road Length were scaled (without centering) by dividing each value of road length by the root mean square prior to model evaluation to avoid model convergence issues.")),
+    ref_symbols = c("b"), part = "body") %>% 
+  footnote(i = 18, j = 3, value = as_paragraph(
     c("Tree cover is assessed as proportion (value from 0 to 1) rather than a percent (values 0 to 100) to avoid model convergence issues.")), 
-    ref_symbols = c("b"), part = "body") %>% 
-  footnote(i = c(17, 20), j = 3, value = as_paragraph(
-    c("Predictors were scaled (each value divided by the standard deviation) prior to model evaluation. Estimate and standard errors are not back transformed.")), 
     ref_symbols = c("c"), part = "body") %>% 
-  save_as_image(path = here::here("manuscript/figures/pred_table_avg.png"))
+  save_as_image(path = here::here("manuscript/figures/pred_table_avg_nb.png"))
 ```
@@
 Variable <- c("Search Distance", "Number of Webs", "Number of Spiders", "Neares Neighbor Distance", "Web Height")
-Chi <- c(340.32, 106.67, 31.65, 3629.30, 10.496)
+Chi <- c(6.37, 19.134, 10.913, 40.757, 12.569)
 df <- c("4, 21", "4, 21", "4, 21", "4, 20", "4, 130")
-P <- c("< 0.001 ***", "< 0.001 ***", "< 0.001 ***", "< 0.001 ***", "  0.033 *")
+P <- c("  0.173", "< 0.001 ***", "  0.028 *", "< 0.001 ***", "  0.014 *")
 land_stats <- data.frame(Variable, Chi, df, P)
@@
   set_caption("") %>% 
-  save_as_image(path = here::here("manuscript/figures/land_stats.png"))
+  save_as_image(path = here::here("manuscript/figures/land_stats_nb.png"))
+
+land_stat_table <- ggtexttable(land_stats, rows = NULL,
+            theme = ttheme("blank")) %>% 
+            tab_add_hline(at.row = c(1, 2), row.side = "top", linewidth = 3, linetype = 1) %>%
+            tab_add_hline(at.row = 6, row.side = "bottom", linewidth = 3, linetype = 1)
+
+webs_land_table <- data.frame(UH = c("", "", "", "", ""),
+                              UM = c("", "", "", "", ""),
+                              UL = c("", "", "", "", ""),
+                              DF = c("*", "**", ".", "", ""),
+                              WW = c(".", "*", ".", "", ""))
+colnames(webs_land_table) <- c("Urban, High", "Urban, Medium", "Urban, Low", "Deciduous Forest", "Woody Wetlands")
+rownames(webs_land_table) <- c("Urban, High", "Urban, Medium", "Urban, Low", "Deciduous Forest", "Woody Wetlands")
+
+webs_land_table2 <- ggtexttable(webs_land_table,
+            theme = ttheme("blank", 
+                           rownames.style = rownames_style(color = "black", face = "plain", size = 10, fill = "white"),
+                           colnames.style = colnames_style(color = "black", face = "plain", size = 10, fill = "white"),
+                           tbody.style = tbody_style(color = "black", face = "plain", size = 12, fill = "white")))
+
+webs_land_table2 <- webs_land_table2 %>% 
+  tab_add_hline(at.row = c(1, 2), row.side = "top", linewidth = 3, linetype = 1) %>%
+  tab_add_hline(at.row = 6, row.side = "bottom", linewidth = 3, linetype = 1) %>%
+  tab_add_vline(at.column = 2, column.side = "left", from.row = 1, linewidth = 3, linetype = 1) %>% 
+  table_cell_bg(row = 2, column = c(3:6), linewidth = 0,
+                fill="lightgrey", color = "white") %>% 
+  table_cell_bg(row = 3, column = c(4:6), linewidth = 0,
+                fill="lightgrey", color = "white") %>% 
+  table_cell_bg(row = 4, column = c(5:6), linewidth = 0,
+                fill="lightgrey", color = "white") %>% 
+  table_cell_bg(row = 5, column = 6, linewidth = 0,
+                fill="lightgrey", color = "white") %>% 
+  tab_add_title(text = "     Number of Webs", face = "bold", size = 10)
+
+spiders_land_table <- data.frame(UH = c("", "", "", "", ""),
+                              UM = c("", "", "", "", ""),
+                              UL = c("", "", "", "", ""),
+                              DF = c("", "", "", "", ""),
+                              WW = c("", "", "", "", ""))
+colnames(spiders_land_table) <- c("Urban, High", "Urban, Medium", "Urban, Low", "Deciduous Forest", "Woody Wetlands")
+rownames(spiders_land_table) <- c("Urban, High", "Urban, Medium", "Urban, Low", "Deciduous Forest", "Woody Wetlands")
+
+spiders_land_table2 <- ggtexttable(spiders_land_table,
+            theme = ttheme("blank", 
+                           rownames.style = rownames_style(color = "black", face = "plain", size = 10, fill = "white"),
+                           colnames.style = colnames_style(color = "black", face = "plain", size = 10, fill = "white"),                           tbody.style = tbody_style(color = "black", face = "plain", size = 12, fill = "white")))
+
+spiders_land_table2 <- spiders_land_table2 %>% 
+  tab_add_hline(at.row = c(1, 2), row.side = "top", linewidth = 3, linetype = 1) %>%
+  tab_add_hline(at.row = 6, row.side = "bottom", linewidth = 3, linetype = 1) %>%
+  tab_add_vline(at.column = 2, column.side = "left", from.row = 1, linewidth = 3, linetype = 1) %>% 
+  table_cell_bg(row = 2, column = c(3:6), linewidth = 0,
+                fill="lightgrey", color = "white") %>% 
+  table_cell_bg(row = 3, column = c(4:6), linewidth = 0,
+                fill="lightgrey", color = "white") %>% 
+  table_cell_bg(row = 4, column = c(5:6), linewidth = 0,
+                fill="lightgrey", color = "white") %>% 
+  table_cell_bg(row = 5, column = 6, linewidth = 0,
+                fill="lightgrey", color = "white") %>% 
+  tab_add_title(text = "      Number of Spiders", face = "bold", size = 10)
+
+dist_land_table <- data.frame(UH = c("", "", "", "", ""),
+                              UM = c("", "", "", "", ""),
+                              UL = c("", "**", "", "", ""),
+                              DF = c("***", "*", "***", "", ""),
+                              WW = c("**", "", "***", "", ""))
+colnames(dist_land_table) <- c("Urban, High", "Urban, Medium", "Urban, Low", "Deciduous Forest", "Woody Wetlands")
+rownames(dist_land_table) <- c("Urban, High", "Urban, Medium", "Urban, Low", "Deciduous Forest", "Woody Wetlands")
+
+dist_land_table2 <- ggtexttable(dist_land_table,
+            theme = ttheme("blank", 
+                           rownames.style = rownames_style(color = "black", face = "plain", size = 10, fill = "white"),
+                           colnames.style = colnames_style(color = "black", face = "plain", size = 10, fill = "white"),                           tbody.style = tbody_style(color = "black", face = "plain", size = 12, fill = "white")))
+
+dist_land_table2 <- dist_land_table2 %>% 
+  tab_add_hline(at.row = c(1, 2), row.side = "top", linewidth = 3, linetype = 1) %>%
+  tab_add_hline(at.row = 6, row.side = "bottom", linewidth = 3, linetype = 1) %>%
+  tab_add_vline(at.column = 2, column.side = "left", from.row = 1, linewidth = 3, linetype = 1) %>% 
+  table_cell_bg(row = 2, column = c(3:6), linewidth = 0,
+                fill="lightgrey", color = "white") %>% 
+  table_cell_bg(row = 3, column = c(4:6), linewidth = 0,
+                fill="lightgrey", color = "white") %>% 
+  table_cell_bg(row = 4, column = c(5:6), linewidth = 0,
+                fill="lightgrey", color = "white") %>% 
+  table_cell_bg(row = 5, column = 6, linewidth = 0,
+                fill="lightgrey", color = "white") %>% 
+  tab_add_title(text = "      Nearest Neighbor Distance", face = "bold", size = 10)
+
+height_land_table <- data.frame(UH = c("", "", "", "", ""),
+                              UM = c("", "", "", "", ""),
+                              UL = c("", "", "", "", ""),
+                              DF = c("", "*", "", "", ""),
+                              WW = c("", "", "", "", ""))
+colnames(height_land_table) <- c("Urban, High", "Urban, Medium", "Urban, Low", "Deciduous Forest", "Woody Wetlands")
+rownames(height_land_table) <- c("Urban, High", "Urban, Medium", "Urban, Low", "Deciduous Forest", "Woody Wetlands")
+
+height_land_table2 <- ggtexttable(height_land_table,
+            theme = ttheme("blank", 
+                           rownames.style = rownames_style(color = "black", face = "plain", size = 10, fill = "white"),
+                           colnames.style = colnames_style(color = "black", face = "plain", size = 10, fill = "white"),                           tbody.style = tbody_style(color = "black", face = "plain", size = 12, fill = "white")))
+
+height_land_table2 <- height_land_table2 %>% 
+  tab_add_hline(at.row = c(1, 2), row.side = "top", linewidth = 3, linetype = 1) %>%
+  tab_add_hline(at.row = 6, row.side = "bottom", linewidth = 3, linetype = 1) %>%
+  tab_add_vline(at.column = 2, column.side = "left", from.row = 1, linewidth = 3, linetype = 1) %>% 
+  table_cell_bg(row = 2, column = c(3:6), linewidth = 0,
+                fill="lightgrey", color = "white") %>% 
+  table_cell_bg(row = 3, column = c(4:6), linewidth = 0,
+                fill="lightgrey", color = "white") %>% 
+  table_cell_bg(row = 4, column = c(5:6), linewidth = 0,
+                fill="lightgrey", color = "white") %>% 
+  table_cell_bg(row = 5, column = 6, linewidth = 0,
+                fill="lightgrey", color = "white") %>% 
+  tab_add_title(text = "      Web Height", face = "bold", size = 10)
+
+land_tables <- ggarrange(land_stat_table, webs_land_table2, spiders_land_table2, dist_land_table2, height_land_table2, nrow = 5, labels = c("a", "b", "c", "d", "e"), font.label = list(size = 12))
+
+jpeg(filename = "manuscript/figures/land_tables.jpeg", units = "cm", width = 17.4, height = 25, res = 300)
+print(land_tables)
+dev.off()
 ```

### 2023-03-22 data_analysis.Rmd
More edits from reviewer comments

@@
   theme_classic() +
-  scale_y_continuous(limits = c(-50, 1000), breaks = c(0, 200, 400, 600, 800, 1000)) +
+  scale_y_continuous(limits = c(-50, 1050), breaks = c(0, 200, 400, 600, 800, 1000)) +
   xlab("Nearest Neighbors") +
@@
 
-main_row1 <- ggarrange(nb_plot_search, nb_plot_webs, nb_plot_spiders, labels = c("a", "b", "c"), nrow = 1, font.label = list(size = 10))
-main_row2 <- ggarrange(nb_plot_dist, nb_plot_height, blankPlot, labels = c("d", "e", ""), nrow = 1, font.label = list(size = 10))
+main_row1 <- ggarrange(nb_plot_webs, nb_plot_spiders, blankPlot, labels = c("a", "b", ""), nrow = 1, font.label = list(size = 10))
+main_row2 <- ggarrange(nb_plot_search, nb_plot_dist, nb_plot_height, labels = c("c", "d", "e"), nrow = 1, font.label = list(size = 10))
 
@@
 rownames(land_cover) <- c("Area (sq.
-km)", "Tree Cover (%)", "Impervious Cover (%)", "Urban Cover (%)", "Urban, High Intensity (%)", "Urban, Medium Intensity (%)", "Urban, low Intensity (%)", "Urban, Open Space (%)", "Forest Cover (%)", "Deciduous Forest (%)", "Mixed Forest (%)", "Evergreen Forest (%)", "Woody Wetlands (%)", "Other Cover (%)", "Herbaceous Wetlands (%)", "Grassland Herbaceous (%)", "Pasture (%)", "Cultivated Crop (%)", "Open Water (%)")
+km)", "Tree Cover (%)", "Impervious Cover (%)", "Urban Cover (%)", "Urban, High Intensity (%)", "Urban, Medium Intensity (%)", "Urban, Low Intensity (%)", "Urban, Open Space (%)", "Forest Cover (%)", "Deciduous Forest (%)", "Mixed Forest (%)", "Evergreen Forest (%)", "Woody Wetlands (%)", "Other Cover (%)", "Herbaceous Wetlands (%)", "Grassland Herbaceous (%)", "Pasture (%)", "Cultivated Crop (%)", "Open Water (%)")
 names <- rownames(land_cover)
@@
       footnote(i = 15, j = 3, value = as_paragraph(
-    c("Total road Length was scaled (without centering) by dividing each value of road length by the root mean square prior to model evaluation to avoid model convergence issues.")),
+    c("Total road length was scaled (without centering) by dividing each value of road length by the root mean square prior to model evaluation to avoid model convergence issues.")),
     ref_symbols = c("b"), part = "body") %>% 
@@
 ```{r land_plots}
+library("gridExtra")
+library("cowplot")
+
 land_plots <- ggarrange(search_land_plot, ggarrange(webs_land_plot, spiders_land_plot, dist_land_plot, height_land_plot, labels = c("b", "c", "d", "e"), ncol = 2, nrow = 2, legend = "none", align = "hv"), labels = c("a"), widths = c(0.3, 0.7))
+
+gt <- arrangeGrob(webs_land_plot, spiders_land_plot,
+             search_land_plot, dist_land_plot, 
+             height_land_plot,
+             ncol = 3, nrow = 2, 
+             layout_matrix = rbind(c(1, 2, 5), c(3, 4, 5)))
+
+land_plots <- as_ggplot(gt) +                                # transform to a ggplot
+  draw_plot_label(label = c("a", "c", "b", "d", "e"), size = 15,
+                  x = c(0, 0, 0.33, 0.33, 0.66), y = c(1, 0.5, 1, 0.5, 1))
 
@@
          Variable = fct_recode(Variable, "Number of Webs" = "NumWebs",
+                               "Number of Spiders" = "NumSpiders",
                                "Nearest Neighbor Distance" = "RetreatDist",
@@
 ```{r land_stats}
-Variable <- c("Search Distance", "Number of Webs", "Number of Spiders", "Neares Neighbor Distance", "Web Height")
-Chi <- c(6.37, 19.134, 10.913, 40.757, 12.569)
+Variable <- c("Number of Webs", "Number of Spiders", "Search Distance", "Neares Neighbor Distance", "Web Height")
+Chi <- c(19.134, 10.913, 6.37, 40.757, 12.569)
 df <- c("4, 21", "4, 21", "4, 21", "4, 20", "4, 130")
-P <- c("  0.173", "< 0.001 ***", "  0.028 *", "< 0.001 ***", "  0.014 *")
+P <- c("< 0.001 ***", "  0.028 *", "  0.173", "< 0.001 ***", "  0.014 *")
 land_stats <- data.frame(Variable, Chi, df, P)

### 2023-03-29 data_analysis.Rmd
New edits during review process

@@
     scale_color_manual(values = c("Urban Center" = "#d95f02", "Urban Forest" = "#1b9e77")) +
-    scale_x_discrete(labels=c("Urban Forest" = "Urban \nForest \nN = 10", "Urban Center" = "Urban \nCenter \nN = 12")) +
+    scale_x_discrete(labels=c("Urban Forest" = "Urban \nForest \nN = 30", "Urban Center" = "Urban \nCenter \nN = 101")) +
     theme_classic() +
@@
 rownames(land_cover) <- c("Area (sq.
-km)", "Tree Cover (%)", "Impervious Cover (%)", "Urban Cover (%)", "Urban, High Intensity (%)", "Urban, Medium Intensity (%)", "Urban, Low Intensity (%)", "Urban, Open Space (%)", "Forest Cover (%)", "Deciduous Forest (%)", "Mixed Forest (%)", "Evergreen Forest (%)", "Woody Wetlands (%)", "Other Cover (%)", "Herbaceous Wetlands (%)", "Grassland Herbaceous (%)", "Pasture (%)", "Cultivated Crop (%)", "Open Water (%)")
+km)", "Impervious Cover (%)", "Tree Cover (%)", "Urban Cover (%)", "Urban, High Intensity (%)", "Urban, Medium Intensity (%)", "Urban, Low Intensity (%)", "Urban, Open Space (%)", "Forest Cover (%)", "Deciduous Forest (%)", "Mixed Forest (%)", "Evergreen Forest (%)", "Woody Wetlands (%)", "Other Cover (%)", "Herbaceous Wetlands (%)", "Grassland Herbaceous (%)", "Pasture (%)", "Cultivated Crop (%)", "Open Water (%)")
 names <- rownames(land_cover)
@@
 mean_se1 <- c("Mean ± Std.
-Error", "Urban Forest \n(Wilderness Park)", "47.15 ± 3.46", "1.27 ± 0.36", "137.44 ± 3.71", "5.89 ± 0.91", "13.30 ± 1.56", "46,295 ± 11,128", "104 ± 36", "35.6 ± 6.04", "15.67 ± 7.54")
+Error", "Urban Forest \n(Wilderness Park)", "1.27 ± 0.36", "47.15 ± 3.46", "137.44 ± 3.71", "5.89 ± 0.91", "13.30 ± 1.56", "46,295 ± 11,128", "104 ± 36", "35.6 ± 6.04", "15.67 ± 7.54")
 mean_se2 <- c("Mean ± Std.
-Error", "Urban Center \n(UNL City Campus)", "1.58 ± 0.37", "76.52 ± 2.63", "153.39 ± 3.58", "116.90 ± 9.39", "3.33 ± 0.58", "654 ± 144", "398 ± 125", "65.0 ± 9.82", "93.03 ± 40.60")
+Error", "Urban Center \n(UNL City Campus)", "76.52 ± 2.63", "1.58 ± 0.37", "153.39 ± 3.58", "116.90 ± 9.39", "3.33 ± 0.58", "654 ± 144", "398 ± 125", "65.0 ± 9.82", "93.03 ± 40.60")
 pred_location <- data.frame(mean_se2, mean_se1)
-rownames(pred_location) <- c("", " ", "Percent Tree Cover [%]", "Percent Impervious Cover [%]", "Spectral Radiance [Watts/(m² * sr * µm)]", "Artificial Night Sky Radiance [mcd/m²]", "Plant Species Richness", "Patch Area [m²]", "Road-Traffic Impact [vehicles/day/m]", "Highway-Traffic Impact [vehicles/day/m]", "Total Road Length [m]")
+rownames(pred_location) <- c("", " ", "Percent Impervious Cover [%]", "Percent Tree Cover [%]", "Spectral Radiance [Watts/(m² * sr * µm)]", "Artificial Night Sky Radiance [mcd/m²]", "Plant Species Richness", "Patch Area [m²]", "Road-Traffic Impact [vehicles/day/m]", "Highway-Traffic Impact [vehicles/day/m]", "Total Road Length [m]")
 names <- rownames(pred_location)
@@
   footnote(i = c(1:3, 5:7, 9, 12:14), j = 3, value = as_paragraph(
-    c("Predictors that were natural log-transformed prior to model evaluation. Estimate and standard errors are not back transformed.")), 
+    c("Predictors that were natural log-transformed prior to model evaluation. Estimate and standard errors were not back transformed.")), 
     ref_symbols = c("a"), part = "body") %>% 
@@
     footnote(i = 16, j = 3, value = as_paragraph(
-    c("Tree cover is assessed as proportion (value from 0 to 1) rather than a percent (values 0 to 100) to avoid model convergence issues.")), 
+    c("Tree cover was assessed as proportion (value from 0 to 1) rather than a percent (values 0 to 100) to avoid model convergence issues.")), 
     ref_symbols = c("c"), part = "body") %>% 
@@
   footnote(i = c(1:3, 5:6, 9:13, 15:16, 19:20), j = 3, value = as_paragraph(
-    c("Predictors that were natural log-transformed prior to model evaluation. Estimate and standard errors are not back transformed.")), 
+    c("Predictors that were natural log-transformed prior to model evaluation. Estimate and standard errors were not back transformed.")), 
     ref_symbols = c("a"), part = "body") %>% 
   footnote(i = c(14, 17), j = 3, value = as_paragraph(
-    c("Spectral radiance and total road Length were scaled (without centering) by dividing each value of road length by the root mean square prior to model evaluation to avoid model convergence issues.")),
+    c("Spectral radiance and total road length were scaled (without centering) by dividing each value of road length by the root mean square prior to model evaluation to avoid model convergence issues.")),
     ref_symbols = c("b"), part = "body") %>% 
   footnote(i = 18, j = 3, value = as_paragraph(
-    c("Tree cover is assessed as proportion (value from 0 to 1) rather than a percent (values 0 to 100) to avoid model convergence issues.")), 
+    c("Tree cover was assessed as proportion (value from 0 to 1) rather than a percent (values 0 to 100) to avoid model convergence issues.")), 
     ref_symbols = c("c"), part = "body") %>% 

### 2024-09-30 functions/get_predictions_function.R
Tidied repository by cleaning up folders and adding the publication and poster PDFs

@@ -1,0 +1,3 @@
+get_predictions <- function(mm) {
+  predict(mm, newdata = predictions, re.form = ~0, type = "response")
+}

### 2024-09-30 functions/model_comparison_function.R

@@ -1,0 +1,108 @@
+library(tidyverse)
+library(broom)
+library(ggpubr)
+
+plot_model_comparisons <- function(data, model_nb, model_poisson, model_log, 
+                                   x_var, y_var, y_limits, y_breaks, y_lab,
+                                   labels = c("0", "0", "0")) {
+  
+  # Raw Data Plot
+  raw_data <- data %>%
+    group_by(Location) %>%
+    summarise(mean = mean(.data[[y_var]]), se = plotrix::std.error(.data[[y_var]]))
+  
+  raw_plot <- ggplot(data, aes_string(x = x_var, y = y_var)) + 
+    geom_jitter(color = "grey", width = 0.1) +
+    geom_point(aes(x = Location, y = mean, color = Location), size = 2, data = raw_data) +
+    geom_errorbar(aes(x = Location, ymin = mean - se, ymax = mean + se, color = Location), 
+                  data = raw_data, inherit.aes = FALSE, width = 0.15, linewidth = 1) +
+    scale_color_manual(values = c("Urban Center" = "#d95f02", "Urban Forest" = "#1b9e77")) +
+    scale_x_discrete(labels=c("Urban Forest" = "Urban \nForest \nN = 10", "Urban Center" = "Urban \nCenter \nN = 12")) +
+    theme_classic() +
+    scale_y_continuous(limits = y_limits, breaks = y_breaks) +
+    xlab("Collection Location") +
+    ylab(y_lab) + 
+    theme(text = element_text(size = 10)) + 
+    theme(axis.text.x = element_text(colour = "black", size = 10)) + 
+    theme(axis.text.y = element_text(colour = "black", size = 10),
+          axis.title.x = element_blank()) +
+    theme(legend.position = "none")
+  
+  # Poisson Predictions and Plot
+  nd <- data.frame(Location = factor(levels(data[[x_var]])))
+  predictions_poisson <- augment(model_poisson, newdata = nd, se_fit = TRUE, type.predict = "response") %>%
+    rename("rate" = ".fitted", "SE" = ".se.fit")
+  
+  poisson_plot <- ggplot(data, aes_string(x = x_var, y = y_var)) + 
+    geom_jitter(color = "grey", width = 0.1) +
+    geom_point(aes(x = Location, y = rate, color = Location), size = 2, data = predictions_poisson) + 
+    geom_errorbar(aes(x = Location, ymin = rate - SE, ymax = rate + SE, color = Location), 
[…]

### 2024-09-30 functions/residual_plots_function.R

@@ -1,0 +1,71 @@
+library(ggplot2)
+library(ggpubr)
+library(broom)
+library(broom.mixed)
+
+residual_plots <- function(model, data) {
+  # Augment the model with the data
+  #test_data <- data.frame(
+  #  .fitted = fitted(model),
+  #  .resid = residuals(model)
+  #)
+  test_data <- augment(model, data = data)
+  
+  # Residuals vs Fitted plot
+  resid_plot <- ggplot(test_data, aes(x = .fitted, y = .resid)) + 
+    geom_point() + 
+    geom_smooth(method = "loess") +
+    geom_hline(yintercept = 0) +
+    xlab("Fitted Values") +
+    ylab("Standardized \nResiduals") +
+    theme_classic() +
+    theme(text = element_text(size = 14, color = "black")) +
+    theme(axis.text.x=element_text(color="black", size=14)) + 
+    theme(axis.text.y=element_text(color="black", size=14))
+  
+  # QQ plot
+  y <- quantile(test_data$.resid, c(0.25, 0.75))
+  x <- qnorm(c(0.25, 0.75))
+  slope <- diff(y) / diff(x)
+  int <- y[1L] - slope * x[1L]
+  
+  qq_plot <- ggplot(test_data, aes(sample = .resid)) + 
+    stat_qq() + 
+    geom_abline(slope = slope, intercept = int) +
+    xlab("Theoretical Quantiles") +
+    ylab("Sample Quantiles") +
+    theme_classic() +
+    theme(text = element_text(size = 14, color = "black")) +
+    theme(axis.text.x=element_text(color="black", size=14)) + 
+    theme(axis.text.y=element_text(color="black", size=14))  
+  
+  scaleloc_plot <- ggplot(test_data, aes(x = .fitted, y = sqrt(abs(.std.resid)))) + 
+    geom_point() + 
+    geom_smooth() + 
+    geom_hline(yintercept = 0.83) +
+    xlab("Fitted Values") +
+    ylab("Sqrt Standardized \nResiduals") +
+    theme_classic() +
+    theme(text = element_text(size = 14, color = "black")) +
+    theme(axis.text.x=element_text(color="black", size=14)) + 
+    theme(axis.text.y=element_text(color="black", size=14))  
+  
+  lev_plot <- ggplot(test_data, aes(.hat, .std.resid)) +
+    geom_vline(colour = "black", xintercept = 0) +
[…]

### 2024-09-30 1_data_wrangling.Rmd
Organized code and wrote README.md file to help viewers interact with code

---
title: "Data Wrangling for Analysis Setup"
author: "Brandi Pessman"
date: "`r Sys.Date()`"
output: html_document
---

# Setting the Working Directory and Global Code Chunk Options

I have set message and warning to FALSE for every chunk so the knitted document does not include messages and warnings.

```{r setup}
knitr::opts_chunk$set(message = FALSE, warning = FALSE)
require("knitr")
opts_knit$set(root.dir = "/Users/bjpessman/Documents/phd_research_code/Agelenopsis_aggregation")
```

# Packages to Load

```{r packages}
library(tidyverse) # we will mostly use dplyr for wrangling
```

# Import the Data from the data/ folder

```{r import}
webs <- read.table(file = "data/webs.txt", header = TRUE) # includes data for every measured web (multiple per site)
sites <- read.table(file = "data/sites.txt", header = TRUE) # includes whole site characteristics
```

# Wrangling the Webs Dataset

Here, we rename some levels of factors Location and Land and put them in the order we want the categories to appear in a graph. We use "webs_wrangled" to compare measurements taken of each web at each site. We use "sites_wrangled" to compare search distance, the number of webs, and the number of spiders between sites. The "neighbors_wrangled" data set is a subset of "webs" that looks at the distance from the focal web to the nearest and second nearest neighbors.

NOTE: At one time, we tried scaling and centering the data in difference ways. We didn't scale and center because log-transformations on right-skewed variables were enough to remove convergence errors.

```{r wrangling webs}
webs_wrangled <- webs %>% 
  mutate(ID = factor(ID), # make spider ID a factor
         Location = factor(Location), # make location a factor so we can recode and relevel it
         Location = fct_recode(Location, 
                               "Urban Forest" = "Forest",
                               "Urban Center" = "Campus"), # recode the location
         Location = fct_relevel(Location, 
                                "Urban Center", "Urban Forest")) # make sure urban center comes before urban forest

webs_wrangled$RetreatHeight[webs_wrangled$RetreatHeight == 0] <- 0.1 # zero entry causes issues later; web with height 0.1cm is similar to 0 cm
```

```{r wrangling sites}
sites_wrangled <- sites %>% 
  mutate(ID = factor(ID), # make spider ID a factor
         Location = factor(Location), # make location a factor so we can recode and relevel it
         Land = factor(Land), # make land a factor so we can recode and relevel it
         Location = fct_recode(Location, 
                               "Urban Forest" = "Forest",
                               "Urban Center" = "Campus"), # recode the location
         Location = fct_relevel(Location, 
                                "Urban Center", "Urban Forest"), # make sure urban center comes before urban forest 
         Land = fct_recode(Land, 
                           "Urban, High" = "UrbanizedHighIntensity",
                           "Urban, Medium" = "UrbanizedMediumIntensity",
                           "Urban, Low" = "UrbanizedLowIntensity",
                           "Deciduous Forest" = "DeciduousForest",
                           "Woody Wetlands" = "WoodyWetlands"), # recode the land variable
         Land = fct_relevel(Land, 
                            "Urban, High", 
                            "Urban, Medium", 
                            "Urban, Low", 
                            "Deciduous Forest", 
                            "Woody Wetlands"),# relevel the factors of the land variable
         log_TotalSub = log(TotalSub), # log transformation
         log_tdr = log(dist_traffic_road), # log transformation
         log_tdh = log(dist_traffic_highway), # log transformation
         log_patch = log(patch_area_km), # log transformation
         ) %>% 
    dplyr::select(-patch_area_km, -Tree, -Imperv, -road_dist_m:-highway_year) %>%  # remove variables that are unused
    rename("Traffic_Dist_Road" = "dist_traffic_road", 
           "Traffic_Dist_Highway" = "dist_traffic_highway")
```

# Add environmental variables to webs_wrangled

```{r merge}
env <- sites_wrangled %>% 
  dplyr::select(ID, Land, tree100m, imperv100m, spec_rad, light_rad, road_length_m, trail_length_m, log_TotalSub, log_tdr, log_tdh, log_patch)
webs_wrangled <- left_join(webs_wrangled, env, by = "ID")
```

```{r neighbors dataset}
neighbors_wrangled <- webs_wrangled %>% 
  filter(RetreatDist != 0, # remove the focal web
         RetreatDist < 1000, # only include webs less than 10 meters away
         Web == "W002" | Web == "W003") %>% # keep only the two nearest neighbor measurements
  mutate(Neighbor = ifelse(Web == "W002", "1", "2")) # create a new label with 1 as the nearest neighbor and 2 as the second nearest
```

# Save Wrangled Datasets to wrangled_data

```{r saving datasets}
saveRDS(webs_wrangled, 'wrangled_data/webs_wrangled.rds')
saveRDS(sites_wrangled, 'wrangled_data/sites_wrangled.rds')
saveRDS(neighbors_wrangled, 'wrangled_data/neighbors_wrangled.rds')
```

### 2024-09-30 2_transformations_reductions.Rmd
Organized code and wrote README.md file to help viewers interact with code

---
title: "Transforming and Reducing Predictor Variables"
author: "Brandi Pessman"
date: "`r Sys.Date()`"
output: html_document
---
# Setting the Working Directory and Global Code Chunk Options

I have set message and warning to FALSE for every chunk so the knitted document does not include messages and warnings.

```{r setup}
knitr::opts_chunk$set(message = FALSE, warning = FALSE)
require("knitr")
opts_knit$set(root.dir = "/Users/bjpessman/Documents/phd_research_code/Agelenopsis_aggregation")
```

# Packages to Load

```{r packages}
library(tidyverse) # we will mostly use dplyr for wrangling
library(ggpubr) # using ggarrange to make multi-panel figures
library(caret) # used to find correlations between predictor variables
library(PerformanceAnalytics) # used to make correlation plots
```

# Import the Data from the wrangled_data/ folder

```{r import}
sites <- read.table(file = "data/sites.txt", header = TRUE) # includes whole site characteristics
sites_wrangled <- readRDS('wrangled_data/sites_wrangled.RDS')
```

# Graphing Predictor Distributions

Here, we graph the distribution of predictor variables in their raw distribution and after log-transformation since all variables are positive values, and many are zero-inflated (right-skewed); we also run shapiro-wilk tests to test for normality including the log-transformed variable if the log-transformed distribution is less skewed

```{r tree cover}
# use as is, log won't work because some data are zero
ggplot(sites, aes(x = tree100m)) +
    geom_density()
shapiro.test(sites$tree100m) # not normal
```

```{r impervious cover}
# use as is, log won't work because some data are zero
ggplot(sites, aes(x = imperv100m)) +
  geom_density()
shapiro.test(sites$imperv100m) # not normal
```

```{r plant species richness}
# better log-transformed
ggarrange(ggplot(sites, aes(x = TotalSub)) + 
            geom_density(), 
          ggplot(sites, aes(x = log10(TotalSub))) +
            geom_density(), 
          nrow = 1, 
          ncol = 2)
shapiro.test(sites$TotalSub) # not normal
shapiro.test(log10(sites$TotalSub)) # normal
```

```{r road disturbance}
# better log-transformed
ggarrange(ggplot(sites, aes(x = dist_traffic_road)) + 
            geom_density(), 
          ggplot(sites, aes(x = log(dist_traffic_road))) + 
            geom_density(), 
          nrow = 1, 
          ncol = 2)
shapiro.test(sites$dist_traffic_road) # not normal
shapiro.test(log(sites$dist_traffic_road)) # normal
```

```{r highway disturbance}
# better log-transformed
ggarrange(ggplot(sites, aes(x = dist_traffic_highway)) + 
            geom_density(), 
          ggplot(sites, aes(x = log(dist_traffic_highway))) + 
            geom_density(), 
          nrow = 1, 
          ncol = 2)
shapiro.test(sites$dist_traffic_highway) # not normal
shapiro.test(log(sites$dist_traffic_highway)) # almost normal
```

```{r spectral radiance}
# looks similar either way
ggarrange(ggplot(sites, aes(x = spec_rad)) + 
            geom_density(), 
          ggplot(sites, aes(x = log(spec_rad))) + 
            geom_density(), 
          nrow = 1, 
          ncol = 2)
shapiro.test(sites$spec_rad) # not normal
shapiro.test(log(sites$spec_rad)) # not normal
```

```{r ALAN}
# looks similar either way, but shapiro tests suggests as is is slightly better
ggarrange(ggplot(sites, aes(x = light_rad)) + 
            geom_density(), 
          ggplot(sites, aes(x = log(light_rad))) + 
            geom_density(), 
          nrow = 1, 
          ncol = 2)
shapiro.test(sites$light_rad) # not normal
shapiro.test(log(sites$light_rad)) # not normal
```

```{r patch area}
# better log-transformed
ggarrange(ggplot(sites, aes(x = patch_area_mm * 1e-6)) +
            geom_density(), 
          ggplot(sites, aes(x = log(patch_area_mm * 1e-6))) +
            geom_density(), 
          nrow = 1, 
          ncol = 2)
shapiro.test(sites$patch_area_mm * 1e-6) # not normal
shapiro.test(log(sites$patch_area_mm * 1e-6)) # almost normal
```

```{r total road length}
# use as is, log won't work because some data are zero
ggplot(sites, aes(x = road_length_m)) + 
  geom_density()
shapiro.test(sites$road_length_m) # not normal
```

```{r total trail length}
# use as is, log won't work because some data are zero
ggplot(sites, aes(x = trail_length_m)) + 
  geom_density()
shapiro.test(sites$trail_length_m) # not normal
```

# Variable Reduction Based on Correlations

Since many of these variables are likely highly correlated, we want to reduce the variables that we include in our model by removing variables that are highly correlated. We will be looking at the data overall and within subsets by Location.

```{r correlations overall}
# We exclude trail length from global correlations because trail length can only collected for the urban forest, and not the urban center
corr <- sites %>% 
  select(tree100m, imperv100m, TotalSub, 
         dist_traffic_road, dist_traffic_highway, 
         spec_rad, light_rad, patch_area_mm, road_length_m)

# When running findCorrelations, we get a vector of variables to remove to reduce pairwise correlations. 
findCorrelation(cor(corr, method = "spearman"), cutoff = .6, verbose = TRUE, names = TRUE)

# This suggests that we remove tree100m, imperv100, spec_rad, light_rad, patch_area_mm, road_length_m
# That leaves us with TotalSub, dist_traffic_road, and dist_traffic_highway; let's check these
chart.Correlation(corr, histogram = TRUE, method = "spearman") # kendall, spearman

corr <- sites %>% 
  select(TotalSub, dist_traffic_road, dist_traffic_highway)

chart.Correlation(corr, histogram = TRUE, method = "spearman") # kendall, spearman

# Let's also test the variables after transformation
corr_transformed <- sites_wrangled %>% 
  select(tree100m, imperv100m, log_TotalSub, 
         log_tdr, log_tdh, 
         spec_rad, light_rad, log_patch, road_length_m)

findCorrelation(cor(corr_transformed, method = "spearman"), cutoff = .6, verbose = TRUE, names = TRUE)

# This suggests to remove tree100m, imperv100m, spec_rad, light_rad, log_patch, and road_length_m.
# This leaves us with log_TotalSub, log_tdr, and log_tdh, the same results as the non-transformed. 
chart.Correlation(corr_transformed, histogram = TRUE, method = "spearman") # kendall, spearman

corr_transformed <- sites_wrangled %>% 
  select(log_TotalSub, log_tdr, log_tdh)

chart.Correlation(corr_transformed, histogram = TRUE, method = "spearman") # kendall, spearman
```

```{r correlations for urban forest}
corr_forest <- sites %>% 
  filter(Location == "Forest") %>% 
  dplyr::select(tree100m, imperv100m, TotalSub, 
         dist_traffic_road, dist_traffic_highway, 
         spec_rad, light_rad, patch_area_mm, road_length_m, trail_length_m)
# Notice trail length is included

findCorrelation(cor(corr_forest, method = "spearman"), cutoff = .6, verbose = TRUE, names = TRUE)

# This suggests removing imperv100m, spec_rad, light_rad, road_length_m, and trail_length_m
# We will keep tree100m, TotalSub, dist_traffic_road, dist_traffic_highway, and patch_area_mm
chart.Correlation(corr_forest, histogram = TRUE, method = "spearman")

corr_forest <- sites %>% 
  filter(Location == "Forest") %>% 
  dplyr::select(tree100m, TotalSub, dist_traffic_road, dist_traffic_highway, patch_area_mm)

chart.Correlation(corr_forest, histogram = TRUE, method = "spearman")

# Let's try with the log-transformed
corr_forest_transformed <- sites_wrangled %>% 
  filter(Location == "Urban Forest") %>% 
  select(tree100m, imperv100m, log_TotalSub, 
         log_tdr, log_tdh, 
         spec_rad, light_rad, log_patch, road_length_m, trail_length_m)

findCorrelation(cor(corr_forest_transformed, method = "spearman"), cutoff = .6, verbose = TRUE, names = TRUE) 
# The same variables are dropped and kept

corr_forest_transformed <- sites_wrangled %>% 
  filter(Location == "Urban Forest") %>% 
  select(tree100m, log_TotalSub, log_tdr, log_patch, log_tdh)

chart.Correlation(corr_forest_transformed, histogram = TRUE, method = "spearman")
```

```{r correlations for urban center}
corr_center <- sites %>% 
  filter(Location == "Campus") %>% 
  select(tree100m, imperv100m, TotalSub, dist_traffic_road, dist_traffic_highway, spec_rad, light_rad, patch_area_mm, road_length_m)
# Trail length is removed because we could not measure trail length on campus

findCorrelation(cor(corr_center, method = "spearman"), cutoff = .6, verbose = TRUE, names = TRUE) 
# This suggests that we remove tree100m, imperv100m, and light_rad
# We will keep TotalSub, dist_traffic_road, dist_traffic_highway, spec_rad, patch_area_mm, and road_length_m

chart.Correlation(corr_center, histogram = TRUE, method = "spearman")

# Let's try with the transformed
corr_center_transformed <- sites_wrangled %>% 
  filter(Location == "Urban Center") %>% 
  select(tree100m, imperv100m, log_TotalSub, log_tdr, log_tdh, spec_rad, light_rad, log_patch, road_length_m)

findCorrelation(cor(corr_center_transformed, method = "spearman"), cutoff = .6, verbose = TRUE, names = TRUE)

chart.Correlation(corr_center_transformed, histogram = TRUE, method = "pearson")
# The same variables are kept or removed
```

This means, for overall analysis of predictors, we will include: 
- log_TotalSub
- log_tdr
- log_tdh

For the urban forest subset, we will use: 
- tree100m 
- log_TotalSub 
- log_tdr 
- log_tdh
- log_patch

Finally, for the urban center subset, we will use: 
- log_TotalSub 
- log_tdr 
- log_tdh 
- spec_rad
- log_patch
- road_length_m

### 2024-09-30 3_habitat_characteristics_nb.Rmd
Organized code and wrote README.md file to help viewers interact with code

---
title: "Urban Habitat Characteristic Analysis"
author: "Brandi Pessman"
date: "`r Sys.Date()`"
output: html_document
---

## Setting the Working Directory and Global Code Chunk Options

I have set message and warning to FALSE for every chunk so the knitted document does not include messages and warnings.

```{r setup}
knitr::opts_chunk$set(message = FALSE, warning = FALSE, echo = FALSE)
require("knitr")
opts_knit$set(root.dir = "/Users/bjpessman/Documents/phd_research_code/Agelenopsis_aggregation")
```

# Packages to Load

```{r packages}
library(tidyverse) # for making graphs
library(MASS) # negative binomial tests
library(emmeans) # for calculating predictions for graphing
source('functions/residual_plots_function.R') # produces residual plots
```

# Import Data

```{r import}
sites_wrangled <- readRDS('wrangled_data/sites_wrangled.RDS')
```

# Comparing Habitat Characteristics by Location

Here, we tested whether each predictor differs between the two Locations: urban forest and urban center. We build models, check assumptions of the model, and make graphs to represent differences.

```{r tree cover}
tree100m <- glm(tree100m ~ Location, family = "poisson", data = sites_wrangled)
summary(tree100m)

# data are likely overdispersed since the residual deviance / degrees of freedom are much larger than 1
tree100m.nb <- glm.nb(tree100m ~ Location, data = sites_wrangled)
summary(tree100m.nb)

# calcuate mean and standard error
sites_wrangled %>% 
  group_by(Location) %>% 
  summarize(mean = mean(tree100m),
            se = plotrix::std.error(tree100m))

# get predictions
predictions <- summary(emmeans(tree100m.nb, ~Location),type = "response")

# graph raw data and predictions
ggplot(sites_wrangled, aes(x = Location, y = tree100m)) + 
  geom_jitter(color = "grey", width = 0.1, size = 1) +
  geom_point(aes(x = Location, y = response, color = Location), size = 2, data = predictions) + 
  geom_errorbar(aes(x = Location, 
                  ymin = response - SE, 
                  ymax = response + SE,
                  color = Location), data = predictions, inherit.aes = FALSE, width = 0.15, linewidth = 1.5) +
  scale_color_manual(values = c("Urban Center" = "#d95f02", "Urban Forest" = "#1b9e77")) +
  scale_x_discrete(labels=c("Urban Forest" = "Urban \nForest \nN = 10", "Urban Center" = "Urban \nCenter \nN = 12")) +
  scale_y_continuous(limits=c(-1, 100), breaks = c(0, 10, 20, 30, 40, 50, 60, 70, 80, 90, 100)) +
  theme_classic() +
  ylab("Percent Tree Cover \n[100m radius]") + 
  theme(text = element_text(size = 18)) + 
  theme(axis.text.x=element_text(colour="black", size=18)) + 
  theme(axis.text.y=element_text(colour="black", size=18),
        axis.title.x = element_blank()) +
  theme(legend.position = "none") +
  annotate(geom="text", x=1.5, y=100, label="***", color="black", size = 10)

# Residual plots
residual_plots(tree100m.nb, sites_wrangled)
```

Tree cover is **significantly higher in the urban forest** than the urban center (z = 13.77, df = 1, 21, p < 0.001). The means and SE's are 47.15 ± 3.46 % for the urban forest and 1.58 ± 0.37 % for the urban center.

```{r impervious cover}
imperv100m <- glm(imperv100m ~ Location, family = "poisson", data = sites_wrangled)
summary(imperv100m)

# data are likely overdispersed since the residual deviance / degrees of freedom are much larger than 1
imperv100m.nb <- glm.nb(imperv100m ~ Location, data = sites_wrangled)
summary(imperv100m.nb)

# calcuate mean and standard error
sites_wrangled %>% 
  group_by(Location) %>% 
  summarize(mean = mean(imperv100m),
            se = plotrix::std.error(imperv100m))

# get predictions
predictions <- summary(emmeans(imperv100m.nb, ~Location),type = "response")

ggplot(sites_wrangled, aes(x = Location, y = imperv100m)) + 
  geom_jitter(color = "grey", width = 0.1, size = 1) +
  geom_point(aes(x = Location, y = response, color = Location), size = 2, data = predictions) + 
  geom_errorbar(aes(x = Location, 
                  ymin = response - SE, 
                  ymax = response + SE,
                  color = Location), data = predictions, inherit.aes = FALSE, width = 0.15, linewidth = 1.5) +
  scale_color_manual(values = c("Urban Center" = "#d95f02", "Urban Forest" = "#1b9e77")) +
  scale_x_discrete(labels=c("Urban Forest" = "Urban \nForest \nN = 10", "Urban Center" = "Urban \nCenter \nN = 12")) +
  scale_y_continuous(limits=c(-1, 100), breaks = c(0, 10, 20, 30, 40, 50, 60, 70, 80, 90, 100)) +
  theme_classic() +
  ylab("Percent Impervious Cover \n[100m radius]") + 
  theme(text = element_text(size = 18)) + 
  theme(axis.text.x=element_text(colour="black", size=18)) + 
  theme(axis.text.y=element_text(colour="black", size=18),
        axis.title.x = element_blank()) +
  theme(legend.position = "none") +
  annotate(geom="text", x=1.5, y=100, label="***", color="black", size = 10)

# Residual plots
residual_plots(imperv100m.nb, sites_wrangled)
```

Impervious cover is **significantly higher in the urban center** than the urban forest (z = -14.49, df = 1, 21, p < 0.001). The means and SE's are 1.27 ± 0.36 % for the urban forest and 76.52 ± 2.63 % for the urban center.

```{r road disturbance}
tdr <- glm(Traffic_Dist_Road ~ Location, family = "poisson", data = sites_wrangled)
summary(tdr)

# data are likely overdispersed since the residual deviance / degrees of freedom are much larger than 1
tdr.nb <- glm.nb(Traffic_Dist_Road ~ Location, data = sites_wrangled)
summary(tdr.nb)

# calcuate mean and standard error
sites_wrangled %>% 
  group_by(Location) %>% 
  summarize(mean = mean(Traffic_Dist_Road),
            se = plotrix::std.error(Traffic_Dist_Road))

# get predictions
predictions <- summary(emmeans(tdr.nb, ~Location),type = "response")

ggplot(sites_wrangled, aes(x = Location, y = Traffic_Dist_Road)) + 
  geom_jitter(color = "grey", width = 0.1, size = 1) +
  geom_point(aes(x = Location, y = (response), color = Location), size = 2, data = predictions) + 
  geom_errorbar(aes(x = Location, 
                  ymin = (response - SE), 
                  ymax = (response + SE),
                  color = Location), data = predictions, inherit.aes = FALSE, width = 0.15, linewidth = 1.5) +
  scale_color_manual(values = c("Urban Center" = "#d95f02", "Urban Forest" = "#1b9e77")) +
  scale_x_discrete(labels=c("Urban Forest" = "Urban \nForest \nN = 10", "Urban Center" = "Urban \nCenter \nN = 12")) +
  scale_y_continuous(limits=c(0, 1400), breaks = c(0, 200, 400, 600, 800, 1000, 1200, 1400)) +
  theme_classic() +
  ylab("Road Disturbance \n[vehicles/day/m]") + 
  theme(text = element_text(size = 18)) + 
  theme(axis.text.x=element_text(colour="black", size=18)) + 
  theme(axis.text.y=element_text(colour="black", size=18),
        axis.title.x = element_blank()) +
  theme(legend.position = "none") +
  annotate(geom="text", x=1.5, y=1400, label="***", color="black", size = 10)

# Residual plots
residual_plots(tdr.nb, sites_wrangled)
```

**Road disturbance is higher in the urban center** than the urban forest (z = -2.87, df = 1, 21, p = 0.004). The means and SE's are 104 ± 36 vehicles/day/m for the urban forest and 398 ± 125 vehicles/day/m for the urban center.

```{r highway disturbance}
tdh <- glm(Traffic_Dist_Highway ~ Location, family = "poisson", data = sites_wrangled)
summary(tdh)

# data are likely overdispersed since the residual deviance / degrees of freedom are much larger than 1
tdh.nb <- glm.nb(Traffic_Dist_Highway ~ Location, data = sites_wrangled)
summary(tdh.nb)

# calcuate mean and standard error
sites_wrangled %>% 
  group_by(Location) %>% 
  summarize(mean = mean(Traffic_Dist_Highway),
            se = plotrix::std.error(Traffic_Dist_Highway))

# get predictions
predictions <- summary(emmeans(tdh.nb, ~Location),type = "response")

ggplot(sites_wrangled, aes(x = Location, y = Traffic_Dist_Highway)) + 
  geom_jitter(color = "grey", width = 0.1, size = 1) +
  geom_point(aes(x = Location, y = (response), color = Location), size = 2, data = predictions) + 
  geom_errorbar(aes(x = Location, 
                  ymin = (response - SE), 
                  ymax = (response + SE),
                  color = Location), data = predictions, inherit.aes = FALSE, width = 0.15, linewidth = 1.5) +
  scale_color_manual(values = c("Urban Center" = "#d95f02", "Urban Forest" = "#1b9e77")) +
  scale_x_discrete(labels=c("Urban Forest" = "Urban \nForest \nN = 10", "Urban Center" = "Urban \nCenter \nN = 12")) +
  scale_y_continuous(limits=c(0, 250), breaks = c(0, 50, 100, 150, 200, 250)) +
  theme_classic() +
  ylab("Highway Disturbance \n[vehicles/day/m]") + 
  theme(text = element_text(size = 18)) + 
  theme(axis.text.x=element_text(colour="black", size=18)) + 
  theme(axis.text.y=element_text(colour="black", size=18),
        axis.title.x = element_blank()) +
  theme(legend.position = "none") +
  annotate(geom="text", x=1.5, y=250, label="***", color="black", size = 10)

# Residual plots
residual_plots(tdh.nb, sites_wrangled)
```

**Highway disturbance is higher in the urban center** than the urban fores (z = -2.64, df = 1, 21, p = 0.008). The means and SE's are 35.6 ± 6.04 vehicles/day/m for the urban forest and 65.0 ± 9.82 vehicles/day/m for the urban center.

```{r plant species richness}
plant <- glm(TotalSub ~ Location, family = "poisson", data = sites_wrangled)
summary(plant)

# data are likely overdispersed since the residual deviance / degrees of freedom are much larger than 1
plant.nb <- glm.nb(TotalSub ~ Location, data = sites_wrangled)
summary(plant.nb)

# calcuate mean and standard error
sites_wrangled %>% 
  group_by(Location) %>% 
  summarize(mean = mean(TotalSub),
            se = plotrix::std.error(TotalSub))
# get predictions
predictions <- summary(emmeans(plant.nb, ~Location),type = "response")

ggplot(sites_wrangled, aes(x = Location, y = (TotalSub))) + 
  geom_jitter(color = "grey", width = 0.1, size = 1) +
  geom_point(aes(x = Location, y = (response), color = Location), size = 2, data = predictions) + 
  geom_errorbar(aes(x = Location, 
                  ymin = (response - SE), 
                  ymax = (response + SE),
                  color = Location), data = predictions, inherit.aes = FALSE, width = 0.15, linewidth = 1.5) +
  scale_color_manual(values = c("Urban Center" = "#d95f02", "Urban Forest" = "#1b9e77")) +
  scale_x_discrete(labels=c("Urban Forest" = "Urban \nForest \nN = 10", "Urban Center" = "Urban \nCenter \nN = 12")) +
  scale_y_continuous(limits=c(0, 25), breaks = c(0, 5, 10, 15, 20, 25)) +
  theme_classic() +
  ylab("Plant Species Richness \n[species/site]") + 
  theme(text = element_text(size = 18)) + 
  theme(axis.text.x=element_text(colour="black", size=18)) + 
  theme(axis.text.y=element_text(colour="black", size=18),
        axis.title.x = element_blank()) +
  theme(legend.position = "none") +
  annotate(geom="text", x=1.5, y=25, label="***", color="black", size = 10)

# Residual plots
residual_plots(plant.nb, sites_wrangled)
```

Plant species richness is **significantly higher in the urban forest** than the urban center (z = 6.61, df = 1, 21, p < 0.001). The means and SE's are 13.30 ± 1.56 species for the urban forest and 3.33 ± 0.58 species for the urban center.

```{r spectral radiance}
spec <- glm(spec_rad ~ Location, family = "poisson", data = sites_wrangled)
summary(spec)

spec.nb <- glm.nb(spec_rad ~ Location, data = sites_wrangled)
summary(spec.nb)

# calcuate mean and standard error
sites_wrangled %>% 
  group_by(Location) %>% 
  summarize(mean = mean(spec_rad),
            se = plotrix::std.error(spec_rad))

# get predictions
predictions <- summary(emmeans(spec.nb, ~Location),type = "response")

ggplot(sites_wrangled, aes(x = Location, y = spec_rad)) + 
  geom_jitter(color = "grey", width = 0.1, size = 1) +
  geom_point(aes(x = Location, y = response, color = Location), size = 2, data = predictions) + 
  geom_errorbar(aes(x = Location, 
                  ymin = response - SE, 
                  ymax = response + SE,
                  color = Location), data = predictions, inherit.aes = FALSE, width = 0.15, linewidth = 1.5) +
  scale_color_manual(values = c("Urban Center" = "#d95f02", "Urban Forest" = "#1b9e77")) +
  scale_x_discrete(labels=c("Urban Forest" = "Urban \nForest \nN = 10", "Urban Center" = "Urban \nCenter \nN = 12")) +
  scale_y_continuous(limits=c(130, 165), breaks = c(130, 135, 140, 145, 150, 155, 160, 165)) +
  theme_classic() +
  ylab("Spectral Radiance \n[Watts/(m² * sr * µm)]") + 
  theme(text = element_text(size = 18)) + 
  theme(axis.text.x=element_text(colour="black", size=18)) + 
  theme(axis.text.y=element_text(colour="black", size=18),
        axis.title.x = element_blank()) +
  theme(legend.position = "none") +
  annotate(geom="text", x=1.5, y=165, label="**", color="black", size = 10)

# Residual plots
residual_plots(spec.nb, sites_wrangled)
```

Spectral radiance is **significantly higher in the urban center** than the urban forest (z = -3.079, df = 1, 21, p = 0.002). The means and SE's are 137 ± 3.71 Watts/(m² * sr * µm) for the urban forest and 153 ± 3.58 Watts/(m² * sr * µm) for the urban center.

```{r light at night}
light <- glm(light_rad ~ Location, family = "poisson", data = sites_wrangled)
summary(light)

# data are likely overdispersed since the residual deviance / degrees of freedom are much larger than 1
light.nb <- glm.nb(light_rad ~ Location, data = sites_wrangled)
summary(light.nb)

# calculate mean and std. error
sites_wrangled %>% 
  group_by(Location) %>% 
  summarize(mean = mean(light_rad),
            se = plotrix::std.error(light_rad))

# get predictions
predictions <- summary(emmeans(light.nb, ~Location),type = "response")

ggplot(sites_wrangled, aes(x = Location, y = light_rad)) + 
  geom_jitter(color = "grey", width = 0.1, size = 1) +
  geom_point(aes(x = Location, y = response, color = Location), size = 2, data = predictions) + 
  geom_errorbar(aes(x = Location, 
                  ymin = response - SE, 
                  ymax = response + SE,
                  color = Location), data = predictions, inherit.aes = FALSE, width = 0.15, linewidth = 1.5) +
  scale_color_manual(values = c("Urban Center" = "#d95f02", "Urban Forest" = "#1b9e77")) +
  scale_x_discrete(labels=c("Urban Forest" = "Urban \nForest \nN = 10", "Urban Center" = "Urban \nCenter \nN = 12")) +
  scale_y_continuous(limits=c(0, 175), breaks = c(0, 25, 50, 75, 100, 125, 150, 175)) +
  theme_classic() +
  ylab("Radiance [mcd/m²]") + 
  theme(text = element_text(size = 18)) + 
  theme(axis.text.x=element_text(colour="black", size=18)) + 
  theme(axis.text.y=element_text(colour="black", size=18),
        axis.title.x = element_blank()) +
  theme(legend.position = "none") +
  annotate(geom="text", x=1.5, y=175, label="***", color="black", size = 10)

# Residual plots
residual_plots(light.nb, sites_wrangled)
```

Light radiance is **significantly higher in the urban center** than the urban forest (z = -17.17, df = 1, 21, p < 0.001). The means and SE's are 5.89 ± 0.91 mcd/m² for the urban forest and 116.90 ± 9.39 mcd/m² for the urban center.

```{r patch area}
patch <- glm(patch_area_mm ~ Location, family = "poisson", data = sites_wrangled)
summary(patch)

# data are likely overdispersed since the residual deviance / degrees of freedom are much larger than 1
patch.nb <- glm.nb(patch_area_mm ~ Location, data = sites_wrangled)
summary(patch.nb)

# calculate mean and standard error
sites_wrangled %>% 
  group_by(Location) %>% 
  summarize(mean = mean(patch_area_mm),
            se = plotrix::std.error(patch_area_mm))

# get predictions
predictions <- summary(emmeans(patch.nb, ~Location),type = "response")

ggplot(sites_wrangled, aes(x = Location, y = (patch_area_mm))) + 
  geom_jitter(color = "grey", width = 0.1, size = 1) +
  geom_point(aes(x = Location, y = (response), color = Location), size = 2, data = predictions) + 
  geom_errorbar(aes(x = Location, 
                  ymin = (response - SE), 
                  ymax = (response + SE),
                  color = Location), data = predictions, inherit.aes = FALSE, width = 0.15, linewidth = 1.5) +
  scale_color_manual(values = c("Urban Center" = "#d95f02", "Urban Forest" = "#1b9e77")) +
  scale_x_discrete(labels=c("Urban Forest" = "Urban \nForest \nN = 10", "Urban Center" = "Urban \nCenter \nN = 12")) +
  scale_y_continuous(limits=c(0, 130310), breaks = c(0, 20000, 40000, 60000, 80000, 100000, 120000)) +
  theme_classic() +
  ylab("Patch Area [mm²]") + 
  theme(text = element_text(size = 18)) + 
  theme(axis.text.x=element_text(colour="black", size=18)) + 
  theme(axis.text.y=element_text(colour="black", size=18),
        axis.title.x = element_blank()) +
  theme(legend.position = "none") +
  annotate(geom="text", x=1.5, y=130310, label="***", color="black", size = 10)

# Residual plots
residual_plots(patch.nb, sites_wrangled)
```

Patch area is **significantly higher in the urban forest** than the urban center (z = 13.08, df = 1, 21, p < 0.001). The means and SE's are 46,295 ± 11,128 mm² for the urban forest and 654 ± 144 mm² for the urban center.

```{r total road length}
road <- glm(road_length_m ~ Location, family = "poisson", data = sites_wrangled)
summary(road)

# data are likely overdispersed since the residual deviance / degrees of freedom are much larger than 1
road.nb <- glm.nb(road_length_m ~ Location, data = sites_wrangled)
summary(road.nb)

# calculate mean and standard error
sites_wrangled %>% 
  group_by(Location) %>% 
  summarize(mean = mean(road_length_m),
            se = plotrix::std.error(road_length_m))

# get predictions
predictions <- summary(emmeans(road.nb, ~Location),type = "response")

ggplot(sites_wrangled, aes(x = Location, y = road_length_m)) + 
  geom_jitter(color = "grey", width = 0.1, size = 1) +
  geom_point(aes(x = Location, y = response, color = Location), size = 2, data = predictions) + 
  geom_errorbar(aes(x = Location, 
                  ymin = response - SE, 
                  ymax = response + SE,
                  color = Location), data = predictions, inherit.aes = FALSE, width = 0.15, linewidth = 1.5) +
  scale_color_manual(values = c("Urban Center" = "#d95f02", "Urban Forest" = "#1b9e77")) +
  scale_x_discrete(labels=c("Urban Forest" = "Urban \nForest \nN = 10", "Urban Center" = "Urban \nCenter \nN = 12")) +
  scale_y_continuous(limits=c(0, 140), breaks = c(0, 20, 40, 60, 80, 100, 120, 140)) +
  theme_classic() +
  ylab("Total Length of Road \n[m, 100m radius]") + 
  theme(text = element_text(size = 18)) + 
  theme(axis.text.x=element_text(colour="black", size=18)) + 
  theme(axis.text.y=element_text(colour="black", size=18),
        axis.title.x = element_blank()) +
  theme(legend.position = "none") +
  annotate(geom="text", x=1.5, y=140, label="***", color="black", size = 10)

# Residual plots
residual_plots(road.nb, sites_wrangled)
```

Total road length is **significantly higher in the urban center** than the urban forest (z = -2.74, df = 1, 21, p = 0.006). The means and SE's are 15.6 ± 7.54 m for the urban forest and 93.0 ± 40.60 m for the urban center.

### 2024-09-30 4_spider_measurements_nb.Rmd
Organized code and wrote README.md file to help viewers interact with code

---
title: "Spider web abundance, patterns, and positions between habitats"
author: "Brandi Pessman"
date: "`r Sys.Date()`"
output: html_document
---
# Setting the Working Directory and Global Code Chunk Options

I have set message and warning to FALSE for every chunk so the knitted document does not include messages and warnings.

```{r setup}
knitr::opts_chunk$set(message = FALSE, warning = FALSE, echo = FALSE)
require("knitr")
opts_knit$set(root.dir = "/Users/bjpessman/Documents/phd_research_code/Agelenopsis_aggregation")
```

# Packages to Load

```{r packages}
library(tidyverse) # for graphing
library(lme4) # to run the glmer function for the web distance (random effects)
library(glmmTMB) # for proportion test
library(MASS) # negative binomial tests
source('functions/residual_plots_function.R') # produces residual plots
source('functions/model_comparison_function.R') # produces model comparison plots
source('functions/get_predictions_function.R') #  get predictions for bootstrapping
```

# Import Data

```{r import}
sites_wrangled <- readRDS('wrangled_data/sites_wrangled.RDS')
neighbors_wrangled <- readRDS('wrangled_data/neighbors_wrangled.RDS')
webs_wrangled <- readRDS('wrangled_data/webs_wrangled.RDS')
```

# Response Variable: Search Distance

For this variable, I've gone back and forth on whether I should log-transform the search distance (because it can be ran Gaussian), or whether to use a log-link function (Poisson Distribution). The poisson glm more closely matches the mean, but the log-transformation is better at capturing the variance. Each step of the way, I have performed each test to try and gauge a best route forward. The poisson glm suggests a significant difference while the log-transformed shows no difference.

```{r search distance}
# graph raw and log-transformed distribution
ggarrange(ggplot(sites_wrangled, aes(x = WalkDist)) +
            geom_density(),
          ggplot(sites_wrangled, aes(x = log(WalkDist))) +
            geom_density(), ncol = 2)

shapiro.test(sites_wrangled$WalkDist) # not normal
shapiro.test(log(sites_wrangled$WalkDist)) # normal

search_poisson <- glm(WalkDist ~ Location, data = sites_wrangled, family = poisson)
summary(search_poisson) # overdispersed

search.nb <- glm.nb(WalkDist ~ Location, data = sites_wrangled)
summary(search.nb)

search_log <- glm(log(WalkDist) ~ Location, data = sites_wrangled)
summary(search_log)

# calculate mean and standard error
sites_wrangled %>% 
  group_by(Location) %>% 
  summarize(mean = mean(WalkDist),
            se = plotrix::std.error(WalkDist))

# Compare model plots
plot_model_comparisons(data = sites_wrangled, 
                       model_nb = search.nb, 
                       model_poisson = search_poisson, 
                       model_log = search_log,
                       x_var = "Location",
                       y_var = "WalkDist",
                       y_limits = c(0, 275), 
                       y_breaks = c(0, 50, 100, 150, 200, 250),
                       y_lab = "Search Distance [m]",
                       labels = c("***", "***", "N.S."))

# Residual plots
residual_plots(search.nb, sites_wrangled)
residual_plots(search_log, sites_wrangled)
```

Using a negative binomial regression,  **search distance did not significantly differ between habitats** (z = -1.15, df = 1, 20, p = 0.251).

# Response Variable: Number of Webs

```{r number of webs}
ggarrange(ggplot(sites_wrangled, aes(x = NumWebs)) +
            geom_density(),
          ggplot(sites_wrangled, aes(x = log(NumWebs))) +
            geom_density(), ncol = 2)

shapiro.test(sites_wrangled$NumWebs) # not normal
shapiro.test(log(sites_wrangled$NumWebs)) # just normal

web_poisson <- glm(NumWebs ~ Location, data = sites_wrangled, family = poisson)
summary(web_poisson)

web.nb <- glm.nb(NumWebs ~ Location, data = sites_wrangled)
summary(web.nb)

web_log <- glm(log(NumWebs) ~ Location, data = sites_wrangled)
summary(web_log)

# Calculate mean and standard error
sites_wrangled %>% 
  group_by(Location) %>% 
  summarize(mean = mean(NumWebs),
            se = plotrix::std.error(NumWebs))

# Compare model plots
plot_model_comparisons(data = sites_wrangled, 
                       model_nb = web.nb, 
                       model_poisson = web_poisson, 
                       model_log = web_log,
                       x_var = "Location",
                       y_var = "NumWebs",
                       y_limits = c(0, 75), 
                       y_breaks = c(0, 15, 30, 45, 60, 75),
                       y_lab = "Number of Webs",
                       labels = c("***", "**", "***"))

# Residual plots
residual_plots(web.nb, sites_wrangled)
residual_plots(web_log, sites_wrangled)
```

There were **significantly more webs at sites in the urban center** than the urban forest (z = 4.45, df = 1, 20, p < 0.001).

# Response Variable: Number of Spiders

```{r number of spiders}
ggarrange(ggplot(sites_wrangled, aes(x = NumSpiders)) +
            geom_density(),
          ggplot(sites_wrangled, aes(x = log(NumSpiders))) +
            geom_density(), ncol = 2)

shapiro.test(sites_wrangled$NumSpiders) # not normal
shapiro.test(log(sites_wrangled$NumSpiders)) # not normal

spider_poisson <- glm(NumSpiders ~ Location, data = sites_wrangled, family = poisson)
summary(spider_poisson)

spider.nb <- glm.nb(NumSpiders ~ Location, data = sites_wrangled)
summary(spider.nb)

spider_log <- glm(log(NumSpiders) ~ Location, data = sites_wrangled)
summary(spider_log)

# Calculate mean and standard error
sites_wrangled %>% 
  group_by(Location) %>% 
  summarize(mean = mean(NumSpiders),
            se = plotrix::std.error(NumSpiders))

# Compare model plots
plot_model_comparisons(data = sites_wrangled, 
                       model_nb = spider.nb, 
                       model_poisson = spider_poisson, 
                       model_log = spider_log,
                       x_var = "Location",
                       y_var = "NumSpiders",
                       y_limits = c(0, 25), 
                       y_breaks = c(0, 5, 10, 15, 20, 25),
                       y_lab = "Number of Spiders",
                       labels = c("***", ".", "**"))

# Residual plots
residual_plots(spider.nb, sites_wrangled)
residual_plots(spider_log, sites_wrangled)
```

The **number of spiders present by site is significantly higher in the urban center** (z = 3.13, df = 1, 20, p = 0.002).

# Response Variable: Nearest Neighbor Distances

```{r neighbor distance stats}
ggarrange(ggplot(neighbors_wrangled, aes(x = RetreatDist)) +
            geom_density(),
          ggplot(neighbors_wrangled, aes(x = log(RetreatDist))) +
            geom_density(), ncol = 2)

shapiro.test(neighbors_wrangled$RetreatDist) # not normal
shapiro.test(log(neighbors_wrangled$RetreatDist)) # not normal

neighbor_poisson <- glmer(round(RetreatDist, 0) ~ Location * factor(Neighbor) + (1 | ID), data = neighbors_wrangled, family = poisson)
summary(neighbor_poisson)

neighbor.nb <- glmer.nb(round(RetreatDist, 0) ~ Location * factor(Neighbor) + (1 | ID), data = neighbors_wrangled)
summary(neighbor.nb)

neighbor_log <- lmer(log(RetreatDist) ~ Location * factor(Neighbor) + (1 | ID), data = neighbors_wrangled)
coefs <- data.frame(coef(summary(neighbor_log)))
coefs$p.z <- 2 * (1 - pnorm(abs(coefs$t.value)))
coefs

# Both methods yield similar results
neighbors_wrangled %>% 
  group_by(Location) %>% 
  summarize(mean = mean(RetreatDist),
            se = plotrix::std.error(RetreatDist))
```

```{r neighbor distance plots}
# Negative Binomial
predictions <- expand.grid(Location = levels(factor(neighbors_wrangled$Location)), Neighbor = levels(factor(neighbors_wrangled$Neighbor)))
predictions$response <- predict(neighbor.nb, newdata = predictions, se.fit = TRUE, re.form = NA, type = "response")

#bigBoot_neighbors_nb <- bootMer(neighbor.nb, get_predictions, nsim = 1000)
#saveRDS(bigBoot_neighbors_nb, file = "bootstrapping/bigBoot_neighbors_nb.Rds")
bigBoot_neighbors_nb <- readRDS("bootstrapping/bigBoot_neighbors_nb.Rds") 
predSE <- t(apply(bigBoot_neighbors_nb$t, MARGIN = 2, FUN = sd, na.rm = TRUE))
predictions$SE <- predSE[1, ]
#predictions2 <- summary(emmeans(neighbor.nb, ~Location | Neighbor,type = "response"))

neighbors_nb_plot <- ggplot(neighbors_wrangled, aes(x = Neighbor, y = RetreatDist)) + 
  geom_jitter(aes(color = Location), alpha = 0.5, width = 0.1) +
    geom_line(aes(x = Neighbor, y = response, group = Location), size = 2, data = predictions, color = "grey") +
  geom_point(aes(x = Neighbor, y = response, color = Location), size = 2, data = predictions) + 
  geom_errorbar(aes(x = Neighbor, 
                  ymin = response - SE, 
                  ymax = response + SE,
                  color = Location), data = predictions, inherit.aes = FALSE, width = 0.15, size = 1) +
  scale_color_manual(values = c("Urban Center" = "#d95f02", "Urban Forest" = "#1b9e77")) +
  scale_x_discrete(labels=c("Urban Forest" = "Urban \nForest \nN = 10", "Urban Center" = "Urban \nCenter \nN = 12")) +
  theme_classic() +
  scale_y_continuous(limits = c(-50, 1050), breaks = c(0, 200, 400, 600, 800, 1000)) +
  xlab("Nearest Neighbors") +
  ylab("Distance from Focal Web \nto Neighbor Web [cm]") + 
  theme(text = element_text(size = 10)) + 
  theme(axis.text.x = element_text(colour = "black", size = 10)) + 
  theme(axis.text.y = element_text(colour = "black", size = 10)) +
  theme(legend.position = "none")

# raw data
raw <- neighbors_wrangled %>% 
  group_by(Location, Neighbor) %>% 
  summarise(mean = mean(RetreatDist),
            se = plotrix::std.error(RetreatDist))

neighbors_raw_plot <- ggplot(neighbors_wrangled, aes(x = Neighbor, y = RetreatDist)) + 
  geom_jitter(aes(color = Location), alpha = 0.5, width = 0.1) +
  geom_point(aes(x = Neighbor, y = mean, color = Location), size = 2, data = raw) +
  geom_line(aes(x = Neighbor, y = mean, group = Location), size = 2, data = raw, color = "grey") +
  geom_errorbar(aes(x= Neighbor, 
                    ymin = mean - se, 
                    ymax = mean + se, 
                    color = Location), data = raw, inherit.aes = FALSE, width = 0.15, size = 1.5) +
    scale_color_manual(values = c("Urban Center" = "#d95f02", "Urban Forest" = "#1b9e77")) +
    scale_x_discrete(labels=c("Urban Forest" = "Urban \nForest \nN = 10", "Urban Center" = "Urban \nCenter \nN = 12")) +
    theme_classic() +
    scale_y_continuous(limits = c(-50, 1000), breaks = c(0, 200, 400, 600, 800, 1000)) +
    xlab("Nearest Neighbors") +
    ylab("Distance from Focal Web \nto Neighbor Web [cm]") + 
    theme(text = element_text(size = 10)) + 
    theme(axis.text.x = element_text(colour = "black", size = 10)) + 
    theme(axis.text.y = element_text(colour = "black", size = 10)) +
    theme(legend.position = "none")

# Non-transformed, poisson distribution
predictions <- expand.grid(Location = levels(factor(neighbors_wrangled$Location)), Neighbor = levels(factor(neighbors_wrangled$Neighbor)))
predictions$response <- predict(neighbor_poisson, newdata = predictions, se.fit = TRUE, re.form = NA, type = "response")

#bigBoot_neighbors_poisson <- bootMer(neighbor_poisson, get_predictions, nsim = 1000)
#saveRDS(bigBoot_neighbors_poisson, file = "bootstrapping/bigBoot_neighbors_poisson.Rds")
bigBoot_neighbors_poisson <- readRDS("bootstrapping/bigBoot_neighbors_poisson.Rds")
predSE <- t(apply(bigBoot_neighbors_poisson$t, MARGIN = 2, FUN = sd))
predictions$SE <- predSE[1, ]
#predictions2 <- summary(emmeans(neighbor_poisson, ~Location | Neighbor,type = "response"))

neighbors_poisson_plot <- ggplot(neighbors_wrangled, aes(x = Neighbor, y = RetreatDist)) + 
  geom_jitter(aes(color = Location), alpha = 0.5, width = 0.1) +
  geom_point(aes(x = Neighbor, y = response, color = Location), size = 2, data = predictions) + 
  geom_line(aes(x = Neighbor, y = response, group = Location), size = 2, data = predictions, color = "grey") +
  geom_errorbar(aes(x = Neighbor, 
                  ymin = response - SE, 
                  ymax = response + SE,
                  color = Location), data = predictions, inherit.aes = FALSE, width = 0.15, size = 1.5) +
  scale_color_manual(values = c("Urban Center" = "#d95f02", "Urban Forest" = "#1b9e77")) +
  scale_x_discrete(labels=c("Urban Forest" = "Urban \nForest \nN = 10", "Urban Center" = "Urban \nCenter \nN = 12")) +
  theme_classic() +
  scale_y_continuous(limits = c(-50, 1000), breaks = c(0, 200, 400, 600, 800, 1000)) +
  xlab("Nearest Neighbors") +
  ylab("Distance from Focal Web \nto Neighbor Web [cm]") + 
  theme(text = element_text(size = 10)) + 
  theme(axis.text.x = element_text(colour = "black", size = 10)) + 
  theme(axis.text.y = element_text(colour = "black", size = 10)) +
  theme(legend.position = "none")

# Let's look at the log-transformed response variable since that is normal
predictions <- expand.grid(Location = levels(factor(neighbors_wrangled$Location)), Neighbor = levels(factor(neighbors_wrangled$Neighbor)))
predictions$response <- predict(neighbor_log, newdata = predictions, se.fit = TRUE, re.form = NA, type = "response")

#bigBoot_neighbors_log <- bootMer(neighbor_log, get_predictions, nsim = 1000)
#saveRDS(bigBoot_neighbors_log, file = "bootstrapping/bigBoot_neighbors_log.Rds")
bigBoot_neighbors_log <- readRDS("bootstrapping/bigBoot_neighbors_log.Rds")
predSE <- t(apply(bigBoot_neighbors_log$t, MARGIN = 2, FUN = sd))
predictions$SE <- predSE[1, ]
#predictions2 <- summary(emmeans(neighbor_log, ~Location | Neighbor,type = "response"))

neighbors_log_plot <- ggplot(neighbors_wrangled, aes(x = Neighbor, y = (RetreatDist))) + 
  geom_jitter(aes(color = Location), alpha = 0.5, width = 0.1) +
  geom_point(aes(x = Neighbor, y = exp(response), color = Location), size = 2, data = predictions) + 
  geom_line(aes(x = Neighbor, y = exp(response), group = Location), size = 2, data = predictions, color = "grey") +
  geom_errorbar(aes(x = Neighbor, 
                  ymin = exp(response - SE), 
                  ymax = exp(response + SE),
                  color = Location), data = predictions, inherit.aes = FALSE, width = 0.15, size = 1.5) +
  scale_color_manual(values = c("Urban Center" = "#d95f02", "Urban Forest" = "#1b9e77")) +
  scale_x_discrete(labels=c("Urban Forest" = "Urban \nForest \nN = 10", "Urban Center" = "Urban \nCenter \nN = 12")) +
  theme_classic() +
  scale_y_continuous(limits = c(-50, 1000), breaks = c(0, 200, 400, 600, 800, 1000)) +
  xlab("Nearest Neighbors") +
  ylab("Distance from Focal Web \nto Neighbor Web [cm]") + 
  theme(text = element_text(size = 10)) + 
  theme(axis.text.x = element_text(colour = "black", size = 10)) + 
  theme(axis.text.y = element_text(colour = "black", size = 10))

ggarrange(neighbors_raw_plot, 
          neighbors_poisson_plot, 
          neighbors_log_plot, 
          neighbors_nb_plot,
          labels = c("Raw Data", "Poisson Distribution", "Log-Transformed", "Negative Binomial"),
          nrow = 1, 
          common.legend = TRUE)
```

```{r neighbor distance residual plots}
# Negative Binomial
test_nb <- augment(neighbor.nb, data = neighbors_wrangled)
resid_nb <- ggplot(test_nb, aes(x = .fitted, y = .resid)) + 
  geom_point() + 
  geom_smooth() +
  geom_hline(yintercept = 0) +
  xlab("Fitted Values") +
  ylab("Standardized \nResiduals") +
  theme_classic() +
  theme(text = element_text(size = 14, color = "black")) +
  theme(axis.text.x=element_text(color="black", size=14)) + 
  theme(axis.text.y=element_text(color="black", size=14))

y <- quantile(test_nb$.resid, c(0.25, 0.75))
x <- qnorm(c(0.25, 0.75))
slope <- diff(y)/diff(x)
int <- y[1L] - slope * x[1L]

qq_nb <- ggplot(test_nb, aes(sample = .resid)) + 
  stat_qq() + 
  geom_abline(slope = slope, intercept = int) +
  xlab("Theoretical Quantiles") +
  ylab("Sample Quantiles") +
  theme_classic() +
  theme(text = element_text(size = 14, color = "black")) +
  theme(axis.text.x=element_text(color="black", size=14)) + 
  theme(axis.text.y=element_text(color="black", size=14))

scaleloc_nb <- ggplot(test_nb, aes(x = .fitted, y = sqrt(abs(.resid)))) + 
  geom_point() + 
  geom_smooth() + 
  geom_hline(yintercept = 0.83) +
  xlab("Fitted Values") +
  ylab("Sqrt Standardized \nResiduals") +
  theme_classic() +
  theme(text = element_text(size = 14, color = "black")) +
  theme(axis.text.x=element_text(color="black", size=14)) + 
  theme(axis.text.y=element_text(color="black", size=14))

lev_nb <- ggplot(test_nb, aes(.hat, .resid)) +
 geom_vline(colour = "black", xintercept = 0) +
  geom_hline(colour = "black", yintercept = 0) +
  geom_point(aes(size = .cooksd)) + geom_smooth(se = FALSE) +
  xlab("Theoretical Quantiles") +
  ylab("Sample Quantiles") +
  labs(size = "Cook's \nDistance") +
  theme_classic() +
  theme(text = element_text(size = 14, color = "black")) +
  theme(axis.text.x=element_text(color="black", size=14)) + 
  theme(axis.text.y=element_text(color="black", size=14))

ggarrange(resid_nb, qq_nb, scaleloc_nb, lev_nb, 
          labels = c("A", "B", "C", "D"),
          ncol = 2, nrow = 2)

# Log-transformed, Normal
test_log <- augment(neighbor_log, data = neighbors_wrangled)
resid_log <- ggplot(test_log, aes(x = .fitted, y = .resid)) + 
  geom_point() + 
  geom_smooth() +
  geom_hline(yintercept = 0) +
  xlab("Fitted Values") +
  ylab("Standardized \nResiduals") +
  theme_classic() +
  theme(text = element_text(size = 14, color = "black")) +
  theme(axis.text.x=element_text(color="black", size=14)) + 
  theme(axis.text.y=element_text(color="black", size=14))

y <- quantile(test_log$.resid, c(0.25, 0.75))
x <- qnorm(c(0.25, 0.75))
slope <- diff(y)/diff(x)
int <- y[1L] - slope * x[1L]

qq_log <- ggplot(test_log, aes(sample = .resid)) + 
  stat_qq() + 
  geom_abline(slope = slope, intercept = int) +
  xlab("Theoretical Quantiles") +
  ylab("Sample Quantiles") +
  theme_classic() +
  theme(text = element_text(size = 14, color = "black")) +
  theme(axis.text.x=element_text(color="black", size=14)) + 
  theme(axis.text.y=element_text(color="black", size=14))

scaleloc_log <- ggplot(test_log, aes(x = .fitted, y = sqrt(abs(.resid)))) + 
  geom_point() + 
  geom_smooth() + 
  geom_hline(yintercept = 0.83) +
  xlab("Fitted Values") +
  ylab("Sqrt Standardized \nResiduals") +
  theme_classic() +
  theme(text = element_text(size = 14, color = "black")) +
  theme(axis.text.x=element_text(color="black", size=14)) + 
  theme(axis.text.y=element_text(color="black", size=14))

lev_log <- ggplot(test_log, aes(.hat, .resid)) +
 geom_vline(colour = "black", xintercept = 0) +
  geom_hline(colour = "black", yintercept = 0) +
  geom_point(aes(size = .cooksd)) + geom_smooth(se = FALSE) +
  xlab("Theoretical Quantiles") +
  ylab("Sample Quantiles") +
  labs(size = "Cook's \nDistance") +
  theme_classic() +
  theme(text = element_text(size = 14, color = "black")) +
  theme(axis.text.x=element_text(color="black", size=14)) + 
  theme(axis.text.y=element_text(color="black", size=14))

ggarrange(resid_log, qq_log, scaleloc_log, lev_log, 
          labels = c("A", "B", "C", "D"),
          ncol = 2, nrow = 2)
```

Spider neighbors were **significantly closer in the urban center** than the urban forest (z = -1.83, df = 1, 21, p < 0.001). The **second neighbor was always further from the focal web** than the first (z = 2.83, df = 1, 21, p = 0.005), as this is how we defined the first and second neighbor. There was **no interaction between location and neighbor** (z = -1.09, df = 1, 21, p = 0.276) - the distance between the first and second neighbor did not differ between the urban center and the urban forest.

# Response Variable: Web Height

```{r web height stats}
ggarrange(ggplot(webs_wrangled, aes(x = RetreatHeight)) +
            geom_density(),
          ggplot(webs_wrangled, aes(x = log(RetreatHeight))) +
            geom_density(), ncol = 2)

shapiro.test(webs_wrangled$RetreatHeight) # not normal
shapiro.test(log(webs_wrangled$RetreatHeight)) # not normal

# retreat height
height_poisson <- glmer(round(RetreatHeight, 0) ~ Location + (1 | ID), data = webs_wrangled, family = poisson)
summary(height_poisson)

height.nb <- glmer.nb(round(RetreatHeight, 0) ~ Location + (1 | ID), data = webs_wrangled)
summary(height.nb)

height_log <- lmer(log(RetreatHeight) ~ Location + (1 | ID), data = webs_wrangled)
summary(height_log)

# substrate height
subheight.nb <- glmer.nb(round(SubHeight, 0) ~ Location + (1 | ID), data = webs_wrangled)
summary(subheight.nb)

# proportion retreat height to substrate height
height_prop <- glmmTMB(Proportion ~ Location + (1|ID), data = webs_wrangled, family = "beta")
summary(height_prop)
```

```{r web heights plots}
# Negative Binomial
predictions <- expand.grid(Location = levels(factor(webs_wrangled$Location)))
predictions$response <- predict(height.nb, newdata = predictions, se.fit = TRUE, re.form = NA, type = "response")

#bigBoot_height_nb <- bootMer(height.nb, get_predictions, nsim = 1000)
#saveRDS(bigBoot_height_nb, file = "bootstrapping/bigBoot_height_nb.Rds")
bigBoot_height_nb <- readRDS("bootstrapping/bigBoot_height_nb.Rds")
predSE <- t(apply(bigBoot_height_nb$t, MARGIN = 2, FUN = sd))
predictions$SE <- predSE[1, ]
#predictions2 <- summary(emmeans(height.nb, ~Location | Neighbor,type = "response"))

height_nb_plot <- ggplot(webs_wrangled, aes(x = Location, y = RetreatHeight)) + 
  geom_jitter(color = "grey", width = 0.1) +
  geom_point(aes(x = Location, y = response, color = Location), size = 2, data = predictions) +
  geom_errorbar(aes(x= Location, 
                    ymin = response - SE, 
                    ymax = response + SE, 
                    color = Location), data = predictions, inherit.aes = FALSE, width = 0.15, size = 1) +
    scale_color_manual(values = c("Urban Center" = "#d95f02", "Urban Forest" = "#1b9e77")) +
    scale_x_discrete(labels=c("Urban Forest" = "Urban \nForest \nN = 30", "Urban Center" = "Urban \nCenter \nN = 101")) +
    theme_classic() +
    scale_y_continuous(limits = c(0, 210), breaks = c(0, 35, 70, 105, 140, 175, 210)) +
    ylab("Web Height [cm]") + 
    theme(text = element_text(size = 10)) + 
    theme(axis.text.x = element_text(colour = "black", size = 10)) + 
    theme(axis.text.y = element_text(colour = "black", size = 10),
        axis.title.x = element_blank()) +
    theme(legend.position = "none") +
    annotate(geom = "text", x = 1.5, y = 210, label = "*", color = "black", size = 5)

# raw data
raw <- webs_wrangled %>% 
  group_by(Location) %>% 
  summarise(mean = mean(RetreatHeight),
            se = plotrix::std.error(RetreatHeight))

height_raw_plot <- ggplot(webs_wrangled, aes(x = Location, y = RetreatHeight)) + 
  geom_jitter(color = "grey", width = 0.1) +
  geom_point(aes(x = Location, y = mean, color = Location), size = 2, data = raw) +
  geom_errorbar(aes(x= Location, 
                    ymin = mean - se, 
                    ymax = mean + se, 
                    color = Location), data = raw, inherit.aes = FALSE, width = 0.15, size = 1.5) +
    scale_color_manual(values = c("Urban Center" = "#d95f02", "Urban Forest" = "#1b9e77")) +
    scale_x_discrete(labels=c("Urban Forest" = "Urban \nForest \nN = 10", "Urban Center" = "Urban \nCenter \nN = 12")) +
    theme_classic() +
    scale_y_continuous(limits = c(0, 210), breaks = c(0, 35, 70, 105, 140, 175, 210)) +
    ylab("Web Height [cm]") + 
    theme(text = element_text(size = 10)) + 
    theme(axis.text.x = element_text(colour = "black", size = 10)) + 
    theme(axis.text.y = element_text(colour = "black", size = 10),
        axis.title.x = element_blank()) +
    theme(legend.position = "none")

# Non-transformed, poisson distribution
predictions <- expand.grid(Location = levels(factor(webs_wrangled$Location)))
predictions$response <- predict(height_poisson, newdata = predictions, se.fit = TRUE, re.form = NA, type = "response")

#bigBoot_height_poisson <- bootMer(height_poisson, get_predictions, nsim = 1000)
#saveRDS(bigBoot_height_poisson, file = "bootstrapping/bigBoot_height_poisson.Rds")
bigBoot_height_poisson <- readRDS("bootstrapping/bigBoot_height_poisson.Rds")
predSE <- t(apply(bigBoot_height_poisson$t, MARGIN = 2, FUN = sd))
predictions$SE <- predSE[1, ]
#predictions2 <- summary(emmeans(height_poisson, ~Location | Neighbor,type = "response"))

height_poisson_plot <- ggplot(webs_wrangled, aes(x = Location, y = RetreatHeight)) + 
  geom_jitter(color = "grey", width = 0.1) +
  geom_point(aes(x = Location, y = response, color = Location), size = 2, data = predictions) +
  geom_errorbar(aes(x= Location, 
                    ymin = response - SE, 
                    ymax = response + SE, 
                    color = Location), data = predictions, inherit.aes = FALSE, width = 0.15, size = 1.5) +
    scale_color_manual(values = c("Urban Center" = "#d95f02", "Urban Forest" = "#1b9e77")) +
    scale_x_discrete(labels=c("Urban Forest" = "Urban \nForest \nN = 10", "Urban Center" = "Urban \nCenter \nN = 12")) +
    theme_classic() +
    scale_y_continuous(limits = c(0, 210), breaks = c(0, 35, 70, 105, 140, 175, 210)) +
    ylab("Web Height [cm]") + 
    theme(text = element_text(size = 10)) + 
    theme(axis.text.x = element_text(colour = "black", size = 10)) + 
    theme(axis.text.y = element_text(colour = "black", size = 10),
        axis.title.x = element_blank()) +
    theme(legend.position = "none") +
    annotate(geom = "text", x = 1.5, y = 210, label = "*", color = "black", size = 5)

# Let's look at the log-transformed response variable since that is normal
predictions <- expand.grid(Location = levels(factor(webs_wrangled$Location)))
predictions$response <- predict(height_log, newdata = predictions, se.fit = TRUE, re.form = NA, type = "response")

#bigBoot_height_log <- bootMer(height_log, get_predictions, nsim = 1000)
#saveRDS(bigBoot_height_log, file = "bootstrapping/bigBoot_height_log.Rds")
bigBoot_height_log <- readRDS("bootstrapping/bigBoot_height_log.Rds")
predSE <- t(apply(bigBoot_height_log$t, MARGIN = 2, FUN = sd))
predictions$SE <- predSE[1, ]
#predictions2 <- summary(emmeans(height_log, ~Location | Neighbor,type = "response"))

height_log_plot <- ggplot(webs_wrangled, aes(x = Location, y = (RetreatHeight))) + 
  geom_jitter(color = "grey", width = 0.1) +
  geom_point(aes(x = Location, y = exp(response), color = Location), size = 2, data = predictions) +
  geom_errorbar(aes(x= Location, 
                    ymin = exp(response - SE), 
                    ymax = exp(response + SE), 
                    color = Location), data = predictions, inherit.aes = FALSE, width = 0.15, size = 1.5) +
    scale_color_manual(values = c("Urban Center" = "#d95f02", "Urban Forest" = "#1b9e77")) +
    scale_x_discrete(labels=c("Urban Forest" = "Urban \nForest \nN = 10", "Urban Center" = "Urban \nCenter \nN = 12")) +
    theme_classic() +
    scale_y_continuous(limits = c(0, 210), breaks = c(0, 35, 70, 105, 140, 175, 210)) +
    ylab("Web Height [cm]") + 
    theme(text = element_text(size = 10)) + 
    theme(axis.text.x = element_text(colour = "black", size = 10)) + 
    theme(axis.text.y = element_text(colour = "black", size = 10),
        axis.title.x = element_blank()) +
    theme(legend.position = "none") +
    annotate(geom = "text", x = 1.5, y = 210, label = "*", color = "black", size = 5)

ggarrange(height_raw_plot, 
          height_poisson_plot, 
          height_log_plot,
          height_nb_plot,
          labels = c("Raw Data", "Poisson Distribution", "Log-Transformed", "Negative Binomial"),
          nrow = 1, 
          common.legend = TRUE)
```

```{r web heights residual plots}
# Negative Binomial
test_nb <- augment(height.nb, data = webs_wrangled)
resid_nb <- ggplot(test_nb, aes(x = .fitted, y = .resid)) + 
  geom_point() + 
  geom_smooth() +
  geom_hline(yintercept = 0) +
  xlab("Fitted Values") +
  ylab("Standardized \nResiduals") +
  theme_classic() +
  theme(text = element_text(size = 14, color = "black")) +
  theme(axis.text.x=element_text(color="black", size=14)) + 
  theme(axis.text.y=element_text(color="black", size=14))

y <- quantile(test_nb$.resid, c(0.25, 0.75))
x <- qnorm(c(0.25, 0.75))
slope <- diff(y)/diff(x)
int <- y[1L] - slope * x[1L]

qq_nb <- ggplot(test_nb, aes(sample = .resid)) + 
  stat_qq() + 
  geom_abline(slope = slope, intercept = int) +
  xlab("Theoretical Quantiles") +
  ylab("Sample Quantiles") +
  theme_classic() +
  theme(text = element_text(size = 14, color = "black")) +
  theme(axis.text.x=element_text(color="black", size=14)) + 
  theme(axis.text.y=element_text(color="black", size=14))

scaleloc_nb <- ggplot(test_nb, aes(x = .fitted, y = sqrt(abs(.resid)))) + 
  geom_point() + 
  geom_smooth() + 
  geom_hline(yintercept = 0.83) +
  xlab("Fitted Values") +
  ylab("Sqrt Standardized \nResiduals") +
  theme_classic() +
  theme(text = element_text(size = 14, color = "black")) +
  theme(axis.text.x=element_text(color="black", size=14)) + 
  theme(axis.text.y=element_text(color="black", size=14))

lev_nb <- ggplot(test_nb, aes(.hat, .resid)) +
 geom_vline(colour = "black", xintercept = 0) +
  geom_hline(colour = "black", yintercept = 0) +
  geom_point(aes(size = .cooksd)) + geom_smooth(se = FALSE) +
  xlab("Theoretical Quantiles") +
  ylab("Sample Quantiles") +
  labs(size = "Cook's \nDistance") +
  theme_classic() +
  theme(text = element_text(size = 14, color = "black")) +
  theme(axis.text.x=element_text(color="black", size=14)) + 
  theme(axis.text.y=element_text(color="black", size=14))

ggarrange(resid_nb, qq_nb, scaleloc_nb, lev_nb, 
          labels = c("A", "B", "C", "D"),
          ncol = 2, nrow = 2)

# Log-transformed, Normal
test_log <- augment(height_log, data = webs_wrangled)
resid_log <- ggplot(test_log, aes(x = .fitted, y = .resid)) + 
  geom_point() + 
  geom_smooth() +
  geom_hline(yintercept = 0) +
  xlab("Fitted Values") +
  ylab("Standardized \nResiduals") +
  theme_classic() +
  theme(text = element_text(size = 14, color = "black")) +
  theme(axis.text.x=element_text(color="black", size=14)) + 
  theme(axis.text.y=element_text(color="black", size=14))

y <- quantile(test_log$.resid, c(0.25, 0.75))
x <- qnorm(c(0.25, 0.75))
slope <- diff(y)/diff(x)
int <- y[1L] - slope * x[1L]

qq_log <- ggplot(test_log, aes(sample = .resid)) + 
  stat_qq() + 
  geom_abline(slope = slope, intercept = int) +
  xlab("Theoretical Quantiles") +
  ylab("Sample Quantiles") +
  theme_classic() +
  theme(text = element_text(size = 14, color = "black")) +
  theme(axis.text.x=element_text(color="black", size=14)) + 
  theme(axis.text.y=element_text(color="black", size=14))

scaleloc_log <- ggplot(test_log, aes(x = .fitted, y = sqrt(abs(.resid)))) + 
  geom_point() + 
  geom_smooth() + 
  geom_hline(yintercept = 0.83) +
  xlab("Fitted Values") +
  ylab("Sqrt Standardized \nResiduals") +
  theme_classic() +
  theme(text = element_text(size = 14, color = "black")) +
  theme(axis.text.x=element_text(color="black", size=14)) + 
  theme(axis.text.y=element_text(color="black", size=14))

lev_log <- ggplot(test_log, aes(.hat, .resid)) +
 geom_vline(colour = "black", xintercept = 0) +
  geom_hline(colour = "black", yintercept = 0) +
  geom_point(aes(size = .cooksd)) + geom_smooth(se = FALSE) +
  xlab("Theoretical Quantiles") +
  ylab("Sample Quantiles") +
  labs(size = "Cook's \nDistance") +
  theme_classic() +
  theme(text = element_text(size = 14, color = "black")) +
  theme(axis.text.x=element_text(color="black", size=14)) + 
  theme(axis.text.y=element_text(color="black", size=14))

ggarrange(resid_log, qq_log, scaleloc_log, lev_log, 
          labels = c("A", "B", "C", "D"),
          ncol = 2, nrow = 2)
```

**Webs are significantly higher in the urban forest** than the urban center (z = -2.44, df = 1, 21, p = 0.015).

### 2024-09-30 5_environmental_aic_selection.Rmd
Organized code and wrote README.md file to help viewers interact with code

---
title: "Environmental predictors of spider spatial patterns "
author: "Brandi Pessman"
date: "`r Sys.Date()`"
output: html_document
---
# Setting the Working Directory and Global Code Chunk Options

I have set message and warning to FALSE for every chunk so the knitted document does not include messages and warnings.

```{r setup}
knitr::opts_chunk$set(message = FALSE, warning = FALSE, echo = FALSE)
require("knitr")
opts_knit$set(root.dir = "/Users/bjpessman/Documents/phd_research_code/Agelenopsis_aggregation")
```

# Packages to Load

```{r packages}
library(tidyverse) # for making graphs
library(pander) # viewing AIC comparisons between models
library(AICcmodavg) # also helps viewing AIC comparisons
library(MuMIn) # to run the dredge function
library(lme4) # to run the glmer function for the web distance (random effects)
source('functions/AIC_function.R') # runs AIC model selection
```

# Import the Data from the wrangled_data/ folder

```{r import}
sites_wrangled <- readRDS('wrangled_data/sites_wrangled.RDS')
neighbors_wrangled <- readRDS('wrangled_data/neighbors_wrangled.RDS')
webs_wrangled <- readRDS('wrangled_data/webs_wrangled.RDS')
```

# Not Used: One method of model selection

```{r unused}
# This is one way to look at the overall data, but ended up not using this information
models = list(WalkDist ~ 1,
              WalkDist ~ log_TotalSub, 
              WalkDist ~ log_tdr, 
              WalkDist ~ log_tdh,
              WalkDist ~ log_TotalSub + log_tdr,
              WalkDist ~ log_TotalSub + log_tdh,
              WalkDist ~ log_tdr + log_tdh,
              WalkDist ~ log_TotalSub + log_tdr + log_tdh)
fits = lapply(models, glm, data = sites_wrangled, family = "poisson")
modnames = sapply(models, function(ff)deparse(ff[[3]]))
pander(aictab(fits, modname = modnames), caption="AICc model selection table for Search Distance to the Focal Web Overall.", split.tables = Inf)
# The top model keeps all 3 variables and no other model is within 2 Model Likelihood Units
summary(glm(WalkDist ~ log_TotalSub + log_tdr + log_tdh, data = sites_wrangled, family = poisson))
```

# Results

```{r results}
aic_selection(y_var = "NumWebs", data = sites_wrangled)
aic_selection(y_var = "NumSpiders", data = sites_wrangled)
aic_selection(y_var = "round(RetreatDist, 0)", data = neighbors_wrangled)

# web height
#overall
global <- glmer.nb(round(RetreatHeight, 0) ~ log_TotalSub + log_tdr + log_tdh + (1 | ID), data = webs_wrangled)
options(na.action = "na.fail") # Required for dredge to run
model_dredge <- dredge(global, beta = "none", evaluate = TRUE, rank = AICc)
options(na.action = "na.omit") # set back to default
top_model <- get.models(model_dredge, subset = 1)[[1]]
summary(top_model)

r.squaredGLMM(top_model) # trigamma R2m
model.sel(model_dredge) #estimates same signs
summary(model.avg(model_dredge, subset = delta <= 2))
car::vif(get.models(model_dredge, 5)[[1]]) # looking for less than 2

# Urban Forest
webs_forest <- webs_wrangled %>% 
  filter(Location == "Urban Forest") %>% 
  mutate(tree100m_frac = I(tree100m/100))
global <- glmer.nb(round(RetreatHeight, 0) ~ tree100m_frac + log_TotalSub + log_tdr + log_tdh + log_patch + (1 | ID), data = webs_forest, control = glmerControl(optimizer = "bobyqa", optCtrl = list(maxfun = 2e4)))
options(na.action = "na.fail") # Required for dredge to run
model_dredge <- dredge(global, beta = "none", evaluate = TRUE, rank = AICc)
options(na.action = "na.omit") # set back to default
top_model <- get.models(model_dredge, subset = 1)[[1]]
summary(top_model)

r.squaredGLMM(top_model) #trigamma R2m
model.sel(model_dredge) #estimates same signs
summary(model.avg(model_dredge, subset = delta <= 2))
#car::vif(get.models(model_dredge, 1)[[1]]) # looking for less than 2

# Urban Center
webs_center <- webs_wrangled %>% 
  filter(Location == "Urban Center")
webs_center$road_length_m_sc <- scale(webs_center$road_length_m, center = FALSE)
global <- glmer.nb(round(RetreatHeight, 0) ~ log_TotalSub + log_tdr + log_tdh + scale(spec_rad, center = FALSE) + log_patch + road_length_m_sc + (1 | ID), data = webs_center)#, control = glmerControl(optimizer = "bobyqa", optCtrl = list(maxfun = 2e4)))
options(na.action = "na.fail") # Required for dredge to run
model_dredge <- dredge(global, beta = "none", evaluate = T, rank = AICc)
options(na.action = "na.omit") # set back to default
top_model <- get.models(model_dredge, subset = 1)[[1]]
summary(top_model)

r.squaredGLMM(top_model) 
model.sel(model_dredge) #estimates same signs
summary(model.avg(model_dredge, subset = delta <= 2))
#car::vif(get.models(model_dredge, 1)[[1]]) # looking for less than 2
```

### 2024-09-30 6_land_cover_posthoc_nb.Rmd
Organized code and wrote README.md file to help viewers interact with code

---
title: "Land cover effects on web abundance, aggregation, and position"
author: "Brandi Pessman"
date: "`r Sys.Date()`"
output: html_document
---
# Setting the Working Directory and Global Code Chunk Options

I have set message and warning to FALSE for every chunk so the knitted document does not include messages and warnings.

```{r setup}
knitr::opts_chunk$set(message = FALSE, warning = FALSE)
require("knitr")
opts_knit$set(root.dir = "/Users/bjpessman/Documents/phd_research_code/Agelenopsis_aggregation")
```

# Packages to Load

```{r packages}
library(MASS) # negative binomial tests
library(multcomp) # for pairwise comparisons of land cover categories
library(lme4) # to run the glmer function for the web distance (random effects)
```

# Import the Data from the wrangled_data/ folder

```{r import}
sites_wrangled <- readRDS('wrangled_data/sites_wrangled.RDS')
neighbors_wrangled <- readRDS('wrangled_data/neighbors_wrangled.RDS')
webs_wrangled <- readRDS('wrangled_data/webs_wrangled.RDS')
```

# Results of the negative binomial and post hoc analyses

```{r results}
# search distance
search_land.nb <- glm.nb(WalkDist ~ Land, data = sites_wrangled)
summary(search_land.nb)
car::Anova(search_land.nb, test.statistic = "LR")
comp <- glht(search_land.nb, linfct = mcp(Land = "Tukey"))
summary(comp)

# number of webs
webs_land_nb <- glm.nb(NumWebs ~ Land, data = sites_wrangled)
summary(webs_land_nb)
car::Anova(webs_land_nb, test.statistic = "LR")
comp <- glht(webs_land_nb, linfct = mcp(Land = "Tukey"))
summary(comp)

# number of spiders
spiders_land_nb <- glm.nb(NumSpiders ~ Land, data = sites_wrangled)
summary(spiders_land_nb)
car::Anova(spiders_land_nb, test.statistic = "LR")
comp <- glht(spiders_land_nb, linfct = mcp(Land = "Tukey"))
summary(comp)

# neighbor distances
dist_land_nb <- glm.nb(round(RetreatDist, 0) ~ Land, data = neighbors_wrangled)
summary(dist_land_nb)
car::Anova(dist_land_nb, test.statistic = "LR")
comp <- glht(dist_land_nb, linfct = mcp(Land = "Tukey"))
summary(comp)

# web height
height_land_nb <- glmer.nb(round(RetreatHeight, 0) ~ Land + (1 | ID), data = webs_wrangled)
summary(height_land_nb)
car::Anova(height_land_nb, type = 3)
comp <- glht(height_land_nb, linfct = mcp(Land = "Tukey"))
summary(comp)
```

### 2024-09-30 7_publication_figures.Rmd
Organized code and wrote README.md file to help viewers interact with code

---
title: "Figures for Publication"
author: "Brandi Pessman"
date: "`r Sys.Date()`"
output: html_document
editor_options: 
  markdown: 
    wrap: 72
---

# Set the Working Directory and Global Code Chunk Options

I have set message, warning, and echo to FALSE for every chunk so the knitted
document does not include messages, warnings, or code.

```{r setup, message = FALSE, warning = FALSE, echo = FALSE}
knitr::opts_chunk$set(message = FALSE, warning = FALSE, echo = FALSE)
require("knitr")
opts_knit$set(root.dir = "/Users/bjpessman/Documents/phd_research_code/Agelenopsis_aggregation")
```

# Packages Loaded

```{r packages}
library(tidyverse) # for making graphs
library(MASS) # negative binomial tests
library(lme4) # to run the glmer function for the web distance (random effects)
library(MuMIn) # to run the dredge function
library(broom) # allows us to use augment when getting predicted values from the model
library(broom.mixed) # for augment of the mixed effect models (web distance) to look at assumptions
library(ggpubr) # using ggarrange to make multi-panel figures
library(jpeg) # save pictures
library(gridExtra)
library(cowplot)
source('functions/get_predictions_function.R') #  get predictions for bootstrapping
```

# BigBoot Function

```{r  bootstrapping function}
BootFunc <- function(mm) {
    predict(mm, newdata = predictions, re.form = ~0, type = "response")
}
```

# Imported the Data from the wrangled_data/ folder

```{r import}
substrates <- read.table(file = "data/substrate.txt", header = TRUE)
sites_wrangled <- readRDS('wrangled_data/sites_wrangled.RDS')
neighbors_wrangled <- readRDS('wrangled_data/neighbors_wrangled.RDS')
webs_wrangled <- readRDS('wrangled_data/webs_wrangled.RDS')
```

# Figure 3

```{r figure 3}
# Search Distance
search.nb <- glm.nb(WalkDist ~ Location, data = sites_wrangled)
nd <- data.frame(Location = factor(levels(sites_wrangled$Location)))
predictions <- augment(search.nb, newdata = nd, se_fit = TRUE, type.predict = "response")
predictions <- predictions %>% 
  rename("rate" = ".fitted", "SE" = ".se.fit")
search_plot_nb <- ggplot(sites_wrangled, aes(x = Location, y = WalkDist)) + 
  geom_jitter(color = "grey", width = 0.1) +
  geom_point(aes(x = Location, y = rate, color = Location), size = 2, data = predictions) + 
  geom_errorbar(aes(x = Location, 
                  ymin = rate - SE, 
                  ymax = rate + SE,
                  color = Location), data = predictions, inherit.aes = FALSE, width = 0.15, size = 1) +
  scale_color_manual(values = c("Urban Center" = "#d95f02", "Urban Forest" = "#1b9e77")) +
  scale_x_discrete(labels=c("Urban Forest" = "Urban \nForest \nN = 10", "Urban Center" = "Urban \nCenter \nN = 12")) +
  theme_classic() +
  scale_y_continuous(limits = c(0, 275), breaks = c(0, 50, 100, 150, 200, 250)) +
  xlab("Collection Location") +
  ylab("Search Distance [m]") + 
  theme(text = element_text(size = 10)) + 
  theme(axis.text.x = element_text(colour = "black", size = 10)) + 
  theme(axis.text.y = element_text(colour = "black", size = 10),
        axis.title.x = element_blank()) +
  theme(legend.position = "none") +
  annotate(geom = "text", x = 1.5, y = 275, label = "N.S.", color = "black", size = 3)

# number of webs
web.nb <- glm.nb(NumWebs ~ Location, data = sites_wrangled)
nd <- data.frame(Location = factor(levels(sites_wrangled$Location)))
predictions <- augment(web.nb, newdata = nd, se_fit = TRUE, type.predict = "response")
predictions <- predictions %>% 
  rename("rate" = ".fitted", "SE" = ".se.fit")
webs_plot_nb <- ggplot(sites_wrangled, aes(x = Location, y = NumWebs)) + 
  geom_jitter(color = "grey", width = 0.1) +
  geom_point(aes(x = Location, y = rate, color = Location), size = 2, data = predictions) + 
  geom_errorbar(aes(x = Location, 
                  ymin = rate - SE, 
                  ymax = rate + SE,
                  color = Location), data = predictions, inherit.aes = FALSE, width = 0.15, size = 1) +
  scale_color_manual(values = c("Urban Center" = "#d95f02", "Urban Forest" = "#1b9e77")) +
  scale_x_discrete(labels=c("Urban Forest" = "Urban \nForest \nN = 10", "Urban Center" = "Urban \nCenter \nN = 12")) +
  theme_classic() +
    scale_y_continuous(limits = c(0, 75), breaks = c(0, 15, 30, 45, 60, 75)) +
  ylab("Number of Webs") + 
  theme(text = element_text(size = 10)) + 
  theme(axis.text.x = element_text(colour = "black", size = 10)) + 
  theme(axis.text.y = element_text(colour = "black", size = 10),
        axis.title.x = element_blank()) +
  theme(legend.position = "none") +
  annotate(geom = "text", x = 1.5, y = 75, label = "***", color = "black", size = 5)

# number of spiders
spiders.nb <- glm.nb(NumSpiders ~ Location, data = sites_wrangled)
nd <- data.frame(Location = factor(levels(sites_wrangled$Location)))
predictions <- augment(spiders.nb, newdata = nd, se_fit = TRUE, type.predict = "response")
predictions <- predictions %>% 
  rename("rate" = ".fitted", "SE" = ".se.fit")
#predictions <- summary(emmeans(spiders, ~Location),type = "response")

spiders_plot_nb <- ggplot(sites_wrangled, aes(x = Location, y = NumSpiders)) + 
  geom_jitter(color = "grey", width = 0.1) +
  geom_point(aes(x = Location, y = rate, color = Location), size = 2, data = predictions) + 
  geom_errorbar(aes(x = Location, 
                  ymin = rate - SE, 
                  ymax = rate + SE,
                  color = Location), data = predictions, inherit.aes = FALSE, width = 0.15, size = 1) +
  scale_color_manual(values = c("Urban Center" = "#d95f02", "Urban Forest" = "#1b9e77")) +
  scale_x_discrete(labels=c("Urban Forest" = "Urban \nForest \nN = 10", "Urban Center" = "Urban \nCenter \nN = 12")) +
  theme_classic() +
    scale_y_continuous(limits = c(0, 25), breaks = c(0, 5, 10, 15, 20, 25)) +
  ylab("Number of Spiders") + 
  theme(text = element_text(size = 10)) + 
  theme(axis.text.x = element_text(colour = "black", size = 10)) + 
  theme(axis.text.y = element_text(colour = "black", size = 10),
        axis.title.x = element_blank()) +
  theme(legend.position = "none") +
  annotate(geom = "text", x = 1.5, y = 25, label = "**", color = "black", size = 5)

# nearest neighbor distances
dist.nb <- glmer.nb(round(RetreatDist, 0) ~ Location * factor(Neighbor) + (1 | ID), data = neighbors_wrangled)
predictions <- expand.grid(Location = levels(factor(neighbors_wrangled$Location)), Neighbor = levels(factor(neighbors_wrangled$Neighbor)))
predictions$response <- predict(dist.nb, newdata = predictions, se.fit = TRUE, re.form = NA, type = "response")

bigBoot_dist_location_nb <- bootMer(dist.nb, BootFunc, nsim = 1000)
predSE <- t(apply(bigBoot_dist_location_nb$t, MARGIN = 2, FUN = sd, na.rm = TRUE))
predictions$SE <- predSE[1, ]
neighbor_plot_nb <- ggplot(neighbors_wrangled, aes(x = Neighbor, y = RetreatDist)) + 
  geom_jitter(aes(color = Location), alpha = 0.5, width = 0.1) +
    geom_line(aes(x = Neighbor, y = response, group = Location), size = 2, data = predictions, color = "grey") +
  geom_point(aes(x = Neighbor, y = response, color = Location), size = 2, data = predictions) + 
  geom_errorbar(aes(x = Neighbor, 
                  ymin = response - SE, 
                  ymax = response + SE,
                  color = Location), data = predictions, inherit.aes = FALSE, width = 0.15, size = 1) +
  scale_color_manual(values = c("Urban Center" = "#d95f02", "Urban Forest" = "#1b9e77")) +
  scale_x_discrete(labels=c("Urban Forest" = "Urban \nForest \nN = 10", "Urban Center" = "Urban \nCenter \nN = 12")) +
  theme_classic() +
  scale_y_continuous(limits = c(-50, 1050), breaks = c(0, 200, 400, 600, 800, 1000)) +
  xlab("Nearest Neighbors") +
  ylab("Distance from Focal Web \nto Neighbor Web [cm]") + 
  theme(text = element_text(size = 10)) + 
  theme(axis.text.x = element_text(colour = "black", size = 10)) + 
  theme(axis.text.y = element_text(colour = "black", size = 10)) +
  theme(legend.position = "none")

# web height
height.nb <- glmer.nb(round(RetreatHeight, 0) ~ Location + (1 | ID), data = webs_wrangled)
predictions <- expand.grid(Location = levels(factor(webs_wrangled$Location)))
predictions$response <- predict(height.nb, newdata = predictions, se.fit = TRUE, re.form = NA, type = "response")
bigBoot_height_location_nb <- bootMer(height.nb, BootFunc, nsim = 1000)
predSE <- t(apply(bigBoot_height_location_nb$t, MARGIN = 2, FUN = sd))
predictions$SE <- predSE[1, ]
height_plot_nb <- ggplot(webs_wrangled, aes(x = Location, y = RetreatHeight)) + 
  geom_jitter(color = "grey", width = 0.1) +
  geom_point(aes(x = Location, y = response, color = Location), size = 2, data = predictions) +
  geom_errorbar(aes(x= Location, 
                    ymin = response - SE, 
                    ymax = response + SE, 
                    color = Location), data = predictions, inherit.aes = FALSE, width = 0.15, size = 1) +
    scale_color_manual(values = c("Urban Center" = "#d95f02", "Urban Forest" = "#1b9e77")) +
    scale_x_discrete(labels=c("Urban Forest" = "Urban \nForest \nN = 30", "Urban Center" = "Urban \nCenter \nN = 101")) +
    theme_classic() +
    scale_y_continuous(limits = c(0, 210), breaks = c(0, 35, 70, 105, 140, 175, 210)) +
    ylab("Web Height [cm]") + 
    theme(text = element_text(size = 10)) + 
    theme(axis.text.x = element_text(colour = "black", size = 10)) + 
    theme(axis.text.y = element_text(colour = "black", size = 10),
        axis.title.x = element_blank()) +
    theme(legend.position = "none") +
    annotate(geom = "text", x = 1.5, y = 210, label = "*", color = "black", size = 5)

blankPlot <- ggplot() + 
  geom_blank(aes(1,1)) + 
  cowplot::theme_nothing()

main_row1 <- ggarrange(webs_plot_nb, spiders_plot_nb, blankPlot, labels = c("a", "b", ""), nrow = 1, font.label = list(size = 10))
main_row2 <- ggarrange(search_plot_nb, neighbor_plot_nb, height_plot_nb, labels = c("c", "d", "e"), nrow = 1, font.label = list(size = 10))

main <- ggarrange(main_row1, main_row2, nrow = 2, font.label = list(size = 10))
main
jpeg(filename = "figures/figure3.jpeg", units = "cm", width = 17.4, height = 17.4, res = 300)
print(main)
dev.off()
```

**Fig. 3** Comparison of the number of webs (a) and spiders (b) in a 10-m radius of the focal web, search distance (c), the distance from the focal web to the first and second (d) nearest neighbors, and web height (e) by habitat—urban center vs. urban forest. Grey jittered points (and faded colored points by habitat in d) represent the raw data, while colored points (orange = urban center, green = urban forest) and error bars represent the mean and standard error, respectively, from model predictions. Models were either negative binomial generalized linear models (a–c) or negative binomial generalized linear mixed effect models with site as a random factor (d–e). Asterisks indicate significance level (\*\*\* P \< 0.001; \*\* P \< 0.01; \* P \< 0.05, N.S. = not significant). We found more webs (a) and spiders (b) in a 10-m radius of the focal web in the urban center than the urban forest. Search distance did not differ between habitats (c), but we measured shorter distances between the focal web and the two nearest neighbors (d), and recorded shorter web heights (e) in the urban center than the urban forest.

# Figure 4

```{r figure 4 webs}
colorc = "#d95f02" 
colorf = "#1b9e77"
coloro = "black"

# number of webs
global <- glm.nb(NumWebs ~ log_TotalSub + log_tdr + log_tdh, data = sites_wrangled)
options(na.action = "na.fail") 
model_dredge <- dredge(global, beta = "none", evaluate = T, rank = AICc)
options(na.action = "na.omit") 
top_model_webs_o <- get.models(model_dredge, subset = 1)[[1]]
nd <- data.frame(log_TotalSub = seq(0, 3.2, 0.03), 
                 log_tdh = mean(sites_wrangled$log_tdh))
predicted.distance <- augment(top_model_webs_o, 
                              newdata = nd, 
                              se_fit = TRUE)
webs_plant <- ggplot(sites_wrangled, aes(x = log_TotalSub, y = log(NumWebs))) + 
  geom_point(aes(color = Location), alpha = 0.7,  
             size = 1) +
  geom_line(aes(x = log_TotalSub, y = .fitted), 
            size = 1, 
            color = coloro, 
            data = predicted.distance) + 
  geom_ribbon(aes(x = log_TotalSub, 
                  ymin = .fitted - 1.96 * .se.fit, 
                  ymax = .fitted + 1.96 * .se.fit), 
              fill = coloro, 
              data = predicted.distance, 
              inherit.aes = FALSE, 
              alpha = 0.25) +
  scale_y_continuous(limits = c(-2, 5), breaks = c(-2, 0, 2, 4)) +  
  scale_color_manual(values = c("Urban Center" = "#d95f02", "Urban Forest" = "#1b9e77")) +
  theme_classic() +
  xlab("Plant Species Richness [ln()]") +
  ylab("Number of Webs [ln()]") + 
  theme(text = element_text(size = 10)) + 
  theme(axis.text.x = element_text(colour = "black", size = 10)) + 
  theme(axis.text.y = element_text(colour = "black", size = 10)) +
  theme(axis.title.x = element_blank(), 
        axis.title.y = element_blank(),
        legend.position = "none") + 
  annotate(geom = "text", x = min(predicted.distance$log_TotalSub) + diff(range(predicted.distance$log_TotalSub))/2, y = 4.8, label = "***", color = "black", size = 4)
```

```{r figure 4 spiders}
# number of spiders
global <- glm.nb(NumSpiders ~ log_TotalSub + log_tdr + log_tdh, data = sites_wrangled)
options(na.action = "na.fail")
model_dredge <- dredge(global, beta = "none", evaluate = T, rank = AICc)
options(na.action = "na.omit") 
top_model_spiders_o <- get.models(model_dredge, subset = 1)[[1]]
nd <- data.frame(log_TotalSub = seq(0, 3.2, 0.03), 
                 log_tdh = mean(sites_wrangled$log_tdh))
predicted.distance <- augment(top_model_spiders_o, 
                              newdata = nd, 
                              se_fit = TRUE)
spiders_plant <- ggplot(sites_wrangled, aes(x = log_TotalSub, y = log(NumSpiders))) + 
  geom_point(aes(color = Location), alpha = 0.7, 
             size = 1) +
  geom_line(aes(x = log_TotalSub, y = .fitted), 
            size = 1, 
            color = coloro, 
            data = predicted.distance) + 
  geom_ribbon(aes(x = log_TotalSub, 
                  ymin = .fitted - 1.96 * .se.fit, 
                  ymax = .fitted + 1.96 * .se.fit), 
              fill = coloro, 
              data = predicted.distance, 
              inherit.aes = FALSE, 
              alpha = 0.25) +
  scale_y_continuous(limits = c(-2, 5), breaks = c(-2, 0, 2, 4)) +  
  scale_color_manual(values = c("Urban Center" = "#d95f02", "Urban Forest" = "#1b9e77")) +
  theme_classic() +
  xlab("Plant Species Richness [ln()]") +
  ylab("Number of Spiders [ln()]") + 
  theme(text = element_text(size = 10)) + 
  theme(axis.text.x = element_text(colour = "black", size = 10)) + 
  theme(axis.text.y = element_text(colour = "black", size = 10)) +
  theme(axis.title.x = element_blank(), 
        axis.title.y = element_blank(),
        legend.position = "none") + 
    annotate(geom = "text", x = min(predicted.distance$log_TotalSub) + diff(range(predicted.distance$log_TotalSub))/2, y = 5, label = "***", color = "black", size = 4)
```

```{r figure 4 neighbor}
# nearest neighbor distances
nearest <- neighbors_wrangled %>% 
  filter(Web == "W002")
global <- glm.nb(round(RetreatDist, 0) ~ log_TotalSub + log_tdr + log_tdh, data = nearest)
options(na.action = "na.fail") 
model_dredge <- dredge(global, beta = "none", evaluate = T, rank = AICc)
options(na.action = "na.omit") 
top_model_neighbor_o <- get.models(model_dredge, subset = 1)[[1]]
nd <- data.frame(log_TotalSub = seq(0, 3.2, 0.03))
predicted.distance <- augment(top_model_neighbor_o, 
                              newdata = nd, 
                              se_fit = TRUE)
dist_plant <- ggplot(nearest, aes(x = log_TotalSub, y = log(RetreatDist))) + 
  geom_point(aes(color = Location), alpha = 0.7, 
             size = 1) +
  geom_line(aes(x = log_TotalSub, y = .fitted), 
            size = 1, 
            color = coloro, 
            data = predicted.distance) + 
  geom_ribbon(aes(x = log_TotalSub, 
                  ymin = .fitted - 1.96 * .se.fit, 
                  ymax = .fitted + 1.96 * .se.fit), 
              fill = coloro, 
              data = predicted.distance, 
              inherit.aes = FALSE, 
              alpha = 0.25) +
  scale_y_continuous(limits = c(2, 7.3), breaks = c(2, 3, 4, 5, 6, 7)) +  
  scale_color_manual(values = c("Urban Center" = "#d95f02", "Urban Forest" = "#1b9e77")) +
  theme_classic() +
  xlab("Plant Species Richness [ln()]") +
  ylab("Distance from Focal Web \nto Neighbor Web [ln(cm)]") + 
  theme(text = element_text(size = 10)) + 
  theme(axis.text.x = element_text(colour = "black", size = 10)) + 
  theme(axis.text.y = element_text(colour = "black", size = 10)) +
  theme(axis.title.x = element_blank(), 
        axis.title.y = element_blank(),
        legend.position = "none") +
  annotate(geom = "text", x = min(predicted.distance$log_TotalSub) + diff(range(predicted.distance$log_TotalSub))/2, y = 7, label = "**", color = "black", size = 4)
```

```{r figure 4 height}
# web height
global <- glmer.nb(round(RetreatHeight, 0) ~ log_TotalSub + log_tdr + log_tdh + (1 | ID), data = webs_wrangled)
options(na.action = "na.fail") 
model_dredge <- dredge(global, beta = "none", evaluate = TRUE, rank = AICc)
options(na.action = "na.omit") 
top_model_height_o <- get.models(model_dredge, subset = 1)[[1]]
predictions <- expand.grid(log_TotalSub = seq(0, 3.15, 0.03),
                           log_tdr = mean(webs_wrangled$log_tdr))
predictions$response <- predict(top_model_height_o, newdata = predictions, se.fit = TRUE, re.form = NA, type = "response")
bigBoot_height_overall_plant_nb <- bootMer(top_model_height_o, BootFunc, nsim = 1000)
predSE <- t(apply(bigBoot_height_overall_plant_nb$t, MARGIN = 2, FUN = sd))
predictions$SE <- predSE[1, ]
height_plant <- ggplot(webs_wrangled, aes(x = log_TotalSub, y = log(RetreatHeight))) + 
  geom_point(aes(color = Location), alpha = 0.7, 
             size = 1) +
  geom_line(aes(x = log_TotalSub, y = log(response)), 
            size = 1, 
            color = coloro, 
            data = predictions) + 
  geom_ribbon(aes(x = log_TotalSub, 
                  ymin = log(response - 1.96 * SE), 
                  ymax = log(response + 1.96 * SE)), 
              fill = coloro, 
              data = predictions, 
              inherit.aes = FALSE, 
              alpha = 0.25) +
  scale_y_continuous(limits = c(-2.5, 6), breaks = c(-2, 0, 2, 4, 6)) + 
  scale_color_manual(values = c("Urban Center" = "#d95f02", "Urban Forest" = "#1b9e77")) +
  theme_classic() +
  xlab("Plant Species Richness [ln()]") +
  ylab("Web Height [ln(cm)]") + 
  theme(text = element_text(size = 10)) + 
  theme(axis.text.x = element_text(colour = "black", size = 10)) + 
  theme(axis.text.y = element_text(colour = "black", size = 10)) +
  theme(axis.title.x = element_blank(), 
        axis.title.y = element_blank(),
        legend.position = "none") + 
    annotate(geom = "text", x = min(predictions$log_TotalSub) + diff(range(predictions$log_TotalSub))/2, y = 5.8, label = "**", color = "black", size = 4)
```

```{r figure 4 panel}
webs_text <- as_ggplot(text_grob(paste("Number of \nWebs \n[ln()]"), size = 10))
spiders_text <- as_ggplot(text_grob(paste("Number of \nSpiders \n[ln()]"), size = 10))
dist_text <- as_ggplot(text_grob(paste("Nearest \nNeighbor \nDist. [ln(cm)]"), size = 10))
height_text <- as_ggplot(text_grob(paste("Web \nHeight \n[ln(cm)]"), size = 10))
plant_text <- as_ggplot(text_grob(paste("Plant Species Richness [ln()]"), size = 10))
blankPlot <- ggplot()+geom_blank(aes(1,1)) + 
  cowplot::theme_nothing()

pred_plant <- ggarrange(webs_text, webs_plant, 
                spiders_text, spiders_plant, 
                dist_text, dist_plant, 
                height_text, height_plant,
                blankPlot, plant_text,
                ncol = 2, nrow = 5, 
                widths = c(0.3, 0.7), 
                heights = c(0.24, 0.24, 0.24, 0.24, 0.04))

jpeg(filename = "figures/figure4.jpeg", units = "cm", width = 8.4, height = 17.4, res = 300)
print(pred_plant)
dev.off()
pred_plant
```

**Fig. 4** Significant correlations between measures of abundance, aggregation, and position, and plant species richness for the overall data. The regression lines and shaded regions represent the predictions and 95% confidence intervals (respectively) from the top negative binomial generalized linear model after AIC selection. The points represent the raw data (orange = urban center, green = urban forest). Asterisks indicate significance level (*** P < 0.001; ** P < 0.01; * P < 0.05).

# Figure 5

```{r figure 5 webs}
sites_center <- sites_wrangled %>% 
  filter(Location == "Urban Center")
# number of webs
global <- glm.nb(NumWebs ~ log_TotalSub + log_tdr + log_tdh + spec_rad + log_patch + road_length_m, data = sites_center)
options(na.action = "na.fail") 
model_dredge <- dredge(global, beta = "none", evaluate = T, rank = AICc)
options(na.action = "na.omit") 
top_model_webs_c <- get.models(model_dredge, subset = 1)[[1]]
nd <- data.frame(log_tdh = seq(3.32, 5.42, 0.02))
predicted.distance <- augment(top_model_webs_c, 
                              newdata = nd, 
                              se_fit = TRUE)
webs_center_tdh <- ggplot(sites_wrangled, aes(x = log_tdh, y = log(NumWebs))) + 
  geom_point(aes(color = Location), alpha = 0.5, 
             size = 1) +
  geom_line(aes(x = log_tdh, y = .fitted), 
            size = 1, 
            color = colorc, 
            data = predicted.distance) + 
  geom_ribbon(aes(x = log_tdh, 
                  ymin = .fitted - 1.96 * .se.fit, 
                  ymax = .fitted + 1.96 * .se.fit), 
              fill = colorc, 
              data = predicted.distance, 
              inherit.aes = FALSE, 
              alpha = 0.25) +
  scale_y_continuous(limits = c(-2, 5), breaks = c(-2, 0, 2, 4)) +  
  scale_x_continuous(breaks = c(3, 4, 5)) +  
  scale_color_manual(values = c("Urban Center" = "#d95f02", "Urban Forest" = "#1b9e77")) +
  theme_classic() +
  xlab("Highway Disturbance [ln(vehicles/day/m)]") +
  ylab("Number of Webs [ln()]") + 
  theme(text = element_text(size = 10)) + 
  theme(axis.text.x = element_text(colour = "black", size = 10)) + 
  theme(axis.text.y = element_text(colour = "black", size = 10)) +
  theme(axis.title.x = element_blank(), 
        axis.title.y = element_blank(),
        legend.position = "none") + 
  annotate(geom = "text", x = 4, y = 5, label = "*", color = "black", size = 4) 
nd <- data.frame(log_TotalSub = mean(sites_wrangled$log_TotalSub), 
                 log_tdh = seq(2.7, 5.5, 0.03))
predicted.distance <- augment(top_model_webs_o, 
                              newdata = nd, 
                              se_fit = TRUE)
webs_tdh <- ggplot(sites_wrangled, aes(x = log_tdh, y = log(NumWebs))) + 
  geom_point(aes(color = Location), alpha = 0.7, 
             size = 1) +
  geom_line(aes(x = log_tdh, y = .fitted), 
            size = 1, 
            color = coloro, 
            data = predicted.distance) + 
  geom_ribbon(aes(x = log_tdh, 
                  ymin = .fitted - 1.96 * .se.fit, 
                  ymax = .fitted + 1.96 * .se.fit), 
              fill = coloro, 
              data = predicted.distance, 
              inherit.aes = FALSE, 
              alpha = 0.25) +
  scale_y_continuous(limits = c(-2, 5), breaks = c(-2, 0, 2, 4)) +  
  scale_x_continuous(breaks = c(3, 4, 5)) +  
  scale_color_manual(values = c("Urban Center" = "#d95f02", "Urban Forest" = "#1b9e77")) +
  theme_classic() +
  xlab("Highway Disturbance [ln(vehicles/day/m)]") +
  ylab("Number of Webs [ln()]") + 
  theme(text = element_text(size = 10)) + 
  theme(axis.text.x = element_text(colour = "black", size = 10)) + 
  theme(axis.text.y = element_text(colour = "black", size = 10)) +
  theme(axis.title.x = element_blank(), 
        axis.title.y = element_blank(), 
        legend.position = "none") + 
  annotate(geom = "text", x = min((predicted.distance$log_tdh)) + diff(range((predicted.distance$log_tdh)))/2, y = 4.8, label = "**", color = "black", size = 4)
```

```{r figure 5 spiders}
# number of spiders
global <- glm.nb(NumSpiders ~ log_TotalSub + log_tdr + log_tdh + spec_rad + log_patch + road_length_m, data = sites_center)
options(na.action = "na.fail") 
model_dredge <- dredge(global, beta = "none", evaluate = T, rank = AICc)
options(na.action = "na.omit")
top_model_spiders_c <- get.models(model_dredge, subset = 1)[[1]]
nd <- data.frame(log_tdh = seq(3.32, 5.42, 0.02))
predicted.distance <- augment(top_model_spiders_c, 
                              newdata = nd, 
                              se_fit = TRUE)
spiders_center_tdh <- ggplot(sites_wrangled, aes(x = log_tdh, y = log(NumSpiders))) + 
  geom_point(aes(color = Location), alpha = 0.5, 
             size = 1) +
  geom_line(aes(x = log_tdh, y = .fitted), 
            size = 1, 
            color = colorc, 
            data = predicted.distance) + 
  geom_ribbon(aes(x = log_tdh, 
                  ymin = .fitted - 1.96 * .se.fit, 
                  ymax = .fitted + 1.96 * .se.fit), 
              fill = colorc, 
              data = predicted.distance, 
              inherit.aes = FALSE, 
              alpha = 0.25) +
  scale_y_continuous(limits = c(-2, 5), breaks = c(-2, 0, 2, 4)) +  
  scale_x_continuous(breaks = c(3, 4, 5)) +  
  scale_color_manual(values = c("Urban Center" = "#d95f02", "Urban Forest" = "#1b9e77")) +
  theme_classic() +
  xlab("Highway Disturbance [ln(vehicles/day/m)]") +
  ylab("Number of Spiders [ln()]") + 
  theme(text = element_text(size = 10)) + 
  theme(axis.text.x = element_text(colour = "black", size = 10)) + 
  theme(axis.text.y = element_text(colour = "black", size = 10)) +
  theme(axis.title.x = element_blank(), 
        axis.title.y = element_blank(),
        legend.position = "none") + 
  annotate(geom = "text", x = 4, y = 5, label = "*", color = "black", size = 4) 
nd <- data.frame(log_TotalSub = mean(sites_wrangled$log_TotalSub), 
                 log_tdh = seq(2.7, 5.5, 0.03))
predicted.distance <- augment(top_model_spiders_o, 
                              newdata = nd, 
                              se_fit = TRUE)
spiders_tdh <- ggplot(sites_wrangled, aes(x = log_tdh, y = log(NumSpiders))) + 
  geom_point(aes(color = Location), alpha = 0.7, 
             size = 1) +
  geom_line(aes(x = log_tdh, y = .fitted), 
            size = 1, 
            color = coloro, 
            data = predicted.distance) + 
  geom_ribbon(aes(x = log_tdh, 
                  ymin = .fitted - 1.96 * .se.fit, 
                  ymax = .fitted + 1.96 * .se.fit), 
              fill = coloro, 
              data = predicted.distance, 
              inherit.aes = FALSE, 
              alpha = 0.25) +
  scale_y_continuous(limits = c(-2, 5), breaks = c(-2, 0, 2, 4)) +  
  scale_x_continuous(breaks = c(3, 4, 5)) +  
  scale_color_manual(values = c("Urban Center" = "#d95f02", "Urban Forest" = "#1b9e77")) +
  theme_classic() +
  xlab("Highway Disturbance [ln(vehicles/day/m)]") +
  ylab("Number of Spiders [ln()]") + 
  theme(text = element_text(size = 10)) + 
  theme(axis.text.x = element_text(colour = "black", size = 10)) + 
  theme(axis.text.y = element_text(colour = "black", size = 10)) +
  theme(axis.title.x = element_blank(), 
        axis.title.y = element_blank(), 
        legend.position = "none") + 
  annotate(geom = "text", x = min((predicted.distance$log_tdh)) + diff(range((predicted.distance$log_tdh)))/2, y = 5, label = "*", color = "black", size = 4)
```

```{r figure 5 neighbor}
# nearest neighbor distance 
near_center <- nearest %>% 
  filter(Location == "Urban Center")
global <- glm.nb(round(RetreatDist, 0) ~ log_TotalSub + log_tdr + log_tdh + spec_rad + log_patch + road_length_m, data = near_center)
options(na.action = "na.fail") 
model_dredge <- dredge(global, beta = "none", evaluate = T, rank = AICc)
options(na.action = "na.omit") 
top_model_neighbor_c <- get.models(model_dredge, subset = 1)[[1]]
nd <- data.frame(road_length_m = seq(47, 117, 0.6))
predicted.distance <- augment(top_model_neighbor_c, 
                              newdata = nd, 
                              se_fit = TRUE)
dist_center_road <- ggplot(neighbors_wrangled, aes(x = (road_length_m), y = log(RetreatDist))) + 
  geom_point(aes(color = Location), alpha = 0.5, 
             size = 1) +
  geom_line(aes(x = (road_length_m), y = (.fitted)), 
            size = 1, 
            color = colorc, 
            data = predicted.distance) + 
  geom_ribbon(aes(x = (road_length_m), 
                  ymin = .fitted - 1.96 * .se.fit, 
                  ymax = .fitted + 1.96 * .se.fit), 
              fill = colorc, 
              data = predicted.distance, 
              inherit.aes = FALSE, 
              alpha = 0.25) +
  scale_y_continuous(limits = c(2, 7), breaks = c(2, 3, 4, 5, 6, 7)) +  
  scale_color_manual(values = c("Urban Center" = "#d95f02", "Urban Forest" = "#1b9e77")) +
  theme_classic() +
  xlab("Total Road Length [m]") +
  ylab("Distance from Focal Web \nto Neighbor Web [ln(cm)]") + 
  theme(text = element_text(size = 10)) + 
  theme(axis.text.x = element_text(colour = "black", size = 10)) + 
  theme(axis.text.y = element_text(colour = "black", size = 10)) +
  theme(axis.title.x = element_blank(), 
        axis.title.y = element_blank(), 
        legend.position = "none") + 
  annotate(geom = "text", x = 55, y = 6.8, label = "*", color = "black", size = 4)
```

```{r figure 5 height}
# web height
webs_wrangled$road_length_m_sc <- scale(webs_wrangled$road_length_m, center = FALSE)
webs_center <- webs_wrangled %>% 
  filter(Location == "Urban Center")
global <- glmer.nb(round(RetreatHeight, 0) ~ log_TotalSub + log_tdr + log_tdh + scale(spec_rad, center = FALSE) + log_patch + road_length_m_sc + (1 | ID), data = webs_center)#, control = glmerControl(optimizer = "bobyqa", optCtrl = list(maxfun = 2e4)))
options(na.action = "na.fail") # Required for dredge to run
model_dredge <- dredge(global, beta = "none", evaluate = T, rank = AICc)
options(na.action = "na.omit") # set back to default
top_model_height_c <- get.models(model_dredge, subset = 1)[[1]]
predictions <- expand.grid(log_TotalSub = mean(webs_center$log_TotalSub),
                           road_length_m_sc = seq(0.5, 1.50, 0.01))
predictions$response <- predict(top_model_height_c, newdata = predictions, se.fit = TRUE, re.form = NA, type = "response")
bigBoot_height_center_road_nb <- bootMer(top_model_height_c, BootFunc, nsim = 1000)
predSE <- t(apply(bigBoot_height_center_road_nb$t, MARGIN = 2, FUN = sd))
predictions$SE <- predSE[1, ]
height_center_road <- ggplot(webs_wrangled, aes(x = road_length_m_sc, y = log(RetreatHeight))) + 
  geom_point(aes(color = Location), alpha = 0.5, 
             size = 1) +
  geom_line(aes(x = road_length_m_sc, y = log(response)), 
            size = 1, 
            color = colorc, 
            data = predictions) + 
  geom_ribbon(aes(x = road_length_m_sc, 
                  ymin = log(response - 1.96 * SE), 
                  ymax = log(response + 1.96 * SE)), 
              fill = colorc, 
              data = predictions, 
              inherit.aes = FALSE, 
              alpha = 0.25) +
  scale_y_continuous(limits = c(-2.5, 6), breaks = c(-2, 0, 2, 4, 6)) +  
  scale_color_manual(values = c("Urban Center" = "#d95f02", "Urban Forest" = "#1b9e77")) +  theme_classic() +
  xlab("Plant Species Richness [ln()]") +
  ylab("Web Height [ln(cm)]") + 
  theme(text = element_text(size = 10)) + 
  theme(axis.text.x = element_text(colour = "black", size = 10)) + 
  theme(axis.text.y = element_text(colour = "black", size = 10)) +
  theme(axis.title.x = element_blank(), 
        axis.title.y = element_blank(),
        legend.position = "none") + 
  annotate(geom = "text", x = 0.9, y = 5.8, label = "N.S.", color = "black", size = 3)

predictions <- expand.grid(log_TotalSub = mean(webs_wrangled$log_TotalSub),
                           log_tdr = seq(2.73, 7.22, 0.05))
predictions$response <- predict(top_model_height_o, newdata = predictions, se.fit = TRUE, re.form = NA, type = "response")
bigBoot_height_overall_tdr_nb <- bootMer(top_model_height_o, BootFunc, nsim = 1000)
predSE <- t(apply(bigBoot_height_overall_tdr_nb$t, MARGIN = 2, FUN = sd))
predictions$SE <- predSE[1, ]
height_tdr <- ggplot(webs_wrangled, aes(x = log_tdr, y = log(RetreatHeight))) + 
  geom_point(aes(color = Location), alpha = 0.7, 
             size = 1) +
  geom_line(aes(x = log_tdr, y = log(response)), 
            size = 1, 
            color = coloro, 
            data = predictions) + 
  geom_ribbon(aes(x = log_tdr, 
                  ymin = log(response - 1.96 * SE), 
                  ymax = log(response + 1.96 * SE)), 
              fill = coloro, 
              data = predictions, 
              inherit.aes = FALSE, 
              alpha = 0.25) +
  scale_y_continuous(limits = c(-2.5, 6), breaks = c(-2, 0, 2, 4, 6)) +  
  scale_color_manual(values = c("Urban Center" = "#d95f02", "Urban Forest" = "#1b9e77")) +
  theme_classic() +
  xlab("Road Disturbance [ln(vehicles/day/m)]") +
  ylab("Web Height [ln(cm)]") + 
  theme(text = element_text(size = 10)) + 
  theme(axis.text.x = element_text(colour = "black", size = 10)) + 
  theme(axis.text.y = element_text(colour = "black", size = 10)) +
  theme(axis.title.x = element_blank(), 
        axis.title.y = element_blank(), 
        legend.position = "none") + 
    annotate(geom = "text", x = min(predictions$log_tdr) + diff(range(predictions$log_tdr))/2, y = 5.8, label = "N. S.", color = "black", size = 3)
```

```{r figure 5 panel}
webs_text <- as_ggplot(text_grob(paste("Number of \nWebs \n[ln()]"), size = 10))
spiders_text <- as_ggplot(text_grob(paste("Number of \nSpiders \n[ln()]"), size = 10))
dist_text <- as_ggplot(text_grob(paste("Nearest \nNeighbor \nDist. [ln(cm)]"), size = 10))
height_text <- as_ggplot(text_grob(paste("Web \nHeight \n[ln(cm)]"), size = 10))
tdr_text <- as_ggplot(text_grob(paste("Road-Traffic \nImpact \n[ln(cars/day/m)]"), size = 10))
tdh_text <- as_ggplot(text_grob(paste("Highway-Traffic \nImpact \n[ln(cars/day/m)]"), size = 10))
road_text <- as_ggplot(text_grob(paste("Road \nLength [m]"), size = 10))
overall_text <- as_ggplot(text_grob(paste("Overall"), size = 10))
center_text <- as_ggplot(text_grob(paste("Urban Center Subset"), size = 10))
blankPlot <- ggplot()+geom_blank(aes(1,1)) + 
  cowplot::theme_nothing() 
greyPlot <- ggplot()+geom_blank(aes(1,1)) + 
  cowplot::theme_nothing() +
  theme(panel.background = element_rect(fill = "grey", color = "white"))

pred_traffic <- ggarrange(webs_text, greyPlot, webs_tdh, blankPlot, webs_center_tdh, greyPlot,
                spiders_text, greyPlot, spiders_tdh, blankPlot, spiders_center_tdh, greyPlot, 
                dist_text, greyPlot, greyPlot, blankPlot, greyPlot, dist_center_road, 
                height_text, height_tdr, greyPlot, blankPlot, greyPlot, height_center_road,
                blankPlot, tdr_text, tdh_text, blankPlot, tdh_text, road_text,
                ncol = 6, nrow = 5, 
                widths = c(0.16, 0.20, 0.20, 0.04, 0.20, 0.20), 
                heights = c(0.22, 0.22, 0.22, 0.22, 0.12))

jpeg(filename = "figures/figure5.jpeg", units = "cm", width = 17.4, height = 17.4, res = 300)
print(pred_traffic)
dev.off()
pred_traffic
```

**Fig. 5** Significant correlations between abundance, aggregation, and position measures and the environmental predictors relating to traffic impacts for the data overall (black outline) and the urban center subset (orange outline). Grey boxes represent environmental predictors that were dropped from models after AIC model selection. The regression lines and shaded regions represent the predictions and 95% confidence intervals (respectively) from the top negative binomial generalized linear model after AIC selection. The points represent the raw data (orange = urban center, green = urban forest). Road length for web height was scaled without centering. Asterisks indicate significance level (*** P < 0.001; ** P < 0.01; * P < 0.05, N. S. = not significant).

# Figure S11

```{r figure s11 search}
search_land.nb <- glm.nb(WalkDist ~ Land, data = sites_wrangled)
nd <- data.frame(Land = factor(levels(sites_wrangled$Land)))
predictions <- augment(search_land.nb, newdata = nd, se_fit = TRUE, type.predict = "response")
predictions <- predictions %>% 
  rename("rate" = ".fitted", "SE" = ".se.fit")
search_land_plot <- ggplot(sites_wrangled, aes(x = Land, y = WalkDist)) + 
  geom_jitter(color = "grey", width = 0.1, size = 0.5) +
  geom_point(aes(x = Land, y = rate, color = Land), size = 2, data = predictions) + 
  geom_errorbar(aes(x = Land, 
                  ymin = rate - SE, 
                  ymax = rate + SE, color = Land), data = predictions, inherit.aes = FALSE, width = 0.25, size = 1) +
  theme_classic() +
  scale_color_manual(values = c("Deciduous Forest" = "#1b9e77", "Woody Wetlands" = "#1b9e77", "Urban, High" = "#d95f02", "Urban, Medium" = "#d95f02", "Urban, Low" = "#d95f02")) +
  xlab("Land Cover Class") +
  ylab("Search Distance [m]") + 
  theme(text = element_text(size = 10)) + 
  theme(axis.text.x=element_text(colour="black", size=10)) + 
  theme(axis.text.y=element_text(colour="black", size=10)) +
  theme(legend.position = "none") +
  theme(axis.text.x = element_text(angle = 90, vjust = 1, hjust=1))
```

```{r figure s11 webs}
webs_land_nb <- glm.nb(NumWebs ~ Land, data = sites_wrangled)
nd <- data.frame(Land = factor(levels(sites_wrangled$Land)))
predictions <- augment(webs_land_nb, newdata = nd, se_fit = TRUE, type.predict = "response")
predictions <- predictions %>% 
  rename("rate" = ".fitted", "SE" = ".se.fit")
webs_land_plot <- ggplot(sites_wrangled, aes(x = Land, y = NumWebs)) + 
  geom_jitter(color = "grey", width = 0.1, size = 0.5) +
  geom_point(aes(x = Land, y = rate, color = Land), size = 2, data = predictions) + 
  geom_errorbar(aes(x = Land, 
                  ymin = rate - SE, 
                  ymax = rate + SE, color = Land), data = predictions, inherit.aes = FALSE, width = 0.25, size = 1) +
  theme_classic() +
  scale_color_manual(values = c("Deciduous Forest" = "#1b9e77", "Woody Wetlands" = "#1b9e77", "Urban, High" = "#d95f02", "Urban, Medium" = "#d95f02", "Urban, Low" = "#d95f02")) +
  xlab("Land Cover Class") +
  ylab("Number of Webs") + 
  theme(text = element_text(size = 10)) + 
  theme(axis.text.x=element_text(colour="black", size=10)) + 
  theme(axis.text.y=element_text(colour="black", size=10)) +
  theme(legend.position = "none") +
  theme(axis.text.x = element_text(angle = 90, vjust = 1, hjust=1))
```

```{r figure s11 spiders}
spiders_land_nb <- glm.nb(NumSpiders ~ Land, data = sites_wrangled)
nd <- data.frame(Land = factor(levels(sites_wrangled$Land)))
predictions <- augment(spiders_land_nb, newdata = nd, se_fit = TRUE, type.predict = "response")
predictions <- predictions %>% 
  rename("rate" = ".fitted", "SE" = ".se.fit")
spiders_land_plot <- ggplot(sites_wrangled, aes(x = Land, y = NumSpiders)) + 
  geom_jitter(color = "grey", width = 0.1, size = 0.5) +
  geom_point(aes(x = Land, y = rate, color = Land), size = 2, data = predictions) + 
  geom_errorbar(aes(x = Land, 
                  ymin = rate - SE, 
                  ymax = rate + SE, color = Land), data = predictions, inherit.aes = FALSE, width = 0.25, size = 1) +
  theme_classic() +
  scale_color_manual(values = c("Deciduous Forest" = "#1b9e77", "Woody Wetlands" = "#1b9e77", "Urban, High" = "#d95f02", "Urban, Medium" = "#d95f02", "Urban, Low" = "#d95f02")) +
  xlab("Land Cover Class") +
  ylab("Number of Spiders") + 
  theme(text = element_text(size = 10)) + 
  theme(axis.text.x=element_text(colour="black", size=10)) + 
  theme(axis.text.y=element_text(colour="black", size=10)) +
  theme(legend.position = "none") +
  theme(axis.text.x = element_text(angle = 90, vjust = 1, hjust=1))
```

```{r figure s11 neighbor}
dist_land_nb <- glm.nb(round(RetreatDist, 0) ~ Land, data = nearest)
nd <- data.frame(Land = factor(levels(nearest$Land)))
predictions <- augment(dist_land_nb, newdata = nd, se_fit = TRUE, type.predict = "response")
predictions <- predictions %>% 
  rename("response" = ".fitted", "SE" = ".se.fit")
dist_land_plot <- ggplot(nearest, aes(x = Land, y = RetreatDist)) + 
  geom_jitter(color = "grey", width = 0.1, size = 0.5) +
  geom_point(aes(x = Land, y = response, color = Land), size = 2, data = predictions) + 
  geom_errorbar(aes(x = Land, 
                  ymin = response - SE, 
                  ymax = response + SE, color = Land), data = predictions, inherit.aes = FALSE, width = 0.25, size = 1) +
  theme_classic() +
  scale_color_manual(values = c("Deciduous Forest" = "#1b9e77", "Woody Wetlands" = "#1b9e77", "Urban, High" = "#d95f02", "Urban, Medium" = "#d95f02", "Urban, Low" = "#d95f02")) +
  xlab("Land Cover Class") +
  ylab("Distance from Focal \nWeb to Neighbor Web [cm]") + 
  theme(text = element_text(size = 10)) + 
  theme(axis.text.x=element_text(colour="black", size=10)) + 
  theme(axis.text.y=element_text(colour="black", size=10)) +
  theme(legend.position = "none") +
  theme(axis.text.x = element_text(angle = 90, vjust = 1, hjust=1))
```

```{r figure s11 height}
height_land_nb <- glmer.nb(round(RetreatHeight, 0) ~ Land + (1 | ID), data = webs_wrangled)
predictions <- expand.grid(Land = levels(factor(webs_wrangled$Land)))
predictions$response <- predict(height_land_nb, newdata = predictions, se.fit = TRUE, re.form = NA, type = "response")
bigBoot_height_land_nb <- bootMer(height_land_nb, BootFunc, nsim = 1000)
predSE <- t(apply(bigBoot_height_land_nb$t, MARGIN = 2, FUN = sd))
predictions$SE <- predSE[1, ]
height_land_plot <- ggplot(webs_wrangled, aes(x = Land, y = RetreatHeight)) + 
  geom_jitter(color = "grey", width = 0.1, size = 0.5) +
  geom_point(aes(x = Land, y = response, color = Land), size = 2, data = predictions) + 
  geom_errorbar(aes(x = Land, 
                  ymin = response - SE, 
                  ymax = response + SE, color = Land), data = predictions, inherit.aes = FALSE, width = 0.25, size = 1) +
  theme_classic() +
  scale_color_manual(values = c("Deciduous Forest" = "#1b9e77", "Woody Wetlands" = "#1b9e77", "Urban, High" = "#d95f02", "Urban, Medium" = "#d95f02", "Urban, Low" = "#d95f02")) +
  xlab("Land Cover Class") +
  ylab("Web Height [cm]") + 
  theme(text = element_text(size = 10)) + 
  theme(axis.text.x=element_text(colour="black", size=10)) + 
  theme(axis.text.y=element_text(colour="black", size=10)) +
  theme(legend.position = "none") +
  theme(axis.text.x = element_text(angle = 90, vjust = 1, hjust=1))
```

```{r figure s11 panel}
land_plots <- ggarrange(search_land_plot, ggarrange(webs_land_plot, spiders_land_plot, dist_land_plot, height_land_plot, labels = c("b", "c", "d", "e"), ncol = 2, nrow = 2, legend = "none", align = "hv"), labels = c("a"), widths = c(0.3, 0.7))

gt <- arrangeGrob(webs_land_plot, spiders_land_plot,
             search_land_plot, dist_land_plot, 
             height_land_plot,
             ncol = 3, nrow = 2, 
             layout_matrix = rbind(c(1, 2, 5), c(3, 4, 5)))

land_plots <- as_ggplot(gt) +                                # transform to a ggplot
  draw_plot_label(label = c("a", "c", "b", "d", "e"), size = 15,
                  x = c(0, 0, 0.33, 0.33, 0.66), y = c(1, 0.5, 1, 0.5, 1))

jpeg(filename = "figures/figureS11.jpeg", units = "cm", width = 17.4, height = 17.4, res = 300)
print(land_plots)
dev.off()
land_plots
```

**Fig. S11** Comparison of the number of webs (a) and spiders (b) in a 10-meter radius of the focal web, search distance (c), the distance from the focal web to the first nearest neighbor (d), and web height (e) by land cover class - urban high-intensity, urban medium-intensity, urban low-intensity, deciduous forest, woody wetlands. Land cover class was determined using the pixel category from the 2019 National Land Cover Data that the focal web site resides in. Grey jittered points represent the raw data while colored points (orange = urban center, green = urban forest) and error bars represent the mean and standard error, respectively, from negative binomial generalized linear model predictions. See table S3 for statistical analysis

# Figure S12

```{r figure s12}
substrates_plot <- substrates %>% 
  mutate(Location = fct_recode(Location, "Urban Center" = "Campus", "Urban Forest" = "Forest"),
         Location = fct_relevel(Location, "Urban Center", "Urban Forest")) %>% 
  ggplot(aes(x = Location, y = Number, fill = factor(Type, levels=c("Cement", "Metal", "Plastic", "Rocks", "Herb", "Litter", "Shrub", "Tree", "Vine")))) + 
  geom_bar(position = "fill",stat = "identity", alpha=1.0) + 
  scale_y_continuous(labels = scales::percent_format()) + 
  theme(axis.title.x = element_blank()) + 
  xlab("Collection Location") +
  ylab("Percent of Web Substrates") + 
  theme_classic() +
  theme(text = element_text(size = 10)) + 
  scale_fill_manual(values = c("#D94701", "#FD8D3C", "#FDBE85", "#FEEDDE", "#006D2C", "#31A354", "#74C476", "#BAE4B3", "#EDF8E9"), 
                    labels = c("Cement", "Metal", "Plastic", "Rocks", "Herb", "Litter", "Shrub", "Tree", "Vine")) + 
  labs(fill="Substrate Material") + 
  theme(axis.text.x=element_text(colour="black", size=10)) + 
  theme(axis.text.y=element_text(colour="black", size=10)) +
  theme(legend.text=element_text(size=10))
jpeg(filename = "figures/figureS12.jpeg", units = "cm", width = 17.4, height = 17.4, res = 300)
print(substrates_plot)
dev.off()
substrates_plot
```

**Fig. S12** Representation of web substrates by class. Orange indicates non-plant materials and green shades indicate plant material classes.

### 2024-09-30 8_publication_tables.Rmd
Organized code and wrote README.md file to help viewers interact with code

--- 2023-03-29 data_analysis.Rmd
@@
 ---
-title: "Data Wrangling and Statistical Analysis of Assessment of Abundance, Aggregation, and Web Placement of *Agelenopsis pennsylvanica*"
+title: "Tables for Publication"
 author: "Brandi Pessman"
-date: "`r Sys.Date()`"
+date: "2024-09-30"
 output: html_document
 ---
-
-## Setting the Working Directory and Global Code Chunk Options
-
-Using include = FALSE means that this chunk will run, but the code and the results will not appear in the knitted document.
-We have set message and warning to FALSE for every chunk so the knitted document is not bombarded with messages and warnings.
-
-```{r setup, include = FALSE}
-knitr::opts_chunk$set(message = FALSE, warning = FALSE)
+# Set the Working Directory and Global Code Chunk Options
+
+I have set message, warning, and echo to FALSE for every chunk so the knitted
+document does not include messages, warnings, or code.
+
+```{r setup, message = FALSE, warning = FALSE, echo = FALSE}
+knitr::opts_chunk$set(message = FALSE, warning = FALSE, echo = FALSE)
 require("knitr")
@@
 
-## Packages to Load
-
-There is a brief explanation of each package's purpose left as a comment following the library call.
-
-```{r packages, include = FALSE}
-library(tidyverse) # to use pipelines in data wrangling
+# Packages Loaded
+
+```{r packages}
+library(tidyverse) # wrangling data
+library(flextable) # making tables
 library(ggpubr) # using ggarrange to make multi-panel figures
-library(caret) # used to find correlations between predictor variables
-library(PerformanceAnalytics) # used to make correlation plots
-library(broom) # allows us to use augment when getting predicted values from the model
-library(emmeans) # for calculating predictions for graphing
-library(pander) # viewing AIC comparisons between models
-library(AICcmodavg) # also helps viewing AIC comparisons
-library(MuMIn) # to run the dredge function
-library(lme4) # to run the glmer function for the web distance (random effects)
-library(broom.mixed) # for augment of the mixed effect models (web distance) to look at assumptions
-library(multcomp) # for pairwise comparisons of land cover categories
-library(flextable) # making tables
-library(MASS) # negative binomial tests
-library(glmmTMB) # for proportion test
-library(jpeg) # save pictures
-```
-
-## Import Data
-
-The document "webs" is a text file in the data folder of the repository/directory.
+```
+
+# Import Data
 
 ```{r import, include = FALSE}
-webs <- read.table(file = "data/webs.txt", header = TRUE) 
-# includes data for every measured web (multiple per site)
 land_cover <- read.table(file = "data/land_cover_table.txt", header = TRUE) # for land cover table
-pred_table <- read.table(file = "data/pred_table.txt", header = TRUE) # for predictor stats table
-substrates <- read.table(file = "data/substrate.txt", header = TRUE) # for substrate figure
+pred_table_nb <- read.table(file = "data/pred_table_nb.txt", header = TRUE) # for predictor stats table
 site_info <- read.table(file = "data/site_info.txt", header = TRUE) # for site information table
-pred_table_avg <- read.table(file = "data/pred_table_avg.txt", header = TRUE) # for predictor stats table
-```
-
-## Data Wrangling
-
-Here, we rename some levels of factors Location and Land and put them in the order we want the categories to appear in a graph.
-We also create another data set "sites" that restricts "webs" to just a single data point for each site.
-We use "sites" to compare search distance, the number of webs, and the number of spiders.
-We will use "webs" for web height.
-The "web_dist" data set is a subset of "webs" that looks at the distance from the focal web to the nearest and second nearest neighbors.
-
-```{r webs_wrangling, include = FALSE}
-webs <- webs %>% 
-  mutate(ID = factor(ID),
-         Location = factor(Location),
-         Location = fct_recode(Location, 
-                               "Urban Forest" = "Forest",
-                               "Urban Center" = "Campus"),
-         Location = fct_relevel(Location, 
-                                "Urban Center", "Urban Forest"),
-         Land = fct_recode(Land, 
-                           "Urban, High" = "UrbanizedHighIntensity",
-                           "Urban, Medium" = "UrbanizedMediumIntensity",
-                           "Urban, Low" = "UrbanizedLowIntensity",
-                           "Deciduous Forest" = "DeciduousForest",
-                           "Woody Wetlands" = "WoodyWetlands"),
-         Land = fct_relevel(Land, 
-                            "Urban, High", 
-                            "Urban, Medium", 
-                            "Urban, Low", 
-                            "Deciduous Forest", 
-                            "Woody Wetlands"),
-         patch_area_km = patch_area_mm * 1e-6) %>% 
-  dplyr::rename("Impervious" = "Imperv", 
-                "Dist_to_Road" = "road_dist_data", 
-                "Traffic_Dist_Road" = "dist_traffic_road", 
-                "Dist_to_Highway" = "highway_dist_m", 
-                "Traffic_Dist_Highway" = "dist_traffic_highway")
-
-sites <- webs %>% 
-  filter(Web == "W001")
-
-web_dist <- webs %>% 
-  filter(RetreatDist != 0,
-         RetreatDist < 1000,
-         Web == "W002" | Web == "W003") %>% 
-  mutate(Neighbor = ifelse(Web == "W002", "1", "2"))
-
-near <- web_dist %>% 
-  filter(Neighbor == 1)
-```
-
-At one time, we tried scaling and centering the data in difference ways. I want to make mention of it here because it might be useful information for me to look back on in the future.
-
-- Scaling is dividing each datum by the standard deviation of the data and centering is subtracting the mean of the data from each datum to try to normalize the data.
-
-- A second type of centering and scaling involves subtracting the median and dividing by the interquartile range.
-
-It's important to remember to back transform when making figures. We didn't scale and center because log-transformations on right-skewed variables were enough to remove convergence errors.
-
-```{r sites_wrangling, include = FALSE}
-sites <- sites %>% 
-  mutate(patch_area_km = patch_area_mm * 1e-6,
-         tree100m_frac = as.numeric(tree100m/100),
-         imperv100m_frac = as.numeric(imperv100m/100))
-```
-
-## Transformation of Variables
-
-Many data are right-skewed.
-We check the distribution of the data and check distributions after log-transformation for right-skewed data not containing zeros.
-Echo = FALSE shows the results, but does not show the code used.
-
-```{r graphing_predictor_distributions, echo = FALSE}
-# Here, we graph the distribution of predictor variables in their raw distribution and after log-transformation since all variables are positive values, and many are zero-inflated; we also run shapiro-wilk tests to test for normality including the log-transformed variable if the log-transformed distribution looks better (less skewed)
-
-# use as is, log won't work because some data are zero
-ggarrange(ggplot(sites, aes(x = tree100m)) +
-  geom_density(), ggplot(sites, aes(x = tree100m_frac)) +
-  geom_density(), ncol = 2, nrow = 1)
-shapiro.test(sites$tree100m) # not normal
-shapiro.test(sites$tree100m_frac) # not normal
-
-# use as is, log won't work because some data are zero
-ggplot(sites, aes(x = imperv100m)) +
-  geom_density()
-shapiro.test(sites$imperv100m) # not normal
-
-# better log-transformed
-ggarrange(ggplot(sites, aes(x = TotalSub)) + 
-            geom_density(), 
-          ggplot(sites, aes(x = log(TotalSub))) +
-            geom_density(), 
-          nrow = 1, 
-          ncol = 2)
-shapiro.test(sites$TotalSub) # not normal
-shapiro.test(log10(sites$TotalSub)) # normal
-
-# better log-transformed
-ggarrange(ggplot(sites, aes(x = Traffic_Dist_Road)) + 
-            geom_density(), 
-          ggplot(sites, aes(x = log(Traffic_Dist_Road))) + 
-            geom_density(), 
-          nrow = 1, 
-          ncol = 2)
-shapiro.test(sites$Traffic_Dist_Road) # not normal
-shapiro.test(log(sites$Traffic_Dist_Road)) # normal
-
-# better log-transformed
-ggarrange(ggplot(sites, aes(x = Traffic_Dist_Highway)) + 
-            geom_density(), 
-          ggplot(sites, aes(x = log(Traffic_Dist_Highway))) + 
-            geom_density(), 
-          nrow = 1, 
-          ncol = 2)
-shapiro.test(sites$Traffic_Dist_Highway) # not normal
-shapiro.test(log(sites$Traffic_Dist_Highway)) # almost normal
-
-# looks similar either way
-ggarrange(ggplot(sites, aes(x = spec_rad)) + 
-            geom_density(), 
-          ggplot(sites, aes(x = log(spec_rad))) + 
-            geom_density(), 
-          nrow = 1, 
-          ncol = 2)
-shapiro.test(sites$spec_rad) # not normal
-shapiro.test(log(sites$spec_rad)) # not normal
-
-# looks similar either way, but shapiro tests suggests as is is slightly better
-ggarrange(ggplot(sites, aes(x = light_rad)) + 
-            geom_density(), 
-          ggplot(sites, aes(x = log(light_rad))) + 
-            geom_density(), 
-          nrow = 1, 
-          ncol = 2)
-shapiro.test(sites$light_rad) # not normal
-shapiro.test(log(sites$light_rad)) # not normal
-
-# better log-transformed
-ggarrange(ggplot(sites, aes(x = patch_area_mm)) +
-            geom_density(), 
-          ggplot(sites, aes(x = log(patch_area_mm))) +
-            geom_density(), 
-          nrow = 1, 
-          ncol = 2)
-shapiro.test(sites$patch_area_mm) # not normal
-shapiro.test(log(sites$patch_area_mm)) # almost normal
-
-# use as is, log won't work because some data are zero
-ggplot(sites, aes(x = road_length_m)) + 
-  geom_density()
-shapiro.test(sites$road_length_m) # not normal
-
-# use as is, log won't work because some data are zero
-ggplot(sites, aes(x = trail_length_m)) + 
-  geom_density()
-shapiro.test(sites$trail_length_m) # not normal
-
-sites <- sites %>% 
-  mutate(log_TotalSub = log(TotalSub),
-         log_tdr = log(Traffic_Dist_Road),
-         log_tdh = log(Traffic_Dist_Highway),
-         log_patch = log(patch_area_km))
-
-webs <- webs %>% 
-  mutate(log_TotalSub = log(TotalSub),
-         log_tdr = log(Traffic_Dist_Road),
-         log_tdh = log(Traffic_Dist_Highway),
-         log_patch = log(patch_area_mm))
-
-sites <- webs %>% 
-  filter(Web == "W001")
-
-web_dist <- webs %>% 
-  filter(RetreatDist != 0,
-         RetreatDist < 1000,
-         Web == "W002" | Web == "W003") %>% 
-  mutate(Neighbor = ifelse(Web == "W002", "1", "2"))
-
-near <- web_dist %>% 
-  filter(Neighbor == 1)
-
-webs$RetreatHeight[webs$RetreatHeight == 0] <- 0.1
-```
-
-We conclude to use log-transformations for TotalSub, Traffic_Dist_Road, Traffic_Dist_Highway, and patch_area_km.
-
-Our analyses include looking at variation within each location. As such, this chunk subsets the "sites" and "webs" data by Location.
-
-```{r location_subsets, include  = FALSE}
-webs_center <- webs %>% 
-  filter(Location == "Urban Center")
-
-webs_forest <- webs %>% 
-  filter(Location == "Urban Forest")
-
-sites_center <- sites %>% 
-  filter(Location == "Urban Center")
-
-sites_forest <- sites %>% 
-  filter(Location == "Urban Forest")
-
-web_dist_center <- web_dist %>% 
-  filter(Location == "Urban Center")
-
-web_dist_forest <- web_dist %>% 
-  filter(Location == "Urban Forest")
-
-near_forest <- near %>% 
-  filter(Location == "Urban Forest")
-
-near_center <- near %>% 
-  filter(Location == "Urban Center")
-```
-
-## Variable Reduction Based on Correlations
-
-Since many of these variables are likely highly correlated, we want to reduce the variables that we include in our model by removing variables that are highly correlated.
-
-```{r correlations_overall}
-corr <- sites %>% 
-  dplyr::select(tree100m, imperv100m, TotalSub, 
-         Traffic_Dist_Road, Traffic_Dist_Highway, 
-         spec_rad, light_rad, patch_area_mm, road_length_m)
-# We exclude trail length from global correlations because trail length can only collected in Wilderness Park, and not for UNL City Campus
-
-# When running findCorrelations, we get a vector of variables to remove to reduce pairwise correlations.
-
-findCorrelation(cor(corr, method = "spearman"), cutoff = .6, verbose = TRUE, names = TRUE)
-
-# This suggests that we remove tree100m, imperv100, spec_rad, light_rad, patch_area_km, road_length_m
-# That leaves us with TotalSub, Traffic_Dist_Road, and Traffic_Dist_Highway
-
-chart.Correlation(corr, histogram = TRUE, method = "spearman") # kendall, spearman
-
-corr <- sites %>% 
-  dplyr::select(TotalSub, Traffic_Dist_Road, Traffic_Dist_Highway)
-chart.Correlation(corr, histogram = TRUE, method = "spearman") # kendall, spearman
-
-# Let's also test the variables after transformation
-
-corr_transformed <- sites %>% 
-  dplyr::select(tree100m, imperv100m, log_TotalSub, 
-         log_tdr, log_tdh, 
-         spec_rad, light_rad, log_patch, road_length_m)
-
-findCorrelation(cor(corr_transformed, method = "spearman"), cutoff = .6, verbose = TRUE, names = TRUE)
-
-# This suggests to remove tree100m, imperv100m, spec_rad, light_rad, log_patch, and road_length_m.
-
-# This leaves us with log_TotalSub, log_tdr, and log_tdh, the same results as the non-transformed.
-
-chart.Correlation(corr_transformed, histogram = TRUE, method = "spearman") # kendall, spearman
-
-corr_transformed <- sites %>% 
-  dplyr::select(log_TotalSub, log_tdr, log_tdh)
-chart.Correlation(corr_transformed, histogram = TRUE, method = "spearman") # kendall, spearman
-```
-
-```{r correlations_forest}
-corr_forest <- sites %>% 
-  filter(Location == "Urban Forest") %>% 
-  dplyr::select(tree100m, imperv100m, TotalSub, 
-         Traffic_Dist_Road, Traffic_Dist_Highway, 
-         spec_rad, light_rad, patch_area_km, road_length_m, trail_length_m)
-# Notice trail length is included
-
-findCorrelation(cor(corr_forest, method = "spearman"), cutoff = .6, verbose = TRUE, names = TRUE) 
-# This suggests removing imperv100m, spec_rad, light_rad, road_length_m, and trail_length_m
-# We will keep tree100m, TotalSub, Traffic_Dist_Road, Traffic_Dist_Highway, and patch_area_km
-chart.Correlation(corr_forest, histogram = TRUE, method = "spearman")
-corr_forest <- sites %>% 
-  filter(Location == "Urban Forest") %>% 
-  dplyr::select(tree100m, TotalSub, Traffic_Dist_Road, patch_area_km, Traffic_Dist_Highway)
-chart.Correlation(corr_forest, histogram = TRUE, method = "spearman")
-
-# Let's try with the log-transformed
-corr_forest_transformed <- sites %>% 
-  filter(Location == "Urban Forest") %>% 
-  dplyr::select(tree100m, imperv100m, log_TotalSub, 
-         log_tdr, log_tdh, 
-         spec_rad, light_rad, log_patch, road_length_m, trail_length_m)
-
-findCorrelation(cor(corr_forest_transformed, method = "spearman"), cutoff = .6, verbose = TRUE, names = TRUE) 
-# The same variables are dropped and kept
-
-corr_forest_transformed <- sites %>% 
-  filter(Location == "Urban Forest") %>% 
-  dplyr::select(tree100m, log_TotalSub, log_tdr, patch_area_km, log_tdh)
-chart.Correlation(corr_forest_transformed, histogram = TRUE, method = "spearman")
-```
-
-```{r correlations_center}
-corr_center <- sites %>% 
-  filter(Location == "Urban Center") %>% 
-  dplyr::select(tree100m, imperv100m, TotalSub, Traffic_Dist_Road, Traffic_Dist_Highway, spec_rad, light_rad, patch_area_km, road_length_m)
-# Trail length is removed because we could not measure trail length on campus
-
-findCorrelation(cor(corr_center, method = "spearman"), cutoff = .6, verbose = TRUE, names = TRUE) 
-# This suggests that we remove tree100m, imperv100m, and light_rad
-# We will keep TotalSub, Traffic_Dist_Road, Traffic_Dist_Highway, spec_rad, patch_area_km, and road_length_m
-
-chart.Correlation(corr_center, histogram = TRUE, method = "spearman")
-
-# Let's try with the transformed
-corr_center_transformed <- sites %>% 
-  filter(Location == "Urban Center") %>% 
-  dplyr::select(tree100m, imperv100m, log_TotalSub, log_tdr, log_tdh, spec_rad, light_rad, log_patch, road_length_m)
-findCorrelation(cor(corr_center_transformed, method = "spearman"), cutoff = .6, verbose = TRUE, names = TRUE) 
-chart.Correlation(corr_center_transformed, histogram = TRUE, method = "pearson")
-# The same variables are kept or removed
-```
-
-For overall analysis of predictors, we will include:
-
-- log_TotalSub
-
-- log_tdr
-
-- log_tdh
-
-For the urban forest subset, we will use:
-
-- tree100m
-
-- log_TotalSub
-
-- log_tdr
-
-- log_tdh
-
-- log_patch
-
-Finally, for the urban center subset, we will use:
-
-- log_TotalSub
-
-- log_tdr
-
-- log_tdh
-
-- spec_rad
-
-- log_patch
-
-- road_length_m
-
-## Graphs, Stats, and Assumptions Comparing Predictors by Location
-
-Here, we just want to see if each predictor differs between the two Locations: urban forest and urban center. We build models, check assumptions of the model, and make graphs to represent differences.
-
-```{r stats_graphs_tree, echo = FALSE}
-tree100m <- glm(tree100m ~ Location, family = "poisson", data = sites)
-summary(tree100m)
-
-tree100m.nb <- glm.nb(tree100m ~ Location, data = sites)
-summary(tree100m.nb)
-
-# The following line tells you the mean and standard error of the raw data for tree cover in a 100 m radius of the sites between the two locations
-sites %>% 
-  group_by(Location) %>% 
-  summarize(mean = mean(tree100m),
-            se = plotrix::std.error(tree100m))
-
-predictions <- summary(emmeans(tree100m.nb, ~Location),type = "response")
-predictions
-
-ggplot(sites, aes(x = Location, y = tree100m)) + 
-  geom_jitter(color = "grey", width = 0.1, size = 1) +
-  geom_point(aes(x = Location, y = rate, color = Location), size = 2, data = predictions) + 
-  geom_errorbar(aes(x = Location, 
-                  ymin = rate - SE, 
-                  ymax = rate + SE,
-                  color = Location), data = predictions, inherit.aes = FALSE, width = 0.15, linewidth = 1.5) +
-  scale_color_manual(values = c("Urban Center" = "#d95f02", "Urban Forest" = "#1b9e77")) +
-  scale_x_discrete(labels=c("Urban Forest" = "Urban \nForest \nN = 10", "Urban Center" = "Urban \nCenter \nN = 12")) +
-  scale_y_continuous(limits=c(0, 100), breaks = c(0, 10, 20, 30, 40, 50, 60, 70, 80, 90, 100)) +
-  theme_classic() +
-  ylab("Percent Tree Cover \n[100m radius]") + 
-  theme(text = element_text(size = 18)) + 
-  theme(axis.text.x=element_text(colour="black", size=18)) + 
-  theme(axis.text.y=element_text(colour="black", size=18),
-        axis.title.x = element_blank()) +
-  theme(legend.position = "none") +
-  annotate(geom="text", x=1.5, y=100, label="***", color="black", size = 10)
-```
-
-```{r tree_assumptions, echo = FALSE}
-test_tree <- augment(tree100m.nb, data = sites)
-resid_tree <- ggplot(test_tree, aes(x = .fitted, y = .resid)) + 
-  geom_point() + 
-  geom_smooth() +
-  geom_hline(yintercept = 0) +
-  xlab("Fitted Values") +
-  ylab("Standardized \nResiduals") +
-  theme_classic() +
-  theme(text = element_text(size = 14, color = "black")) +
-  theme(axis.text.x=element_text(color="black", size=14)) + 
-  theme(axis.text.y=element_text(color="black", size=14))
-
-y <- quantile(test_tree$.resid, c(0.25, 0.75))
-x <- qnorm(c(0.25, 0.75))
-slope <- diff(y)/diff(x)
-int <- y[1L] - slope * x[1L]
-
-qq_tree <- ggplot(test_tree, aes(sample = .resid)) + 
-  stat_qq() + 
-  geom_abline(slope = slope, intercept = int) +
-  xlab("Theoretical Quantiles") +
-  ylab("Sample Quantiles") +
-  theme_classic() +
-  theme(text = element_text(size = 14, color = "black")) +
-  theme(axis.text.x=element_text(color="black", size=14)) + 
-  theme(axis.text.y=element_text(color="black", size=14))
-
-ggarrange(resid_tree, qq_tree, 
-          labels = c("A", "B"),
-          ncol = 2, nrow = 1)
-```
-
-Tree cover is **significantly higher in the urban forest** than the urban center (z = 13.77, df = 1, 21, p < 0.001).
-The means and SE's are 47.15 ± 3.46 % for the urban forest and 1.58 ± 0.37 % for the urban center.
-
-```{r stats_graphs_imperv, echo = FALSE}
-imperv100m <- glm(imperv100m ~ Location, family = "poisson", data = sites)
-summary(imperv100m)
-
-imperv100m.nb <- glm.nb(imperv100m ~ Location, data = sites)
-summary(imperv100m.nb)
-
-# The following line tells you the mean and standard error of the raw data for impervious cover in a 100 m radius of the sites between the two locations
-sites %>% 
-  group_by(Location) %>% 
-  summarize(mean = mean(imperv100m),
-            se = plotrix::std.error(imperv100m))
-
-predictions <- summary(emmeans(imperv100m.nb, ~Location),type = "response")
-predictions
-
-ggplot(sites, aes(x = Location, y = imperv100m)) + 
-  geom_jitter(color = "grey", width = 0.1, size = 1) +
-  geom_point(aes(x = Location, y = rate, color = Location), size = 2, data = predictions) + 
-  geom_errorbar(aes(x = Location, 
-                  ymin = rate - SE, 
-                  ymax = rate + SE,
-                  color = Location), data = predictions, inherit.aes = FALSE, width = 0.15, linewidth = 1.5) +
-  scale_color_manual(values = c("Urban Center" = "#d95f02", "Urban Forest" = "#1b9e77")) +
-  scale_x_discrete(labels=c("Urban Forest" = "Urban \nForest \nN = 10", "Urban Center" = "Urban \nCenter \nN = 12")) +
-  scale_y_continuous(limits=c(0, 100), breaks = c(0, 10, 20, 30, 40, 50, 60, 70, 80, 90, 100)) +
-  theme_classic() +
-  ylab("Percent Impervious Cover \n[100m radius]") + 
-  theme(text = element_text(size = 18)) + 
-  theme(axis.text.x=element_text(colour="black", size=18)) + 
-  theme(axis.text.y=element_text(colour="black", size=18),
-        axis.title.x = element_blank()) +
-  theme(legend.position = "none") +
-  annotate(geom="text", x=1.5, y=100, label="***", color="black", size = 10)
-```
-
-```{r imperv_assumptions, echo = FALSE}
-test_imperv <- augment(imperv100m.nb, data = sites)
-resid_imperv <- ggplot(test_imperv, aes(x = .fitted, y = .resid)) + 
-  geom_point() + 
-  geom_smooth() +
-  geom_hline(yintercept = 0) +
-  xlab("Fitted Values") +
-  ylab("Standardized \nResiduals") +
-  theme_classic() +
-  theme(text = element_text(size = 14, color = "black")) +
-  theme(axis.text.x=element_text(color="black", size=14)) + 
-  theme(axis.text.y=element_text(color="black", size=14))
-
-y <- quantile(test_imperv$.resid, c(0.25, 0.75))
-x <- qnorm(c(0.25, 0.75))
-slope <- diff(y)/diff(x)
-int <- y[1L] - slope * x[1L]
-
-qq_imperv <- ggplot(test_imperv, aes(sample = .resid)) + 
-  stat_qq() + 
-  geom_abline(slope = slope, intercept = int) +
-  xlab("Theoretical Quantiles") +
-  ylab("Sample Quantiles") +
-  theme_classic() +
-  theme(text = element_text(size = 14, color = "black")) +
-  theme(axis.text.x=element_text(color="black", size=14)) + 
-  theme(axis.text.y=element_text(color="black", size=14))
-
-ggarrange(resid_imperv, qq_imperv, 
-          labels = c("A", "B"),
-          ncol = 2, nrow = 1)
-```
-
-Impervious cover is **significantly higher in the urban center** than the urban forest (z = -14.49, df = 1, 21, p < 0.001).
-The means and SE's are 1.27 ± 0.36 % for the urban forest and 76.52 ± 2.63 % for the urban center.
-
-```{r stats_graphs_tdr, echo = FALSE}
-tdr <- glm(Traffic_Dist_Road ~ Location, family = "poisson", data = sites)
-summary(tdr)
-
-tdr.nb <- glm.nb(Traffic_Dist_Road ~ Location, data = sites)
-summary(tdr.nb)
-
-sites %>% 
-  group_by(Location) %>% 
-  summarize(mean = mean(Traffic_Dist_Road),
-            se = plotrix::std.error(Traffic_Dist_Road))
-
-predictions <- summary(emmeans(tdr.nb, ~Location),type = "response")
-predictions
-
-ggplot(sites, aes(x = Location, y = Traffic_Dist_Road)) + 
-  geom_jitter(color = "grey", width = 0.1, size = 1) +
-  geom_point(aes(x = Location, y = (rate), color = Location), size = 2, data = predictions) + 
-  geom_errorbar(aes(x = Location, 
-                  ymin = (rate - SE), 
-                  ymax = (rate + SE),
-                  color = Location), data = predictions, inherit.aes = FALSE, width = 0.15, linewidth = 1.5) +
-  scale_color_manual(values = c("Urban Center" = "#d95f02", "Urban Forest" = "#1b9e77")) +
-  scale_x_discrete(labels=c("Urban Forest" = "Urban \nForest \nN = 10", "Urban Center" = "Urban \nCenter \nN = 12")) +
-  scale_y_continuous(limits=c(0, 1400), breaks = c(0, 200, 400, 600, 800, 1000, 1200, 1400)) +
-  theme_classic() +
-  ylab("Road Disturbance \n[vehicles/day/m]") + 
-  theme(text = element_text(size = 18)) + 
-  theme(axis.text.x=element_text(colour="black", size=18)) + 
-  theme(axis.text.y=element_text(colour="black", size=18),
-        axis.title.x = element_blank()) +
-  theme(legend.position = "none") +
-  annotate(geom="text", x=1.5, y=1400, label="***", color="black", size = 10)
-```
-
-```{r tdr_assumptions, echo = FALSE}
-test_tdr <- augment(tdr.nb, data = sites)
-resid_tdr <- ggplot(test_tdr, aes(x = .fitted, y = .resid)) + 
-  geom_point() + 
-  geom_smooth() +
-  geom_hline(yintercept = 0) +
-  xlab("Fitted Values") +
-  ylab("Standardized \nResiduals") +
-  theme_classic() +
-  theme(text = element_text(size = 14, color = "black")) +
-  theme(axis.text.x=element_text(color="black", size=14)) + 
-  theme(axis.text.y=element_text(color="black", size=14))
-
-y <- quantile(test_tdr$.resid, c(0.25, 0.75))
-x <- qnorm(c(0.25, 0.75))
-slope <- diff(y)/diff(x)
-int <- y[1L] - slope * x[1L]
-
-qq_tdr <- ggplot(test_tdr, aes(sample = .resid)) + 
-  stat_qq() + 
-  geom_abline(slope = slope, intercept = int) +
-  xlab("Theoretical Quantiles") +
-  ylab("Sample Quantiles") +
-  theme_classic() +
-  theme(text = element_text(size = 14, color = "black")) +
-  theme(axis.text.x=element_text(color="black", size=14)) + 
-  theme(axis.text.y=element_text(color="black", size=14))
-
-ggarrange(resid_tdr, qq_tdr, 
-          labels = c("A", "B"),
-          ncol = 2, nrow = 1)
-```
-
-**Road disturbance is higher in the urban center** than the urban forest (z = -2.87, df = 1, 21, p = 0.004).
-The means and SE's are 104 ± 36 vehicles/day/m for the urban forest and 398 ± 125 vehicles/day/m for the urban center.
-
-```{r stats_graphs_tdh, echo = FALSE}
-tdh <- glm(Traffic_Dist_Highway ~ Location, family = "poisson", data = sites)
-summary(tdh)
-
-tdh.nb <- glm.nb(Traffic_Dist_Highway ~ Location, data = sites)
-summary(tdh.nb)
-
-sites %>% 
-  group_by(Location) %>% 
-  summarize(mean = mean(Traffic_Dist_Highway),
-            se = plotrix::std.error(Traffic_Dist_Highway))
-
-predictions <- summary(emmeans(tdh.nb, ~Location),type = "response")
-predictions
-
-ggplot(sites, aes(x = Location, y = (Traffic_Dist_Highway))) + 
-  geom_jitter(color = "grey", width = 0.1, size = 1) +
-  geom_point(aes(x = Location, y = (rate), color = Location), size = 2, data = predictions) + 
-  geom_errorbar(aes(x = Location, 
-                  ymin = (rate - SE), 
-                  ymax = (rate + SE),
-                  color = Location), data = predictions, inherit.aes = FALSE, width = 0.15, linewidth = 1.5) +
-  scale_color_manual(values = c("Urban Center" = "#d95f02", "Urban Forest" = "#1b9e77")) +
-  scale_x_discrete(labels=c("Urban Forest" = "Urban \nForest \nN = 10", "Urban Center" = "Urban \nCenter \nN = 12")) +
-  scale_y_continuous(limits=c(0, 250), breaks = c(0, 50, 100, 150, 200, 250)) +
-  theme_classic() +
-  ylab("Highway Disturbance \n[vehicles/day/m]") + 
-  theme(text = element_text(size = 18)) + 
-  theme(axis.text.x=element_text(colour="black", size=18)) + 
-  theme(axis.text.y=element_text(colour="black", size=18),
-        axis.title.x = element_blank()) +
-  theme(legend.position = "none") +
-  annotate(geom="text", x=1.5, y=250, label="***", color="black", size = 10)
-```
-
-```{r tdh_assumptions, echo = FALSE}
-test_tdh <- augment(tdh.nb, data = sites)
-resid_tdh <- ggplot(test_tdh, aes(x = .fitted, y = .resid)) + 
-  geom_point() + 
-  geom_smooth() +
-  geom_hline(yintercept = 0) +
-  xlab("Fitted Values") +
-  ylab("Standardized \nResiduals") +
-  theme_classic() +
-  theme(text = element_text(size = 14, color = "black")) +
-  theme(axis.text.x=element_text(color="black", size=14)) + 
-  theme(axis.text.y=element_text(color="black", size=14))
-
-y <- quantile(test_tdh$.resid, c(0.25, 0.75))
-x <- qnorm(c(0.25, 0.75))
-slope <- diff(y)/diff(x)
-int <- y[1L] - slope * x[1L]
-
-qq_tdh <- ggplot(test_tdh, aes(sample = .resid)) + 
-  stat_qq() + 
-  geom_abline(slope = slope, intercept = int) +
-  xlab("Theoretical Quantiles") +
-  ylab("Sample Quantiles") +
-  theme_classic() +
-  theme(text = element_text(size = 14, color = "black")) +
-  theme(axis.text.x=element_text(color="black", size=14)) + 
-  theme(axis.text.y=element_text(color="black", size=14))
-
-ggarrange(resid_tdh, qq_tdh, 
-          labels = c("A", "B"),
-          ncol = 2, nrow = 1)
-```
-
-**Highway disturbance is higher in the urban center** than the urban fores (z = -2.64, df = 1, 21, p = 0.008).
-The means and SE's are 35.6 ± 6.04 vehicles/day/m for the urban forest and 65.0 ± 9.82 vehicles/day/m for the urban center.
-
-```{r stats_graphs_plant, echo = FALSE}
-plant <- glm(TotalSub ~ Location, family = "poisson", data = sites)
-summary(plant)
-
-plant.nb <- glm.nb(TotalSub ~ Location, data = sites)
-summary(plant.nb)
-
-predictions <- summary(emmeans(plant.nb, ~Location),type = "response")
-predictions
-
-plant_used.nb <- glm.nb(SubUsed ~ Location, data = sites)
-summary(plant_used.nb)
-
-predictions <- summary(emmeans(plant_used.nb, ~Location),type = "response")
-predictions
-
-sites %>% 
-  group_by(Location) %>% 
-  summarize(mean = mean(TotalSub),
-            se = plotrix::std.error(TotalSub))
-
-ggplot(sites, aes(x = Location, y = (TotalSub))) + 
-  geom_jitter(color = "grey", width = 0.1, size = 1) +
-  geom_point(aes(x = Location, y = (rate), color = Location), size = 2, data = predictions) + 
-  geom_errorbar(aes(x = Location, 
-                  ymin = (rate - SE), 
-                  ymax = (rate + SE),
-                  color = Location), data = predictions, inherit.aes = FALSE, width = 0.15, linewidth = 1.5) +
-  scale_color_manual(values = c("Urban Center" = "#d95f02", "Urban Forest" = "#1b9e77")) +
-  scale_x_discrete(labels=c("Urban Forest" = "Urban \nForest \nN = 10", "Urban Center" = "Urban \nCenter \nN = 12")) +
-  scale_y_continuous(limits=c(0, 25), breaks = c(0, 5, 10, 15, 20, 25)) +
-  theme_classic() +
-  ylab("Plant Species Richness \n[species/site]") + 
-  theme(text = element_text(size = 18)) + 
-  theme(axis.text.x=element_text(colour="black", size=18)) + 
-  theme(axis.text.y=element_text(colour="black", size=18),
-        axis.title.x = element_blank()) +
-  theme(legend.position = "none") +
-  annotate(geom="text", x=1.5, y=25, label="***", color="black", size = 10)
-```
-
-```{r plant_assumptions, echo = FALSE}
-test_plant <- augment(plant.nb, data = sites)
-resid_plant <- ggplot(test_plant, aes(x = .fitted, y = .resid)) + 
-  geom_point() + 
-  geom_smooth() +
-  geom_hline(yintercept = 0) +
-  xlab("Fitted Values") +
-  ylab("Standardized \nResiduals") +
-  theme_classic() +
-  theme(text = element_text(size = 14, color = "black")) +
-  theme(axis.text.x=element_text(color="black", size=14)) + 
-  theme(axis.text.y=element_text(color="black", size=14))
-
-y <- quantile(test_plant$.resid, c(0.25, 0.75))
-x <- qnorm(c(0.25, 0.75))
-slope <- diff(y)/diff(x)
-int <- y[1L] - slope * x[1L]
-
-qq_plant <- ggplot(test_plant, aes(sample = .resid)) + 
-  stat_qq() + 
-  geom_abline(slope = slope, intercept = int) +
-  xlab("Theoretical Quantiles") +
-  ylab("Sample Quantiles") +
-  theme_classic() +
-  theme(text = element_text(size = 14, color = "black")) +
-  theme(axis.text.x=element_text(color="black", size=14)) + 
-  theme(axis.text.y=element_text(color="black", size=14))
-
-ggarrange(resid_plant, qq_plant, 
-          labels = c("A", "B"),
-          ncol = 2, nrow = 1)
-```
-
-Plant species richness is **significantly higher in the urban forest** than the urban center (z = 6.61, df = 1, 21, p < 0.001).
-The means and SE's are 13.30 ± 1.56 species for the urban forest and 3.33 ± 0.58 species for the urban center.
-
-```{r stats_graphs_spec, echo = FALSE}
-spec <- glm(spec_rad ~ Location, family = "poisson", data = sites)
-summary(spec)
-
-spec.nb <- glm.nb(spec_rad ~ Location, data = sites)
-summary(spec.nb)
-
-sites %>% 
-  group_by(Location) %>% 
-  summarize(mean = mean(spec_rad),
-            se = plotrix::std.error(spec_rad))
-
-predictions <- summary(emmeans(spec.nb, ~Location),type = "response")
-predictions
-
-ggplot(sites, aes(x = Location, y = spec_rad)) + 
-  geom_jitter(color = "grey", width = 0.1, size = 1) +
-  geom_point(aes(x = Location, y = rate, color = Location), size = 2, data = predictions) + 
-  geom_errorbar(aes(x = Location, 
-                  ymin = rate - SE, 
-                  ymax = rate + SE,
-                  color = Location), data = predictions, inherit.aes = FALSE, width = 0.15, linewidth = 1.5) +
-  scale_color_manual(values = c("Urban Center" = "#d95f02", "Urban Forest" = "#1b9e77")) +
-  scale_x_discrete(labels=c("Urban Forest" = "Urban \nForest \nN = 10", "Urban Center" = "Urban \nCenter \nN = 12")) +
-  scale_y_continuous(limits=c(130, 165), breaks = c(130, 135, 140, 145, 150, 155, 160, 165)) +
-  theme_classic() +
-  ylab("Spectral Radiance \n[Watts/(m² * sr * µm)]") + 
-  theme(text = element_text(size = 18)) + 
-  theme(axis.text.x=element_text(colour="black", size=18)) + 
-  theme(axis.text.y=element_text(colour="black", size=18),
-        axis.title.x = element_blank()) +
-  theme(legend.position = "none") +
-  annotate(geom="text", x=1.5, y=165, label="**", color="black", size = 10)
-```
-
-```{r spec_assumptions, echo = FALSE}
-test_spec <- augment(spec.nb, data = sites)
-resid_spec <- ggplot(test_spec, aes(x = .fitted, y = .resid)) + 
-  geom_point() + 
-  geom_smooth() +
-  geom_hline(yintercept = 0) +
-  xlab("Fitted Values") +
-  ylab("Standardized \nResiduals") +
-  theme_classic() +
-  theme(text = element_text(size = 14, color = "black")) +
-  theme(axis.text.x=element_text(color="black", size=14)) + 
-  theme(axis.text.y=element_text(color="black", size=14))
-
-y <- quantile(test_spec$.resid, c(0.25, 0.75))
-x <- qnorm(c(0.25, 0.75))
-slope <- diff(y)/diff(x)
-int <- y[1L] - slope * x[1L]
-
-qq_spec <- ggplot(test_spec, aes(sample = .resid)) + 
-  stat_qq() + 
-  geom_abline(slope = slope, intercept = int) +
-  xlab("Theoretical Quantiles") +
-  ylab("Sample Quantiles") +
-  theme_classic() +
-  theme(text = element_text(size = 14, color = "black")) +
-  theme(axis.text.x=element_text(color="black", size=14)) + 
-  theme(axis.text.y=element_text(color="black", size=14))
-
-ggarrange(resid_spec, qq_spec, 
-          labels = c("A", "B"),
-          ncol = 2, nrow = 1)
-```
-
-Spectral radiance is **significantly higher in the urban center** than the urban forest (z = -3.079, df = 1, 21, p = 0.002).
-The means and SE's are 137 ± 3.71 Watts/(m² * sr * µm) for the urban forest and 153 ± 3.58 Watts/(m² * sr * µm) for the urban center.
-
-```{r stats_graphs_light, echo = FALSE}
-light <- glm(light_rad ~ Location, family = "poisson", data = sites)
-summary(light)
-
-light.nb <- glm.nb(light_rad ~ Location, data = sites)
-summary(light.nb)
-
-sites %>% 
-  group_by(Location) %>% 
-  summarize(mean = mean(light_rad),
-            se = plotrix::std.error(light_rad))
-
-predictions <- summary(emmeans(light.nb, ~Location),type = "response")
-predictions
-
-ggplot(sites, aes(x = Location, y = light_rad)) + 
-  geom_jitter(color = "grey", width = 0.1, size = 1) +
-  geom_point(aes(x = Location, y = rate, color = Location), size = 2, data = predictions) + 
-  geom_errorbar(aes(x = Location, 
-                  ymin = rate - SE, 
-                  ymax = rate + SE,
-                  color = Location), data = predictions, inherit.aes = FALSE, width = 0.15, linewidth = 1.5) +
-  scale_color_manual(values = c("Urban Center" = "#d95f02", "Urban Forest" = "#1b9e77")) +
-  scale_x_discrete(labels=c("Urban Forest" = "Urban \nForest \nN = 10", "Urban Center" = "Urban \nCenter \nN = 12")) +
-  scale_y_continuous(limits=c(0, 175), breaks = c(0, 25, 50, 75, 100, 125, 150, 175)) +
-  theme_classic() +
-  ylab("Radiance [mcd/m²]") + 
-  theme(text = element_text(size = 18)) + 
-  theme(axis.text.x=element_text(colour="black", size=18)) + 
-  theme(axis.text.y=element_text(colour="black", size=18),
-        axis.title.x = element_blank()) +
-  theme(legend.position = "none") +
-  annotate(geom="text", x=1.5, y=175, label="***", color="black", size = 10)
-```
-
-```{r light_assumptions, echo = FALSE}
-test_light <- augment(light.nb, data = sites)
-resid_light <- ggplot(test_light, aes(x = .fitted, y = .resid)) + 
-  geom_point() + 
-  geom_smooth() +
-  geom_hline(yintercept = 0) +
-  xlab("Fitted Values") +
-  ylab("Standardized \nResiduals") +
-  theme_classic() +
-  theme(text = element_text(size = 14, color = "black")) +
-  theme(axis.text.x=element_text(color="black", size=14)) + 
-  theme(axis.text.y=element_text(color="black", size=14))
-
-y <- quantile(test_light$.resid, c(0.25, 0.75))
-x <- qnorm(c(0.25, 0.75))
-slope <- diff(y)/diff(x)
-int <- y[1L] - slope * x[1L]
-
-qq_light <- ggplot(test_light, aes(sample = .resid)) + 
-  stat_qq() + 
-  geom_abline(slope = slope, intercept = int) +
-  xlab("Theoretical Quantiles") +
-  ylab("Sample Quantiles") +
-  theme_classic() +
-  theme(text = element_text(size = 14, color = "black")) +
-  theme(axis.text.x=element_text(color="black", size=14)) + 
-  theme(axis.text.y=element_text(color="black", size=14))
-
-ggarrange(resid_light, qq_light, 
-          labels = c("A", "B"),
-          ncol = 2, nrow = 1)
-```
-
-Light radiance is **significantly higher in the urban center** than the urban forest (z = -17.17, df = 1, 21, p < 0.001).
-The means and SE's are 5.89 ± 0.91 mcd/m² for the urban forest and 116.90 ± 9.39 mcd/m² for the urban center.
-
-```{r stats_graphs_patch, echo = FALSE}
-patch <- glm(patch_area_mm ~ Location, family = "poisson", data = sites)
-summary(patch)
-
-patch.nb <- glm.nb(patch_area_mm ~ Location, data = sites)
-summary(patch.nb)
-
-sites %>% 
-  group_by(Location) %>% 
-  summarize(mean = mean(patch_area_mm),
-            se = plotrix::std.error(patch_area_mm))
-
-predictions <- summary(emmeans(patch.nb, ~Location),type = "response")
-predictions
-
-ggplot(sites, aes(x = Location, y = (patch_area_mm))) + 
-  geom_jitter(color = "grey", width = 0.1, size = 1) +
-  geom_point(aes(x = Location, y = (rate), color = Location), size = 2, data = predictions) + 
-  geom_errorbar(aes(x = Location, 
-                  ymin = (rate - SE), 
-                  ymax = (rate + SE),
-                  color = Location), data = predictions, inherit.aes = FALSE, width = 0.15, linewidth = 1.5) +
-  scale_color_manual(values = c("Urban Center" = "#d95f02", "Urban Forest" = "#1b9e77")) +
-  scale_x_discrete(labels=c("Urban Forest" = "Urban \nForest \nN = 10", "Urban Center" = "Urban \nCenter \nN = 12")) +
-  scale_y_continuous(limits=c(0, 130310), breaks = c(0, 20000, 40000, 60000, 80000, 100000, 120000)) +
-  theme_classic() +
-  ylab("Patch Area [mm²]") + 
-  theme(text = element_text(size = 18)) + 
-  theme(axis.text.x=element_text(colour="black", size=18)) + 
-  theme(axis.text.y=element_text(colour="black", size=18),
-        axis.title.x = element_blank()) +
-  theme(legend.position = "none") +
-  annotate(geom="text", x=1.5, y=130310, label="***", color="black", size = 10)
-```
-
-```{r patch_assumptions, echo = FALSE}
-test_patch <- augment(patch.nb, data = sites)
-resid_patch <- ggplot(test_patch, aes(x = .fitted, y = .resid)) + 
-  geom_point() + 
-  geom_smooth() +
-  geom_hline(yintercept = 0) +
-  xlab("Fitted Values") +
-  ylab("Standardized \nResiduals") +
-  theme_classic() +
-  theme(text = element_text(size = 14, color = "black")) +
-  theme(axis.text.x=element_text(color="black", size=14)) + 
-  theme(axis.text.y=element_text(color="black", size=14))
-
-y <- quantile(test_patch$.resid, c(0.25, 0.75))
-x <- qnorm(c(0.25, 0.75))
-slope <- diff(y)/diff(x)
-int <- y[1L] - slope * x[1L]
-
-qq_patch <- ggplot(test_patch, aes(sample = .resid)) + 
-  stat_qq() + 
-  geom_abline(slope = slope, intercept = int) +
-  xlab("Theoretical Quantiles") +
-  ylab("Sample Quantiles") +
-  theme_classic() +
-  theme(text = element_text(size = 14, color = "black")) +
-  theme(axis.text.x=element_text(color="black", size=14)) + 
-  theme(axis.text.y=element_text(color="black", size=14))
-
-ggarrange(resid_patch, qq_patch, 
-          labels = c("A", "B"),
-          ncol = 2, nrow = 1)
-```
-
-Patch area is **significantly higher in the urban forest** than the urban center (z = 13.08, df = 1, 21, p < 0.001).
-The means and SE's are 46,295 ± 11,128 mm² for the urban forest and 654 ± 144 mm² for the urban center.
-
-```{r stats_graphs_road, echo = FALSE}
-road <- glm(road_length_m ~ Location, family = "poisson", data = sites)
-summary(road)
-
-road.nb <- glm.nb(road_length_m ~ Location, data = sites)
-summary(road.nb)
-
-sites %>% 
-  group_by(Location) %>% 
-  summarize(mean = mean(road_length_m),
-            se = plotrix::std.error(road_length_m))
-
-predictions <- summary(emmeans(road.nb, ~Location),type = "response")
-predictions
-
-ggplot(sites, aes(x = Location, y = road_length_m)) + 
-  geom_jitter(color = "grey", width = 0.1, size = 1) +
-  geom_point(aes(x = Location, y = rate, color = Location), size = 2, data = predictions) + 
-  geom_errorbar(aes(x = Location, 
-                  ymin = rate - SE, 
-                  ymax = rate + SE,
-                  color = Location), data = predictions, inherit.aes = FALSE, width = 0.15, linewidth = 1.5) +
-  scale_color_manual(values = c("Urban Center" = "#d95f02", "Urban Forest" = "#1b9e77")) +
-  scale_x_discrete(labels=c("Urban Forest" = "Urban \nForest \nN = 10", "Urban Center" = "Urban \nCenter \nN = 12")) +
-  scale_y_continuous(limits=c(0, 140), breaks = c(0, 20, 40, 60, 80, 100, 120, 140)) +
-  theme_classic() +
-  ylab("Total Length of Road \n[m, 100m radius]") + 
-  theme(text = element_text(size = 18)) + 
-  theme(axis.text.x=element_text(colour="black", size=18)) + 
-  theme(axis.text.y=element_text(colour="black", size=18),
-        axis.title.x = element_blank()) +
-  theme(legend.position = "none") +
-  annotate(geom="text", x=1.5, y=140, label="***", color="black", size = 10)
-```
-
-```{r road_assumptions, echo = FALSE}
-test_road <- augment(road.nb, data = sites)
-resid_road <- ggplot(test_road, aes(x = .fitted, y = .resid)) + 
-  geom_point() + 
-  geom_smooth() +
-  geom_hline(yintercept = 0) +
-  xlab("Fitted Values") +
-  ylab("Standardized \nResiduals") +
-  theme_classic() +
-  theme(text = element_text(size = 14, color = "black")) +
-  theme(axis.text.x=element_text(color="black", size=14)) + 
-  theme(axis.text.y=element_text(color="black", size=14))
-
-y <- quantile(test_road$.resid, c(0.25, 0.75))
-x <- qnorm(c(0.25, 0.75))
-slope <- diff(y)/diff(x)
-int <- y[1L] - slope * x[1L]
-
-qq_road <- ggplot(test_road, aes(sample = .resid)) + 
-  stat_qq() + 
-  geom_abline(slope = slope, intercept = int) +
-  xlab("Theoretical Quantiles") +
-  ylab("Sample Quantiles") +
-  theme_classic() +
-  theme(text = element_text(size = 14, color = "black")) +
-  theme(axis.text.x=element_text(color="black", size=14)) + 
-  theme(axis.text.y=element_text(color="black", size=14))
-
-ggarrange(resid_road, qq_road, 
-          labels = c("A", "B"),
-          ncol = 2, nrow = 1)
-```
-
-Total road length is **significantly higher in the urban center** than the urban forest (z = -2.74, df = 1, 21, p = 0.006).
-The means and SE's are 15.6 ± 7.54 m for the urban forest and 93.0 ± 40.60 m for the urban center.
-
-## Response Variable: Search Distance
-
-### Search Distance by Location
-
-For this variable, I've gone back and forth on whether I should log-transform the search distance (because it can be ran Gaussian), or whether to use a log-link function (Poisson Distribution).
-The poisson glm more closely matches the mean, but the log-transformation is better at capturing the variance.
-Each step of the way, I have performed each test to try and gauge a best route forward.
-The poisson glm suggests a significant difference while the log-transformed shows no difference.
-
-```{r search_location_stats}
-ggarrange(ggplot(sites, aes(x = WalkDist)) +
-            geom_density(),
-          ggplot(sites, aes(x = log(WalkDist))) +
-            geom_density(), ncol = 2)
-
-shapiro.test(sites$WalkDist) # not normal
-shapiro.test(log(sites$WalkDist)) # normal
-
-search <- glm(WalkDist ~ Location, data = sites, family = poisson)
-summary(search)
-
-search.nb <- glm.nb(WalkDist ~ Location, data = sites)
-summary(search.nb)
-
-search2 <- glm(log(WalkDist) ~ Location, data = sites)
-summary(search2)
-
-sites %>% 
-  group_by(Location) %>% 
-  summarize(mean = mean(WalkDist),
-            se = plotrix::std.error(WalkDist))
-```
-
-```{r search_location_assumptions, echo = FALSE}
-# As is, Poisson
-test_search <- augment(search.nb, data = sites)
-resid_search <- ggplot(test_search, aes(x = .fitted, y = .resid)) + 
-  geom_point() + 
-  geom_smooth() +
-  geom_hline(yintercept = 0) +
-  xlab("Fitted Values") +
-  ylab("Standardized \nResiduals") +
-  theme_classic() +
-  theme(text = element_text(size = 14, color = "black")) +
-  theme(axis.text.x=element_text(color="black", size=14)) + 
-  theme(axis.text.y=element_text(color="black", size=14))
-
-y <- quantile(test_search$.resid, c(0.25, 0.75))
-x <- qnorm(c(0.25, 0.75))
-slope <- diff(y)/diff(x)
-int <- y[1L] - slope * x[1L]
-
-qq_search <- ggplot(test_search, aes(sample = .resid)) + 
-  stat_qq() + 
-  geom_abline(slope = slope, intercept = int) +
-  xlab("Theoretical Quantiles") +
-  ylab("Sample Quantiles") +
-  theme_classic() +
-  theme(text = element_text(size = 14, color = "black")) +
-  theme(axis.text.x=element_text(color="black", size=14)) + 
-  theme(axis.text.y=element_text(color="black", size=14))
-
-scaleloc_search <- ggplot(test_search, aes(x = .fitted, y = sqrt(abs(.std.resid)))) + 
-  geom_point() + 
-  geom_smooth() + 
-  geom_hline(yintercept = 0.83) +
-  xlab("Fitted Values") +
-  ylab("Sqrt Standardized \nResiduals") +
-  theme_classic() +
-  theme(text = element_text(size = 14, color = "black")) +
-  theme(axis.text.x=element_text(color="black", size=14)) + 
-  theme(axis.text.y=element_text(color="black", size=14))
-
-lev_search <- ggplot(test_search, aes(.hat, .std.resid)) +
- geom_vline(colour = "black", xintercept = 0) +
-  geom_hline(colour = "black", yintercept = 0) +
-  geom_point(aes(size = .cooksd)) + geom_smooth(se = FALSE) +
-  xlab("Theoretical Quantiles") +
-  ylab("Sample Quantiles") +
-  labs(size = "Cook's \nDistance") +
-  theme_classic() +
-  theme(text = element_text(size = 14, color = "black")) +
-  theme(axis.text.x=element_text(color="black", size=14)) + 
-  theme(axis.text.y=element_text(color="black", size=14))
-
-ggarrange(resid_search, qq_search, scaleloc_search, lev_search, 
-          labels = c("A", "B", "C", "D"),
-          ncol = 2, nrow = 2)
-
-# Log-transformed, Normal
-test_search2 <- augment(search2, data = sites)
-resid_search2 <- ggplot(test_search2, aes(x = .fitted, y = .resid)) + 
-  geom_point() + 
-  geom_smooth() +
-  geom_hline(yintercept = 0) +
-  xlab("Fitted Values") +
-  ylab("Standardized \nResiduals") +
-  theme_classic() +
-  theme(text = element_text(size = 14, color = "black")) +
-  theme(axis.text.x=element_text(color="black", size=14)) + 
-  theme(axis.text.y=element_text(color="black", size=14))
-
-y <- quantile(test_search2$.resid, c(0.25, 0.75))
-x <- qnorm(c(0.25, 0.75))
-slope <- diff(y)/diff(x)
-int <- y[1L] - slope * x[1L]
-
-qq_search2 <- ggplot(test_search2, aes(sample = .resid)) + 
-  stat_qq() + 
-  geom_abline(slope = slope, intercept = int) +
-  xlab("Theoretical Quantiles") +
-  ylab("Sample Quantiles") +
-  theme_classic() +
-  theme(text = element_text(size = 14, color = "black")) +
-  theme(axis.text.x=element_text(color="black", size=14)) + 
-  theme(axis.text.y=element_text(color="black", size=14))
-
-scaleloc_search2 <- ggplot(test_search2, aes(x = .fitted, y = sqrt(abs(.std.resid)))) + 
-  geom_point() + 
-  geom_smooth() + 
-  geom_hline(yintercept = 0.83) +
-  xlab("Fitted Values") +
-  ylab("Sqrt Standardized \nResiduals") +
-  theme_classic() +
-  theme(text = element_text(size = 14, color = "black")) +
-  theme(axis.text.x=element_text(color="black", size=14)) + 
-  theme(axis.text.y=element_text(color="black", size=14))
-
-lev_search2 <- ggplot(test_search2, aes(.hat, .std.resid)) +
- geom_vline(colour = "black", xintercept = 0) +
-  geom_hline(colour = "black", yintercept = 0) +
-  geom_point(aes(size = .cooksd)) + geom_smooth(se = FALSE) +
-  xlab("Theoretical Quantiles") +
-  ylab("Sample Quantiles") +
-  labs(size = "Cook's \nDistance") +
-  theme_classic() +
-  theme(text = element_text(size = 14, color = "black")) +
-  theme(axis.text.x=element_text(color="black", size=14)) + 
-  theme(axis.text.y=element_text(color="black", size=14))
-
-ggarrange(resid_search2, qq_search2, scaleloc_search2, lev_search2, 
-          labels = c("A", "B", "C", "D"),
-          ncol = 2, nrow = 2)
-```
-
-```{r search_location_graph, echo = FALSE}
-# negative binomial 
-nd <- data.frame(Location = factor(levels(sites$Location)))
-predictions <- augment(search.nb, newdata = nd, se_fit = TRUE, type.predict = "response")
-predictions <- predictions %>% 
-  rename("rate" = ".fitted", "SE" = ".se.fit")
-
-nb_plot_search <- ggplot(sites, aes(x = Location, y = WalkDist)) + 
-  geom_jitter(color = "grey", width = 0.1) +
-  geom_point(aes(x = Location, y = rate, color = Location), size = 2, data = predictions) + 
-  geom_errorbar(aes(x = Location, 
-                  ymin = rate - SE, 
-                  ymax = rate + SE,
-                  color = Location), data = predictions, inherit.aes = FALSE, width = 0.15, size = 1) +
-  scale_color_manual(values = c("Urban Center" = "#d95f02", "Urban Forest" = "#1b9e77")) +
-  scale_x_discrete(labels=c("Urban Forest" = "Urban \nForest \nN = 10", "Urban Center" = "Urban \nCenter \nN = 12")) +
-  theme_classic() +
-  scale_y_continuous(limits = c(0, 275), breaks = c(0, 50, 100, 150, 200, 250)) +
-  xlab("Collection Location") +
-  ylab("Search Distance [m]") + 
-  theme(text = element_text(size = 10)) + 
-  theme(axis.text.x = element_text(colour = "black", size = 10)) + 
-  theme(axis.text.y = element_text(colour = "black", size = 10),
-        axis.title.x = element_blank()) +
-  theme(legend.position = "none") +
-  annotate(geom = "text", x = 1.5, y = 275, label = "N.S.", color = "black", size = 3)
-
-# raw data
-raw <- sites %>% 
-  group_by(Location) %>% 
-  summarise(mean = mean(WalkDist),
-            se = plotrix::std.error(WalkDist))
-
-raw_plot_search <- ggplot(sites, aes(x = Location, y = WalkDist)) + 
-  geom_jitter(color = "grey", width = 0.1) +
-  geom_point(aes(x = Location, y = mean, color = Location), size = 2, data = raw) +
-  geom_errorbar(aes(x= Location, 
-                    ymin = mean - se, 
-                    ymax = mean + se, 
-                    color = Location), data = raw, inherit.aes = FALSE, width = 0.15, size = 1.5) +
-    scale_color_manual(values = c("Urban Center" = "#d95f02", "Urban Forest" = "#1b9e77")) +
-    scale_x_discrete(labels=c("Urban Forest" = "Urban \nForest \nN = 10", "Urban Center" = "Urban \nCenter \nN = 12")) +
-    theme_classic() +
-    scale_y_continuous(limits = c(0, 275), breaks = c(0, 50, 100, 150, 200, 250)) +
-    xlab("Collection Location") +
-    ylab("Search Distance [m]") + 
-    theme(text = element_text(size = 10)) + 
-    theme(axis.text.x = element_text(colour = "black", size = 10)) + 
-    theme(axis.text.y = element_text(colour = "black", size = 10),
-        axis.title.x = element_blank()) +
-    theme(legend.position = "none")
-
-# Non-transformed, poisson distribution
-nd <- data.frame(Location = factor(levels(sites$Location)))
-predictions <- augment(search, newdata = nd, se_fit = TRUE, type.predict = "response")
-predictions <- predictions %>% 
-  rename("rate" = ".fitted", "SE" = ".se.fit")
-#predictions2 <- summary(emmeans(search, ~Location),type = "response")
-
-poisson_plot_search <- ggplot(sites, aes(x = Location, y = WalkDist)) + 
-  geom_jitter(color = "grey", width = 0.1) +
-  geom_point(aes(x = Location, y = rate, color = Location), size = 2, data = predictions) + 
-  geom_errorbar(aes(x = Location, 
-                  ymin = rate - SE, 
-                  ymax = rate + SE,
-                  color = Location), data = predictions, inherit.aes = FALSE, width = 0.15, size = 1.5) +
-  scale_color_manual(values = c("Urban Center" = "#d95f02", "Urban Forest" = "#1b9e77")) +
-  scale_x_discrete(labels=c("Urban Forest" = "Urban \nForest \nN = 10", "Urban Center" = "Urban \nCenter \nN = 12")) +
-  theme_classic() +
-  scale_y_continuous(limits = c(0, 275), breaks = c(0, 50, 100, 150, 200, 250)) +
-  xlab("Collection Location") +
-  ylab("Search Distance [m]") + 
-  theme(text = element_text(size = 10)) + 
-  theme(axis.text.x = element_text(colour = "black", size = 10)) + 
-  theme(axis.text.y = element_text(colour = "black", size = 10),
-        axis.title.x = element_blank()) +
-  theme(legend.position = "none") +
-  annotate(geom = "text", x = 1.5, y = 275, label = "***", color = "black", size = 5)
-
-# Let's look at the log-transformed response variable since that is normal
-nd <- data.frame(Location = factor(levels(sites$Location)))
-predictions2 <- augment(search2, newdata = nd, se_fit = TRUE, type.predict = "response")
-predictions2 <- predictions2 %>% 
-  rename("response" = ".fitted", "SE" = ".se.fit")
-#predictions2 <- summary(emmeans(search2, ~Location),type = "response")
-
-log_plot_search <- ggplot(sites, aes(x = Location, y = (WalkDist))) + 
-  geom_jitter(color = "grey", width = 0.1) +
-  geom_point(aes(x = Location, y = exp(response), color = Location), size = 2, data = predictions2) + 
-  geom_errorbar(aes(x = Location, 
-                  ymin = exp(response - SE), 
-                  ymax = exp(response + SE),
-                  color = Location), data = predictions2, inherit.aes = FALSE, width = 0.15, size = 1.5) +
-  scale_color_manual(values = c("Urban Center" = "#d95f02", "Urban Forest" = "#1b9e77")) +
-  scale_x_discrete(labels=c("Urban Forest" = "Urban \nForest \nN = 10", "Urban Center" = "Urban \nCenter \nN = 12")) +
-  theme_classic() +
-  scale_y_continuous(limits = c(0, 275), breaks = c(0, 50, 100, 150, 200, 250)) +
-  xlab("Collection Location") +
-  ylab("Search Distance [m]") + 
-  theme(text = element_text(size = 10)) + 
-  theme(axis.text.x = element_text(colour = "black", size = 10)) + 
-  theme(axis.text.y = element_text(colour = "black", size = 10),
-        axis.title.x = element_blank()) +
-  theme(legend.position = "none") +
-  annotate(geom = "text", x = 1.5, y = 275, label = "", color = "black", size = 5)
-
-ggarrange(raw_plot_search, 
-          poisson_plot_search, 
-          log_plot_search, 
-          nb_plot_search,
-          labels = c("Raw Data", "Poisson Distribution", "Log-Transformed", "Negative Binamial"),
-          nrow = 1)
-```
-
-Using a negative binomial regression,  **search distance did not significantly differ between habitats** (z = -1.15, df = 1, 20, p = 0.251).
-
-### Search Distance by Predictors
-
-```{r search_predictors_stats}
-# This is one way to look at the overall data, but I think I end up not using this information
-models = list(WalkDist ~ 1,
-              WalkDist ~ log_TotalSub, 
-              WalkDist ~ log_tdr, 
-              WalkDist ~ log_tdh,
-              WalkDist ~ log_TotalSub + log_tdr,
-              WalkDist ~ log_TotalSub + log_tdh,
-              WalkDist ~ log_tdr + log_tdh,
-              WalkDist ~ log_TotalSub + log_tdr + log_tdh)
-fits = lapply(models, glm, data = sites, family = "poisson")
-modnames = sapply(models, function(ff)deparse(ff[[3]]))
-pander(aictab(fits, modname = modnames), caption="Table 1. AICc model selection table for Search Distance to the Focal Web Overall.", split.tables = Inf)
-# The top model keeps all 3 variables and no other model is within 2 Model Likelihood Units
-summary(glm(WalkDist ~ log_TotalSub + log_tdr + log_tdh, data = sites, family = poisson))
-
-global <- glm(WalkDist ~ log_TotalSub + log_tdr + log_tdh, data = sites, family = poisson)
-options(na.action = "na.fail") # Required for dredge to run
-model_dredge <- dredge(global, beta = "none", evaluate = T, rank = AICc)
-options(na.action = "na.omit") # set back to default
-top_model_sd_o <- get.models(model_dredge, subset = 1)[[1]]
-out <- summary(top_model_sd_o)
-out
-info <- out[[12]]
-#TotalSub (log_TotalSub)
-exp(info[4, 1])
-exp(info[4, 2])
-#Traffic_Dist_Road (log_tdr)
-exp(info[3, 1])
-exp(info[3, 2])
-#Traffic_Dist_Highway (log_tdh)
-exp(info[2, 1])
-exp(info[2, 2])
-
-with(summary(top_model_sd_o), 1 - deviance/null.deviance) # This gives the R squared value
-#summary(model.avg(model_dredge, subset = delta <= 2))
-#summary(model.avg(model_dredge))
-model.sel(model_dredge) #estimates same signs
-car::vif(get.models(model_dredge, 1)[[1]]) #looking for less than 2
-
-# urban forest
-global <- glm(WalkDist ~ tree100m + log_TotalSub + log_tdh + log_patch + log_tdr, data = sites_forest, family = poisson)
-options(na.action = "na.fail") # Required for dredge to run
-model_dredge <- dredge(global, beta = "none", evaluate = T, rank = AICc)
-options(na.action = "na.omit") # set back to default
-top_model_sd_f <- get.models(model_dredge, subset = 1)[[1]]
-out <- summary(top_model_sd_f)
-out
-info <- out[[12]]
-#tree100m
-info[5, 1]
-info[5, 2]
-#TotalSub
--exp(info[4, 1])
-exp(info[4, 2])
-#Traffic_Dist_Road
-exp(info[3, 1])
-exp(info[3, 2])
-#Traffic_Dist_Highway
-exp(info[2, 1])
-exp(info[2, 2])
-with(summary(top_model_sd_f), 1 - deviance/null.deviance) # This gives the R squared value
-model.sel(model_dredge) #estimates same signs
-#summary(model.avg(model_dredge, subset = delta <= 2))
-car::vif(get.models(model_dredge, 1)[[1]]) #looking for less than 2
-
-# urban center
-global <- glm(WalkDist ~ log_TotalSub + log_tdr + log_tdh + spec_rad + log_patch + road_length_m, data = sites_center, family = poisson)
-options(na.action = "na.fail") # Required for dredge to run
-model_dredge <- dredge(global, beta = "none", evaluate = T, rank = AICc)
-options(na.action = "na.omit") # set back to default
-top_model_sd_c <- get.models(model_dredge, subset = 1)[[1]]
-out <- summary(top_model_sd_c)
-out
-info <- out[[12]]
-#TotalSub
-exp(info[5, 1])
-exp(info[5, 2])
-#patch_area_km
-exp(info[2, 1])
-exp(info[2, 2])
-#spec_rad
-info[6, 1]
-info[6, 2]
-#Traffic_Dist_Road
-exp(info[4, 1])
-exp(info[4, 2])
-#Traffic_Dist_Highway
-exp(info[3, 1])
-exp(info[3, 2])
-with(summary(top_model_sd_c), 1 - deviance/null.deviance) # This gives the R squared value
-model.sel(model_dredge) #estimates same signs
-#summary(model.avg(model_dredge, subset = delta <= 2))
-car::vif(get.models(model_dredge, 1)[[1]]) # road and highway disturbance between 2 and 3
-```
-
-*Overall*
-Coefficients:
-             Estimate Std. Error z value Pr(>|z|)    
-(Intercept)   2.45699    0.24451  10.049  < 2e-16 ***
-log_tdh       0.21434    0.04469   4.796 1.62e-06 *** **positive**
-log_tdr       0.13279    0.01775   7.480 7.42e-14 *** **positive**
-log_TotalSub  0.31671    0.03252   9.740  < 2e-16 *** **positive**
-
-R-squared = 0.0821148
-
-*Urban Forest*
-Coefficients:
-              Estimate Std. Error z value Pr(>|z|)    
-(Intercept)  -2.962190   0.608574  -4.867 1.13e-06 ***
-log_tdh       1.354582   0.109952  12.320  < 2e-16 *** **positive**
-log_tdr       0.718623   0.038386  18.721  < 2e-16 *** **positive**
-log_TotalSub -1.010040   0.095179 -10.612  < 2e-16 *** **negative**
-tree100m      0.049914   0.004241  11.770  < 2e-16 *** **positive**
-
-R-squared = 0.5328974
-
-*Urban Center*
-Coefficients:
-              Estimate Std. Error z value Pr(>|z|)    
-(Intercept)  -26.90656    2.78649  -9.656  < 2e-16 ***
-log_patch      1.05254    0.05903  17.832  < 2e-16 *** **positive** 
-log_tdh        0.58001    0.09128   6.354 2.10e-10 *** **positive**
-log_tdr        0.45331    0.04386  10.335  < 2e-16 *** **positive**
-log_TotalSub   0.54581    0.08135   6.709 1.96e-11 *** **positive**
-spec_rad       0.12466    0.01458   8.549  < 2e-16 *** **positive**
-
-R-squared = 0.9399876
-
-```{r search_predictors_overall_graphs, echo = FALSE}
-colorc = "#d95f02" 
-colorf = "#1b9e77"
-coloro = "black"
-
-# Plant Species Richness
-nd <- data.frame(log_TotalSub = seq(0, 3.2, 0.03), 
-                 log_tdr = mean(sites$log_tdr), 
-                 log_tdh = mean(sites$log_tdh))
-predicted.distance <- augment(top_model_sd_o, 
-                              newdata = nd, 
-                              se_fit = TRUE)
-search_plant <- ggplot(sites, aes(x = log_TotalSub, y = log(WalkDist))) + 
-  geom_point(color = "grey", 
-             size = 1) +
-  geom_line(aes(x = log_TotalSub, y = .fitted), 
-            size = 1, 
-            color = coloro, 
-            data = predicted.distance) + 
-  geom_ribbon(aes(x = log_TotalSub, 
-                  ymin = .fitted - 1.96 * .se.fit, 
-                  ymax = .fitted + 1.96 * .se.fit), 
-              fill = coloro, 
-              data = predicted.distance, 
-              inherit.aes = FALSE, 
-              alpha = 0.25) +
-  scale_y_continuous(limits = c(min(log(sites$WalkDist)), max(log(sites$WalkDist)) + 0.1 * diff(range(log(sites$WalkDist))))) +  
-  theme_classic() +
-  xlab("Plant Species Richness [log()]") +
-  ylab("Search Distance [log(m)]") + 
-  theme(text = element_text(size = 10)) + 
-  theme(axis.text.x = element_text(colour = "black", size = 10)) + 
-  theme(axis.text.y = element_text(colour = "black", size = 10)) +
-  theme(axis.text.x = element_blank(), 
-        axis.title.x = element_blank(),
-        axis.text.y = element_blank(),
-        axis.title.y = element_blank()) +
-  annotate(geom = "text", x = min(predicted.distance$log_TotalSub) + diff(range(predicted.distance$log_TotalSub))/2, y = max(log(sites$WalkDist)), label = "***", color = "black", size = 4)
-
-# Road Disturbance
-nd <- data.frame(log_TotalSub = mean(sites$log_TotalSub), 
-                 log_tdr = seq(2.7, 7.3, 0.05), 
-                 log_tdh = mean(sites$log_tdh))
-predicted.distance <- augment(top_model_sd_o, 
-                              newdata = nd, 
-                              se_fit = TRUE)
-search_tdr <- ggplot(sites, aes(x = log_tdr, y = log(WalkDist))) + 
-  geom_point(color = "grey", 
-             size = 1) +
-  geom_line(aes(x = log_tdr, y = .fitted), 
-            size = 1, 
-            color = coloro, 
-            data = predicted.distance) + 
-  geom_ribbon(aes(x = log_tdr, 
-                  ymin = .fitted - 1.96 * .se.fit, 
-                  ymax = .fitted + 1.96 * .se.fit), 
-              fill = coloro, 
-              data = predicted.distance, 
-              inherit.aes = FALSE, 
-              alpha = 0.25) +
-  scale_y_continuous(limits = c(min(log(sites$WalkDist)), max(log(sites$WalkDist)) + 0.1 * diff(range(log(sites$WalkDist))))) +  
-  theme_classic() +
-  xlab("Road Disturbance [log(vehicles/day/m)]") +
-  ylab("Search Distance [log(m)]") + 
-  theme(text = element_text(size = 10)) + 
-  theme(axis.text.x = element_text(colour = "black", size = 10)) + 
-  theme(axis.text.y = element_text(colour = "black", size = 10)) +
-  theme(axis.text.x = element_blank(), 
-        axis.title.x = element_blank(),
-        axis.text.y = element_blank(),
-        axis.title.y = element_blank()) +
-  annotate(geom = "text", x = min((predicted.distance$log_tdr)) + diff(range((predicted.distance$log_tdr)))/2, y = max(log(sites$WalkDist)), label = "***", color = "black", size = 4)
-
-# Highway Disturbance
-nd <- data.frame(log_TotalSub = mean(sites$log_TotalSub), 
-                 log_tdr = mean(sites$log_tdr), 
-                 log_tdh = seq(2.7, 5.5, 0.03))
-predicted.distance <- augment(top_model_sd_o, 
-                              newdata = nd, 
-                              se_fit = TRUE)
-search_tdh <- ggplot(sites, aes(x = log_tdh, y = log(WalkDist))) + 
-  geom_point(color = "grey", 
-             size = 1) +
-  geom_line(aes(x = log_tdh, y = .fitted), 
-            size = 1, 
-            color = coloro, 
-            data = predicted.distance) + 
-  geom_ribbon(aes(x = log_tdh, 
-                  ymin = .fitted - 1.96 * .se.fit, 
-                  ymax = .fitted + 1.96 * .se.fit), 
-              fill = coloro, 
-              data = predicted.distance, 
-              inherit.aes = FALSE, 
-              alpha = 0.25) +
-  scale_y_continuous(limits = c(min(log(sites$WalkDist)), max(log(sites$WalkDist)) + 0.1 * diff(range(log(sites$WalkDist))))) +  
-  theme_classic() +
-  xlab("Highway Disturbance [log(vehicles/day/m)]") +
-  ylab("Search Distance [log(m)]") + 
-  theme(text = element_text(size = 10)) + 
-  theme(axis.text.x = element_text(colour = "black", size = 10)) + 
-  theme(axis.text.y = element_text(colour = "black", size = 10)) +
-  theme(axis.text.x = element_blank(), 
-        axis.title.x = element_blank(),
-        axis.text.y = element_blank(),
-        axis.title.y = element_blank()) +
-  annotate(geom = "text", x = min((predicted.distance$log_tdh)) + diff(range((predicted.distance$log_tdh)))/2, y = max(log(sites$WalkDist)), label = "***", color = "black", size = 4)
-
-search_plant
-search_tdr
-search_tdh
-```
-
-```{r search_predictors_forest_graphs, echo = FALSE}
-colorc = "#d95f02" 
-colorf = "#1b9e77"
-coloro = "black"
-
-# Tree
-nd <- data.frame(tree100m = seq(31, 66, 0.3),
-                 log_TotalSub = mean(sites_forest$log_TotalSub), 
-                 log_tdr = mean(sites_forest$log_tdr), 
-                 log_tdh = mean(sites_forest$log_tdh))
-predicted.distance <- augment(top_model_sd_f, 
-                              newdata = nd, 
-                              se_fit = TRUE)
-search_forest_tree <- ggplot(sites_forest, aes(x = (tree100m), y = log(WalkDist))) + 
-  geom_point(color = "grey", 
-             size = 1) +
-  geom_line(aes(x = (tree100m), y = .fitted), 
-            size = 1, 
-            color = colorf, 
-            data = predicted.distance) + 
-  geom_ribbon(aes(x = (tree100m), 
-                  ymin = .fitted - 1.96 * .se.fit, 
-                  ymax = .fitted + 1.96 * .se.fit), 
-              fill = colorf, 
-              data = predicted.distance, 
-              inherit.aes = FALSE, 
-              alpha = 0.25) +
-  scale_y_continuous(limits = c(min(log(sites_forest$WalkDist)), max(log(sites_forest$WalkDist)) + 0.1 * diff(range(log(sites_forest$WalkDist))))) +  
-  theme_classic() +
-  xlab("Percent Tree Cover [%]") +
-  ylab("Search Distance [log(m)]") + 
-  theme(text = element_text(size = 10)) + 
-  theme(axis.text.x = element_text(colour = "black", size = 10)) + 
-  theme(axis.text.y = element_text(colour = "black", size = 10)) +
-  theme(axis.text.x = element_blank(), 
-        axis.title.x = element_blank(),
-        axis.text.y = element_blank(),
-        axis.title.y = element_blank()) +
-  annotate(geom = "text", x = min((predicted.distance$tree100m)) + diff(range((predicted.distance$tree100m)))/2, y = max(log(sites_forest$WalkDist)), label = "***", color = "black", size = 4)
-
-# TotalSub
-nd <- data.frame(tree100m = mean(sites_forest$tree100m),
-                 log_TotalSub = seq(1.94, 3.14, 0.01), 
-                 log_tdr = mean(sites_forest$log_tdr), 
-                 log_tdh = mean(sites_forest$log_tdh))
-predicted.distance <- augment(top_model_sd_f, 
-                              newdata = nd, 
-                              se_fit = TRUE)
-search_forest_plant <- ggplot(sites_forest, aes(x = log_TotalSub, y = log(WalkDist))) + 
-  geom_point(color = "grey", 
-             size = 1) +
-  geom_line(aes(x = log_TotalSub, y = .fitted), 
-            size = 1, 
-            color = colorf, 
-            data = predicted.distance) + 
-  geom_ribbon(aes(x = log_TotalSub, 
-                  ymin = .fitted - 1.96 * .se.fit, 
-                  ymax = .fitted + 1.96 * .se.fit), 
-              fill = colorf, 
-              data = predicted.distance, 
-              inherit.aes = FALSE, 
-              alpha = 0.25) +
-  scale_y_continuous(limits = c(min(log(sites_forest$WalkDist)), max(log(sites_forest$WalkDist)) + 0.1 * diff(range(log(sites_forest$WalkDist))))) +  
-  theme_classic() +
-  xlab("Plant Species Richness [log()]") +
-  ylab("Search Distance [log(m)]") + 
-  theme(text = element_text(size = 10)) + 
-  theme(axis.text.x = element_text(colour = "black", size = 10)) + 
-  theme(axis.text.y = element_text(colour = "black", size = 10)) +
-  theme(axis.text.x = element_blank(), 
-        axis.title.x = element_blank(),
-        axis.text.y = element_blank(),
-        axis.title.y = element_blank()) +
-  annotate(geom = "text", x = min((predicted.distance$log_TotalSub)) + diff(range((predicted.distance$log_TotalSub)))/2, y = max(log(sites_forest$WalkDist)), label = "***", color = "black", size = 4)
-
-# Road Disturbance
-nd <- data.frame(tree100m = mean(sites_forest$tree100m),
-                 log_TotalSub = mean(sites_forest$log_TotalSub), 
-                 log_tdr = seq(2.73, 6.22, 0.03), 
-                 log_tdh = mean(sites_forest$log_tdh))
-predicted.distance <- augment(top_model_sd_f, 
-                              newdata = nd, 
-                              se_fit = TRUE)
-search_forest_tdr <- ggplot(sites_forest, aes(x = log_tdr, y = log(WalkDist))) + 
-  geom_point(color = "grey", 
-             size = 1) +
-  geom_line(aes(x = log_tdr, y = .fitted), 
-            size = 1, 
-            color = colorf, 
-            data = predicted.distance) + 
-  geom_ribbon(aes(x = log_tdr, 
-                  ymin = .fitted - 1.96 * .se.fit, 
-                  ymax = .fitted + 1.96 * .se.fit), 
-              fill = colorf, 
-              data = predicted.distance, 
-              inherit.aes = FALSE, 
-              alpha = 0.25) +
-  scale_y_continuous(limits = c(min(log(sites_forest$WalkDist)), max(log(sites_forest$WalkDist)) + 0.15 * diff(range(log(sites_forest$WalkDist))))) +  
-  theme_classic() +
-  xlab("Road Disturbance [log(vehicles/day/m)]") +
-  ylab("Search Distance [log(m)]") + 
-  theme(text = element_text(size = 10)) + 
-  theme(axis.text.x = element_text(colour = "black", size = 10)) + 
-  theme(axis.text.y = element_text(colour = "black", size = 10)) +
-  theme(axis.text.x = element_blank(), 
-        axis.title.x = element_blank(),
-        axis.text.y = element_blank(),
-        axis.title.y = element_blank()) +
-  annotate(geom = "text", x = min((predicted.distance$log_tdr)) + diff(range((predicted.distance$log_tdr)))/2, y = max(log(sites_forest$WalkDist)), label = "***", color = "black", size = 4)
-
-# Highway Disturbance
-nd <- data.frame(tree100m = mean(sites_forest$tree100m),
-                 log_TotalSub = mean(sites_forest$log_TotalSub), 
-                 log_tdr = mean(sites_forest$log_tdr), 
-                 log_tdh = seq(2.76, 3.89, 0.01))
-predicted.distance <- augment(top_model_sd_f, 
-                              newdata = nd, 
-                              se_fit = TRUE)
-search_forest_tdh <- ggplot(sites_forest, aes(x = log_tdh, y = log(WalkDist))) + 
-  geom_point(color = "grey", 
-             size = 1) +
-  geom_line(aes(x = log_tdh, y = .fitted), 
-            size = 1, 
-            color = colorf, 
-            data = predicted.distance) + 
-  geom_ribbon(aes(x = log_tdh, 
-                  ymin = .fitted - 1.96 * .se.fit, 
-                  ymax = .fitted + 1.96 * .se.fit), 
-              fill = colorf, 
-              data = predicted.distance, 
-              inherit.aes = FALSE, 
-              alpha = 0.25) +
-  scale_y_continuous(limits = c(min(log(sites_forest$WalkDist)), max(log(sites_forest$WalkDist)) + 0.1 * diff(range(log(sites_forest$WalkDist))))) +  
-  theme_classic() +
-  xlab("Highway Disturbance [log(vehicles/day/m)]") +
-  ylab("Search Distance [log(m)]") + 
-  theme(text = element_text(size = 10)) + 
-  theme(axis.text.x = element_text(colour = "black", size = 10)) + 
-  theme(axis.text.y = element_text(colour = "black", size = 10)) +
-  theme(axis.text.x = element_blank(), 
-        axis.title.x = element_blank(),
-        axis.text.y = element_blank(),
-        axis.title.y = element_blank()) +
-  annotate(geom = "text", x = min((predicted.distance$log_tdh)) + diff(range((predicted.distance$log_tdh)))/2, y = max(log(sites_forest$WalkDist)), label = "***", color = "black", size = 4)
-
-search_forest_tree
-search_forest_plant
-search_forest_tdr
-search_forest_tdh
-```
-
-```{r search_predictors_center_graphs, echo = FALSE}
-colorc = "#d95f02" 
-colorf = "#1b9e77"
-coloro = "black"
-
-# Plant Species Richness
-nd <- data.frame(log_TotalSub = seq(0, 1.8, 0.02), 
-                 log_patch = mean(sites_center$log_patch),
-                 spec_rad = mean(sites_center$spec_rad),
-                 log_tdr = mean(sites_center$log_tdr), 
-                 log_tdh = mean(sites_center$log_tdh))
-predicted.distance <- augment(top_model_sd_c, 
-                              newdata = nd, 
-                              se_fit = TRUE)
-search_center_plant <- ggplot(sites_center, aes(x = log_TotalSub, y = log(WalkDist))) + 
-  geom_point(color = "grey", 
-             size = 1) +
-  geom_line(aes(x = log_TotalSub, y = .fitted), 
-            size = 1, 
-            color = colorc, 
-            data = predicted.distance) + 
-  geom_ribbon(aes(x = log_TotalSub, 
-                  ymin = .fitted - 1.96 * .se.fit, 
-                  ymax = .fitted + 1.96 * .se.fit), 
-              fill = colorc, 
-              data = predicted.distance, 
-              inherit.aes = FALSE, 
-              alpha = 0.25) +
-  scale_y_continuous(limits = c(min(log(sites_center$WalkDist)), max(log(sites_center$WalkDist)) + 0.1 * diff(range(log(sites_center$WalkDist))))) +  
-  theme_classic() +
-  xlab("Plant Species Richness [log()]") +
-  ylab("Search Distance [log(m)]") + 
-  theme(text = element_text(size = 10)) + 
-  theme(axis.text.x = element_text(colour = "black", size = 10)) + 
-  theme(axis.text.y = element_text(colour = "black", size = 10)) +
-  theme(axis.text.x = element_blank(), 
-        axis.title.x = element_blank(),
-        axis.text.y = element_blank(),
-        axis.title.y = element_blank()) +
-  annotate(geom = "text", x = min((predicted.distance$log_TotalSub)) + diff(range((predicted.distance$log_TotalSub)))/2, y = max(log(sites_center$WalkDist)), label = "***", color = "black", size = 4)
-
-# Patch Area
-nd <- data.frame(log_TotalSub = mean(sites_center$log_TotalSub), 
-                 log_patch = seq(4.34, 7.52, 0.03),
-                 spec_rad = mean(sites_center$spec_rad),
-                 log_tdr = mean(sites_center$log_tdr), 
-                 log_tdh = mean(sites_center$log_tdh))
-predicted.distance <- augment(top_model_sd_c, 
-                              newdata = nd, 
-                              se_fit = TRUE)
-search_center_patch <- ggplot(sites_center, aes(x = log_patch, y = log(WalkDist))) + 
-  geom_point(color = "grey", 
-             size = 1) +
-  geom_line(aes(x = log_patch, y = .fitted), 
-            size = 1, 
-            color = colorc, 
-            data = predicted.distance) + 
-  geom_ribbon(aes(x = log_patch, 
-                  ymin = .fitted - 1.96 * .se.fit, 
-                  ymax = .fitted + 1.96 * .se.fit), 
-              fill = colorc, 
-              data = predicted.distance, 
-              inherit.aes = FALSE, 
-              alpha = 0.25) +
-  scale_y_continuous(limits = c(min(log(sites_center$WalkDist)) - 0.75, max(log(sites_center$WalkDist)) + 0.15 * diff(range(log(sites_center$WalkDist))))) +  
-  theme_classic() +
-  xlab("Patch Area [log(mm²)]") +
-  ylab("Search Distance [log(m)]") + 
-  theme(text = element_text(size = 10)) + 
-  theme(axis.text.x = element_text(colour = "black", size = 10)) + 
-  theme(axis.text.y = element_text(colour = "black", size = 10)) +
-  theme(axis.text.x = element_blank(), 
-        axis.title.x = element_blank(),
-        axis.text.y = element_blank(),
-        axis.title.y = element_blank()) +
-  annotate(geom = "text", x = min((predicted.distance$log_patch)) + diff(range((predicted.distance$log_patch)))/2, y = max(log(sites_center$WalkDist)), label = "***", color = "black", size = 4)
-
-# Spectral Radiance
-nd <- data.frame(log_TotalSub = mean(sites_center$log_TotalSub), 
-                 log_patch = mean(sites_center$log_patch),
-                 spec_rad = seq(144.36, 162.87, 0.1),
-                 log_tdr = mean(sites_center$log_tdr), 
-                 log_tdh = mean(sites_center$log_tdh))
-predicted.distance <- augment(top_model_sd_c, 
-                              newdata = nd, 
-                              se_fit = TRUE)
-search_center_spec <- ggplot(sites_center, aes(x = (spec_rad), y = log(WalkDist))) + 
-  geom_point(color = "grey", 
-             size = 1) +
-  geom_line(aes(x = (spec_rad), y = .fitted), 
-            size = 1, 
-            color = colorc, 
-            data = predicted.distance) + 
-  geom_ribbon(aes(x = (spec_rad), 
-                  ymin = .fitted - 1.96 * .se.fit, 
-                  ymax = .fitted + 1.96 * .se.fit), 
-              fill = colorc, 
-              data = predicted.distance, 
-              inherit.aes = FALSE, 
-              alpha = 0.25) +
-  scale_y_continuous(limits = c(min(log(sites_center$WalkDist)), max(log(sites_center$WalkDist)) + 0.1 * diff(range(log(sites_center$WalkDist))))) +  
-  theme_classic() +
-  xlab("Spectral Radiance [Watts/(m² * sr * µm)]") +
-  ylab("Search Distance [log(m)]") + 
-  theme(text = element_text(size = 10)) + 
-  theme(axis.text.x = element_text(colour = "black", size = 10)) + 
-  theme(axis.text.y = element_text(colour = "black", size = 10)) +
-  theme(axis.text.x = element_blank(), 
-        axis.title.x = element_blank(),
-        axis.text.y = element_blank(),
-        axis.title.y = element_blank()) +
-  annotate(geom = "text", x = min((predicted.distance$spec_rad)) + diff(range((predicted.distance$spec_rad)))/2, y = max(log(sites_center$WalkDist)), label = "***", color = "black", size = 4)
-
-# Road Disturbance
-nd <- data.frame(log_TotalSub = mean(sites_center$log_TotalSub), 
-                 log_patch = mean(sites_center$log_patch),
-                 spec_rad = mean(sites_center$spec_rad),
-                 log_tdr = seq(3.00, 7.22, 0.04), 
-                 log_tdh = mean(sites_center$log_tdh))
-predicted.distance <- augment(top_model_sd_c, 
-                              newdata = nd, 
-                              se_fit = TRUE)
-search_center_tdr <- ggplot(sites_center, aes(x = log_tdr, y = log(WalkDist))) + 
-  geom_point(color = "grey", 
-             size = 1) +
-  geom_line(aes(x = log_tdr, y = .fitted), 
-            size = 1, 
-            color = colorc, 
-            data = predicted.distance) + 
-  geom_ribbon(aes(x = log_tdr, 
-                  ymin = .fitted - 1.96 * .se.fit, 
-                  ymax = .fitted + 1.96 * .se.fit), 
-              fill = colorc, 
-              data = predicted.distance, 
-              inherit.aes = FALSE, 
-              alpha = 0.25) +
-  scale_y_continuous(limits = c(min(log(sites_center$WalkDist)), max(log(sites_center$WalkDist)) + 0.1 * diff(range(log(sites_center$WalkDist))))) +  
-  theme_classic() +
-  xlab("Road Disturbance [log(vehicles/day/m)]") +
-  ylab("Search Distance [log(m)]") + 
-  theme(text = element_text(size = 10)) + 
-  theme(axis.text.x = element_text(colour = "black", size = 10)) + 
-  theme(axis.text.y = element_text(colour = "black", size = 10)) +
-  theme(axis.text.x = element_blank(), 
-        axis.title.x = element_blank(),
-        axis.text.y = element_blank(),
-        axis.title.y = element_blank()) +
-  annotate(geom = "text", x = min((predicted.distance$log_tdr)) + diff(range((predicted.distance$log_tdr)))/2, y = max(log(sites_center$WalkDist)), label = "***", color = "black", size = 4)
-
-# Highway Disturbance
-nd <- data.frame(log_TotalSub = mean(sites_center$log_TotalSub), 
-                 log_patch = mean(sites_center$log_patch),
-                 spec_rad = mean(sites_center$spec_rad),
-                 log_tdr = mean(sites_center$log_tdr), 
-                 log_tdh = seq(3.32, 5.42, 0.02))
-predicted.distance <- augment(top_model_sd_c, 
-                              newdata = nd, 
-                              se_fit = TRUE)
-search_center_tdh <- ggplot(sites_center, aes(x = log_tdh, y = log(WalkDist))) + 
-  geom_point(color = "grey", 
-             size = 1) +
-  geom_line(aes(x = log_tdh, y = .fitted), 
-            size = 1, 
-            color = colorc, 
-            data = predicted.distance) + 
-  geom_ribbon(aes(x = log_tdh, 
-                  ymin = .fitted - 1.96 * .se.fit, 
-                  ymax = .fitted + 1.96 * .se.fit), 
-              fill = colorc, 
-              data = predicted.distance, 
-              inherit.aes = FALSE, 
-              alpha = 0.25) +
-  scale_y_continuous(limits = c(min(log(sites_center$WalkDist)), max(log(sites_center$WalkDist)) + 0.1 * diff(range(log(sites_center$WalkDist))))) +  
-  theme_classic() +
-  xlab("Highway Disturbance [log(vehicles/day/m)]") +
-  ylab("Search Distance [log(m)]") + 
-  theme(text = element_text(size = 10)) + 
-  theme(axis.text.x = element_text(colour = "black", size = 10)) + 
-  theme(axis.text.y = element_text(colour = "black", size = 10)) +
-  theme(axis.text.x = element_blank(), 
-        axis.title.x = element_blank(),
-        axis.text.y = element_blank(),
-        axis.title.y = element_blank()) +
-  annotate(geom = "text", x = min((predicted.distance$log_tdh)) + diff(range((predicted.distance$log_tdh)))/2, y = max(log(sites_center$WalkDist)), label = "***", color = "black", size = 4)
-
-search_center_plant
-search_center_patch
-search_center_spec
-search_center_tdr
-search_center_tdh
-```
-
-### Search Distance by Land
-
-```{r search_land_stats}
-search_land <- glm(WalkDist ~ Land, data = sites, family = poisson)
-summary(search_land)
-car::Anova(search_land, test.statistic = "LR")
-comp <- glht(search_land, linfct = mcp(Land = "Tukey"))
-summary(comp)
-
-search_land.nb <- glm.nb(WalkDist ~ Land, data = sites)
-summary(search_land.nb)
-car::Anova(search_land.nb, test.statistic = "LR")
-comp <- glht(search_land.nb, linfct = mcp(Land = "Tukey"))
-summary(comp)
-```
-
-```{r search_land_graph}
-#sites <- sites %>% 
-#  mutate(Land = fct_relevel(Land, "Deciduous Forest", 
-#                            "Woody Wetlands", 
-#                            "Urban, High", 
-#                            "Urban, Medium", 
-#                            "Urban, Low"))
-nd <- data.frame(Land = factor(levels(sites$Land)))
-predictions <- augment(search_land.nb, newdata = nd, se_fit = TRUE, type.predict = "response")
-predictions <- predictions %>% 
-  rename("rate" = ".fitted", "SE" = ".se.fit")
-#predictions <- summary(emmeans(search_land, ~Land),type = "response")
-
-search_land_plot <- ggplot(sites, aes(x = Land, y = WalkDist)) + 
-  geom_jitter(color = "grey", width = 0.1, size = 0.5) +
-  geom_point(aes(x = Land, y = rate, color = Land), size = 2, data = predictions) + 
-  geom_errorbar(aes(x = Land, 
-                  ymin = rate - SE, 
-                  ymax = rate + SE, color = Land), data = predictions, inherit.aes = FALSE, width = 0.25, size = 1) +
-  theme_classic() +
-  scale_color_manual(values = c("Deciduous Forest" = "#1b9e77", "Woody Wetlands" = "#1b9e77", "Urban, High" = "#d95f02", "Urban, Medium" = "#d95f02", "Urban, Low" = "#d95f02")) +
-  xlab("Land Cover Class") +
-  ylab("Search Distance [m]") + 
-  theme(text = element_text(size = 10)) + 
-  theme(axis.text.x=element_text(colour="black", size=10)) + 
-  theme(axis.text.y=element_text(colour="black", size=10)) +
-  theme(legend.position = "none") +
-  theme(axis.text.x = element_text(angle = 90, vjust = 1, hjust=1)) #+
-  #annotate(geom="text", x=1, y=max(sites$WalkDist), label="A", color="black", size = 3) +
-  #annotate(geom="text", x=2, y=max(sites$WalkDist), label="B", color="black", size = 3) +
-  #annotate(geom="text", x=3, y=max(sites$WalkDist), label="B", color="black", size = 3) +
-  #annotate(geom="text", x=4, y=max(sites$WalkDist), label="B", color="black", size = 3) +
-  #annotate(geom="text", x=5, y=max(sites$WalkDist), label="C", color="black", size = 3)
-
-search_land_plot
-```
-
-**Search distance does not significantly differ** by land class (Chi = 6.37, df = 4, p = 0.173).
-
-## Response Variable: Number of Webs
-
-### Number of Webs by Location
-
-I also tested Poisson glm vs log-transformation here since log-transformed does help make the data more Gaussian. However, similar results arise in this case.
-
-```{r webs_location_stats}
-ggarrange(ggplot(sites, aes(x = NumWebs)) +
-            geom_density(),
-          ggplot(sites, aes(x = log(NumWebs))) +
-            geom_density(), ncol = 2)
-
-shapiro.test(sites$NumWebs) # not normal
-shapiro.test(log(sites$NumWebs)) # just normal
-
-web <- glm(NumWebs ~ Location, data = sites, family = poisson)
-summary(web)
-
-web.nb <- glm.nb(NumWebs ~ Location, data = sites)
-summary(web.nb)
-
-web2 <- glm(log(NumWebs) ~ Location, data = sites)
-summary(web)
-
-# Both methods yield similar results
-sites %>% 
-  group_by(Location) %>% 
-  summarize(mean = mean(NumWebs),
-            se = plotrix::std.error(NumWebs))
-```
-
-```{r webs_location_assumptions, echo = FALSE}
-# As is, Poisson
-test_webs <- augment(web.nb, data = sites)
-resid_webs <- ggplot(test_webs, aes(x = .fitted, y = .resid)) + 
-  geom_point() + 
-  geom_smooth() +
-  geom_hline(yintercept = 0) +
-  xlab("Fitted Values") +
-  ylab("Standardized \nResiduals") +
-  theme_classic() +
-  theme(text = element_text(size = 14, color = "black")) +
-  theme(axis.text.x=element_text(color="black", size=14)) + 
-  theme(axis.text.y=element_text(color="black", size=14))
-
-y <- quantile(test_webs$.resid, c(0.25, 0.75))
-x <- qnorm(c(0.25, 0.75))
-slope <- diff(y)/diff(x)
-int <- y[1L] - slope * x[1L]
-
-qq_webs <- ggplot(test_webs, aes(sample = .resid)) + 
-  stat_qq() + 
-  geom_abline(slope = slope, intercept = int) +
-  xlab("Theoretical Quantiles") +
-  ylab("Sample Quantiles") +
-  theme_classic() +
-  theme(text = element_text(size = 14, color = "black")) +
-  theme(axis.text.x=element_text(color="black", size=14)) + 
-  theme(axis.text.y=element_text(color="black", size=14))
-
-scaleloc_webs <- ggplot(test_webs, aes(x = .fitted, y = sqrt(abs(.std.resid)))) + 
-  geom_point() + 
-  geom_smooth() + 
-  geom_hline(yintercept = 0.83) +
-  xlab("Fitted Values") +
-  ylab("Sqrt Standardized \nResiduals") +
-  theme_classic() +
-  theme(text = element_text(size = 14, color = "black")) +
-  theme(axis.text.x=element_text(color="black", size=14)) + 
-  theme(axis.text.y=element_text(color="black", size=14))
-
-lev_webs <- ggplot(test_webs, aes(.hat, .std.resid)) +
- geom_vline(colour = "black", xintercept = 0) +
-  geom_hline(colour = "black", yintercept = 0) +
-  geom_point(aes(size = .cooksd)) + geom_smooth(se = FALSE) +
-  xlab("Theoretical Quantiles") +
-  ylab("Sample Quantiles") +
-  labs(size = "Cook's \nDistance") +
-  theme_classic() +
-  theme(text = element_text(size = 14, color = "black")) +
-  theme(axis.text.x=element_text(color="black", size=14)) + 
-  theme(axis.text.y=element_text(color="black", size=14))
-
-ggarrange(resid_webs, qq_webs, scaleloc_webs, lev_webs, 
-          labels = c("A", "B", "C", "D"),
-          ncol = 2, nrow = 2)
-
-# Log-transformed, Normal
-test_webs2 <- augment(web2, data = sites)
-resid_webs2 <- ggplot(test_webs2, aes(x = .fitted, y = .resid)) + 
-  geom_point() + 
-  geom_smooth() +
-  geom_hline(yintercept = 0) +
-  xlab("Fitted Values") +
-  ylab("Standardized \nResiduals") +
-  theme_classic() +
-  theme(text = element_text(size = 14, color = "black")) +
-  theme(axis.text.x=element_text(color="black", size=14)) + 
-  theme(axis.text.y=element_text(color="black", size=14))
-
-y <- quantile(test_webs2$.resid, c(0.25, 0.75))
-x <- qnorm(c(0.25, 0.75))
-slope <- diff(y)/diff(x)
-int <- y[1L] - slope * x[1L]
-
-qq_webs2 <- ggplot(test_webs2, aes(sample = .resid)) + 
-  stat_qq() + 
-  geom_abline(slope = slope, intercept = int) +
-  xlab("Theoretical Quantiles") +
-  ylab("Sample Quantiles") +
-  theme_classic() +
-  theme(text = element_text(size = 14, color = "black")) +
-  theme(axis.text.x=element_text(color="black", size=14)) + 
-  theme(axis.text.y=element_text(color="black", size=14))
-
-scaleloc_webs2 <- ggplot(test_webs2, aes(x = .fitted, y = sqrt(abs(.std.resid)))) + 
-  geom_point() + 
-  geom_smooth() + 
-  geom_hline(yintercept = 0.83) +
-  xlab("Fitted Values") +
-  ylab("Sqrt Standardized \nResiduals") +
-  theme_classic() +
-  theme(text = element_text(size = 14, color = "black")) +
-  theme(axis.text.x=element_text(color="black", size=14)) + 
-  theme(axis.text.y=element_text(color="black", size=14))
-
-lev_webs2 <- ggplot(test_webs2, aes(.hat, .std.resid)) +
- geom_vline(colour = "black", xintercept = 0) +
-  geom_hline(colour = "black", yintercept = 0) +
-  geom_point(aes(size = .cooksd)) + geom_smooth(se = FALSE) +
-  xlab("Theoretical Quantiles") +
-  ylab("Sample Quantiles") +
-  labs(size = "Cook's \nDistance") +
-  theme_classic() +
-  theme(text = element_text(size = 14, color = "black")) +
-  theme(axis.text.x=element_text(color="black", size=14)) + 
-  theme(axis.text.y=element_text(color="black", size=14))
-
-ggarrange(resid_webs2, qq_webs2, scaleloc_webs2, lev_webs2, 
-          labels = c("A", "B", "C", "D"),
-          ncol = 2, nrow = 2)
-```
-
-```{r webs_location_graph, echo = FALSE}
-# negative binomial
-nd <- data.frame(Location = factor(levels(sites$Location)))
-predictions <- augment(web.nb, newdata = nd, se_fit = TRUE, type.predict = "response")
-predictions <- predictions %>% 
-  rename("rate" = ".fitted", "SE" = ".se.fit")
-#predictions <- summary(emmeans(web, ~Location),type = "response")
-
-nb_plot_webs <- ggplot(sites, aes(x = Location, y = NumWebs)) + 
-  geom_jitter(color = "grey", width = 0.1) +
-  geom_point(aes(x = Location, y = rate, color = Location), size = 2, data = predictions) + 
-  geom_errorbar(aes(x = Location, 
-                  ymin = rate - SE, 
-                  ymax = rate + SE,
-                  color = Location), data = predictions, inherit.aes = FALSE, width = 0.15, size = 1) +
-  scale_color_manual(values = c("Urban Center" = "#d95f02", "Urban Forest" = "#1b9e77")) +
-  scale_x_discrete(labels=c("Urban Forest" = "Urban \nForest \nN = 10", "Urban Center" = "Urban \nCenter \nN = 12")) +
-  theme_classic() +
-    scale_y_continuous(limits = c(0, 75), breaks = c(0, 15, 30, 45, 60, 75)) +
-  ylab("Number of Webs") + 
-  theme(text = element_text(size = 10)) + 
-  theme(axis.text.x = element_text(colour = "black", size = 10)) + 
-  theme(axis.text.y = element_text(colour = "black", size = 10),
-        axis.title.x = element_blank()) +
-  theme(legend.position = "none") +
-  annotate(geom = "text", x = 1.5, y = 75, label = "***", color = "black", size = 5)
-
-# raw data
-raw <- sites %>% 
-  group_by(Location) %>% 
-  summarise(mean = mean(NumWebs),
-            se = plotrix::std.error(NumWebs))
-
-raw_plot_webs <- ggplot(sites, aes(x = Location, y = NumWebs)) + 
-  geom_jitter(color = "grey", width = 0.1) +
-  geom_point(aes(x = Location, y = mean, color = Location), size = 2, data = raw) +
-  geom_errorbar(aes(x= Location, 
-                    ymin = mean - se, 
-                    ymax = mean + se, 
-                    color = Location), data = raw, inherit.aes = FALSE, width = 0.15, size = 1.5) +
-    scale_color_manual(values = c("Urban Center" = "#d95f02", "Urban Forest" = "#1b9e77")) +
-    scale_x_discrete(labels=c("Urban Forest" = "Urban \nForest \nN = 10", "Urban Center" = "Urban \nCenter \nN = 12")) +
-    theme_classic() +
-    scale_y_continuous(limits = c(0, 75), breaks = c(0, 15, 30, 45, 60, 75)) +
-    ylab("Number of Webs") + 
-    theme(text = element_text(size = 10)) + 
-    theme(axis.text.x = element_text(colour = "black", size = 10)) + 
-    theme(axis.text.y = element_text(colour = "black", size = 10),
-        axis.title.x = element_blank()) +
-    theme(legend.position = "none")
-
-# Non-transformed, poisson distribution
-nd <- data.frame(Location = factor(levels(sites$Location)))
-predictions <- augment(web, newdata = nd, se_fit = TRUE, type.predict = "response")
-predictions <- predictions %>% 
-  rename("rate" = ".fitted", "SE" = ".se.fit")
-#predictions <- summary(emmeans(web, ~Location),type = "response")
-
-poisson_plot_webs <- ggplot(sites, aes(x = Location, y = NumWebs)) + 
-  geom_jitter(color = "grey", width = 0.1) +
-  geom_point(aes(x = Location, y = rate, color = Location), size = 2, data = predictions) + 
-  geom_errorbar(aes(x = Location, 
-                  ymin = rate - SE, 
-                  ymax = rate + SE,
-                  color = Location), data = predictions, inherit.aes = FALSE, width = 0.15, size = 1.5) +
-  scale_color_manual(values = c("Urban Center" = "#d95f02", "Urban Forest" = "#1b9e77")) +
-  scale_x_discrete(labels=c("Urban Forest" = "Urban \nForest \nN = 10", "Urban Center" = "Urban \nCenter \nN = 12")) +
-  theme_classic() +
-    scale_y_continuous(limits = c(0, 75), breaks = c(0, 15, 30, 45, 60, 75)) +
-  ylab("Number of Webs") + 
-  theme(text = element_text(size = 10)) + 
-  theme(axis.text.x = element_text(colour = "black", size = 10)) + 
-  theme(axis.text.y = element_text(colour = "black", size = 10),
-        axis.title.x = element_blank()) +
-  theme(legend.position = "none") +
-  annotate(geom = "text", x = 1.5, y = 75, label = "***", color = "black", size = 5)
-
-# Let's look at the log-transformed response variable since that is normal
-nd <- data.frame(Location = factor(levels(sites$Location)))
-predictions <- augment(web2, newdata = nd, se_fit = TRUE, type.predict = "response")
-predictions <- predictions %>% 
-  rename("response" = ".fitted", "SE" = ".se.fit")
-#predictions2 <- summary(emmeans(webs2, ~Location),type = "response")
-
-log_plot_webs <- ggplot(sites, aes(x = Location, y = (NumWebs))) + 
-  geom_jitter(color = "grey", width = 0.1) +
-  geom_point(aes(x = Location, y = exp(response), color = Location), size = 2, data = predictions) + 
-  geom_errorbar(aes(x = Location, 
-                  ymin = exp(response - SE), 
-                  ymax = exp(response + SE),
-                  color = Location), data = predictions, inherit.aes = FALSE, width = 0.15, size = 1.5) +
-  scale_color_manual(values = c("Urban Center" = "#d95f02", "Urban Forest" = "#1b9e77")) +
-  scale_x_discrete(labels=c("Urban Forest" = "Urban \nForest \nN = 10", "Urban Center" = "Urban \nCenter \nN = 12")) +
-  theme_classic() +
-    scale_y_continuous(limits = c(0, 75), breaks = c(0, 15, 30, 45, 60, 75)) +
-  ylab("Number of Webs") + 
-  theme(text = element_text(size = 10)) + 
-  theme(axis.text.x = element_text(colour = "black", size = 10)) + 
-  theme(axis.text.y = element_text(colour = "black", size = 10),
-        axis.title.x = element_blank()) +
-  theme(legend.position = "none") +
-  annotate(geom = "text", x = 1.5, y = 75, label = "**", color = "black", size = 5)
-
-ggarrange(raw_plot_webs, 
-          poisson_plot_webs, 
-          log_plot_webs,
-          nb_plot_webs,
-          labels = c("Raw Data", "Poisson Distribution", "Log-Transformed", "Negative Binomial"),
-          nrow = 1)
-```
-
-There were **significantly more webs at sites in the urban center** than the urban forest (z = 4.45, df = 1, 20, p < 0.001).
-
-### Number of Webs by Predictors
-
-```{r webs_predictors_stats}
-# This is one way to look at the overall data, but I think I end up not using this information
-models = list(NumWebs ~ 1,
-              NumWebs ~ log_TotalSub, 
-              NumWebs ~ log_tdr, 
-              NumWebs ~ log_tdh,
-              NumWebs ~ log_TotalSub + log_tdr,
-              NumWebs ~ log_TotalSub + log_tdh,
-              NumWebs ~ log_tdr + log_tdh,
-              NumWebs ~ log_TotalSub + log_tdr + log_tdh)
-fits = lapply(models, glm, data = sites, family = "poisson")
-modnames = sapply(models, function(ff)deparse(ff[[3]]))
-pander(aictab(fits, modname = modnames), caption="Table 1. AICc model selection table for Search Distance to the Focal Web Overall.", split.tables = Inf)
-# The top model keeps all 3 variables and no other model is within 2 Model Likelihood Units
-summary(glm(NumWebs ~ log_TotalSub + log_tdr + log_tdh, data = sites, family = poisson))
-
-global <- glm(NumWebs ~ log_TotalSub + log_tdr + log_tdh, data = sites, family = poisson)
-options(na.action = "na.fail") # Required for dredge to run
-model_dredge <- dredge(global, beta = "none", evaluate = T, rank = AICc)
-options(na.action = "na.omit") # set back to default
-top_model_nw_o <- get.models(model_dredge, subset = 1)[[1]]
-out <- summary(top_model_nw_o)
-out
-info <- out[[12]]
-#TotalSub (log_TotalSub)
-exp(info[4, 1])
-exp(info[4, 2])
-#Traffic_Dist_Road (log_tdr)
-exp(info[3, 1])
-exp(info[3, 2])
-#Traffic_Dist_Highway (log_tdh)
-exp(info[2, 1])
-exp(info[2, 2])
-
-with(summary(top_model_nw_o), 1 - deviance/null.deviance) # This gives the R squared value
-#summary(model.avg(model_dredge, subset = delta <= 2))
-#summary(model.avg(model_dredge))
-model.sel(model_dredge) #estimates same signs
-car::vif(get.models(model_dredge, 1)[[1]]) #looking for less than 2
-
-# urban forest
-global <- glm(NumWebs ~ tree100m + log_TotalSub + log_tdh + log_patch + log_tdr, data = sites_forest, family = poisson)
-options(na.action = "na.fail") # Required for dredge to run
-model_dredge <- dredge(global, beta = "none", evaluate = T, rank = AICc)
-options(na.action = "na.omit") # set back to default
-top_model_nw_f <- get.models(model_dredge, subset = 1)[[1]]
-out <- summary(top_model_nw_f)
-out
-info <- out[[11]]
-with(summary(top_model_nw_f), 1 - deviance/null.deviance) # This gives the R squared value
-model.sel(model_dredge) #estimates same signs
-#summary(model.avg(model_dredge, subset = delta <= 2))
-#car::vif(get.models(model_dredge, 1)[[1]]) #looking for less than 2
-
-# urban center
-global <- glm(NumWebs ~ log_TotalSub + log_tdr + log_tdh + spec_rad + log_patch + road_length_m, data = sites_center, family = poisson)
-options(na.action = "na.fail") # Required for dredge to run
-model_dredge <- dredge(global, beta = "none", evaluate = T, rank = AICc)
-options(na.action = "na.omit") # set back to default
-top_model_nw_c <- get.models(model_dredge, subset = 1)[[1]]
-out <- summary(top_model_nw_c)
-out
-info <- out[[12]]
-#TotalSub
-exp(info[4, 1])
-exp(info[4, 2])
-#patch_area_km
-exp(info[2, 1])
-exp(info[2, 2])
-#Traffic_Dist_Highway
-exp(info[3, 1])
-exp(info[3, 2])
-#road_length
-info[5, 1]
-info[5, 2]
-with(summary(top_model_nw_c), 1 - deviance/null.deviance) # This gives the R squared value
-model.sel(model_dredge) #estimates same signs
-summary(model.avg(model_dredge, subset = delta <= 2))
-# We'll use the conditional average
-#TotalSub
--exp(0.659231)
-exp(0.186648)
-#patch_area_km
--exp(0.293327)
-exp(0.113716)
-#Traffic_Dist_Highway
--exp(1.560993)
-exp(0.192352)
-#road_length_m
--0.021230 
-0.004766
-car::vif(get.models(model_dredge, 1)[[1]]) # looking for values < 2
-```
-
-*Overall*
-Coefficients:
-             Estimate Std. Error z value Pr(>|z|)    
-(Intercept)   7.55449    0.87254   8.658  < 2e-16 ***
-log_tdh      -1.26833    0.19726  -6.430 1.28e-10 *** **negative**
-log_tdr       0.18726    0.04729   3.960 7.49e-05 *** **positive**
-log_TotalSub -1.02619    0.09768 -10.505  < 2e-16 *** **negative**
-
-R-squared = 0.556197
-
-*Urban Forest*
-Coefficients:
-            Estimate Std. Error z value Pr(>|z|)    
-(Intercept)   1.0986     0.1826   6.017 1.77e-09 ***
-
-R-squared = -6.661338e-16
-
-*Urban Center*
-Coefficients:
-               Estimate Std. Error z value Pr(>|z|)    
-(Intercept)   13.145965   1.236110  10.635  < 2e-16 ***
-log_patch     -0.293327   0.113716  -2.579   0.0099 **  **negative**
-log_tdh       -1.539660   0.190172  -8.096 5.67e-16 *** **negative**
-log_TotalSub  -0.717109   0.183835  -3.901 9.59e-05 *** **negative**
-road_length_m -0.022553   0.004713  -4.785 1.71e-06 *** **negative**
-
-R-squared = 0.5814882
-
-(conditional average) 
-               Estimate Std. Error Adjusted SE z value Pr(>|z|)    
-(Intercept)   12.284984   1.481836    1.650697   7.442  < 2e-16 ***
-log_patch     -0.293327   0.113716    0.137194   2.138 0.032513 *   **negative**
-log_tdh       -1.560993   0.192352    0.229029   6.816  < 2e-16 *** **negative**
-log_TotalSub  -0.659231   0.186648    0.218846   3.012 0.002593 **  **negative**
-road_length_m -0.021230   0.004766    0.005608   3.786 0.000153 *** **negative**
-
-```{r webs_predictors_stats_nb}
-global <- glm.nb(NumWebs ~ log_TotalSub + log_tdr + log_tdh, data = sites)
-options(na.action = "na.fail") # Required for dredge to run
-model_dredge <- dredge(global, beta = "none", evaluate = T, rank = AICc)
-options(na.action = "na.omit") # set back to default
-top_model_nw_o <- get.models(model_dredge, subset = 1)[[1]]
-out <- summary(top_model_nw_o)
-out
-info <- out[[12]]
-#TotalSub (log_TotalSub)
-#exp(info[4, 1])
-#exp(info[4, 2])
-#Traffic_Dist_Road (log_tdr)
-#exp(info[3, 1])
-#exp(info[3, 2])
-#Traffic_Dist_Highway (log_tdh)
-#exp(info[2, 1])
-#exp(info[2, 2])
-
-with(summary(top_model_nw_o), 1 - deviance/null.deviance) # This gives the R squared value
-#summary(model.avg(model_dredge, subset = delta <= 2))
-#summary(model.avg(model_dredge))
-model.sel(model_dredge) #estimates same signs
-car::vif(get.models(model_dredge, 1)[[1]]) #looking for less than 2
-
-# urban forest
-global <- glm.nb(NumWebs ~ tree100m + log_TotalSub + log_tdh + log_patch + log_tdr, data = sites_forest)
-options(na.action = "na.fail") # Required for dredge to run
-model_dredge <- dredge(global, beta = "none", evaluate = T, rank = AICc)
-options(na.action = "na.omit") # set back to default
-top_model_nw_f <- get.models(model_dredge, subset = 1)[[1]]
-out <- summary(top_model_nw_f)
-out
-info <- out[[12]]
-with(summary(top_model_nw_f), 1 - deviance/null.deviance) # This gives the R squared value
-model.sel(model_dredge) #estimates same signs
-#summary(model.avg(model_dredge, subset = delta <= 2))
-#car::vif(get.models(model_dredge, 1)[[1]]) #looking for less than 2
-
-# urban center
-global <- glm.nb(NumWebs ~ log_TotalSub + log_tdr + log_tdh + spec_rad + log_patch + road_length_m, data = sites_center)
-options(na.action = "na.fail") # Required for dredge to run
-model_dredge <- dredge(global, beta = "none", evaluate = T, rank = AICc)
-options(na.action = "na.omit") # set back to default
-top_model_nw_c <- get.models(model_dredge, subset = 1)[[1]]
-out <- summary(top_model_nw_c)
-out
-info <- out[[12]]
-#TotalSub
-#exp(info[4, 1])
-#exp(info[4, 2])
-#patch_area_km
-#exp(info[2, 1])
-#exp(info[2, 2])
-#Traffic_Dist_Highway
-#exp(info[3, 1])
-#exp(info[3, 2])
-#road_length
-#info[5, 1]
-#info[5, 2]
-with(summary(top_model_nw_c), 1 - deviance/null.deviance) # This gives the R squared value
-model.sel(model_dredge) #estimates same signs
-summary(model.avg(model_dredge, subset = delta <= 2))
-# We'll use the conditional average
-#TotalSub
-#-exp(0.659231)
-#exp(0.186648)
-#patch_area_km
-#-exp(0.293327)
-#exp(0.113716)
-#Traffic_Dist_Highway
-#-exp(1.560993)
-#exp(0.192352)
-#road_length_m
-#-0.021230 
-#0.004766
-#car::vif(get.models(model_dredge, 1)[[1]]) # looking for values < 2
-```
-
-```{r webs_predictors_overall_graphs, echo = FALSE}
-colorc = "#d95f02" 
-colorf = "#1b9e77"
-coloro = "black"
-
-# Plant Species Richness
-nd <- data.frame(log_TotalSub = seq(0, 3.2, 0.03), 
-                 log_tdh = mean(sites$log_tdh))
-predicted.distance <- augment(top_model_nw_o, 
-                              newdata = nd, 
-                              se_fit = TRUE)
-webs_plant <- ggplot(sites, aes(x = log_TotalSub, y = log(NumWebs))) + 
-  geom_point(aes(color = Location), alpha = 0.7,  
-             size = 1) +
-  geom_line(aes(x = log_TotalSub, y = .fitted), 
-            size = 1, 
-            color = coloro, 
-            data = predicted.distance) + 
-  geom_ribbon(aes(x = log_TotalSub, 
-                  ymin = .fitted - 1.96 * .se.fit, 
-                  ymax = .fitted + 1.96 * .se.fit), 
-              fill = coloro, 
-              data = predicted.distance, 
-              inherit.aes = FALSE, 
-              alpha = 0.25) +
-#  scale_y_continuous(limits = c(min(log(sites$NumWebs)), max(log(sites$NumWebs)) + 0.1 * diff(range(log(sites$NumWebs))))) +  
-  scale_y_continuous(limits = c(-2, 5), breaks = c(-2, 0, 2, 4)) +  
-  scale_color_manual(values = c("Urban Center" = "#d95f02", "Urban Forest" = "#1b9e77")) +
-  theme_classic() +
-  xlab("Plant Species Richness [ln()]") +
-  ylab("Number of Webs [ln()]") + 
-  theme(text = element_text(size = 10)) + 
-  theme(axis.text.x = element_text(colour = "black", size = 10)) + 
-  theme(axis.text.y = element_text(colour = "black", size = 10)) +
-  theme(axis.title.x = element_blank(), 
-        axis.title.y = element_blank(),
-        #axis.text.x = element_blank(),
-        legend.position = "none") + 
-#  theme(axis.text.y = element_blank()) +
-#  annotate(geom = "text", x = min(predicted.distance$log_TotalSub) + diff(range(predicted.distance$log_TotalSub))/2, y = max(log(sites$NumWebs)), label = "***", color = "black", size = 4) +
-  annotate(geom = "text", x = min(predicted.distance$log_TotalSub) + diff(range(predicted.distance$log_TotalSub))/2, y = 4.8, label = "***", color = "black", size = 4)
-
-# Road Disturbance
-#nd <- data.frame(log_TotalSub = mean(sites$log_TotalSub), 
-#                 log_tdr = seq(2.7, 7.3, 0.05), 
-#                 log_tdh = mean(sites$log_tdh))
-#predicted.distance <- augment(top_model_nw_o, 
-#                              newdata = nd, 
-#                              se_fit = TRUE)
-#webs_tdr <- ggplot(sites, aes(x = log_tdr, y = log(NumWebs))) + 
-#  geom_point(color = "grey", 
-#             size = 1) +
-#  geom_line(aes(x = log_tdr, y = .fitted), 
-#            size = 1, 
-#            color = coloro, 
-#            data = predicted.distance) + 
-#  geom_ribbon(aes(x = log_tdr, 
-#                  ymin = .fitted - 1.96 * .se.fit, 
-#                  ymax = .fitted + 1.96 * .se.fit), 
-#              fill = coloro, 
-#              data = predicted.distance, 
-#              inherit.aes = FALSE, 
-#              alpha = 0.25) +
-#  scale_y_continuous(limits = c(min(log(sites$NumWebs)), max(log(sites$NumWebs)) + 0.1 * diff(range(log(sites$NumWebs))))) +  
-#  scale_y_continuous(limits = c(-1.2, 5), breaks = c(-1, 0, 1, 2, 3, 4, 5)) +  
-#  theme_classic() +
-#  xlab("Road Disturbance [log(vehicles/day/m)]") +
-#  ylab("Number of Webs [log()]") + 
-#  theme(text = element_text(size = 10)) + 
-#  theme(axis.text.x = element_text(colour = "black", size = 10)) + 
-#  theme(axis.text.y = element_text(colour = "black", size = 10)) +
-#  theme(axis.title.x = element_blank(), 
-#        axis.title.y = element_blank(), 
-#        axis.text.y = element_blank(),
-#        axis.text.x = element_blank()) + 
-#  annotate(geom = "text", x = min((predicted.distance$log_tdr)) + diff(range((predicted.distance$log_tdr)))/2, y = max(log(sites$NumWebs)), label = "***", color = "black", size = 4) +
-#    annotate(geom = "text", x = min((predicted.distance$log_tdr)) + diff(range((predicted.distance$log_tdr)))/2, y = 4.8, label = "***", color = "black", size = 4)
-
-# Highway Disturbance
-nd <- data.frame(log_TotalSub = mean(sites$log_TotalSub), 
-                 log_tdh = seq(2.7, 5.5, 0.03))
-predicted.distance <- augment(top_model_nw_o, 
-                              newdata = nd, 
-                              se_fit = TRUE)
-webs_tdh <- ggplot(sites, aes(x = log_tdh, y = log(NumWebs))) + 
-  geom_point(aes(color = Location), alpha = 0.7, 
-             size = 1) +
-  geom_line(aes(x = log_tdh, y = .fitted), 
-            size = 1, 
-            color = coloro, 
-            data = predicted.distance) + 
-  geom_ribbon(aes(x = log_tdh, 
-                  ymin = .fitted - 1.96 * .se.fit, 
-                  ymax = .fitted + 1.96 * .se.fit), 
-              fill = coloro, 
-              data = predicted.distance, 
-              inherit.aes = FALSE, 
-              alpha = 0.25) +
-#  scale_y_continuous(limits = c(min(log(sites$NumWebs)) - 1.2, max(log(sites$NumWebs)) + 0.1 * diff(range(log(sites$NumWebs))))) +  
-  scale_y_continuous(limits = c(-2, 5), breaks = c(-2, 0, 2, 4)) +  
-  scale_x_continuous(breaks = c(3, 4, 5)) +  
-  scale_color_manual(values = c("Urban Center" = "#d95f02", "Urban Forest" = "#1b9e77")) +
-  theme_classic() +
-  xlab("Highway Disturbance [ln(vehicles/day/m)]") +
-  ylab("Number of Webs [ln()]") + 
-  theme(text = element_text(size = 10)) + 
-  theme(axis.text.x = element_text(colour = "black", size = 10)) + 
-  theme(axis.text.y = element_text(colour = "black", size = 10)) +
-  theme(axis.title.x = element_blank(), 
-        axis.title.y = element_blank(), 
-        #axis.text.y = element_blank(),
-        #axis.text.x = element_blank(),
-        legend.position = "none") + 
-#  annotate(geom = "text", x = min((predicted.distance$log_tdh)) + diff(range((predicted.distance$log_tdh)))/2, y = max(log(sites$NumWebs)), label = "***", color = "black", size = 4) +
-  annotate(geom = "text", x = min((predicted.distance$log_tdh)) + diff(range((predicted.distance$log_tdh)))/2, y = 4.8, label = "**", color = "black", size = 4)
-
-webs_plant
-#webs_tdr
-webs_tdh
-```
-
-```{r webs_predictors_center_graphs, echo = FALSE}
-colorc = "#d95f02" 
-colorf = "#1b9e77"
-coloro = "black"
-
-# Plant Species Richness
-#nd <- data.frame(log_TotalSub = seq(0, 1.8, 0.02), 
-#                 log_patch = mean(sites_center$log_patch),
-#                 road_length_m = mean(sites_center$road_length_m),
-#                 log_tdh = mean(sites_center$log_tdh))
-#predicted.distance <- augment(top_model_nw_c, 
-#                              newdata = nd, 
-#                              se_fit = TRUE)
-#webs_center_plant <- ggplot(sites_center, aes(x = log_TotalSub, y = log(NumWebs))) + 
-#  geom_point(color = "grey", 
-#             size = 1) +
-#  geom_line(aes(x = log_TotalSub, y = .fitted), 
-#            size = 1, 
-#            color = colorc, 
-#            data = predicted.distance) + 
-#  geom_ribbon(aes(x = log_TotalSub, 
-#                  ymin = .fitted - 1.96 * .se.fit, 
-#                  ymax = .fitted + 1.96 * .se.fit), 
-#              fill = colorc, 
-#              data = predicted.distance, 
-#              inherit.aes = FALSE, 
-#              alpha = 0.25) +
-##  scale_y_continuous(limits = c(min(log(sites_center$NumWebs)), max(log(sites_center$NumWebs)) + 0.1 * diff(range(log(sites_center$NumWebs))))) +  
-#  scale_y_continuous(limits = c(-1.2, 5), breaks = c(-1, 0, 1, 2, 3, 4, 5)) +
-#  theme_classic() +
-#  xlab("Plant Species Richness [log()]") +
-#  ylab("Number of Webs [log()]") + 
-#  theme(text = element_text(size = 10)) + 
-#  theme(axis.text.x = element_text(colour = "black", size = 10)) + 
-#  theme(axis.text.y = element_text(colour = "black", size = 10)) +
-#  theme(axis.title.x = element_blank(), 
-#        axis.title.y = element_blank(), 
-#        axis.text.x = element_blank()) + 
-##  theme(axis.text.y = element_blank()) +
-##  annotate(geom = "text", x = min((predicted.distance$log_TotalSub)) + diff(range((predicted.distance$log_TotalSub)))/2, y = max(log(sites_center$NumWebs)), label = "***", color = "black", size = 4) +
-#  annotate(geom = "text", x = min((predicted.distance$log_TotalSub)) + diff(range((predicted.distance$log_TotalSub)))/2, y = 5, label = "***", color = "black", size = 4)
-
-# Patch Area
-#nd <- data.frame(log_TotalSub = mean(sites_center$log_TotalSub), 
-#                 log_patch = seq(4.34, 7.52, 0.025),
-#                 road_length_m = mean(sites_center$road_length_m),
-#                 log_tdh = mean(sites_center$log_tdh))
-#predicted.distance <- augment(top_model_nw_c, 
-#                              newdata = nd, 
-#                              se_fit = TRUE)
-#webs_center_patch <- ggplot(sites_center, aes(x = log_patch, y = log(NumWebs))) + 
-#  geom_point(color = "grey", 
-#             size = 1) +
-#  geom_line(aes(x = log_patch, y = .fitted), 
-#            size = 1, 
-#            color = colorc, 
-#            data = predicted.distance) + 
-#  geom_ribbon(aes(x = log_patch, 
-#                  ymin = .fitted - 1.96 * .se.fit, 
-#                  ymax = .fitted + 1.96 * .se.fit), 
-#              fill = colorc, 
-#              data = predicted.distance, 
-#              inherit.aes = FALSE, 
-#              alpha = 0.25) +
-##  scale_y_continuous(limits = c(min(log(sites_center$NumWebs)) - 0.75, max(log(sites_center$NumWebs)) + 0.15 * diff(range(log(sites_center$NumWebs))))) +  
-#  scale_y_continuous(limits = c(-1.2, 5), breaks = c(-1, 0, 1, 2, 3, 4, 5)) +
-#  theme_classic() +
-#  xlab("Patch Area [log(mm²)]") +
-#  ylab("Number of Webs [log()]") + 
-#  theme(text = element_text(size = 10)) + 
-#  theme(axis.text.x = element_text(colour = "black", size = 10)) + 
-#  theme(axis.text.y = element_text(colour = "black", size = 10)) +
-#  theme(axis.title.x = element_blank(), 
-#        axis.title.y = element_blank(), 
-#        axis.text.y = element_blank(),
-#        axis.text.x = element_blank()) + 
-##  annotate(geom = "text", x = min((predicted.distance$log_patch)) + diff(range((predicted.distance$log_patch)))/2, y = max(log(sites_center$NumWebs)), label = "**", color = "black", size = 4) +
-#    annotate(geom = "text", x = min((predicted.distance$log_patch)) + diff(range((predicted.distance$log_patch)))/2, y = 5, label = "**", color = "black", size = 4)
-
-# Highway Disturbance
-nd <- data.frame(log_tdh = seq(3.32, 5.42, 0.02))
-predicted.distance <- augment(top_model_nw_c, 
-                              newdata = nd, 
-                              se_fit = TRUE)
-webs_center_tdh <- ggplot(sites, aes(x = log_tdh, y = log(NumWebs))) + 
-  geom_point(aes(color = Location), alpha = 0.5, 
-             size = 1) +
-  geom_line(aes(x = log_tdh, y = .fitted), 
-            size = 1, 
-            color = colorc, 
-            data = predicted.distance) + 
-  geom_ribbon(aes(x = log_tdh, 
-                  ymin = .fitted - 1.96 * .se.fit, 
-                  ymax = .fitted + 1.96 * .se.fit), 
-              fill = colorc, 
-              data = predicted.distance, 
-              inherit.aes = FALSE, 
-              alpha = 0.25) +
-#  scale_y_continuous(limits = c(min(log(sites_center$NumWebs)) - 0.75, max(log(sites_center$NumWebs)) + 0.1 * diff(range(log(sites_center$NumWebs))))) +  
-  scale_y_continuous(limits = c(-2, 5), breaks = c(-2, 0, 2, 4)) +  
-  scale_x_continuous(breaks = c(3, 4, 5)) +  
-  scale_color_manual(values = c("Urban Center" = "#d95f02", "Urban Forest" = "#1b9e77")) +
-  theme_classic() +
-  xlab("Highway Disturbance [ln(vehicles/day/m)]") +
-  ylab("Number of Webs [ln()]") + 
-  theme(text = element_text(size = 10)) + 
-  theme(axis.text.x = element_text(colour = "black", size = 10)) + 
-  theme(axis.text.y = element_text(colour = "black", size = 10)) +
-  theme(axis.title.x = element_blank(), 
-        axis.title.y = element_blank(),
-        legend.position = "none") + 
-        #axis.text.y = element_blank(),
-        #axis.text.x = element_blank()) + 
-#  annotate(geom = "text", x = min((predicted.distance$log_tdh)) + diff(range((predicted.distance$log_tdh)))/2, y = max(log(sites_center$NumWebs)), label = "***", color = "black", size = 4) +
-  annotate(geom = "text", x = 4, y = 5, label = "*", color = "black", size = 4)
-
-# Road Length
-#nd <- data.frame(log_TotalSub = mean(sites_center$log_TotalSub), 
-#                 log_patch = mean(sites_center$log_patch),
-#                 road_length_m = seq(47, 136, 1),
-#                 log_tdh = mean(sites_center$log_tdh))
-#predicted.distance <- augment(top_model_nw_c, 
-#                              newdata = nd, 
-#                              se_fit = TRUE)
-#webs_center_road <- ggplot(sites_center, aes(x = (road_length_m), y = log(NumWebs))) + 
-#  geom_point(color = "grey", 
-#             size = 1) +
-#  geom_line(aes(x = (road_length_m), y = .fitted), 
-#            size = 1, 
-#            color = colorc, 
-#            data = predicted.distance) + 
-#  geom_ribbon(aes(x = (road_length_m), 
-#                  ymin = .fitted - 1.96 * .se.fit, 
-#                  ymax = .fitted + 1.96 * .se.fit), 
-#              fill = colorc, 
-#              data = predicted.distance, 
-#              inherit.aes = FALSE, 
-#              alpha = 0.25) +
-##  scale_y_continuous(limits = c(min(log(sites_center$NumWebs)), max(log(sites_center$NumWebs)) + 0.1 * diff(range(log(sites_center$NumWebs))))) +
-#  scale_y_continuous(limits = c(-1.2, 5), breaks = c(-1, 0, 1, 2, 3, 4, 5)) +
-#  theme_classic() +
-#  xlab("Total Road Length [m]") +
-#  ylab("Number of Webs [log()]") + 
-#  theme(text = element_text(size = 10)) + 
-#  theme(axis.text.x = element_text(colour = "black", size = 10)) + 
-#  theme(axis.text.y = element_text(colour = "black", size = 10)) +
-#  theme(axis.title.x = element_blank(), 
-#        axis.title.y = element_blank(), 
-#        axis.text.y = element_blank(),
-#        axis.text.x = element_blank()) + 
-##  annotate(geom = "text", x = min((predicted.distance$road_length_m)) + diff(range((predicted.distance$road_length_m)))/2, y = max(log(sites_center$NumWebs)), label = "***", color = "black", size = 4) +
-#  annotate(geom = "text", x = min((predicted.distance$road_length_m)) + diff(range((predicted.distance$road_length_m)))/2, y = 5, label = "***", color = "black", size = 4)
-
-#webs_center_plant
-#webs_center_patch
-#webs_center_road
-webs_center_tdh
-```
-
-### Number of Webs by Land
-
-```{r webs_land_stats}
-webs_land <- glm(NumWebs ~ Land, data = sites, family = poisson)
-summary(webs_land)
-car::Anova(webs_land, test.statistic = "LR")
-comp <- glht(webs_land, linfct = mcp(Land = "Tukey"))
-summary(comp)
-
-webs_land_nb <- glm.nb(NumWebs ~ Land, data = sites)
-summary(webs_land_nb)
-car::Anova(webs_land_nb, test.statistic = "LR")
-comp <- glht(webs_land_nb, linfct = mcp(Land = "Tukey"))
-summary(comp)
-```
-
-```{r webs_land_graph}
-#sites <- sites %>% 
-#  mutate(Land = fct_relevel(Land, "Deciduous Forest", 
-#                            "Woody Wetlands", 
-#                            "Urban, High", 
-#                            "Urban, Medium", 
-#                            "Urban, Low"))
-nd <- data.frame(Land = factor(levels(sites$Land)))
-predictions <- augment(webs_land_nb, newdata = nd, se_fit = TRUE, type.predict = "response")
-predictions <- predictions %>% 
-  rename("rate" = ".fitted", "SE" = ".se.fit")
-#predictions <- summary(emmeans(webs_land, ~Land),type = "response")
-
-webs_land_plot <- ggplot(sites, aes(x = Land, y = NumWebs)) + 
-  geom_jitter(color = "grey", width = 0.1, size = 0.5) +
-  geom_point(aes(x = Land, y = rate, color = Land), size = 2, data = predictions) + 
-  geom_errorbar(aes(x = Land, 
-                  ymin = rate - SE, 
-                  ymax = rate + SE, color = Land), data = predictions, inherit.aes = FALSE, width = 0.25, size = 1) +
-  theme_classic() +
-  scale_color_manual(values = c("Deciduous Forest" = "#1b9e77", "Woody Wetlands" = "#1b9e77", "Urban, High" = "#d95f02", "Urban, Medium" = "#d95f02", "Urban, Low" = "#d95f02")) +
-  xlab("Land Cover Class") +
-  ylab("Number of Webs") + 
-  theme(text = element_text(size = 10)) + 
-  theme(axis.text.x=element_text(colour="black", size=10)) + 
-  theme(axis.text.y=element_text(colour="black", size=10)) +
-  theme(legend.position = "none") +
-  theme(axis.text.x = element_text(angle = 90, vjust = 1, hjust=1))# +
-  #annotate(geom="text", x=1, y=max(sites$NumWebs), label="A", color="black", size = 3) +
-  #annotate(geom="text", x=2, y=max(sites$NumWebs), label="A", color="black", size = 3) +
-  #annotate(geom="text", x=3, y=max(sites$NumWebs), label="A", color="black", size = 3) +
-  #annotate(geom="text", x=4, y=max(sites$NumWebs), label="B", color="black", size = 3) +
-  #annotate(geom="text", x=5, y=max(sites$NumWebs), label="B", color="black", size = 3)
-
-webs_land_plot_nox <- webs_land_plot + 
-  theme(axis.text.x = element_blank()) + 
-  theme(axis.title.x = element_blank())
-
-webs_land_plot
-```
-
-The **number of webs significantly varies** by land cover class (chi = 19.13, df = 4, p < 0.001).
-
-## Response Variable: Number of Spiders
-
-### Number of Spiders by Location
-
-```{r spiders_location_stats}
-ggarrange(ggplot(sites, aes(x = NumSpiders)) +
-            geom_density(),
-          ggplot(sites, aes(x = log(NumSpiders))) +
-            geom_density(), ncol = 2)
-
-shapiro.test(sites$NumSpiders) # not normal
-shapiro.test(log(sites$NumSpiders)) # not normal
-
-spiders <- glm(NumSpiders ~ Location, data = sites, family = poisson)
-summary(spiders)
-
-spiders.nb <- glm.nb(NumSpiders ~ Location, data = sites)
-summary(spiders.nb)
-
-spiders2 <- glm(log(NumSpiders) ~ Location, data = sites)
-summary(spiders2)
-
-# Both methods yield similar results
-sites %>% 
-  group_by(Location) %>% 
-  summarize(mean = mean(NumSpiders),
-            se = plotrix::std.error(NumSpiders))
-```
-
-```{r spiders_location_assumptions, echo = FALSE}
-# As is, Poisson
-test_spiders <- augment(spiders.nb, data = sites)
-resid_spiders <- ggplot(test_spiders, aes(x = .fitted, y = .resid)) + 
-  geom_point() + 
-  geom_smooth() +
-  geom_hline(yintercept = 0) +
-  xlab("Fitted Values") +
-  ylab("Standardized \nResiduals") +
-  theme_classic() +
-  theme(text = element_text(size = 14, color = "black")) +
-  theme(axis.text.x=element_text(color="black", size=14)) + 
-  theme(axis.text.y=element_text(color="black", size=14))
-
-y <- quantile(test_spiders$.resid, c(0.25, 0.75))
-x <- qnorm(c(0.25, 0.75))
-slope <- diff(y)/diff(x)
-int <- y[1L] - slope * x[1L]
-
-qq_spiders <- ggplot(test_spiders, aes(sample = .resid)) + 
-  stat_qq() + 
-  geom_abline(slope = slope, intercept = int) +
-  xlab("Theoretical Quantiles") +
-  ylab("Sample Quantiles") +
-  theme_classic() +
-  theme(text = element_text(size = 14, color = "black")) +
-  theme(axis.text.x=element_text(color="black", size=14)) + 
-  theme(axis.text.y=element_text(color="black", size=14))
-
-scaleloc_spiders <- ggplot(test_spiders, aes(x = .fitted, y = sqrt(abs(.std.resid)))) + 
-  geom_point() + 
-  geom_smooth() + 
-  geom_hline(yintercept = 0.83) +
-  xlab("Fitted Values") +
-  ylab("Sqrt Standardized \nResiduals") +
-  theme_classic() +
-  theme(text = element_text(size = 14, color = "black")) +
-  theme(axis.text.x=element_text(color="black", size=14)) + 
-  theme(axis.text.y=element_text(color="black", size=14))
-
-lev_spiders <- ggplot(test_spiders, aes(.hat, .std.resid)) +
- geom_vline(colour = "black", xintercept = 0) +
-  geom_hline(colour = "black", yintercept = 0) +
-  geom_point(aes(size = .cooksd)) + geom_smooth(se = FALSE) +
-  xlab("Theoretical Quantiles") +
-  ylab("Sample Quantiles") +
-  labs(size = "Cook's \nDistance") +
-  theme_classic() +
-  theme(text = element_text(size = 14, color = "black")) +
-  theme(axis.text.x=element_text(color="black", size=14)) + 
-  theme(axis.text.y=element_text(color="black", size=14))
-
-ggarrange(resid_spiders, qq_spiders, scaleloc_spiders, lev_spiders, 
-          labels = c("A", "B", "C", "D"),
-          ncol = 2, nrow = 2)
-
-# Log-transformed, Normal
-test_spiders2 <- augment(spiders2, data = sites)
-resid_spiders2 <- ggplot(test_spiders2, aes(x = .fitted, y = .resid)) + 
-  geom_point() + 
-  geom_smooth() +
-  geom_hline(yintercept = 0) +
-  xlab("Fitted Values") +
-  ylab("Standardized \nResiduals") +
-  theme_classic() +
-  theme(text = element_text(size = 14, color = "black")) +
-  theme(axis.text.x=element_text(color="black", size=14)) + 
-  theme(axis.text.y=element_text(color="black", size=14))
-
-y <- quantile(test_spiders2$.resid, c(0.25, 0.75))
-x <- qnorm(c(0.25, 0.75))
-slope <- diff(y)/diff(x)
-int <- y[1L] - slope * x[1L]
-
-qq_spiders2 <- ggplot(test_spiders2, aes(sample = .resid)) + 
-  stat_qq() + 
-  geom_abline(slope = slope, intercept = int) +
-  xlab("Theoretical Quantiles") +
-  ylab("Sample Quantiles") +
-  theme_classic() +
-  theme(text = element_text(size = 14, color = "black")) +
-  theme(axis.text.x=element_text(color="black", size=14)) + 
-  theme(axis.text.y=element_text(color="black", size=14))
-
-scaleloc_spiders2 <- ggplot(test_spiders2, aes(x = .fitted, y = sqrt(abs(.std.resid)))) + 
-  geom_point() + 
-  geom_smooth() + 
-  geom_hline(yintercept = 0.83) +
-  xlab("Fitted Values") +
-  ylab("Sqrt Standardized \nResiduals") +
-  theme_classic() +
-  theme(text = element_text(size = 14, color = "black")) +
-  theme(axis.text.x=element_text(color="black", size=14)) + 
-  theme(axis.text.y=element_text(color="black", size=14))
-
-lev_spiders2 <- ggplot(test_spiders2, aes(.hat, .std.resid)) +
- geom_vline(colour = "black", xintercept = 0) +
-  geom_hline(colour = "black", yintercept = 0) +
-  geom_point(aes(size = .cooksd)) + geom_smooth(se = FALSE) +
-  xlab("Theoretical Quantiles") +
-  ylab("Sample Quantiles") +
-  labs(size = "Cook's \nDistance") +
-  theme_classic() +
-  theme(text = element_text(size = 14, color = "black")) +
-  theme(axis.text.x=element_text(color="black", size=14)) + 
-  theme(axis.text.y=element_text(color="black", size=14))
-
-ggarrange(resid_spiders2, qq_spiders2, scaleloc_spiders2, lev_spiders2, 
-          labels = c("A", "B", "C", "D"),
-          ncol = 2, nrow = 2)
-```
-
-```{r spiders_location_graph, echo = FALSE}
-# Negative Binomial
-nd <- data.frame(Location = factor(levels(sites$Location)))
-predictions <- augment(spiders.nb, newdata = nd, se_fit = TRUE, type.predict = "response")
-predictions <- predictions %>% 
-  rename("rate" = ".fitted", "SE" = ".se.fit")
-#predictions <- summary(emmeans(spiders, ~Location),type = "response")
-
-nb_plot_spiders <- ggplot(sites, aes(x = Location, y = NumSpiders)) + 
-  geom_jitter(color = "grey", width = 0.1) +
-  geom_point(aes(x = Location, y = rate, color = Location), size = 2, data = predictions) + 
-  geom_errorbar(aes(x = Location, 
-                  ymin = rate - SE, 
-                  ymax = rate + SE,
-                  color = Location), data = predictions, inherit.aes = FALSE, width = 0.15, size = 1) +
-  scale_color_manual(values = c("Urban Center" = "#d95f02", "Urban Forest" = "#1b9e77")) +
-  scale_x_discrete(labels=c("Urban Forest" = "Urban \nForest \nN = 10", "Urban Center" = "Urban \nCenter \nN = 12")) +
-  theme_classic() +
-    scale_y_continuous(limits = c(0, 25), breaks = c(0, 5, 10, 15, 20, 25)) +
-  ylab("Number of Spiders") + 
-  theme(text = element_text(size = 10)) + 
-  theme(axis.text.x = element_text(colour = "black", size = 10)) + 
-  theme(axis.text.y = element_text(colour = "black", size = 10),
-        axis.title.x = element_blank()) +
-  theme(legend.position = "none") +
-  annotate(geom = "text", x = 1.5, y = 25, label = "**", color = "black", size = 5)
-
-# raw data
-raw <- sites %>% 
-  group_by(Location) %>% 
-  summarise(mean = mean(NumSpiders),
-            se = plotrix::std.error(NumSpiders))
-
-raw_plot_spiders <- ggplot(sites, aes(x = Location, y = NumSpiders)) + 
-  geom_jitter(color = "grey", width = 0.1) +
-  geom_point(aes(x = Location, y = mean, color = Location), size = 2, data = raw) +
-  geom_errorbar(aes(x= Location, 
-                    ymin = mean - se, 
-                    ymax = mean + se, 
-                    color = Location), data = raw, inherit.aes = FALSE, width = 0.15, size = 1.5) +
-    scale_color_manual(values = c("Urban Center" = "#d95f02", "Urban Forest" = "#1b9e77")) +
-    scale_x_discrete(labels=c("Urban Forest" = "Urban \nForest \nN = 10", "Urban Center" = "Urban \nCenter \nN = 12")) +
-    theme_classic() +
-    scale_y_continuous(limits = c(0, 25), breaks = c(0, 5, 10, 15, 20, 25)) +
-    ylab("Number of Spiders") + 
-    theme(text = element_text(size = 10)) + 
-    theme(axis.text.x = element_text(colour = "black", size = 10)) + 
-    theme(axis.text.y = element_text(colour = "black", size = 10),
-        axis.title.x = element_blank()) +
-    theme(legend.position = "none")
-
-# Non-transformed, poisson distribution
-nd <- data.frame(Location = factor(levels(sites$Location)))
-predictions <- augment(spiders, newdata = nd, se_fit = TRUE, type.predict = "response")
-predictions <- predictions %>% 
-  rename("rate" = ".fitted", "SE" = ".se.fit")
-#predictions <- summary(emmeans(spiders, ~Location),type = "response")
-
-poisson_plot_spiders <- ggplot(sites, aes(x = Location, y = NumSpiders)) + 
-  geom_jitter(color = "grey", width = 0.1) +
-  geom_point(aes(x = Location, y = rate, color = Location), size = 2, data = predictions) + 
-  geom_errorbar(aes(x = Location, 
-                  ymin = rate - SE, 
-                  ymax = rate + SE,
-                  color = Location), data = predictions, inherit.aes = FALSE, width = 0.15, size = 1.5) +
-  scale_color_manual(values = c("Urban Center" = "#d95f02", "Urban Forest" = "#1b9e77")) +
-  scale_x_discrete(labels=c("Urban Forest" = "Urban \nForest \nN = 10", "Urban Center" = "Urban \nCenter \nN = 12")) +
-  theme_classic() +
-    scale_y_continuous(limits = c(0, 25), breaks = c(0, 5, 10, 15, 20, 25)) +
-  ylab("Number of Spiders") + 
-  theme(text = element_text(size = 10)) + 
-  theme(axis.text.x = element_text(colour = "black", size = 10)) + 
-  theme(axis.text.y = element_text(colour = "black", size = 10),
-        axis.title.x = element_blank()) +
-  theme(legend.position = "none") +
-  annotate(geom = "text", x = 1.5, y = 25, label = "***", color = "black", size = 5)
-
-# Let's look at the log-transformed response variable since that is normal
-nd <- data.frame(Location = factor(levels(sites$Location)))
-predictions <- augment(spiders2, newdata = nd, se_fit = TRUE, type.predict = "response")
-predictions <- predictions %>% 
-  rename("response" = ".fitted", "SE" = ".se.fit")
-#predictions2 <- summary(emmeans(webs2, ~Location),type = "response")
-
-log_plot_spiders <- ggplot(sites, aes(x = Location, y = (NumSpiders))) + 
-  geom_jitter(color = "grey", width = 0.1) +
-  geom_point(aes(x = Location, y = exp(response), color = Location), size = 2, data = predictions) + 
-  geom_errorbar(aes(x = Location, 
-                  ymin = exp(response - SE), 
-                  ymax = exp(response + SE),
-                  color = Location), data = predictions, inherit.aes = FALSE, width = 0.15, size = 1.5) +
-  scale_color_manual(values = c("Urban Center" = "#d95f02", "Urban Forest" = "#1b9e77")) +
-  scale_x_discrete(labels=c("Urban Forest" = "Urban \nForest \nN = 10", "Urban Center" = "Urban \nCenter \nN = 12")) +
-  theme_classic() +
-    scale_y_continuous(limits = c(0, 25), breaks = c(0, 5, 10, 15, 20, 25)) +
-  ylab("Number of Spiders") + 
-  theme(text = element_text(size = 10)) + 
-  theme(axis.text.x = element_text(colour = "black", size = 10)) + 
-  theme(axis.text.y = element_text(colour = "black", size = 10),
-        axis.title.x = element_blank()) +
-  theme(legend.position = "none") +
-  annotate(geom = "text", x = 1.5, y = 25, label = ".", color = "black", size = 5)
-
-ggarrange(raw_plot_spiders, 
-          poisson_plot_spiders, 
-          log_plot_spiders, 
-          nb_plot_spiders,
-          labels = c("Raw Data", "Poisson Distribution", "Log-Transformed", "Negative Binomial"),
-          nrow = 1)
-```
-
-The **number of spiders present by site is significantly higher in the urban center** (z = 3.13, df = 1, 20, p = 0.002).
-
-### Number of Spiders by Predictors
-
-```{r spiders_predictors_stats}
-# This is one way to look at the overall data, but I think I end up not using this information
-models = list(NumSpiders ~ 1,
-              NumSpiders ~ log_TotalSub, 
-              NumSpiders ~ log_tdr, 
-              NumSpiders ~ log_tdh,
-              NumSpiders ~ log_TotalSub + log_tdr,
-              NumSpiders ~ log_TotalSub + log_tdh,
-              NumSpiders ~ log_tdr + log_tdh,
-              NumSpiders ~ log_TotalSub + log_tdr + log_tdh)
-fits = lapply(models, glm, data = sites, family = "poisson")
-modnames = sapply(models, function(ff)deparse(ff[[3]]))
-pander(aictab(fits, modname = modnames), caption="Table 1. AICc model selection table for Search Distance to the Focal Web Overall.", split.tables = Inf)
-# The top model keeps all 3 variables and no other model is within 2 Model Likelihood Units
-summary(glm(NumSpiders ~ log_TotalSub + log_tdr + log_tdh, data = sites, family = poisson))
-
-global <- glm(NumSpiders ~ log_TotalSub + log_tdr + log_tdh, data = sites, family = poisson)
-options(na.action = "na.fail") # Required for dredge to run
-model_dredge <- dredge(global, beta = "none", evaluate = T, rank = AICc)
-options(na.action = "na.omit") # set back to default
-top_model_ns_o <- get.models(model_dredge, subset = 1)[[1]]
-out <- summary(top_model_ns_o)
-out
-info <- out[[12]]
-#TotalSub (log_TotalSub)
-exp(info[3, 1])
-exp(info[3, 2])
-#Traffic_Dist_Highway (log_tdh)
-exp(info[2, 1])
-exp(info[2, 2])
-
-with(summary(top_model_ns_o), 1 - deviance/null.deviance) # This gives the R squared value
-#summary(model.avg(model_dredge, subset = delta <= 2))
-#summary(model.avg(model_dredge))
-model.sel(model_dredge) #estimates same signs
-car::vif(get.models(model_dredge, 1)[[1]]) #looking for less than 2
-
-# urban forest
-global <- glm(NumSpiders ~ tree100m + log_TotalSub + log_tdh + log_patch + log_tdr, data = sites_forest, family = poisson)
-options(na.action = "na.fail") # Required for dredge to run
-model_dredge <- dredge(global, beta = "none", evaluate = T, rank = AICc)
-options(na.action = "na.omit") # set back to default
-top_model_ns_f <- get.models(model_dredge, subset = 1)[[1]]
-out <- summary(top_model_ns_f)
-out
-info <- out[[12]]
-with(summary(top_model_ns_f), 1 - deviance/null.deviance) # This gives the R squared value
-model.sel(model_dredge) #estimates same signs
-#summary(model.avg(model_dredge, subset = delta <= 2))
-#car::vif(get.models(model_dredge, 1)[[1]]) #looking for less than 2
-
-# urban center
-global <- glm(NumSpiders ~ log_TotalSub + log_tdr + log_tdh + spec_rad + log_patch + road_length_m, data = sites_center, family = poisson)
-options(na.action = "na.fail") # Required for dredge to run
-model_dredge <- dredge(global, beta = "none", evaluate = T, rank = AICc)
-options(na.action = "na.omit") # set back to default
-top_model_ns_c <- get.models(model_dredge, subset = 1)[[1]]
-out <- summary(top_model_ns_c)
-out
-info <- out[[12]]
-#TotalSub
-exp(info[4, 1])
-exp(info[4, 2])
-#patch_area_km
-exp(info[2, 1])
-exp(info[2, 2])
-#Traffic_Dist_Highway
-exp(info[3, 1])
-exp(info[3, 2])
-#road_length
-info[5, 1]
-info[5, 2]
-with(summary(top_model_ns_c), 1 - deviance/null.deviance) # This gives the R squared value
-model.sel(model_dredge) #estimates same signs
-#summary(model.avg(model_dredge, subset = delta <= 2))
-car::vif(get.models(model_dredge, 1)[[1]]) # looking for values < 2
-```
-
-*Overall*
-Coefficients:
-             Estimate Std. Error z value Pr(>|z|)    
-(Intercept)    7.3234     1.1068   6.617 3.67e-11 ***
-log_tdh       -1.1932     0.2785  -4.284 1.84e-05 *** **negative**
-log_TotalSub  -0.9523     0.1370  -6.952 3.61e-12 *** **negative**
-
-R-squared = 0.5363275
-
-*Urban Forest*
-Coefficients:
-            Estimate Std. Error z value Pr(>|z|)   
-(Intercept)   0.6419     0.2294   2.798  0.00515 **
-
-R-squared = -8.881784e-16
-
-*Urban Center*
-Coefficients:
-               Estimate Std. Error z value Pr(>|z|)    
-(Intercept)   14.516312   2.195703   6.611 3.81e-11 ***
-log_patch     -0.618055   0.205145  -3.013 0.002589 **  **negative**
-log_tdh       -1.393026   0.286317  -4.865 1.14e-06 *** **negative**
-log_TotalSub  -1.331282   0.357971  -3.719 0.000200 *** **negative**
-road_length_m -0.025605   0.007753  -3.303 0.000958 *** **negative**
-
-R-squared = 0.7582528
-
-```{r spiders_predictors_stats_nb}
-global <- glm.nb(NumSpiders ~ log_TotalSub + log_tdr + log_tdh, data = sites)
-options(na.action = "na.fail") # Required for dredge to run
-model_dredge <- dredge(global, beta = "none", evaluate = T, rank = AICc)
-options(na.action = "na.omit") # set back to default
-top_model_ns_o <- get.models(model_dredge, subset = 1)[[1]]
-out <- summary(top_model_ns_o)
-out
-info <- out[[11]]
-#TotalSub (log_TotalSub)
-#exp(info[3, 1])
-#exp(info[3, 2])
-#Traffic_Dist_Highway (log_tdh)
-#exp(info[2, 1])
-#exp(info[2, 2])
-
-with(summary(top_model_ns_o), 1 - deviance/null.deviance) # This gives the R squared value
-#summary(model.avg(model_dredge, subset = delta <= 2))
-#summary(model.avg(model_dredge))
-model.sel(model_dredge) #estimates same signs
-car::vif(get.models(model_dredge, 1)[[1]]) #looking for less than 2
-
-# urban forest
-global <- glm.nb(NumSpiders ~ tree100m + log_TotalSub + log_tdh + log_patch + log_tdr, data = sites_forest)
-options(na.action = "na.fail") # Required for dredge to run
-model_dredge <- dredge(global, beta = "none", evaluate = T, rank = AICc)
-options(na.action = "na.omit") # set back to default
-top_model_ns_f <- get.models(model_dredge, subset = 1)[[1]]
-out <- summary(top_model_ns_f)
-out
-info <- out[[11]]
-with(summary(top_model_ns_f), 1 - deviance/null.deviance) # This gives the R squared value
-model.sel(model_dredge) #estimates same signs
-#summary(model.avg(model_dredge, subset = delta <= 2))
-#car::vif(get.models(model_dredge, 1)[[1]]) #looking for less than 2
-
-# urban center
-global <- glm.nb(NumSpiders ~ log_TotalSub + log_tdr + log_tdh + spec_rad + log_patch + road_length_m, data = sites_center)
-options(na.action = "na.fail") # Required for dredge to run
-model_dredge <- dredge(global, beta = "none", evaluate = T, rank = AICc)
-options(na.action = "na.omit") # set back to default
-top_model_ns_c <- get.models(model_dredge, subset = 1)[[1]]
-out <- summary(top_model_ns_c)
-out
-info <- out[[11]]
-#TotalSub
-#exp(info[4, 1])
-#exp(info[4, 2])
-#patch_area_km
-#exp(info[2, 1])
-#exp(info[2, 2])
-#Traffic_Dist_Highway
-#exp(info[3, 1])
-#exp(info[3, 2])
-#road_length
-#info[5, 1]
-#info[5, 2]
-with(summary(top_model_ns_c), 1 - deviance/null.deviance) # This gives the R squared value
-model.sel(model_dredge) #estimates same signs
-summary(model.avg(model_dredge, subset = delta <= 2))
-#car::vif(get.models(model_dredge, 1)[[1]]) # looking for values < 2
-```
-
-```{r spiders_predictors_overall_graphs, echo = FALSE}
-colorc = "#d95f02" 
-colorf = "#1b9e77"
-coloro = "black"
-
-# Plant Species Richness
-nd <- data.frame(log_TotalSub = seq(0, 3.2, 0.03), 
-                 log_tdh = mean(sites$log_tdh))
-predicted.distance <- augment(top_model_ns_o, 
-                              newdata = nd, 
-                              se_fit = TRUE)
-spiders_plant <- ggplot(sites, aes(x = log_TotalSub, y = log(NumSpiders))) + 
-  geom_point(aes(color = Location), alpha = 0.7, 
-             size = 1) +
-  geom_line(aes(x = log_TotalSub, y = .fitted), 
-            size = 1, 
-            color = coloro, 
-            data = predicted.distance) + 
-  geom_ribbon(aes(x = log_TotalSub, 
-                  ymin = .fitted - 1.96 * .se.fit, 
-                  ymax = .fitted + 1.96 * .se.fit), 
-              fill = coloro, 
-              data = predicted.distance, 
-              inherit.aes = FALSE, 
-              alpha = 0.25) +
-#  scale_y_continuous(limits = c(min(log(sites$NumSpiders)) - 2, max(log(sites$NumSpiders)) + 0.1 * diff(range(log(sites$NumSpiders))))) +  
-  scale_y_continuous(limits = c(-2, 5), breaks = c(-2, 0, 2, 4)) +  
-  scale_color_manual(values = c("Urban Center" = "#d95f02", "Urban Forest" = "#1b9e77")) +
-  theme_classic() +
-  xlab("Plant Species Richness [ln()]") +
-  ylab("Number of Spiders [ln()]") + 
-  theme(text = element_text(size = 10)) + 
-  theme(axis.text.x = element_text(colour = "black", size = 10)) + 
-  theme(axis.text.y = element_text(colour = "black", size = 10)) +
-  theme(axis.title.x = element_blank(), 
-        axis.title.y = element_blank(),
-        #axis.text.x = element_blank(),
-        legend.position = "none") + 
-#  theme(axis.text.y = element_blank()) +
-#  annotate(geom = "text", x = min(predicted.distance$log_TotalSub) + diff(range(predicted.distance$log_TotalSub))/2, y = max(log(sites$NumSpiders)), label = "***", color = "black", size = 4)
-    annotate(geom = "text", x = min(predicted.distance$log_TotalSub) + diff(range(predicted.distance$log_TotalSub))/2, y = 5, label = "***", color = "black", size = 4)
-
-# Highway Disturbance
-nd <- data.frame(log_TotalSub = mean(sites$log_TotalSub), 
-                 log_tdh = seq(2.7, 5.5, 0.03))
-predicted.distance <- augment(top_model_ns_o, 
-                              newdata = nd, 
-                              se_fit = TRUE)
-spiders_tdh <- ggplot(sites, aes(x = log_tdh, y = log(NumSpiders))) + 
-  geom_point(aes(color = Location), alpha = 0.7, 
-             size = 1) +
-  geom_line(aes(x = log_tdh, y = .fitted), 
-            size = 1, 
-            color = coloro, 
-            data = predicted.distance) + 
-  geom_ribbon(aes(x = log_tdh, 
-                  ymin = .fitted - 1.96 * .se.fit, 
-                  ymax = .fitted + 1.96 * .se.fit), 
-              fill = coloro, 
-              data = predicted.distance, 
-              inherit.aes = FALSE, 
-              alpha = 0.25) +
-#  scale_y_continuous(limits = c(min(log(sites$NumSpiders)) - 2, max(log(sites$NumSpiders)) + 0.1 * diff(range(log(sites$NumSpiders))))) +  
-  scale_y_continuous(limits = c(-2, 5), breaks = c(-2, 0, 2, 4)) +  
-  scale_x_continuous(breaks = c(3, 4, 5)) +  
-  scale_color_manual(values = c("Urban Center" = "#d95f02", "Urban Forest" = "#1b9e77")) +
-  theme_classic() +
-  xlab("Highway Disturbance [ln(vehicles/day/m)]") +
-  ylab("Number of Spiders [ln()]") + 
-  theme(text = element_text(size = 10)) + 
-  theme(axis.text.x = element_text(colour = "black", size = 10)) + 
-  theme(axis.text.y = element_text(colour = "black", size = 10)) +
-  theme(axis.title.x = element_blank(), 
-        axis.title.y = element_blank(), 
-        #axis.text.y = element_blank(),
-        legend.position = "none") + 
-#  theme(axis.text.x = element_blank()) +
-#  annotate(geom = "text", x = min((predicted.distance$log_tdh)) + diff(range((predicted.distance$log_tdh)))/2, y = max(log(sites$NumSpiders)), label = "***", color = "black", size = 4)
-  annotate(geom = "text", x = min((predicted.distance$log_tdh)) + diff(range((predicted.distance$log_tdh)))/2, y = 5, label = "*", color = "black", size = 4)
-
-spiders_plant
-spiders_tdh
-```
-
-```{r spiders_predictors_center_graphs, echo = FALSE}
-colorc = "#d95f02" 
-colorf = "#1b9e77"
-coloro = "black"
-
-# Plant Species Richness
-#nd <- data.frame(log_TotalSub = seq(0, 1.8, 0.02), 
-#                 log_patch = mean(sites_center$log_patch),
-#                 road_length_m = mean(sites_center$road_length_m),
-#                 log_tdh = mean(sites_center$log_tdh))
-#predicted.distance <- augment(top_model_ns_c, 
-#                              newdata = nd, 
-#                              se_fit = TRUE)
-#spiders_center_plant <- ggplot(sites_center, aes(x = log_TotalSub, y = log(NumSpiders))) + 
-#  geom_point(color = "grey", 
-#             size = 1) +
-#  geom_line(aes(x = log_TotalSub, y = .fitted), 
-#            size = 1, 
-#            color = colorc, 
-#            data = predicted.distance) + 
-#  geom_ribbon(aes(x = log_TotalSub, 
-#                  ymin = .fitted - 1.96 * .se.fit, 
-#                  ymax = .fitted + 1.96 * .se.fit), 
-#              fill = colorc, 
-#              data = predicted.distance, 
-#              inherit.aes = FALSE, 
-#              alpha = 0.25) +
-##  scale_y_continuous(limits = c(min(log(sites_center$NumSpiders)) - 1, max(log(sites_center$NumSpiders)) + 0.2 * diff(range(log(sites_center$NumSpiders))))) +  
-#  scale_y_continuous(limits = c(-2, 3.5), breaks = c(-2, -1, 0, 1, 2, 3)) +  
-#  theme_classic() +
-#  xlab("Plant Species Richness [log()]") +
-#  ylab("Number of Spiders [log()]") + 
-#  theme(text = element_text(size = 10)) + 
-#  theme(axis.text.x = element_text(colour = "black", size = 10)) + 
-#  theme(axis.text.y = element_text(colour = "black", size = 10)) +
-#  theme(axis.title.x = element_blank(), 
-#        axis.title.y = element_blank()) + 
-##  theme(axis.text.x = element_blank(), 
-##        axis.text.y = element_blank()) +
-##  annotate(geom = "text", x = min((predicted.distance$log_TotalSub)) + diff(range((predicted.distance$log_TotalSub)))/2, y = max(log(sites_center$NumSpiders)), label = "***", color = "black", size = 4)
-#  annotate(geom = "text", x = min((predicted.distance$log_TotalSub)) + diff(range((predicted.distance$log_TotalSub)))/2, y = 3.5, label = "***", color = "black", size = 4)
-
-# Patch Area
-#nd <- data.frame(log_TotalSub = mean(sites_center$log_TotalSub), 
-#                 log_patch = seq(4.34, 7.52, 0.025),
-#                 road_length_m = mean(sites_center$road_length_m),
-#                 log_tdh = mean(sites_center$log_tdh))
-#predicted.distance <- augment(top_model_ns_c, 
-#                              newdata = nd, 
-#                              se_fit = TRUE)
-#spiders_center_patch <- ggplot(sites_center, aes(x = log_patch, y = log(NumSpiders))) + 
-#  geom_point(color = "grey", 
-#             size = 1) +
-#  geom_line(aes(x = log_patch, y = .fitted), 
-#            size = 1, 
-#            color = colorc, 
-#            data = predicted.distance) + 
-#  geom_ribbon(aes(x = log_patch, 
-#                  ymin = .fitted - 1.96 * .se.fit, 
-#                  ymax = .fitted + 1.96 * .se.fit), 
-#              fill = colorc, 
-#              data = predicted.distance, 
-#              inherit.aes = FALSE, 
-#              alpha = 0.25) +
-##  scale_y_continuous(limits = c(min(log(sites_center$NumSpiders)) - 1, max(log(sites_center$NumSpiders)) + 0.15 * diff(range(log(sites_center$NumSpiders))))) +  
-#  scale_y_continuous(limits = c(-2, 3.5), breaks = c(-2, -1, 0, 1, 2, 3)) +  
-#  theme_classic() +
-#  xlab("Patch Area [log(mm²)]") +
-#  ylab("Number of Spiders [log()]") + 
-#  theme(text = element_text(size = 10)) + 
-#  theme(axis.text.x = element_text(colour = "black", size = 10)) + 
-#  theme(axis.text.y = element_text(colour = "black", size = 10)) +
-#  theme(axis.title.x = element_blank(), 
-#        axis.title.y = element_blank(), 
-#        axis.text.y = element_blank()) + 
-##  theme(axis.text.x = element_blank()) +
-##  annotate(geom = "text", x = min((predicted.distance$log_patch)) + diff(range((predicted.distance$log_patch)))/2, y = max(log(sites_center$NumSpiders)), label = "**", color = "black", size = 4) 
-#  annotate(geom = "text", x = min((predicted.distance$log_patch)) + diff(range((predicted.distance$log_patch)))/2, y = 3.5, label = "**", color = "black", size = 4)
-
-# Highway Disturbance
-nd <- data.frame(log_tdh = seq(3.32, 5.42, 0.02))
-predicted.distance <- augment(top_model_ns_c, 
-                              newdata = nd, 
-                              se_fit = TRUE)
-spiders_center_tdh <- ggplot(sites, aes(x = log_tdh, y = log(NumSpiders))) + 
-  geom_point(aes(color = Location), alpha = 0.5, 
-             size = 1) +
-  geom_line(aes(x = log_tdh, y = .fitted), 
-            size = 1, 
-            color = colorc, 
-            data = predicted.distance) + 
-  geom_ribbon(aes(x = log_tdh, 
-                  ymin = .fitted - 1.96 * .se.fit, 
-                  ymax = .fitted + 1.96 * .se.fit), 
-              fill = colorc, 
-              data = predicted.distance, 
-              inherit.aes = FALSE, 
-              alpha = 0.25) +
-#  scale_y_continuous(limits = c(min(log(sites_center$NumSpiders)) - 2, max(log(sites_center$NumSpiders)) + 0.1 * diff(range(log(sites_center$NumSpiders))))) +  
-  scale_y_continuous(limits = c(-2, 5), breaks = c(-2, 0, 2, 4)) +  
-  scale_x_continuous(breaks = c(3, 4, 5)) +  
-  scale_color_manual(values = c("Urban Center" = "#d95f02", "Urban Forest" = "#1b9e77")) +
-  theme_classic() +
-  xlab("Highway Disturbance [ln(vehicles/day/m)]") +
-  ylab("Number of Spiders [ln()]") + 
-  theme(text = element_text(size = 10)) + 
-  theme(axis.text.x = element_text(colour = "black", size = 10)) + 
-  theme(axis.text.y = element_text(colour = "black", size = 10)) +
-  theme(axis.title.x = element_blank(), 
-        axis.title.y = element_blank(),
-        legend.position = "none") + 
-        #axis.text.y = element_blank()) + 
-#  theme(axis.text.x = element_blank()) +
-#  annotate(geom = "text", x = min((predicted.distance$log_tdh)) + diff(range((predicted.distance$log_tdh)))/2, y = max(log(sites_center$NumSpiders)), label = "***", color = "black", size = 4) 
-  annotate(geom = "text", x = 4, y = 5, label = "*", color = "black", size = 4)
-
-# Road Length
-#nd <- data.frame(log_TotalSub = mean(sites_center$log_TotalSub), 
-#                 log_patch = mean(sites_center$log_patch),
-#                 road_length_m = seq(47, 136, 1),
-#                 log_tdh = mean(sites_center$log_tdh))
-#predicted.distance <- augment(top_model_ns_c, 
-#                              newdata = nd, 
-#                              se_fit = TRUE)
-#spiders_center_road <- ggplot(sites_center, aes(x = (road_length_m), y = log(NumSpiders))) + 
-#  geom_point(color = "grey", 
-#             size = 1) +
-#  geom_line(aes(x = (road_length_m), y = .fitted), 
-#            size = 1, 
-#            color = colorc, 
-#            data = predicted.distance) + 
-#  geom_ribbon(aes(x = (road_length_m), 
-#                  ymin = .fitted - 1.96 * .se.fit, 
-#                  ymax = .fitted + 1.96 * .se.fit), 
-#              fill = colorc, 
-#              data = predicted.distance, 
-#              inherit.aes = FALSE, 
-#              alpha = 0.25) +
-##  scale_y_continuous(limits = c(min(log(sites_center$NumSpiders)) - 1, max(log(sites_center$NumSpiders)) + 0.1 * diff(range(log(sites_center$NumSpiders))))) +  
-#  scale_y_continuous(limits = c(-2, 3.5), breaks = c(-2, -1, 0, 1, 2, 3)) +  
-#  theme_classic() +
-#  xlab("Total Road Length [m]") +
-#  ylab("Number of Spiders [log()]") + 
-#  theme(text = element_text(size = 10)) + 
-#  theme(axis.text.x = element_text(colour = "black", size = 10)) + 
-#  theme(axis.text.y = element_text(colour = "black", size = 10)) +
-#  theme(axis.title.x = element_blank(), 
-#        axis.title.y = element_blank(), 
-#        axis.text.y = element_blank()) + 
-##  theme(axis.text.x = element_blank()) +
-##  annotate(geom = "text", x = min((predicted.distance$road_length_m)) + diff(range((predicted.distance$road_length_m)))/2, y = max(log(sites_center$NumSpiders)), label = "***", color = "black", size = 4)
-#  annotate(geom = "text", x = min((predicted.distance$road_length_m)) + diff(range((predicted.distance$road_length_m)))/2, y = 3.5, label = "***", color = "black", size = 4)
-
-#spiders_center_plant
-#spiders_center_patch
-#spiders_center_road
-spiders_center_tdh
-```
-
-### Number of Spiders by Land
-
-```{r spiders_land_stats}
-spiders_land <- glm(NumSpiders ~ Land, data = sites, family = poisson)
-summary(spiders_land)
-car::Anova(spiders_land, test.statistic = "LR")
-comp <- glht(spiders_land, linfct = mcp(Land = "Tukey"))
-summary(comp)
-
-spiders_land_nb <- glm.nb(NumSpiders ~ Land, data = sites)
-summary(spiders_land_nb)
-car::Anova(spiders_land_nb, test.statistic = "LR")
-comp <- glht(spiders_land_nb, linfct = mcp(Land = "Tukey"))
-summary(comp)
-```
-
-```{r spiders_land_graph}
-#sites <- sites %>% 
-#  mutate(Land = fct_relevel(Land, "Deciduous Forest", 
-#                            "Woody Wetlands", 
-#                            "Urban, High", 
-#                            "Urban, Medium", 
-#                            "Urban, Low"))
-nd <- data.frame(Land = factor(levels(sites$Land)))
-predictions <- augment(spiders_land_nb, newdata = nd, se_fit = TRUE, type.predict = "response")
-predictions <- predictions %>% 
-  rename("rate" = ".fitted", "SE" = ".se.fit")
-#predictions <- summary(emmeans(spiders_land, ~Land),type = "response")
-
-spiders_land_plot <- ggplot(sites, aes(x = Land, y = NumSpiders)) + 
-  geom_jitter(color = "grey", width = 0.1, size = 0.5) +
-  geom_point(aes(x = Land, y = rate, color = Land), size = 2, data = predictions) + 
-  geom_errorbar(aes(x = Land, 
-                  ymin = rate - SE, 
-                  ymax = rate + SE, color = Land), data = predictions, inherit.aes = FALSE, width = 0.25, size = 1) +
-  theme_classic() +
-  scale_color_manual(values = c("Deciduous Forest" = "#1b9e77", "Woody Wetlands" = "#1b9e77", "Urban, High" = "#d95f02", "Urban, Medium" = "#d95f02", "Urban, Low" = "#d95f02")) +
-  xlab("Land Cover Class") +
-  ylab("Number of Spiders") + 
-  theme(text = element_text(size = 10)) + 
-  theme(axis.text.x=element_text(colour="black", size=10)) + 
-  theme(axis.text.y=element_text(colour="black", size=10)) +
-  theme(legend.position = "none") +
-  theme(axis.text.x = element_text(angle = 90, vjust = 1, hjust=1))# +
-  #annotate(geom="text", x=1, y=max(sites$NumSpiders), label="A", color="black", size = 3) +
-  #annotate(geom="text", x=2, y=max(sites$NumSpiders), label="A", color="black", size = 3) +
-  #annotate(geom="text", x=3, y=max(sites$NumSpiders), label="A", color="black", size = 3) +
-  #annotate(geom="text", x=4, y=max(sites$NumSpiders), label="A", color="black", size = 3) +
-  #annotate(geom="text", x=5, y=max(sites$NumSpiders), label="A", color="black", size = 3)
-
-spiders_land_plot_nox <- spiders_land_plot + 
-  theme(axis.text.x = element_blank()) + 
-  theme(axis.title.x = element_blank())
-
-spiders_land_plot
-```
-
-The **number of spiders per site significantly varies** across land cover class (Chi = 10.91, df = 4, p = 0.028).
-
-## Response Variable: Web Distance
-
-### Web Distance by Location
-
-```{r dist_location_stats}
-ggarrange(ggplot(web_dist, aes(x = RetreatDist)) +
-            geom_density(),
-          ggplot(web_dist, aes(x = log(RetreatDist))) +
-            geom_density(), ncol = 2)
-
-shapiro.test(web_dist$RetreatDist) # not normal
-shapiro.test(log(web_dist$RetreatDist)) # not normal
-
-dist <- glmer(round(RetreatDist, 0) ~ Location * factor(Neighbor) + (1 | ID), data = web_dist, family = poisson)
-summary(dist)
-
-dist.nb <- glmer.nb(round(RetreatDist, 0) ~ Location * factor(Neighbor) + (1 | ID), data = web_dist)
-summary(dist.nb)
-
-dist2 <- lmer(log(RetreatDist) ~ Location * factor(Neighbor) + (1 | ID), data = web_dist)
-coefs <- data.frame(coef(summary(dist2)))
-coefs$p.z <- 2 * (1 - pnorm(abs(coefs$t.value)))
-coefs
-
-# Both methods yield similar results
-web_dist %>% 
-  group_by(Location) %>% 
-  summarize(mean = mean(RetreatDist),
-            se = plotrix::std.error(RetreatDist))
-```
-
-```{r dist_location_assumptions, echo = FALSE}
-# As is, Poisson
-test_dist <- augment(dist.nb, data = web_dist)
-resid_dist <- ggplot(test_dist, aes(x = .fitted, y = .resid)) + 
-  geom_point() + 
-  geom_smooth() +
-  geom_hline(yintercept = 0) +
-  xlab("Fitted Values") +
-  ylab("Standardized \nResiduals") +
-  theme_classic() +
-  theme(text = element_text(size = 14, color = "black")) +
-  theme(axis.text.x=element_text(color="black", size=14)) + 
-  theme(axis.text.y=element_text(color="black", size=14))
-
-y <- quantile(test_dist$.resid, c(0.25, 0.75))
-x <- qnorm(c(0.25, 0.75))
-slope <- diff(y)/diff(x)
-int <- y[1L] - slope * x[1L]
-
-qq_dist <- ggplot(test_dist, aes(sample = .resid)) + 
-  stat_qq() + 
-  geom_abline(slope = slope, intercept = int) +
-  xlab("Theoretical Quantiles") +
-  ylab("Sample Quantiles") +
-  theme_classic() +
-  theme(text = element_text(size = 14, color = "black")) +
-  theme(axis.text.x=element_text(color="black", size=14)) + 
-  theme(axis.text.y=element_text(color="black", size=14))
-
-scaleloc_dist <- ggplot(test_dist, aes(x = .fitted, y = sqrt(abs(.resid)))) + 
-  geom_point() + 
-  geom_smooth() + 
-  geom_hline(yintercept = 0.83) +
-  xlab("Fitted Values") +
-  ylab("Sqrt Standardized \nResiduals") +
-  theme_classic() +
-  theme(text = element_text(size = 14, color = "black")) +
-  theme(axis.text.x=element_text(color="black", size=14)) + 
-  theme(axis.text.y=element_text(color="black", size=14))
-
-lev_dist <- ggplot(test_dist, aes(.hat, .resid)) +
- geom_vline(colour = "black", xintercept = 0) +
-  geom_hline(colour = "black", yintercept = 0) +
-  geom_point(aes(size = .cooksd)) + geom_smooth(se = FALSE) +
-  xlab("Theoretical Quantiles") +
-  ylab("Sample Quantiles") +
-  labs(size = "Cook's \nDistance") +
-  theme_classic() +
-  theme(text = element_text(size = 14, color = "black")) +
-  theme(axis.text.x=element_text(color="black", size=14)) + 
-  theme(axis.text.y=element_text(color="black", size=14))
-
-ggarrange(resid_dist, qq_dist, scaleloc_dist, lev_dist, 
-          labels = c("A", "B", "C", "D"),
-          ncol = 2, nrow = 2)
-
-# Log-transformed, Normal
-test_dist2 <- augment(dist2, data = web_dist)
-resid_dist2 <- ggplot(test_dist2, aes(x = .fitted, y = .resid)) + 
-  geom_point() + 
-  geom_smooth() +
-  geom_hline(yintercept = 0) +
-  xlab("Fitted Values") +
-  ylab("Standardized \nResiduals") +
-  theme_classic() +
-  theme(text = element_text(size = 14, color = "black")) +
-  theme(axis.text.x=element_text(color="black", size=14)) + 
-  theme(axis.text.y=element_text(color="black", size=14))
-
-y <- quantile(test_dist2$.resid, c(0.25, 0.75))
-x <- qnorm(c(0.25, 0.75))
-slope <- diff(y)/diff(x)
-int <- y[1L] - slope * x[1L]
-
-qq_dist2 <- ggplot(test_dist2, aes(sample = .resid)) + 
-  stat_qq() + 
-  geom_abline(slope = slope, intercept = int) +
-  xlab("Theoretical Quantiles") +
-  ylab("Sample Quantiles") +
-  theme_classic() +
-  theme(text = element_text(size = 14, color = "black")) +
-  theme(axis.text.x=element_text(color="black", size=14)) + 
-  theme(axis.text.y=element_text(color="black", size=14))
-
-scaleloc_dist2 <- ggplot(test_dist2, aes(x = .fitted, y = sqrt(abs(.resid)))) + 
-  geom_point() + 
-  geom_smooth() + 
-  geom_hline(yintercept = 0.83) +
-  xlab("Fitted Values") +
-  ylab("Sqrt Standardized \nResiduals") +
-  theme_classic() +
-  theme(text = element_text(size = 14, color = "black")) +
-  theme(axis.text.x=element_text(color="black", size=14)) + 
-  theme(axis.text.y=element_text(color="black", size=14))
-
-lev_dist2 <- ggplot(test_dist2, aes(.hat, .resid)) +
- geom_vline(colour = "black", xintercept = 0) +
-  geom_hline(colour = "black", yintercept = 0) +
-  geom_point(aes(size = .cooksd)) + geom_smooth(se = FALSE) +
-  xlab("Theoretical Quantiles") +
-  ylab("Sample Quantiles") +
-  labs(size = "Cook's \nDistance") +
-  theme_classic() +
-  theme(text = element_text(size = 14, color = "black")) +
-  theme(axis.text.x=element_text(color="black", size=14)) + 
-  theme(axis.text.y=element_text(color="black", size=14))
-
-ggarrange(resid_dist2, qq_dist2, scaleloc_dist2, lev_dist2, 
-          labels = c("A", "B", "C", "D"),
-          ncol = 2, nrow = 2)
-```
-
-```{r dist_location_graph, echo = FALSE}
-# Negative Binomial
-variable_names <- list("1" = "Nearest Neighbor",
-                       "2" = "2nd Nearest Neighbor")
-variable_labeller <- function(variable,value){
-  return(variable_names[value])
-}
-predictions <- expand.grid(Location = levels(factor(web_dist$Location)), Neighbor = levels(factor(web_dist$Neighbor)))
-predictions$response <- predict(dist.nb, newdata = predictions, se.fit = TRUE, re.form = NA, type = "response")
-
-myFunc <- function(mm) {
-    predict(mm, newdata = predictions, re.form = ~0, type = "response")
-}
-#bigBoot_dist_location_nb <- bootMer(dist.nb, myFunc, nsim = 1000)
-#saveRDS(bigBoot_dist_location_nb, file = "bootstrapping/bigBoot_dist_location_nb.Rds")
-bigBoot_dist_location_nb <- readRDS("bootstrapping/bigBoot_dist_location_nb.Rds") 
-predSE <- t(apply(bigBoot_dist_location_nb$t, MARGIN = 2, FUN = sd, na.rm = TRUE))
-predictions$SE <- predSE[1, ]
-#predictions2 <- summary(emmeans(dist, ~Location | Neighbor,type = "response"))
-
-nb_plot_dist <- ggplot(web_dist, aes(x = Neighbor, y = RetreatDist)) + 
-  geom_jitter(aes(color = Location), alpha = 0.5, width = 0.1) +
-    geom_line(aes(x = Neighbor, y = response, group = Location), size = 2, data = predictions, color = "grey") +
-  geom_point(aes(x = Neighbor, y = response, color = Location), size = 2, data = predictions) + 
-  geom_errorbar(aes(x = Neighbor, 
-                  ymin = response - SE, 
-                  ymax = response + SE,
-                  color = Location), data = predictions, inherit.aes = FALSE, width = 0.15, size = 1) +
-  scale_color_manual(values = c("Urban Center" = "#d95f02", "Urban Forest" = "#1b9e77")) +
-  scale_x_discrete(labels=c("Urban Forest" = "Urban \nForest \nN = 10", "Urban Center" = "Urban \nCenter \nN = 12")) +
-  theme_classic() +
-  scale_y_continuous(limits = c(-50, 1050), breaks = c(0, 200, 400, 600, 800, 1000)) +
-  xlab("Nearest Neighbors") +
-  ylab("Distance from Focal Web \nto Neighbor Web [cm]") + 
-  theme(text = element_text(size = 10)) + 
-  theme(axis.text.x = element_text(colour = "black", size = 10)) + 
-  theme(axis.text.y = element_text(colour = "black", size = 10)) +
-  theme(legend.position = "none")
-
-# raw data
-raw <- web_dist %>% 
-  group_by(Location, Neighbor) %>% 
-  summarise(mean = mean(RetreatDist),
-            se = plotrix::std.error(RetreatDist))
-
-raw_plot_dist <- ggplot(web_dist, aes(x = Neighbor, y = RetreatDist)) + 
-  geom_jitter(color = "grey", width = 0.1) +
-  geom_point(aes(x = Neighbor, y = mean, color = Location), size = 2, data = raw) +
-  geom_line(aes(x = Neighbor, y = mean, group = Location), size = 2, data = raw, color = "grey") +
-  geom_errorbar(aes(x= Neighbor, 
-                    ymin = mean - se, 
-                    ymax = mean + se, 
-                    color = Location), data = raw, inherit.aes = FALSE, width = 0.15, size = 1.5) +
-    scale_color_manual(values = c("Urban Center" = "#d95f02", "Urban Forest" = "#1b9e77")) +
-    scale_x_discrete(labels=c("Urban Forest" = "Urban \nForest \nN = 10", "Urban Center" = "Urban \nCenter \nN = 12")) +
-    theme_classic() +
-    scale_y_continuous(limits = c(-50, 1000), breaks = c(0, 200, 400, 600, 800, 1000)) +
-    xlab("Nearest Neighbors") +
-    ylab("Distance from Focal Web \nto Neighbor Web [cm]") + 
-    theme(text = element_text(size = 10)) + 
-    theme(axis.text.x = element_text(colour = "black", size = 10)) + 
-    theme(axis.text.y = element_text(colour = "black", size = 10)) +
-    theme(legend.position = "none")
-
-# Non-transformed, poisson distribution
-variable_names <- list("1" = "Nearest Neighbor",
-                       "2" = "2nd Nearest Neighbor")
-variable_labeller <- function(variable,value){
-  return(variable_names[value])
-}
-predictions <- expand.grid(Location = levels(factor(web_dist$Location)), Neighbor = levels(factor(web_dist$Neighbor)))
-predictions$response <- predict(dist, newdata = predictions, se.fit = TRUE, re.form = NA, type = "response")
-
-myFunc <- function(mm) {
-    predict(mm, newdata = predictions, re.form = ~0, type = "response")
-}
-#bigBoot_dist_location <- bootMer(dist, myFunc, nsim = 1000)
-#saveRDS(bigBoot_dist_location, file = "bootstrapping/bigBoot_dist_location.Rds")
-bigBoot_dist_location <- readRDS("bootstrapping/bigBoot_dist_location.Rds")
-predSE <- t(apply(bigBoot_dist_location$t, MARGIN = 2, FUN = sd))
-predictions$SE <- predSE[1, ]
-#predictions2 <- summary(emmeans(dist, ~Location | Neighbor,type = "response"))
-
-poisson_plot_dist <- ggplot(web_dist, aes(x = Neighbor, y = RetreatDist)) + 
-  geom_jitter(color = "grey", width = 0.1) +
-  geom_point(aes(x = Neighbor, y = response, color = Location), size = 2, data = predictions) + 
-  geom_line(aes(x = Neighbor, y = response, group = Location), size = 2, data = predictions, color = "grey") +
-  geom_errorbar(aes(x = Neighbor, 
-                  ymin = response - SE, 
-                  ymax = response + SE,
-                  color = Location), data = predictions, inherit.aes = FALSE, width = 0.15, size = 1.5) +
-  scale_color_manual(values = c("Urban Center" = "#d95f02", "Urban Forest" = "#1b9e77")) +
-  scale_x_discrete(labels=c("Urban Forest" = "Urban \nForest \nN = 10", "Urban Center" = "Urban \nCenter \nN = 12")) +
-  theme_classic() +
-  scale_y_continuous(limits = c(-50, 1000), breaks = c(0, 200, 400, 600, 800, 1000)) +
-  xlab("Nearest Neighbors") +
-  ylab("Distance from Focal Web \nto Neighbor Web [cm]") + 
-  theme(text = element_text(size = 10)) + 
-  theme(axis.text.x = element_text(colour = "black", size = 10)) + 
-  theme(axis.text.y = element_text(colour = "black", size = 10)) +
-  theme(legend.position = "none")
-
-# Let's look at the log-transformed response variable since that is normal
-variable_names <- list("1" = "Nearest Neighbor",
-                       "2" = "2nd Nearest Neighbor")
-variable_labeller <- function(variable,value){
-  return(variable_names[value])
-}
-predictions <- expand.grid(Location = levels(factor(web_dist$Location)), Neighbor = levels(factor(web_dist$Neighbor)))
-predictions$response <- predict(dist2, newdata = predictions, se.fit = TRUE, re.form = NA, type = "response")
-
-myFunc <- function(mm) {
-    predict(mm, newdata = predictions, re.form = ~0, type = "response")
-}
-#bigBoot_dist_location2 <- bootMer(dist2, myFunc, nsim = 1000)
-#saveRDS(bigBoot_dist_location2, file = "bootstrapping/bigBoot_dist_location2.Rds")
-bigBoot_dist_location2 <- readRDS("bootstrapping/bigBoot_dist_location2.Rds")
-predSE <- t(apply(bigBoot_dist_location2$t, MARGIN = 2, FUN = sd))
-predictions$SE <- predSE[1, ]
-#predictions2 <- summary(emmeans(dist2, ~Location | Neighbor,type = "response"))
-
-log_plot_dist <- ggplot(web_dist, aes(x = Neighbor, y = (RetreatDist))) + 
-  geom_jitter(color = "grey", width = 0.1) +
-  geom_point(aes(x = Neighbor, y = exp(response), color = Location), size = 2, data = predictions) + 
-  geom_line(aes(x = Neighbor, y = exp(response), group = Location), size = 2, data = predictions, color = "grey") +
-  geom_errorbar(aes(x = Neighbor, 
-                  ymin = exp(response - SE), 
-                  ymax = exp(response + SE),
-                  color = Location), data = predictions, inherit.aes = FALSE, width = 0.15, size = 1.5) +
-  scale_color_manual(values = c("Urban Center" = "#d95f02", "Urban Forest" = "#1b9e77")) +
-  scale_x_discrete(labels=c("Urban Forest" = "Urban \nForest \nN = 10", "Urban Center" = "Urban \nCenter \nN = 12")) +
-  theme_classic() +
-  scale_y_continuous(limits = c(-50, 1000), breaks = c(0, 200, 400, 600, 800, 1000)) +
-  xlab("Nearest Neighbors") +
-  ylab("Distance from Focal Web \nto Neighbor Web [cm]") + 
-  theme(text = element_text(size = 10)) + 
-  theme(axis.text.x = element_text(colour = "black", size = 10)) + 
-  theme(axis.text.y = element_text(colour = "black", size = 10))
-
-ggarrange(raw_plot_dist, 
-          poisson_plot_dist, 
-          log_plot_dist, 
-          nb_plot_dist,
-          labels = c("Raw Data", "Poisson Distribution", "Log-Transformed", "Negative Binomial"),
-          nrow = 1, 
-          common.legend = TRUE)
-```
-
-Spider neighbors were **significantly closer in the urban center** than the urban forest (z = -1.83, df = 1, 21, p < 0.001).
-The **second neighbor was always further from the focal web** than the first (z = 2.83, df = 1, 21, p = 0.005), as this is how we defined the first and second neighbor.
-There was **no interaction between location and neighbor** (z = -1.09, df = 1, 21, p = 0.276) - the distance between the first and second neighbor did not differ between the urban center and the urban forest.
-
-### Web Distance by Predictors
-
-To look at the predictors, we will restrict to just the nearest neighbor instead of the nearest and second nearest neighbor.
-
-```{r dist_predictors_stats}
-#overall
-models = list(round(RetreatDist,0) ~ 1,
-              round(RetreatDist,0) ~ log_TotalSub,
-              round(RetreatDist,0) ~ log_tdr, 
-              round(RetreatDist,0) ~ log_tdh,
-              round(RetreatDist,0) ~ log_TotalSub + log_tdr,
-              round(RetreatDist,0) ~ log_TotalSub + log_tdh,
-              round(RetreatDist,0) ~ log_tdr + log_tdh,
-              round(RetreatDist,0) ~ log_TotalSub + log_tdr + log_tdh)
-fits = lapply(models, glm, data = near, family = "poisson")
-modnames = sapply(models, function(ff)deparse(ff[[3]]))
-pander(aictab(fits, modname = modnames), caption="Table 1. AICc model selection table for Search Distance to the Focal Web.", split.tables = Inf)
-
-global <- glm(round(RetreatDist, 0) ~ log_TotalSub + log_tdr + log_tdh, data = near, family = poisson)
-options(na.action = "na.fail") # Required for dredge to run
-model_dredge <- dredge(global, beta = "none", evaluate = T, rank = AICc)
-options(na.action = "na.omit") # set back to default
-top_model_wd_o <- get.models(model_dredge, subset = 1)[[1]]
-out <- summary(top_model_wd_o)
-out
-info <- out[[12]]
-# TotalSub
-exp(info[3, 1])
-exp(info[3, 2])
-#Traffic_Dist_Road
-exp(info[2, 1])
-exp(info[2, 1])
-
-with(summary(top_model_wd_o), 1 - deviance/null.deviance)
-model.sel(model_dredge) #estimates same signs
-#summary(model.avg(model_dredge, subset = delta <= 2))
-car::vif(get.models(model_dredge, 5)[[1]]) # looking for less than 2
-
-# Urban Forest
-global <- glm(round(RetreatDist, 0) ~ tree100m + log_TotalSub + log_tdr + log_tdh + log_patch, data = near_forest, family = poisson)
-options(na.action = "na.fail") # Required for dredge to run
-model_dredge <- dredge(global, beta = "none", evaluate = T, rank = AICc)
-options(na.action = "na.omit") # set back to default
-top_model_wd_f <- get.models(model_dredge, subset = 1)[[1]]
-out <- summary(top_model_wd_f)
-out
-info <- out[[12]]
-#tree100m
-info[5, 1]
-info[5, 2]
-#TotalSub
-exp(info[4, 1])
-exp(info[4, 2])
-#Road
-exp(info[3, 1])
-exp(info[3, 2])
-#Highway
-exp(info[2, 1])
-exp(info[2, 2])
-
-with(summary(top_model_wd_f), 1 - deviance/null.deviance)
-model.sel(model_dredge) #estimates same signs
-#summary(model.avg(model_dredge, subset = delta <= 2))
-car::vif(get.models(model_dredge, 1)[[1]]) # looking for less than 2
-
-# Urban Center
-global <- glm(round(RetreatDist, 0) ~ log_TotalSub + log_tdr + log_tdh + spec_rad + log_patch + road_length_m, data = near_center, family = poisson)
-options(na.action = "na.fail") # Required for dredge to run
-model_dredge <- dredge(global, beta = "none", evaluate = T, rank = AICc)
-options(na.action = "na.omit") # set back to default
-top_model_wd_c <- get.models(model_dredge, subset = 1)[[1]]
-out <- summary(top_model_wd_c)
-out
-info <- out[[12]]
-#TotalSub
-exp(info[2, 1])
-exp(info[2, 2])
-#spec_rad
-info[4, 1]
-info[4, 2]
-#road_length_m
-info[3, 1]
-info[3, 2]
-
-with(summary(top_model_wd_c), 1 - deviance/null.deviance)
-model.sel(model_dredge) #estimates same signs
-out <- summary(model.avg(model_dredge, subset = delta <= 2))
-out
-info <- out[[10]]
-#TotalSub
-exp(info[2, 1])
-exp(info[2, 2])
-#spec_rad
-info[4, 1]
-info[4, 2]
-#road_length_m
-info[3, 1]
-info[3, 2]
-#log_patch
-exp(info[5, 1])
-exp(info[5, 2])
-car::vif(get.models(model_dredge, 1)[[1]]) # looking for less than 2
-
-# If any value is much greater than 2, this means there is quite a bit of multicollinearity, and we can try removing the variable with the highest vif.
-Here is the code you would run to accomplish this.
-
-#global2 <- update(global, .~. -spec_rad)
-#options(na.action = "na.fail") # Required for dredge to run
-#model_dredge <- dredge(global2, beta = "none", evaluate = T, rank = AICc)
-#options(na.action = "na.omit") # set back to default
-#top_model_wd_c <- get.models(model_dredge, subset = 1)[[1]]
-#out <- summary(top_model_wd_c)
-#out
-#info <- out[[12]]
-#car::vif(get.models(model_dredge, 1)[[1]]) 
-```
-
-*Overall*
-Coefficients:
-             Estimate Std. Error z value Pr(>|z|)    
-(Intercept)   5.38311    0.06200   86.83   <2e-16 ***
-log_tdr      -0.18279    0.01024  -17.84   <2e-16 *** **negative**
-log_TotalSub  0.57484    0.01653   34.78   <2e-16 *** **positive**
-
-R-squared = 0.3424213
-
-*Urban Forest*
-Coefficients:
-              Estimate Std. Error z value Pr(>|z|)    
-(Intercept)   5.247233   0.253935  20.664  < 2e-16 ***
-log_tdh       0.192623   0.045552   4.229 2.35e-05 *** **positive**
-log_tdr       0.097475   0.018717   5.208 1.91e-07 *** **positive**
-log_TotalSub -0.182147   0.037627  -4.841 1.29e-06 *** **negative**
-tree100m      0.007928   0.001747   4.540 5.64e-06 *** **positive**
-
-R-squared = 0.03720731
-
-*Urban Center*
-Coefficients:
-               Estimate Std. Error z value Pr(>|z|)    
-(Intercept)   25.656433   1.978299  12.969   <2e-16 ***
-log_TotalSub  -0.949802   0.081234 -11.692   <2e-16 *** **negative**
-road_length_m -0.028700   0.001686 -17.019   <2e-16 *** **negative**
-spec_rad      -0.116126   0.013624  -8.523   <2e-16 *** **negative**
-
-R-squared = 0.8382736
-
-(conditional average) 
-               Estimate Std. Error Adjusted SE z value Pr(>|z|)    
-(Intercept)   27.444071   3.180180    3.580799   7.664   <2e-16 ***
-log_TotalSub  -1.011887   0.119466    0.136311   7.423   <2e-16 ***
-road_length_m -0.028829   0.001723    0.002106  13.691   <2e-16 ***
-spec_rad      -0.124872   0.018357    0.021193   5.892   <2e-16 ***
-log_patch     -0.152072   0.060123    0.075060   2.026   0.0428 *
-
-```{r dist_predictors_stats_nb}
-#overall
-global <- glm.nb(round(RetreatDist, 0) ~ log_TotalSub + log_tdr + log_tdh, data = near)
-options(na.action = "na.fail") # Required for dredge to run
-model_dredge <- dredge(global, beta = "none", evaluate = T, rank = AICc)
-options(na.action = "na.omit") # set back to default
-top_model_wd_o <- get.models(model_dredge, subset = 1)[[1]]
-out <- summary(top_model_wd_o)
-out
-info <- out[[11]]
-# TotalSub
-#exp(info[3, 1])
-#exp(info[3, 2])
-#Traffic_Dist_Road
-#exp(info[2, 1])
-#exp(info[2, 1])
-
-with(summary(top_model_wd_o), 1 - deviance/null.deviance)
-model.sel(model_dredge) #estimates same signs
-summary(model.avg(model_dredge, subset = delta <= 2))
-#car::vif(get.models(model_dredge, 5)[[1]]) # looking for less than 2
-
-# Urban Forest
-global <- glm.nb(round(RetreatDist, 0) ~ tree100m + log_TotalSub + log_tdr + log_tdh + log_patch, data = near_forest)
-options(na.action = "na.fail") # Required for dredge to run
-model_dredge <- dredge(global, beta = "none", evaluate = T, rank = AICc)
-options(na.action = "na.omit") # set back to default
-top_model_wd_f <- get.models(model_dredge, subset = 1)[[1]]
-out <- summary(top_model_wd_f)
-out
-info <- out[[11]]
-#tree100m
-#info[5, 1]
-#info[5, 2]
-#TotalSub
-#exp(info[4, 1])
-#exp(info[4, 2])
-#Road
-#exp(info[3, 1])
-#exp(info[3, 2])
-#Highway
-#exp(info[2, 1])
-#exp(info[2, 2])
-
-with(summary(top_model_wd_f), 1 - deviance/null.deviance)
-model.sel(model_dredge) #estimates same signs
-#summary(model.avg(model_dredge, subset = delta <= 2))
-#car::vif(get.models(model_dredge, 1)[[1]]) # looking for less than 2
-
-# Urban Center
-global <- glm.nb(round(RetreatDist, 0) ~ log_TotalSub + log_tdr + log_tdh + spec_rad + log_patch + road_length_m, data = near_center)
-options(na.action = "na.fail") # Required for dredge to run
-model_dredge <- dredge(global, beta = "none", evaluate = T, rank = AICc)
-options(na.action = "na.omit") # set back to default
-top_model_wd_c <- get.models(model_dredge, subset = 1)[[1]]
-out <- summary(top_model_wd_c)
-out
-info <- out[[11]]
-#TotalSub
-#exp(info[2, 1])
-#exp(info[2, 2])
-#spec_rad
-#info[4, 1]
-#info[4, 2]
-#road_length_m
-#info[3, 1]
-#info[3, 2]
-
-with(summary(top_model_wd_c), 1 - deviance/null.deviance)
-model.sel(model_dredge) #estimates same signs
-summary(model.avg(model_dredge, subset = delta <= 2))
-
-#TotalSub
-#exp(info[2, 1])
-#exp(info[2, 2])
-#spec_rad
-#info[4, 1]
-#info[4, 2]
-#road_length_m
-#info[3, 1]
-#info[3, 2]
-#log_patch
-#exp(info[5, 1])
-#exp(info[5, 2])
-#car::vif(get.models(model_dredge, 1)[[1]]) # looking for less than 2
-
-# If any value is much greater than 2, this means there is quite a bit of multicollinearity, and we can try removing the variable with the highest vif.
-Here is the code you would run to accomplish this.
-
-#global2 <- update(global, .~. -spec_rad)
-#options(na.action = "na.fail") # Required for dredge to run
-#model_dredge <- dredge(global2, beta = "none", evaluate = T, rank = AICc)
-#options(na.action = "na.omit") # set back to default
-#top_model_wd_c <- get.models(model_dredge, subset = 1)[[1]]
-#out <- summary(top_model_wd_c)
-#out
-#info <- out[[12]]
-#car::vif(get.models(model_dredge, 1)[[1]]) 
-```
-
-```{r dist_predictors_overall_graphs, echo = FALSE}
-colorc = "#d95f02" 
-colorf = "#1b9e77"
-coloro = "black"
-
-# Plant Species Richness
-nd <- data.frame(log_TotalSub = seq(0, 3.2, 0.03))
-predicted.distance <- augment(top_model_wd_o, 
-                              newdata = nd, 
-                              se_fit = TRUE)
-dist_plant <- ggplot(near, aes(x = log_TotalSub, y = log(RetreatDist))) + 
-  geom_point(aes(color = Location), alpha = 0.7, 
-             size = 1) +
-  geom_line(aes(x = log_TotalSub, y = .fitted), 
-            size = 1, 
-            color = coloro, 
-            data = predicted.distance) + 
-  geom_ribbon(aes(x = log_TotalSub, 
-                  ymin = .fitted - 1.96 * .se.fit, 
-                  ymax = .fitted + 1.96 * .se.fit), 
-              fill = coloro, 
-              data = predicted.distance, 
-              inherit.aes = FALSE, 
-              alpha = 0.25) +
-#  scale_y_continuous(limits = c(min(log(near$RetreatDist)), max(log(near$RetreatDist)) + 0.1 * diff(range(log(near$RetreatDist))))) +  
-  scale_y_continuous(limits = c(2, 7.3), breaks = c(2, 3, 4, 5, 6, 7)) +  
-  scale_color_manual(values = c("Urban Center" = "#d95f02", "Urban Forest" = "#1b9e77")) +
-  theme_classic() +
-  xlab("Plant Species Richness [ln()]") +
-  ylab("Distance from Focal Web \nto Neighbor Web [ln(cm)]") + 
-  theme(text = element_text(size = 10)) + 
-  theme(axis.text.x = element_text(colour = "black", size = 10)) + 
-  theme(axis.text.y = element_text(colour = "black", size = 10)) +
-  theme(axis.title.x = element_blank(), 
-        axis.title.y = element_blank(),
-        legend.position = "none") +
-        #axis.text.x = element_blank()) + 
-#  theme(axis.text.y = element_blank()) +
-#  annotate(geom = "text", x = min(predicted.distance$log_TotalSub) + diff(range(predicted.distance$log_TotalSub))/2, y = max(log(near$RetreatDist)), label = "***", color = "black", size = 4)
-  annotate(geom = "text", x = min(predicted.distance$log_TotalSub) + diff(range(predicted.distance$log_TotalSub))/2, y = 7, label = "**", color = "black", size = 4)
-
-# Road Disturbance
-#nd <- data.frame(log_TotalSub = mean(near$log_TotalSub), 
-#                 log_tdr = seq(2.7, 7.3, 0.05))
-#predicted.distance <- augment(top_model_wd_o, 
-#                              newdata = nd, 
-#                              se_fit = TRUE)
-#dist_tdr <- ggplot(near, aes(x = log_tdr, y = log(RetreatDist))) + 
-#  geom_point(color = "grey", 
-#             size = 1) +
-#  geom_line(aes(x = log_tdr, y = .fitted), 
-#            size = 1, 
-#            color = coloro, 
-#            data = predicted.distance) + 
-#  geom_ribbon(aes(x = log_tdr, 
-#                  ymin = .fitted - 1.96 * .se.fit, 
-#                  ymax = .fitted + 1.96 * .se.fit), 
-#              fill = coloro, 
-#              data = predicted.distance, 
-#              inherit.aes = FALSE, 
-#              alpha = 0.25) +
-##  scale_y_continuous(limits = c(min(log(near$RetreatDist)), max(log(near$RetreatDist)) + 0.1 * diff(range(log(near$RetreatDist))))) + 
-#  scale_y_continuous(limits = c(2, 7), breaks = c(2, 3, 4, 5, 6, 7)) +  
-#  theme_classic() +
-#  xlab("Road Disturbance [log(vehicles/day/m)]") +
-#  ylab("Distance from Focal Web \nto Neighbor Web [log(cm)]") + 
-#  theme(text = element_text(size = 10)) + 
-#  theme(axis.text.x = element_text(colour = "black", size = 10)) + 
-#  theme(axis.text.y = element_text(colour = "black", size = 10)) +
-#  theme(axis.title.x = element_blank(), 
-#        axis.title.y = element_blank(), 
-#        axis.text.y = element_blank(),
-#        axis.text.x = element_blank()) + 
-##  annotate(geom = "text", x = min((predicted.distance$log_tdr)) + diff(range((predicted.distance$log_tdr)))/2, y = max(log(near$RetreatDist)), label = "***", color = "black", size = 4)
-#    annotate(geom = "text", x = min((predicted.distance$log_tdr)) + diff(range((predicted.distance$log_tdr)))/2, y =6.8, label = "***", color = "black", size = 4)
-
-dist_plant
-#dist_tdr
-```
-
-```{r dist_predictors_forest_graphs, echo = FALSE}
-colorc = "#d95f02" 
-colorf = "#1b9e77"
-coloro = "black"
-
-# Plant Species Richness
-nd <- data.frame(log_TotalSub = seq(1.94, 3.14, 0.015), 
-                 log_tdr = mean(near_forest$log_tdr),
-                 log_tdh = mean(near_forest$log_tdh),
-                 tree100m = mean(near_forest$tree100m))
-predicted.distance <- augment(top_model_wd_f, 
-                              newdata = nd, 
-                              se_fit = TRUE)
-dist_forest_plant <- ggplot(near, aes(x = log_TotalSub, y = log(RetreatDist))) + 
-  geom_point(aes(color = Location), alpha = 0.5, 
-             size = 1) +
-  geom_line(aes(x = log_TotalSub, y = .fitted), 
-            size = 1, 
-            color = colorf, 
-            data = predicted.distance) + 
-  geom_ribbon(aes(x = log_TotalSub, 
-                  ymin = .fitted - 1.96 * .se.fit, 
-                  ymax = .fitted + 1.96 * .se.fit), 
-              fill = colorf, 
-              data = predicted.distance, 
-              inherit.aes = FALSE, 
-              alpha = 0.25) +
-#  scale_y_continuous(limits = c(min(log(near_forest$RetreatDist)), max(log(near_forest$RetreatDist)) + 0.1 * diff(range(log(near_forest$RetreatDist))))) +  
-  scale_y_continuous(limits = c(4, 7), breaks = c(4, 5, 6, 7)) +  
-  scale_color_manual(values = c("Urban Center" = "#d95f02", "Urban Forest" = "#1b9e77")) +
-  theme_classic() +
-  xlab("Plant Species Richness [log()]") +
-  ylab("Distance from Focal Web \nto Neighbor Web [log(cm)]") + 
-  theme(text = element_text(size = 10)) + 
-  theme(axis.text.x = element_text(colour = "black", size = 10)) + 
-  theme(axis.text.y = element_text(colour = "black", size = 10)) +
-  theme(axis.title.x = element_blank(), 
-        axis.title.y = element_blank(),
-        legend.position = "none") + 
-#  theme(axis.text.x = element_blank(), 
-#        axis.text.y = element_blank()) +
-#  annotate(geom = "text", x = min(predicted.distance$log_TotalSub) + diff(range(predicted.distance$log_TotalSub))/2, y = max(log(near_forest$RetreatDist)), label = "***", color = "black", size = 4)
-  annotate(geom = "text", x = min(predicted.distance$log_TotalSub) + diff(range(predicted.distance$log_TotalSub))/2, y = 7, label = "***", color = "black", size = 4)
-
-# Highway Disturbance
-nd <- data.frame(log_TotalSub = mean(near_forest$log_TotalSub), 
-                 log_tdr = mean(near_forest$log_tdr),
-                 log_tdh = seq(2.76, 3.89, 0.01),
-                 tree100m = mean(near_forest$tree100m))
-predicted.distance <- augment(top_model_wd_f, 
-                              newdata = nd, 
-                              se_fit = TRUE)
-dist_forest_tdh <- ggplot(near, aes(x = log_tdh, y = log(RetreatDist))) + 
-  geom_point(color = "grey", 
-             size = 1) +
-  geom_line(aes(x = log_tdh, y = .fitted), 
-            size = 1, 
-            color = colorf, 
-            data = predicted.distance) + 
-  geom_ribbon(aes(x = log_tdh, 
-                  ymin = .fitted - 1.96 * .se.fit, 
-                  ymax = .fitted + 1.96 * .se.fit), 
-              fill = colorf, 
-              data = predicted.distance, 
-              inherit.aes = FALSE, 
-              alpha = 0.25) +
-#  scale_y_continuous(limits = c(min(log(near_forest$RetreatDist)), max(log(near_forest$RetreatDist)) + 0.1 * diff(range(log(near_forest$RetreatDist))))) +  
-  scale_y_continuous(limits = c(4, 7), breaks = c(4, 5, 6, 7)) +  
-  theme_classic() +
-  xlab("Highway Disturbance [log(vehicles/day/m)]") +
-  ylab("Distance from Focal Web \nto Neighbor Web [log(cm)]") + 
-  theme(text = element_text(size = 10)) + 
-  theme(axis.text.x = element_text(colour = "black", size = 10)) + 
-  theme(axis.text.y = element_text(colour = "black", size = 10)) +
-  theme(axis.title.x = element_blank(), 
-        axis.title.y = element_blank(), 
-        axis.text.y = element_blank()) + 
-#  theme(axis.text.x = element_blank()) +
-#  annotate(geom = "text", x = min((predicted.distance$log_tdh)) + diff(range((predicted.distance$log_tdh)))/2, y = max(log(near_forest$RetreatDist)), label = "***", color = "black", size = 4)
-  annotate(geom = "text", x = min((predicted.distance$log_tdh)) + diff(range((predicted.distance$log_tdh)))/2, y = 7, label = "***", color = "black", size = 4)
-
-# Road Disturbance
-nd <- data.frame(log_TotalSub = mean(near_forest$log_TotalSub), 
-                 log_tdr = seq(2.73, 6.22, 0.04),
-                 log_tdh = mean(near_forest$log_tdh),
-                 tree100m = mean(near_forest$tree100m))
-predicted.distance <- augment(top_model_wd_f, 
-                              newdata = nd, 
-                              se_fit = TRUE)
-dist_forest_tdr <- ggplot(near_forest, aes(x = log_tdr, y = log(RetreatDist))) + 
-  geom_point(color = "grey", 
-             size = 1) +
-  geom_line(aes(x = log_tdr, y = .fitted), 
-            size = 1, 
-            color = colorf, 
-            data = predicted.distance) + 
-  geom_ribbon(aes(x = log_tdr, 
-                  ymin = .fitted - 1.96 * .se.fit, 
-                  ymax = .fitted + 1.96 * .se.fit), 
-              fill = colorf, 
-              data = predicted.distance, 
-              inherit.aes = FALSE, 
-              alpha = 0.25) +
-#  scale_y_continuous(limits = c(min(log(near_forest$RetreatDist)), max(log(near_forest$RetreatDist)) + 0.1 * diff(range(log(near_forest$RetreatDist))))) +  
-  scale_y_continuous(limits = c(4, 7), breaks = c(4, 5, 6, 7)) +  
-  theme_classic() +
-  xlab("Road Disturbance [log(vehicles/day/m)]") +
-  ylab("Distance from Focal Web \nto Neighbor Web [log(cm)]") + 
-  theme(text = element_text(size = 10)) + 
-  theme(axis.text.x = element_text(colour = "black", size = 10)) + 
-  theme(axis.text.y = element_text(colour = "black", size = 10)) +
-  theme(axis.title.x = element_blank(), 
-        axis.title.y = element_blank(), 
-        axis.text.y = element_blank()) + 
-#  theme(axis.text.x = element_blank()) +
-#  annotate(geom = "text", x = min((predicted.distance$log_tdr)) + diff(range((predicted.distance$log_tdr)))/2, y = max(log(near_forest$RetreatDist)), label = "***", color = "black", size = 4)
-  annotate(geom = "text", x = min((predicted.distance$log_tdr)) + diff(range((predicted.distance$log_tdr)))/2, y = 7, label = "***", color = "black", size = 4)
-
-# Tree
-nd <- data.frame(log_TotalSub = mean(near_forest$log_TotalSub), 
-                 log_tdr = mean(near_forest$log_tdr),
-                 log_tdh = mean(near_forest$log_tdh),
-                 tree100m = seq(31.37, 65.87, 0.35))
-predicted.distance <- augment(top_model_wd_f, 
-                              newdata = nd, 
-                              se_fit = TRUE)
-dist_forest_tree <- ggplot(near_forest, aes(x = (tree100m), y = log(RetreatDist))) + 
-  geom_point(color = "grey", 
-             size = 1) +
-  geom_line(aes(x = (tree100m), y = .fitted), 
-            size = 1, 
-            color = colorf, 
-            data = predicted.distance) + 
-  geom_ribbon(aes(x = (tree100m), 
-                  ymin = .fitted - 1.96 * .se.fit, 
-                  ymax = .fitted + 1.96 * .se.fit), 
-              fill = colorf, 
-              data = predicted.distance, 
-              inherit.aes = FALSE, 
-              alpha = 0.25) +
-#  scale_y_continuous(limits = c(min(log(near_forest$RetreatDist)), max(log(near_forest$RetreatDist)) + 0.1 * diff(range(log(near_forest$RetreatDist))))) +  
-  scale_y_continuous(limits = c(4, 7), breaks = c(4, 5, 6, 7)) +  
-  theme_classic() +
-  xlab("Percent Tree Cover [%]") +
-  ylab("Distance from Focal Web \nto Neighbor Web [log(cm)]") + 
-  theme(text = element_text(size = 10)) + 
-  theme(axis.text.x = element_text(colour = "black", size = 10)) + 
-  theme(axis.text.y = element_text(colour = "black", size = 10)) +
-  theme(axis.title.x = element_blank(), 
-        axis.title.y = element_blank(), 
-        axis.text.y = element_blank()) + 
-#  theme(axis.text.x = element_blank()) +
-#  annotate(geom = "text", x = min((predicted.distance$tree100m)) + diff(range((predicted.distance$tree100m)))/2, y = max(log(near_forest$RetreatDist)), label = "***", color = "black", size = 4)
-  annotate(geom = "text", x = min((predicted.distance$tree100m)) + diff(range((predicted.distance$tree100m)))/2, y = 7, label = "***", color = "black", size = 4)
-
-dist_forest_plant
-dist_forest_tdr
-dist_forest_tdh
-dist_forest_tree
-```
-
-```{r dist_predictors_center_graphs, echo = FALSE}
-colorc = "#d95f02" 
-colorf = "#1b9e77"
-coloro = "black"
-
-# Plant Species Richness
-#nd <- data.frame(log_TotalSub = seq(0, 1.8, 0.02), 
-#                 spec_rad = mean(near_center$spec_rad),
-#                 road_length_m = mean(near_center$road_length_m))
-#predicted.distance <- augment(top_model_wd_c, 
-#                              newdata = nd, 
-#                              se_fit = TRUE)
-#dist_center_plant <- ggplot(near_center, aes(x = log_TotalSub, y = log(RetreatDist))) + 
-#  geom_point(color = "grey", 
-#             size = 1) +
-#  geom_line(aes(x = log_TotalSub, y = .fitted), 
-#            size = 1, 
-#            color = colorc, 
-#            data = predicted.distance) + 
-#  geom_ribbon(aes(x = log_TotalSub, 
-#                  ymin = .fitted - 1.96 * .se.fit, 
-#                  ymax = .fitted + 1.96 * .se.fit), 
-#              fill = colorc, 
-#              data = predicted.distance, 
-#              inherit.aes = FALSE, 
-#              alpha = 0.25) +
-##  scale_y_continuous(limits = c(min(log(near_center$RetreatDist)), max(log(near_center$RetreatDist)) + 0.1 * diff(range(log(near_center$RetreatDist))))) +  
-#  scale_y_continuous(limits = c(2, 7), breaks = c(2, 3, 4, 5, 6, 7)) +  
-#  theme_classic() +
-#  xlab("Plant Species Richness [log()]") +
-#  ylab("Distance from Focal Web \nto Neighbor Web [log(cm)]") + 
-#  theme(text = element_text(size = 10)) + 
-#  theme(axis.text.x = element_text(colour = "black", size = 10)) + 
-#  theme(axis.text.y = element_text(colour = "black", size = 10)) +
-#  theme(axis.title.x = element_blank(), 
-#        axis.title.y = element_blank()) + 
-##  theme(axis.text.x = element_blank(), 
-##        axis.text.y = element_blank()) +
-##  annotate(geom = "text", x = min(predicted.distance$log_TotalSub) + diff(range(predicted.distance$log_TotalSub))/2, y = max(log(near_center$RetreatDist)), label = "***", color = "black", size = 4)
-#  annotate(geom = "text", x = min(predicted.distance$log_TotalSub) + diff(range(predicted.distance$log_TotalSub))/2, y = 7, label = "***", color = "black", size = 4)
-
-# Spectral Radiance
-#nd <- data.frame(log_TotalSub = mean(near_center$log_TotalSub), 
-#                 spec_rad = seq(149, 163, 0.15),
-#                 road_length_m = mean(near_center$road_length_m))
-#predicted.distance <- augment(top_model_wd_c, 
-#                              newdata = nd, 
-#                              se_fit = TRUE)
-#dist_center_spec <- ggplot(near_center, aes(x = (spec_rad), y = log(RetreatDist))) + 
-#  geom_point(color = "grey", 
-#             size = 1) +
-#  geom_line(aes(x = (spec_rad), y = .fitted), 
-#            size = 1, 
-#            color = colorc, 
-#            data = predicted.distance) + 
-#  geom_ribbon(aes(x = (spec_rad), 
-#                  ymin = .fitted - 1.96 * .se.fit, 
-#                  ymax = .fitted + 1.96 * .se.fit), 
-#              fill = colorc, 
-#              data = predicted.distance, 
-#              inherit.aes = FALSE, 
-#              alpha = 0.25) +
-##  scale_y_continuous(limits = c(min(log(near_center$RetreatDist)), max(log(near_center$RetreatDist)) + 0.1 * diff(range(log(near_center$RetreatDist))))) +  
-#  scale_y_continuous(limits = c(2, 7), breaks = c(2, 3, 4, 5, 6, 7)) +  
-#  theme_classic() +
-#  xlab("Spectral Radiance \n[Watts/(m² * sr * µm)]") + 
-#  ylab("Distance from Focal Web \nto Neighbor Web [log(cm)]") + 
-#  theme(text = element_text(size = 10)) + 
-#  theme(axis.text.x = element_text(colour = "black", size = 10)) + 
-#  theme(axis.text.y = element_text(colour = "black", size = 10)) +
-#  theme(axis.title.x = element_blank(), 
-#        axis.title.y = element_blank(), 
-#        axis.text.y = element_blank()) + 
-##  theme(axis.text.x = element_blank()) +
-##  annotate(geom = "text", x = min((predicted.distance$spec_rad)) + diff(range((predicted.distance$spec_rad)))/2, y = max(log(near_center$RetreatDist)), label = "***", color = "black", size = 4)
-#  annotate(geom = "text", x = min((predicted.distance$spec_rad)) + diff(range((predicted.distance$spec_rad)))/2, y = 7, label = "***", color = "black", size = 4)
-
-# Road Length
-nd <- data.frame(road_length_m = seq(47, 117, 0.6))
-predicted.distance <- augment(top_model_wd_c, 
-                              newdata = nd, 
-                              se_fit = TRUE)
-dist_center_road <- ggplot(near, aes(x = (road_length_m), y = log(RetreatDist))) + 
-  geom_point(aes(color = Location), alpha = 0.5, 
-             size = 1) +
-  geom_line(aes(x = (road_length_m), y = (.fitted)), 
-            size = 1, 
-            color = colorc, 
-            data = predicted.distance) + 
-  geom_ribbon(aes(x = (road_length_m), 
-                  ymin = .fitted - 1.96 * .se.fit, 
-                  ymax = .fitted + 1.96 * .se.fit), 
-              fill = colorc, 
-              data = predicted.distance, 
-              inherit.aes = FALSE, 
-              alpha = 0.25) +
-#  scale_y_continuous(limits = c(min(log(near_center$RetreatDist)), max(log(near_center$RetreatDist)) + 0.1 * diff(range(log(near_center$RetreatDist))))) +  
-  scale_y_continuous(limits = c(2, 7), breaks = c(2, 3, 4, 5, 6, 7)) +  
-  scale_color_manual(values = c("Urban Center" = "#d95f02", "Urban Forest" = "#1b9e77")) +
-  theme_classic() +
-  xlab("Total Road Length [m]") +
-  ylab("Distance from Focal Web \nto Neighbor Web [ln(cm)]") + 
-  theme(text = element_text(size = 10)) + 
-  theme(axis.text.x = element_text(colour = "black", size = 10)) + 
-  theme(axis.text.y = element_text(colour = "black", size = 10)) +
-  theme(axis.title.x = element_blank(), 
-        axis.title.y = element_blank(), 
-        #axis.text.y = element_blank(),
-        legend.position = "none") + 
-#  theme(axis.text.x = element_blank()) +
-#  annotate(geom = "text", x = min((predicted.distance$road_length_m)) + diff(range((predicted.distance$road_length_m)))/2, y = max(log(near_center$RetreatDist)), label = "***", color = "black", size = 4)
-  annotate(geom = "text", x = 55, y = 6.8, label = "*", color = "black", size = 4)
-
-#dist_center_plant
-#dist_center_spec
-dist_center_road
-```
-
-### Web Distance by Land
-
-```{r dist_land_stats}
-dist_land <- glm(round(RetreatDist, 0) ~ Land, data = near, family = poisson)
-summary(dist_land)
-car::Anova(dist_land, test.statistic = "LR")
-comp <- glht(dist_land, linfct = mcp(Land = "Tukey"))
-summary(comp)
-
-dist_land_nb <- glm.nb(round(RetreatDist, 0) ~ Land, data = near)
-summary(dist_land_nb)
-car::Anova(dist_land_nb, test.statistic = "LR")
-comp <- glht(dist_land_nb, linfct = mcp(Land = "Tukey"))
-summary(comp)
-```
-
-```{r dist_land_graph}
-#near <- near %>% 
-#  mutate(Land = fct_relevel(Land, "Deciduous Forest", 
-#                            "Woody Wetlands", 
-#                            "Urban, High", 
-#                            "Urban, Medium", 
-#                            "Urban, Low"))
-nd <- data.frame(Land = factor(levels(sites$Land)))
-predictions <- augment(dist_land_nb, newdata = nd, se_fit = TRUE, type.predict = "response")
-predictions <- predictions %>% 
-  rename("response" = ".fitted", "SE" = ".se.fit")
-#predictions <- summary(emmeans(dist_land, ~Land),type = "response")
-
-dist_land_plot <- ggplot(near, aes(x = Land, y = RetreatDist)) + 
-  geom_jitter(color = "grey", width = 0.1, size = 0.5) +
-  geom_point(aes(x = Land, y = response, color = Land), size = 2, data = predictions) + 
-  geom_errorbar(aes(x = Land, 
-                  ymin = response - SE, 
-                  ymax = response + SE, color = Land), data = predictions, inherit.aes = FALSE, width = 0.25, size = 1) +
-  theme_classic() +
-  scale_color_manual(values = c("Deciduous Forest" = "#1b9e77", "Woody Wetlands" = "#1b9e77", "Urban, High" = "#d95f02", "Urban, Medium" = "#d95f02", "Urban, Low" = "#d95f02")) +
-  xlab("Land Cover Class") +
-  ylab("Distance from Focal \nWeb to Neighbor Web [cm]") + 
-  theme(text = element_text(size = 10)) + 
-  theme(axis.text.x=element_text(colour="black", size=10)) + 
-  theme(axis.text.y=element_text(colour="black", size=10)) +
-  theme(legend.position = "none") +
-  theme(axis.text.x = element_text(angle = 90, vjust = 1, hjust=1))# +
-  #annotate(geom="text", x=1, y=max(near$RetreatDist), label="A", color="black", size = 3) +
-  #annotate(geom="text", x=2, y=max(near$RetreatDist), label="A", color="black", size = 3) +
-  #annotate(geom="text", x=3, y=max(near$RetreatDist), label="AC", color="black", size = 3) +
-  #nnotate(geom="text", x=4, y=max(near$RetreatDist), label="B", color="black", size = 3) +
-  #annotate(geom="text", x=5, y=max(near$RetreatDist), label="B", color="black", size = 3)
-
-dist_land_plot
-```
-
-**Distance between webs significantly varies** by land cover class (Chi = 3629.3, df = 4, p < 0.001).
-
-## Response Variable: Web Height
-
-### Web Height by Location
-
-```{r height_location_stats}
-webs$RetreatHeight[webs$RetreatHeight == 0] <- 0.1
-ggarrange(ggplot(webs, aes(x = RetreatHeight)) +
-            geom_density(),
-          ggplot(webs, aes(x = log(RetreatHeight))) +
-            geom_density(), ncol = 2)
-
-shapiro.test(webs$RetreatHeight) # not normal
-shapiro.test(log(webs$RetreatHeight)) # not normal
-
-height <- glmer(round(RetreatHeight, 0) ~ Location + (1 | ID), data = webs, family = poisson)
-summary(height)
-
-height.nb <- glmer.nb(round(RetreatHeight, 0) ~ Location + (1 | ID), data = webs)
-summary(height.nb)
-
-subheight.nb <- glmer.nb(round(SubHeight, 0) ~ Location + (1 | ID), data = webs)
-summary(subheight.nb)
-
-height2 <- lmer(log(RetreatHeight) ~ Location + (1 | ID), data = webs)
-summary(height2)
-
-height_prop <- glmmTMB(Proportion ~ Location + (1|ID), data = webs, family = "beta")
-summary(height_prop)
-```
-
-```{r height_location_assumptions, echo = FALSE}
-# As is, Poisson
-test_height <- augment(height.nb, data = webs)
-resid_height <- ggplot(test_height, aes(x = .fitted, y = .resid)) + 
-  geom_point() + 
-  geom_smooth() +
-  geom_hline(yintercept = 0) +
-  xlab("Fitted Values") +
-  ylab("Standardized \nResiduals") +
-  theme_classic() +
-  theme(text = element_text(size = 14, color = "black")) +
-  theme(axis.text.x=element_text(color="black", size=14)) + 
-  theme(axis.text.y=element_text(color="black", size=14))
-
-y <- quantile(test_height$.resid, c(0.25, 0.75))
-x <- qnorm(c(0.25, 0.75))
-slope <- diff(y)/diff(x)
-int <- y[1L] - slope * x[1L]
-
-qq_height <- ggplot(test_height, aes(sample = .resid)) + 
-  stat_qq() + 
-  geom_abline(slope = slope, intercept = int) +
-  xlab("Theoretical Quantiles") +
-  ylab("Sample Quantiles") +
-  theme_classic() +
-  theme(text = element_text(size = 14, color = "black")) +
-  theme(axis.text.x=element_text(color="black", size=14)) + 
-  theme(axis.text.y=element_text(color="black", size=14))
-
-scaleloc_height <- ggplot(test_height, aes(x = .fitted, y = sqrt(abs(.resid)))) + 
-  geom_point() + 
-  geom_smooth() + 
-  geom_hline(yintercept = 0.83) +
-  xlab("Fitted Values") +
-  ylab("Sqrt Standardized \nResiduals") +
-  theme_classic() +
-  theme(text = element_text(size = 14, color = "black")) +
-  theme(axis.text.x=element_text(color="black", size=14)) + 
-  theme(axis.text.y=element_text(color="black", size=14))
-
-lev_height <- ggplot(test_height, aes(.hat, .resid)) +
- geom_vline(colour = "black", xintercept = 0) +
-  geom_hline(colour = "black", yintercept = 0) +
-  geom_point(aes(size = .cooksd)) + geom_smooth(se = FALSE) +
-  xlab("Theoretical Quantiles") +
-  ylab("Sample Quantiles") +
-  labs(size = "Cook's \nDistance") +
-  theme_classic() +
-  theme(text = element_text(size = 14, color = "black")) +
-  theme(axis.text.x=element_text(color="black", size=14)) + 
-  theme(axis.text.y=element_text(color="black", size=14))
-
-ggarrange(resid_height, qq_height, scaleloc_height, lev_height, 
-          labels = c("A", "B", "C", "D"),
-          ncol = 2, nrow = 2)
-
-# Log-transformed, Normal
-test_height2 <- augment(height2, data = webs)
-resid_height2 <- ggplot(test_height2, aes(x = .fitted, y = .resid)) + 
-  geom_point() + 
-  geom_smooth() +
-  geom_hline(yintercept = 0) +
-  xlab("Fitted Values") +
-  ylab("Standardized \nResiduals") +
-  theme_classic() +
-  theme(text = element_text(size = 14, color = "black")) +
-  theme(axis.text.x=element_text(color="black", size=14)) + 
-  theme(axis.text.y=element_text(color="black", size=14))
-
-y <- quantile(test_height2$.resid, c(0.25, 0.75))
-x <- qnorm(c(0.25, 0.75))
-slope <- diff(y)/diff(x)
-int <- y[1L] - slope * x[1L]
-
-qq_height2 <- ggplot(test_height2, aes(sample = .resid)) + 
-  stat_qq() + 
-  geom_abline(slope = slope, intercept = int) +
-  xlab("Theoretical Quantiles") +
-  ylab("Sample Quantiles") +
-  theme_classic() +
-  theme(text = element_text(size = 14, color = "black")) +
-  theme(axis.text.x=element_text(color="black", size=14)) + 
-  theme(axis.text.y=element_text(color="black", size=14))
-
-scaleloc_height2 <- ggplot(test_height2, aes(x = .fitted, y = sqrt(abs(.resid)))) + 
-  geom_point() + 
-  geom_smooth() + 
-  geom_hline(yintercept = 0.83) +
-  xlab("Fitted Values") +
-  ylab("Sqrt Standardized \nResiduals") +
-  theme_classic() +
-  theme(text = element_text(size = 14, color = "black")) +
-  theme(axis.text.x=element_text(color="black", size=14)) + 
-  theme(axis.text.y=element_text(color="black", size=14))
-
-lev_height2 <- ggplot(test_height2, aes(.hat, .resid)) +
- geom_vline(colour = "black", xintercept = 0) +
-  geom_hline(colour = "black", yintercept = 0) +
-  geom_point(aes(size = .cooksd)) + geom_smooth(se = FALSE) +
-  xlab("Theoretical Quantiles") +
-  ylab("Sample Quantiles") +
-  labs(size = "Cook's \nDistance") +
-  theme_classic() +
-  theme(text = element_text(size = 14, color = "black")) +
-  theme(axis.text.x=element_text(color="black", size=14)) + 
-  theme(axis.text.y=element_text(color="black", size=14))
-
-ggarrange(resid_height2, qq_height2, scaleloc_height2, lev_height2, 
-          labels = c("A", "B", "C", "D"),
-          ncol = 2, nrow = 2)
-```
-
-```{r height_location_graph, echo = FALSE}
-# Negative Binomial
-predictions <- expand.grid(Location = levels(factor(webs$Location)))
-predictions$response <- predict(height.nb, newdata = predictions, se.fit = TRUE, re.form = NA, type = "response")
-
-myFunc <- function(mm) {
-    predict(mm, newdata = predictions, re.form = ~0, type = "response")
-}
-#bigBoot_height_location_nb <- bootMer(height.nb, myFunc, nsim = 1000)
-#saveRDS(bigBoot_height_location_nb, file = "bootstrapping/bigBoot_height_location_nb.Rds")
-bigBoot_height_location_nb <- readRDS("bootstrapping/bigBoot_height_location_nb.Rds")
-predSE <- t(apply(bigBoot_height_location_nb$t, MARGIN = 2, FUN = sd))
-predictions$SE <- predSE[1, ]
-#predictions2 <- summary(emmeans(height, ~Location | Neighbor,type = "response"))
-
-nb_plot_height <- ggplot(webs, aes(x = Location, y = RetreatHeight)) + 
-  geom_jitter(color = "grey", width = 0.1) +
-  geom_point(aes(x = Location, y = response, color = Location), size = 2, data = predictions) +
-  geom_errorbar(aes(x= Location, 
-                    ymin = response - SE, 
-                    ymax = response + SE, 
-                    color = Location), data = predictions, inherit.aes = FALSE, width = 0.15, size = 1) +
-    scale_color_manual(values = c("Urban Center" = "#d95f02", "Urban Forest" = "#1b9e77")) +
-    scale_x_discrete(labels=c("Urban Forest" = "Urban \nForest \nN = 30", "Urban Center" = "Urban \nCenter \nN = 101")) +
-    theme_classic() +
-    scale_y_continuous(limits = c(0, 210), breaks = c(0, 35, 70, 105, 140, 175, 210)) +
-    ylab("Web Height [cm]") + 
-    theme(text = element_text(size = 10)) + 
-    theme(axis.text.x = element_text(colour = "black", size = 10)) + 
-    theme(axis.text.y = element_text(colour = "black", size = 10),
-        axis.title.x = element_blank()) +
-    theme(legend.position = "none") +
-    annotate(geom = "text", x = 1.5, y = 210, label = "*", color = "black", size = 5)
-
-# raw data
-raw <- webs %>% 
-  group_by(Location) %>% 
-  summarise(mean = mean(RetreatHeight),
-            se = plotrix::std.error(RetreatHeight))
-
-raw_plot_height <- ggplot(webs, aes(x = Location, y = RetreatHeight)) + 
-  geom_jitter(color = "grey", width = 0.1) +
-  geom_point(aes(x = Location, y = mean, color = Location), size = 2, data = raw) +
-  geom_errorbar(aes(x= Location, 
-                    ymin = mean - se, 
-                    ymax = mean + se, 
-                    color = Location), data = raw, inherit.aes = FALSE, width = 0.15, size = 1.5) +
-    scale_color_manual(values = c("Urban Center" = "#d95f02", "Urban Forest" = "#1b9e77")) +
-    scale_x_discrete(labels=c("Urban Forest" = "Urban \nForest \nN = 10", "Urban Center" = "Urban \nCenter \nN = 12")) +
-    theme_classic() +
-    scale_y_continuous(limits = c(0, 210), breaks = c(0, 35, 70, 105, 140, 175, 210)) +
-    ylab("Web Height [cm]") + 
-    theme(text = element_text(size = 10)) + 
-    theme(axis.text.x = element_text(colour = "black", size = 10)) + 
-    theme(axis.text.y = element_text(colour = "black", size = 10),
-        axis.title.x = element_blank()) +
-    theme(legend.position = "none")
-
-# Non-transformed, poisson distribution
-predictions <- expand.grid(Location = levels(factor(webs$Location)))
-predictions$response <- predict(height, newdata = predictions, se.fit = TRUE, re.form = NA, type = "response")
-
-myFunc <- function(mm) {
-    predict(mm, newdata = predictions, re.form = ~0, type = "response")
-}
-#bigBoot_height_location <- bootMer(height, myFunc, nsim = 1000)
-#saveRDS(bigBoot_height_location, file = "bootstrapping/bigBoot_height_location.Rds")
-bigBoot_height_location <- readRDS("bootstrapping/bigBoot_height_location.Rds")
-predSE <- t(apply(bigBoot_height_location$t, MARGIN = 2, FUN = sd))
-predictions$SE <- predSE[1, ]
-#predictions2 <- summary(emmeans(height, ~Location | Neighbor,type = "response"))
-
-poisson_plot_height <- ggplot(webs, aes(x = Location, y = RetreatHeight)) + 
-  geom_jitter(color = "grey", width = 0.1) +
-  geom_point(aes(x = Location, y = response, color = Location), size = 2, data = predictions) +
-  geom_errorbar(aes(x= Location, 
-                    ymin = response - SE, 
-                    ymax = response + SE, 
-                    color = Location), data = predictions, inherit.aes = FALSE, width = 0.15, size = 1.5) +
-    scale_color_manual(values = c("Urban Center" = "#d95f02", "Urban Forest" = "#1b9e77")) +
-    scale_x_discrete(labels=c("Urban Forest" = "Urban \nForest \nN = 10", "Urban Center" = "Urban \nCenter \nN = 12")) +
-    theme_classic() +
-    scale_y_continuous(limits = c(0, 210), breaks = c(0, 35, 70, 105, 140, 175, 210)) +
-    ylab("Web Height [cm]") + 
-    theme(text = element_text(size = 10)) + 
-    theme(axis.text.x = element_text(colour = "black", size = 10)) + 
-    theme(axis.text.y = element_text(colour = "black", size = 10),
-        axis.title.x = element_blank()) +
-    theme(legend.position = "none") +
-    annotate(geom = "text", x = 1.5, y = 210, label = "*", color = "black", size = 5)
-
-# Let's look at the log-transformed response variable since that is normal
-predictions <- expand.grid(Location = levels(factor(webs$Location)))
-predictions$response <- predict(height2, newdata = predictions, se.fit = TRUE, re.form = NA, type = "response")
-
-myFunc <- function(mm) {
-    predict(mm, newdata = predictions, re.form = ~0, type = "response")
-}
-#bigBoot_height_location2 <- bootMer(height2, myFunc, nsim = 1000)
-#saveRDS(bigBoot_height_location2, file = "bootstrapping/bigBoot_height_location2.Rds")
-bigBoot_height_location2 <- readRDS("bootstrapping/bigBoot_height_location2.Rds")
-predSE <- t(apply(bigBoot_height_location2$t, MARGIN = 2, FUN = sd))
-predictions$SE <- predSE[1, ]
-#predictions2 <- summary(emmeans(height2, ~Location | Neighbor,type = "response"))
-
-log_plot_height <- ggplot(webs, aes(x = Location, y = (RetreatHeight))) + 
-  geom_jitter(color = "grey", width = 0.1) +
-  geom_point(aes(x = Location, y = exp(response), color = Location), size = 2, data = predictions) +
-  geom_errorbar(aes(x= Location, 
-                    ymin = exp(response - SE), 
-                    ymax = exp(response + SE), 
-                    color = Location), data = predictions, inherit.aes = FALSE, width = 0.15, size = 1.5) +
-    scale_color_manual(values = c("Urban Center" = "#d95f02", "Urban Forest" = "#1b9e77")) +
-    scale_x_discrete(labels=c("Urban Forest" = "Urban \nForest \nN = 10", "Urban Center" = "Urban \nCenter \nN = 12")) +
-    theme_classic() +
-    scale_y_continuous(limits = c(0, 210), breaks = c(0, 35, 70, 105, 140, 175, 210)) +
-    ylab("Web Height [cm]") + 
-    theme(text = element_text(size = 10)) + 
-    theme(axis.text.x = element_text(colour = "black", size = 10)) + 
-    theme(axis.text.y = element_text(colour = "black", size = 10),
-        axis.title.x = element_blank()) +
-    theme(legend.position = "none") +
-    annotate(geom = "text", x = 1.5, y = 210, label = "*", color = "black", size = 5)
-
-ggarrange(raw_plot_height, 
-          poisson_plot_height, 
-          log_plot_height,
-          nb_plot_height,
-          labels = c("Raw Data", "Poisson Distribution", "Log-Transformed", "Negative Binomial"),
-          nrow = 1, 
-          common.legend = TRUE)
-```
-
-**Webs are significantly higher in the urban forest** than the urban center (z = -2.44, df = 1, 21, p = 0.015).
-
-### Web Height by Predictors
-
-```{r height_predictors_stats}
-#overall
-models = list(ceiling(RetreatHeight) ~ 1,
-              ceiling(RetreatHeight) ~ log_TotalSub,
-              ceiling(RetreatHeight) ~ log_tdr, 
-              ceiling(RetreatHeight) ~ log_tdh,
-              ceiling(RetreatHeight) ~ log_TotalSub + log_tdr,
-              ceiling(RetreatHeight) ~ log_TotalSub + log_tdh,
-              ceiling(RetreatHeight) ~ log_tdr + log_tdh,
-              ceiling(RetreatHeight) ~ log_TotalSub + log_tdr + log_tdh)
-fits = lapply(models, glm, data = webs, family = "poisson")
-modnames = sapply(models, function(ff)deparse(ff[[3]]))
-pander(aictab(fits, modname = modnames), caption="Table 1. AICc model selection table for Search Distance to the Focal Web.", split.tables = Inf)
-
-global <- glmer(round(RetreatHeight, 0) ~ log_TotalSub + log_tdr + log_tdh + (1 | ID), data = webs, family = poisson)
-options(na.action = "na.fail") # Required for dredge to run
-model_dredge <- dredge(global, beta = "none", evaluate = TRUE, rank = AICc)
-options(na.action = "na.omit") # set back to default
-top_model_wh_o <- get.models(model_dredge, subset = 1)[[1]]
-out <- summary(top_model_wh_o)
-out
-info <- out[[10]]
-# TotalSub
-exp(info[3, 1])
-exp(info[3, 2])
-#Traffic_Dist_Road
-exp(info[2, 1])
-exp(info[2, 1])
-
-r.squaredGLMM(top_model_wh_o) 
-model.sel(model_dredge) #estimates same signs
-out <- summary(model.avg(model_dredge, subset = delta <= 2))
-out
-info <- out[[10]]
-#tdr
-exp(info[2, 1])
-exp(info[2, 2])
-#TotalSub
-exp(info[3, 1])
-exp(info[3, 2])
-#tdh
-exp(info[4, 1])
-exp(info[4, 2])
-car::vif(get.models(model_dredge, 5)[[1]]) # looking for less than 2
-
-# Urban Forest
-webs_forest <- webs_forest %>% 
-  mutate(tree100m_frac = I(tree100m/100))
-global <- glmer(round(RetreatHeight, 0) ~ tree100m_frac + log_TotalSub + log_tdr + log_tdh + log_patch + (1 | ID), data = webs_forest, family = poisson, control = glmerControl(optimizer = "bobyqa", optCtrl = list(maxfun = 2e4)))
-options(na.action = "na.fail") # Required for dredge to run
-model_dredge <- dredge(global, beta = "none", evaluate = TRUE, rank = AICc)
-options(na.action = "na.omit") # set back to default
-top_model_wh_f <- get.models(model_dredge, subset = 1)[[1]]
-out <- summary(top_model_wh_f)
-out
-info <- out[[10]]
-
-#tree
-exp(info[2, 1])
-exp(info[2, 2])
-
-r.squaredGLMM(top_model_wh_f) 
-model.sel(model_dredge) #estimates same signs
-out <- summary(model.avg(model_dredge, subset = delta <= 2))
-out
-info <- out[[10]]
-#tree
-exp(info[2, 1])
-exp(info[2, 2])
-#TotalSub
-exp(info[3, 1])
-exp(info[3, 2])
-#tdr
-exp(info[4, 1])
-exp(info[4, 2])
-
-#car::vif(get.models(model_dredge, 1)[[1]]) # looking for less than 2
-
-# Urban Center
-global <- glmer(round(RetreatHeight, 0) ~ log_TotalSub + log_tdr + log_tdh + scale(spec_rad, center = FALSE) + log_patch + scale(road_length_m, center = FALSE) + (1 | ID), data = webs_center, family = poisson,  control = glmerControl(optimizer = "bobyqa", optCtrl = list(maxfun = 2e4)))
-options(na.action = "na.fail") # Required for dredge to run
-model_dredge <- dredge(global, beta = "none", evaluate = T, rank = AICc)
-options(na.action = "na.omit") # set back to default
-top_model_wh_c <- get.models(model_dredge, subset = 1)[[1]]
-out <- summary(top_model_wh_c)
-out
-info <- out[[10]]
-#TotalSub
-exp(info[2, 1])
-exp(info[2, 2])
-
-r.squaredGLMM(top_model_wh_c) 
-model.sel(model_dredge) #estimates same signs
-out <- summary(model.avg(model_dredge, subset = delta <= 2))
-out
-info <- out[[10]]
-#TotalSub
-exp(info[2, 1])
-exp(info[2, 2])
-#road length
-exp(info[3, 1])
-exp(info[3, 2])
-#tdh
-exp(info[4, 1])
-exp(info[4, 2])
-#tdr
-exp(info[5, 1])
-exp(info[5, 2])
-#patch
-exp(info[6, 1])
-exp(info[6, 2])
-#spec_rad
-exp(info[7, 1])
-exp(info[7, 2])
-#car::vif(get.models(model_dredge, 1)[[1]]) # looking for less than 2
-```
-
-*Overall* 
-Fixed effects:
-             Estimate Std. Error z value Pr(>|z|)    
-(Intercept)    3.1686     0.6215   5.098 3.43e-07 ***
-log_tdr       -0.1896     0.1023  -1.854  0.06378 .   **negative**
-log_TotalSub   0.4812     0.1659   2.901  0.00372 **  **positive**
-
-R-squared = 0.3671774 (marginal - fixed) 0.9521663 (conditional - fixed and random)
-
-(conditional average) 
-             Estimate Std. Error Adjusted SE z value Pr(>|z|)   
-(Intercept)    3.3701     1.2954      1.3012   2.590  0.00959 **
-log_tdr       -0.1986     0.1022      0.1032   1.924  0.05432 .  
-log_TotalSub   0.4697     0.1814      0.1830   2.567  0.01026 * 
-log_tdh       -0.3307     0.2719      0.2745   1.205  0.22832
-
-*Urban Forest*
-Fixed effects:
-              Estimate Std. Error z value Pr(>|z|)   
-(Intercept)     1.1283     0.8355   1.350  0.17687   
-tree100m_frac   5.0864     1.7266   2.946  0.00322 ** **positive**
-
-R-squared = 0.4787743 (marginal - fixed) 0.9596909 (conditional - fixed and random)
-
-(conditional average) 
-              Estimate Std. Error Adjusted SE z value Pr(>|z|)   
-(Intercept)     0.3764     1.3417      1.3881   0.271   0.7863   
-tree100m_frac   5.0033     1.7056      1.7823   2.807   0.0050 **
-log_TotalSub    0.6815     0.3801      0.3976   1.714   0.0865 . 
-log_tdr        -0.2415     0.1683      0.1769   1.365   0.1721
-
-*Urban Center*
-Fixed effects:
-             Estimate Std. Error z value Pr(>|z|)    
-(Intercept)    2.0705     0.4687   4.417    1e-05 ***
-log_TotalSub   0.6449     0.3921   1.645      0.1     **positive**
-
-R-squared = 0.1332201 (marginal - fixed) 0.9103755 (conditional - fixed and random)
-
-(conditional average) 
-                                     Estimate Std. Error Adjusted SE z value Pr(>|z|)  
-(Intercept)                            2.6980     2.7479      2.7626   0.977   0.3288  
-log_TotalSub                           0.7725     0.4093      0.4138   1.867   0.0619 .
-scale(road_length_m, center = FALSE)   1.0413     0.7533      0.7625   1.366   0.1720  
-log_tdh                               -0.3763     0.3175      0.3212   1.172   0.2413  
-log_tdr                               -0.2307     0.1466      0.1483   1.555   0.1199  
-log_patch                              0.2033     0.1934      0.1959   1.038   0.2994  
-scale(spec_rad, center = FALSE)       -5.6099     6.2722      6.3531   0.883   0.3772
-
-```{r height_predictors_stats_nb}
-#overall
-global <- glmer.nb(round(RetreatHeight, 0) ~ log_TotalSub + log_tdr + log_tdh + (1 | ID), data = webs)
-options(na.action = "na.fail") # Required for dredge to run
-model_dredge <- dredge(global, beta = "none", evaluate = TRUE, rank = AICc)
-options(na.action = "na.omit") # set back to default
-top_model_wh_o <- get.models(model_dredge, subset = 1)[[1]]
-out <- summary(top_model_wh_o)
-out
-info <- out[[10]]
-# TotalSub
-#exp(info[3, 1])
-#exp(info[3, 2])
-#Traffic_Dist_Road
-#exp(info[2, 1])
-#exp(info[2, 1])
-
-r.squaredGLMM(top_model_wh_o) # trigamma R2m
-model.sel(model_dredge) #estimates same signs
-summary(model.avg(model_dredge, subset = delta <= 2))
-
-#tdr
-#exp(info[2, 1])
-#exp(info[2, 2])
-#TotalSub
-#exp(info[3, 1])
-#exp(info[3, 2])
-#tdh
-#exp(info[4, 1])
-#exp(info[4, 2])
-car::vif(get.models(model_dredge, 5)[[1]]) # looking for less than 2
-
-# Urban Forest
-webs_forest <- webs_forest %>% 
-  mutate(tree100m_frac = I(tree100m/100))
-global <- glmer.nb(round(RetreatHeight, 0) ~ tree100m_frac + log_TotalSub + log_tdr + log_tdh + log_patch + (1 | ID), data = webs_forest, control = glmerControl(optimizer = "bobyqa", optCtrl = list(maxfun = 2e4)))
-options(na.action = "na.fail") # Required for dredge to run
-model_dredge <- dredge(global, beta = "none", evaluate = TRUE, rank = AICc)
-options(na.action = "na.omit") # set back to default
-top_model_wh_f <- get.models(model_dredge, subset = 1)[[1]]
-out <- summary(top_model_wh_f)
-out
-info <- out[[10]]
-
-#tree
-#exp(info[2, 1])
-#exp(info[2, 2])
-
-r.squaredGLMM(top_model_wh_f) #trigamma R2m
-model.sel(model_dredge) #estimates same signs
-summary(model.avg(model_dredge, subset = delta <= 2))
-
-#tree
-#exp(info[2, 1])
-#exp(info[2, 2])
-#TotalSub
-#exp(info[3, 1])
-#exp(info[3, 2])
-#tdr
-#exp(info[4, 1])
-#exp(info[4, 2])
-
-#car::vif(get.models(model_dredge, 1)[[1]]) # looking for less than 2
-
-webs_center$road_length_m_sc <- scale(webs_center$road_length_m, center = FALSE)
-
-# Urban Center
-global <- glmer.nb(round(RetreatHeight, 0) ~ log_TotalSub + log_tdr + log_tdh + scale(spec_rad, center = FALSE) + log_patch + road_length_m_sc + (1 | ID), data = webs_center)#, control = glmerControl(optimizer = "bobyqa", optCtrl = list(maxfun = 2e4)))
-options(na.action = "na.fail") # Required for dredge to run
-model_dredge <- dredge(global, beta = "none", evaluate = T, rank = AICc)
-options(na.action = "na.omit") # set back to default
-top_model_wh_c <- get.models(model_dredge, subset = 1)[[1]]
-out <- summary(top_model_wh_c)
-out
-info <- out[[10]]
-#TotalSub
-#exp(info[2, 1])
-#exp(info[2, 2])
-
-r.squaredGLMM(top_model_wh_c) 
-model.sel(model_dredge) #estimates same signs
-summary(model.avg(model_dredge, subset = delta <= 2))
-
-#TotalSub
-#exp(info[2, 1])
-#exp(info[2, 2])
-#road length
-#exp(info[3, 1])
-#exp(info[3, 2])
-#tdh
-#exp(info[4, 1])
-#exp(info[4, 2])
-#tdr
-#exp(info[5, 1])
-#exp(info[5, 2])
-#patch
-#exp(info[6, 1])
-#exp(info[6, 2])
-#spec_rad
-#exp(info[7, 1])
-#exp(info[7, 2])
-#car::vif(get.models(model_dredge, 1)[[1]]) # looking for less than 2
-```
-
-```{r height_predictor_overall_graphs}
-colorc = "#d95f02" 
-colorf = "#1b9e77"
-coloro = "black"
-
-# Plant Species Richness
-predictions <- expand.grid(log_TotalSub = seq(0, 3.15, 0.03),
-                           log_tdr = mean(webs$log_tdr))
-predictions$response <- predict(top_model_wh_o, newdata = predictions, se.fit = TRUE, re.form = NA, type = "response")
-
-myFunc <- function(mm) {
-    predict(mm, newdata = predictions, re.form = ~0, type = "response")
-}
-#bigBoot_height_overall_plant_nb <- bootMer(top_model_wh_o, myFunc, nsim = 1000)
-#saveRDS(bigBoot_height_overall_plant_nb, file = "bootstrapping/bigBoot_height_overall_plant_nb.Rds")
-bigBoot_height_overall_plant_nb <- readRDS("bootstrapping/bigBoot_height_overall_plant_nb.Rds")
-predSE <- t(apply(bigBoot_height_overall_plant_nb$t, MARGIN = 2, FUN = sd))
-predictions$SE <- predSE[1, ]
-
-height_plant <- ggplot(webs, aes(x = log_TotalSub, y = log(RetreatHeight))) + 
-  geom_point(aes(color = Location), alpha = 0.7, 
-             size = 1) +
-  geom_line(aes(x = log_TotalSub, y = log(response)), 
-            size = 1, 
-            color = coloro, 
-            data = predictions) + 
-  geom_ribbon(aes(x = log_TotalSub, 
-                  ymin = log(response - 1.96 * SE), 
-                  ymax = log(response + 1.96 * SE)), 
-              fill = coloro, 
-              data = predictions, 
-              inherit.aes = FALSE, 
-              alpha = 0.25) +
-#  scale_y_continuous(limits = c(min(log(webs$RetreatHeight)), max(log(webs$RetreatHeight)) + 0.1 * diff(range(log(webs$RetreatHeight))))) +  
-  scale_y_continuous(limits = c(-2.5, 6), breaks = c(-2, 0, 2, 4, 6)) + 
-  scale_color_manual(values = c("Urban Center" = "#d95f02", "Urban Forest" = "#1b9e77")) +
-  theme_classic() +
-  xlab("Plant Species Richness [ln()]") +
-  ylab("Web Height [ln(cm)]") + 
-  theme(text = element_text(size = 10)) + 
-  theme(axis.text.x = element_text(colour = "black", size = 10)) + 
-  theme(axis.text.y = element_text(colour = "black", size = 10)) +
-  theme(axis.title.x = element_blank(), 
-        axis.title.y = element_blank(),
-        legend.position = "none") + 
-#  theme(axis.text.x = element_blank(), 
-#        axis.text.y = element_blank()) +
-#  annotate(geom = "text", x = min(predictions$log_TotalSub) + diff(range(predictions$log_TotalSub))/2, y = max(log(webs$RetreatHeight)), label = "**", color = "black", size = 4)
-    annotate(geom = "text", x = min(predictions$log_TotalSub) + diff(range(predictions$log_TotalSub))/2, y = 5.8, label = "**", color = "black", size = 4)
-
-# Road Disturbance
-predictions <- expand.grid(log_TotalSub = mean(webs$log_TotalSub),
-                           log_tdr = seq(2.73, 7.22, 0.05))
-predictions$response <- predict(top_model_wh_o, newdata = predictions, se.fit = TRUE, re.form = NA, type = "response")
-
-myFunc <- function(mm) {
-    predict(mm, newdata = predictions, re.form = ~0, type = "response")
-}
-#bigBoot_height_overall_tdr_nb <- bootMer(top_model_wh_o, myFunc, nsim = 1000)
-#saveRDS(bigBoot_height_overall_tdr_nb, file = "bootstrapping/bigBoot_height_overall_tdr_nb.Rds")
-bigBoot_height_overall_tdr_nb <- readRDS("bootstrapping/bigBoot_height_overall_tdr_nb.Rds")
-predSE <- t(apply(bigBoot_height_overall_tdr_nb$t, MARGIN = 2, FUN = sd))
-predictions$SE <- predSE[1, ]
-
-height_tdr <- ggplot(webs, aes(x = log_tdr, y = log(RetreatHeight))) + 
-  geom_point(aes(color = Location), alpha = 0.7, 
-             size = 1) +
-  geom_line(aes(x = log_tdr, y = log(response)), 
-            size = 1, 
-            color = coloro, 
-            data = predictions) + 
-  geom_ribbon(aes(x = log_tdr, 
-                  ymin = log(response - 1.96 * SE), 
-                  ymax = log(response + 1.96 * SE)), 
-              fill = coloro, 
-              data = predictions, 
-              inherit.aes = FALSE, 
-              alpha = 0.25) +
-#  scale_y_continuous(limits = c(min(log(webs$RetreatHeight)), max(log(webs$RetreatHeight)) + 0.1 * diff(range(log(webs$RetreatHeight))))) +  
-  scale_y_continuous(limits = c(-2.5, 6), breaks = c(-2, 0, 2, 4, 6)) +  
-  scale_color_manual(values = c("Urban Center" = "#d95f02", "Urban Forest" = "#1b9e77")) +
-  theme_classic() +
-  xlab("Road Disturbance [ln(vehicles/day/m)]") +
-  ylab("Web Height [ln(cm)]") + 
-  theme(text = element_text(size = 10)) + 
-  theme(axis.text.x = element_text(colour = "black", size = 10)) + 
-  theme(axis.text.y = element_text(colour = "black", size = 10)) +
-  theme(axis.title.x = element_blank(), 
-        axis.title.y = element_blank(), 
-        #axis.text.y = element_blank(),
-        legend.position = "none") + 
-#  theme(axis.text.x = element_blank()) +
-#  annotate(geom = "text", x = min(predictions$log_tdr) + diff(range(predictions$log_tdr))/2, y = max(log(webs$RetreatHeight)), label = "N. S.", color = "black", size = 4)
-    annotate(geom = "text", x = min(predictions$log_tdr) + diff(range(predictions$log_tdr))/2, y = 5.8, label = "N. S.", color = "black", size = 3)
-
-height_plant
-height_tdr
-```
-
-```{r height_predictor_forest_graphs}
-colorc = "#d95f02" 
-colorf = "#1b9e77"
-coloro = "black"
-
-webs <- webs %>% 
-  mutate(tree100m_frac = I(tree100m/100))
-
-# Tree
-predictions <- expand.grid(tree100m_frac = seq(0.31, 0.66, 0.003))
-predictions$response <- predict(top_model_wh_f, newdata = predictions, se.fit = TRUE, re.form = NA, type = "response")
-
-myFunc <- function(mm) {
-    predict(mm, newdata = predictions, re.form = ~0, type = "response")
-}
-#bigBoot_height_forest_tree_nb <- bootMer(top_model_wh_f, myFunc, nsim = 1000)
-#saveRDS(bigBoot_height_forest_tree_nb, file = "bootstrapping/bigBoot_height_forest_tree_nb.Rds")
-bigBoot_height_forest_tree_nb <- readRDS("bootstrapping/bigBoot_height_forest_tree_nb.Rds")
-predSE <- t(apply(bigBoot_height_forest_tree_nb$t, MARGIN = 2, FUN = sd))
-predictions$SE <- predSE[1, ]
-
-height_forest_tree <- ggplot(webs, aes(x = (tree100m_frac), y = log(RetreatHeight))) + 
-  geom_point(aes(color = Location), alpha = 0.5, 
-             size = 1) +
-  geom_line(aes(x = (tree100m_frac), y = log(response)), 
-            size = 1, 
-            color = colorf, 
-            data = predictions) + 
-  geom_ribbon(aes(x = (tree100m_frac), 
-                  ymin = log(response - 1.96 * SE), 
-                  ymax = log(response + 1.96 * SE)), 
-              fill = colorf, 
-              data = predictions, 
-              inherit.aes = FALSE, 
-              alpha = 0.25) +
-  scale_y_continuous(limits = c(0, 5.2), breaks = c(0, 1, 2, 3, 4, 5)) +  
-  scale_color_manual(values = c("Urban Center" = "#d95f02", "Urban Forest" = "#1b9e77")) +
-  theme_classic() +
-  xlab("Proportion of Tree Cover in 100-Meter Buffer of Site [ln()]") +
-  ylab("Web Height [ln(cm)]") + 
-  theme(text = element_text(size = 10)) + 
-  theme(axis.text.x = element_text(colour = "black", size = 10)) + 
-  theme(axis.text.y = element_text(colour = "black", size = 10)) +
-  theme(axis.title.x = element_blank(), 
-        axis.title.y = element_blank(),
-        legend.position = "none") + 
-#  theme(axis.text.x = element_blank(), 
-#        axis.text.y = element_blank()) +
-  annotate(geom = "text", x = 0.33, y = 5, label = "**", color = "black", size = 4)
-
-height_forest_tree
-```
-
-```{r height_predictor_center_graphs}
-colorc = "#d95f02" 
-colorf = "#1b9e77"
-coloro = "black"
-
-webs$road_length_m_sc <- scale(webs$road_length_m, center = FALSE)
-
-# Plant Species Richness
-predictions <- expand.grid(log_TotalSub = seq(0, 1.80, 0.02),
-                           road_length_m_sc = mean(webs_center$road_length_m_sc))
-predictions$response <- predict(top_model_wh_c, newdata = predictions, se.fit = TRUE, re.form = NA, type = "response")
-
-myFunc <- function(mm) {
-    predict(mm, newdata = predictions, re.form = ~0, type = "response")
-}
-#bigBoot_height_center_plant_nb <- bootMer(top_model_wh_c, myFunc, nsim = 1000)
-#saveRDS(bigBoot_height_center_plant_nb, file = "bootstrapping/bigBoot_height_center_plant_nb.Rds")
-bigBoot_height_center_plant_nb <- readRDS("bootstrapping/bigBoot_height_center_plant_nb.Rds")
-predSE <- t(apply(bigBoot_height_center_plant_nb$t, MARGIN = 2, FUN = sd))
-predictions$SE <- predSE[1, ]
-
-height_center_plant <- ggplot(webs, aes(x = log_TotalSub, y = log(RetreatHeight))) + 
-  geom_point(aes(color = Location), alpha = 0.5, 
-             size = 1) +
-  geom_line(aes(x = log_TotalSub, y = log(response)), 
-            size = 1, 
-            color = colorc, 
-            data = predictions) + 
-  geom_ribbon(aes(x = log_TotalSub, 
-                  ymin = log(response - 1.96 * SE), 
-                  ymax = log(response + 1.96 * SE)), 
-              fill = colorc, 
-              data = predictions, 
-              inherit.aes = FALSE, 
-              alpha = 0.25) +
-  scale_y_continuous(limits = c(0, 5.2), breaks = c(0, 1, 2, 3, 4, 5)) +  
-  scale_color_manual(values = c("Urban Center" = "#d95f02", "Urban Forest" = "#1b9e77")) +
-  theme_classic() +
-  xlab("Plant Species Richness [ln()]") +
-  ylab("Web Height [ln(cm)]") + 
-  theme(text = element_text(size = 10)) + 
-  theme(axis.text.x = element_text(colour = "black", size = 10)) + 
-  theme(axis.text.y = element_text(colour = "black", size = 10)) +
-  theme(axis.title.x = element_blank(), 
-        axis.title.y = element_blank(),
-        legend.position = "none") + 
-#  theme(axis.text.x = element_blank(), 
-#        axis.text.y = element_blank()) +
-  annotate(geom = "text", x = 1.6, y = 5, label = "N.S.", color = "black", size = 4)
-
-# Road Length
-predictions <- expand.grid(log_TotalSub = mean(webs_center$log_TotalSub),
-                           road_length_m_sc = seq(0.5, 1.50, 0.01))
-predictions$response <- predict(top_model_wh_c, newdata = predictions, se.fit = TRUE, re.form = NA, type = "response")
-
-myFunc <- function(mm) {
-    predict(mm, newdata = predictions, re.form = ~0, type = "response")
-}
-#bigBoot_height_center_road_nb <- bootMer(top_model_wh_c, myFunc, nsim = 1000)
-#saveRDS(bigBoot_height_center_road_nb, file = "bootstrapping/bigBoot_height_center_road_nb.Rds")
-bigBoot_height_center_road_nb <- readRDS("bootstrapping/bigBoot_height_center_road_nb.Rds")
-predSE <- t(apply(bigBoot_height_center_road_nb$t, MARGIN = 2, FUN = sd))
-predictions$SE <- predSE[1, ]
-
-height_center_road <- ggplot(webs, aes(x = road_length_m_sc, y = log(RetreatHeight))) + 
-  geom_point(aes(color = Location), alpha = 0.5, 
-             size = 1) +
-  geom_line(aes(x = road_length_m_sc, y = log(response)), 
-            size = 1, 
-            color = colorc, 
-            data = predictions) + 
-  geom_ribbon(aes(x = road_length_m_sc, 
-                  ymin = log(response - 1.96 * SE), 
-                  ymax = log(response + 1.96 * SE)), 
-              fill = colorc, 
-              data = predictions, 
-              inherit.aes = FALSE, 
-              alpha = 0.25) +
-  scale_y_continuous(limits = c(-2.5, 6), breaks = c(-2, 0, 2, 4, 6)) +  
-  scale_color_manual(values = c("Urban Center" = "#d95f02", "Urban Forest" = "#1b9e77")) +  theme_classic() +
-  xlab("Plant Species Richness [ln()]") +
-  ylab("Web Height [ln(cm)]") + 
-  theme(text = element_text(size = 10)) + 
-  theme(axis.text.x = element_text(colour = "black", size = 10)) + 
-  theme(axis.text.y = element_text(colour = "black", size = 10)) +
-  theme(axis.title.x = element_blank(), 
-        axis.title.y = element_blank(),
-        legend.position = "none") + 
-#  theme(axis.text.x = element_blank(), 
-#        axis.text.y = element_blank()) +
-  annotate(geom = "text", x = 0.9, y = 5.8, label = "N.S.", color = "black", size = 3)
-
-height_center_plant
-height_center_road
-```
-
-### Web Height by Land
-
-```{r height_land_stats}
-height_land <- glmer(round(RetreatHeight, 0) ~ Land + (1 | ID), data = webs, family = poisson)
-summary(height_land)
-car::Anova(height_land, type = 3)
-comp <- glht(height_land, linfct = mcp(Land = "Tukey"))
-summary(comp)
-
-height_land_nb <- glmer.nb(round(RetreatHeight, 0) ~ Land + (1 | ID), data = webs)
-summary(height_land_nb)
-car::Anova(height_land_nb, type = 3)
-comp <- glht(height_land_nb, linfct = mcp(Land = "Tukey"))
-summary(comp)
-```
-
-```{r height_land_graph}
-#webs <- webs %>% 
-#  mutate(Land = fct_relevel(Land, "Deciduous Forest", 
-#                            "Woody Wetlands", 
-#                            "Urban, High", 
-#                            "Urban, Medium", 
-#                            "Urban, Low"))
-predictions <- expand.grid(Land = levels(factor(webs$Land)))
-predictions$response <- predict(height_land_nb, newdata = predictions, se.fit = TRUE, re.form = NA, type = "response")
-
-myFunc <- function(mm) {
-    predict(mm, newdata = predictions, re.form = ~0, type = "response")
-}
-#bigBoot_height_land_nb <- bootMer(height_land_nb, myFunc, nsim = 1000)
-#saveRDS(bigBoot_height_land_nb, file = "bootstrapping/bigBoot_height_land_nb.Rds")
-bigBoot_height_land_nb <- readRDS("bootstrapping/bigBoot_height_land_nb.Rds")
-predSE <- t(apply(bigBoot_height_land_nb$t, MARGIN = 2, FUN = sd))
-predictions$SE <- predSE[1, ]
-#predictions2 <- summary(emmeans(height_land, ~Land,type = "response"))
-
-height_land_plot <- ggplot(webs, aes(x = Land, y = RetreatHeight)) + 
-  geom_jitter(color = "grey", width = 0.1, size = 0.5) +
-  geom_point(aes(x = Land, y = response, color = Land), size = 2, data = predictions) + 
-  geom_errorbar(aes(x = Land, 
-                  ymin = response - SE, 
-                  ymax = response + SE, color = Land), data = predictions, inherit.aes = FALSE, width = 0.25, size = 1) +
-  theme_classic() +
-  scale_color_manual(values = c("Deciduous Forest" = "#1b9e77", "Woody Wetlands" = "#1b9e77", "Urban, High" = "#d95f02", "Urban, Medium" = "#d95f02", "Urban, Low" = "#d95f02")) +
-  xlab("Land Cover Class") +
-  ylab("Web Height [cm]") + 
-  theme(text = element_text(size = 10)) + 
-  theme(axis.text.x=element_text(colour="black", size=10)) + 
-  theme(axis.text.y=element_text(colour="black", size=10)) +
-  theme(legend.position = "none") +
-  theme(axis.text.x = element_text(angle = 90, vjust = 1, hjust=1))# +
-  #annotate(geom="text", x=1, y=max(webs$RetreatHeight), label="A", color="black", size = 3) +
-  #annotate(geom="text", x=2, y=max(webs$RetreatHeight), label="A", color="black", size = 3) +
-  #annotate(geom="text", x=3, y=max(webs$RetreatHeight), label="A", color="black", size = 3) +
-  #annotate(geom="text", x=4, y=max(webs$RetreatHeight), label="A", color="black", size = 3) +
-  #annotate(geom="text", x=5, y=max(webs$RetreatHeight), label="A", color="black", size = 3)
-
-height_land_plot
-```
-
-**Web height varies significantly** across land cover class (chi = 10.495, df = 4, p = 0.033).
-
-## Figures for Manuscript
-
-### Measurement by Location Figure
-
-```{r main}
-blankPlot <- ggplot() + 
-  geom_blank(aes(1,1)) + 
-  cowplot::theme_nothing()
-
-main_row1 <- ggarrange(nb_plot_webs, nb_plot_spiders, blankPlot, labels = c("a", "b", ""), nrow = 1, font.label = list(size = 10))
-main_row2 <- ggarrange(nb_plot_search, nb_plot_dist, nb_plot_height, labels = c("c", "d", "e"), nrow = 1, font.label = list(size = 10))
-
-main <- ggarrange(main_row1, main_row2, nrow = 2, font.label = list(size = 10))
-main
-jpeg(filename = "manuscript/figures/main.jpeg", units = "cm", width = 17.4, height = 17.4, res = 300)
-print(main)
-dev.off()
-#saveRDS(main, "manuscript/figures/main.Rds")
-```
-
-### Predictors Plant
-
-```{r predictors_plant}
-webs_text <- as_ggplot(text_grob(paste("Number of \nWebs \n[ln()]"), size = 10))
-spiders_text <- as_ggplot(text_grob(paste("Number of \nSpiders \n[ln()]"), size = 10))
-dist_text <- as_ggplot(text_grob(paste("Nearest \nNeighbor \nDist. [ln(cm)]"), size = 10))
-height_text <- as_ggplot(text_grob(paste("Web \nHeight \n[ln(cm)]"), size = 10))
-plant_text <- as_ggplot(text_grob(paste("Plant Species Richness [ln()]"), size = 10))
-blankPlot <- ggplot()+geom_blank(aes(1,1)) + 
-  cowplot::theme_nothing()
-
-pred_plant <- ggarrange(webs_text, webs_plant, 
-                spiders_text, spiders_plant, 
-                dist_text, dist_plant, 
-                height_text, height_plant,
-                blankPlot, plant_text,
-                ncol = 2, nrow = 5, 
-                widths = c(0.3, 0.7), 
-                heights = c(0.24, 0.24, 0.24, 0.24, 0.04))
-
-jpeg(filename = "manuscript/figures/pred_plant.jpeg", units = "cm", width = 8.4, height = 17.4, res = 300)
-print(pred_plant)
-dev.off()
-```
-
-### Predictors Traffic Impact
-
-```{r predictors_traffic}
-webs_text <- as_ggplot(text_grob(paste("Number of \nWebs \n[ln()]"), size = 10))
-spiders_text <- as_ggplot(text_grob(paste("Number of \nSpiders \n[ln()]"), size = 10))
-dist_text <- as_ggplot(text_grob(paste("Nearest \nNeighbor \nDist. [ln(cm)]"), size = 10))
-height_text <- as_ggplot(text_grob(paste("Web \nHeight \n[ln(cm)]"), size = 10))
-tdr_text <- as_ggplot(text_grob(paste("Road-Traffic \nImpact \n[ln(cars/day/m)]"), size = 10))
-tdh_text <- as_ggplot(text_grob(paste("Highway-Traffic \nImpact \n[ln(cars/day/m)]"), size = 10))
-road_text <- as_ggplot(text_grob(paste("Road \nLength [m]"), size = 10))
-overall_text <- as_ggplot(text_grob(paste("Overall"), size = 10))
-center_text <- as_ggplot(text_grob(paste("Urban Center Subset"), size = 10))
-blankPlot <- ggplot()+geom_blank(aes(1,1)) + 
-  cowplot::theme_nothing() 
-greyPlot <- ggplot()+geom_blank(aes(1,1)) + 
-  cowplot::theme_nothing() +
-  theme(panel.background = element_rect(fill = "grey", color = "white"))
-
-pred_traffic <- ggarrange(webs_text, greyPlot, webs_tdh, blankPlot, webs_center_tdh, greyPlot,
-                spiders_text, greyPlot, spiders_tdh, blankPlot, spiders_center_tdh, greyPlot, 
-                dist_text, greyPlot, greyPlot, blankPlot, greyPlot, dist_center_road, 
-                height_text, height_tdr, greyPlot, blankPlot, greyPlot, height_center_road,
-                blankPlot, tdr_text, tdh_text, blankPlot, tdh_text, road_text,
-                ncol = 6, nrow = 5, 
-                widths = c(0.16, 0.20, 0.20, 0.04, 0.20, 0.20), 
-                heights = c(0.22, 0.22, 0.22, 0.22, 0.12))
-
-jpeg(filename = "manuscript/figures/pred_traffic.jpeg", units = "cm", width = 17.4, height = 17.4, res = 300)
-print(pred_traffic)
-dev.off()
-```
-
-### Predictors of Web and Spider Abundance
-
-```{r predictors_abund}
-webs_text <- as_ggplot(text_grob(paste("Number of \nWebs \n[log()]"), size = 10))
-spiders_text <- as_ggplot(text_grob(paste("Number of \nSpiders \n[log()]"), size = 10))
-plant_text <- as_ggplot(text_grob(paste("Plant Species \nRichness \n[log()]"), size = 10))
-patch_text <-as_ggplot(text_grob(paste("Patch Area \n[log(km²)]"), size = 10))
-highway_text <- as_ggplot(text_grob(paste("Highway Disturb. \n[log(cars/\nday/m)]"), size = 10))
-rlength_text <- as_ggplot(text_grob(paste("Road \nLength [m]"), size = 10))
-blankPlot <- ggplot()+geom_blank(aes(1,1)) + 
-  cowplot::theme_nothing()
-
-pa <- ggarrange(webs_text, webs_center_plant, webs_center_patch, webs_center_tdh, webs_center_road,
-           spiders_text, spiders_center_plant, spiders_center_patch, spiders_center_tdh, spiders_center_road,
-          ncol = 5, nrow = 2, widths = c(0.1, 0.225, 0.225, 0.225, 0.225))
-
-labels <- ggarrange(blankPlot, plant_text, patch_text, highway_text, rlength_text, ncol = 5, nrow = 1, widths = c(0.1, 0.225, 0.225, 0.225, 0.225))
-
-predictors_abund <- ggarrange(pa, labels, nrow = 2, heights = c(0.8, 0.2))
-#saveRDS(predictors_abund, "manuscript/figures/predictors_abund.Rds")
-```
-
-### Predictors of Aggregation
-
-```{r predictors_agg}
-wd_text1 <- as_ggplot(text_grob(paste("Forest \nNearest \nNeighbor \nDist. [log(cm)]"), size = 10))
-wd_text2 <- as_ggplot(text_grob(paste("Center \nNearest \nNeighbor \nDist. [log(cm)]"), size = 10))
-tree_text <- as_ggplot(text_grob(paste("Tree Cover [%]"), size = 10))
-plant_text <- as_ggplot(text_grob(paste("Plant Species \nRichness \n[log()]"), size = 10))
-road_text <- as_ggplot(text_grob(paste("Road Disturb. \n[log(cars/day/m)]"), size = 10))
-highway_text <- as_ggplot(text_grob(paste("Highway Disturb. \n[log(cars/day/m)]"), size = 10))
-spec_text <- as_ggplot(text_grob(paste("Spectral \nRadiance \n[Watts/(m²*sr*µm)]"), size = 10))
-rlength_text <- as_ggplot(text_grob(paste("Road \nLength [m]"), size = 10))
-blankPlot <- ggplot()+geom_blank(aes(1,1)) + 
-  cowplot::theme_nothing()
-
-agg1 <- ggarrange(wd_text1, dist_forest_plant, dist_forest_tree, dist_forest_tdr, dist_forest_tdh,
-          ncol = 5, nrow = 1, widths = c(0.12, 0.22, 0.22, 0.22, 0.22))
-
-agg2 <- ggarrange(wd_text2, dist_center_plant, dist_center_spec, dist_center_road, blankPlot,
-          ncol = 5, nrow = 1, widths = c(0.12, 0.22, 0.22, 0.22, 0.22))
-
-labels1 <- ggarrange(blankPlot, plant_text, tree_text, road_text, highway_text, ncol = 5, nrow = 1, widths = c(0.1, 0.225, 0.225, 0.225, 0.225))
-
-labels2 <- ggarrange(blankPlot, plant_text, spec_text, rlength_text, blankPlot, ncol = 5, nrow = 1, widths = c(0.1, 0.225, 0.225, 0.225, 0.225))
-
-predictors_agg <- ggarrange(agg2, labels2, agg1, labels1, nrow = 4, heights = c(0.35, 0.15, 0.35, 0.15))
-#saveRDS(predictors_agg, "manuscript/figures/predictors_agg.Rds")
-```
-
-## Tables for Manuscript
-
-### Landscape Features by Location
-
-```{r landscape_table}
+pred_table_avg_nb <- read.table(file = "data/pred_table_avg_nb.txt", header = TRUE) # for predictor stats table
+
+```
+
+# Table 1
+
+**Table 1** Landscape variables for the urban center (UNL City Campus), the urban forest (Wilderness Park), and Lincoln (Nebraska, USA) city limits, collected from the National Land Cover Database (2016 Tree Cover, 2019 Impervious Cover, 2019 Land Cover) using QGIS (v.
+3.16.3-Hannover, ESRI 102704).
+The National Land Cover Database assigned the intensity of urban cover based on percent impervious cover (High = 80–100%, Medium = 50–79%, Low = 20–49%, Open Space = 0–19% (https://www.mrlc.gov/data/legends/national- land-cover-database-class-legend-and-description)
+
+```{r table 1}
 rownames(land_cover) <- c("Area (sq.
@@
   set_caption("") %>% 
-  save_as_image(path = here::here("manuscript/figures/landscape.png"))
-```
-
-### Predictors by Location
-
-```{r pred_location, fig.width = 6.85, dpi = 300}
+  save_as_image(path = here::here("tables/table1.png"))
+```
+
+# Table 2
+
+**Table 2** Mean and standard error of the collected environmental predictors by habitat.
+Percent impervious and tree cover, spectral radiance, artificial night sky radiance, and total road length were collected in a 100-m buffer of each focal web, while plant species richness was recorded in a 10-m buffer of each focal web.
+We used the nearest road or highway for traffic impact measures.
+Patch area was defined as the area of continuous vegetation that includes the focal web
+
+```{r table 2}
 mean_se1 <- c("Mean ± Std.
@@
   set_caption("") %>% 
-  save_as_image(path = here::here("manuscript/figures/pred_location.png"))
-```
-
-### Predictor Stats Table
-
-```{r pred_table}
-pred_table_nb <- read.table(file = "data/pred_table_nb.txt", header = TRUE) # for predictor stats table
-
+  save_as_image(path = here::here("tables/table2.png"))
+```
+
+# Table 3
+
+**Table 3** Results of the top models after AIC model selection from negative binomial generalized linear models with the environmental predictors for data overall and subset by habitat (urban center and urban forest).
+Asterisks indicate significance level (*** P < 0.001; ** P < 0.01; * P < 0.05; P < 0.10)
+
+```{r table 3}
 pred_table_nb <- pred_table_nb %>% 
@@
   hline_bottom(part = "body", border = officer::fp_border(width = 2)) %>% 
-  border(j = 'Variable', border.bottom = officer::fp_border(width = 2)) %>% 
+  #border(j = 'Variable', border.bottom = officer::fp_border(width = 2)) %>% 
   hline(i = c("4", "8", "11"), part = "body", border = officer::fp_border(width = 2)) %>%     
@@
     ref_symbols = c("c"), part = "body") %>% 
-  save_as_image(path = here::here("manuscript/figures/pred_table_nb.png"))
-```
-
-## Supplementary Figures and Tables
-
-### Substrate Figures
-
-```{r substrate}
-substrates %>% 
-  mutate(Location = fct_recode(Location, "Urban Center" = "Campus", "Urban Forest" = "Forest"),
-         Location = fct_relevel(Location, "Urban Center", "Urban Forest")) %>% 
-  ggplot(aes(x = Location, y = Number, fill = factor(Type, levels=c("Cement", "Metal", "Plastic", "Rocks", "Herb", "Litter", "Shrub", "Tree", "Vine")))) + 
-  geom_bar(position = "fill",stat = "identity", alpha=1.0) + 
-  scale_y_continuous(labels = scales::percent_format()) + 
-  theme(axis.title.x = element_blank()) + 
-  xlab("Collection Location") +
-  ylab("Percent of Web Substrates") + 
-  theme_classic() +
-  theme(text = element_text(size = 10)) + 
-  scale_fill_manual(values = c("#D94701", "#FD8D3C", "#FDBE85", "#FEEDDE", "#006D2C", "#31A354", "#74C476", "#BAE4B3", "#EDF8E9"), 
-                    labels = c("Cement", "Metal", "Plastic", "Rocks", "Herb", "Litter", "Shrub", "Tree", "Vine")) + 
-  labs(fill="Substrate Material") + 
-  theme(axis.text.x=element_text(colour="black", size=10)) + 
-  theme(axis.text.y=element_text(colour="black", size=10)) +
-  theme(legend.text=element_text(size=10))
-  ggsave("manuscript/figures/substrate_plot.png")
-```
-
-### Overall Predictor Plots
-```{r predictors_overall}
-dist_text <- as_ggplot(text_grob(paste("Search \nDistance \n[log(m)]"), size = 10))
-webs_text <- as_ggplot(text_grob(paste("Number of \nWebs \n[log()]"), size = 10))
-spiders_text <- as_ggplot(text_grob(paste("Number of \nSpiders \n[log()]"), size = 10))
-wd_text <- as_ggplot(text_grob(paste("Nearest \nNeighbor \nDist. [log(cm)]"), size = 10))
-wh_text <- as_ggplot(text_grob(paste("Web \nHeight \n[log(cm)]"), size = 10))
-plant_text <- as_ggplot(text_grob(paste("Plant Species \nRichness [log()]"), size = 10))
-road_text <- as_ggplot(text_grob(paste("Road Disturbance \n[log(vehicles/day/m)]"), size = 10))
-highway_text <- as_ggplot(text_grob(paste("Highway Disturbance \n[log(vehicles/day/m)]"), size = 10))
-blankPlot <- ggplot()+geom_blank(aes(1,1)) + 
-  cowplot::theme_nothing() 
-greyPlot <- ggplot()+geom_blank(aes(1,1)) + 
-  cowplot::theme_nothing() +
-  theme(panel.background = element_rect(fill = "grey", color = "white"))
-
-graphs <- ggarrange(webs_text, webs_plant, webs_tdr, webs_tdh,
-           spiders_text, spiders_plant, greyPlot, spiders_tdh,
-           wd_text, dist_plant, dist_tdr, greyPlot, 
-           wh_text, height_plant, height_tdr, greyPlot, 
-          ncol = 4, nrow = 4)
-
-labels <- ggarrange(blankPlot, plant_text, road_text, highway_text, ncol = 4, nrow = 1)
-
-predictors_overall <- ggarrange(graphs, labels, nrow = 2, heights = c(0.8, 0.2))
-#saveRDS(predictors_overall, "manuscript/figures/predictors_overall.Rds")
-```
-
-## Response Variables by Land Cover Class
-
-```{r land_plots}
-library("gridExtra")
-library("cowplot")
-
-land_plots <- ggarrange(search_land_plot, ggarrange(webs_land_plot, spiders_land_plot, dist_land_plot, height_land_plot, labels = c("b", "c", "d", "e"), ncol = 2, nrow = 2, legend = "none", align = "hv"), labels = c("a"), widths = c(0.3, 0.7))
-
-gt <- arrangeGrob(webs_land_plot, spiders_land_plot,
-             search_land_plot, dist_land_plot, 
-             height_land_plot,
-             ncol = 3, nrow = 2, 
-             layout_matrix = rbind(c(1, 2, 5), c(3, 4, 5)))
-
-land_plots <- as_ggplot(gt) +                                # transform to a ggplot
-  draw_plot_label(label = c("a", "c", "b", "d", "e"), size = 15,
-                  x = c(0, 0, 0.33, 0.33, 0.66), y = c(1, 0.5, 1, 0.5, 1))
-
-land_plots
-
-jpeg(filename = "manuscript/figures/land_plots.jpeg", units = "cm", width = 17.4, height = 17.4, res = 300)
-print(land_plots)
-dev.off()
-#saveRDS(land_plots, "manuscript/figures/land_plots.Rds")
-```
-
-## Site Information Table
-
-```{r site_info}
+  save_as_image(path = here::here("tables/table3.png"))
+```
+
+# Table S1
+
+**Table S1** Geographical information for the University of Nebraska-Lincoln (UNL) City Campus and Wilderness Park Sites
+
+```{r table s1}
 site_info <- site_info %>% 
@@
   align(align = "center", part = "all") %>% 
-  save_as_image(path = here::here("manuscript/figures/site_info.png"))
-```
-
-## Table of Predictor Stats from Model Average
-
-```{r pred_table_avg}
-pred_table_avg_nb <- read.table(file = "data/pred_table_avg_nb.txt", header = TRUE) # for predictor stats table
-
+  save_as_image(path = here::here("tables/tableS1.png"))
+```
+
+# Table S3
+
+**Table S3** Statistical results of Likelihood Ratio Tests (a) following negative binomial generalized linear models (mixed effects model for web height with site ID as a random effect) for each response variable by land cover class.
+We performed multiple comparisons (Tukey’s all-pair) for variables that significantly differed by land cover class (b-e) where the asterisks in the grey boxes show comparisons that significantly differed.
+Significance indicated by asterisks (*** P < 0.001; ** P < 0.01; * P < 0.05, .
+P < 0.10).
+
+```{r table s3}
+Variable <- c("Number of Webs", "Number of Spiders", "Search Distance", "Neares Neighbor Distance", "Web Height")
+Chi <- c(19.134, 10.913, 6.37, 40.757, 12.569)
+df <- c("4, 21", "4, 21", "4, 21", "4, 20", "4, 130")
+P <- c("< 0.001 ***", "  0.028 *", "  0.173", "< 0.001 ***", "  0.014 *")
+land_stats <- data.frame(Variable, Chi, df, P)
+colnames(land_stats) <- c('Variable','Likelihood Ratio \nChi-Squared','Degrees of Freedom', 'P-Value')
+
+flextable(land_stats[ , 1:4]) %>% 
+  autofit() %>% 
+  bold(bold = TRUE, part = "header") %>% 
+  fontsize(size = 10, part = "all") %>% 
+  align(align = "center", part = "all") %>% 
+  valign(valign = "top", part = "all") %>% 
+  set_caption("")
+
+land_stat_table <- ggtexttable(land_stats, rows = NULL,
+            theme = ttheme("blank")) %>% 
+            tab_add_hline(at.row = c(1, 2), row.side = "top", linewidth = 3, linetype = 1) %>%
+            tab_add_hline(at.row = 6, row.side = "bottom", linewidth = 3, linetype = 1)
+
+webs_land_table <- data.frame(UH = c("", "", "", "", ""),
+                              UM = c("", "", "", "", ""),
+                              UL = c("", "", "", "", ""),
+                              DF = c("*", "**", ".", "", ""),
+                              WW = c(".", "*", ".", "", ""))
+colnames(webs_land_table) <- c("Urban, High", "Urban, Medium", "Urban, Low", "Deciduous Forest", "Woody Wetlands")
+rownames(webs_land_table) <- c("Urban, High", "Urban, Medium", "Urban, Low", "Deciduous Forest", "Woody Wetlands")
+
+webs_land_table2 <- ggtexttable(webs_land_table,
+            theme = ttheme("blank", 
+                           rownames.style = rownames_style(color = "black", face = "plain", size = 10, fill = "white"),
+                           colnames.style = colnames_style(color = "black", face = "plain", size = 10, fill = "white"),
+                           tbody.style = tbody_style(color = "black", face = "plain", size = 12, fill = "white")))
+
+webs_land_table2 <- webs_land_table2 %>% 
+  tab_add_hline(at.row = c(1, 2), row.side = "top", linewidth = 3, linetype = 1) %>%
+  tab_add_hline(at.row = 6, row.side = "bottom", linewidth = 3, linetype = 1) %>%
+  tab_add_vline(at.column = 2, column.side = "left", from.row = 1, linewidth = 3, linetype = 1) %>% 
+  table_cell_bg(row = 2, column = c(3:6), linewidth = 0,
+                fill="lightgrey", color = "white") %>% 
+  table_cell_bg(row = 3, column = c(4:6), linewidth = 0,
+                fill="lightgrey", color = "white") %>% 
+  table_cell_bg(row = 4, column = c(5:6), linewidth = 0,
+                fill="lightgrey", color = "white") %>% 
+  table_cell_bg(row = 5, column = 6, linewidth = 0,
+                fill="lightgrey", color = "white") %>% 
+  tab_add_title(text = "     Number of Webs", face = "bold", size = 10)
+
+spiders_land_table <- data.frame(UH = c("", "", "", "", ""),
+                              UM = c("", "", "", "", ""),
+                              UL = c("", "", "", "", ""),
+                              DF = c("", "", "", "", ""),
+                              WW = c("", "", "", "", ""))
+colnames(spiders_land_table) <- c("Urban, High", "Urban, Medium", "Urban, Low", "Deciduous Forest", "Woody Wetlands")
+rownames(spiders_land_table) <- c("Urban, High", "Urban, Medium", "Urban, Low", "Deciduous Forest", "Woody Wetlands")
+
+spiders_land_table2 <- ggtexttable(spiders_land_table,
+            theme = ttheme("blank", 
+                           rownames.style = rownames_style(color = "black", face = "plain", size = 10, fill = "white"),
+                           colnames.style = colnames_style(color = "black", face = "plain", size = 10, fill = "white"),                           tbody.style = tbody_style(color = "black", face = "plain", size = 12, fill = "white")))
+
+spiders_land_table2 <- spiders_land_table2 %>% 
+  tab_add_hline(at.row = c(1, 2), row.side = "top", linewidth = 3, linetype = 1) %>%
+  tab_add_hline(at.row = 6, row.side = "bottom", linewidth = 3, linetype = 1) %>%
+  tab_add_vline(at.column = 2, column.side = "left", from.row = 1, linewidth = 3, linetype = 1) %>% 
+  table_cell_bg(row = 2, column = c(3:6), linewidth = 0,
+                fill="lightgrey", color = "white") %>% 
+  table_cell_bg(row = 3, column = c(4:6), linewidth = 0,
+                fill="lightgrey", color = "white") %>% 
+  table_cell_bg(row = 4, column = c(5:6), linewidth = 0,
+                fill="lightgrey", color = "white") %>% 
+  table_cell_bg(row = 5, column = 6, linewidth = 0,
+                fill="lightgrey", color = "white") %>% 
+  tab_add_title(text = "      Number of Spiders", face = "bold", size = 10)
+
+dist_land_table <- data.frame(UH = c("", "", "", "", ""),
+                              UM = c("", "", "", "", ""),
+                              UL = c("", "**", "", "", ""),
+                              DF = c("***", "*", "***", "", ""),
+                              WW = c("**", "", "***", "", ""))
+colnames(dist_land_table) <- c("Urban, High", "Urban, Medium", "Urban, Low", "Deciduous Forest", "Woody Wetlands")
+rownames(dist_land_table) <- c("Urban, High", "Urban, Medium", "Urban, Low", "Deciduous Forest", "Woody Wetlands")
+
+dist_land_table2 <- ggtexttable(dist_land_table,
+            theme = ttheme("blank", 
+                           rownames.style = rownames_style(color = "black", face = "plain", size = 10, fill = "white"),
+                           colnames.style = colnames_style(color = "black", face = "plain", size = 10, fill = "white"),                           tbody.style = tbody_style(color = "black", face = "plain", size = 12, fill = "white")))
+
+dist_land_table2 <- dist_land_table2 %>% 
+  tab_add_hline(at.row = c(1, 2), row.side = "top", linewidth = 3, linetype = 1) %>%
+  tab_add_hline(at.row = 6, row.side = "bottom", linewidth = 3, linetype = 1) %>%
+  tab_add_vline(at.column = 2, column.side = "left", from.row = 1, linewidth = 3, linetype = 1) %>% 
+  table_cell_bg(row = 2, column = c(3:6), linewidth = 0,
+                fill="lightgrey", color = "white") %>% 
+  table_cell_bg(row = 3, column = c(4:6), linewidth = 0,
+                fill="lightgrey", color = "white") %>% 
+  table_cell_bg(row = 4, column = c(5:6), linewidth = 0,
+                fill="lightgrey", color = "white") %>% 
+  table_cell_bg(row = 5, column = 6, linewidth = 0,
+                fill="lightgrey", color = "white") %>% 
+  tab_add_title(text = "      Nearest Neighbor Distance", face = "bold", size = 10)
+
+height_land_table <- data.frame(UH = c("", "", "", "", ""),
+                              UM = c("", "", "", "", ""),
+                              UL = c("", "", "", "", ""),
+                              DF = c("", "*", "", "", ""),
+                              WW = c("", "", "", "", ""))
+colnames(height_land_table) <- c("Urban, High", "Urban, Medium", "Urban, Low", "Deciduous Forest", "Woody Wetlands")
+rownames(height_land_table) <- c("Urban, High", "Urban, Medium", "Urban, Low", "Deciduous Forest", "Woody Wetlands")
+
+height_land_table2 <- ggtexttable(height_land_table,
+            theme = ttheme("blank", 
+                           rownames.style = rownames_style(color = "black", face = "plain", size = 10, fill = "white"),
+                           colnames.style = colnames_style(color = "black", face = "plain", size = 10, fill = "white"),                           tbody.style = tbody_style(color = "black", face = "plain", size = 12, fill = "white")))
+
+height_land_table2 <- height_land_table2 %>% 
+  tab_add_hline(at.row = c(1, 2), row.side = "top", linewidth = 3, linetype = 1) %>%
+  tab_add_hline(at.row = 6, row.side = "bottom", linewidth = 3, linetype = 1) %>%
+  tab_add_vline(at.column = 2, column.side = "left", from.row = 1, linewidth = 3, linetype = 1) %>% 
+  table_cell_bg(row = 2, column = c(3:6), linewidth = 0,
+                fill="lightgrey", color = "white") %>% 
+  table_cell_bg(row = 3, column = c(4:6), linewidth = 0,
+                fill="lightgrey", color = "white") %>% 
+  table_cell_bg(row = 4, column = c(5:6), linewidth = 0,
+                fill="lightgrey", color = "white") %>% 
+  table_cell_bg(row = 5, column = 6, linewidth = 0,
+                fill="lightgrey", color = "white") %>% 
+  tab_add_title(text = "      Web Height", face = "bold", size = 10)
+
+land_tables <- ggarrange(land_stat_table, webs_land_table2, spiders_land_table2, dist_land_table2, height_land_table2, nrow = 5, labels = c("a", "b", "c", "d", "e"), font.label = list(size = 12))
+
+jpeg(filename = "tables/tableS3.jpeg", units = "cm", width = 17.4, height = 25, res = 300)
+print(land_tables)
+dev.off()
+```
+
+# Table S4
+
+**Table S4** Results of model averages (all models within 2 delta AICc points) from negative binomial generalized linear models (mixed model for web height with site ID as a random effect) with the environmental predictors for data overall and subset by habitat (urban center and urban forest), where applicable.
+Asterisks indicate significance level (*** P < 0.001; ** P < 0.01; * P < 0.05, .
+P < 0.10)
+
+```{r table s4}
 pred_table_avg_nb <- pred_table_avg_nb %>% 
@@
   hline_bottom(part = "body", border = officer::fp_border(width = 2)) %>% 
-  border(j = 'Variable', border.bottom = officer::fp_border(width = 2)) %>% 
+  #border(j = 'Variable', border.bottom = officer::fp_border(width = 2)) %>% 
   hline(i = c("1", "4", "8"), part = "body", border = officer::fp_border(width = 2)) %>%   
@@
     ref_symbols = c("c"), part = "body") %>% 
-  save_as_image(path = here::here("manuscript/figures/pred_table_avg_nb.png"))
-```
-
-## Table of Land Stats
-
-```{r land_stats}
-Variable <- c("Number of Webs", "Number of Spiders", "Search Distance", "Neares Neighbor Distance", "Web Height")
-Chi <- c(19.134, 10.913, 6.37, 40.757, 12.569)
-df <- c("4, 21", "4, 21", "4, 21", "4, 20", "4, 130")
-P <- c("< 0.001 ***", "  0.028 *", "  0.173", "< 0.001 ***", "  0.014 *")
-land_stats <- data.frame(Variable, Chi, df, P)
-colnames(land_stats) <- c('Variable','Likelihood Ratio \nChi-Squared','Degrees of Freedom', 'P-Value')
-
-flextable(land_stats[ , 1:4]) %>% 
-  autofit() %>% 
-  bold(bold = TRUE, part = "header") %>% 
-  fontsize(size = 10, part = "all") %>% 
-  align(align = "center", part = "all") %>% 
-  valign(valign = "top", part = "all") %>% 
-  set_caption("") %>% 
-  save_as_image(path = here::here("manuscript/figures/land_stats_nb.png"))
-
-land_stat_table <- ggtexttable(land_stats, rows = NULL,
-            theme = ttheme("blank")) %>% 
-            tab_add_hline(at.row = c(1, 2), row.side = "top", linewidth = 3, linetype = 1) %>%
-            tab_add_hline(at.row = 6, row.side = "bottom", linewidth = 3, linetype = 1)
-
-webs_land_table <- data.frame(UH = c("", "", "", "", ""),
-                              UM = c("", "", "", "", ""),
-                              UL = c("", "", "", "", ""),
-                              DF = c("*", "**", ".", "", ""),
-                              WW = c(".", "*", ".", "", ""))
-colnames(webs_land_table) <- c("Urban, High", "Urban, Medium", "Urban, Low", "Deciduous Forest", "Woody Wetlands")
-rownames(webs_land_table) <- c("Urban, High", "Urban, Medium", "Urban, Low", "Deciduous Forest", "Woody Wetlands")
-
-webs_land_table2 <- ggtexttable(webs_land_table,
-            theme = ttheme("blank", 
-                           rownames.style = rownames_style(color = "black", face = "plain", size = 10, fill = "white"),
-                           colnames.style = colnames_style(color = "black", face = "plain", size = 10, fill = "white"),
-                           tbody.style = tbody_style(color = "black", face = "plain", size = 12, fill = "white")))
-
-webs_land_table2 <- webs_land_table2 %>% 
-  tab_add_hline(at.row = c(1, 2), row.side = "top", linewidth = 3, linetype = 1) %>%
-  tab_add_hline(at.row = 6, row.side = "bottom", linewidth = 3, linetype = 1) %>%
-  tab_add_vline(at.column = 2, column.side = "left", from.row = 1, linewidth = 3, linetype = 1) %>% 
-  table_cell_bg(row = 2, column = c(3:6), linewidth = 0,
-                fill="lightgrey", color = "white") %>% 
-  table_cell_bg(row = 3, column = c(4:6), linewidth = 0,
-                fill="lightgrey", color = "white") %>% 
-  table_cell_bg(row = 4, column = c(5:6), linewidth = 0,
-                fill="lightgrey", color = "white") %>% 
-  table_cell_bg(row = 5, column = 6, linewidth = 0,
-                fill="lightgrey", color = "white") %>% 
-  tab_add_title(text = "     Number of Webs", face = "bold", size = 10)
-
-spiders_land_table <- data.frame(UH = c("", "", "", "", ""),
-                              UM = c("", "", "", "", ""),
-                              UL = c("", "", "", "", ""),
-                              DF = c("", "", "", "", ""),
-                              WW = c("", "", "", "", ""))
-colnames(spiders_land_table) <- c("Urban, High", "Urban, Medium", "Urban, Low", "Deciduous Forest", "Woody Wetlands")
-rownames(spiders_land_table) <- c("Urban, High", "Urban, Medium", "Urban, Low", "Deciduous Forest", "Woody Wetlands")
-
-spiders_land_table2 <- ggtexttable(spiders_land_table,
-            theme = ttheme("blank", 
-                           rownames.style = rownames_style(color = "black", face = "plain", size = 10, fill = "white"),
-                           colnames.style = colnames_style(color = "black", face = "plain", size = 10, fill = "white"),                           tbody.style = tbody_style(color = "black", face = "plain", size = 12, fill = "white")))
-
-spiders_land_table2 <- spiders_land_table2 %>% 
-  tab_add_hline(at.row = c(1, 2), row.side = "top", linewidth = 3, linetype = 1) %>%
-  tab_add_hline(at.row = 6, row.side = "bottom", linewidth = 3, linetype = 1) %>%
-  tab_add_vline(at.column = 2, column.side = "left", from.row = 1, linewidth = 3, linetype = 1) %>% 
-  table_cell_bg(row = 2, column = c(3:6), linewidth = 0,
-                fill="lightgrey", color = "white") %>% 
-  table_cell_bg(row = 3, column = c(4:6), linewidth = 0,
-                fill="lightgrey", color = "white") %>% 
-  table_cell_bg(row = 4, column = c(5:6), linewidth = 0,
-                fill="lightgrey", color = "white") %>% 
-  table_cell_bg(row = 5, column = 6, linewidth = 0,
-                fill="lightgrey", color = "white") %>% 
-  tab_add_title(text = "      Number of Spiders", face = "bold", size = 10)
-
-dist_land_table <- data.frame(UH = c("", "", "", "", ""),
-                              UM = c("", "", "", "", ""),
-                              UL = c("", "**", "", "", ""),
-                              DF = c("***", "*", "***", "", ""),
-                              WW = c("**", "", "***", "", ""))
-colnames(dist_land_table) <- c("Urban, High", "Urban, Medium", "Urban, Low", "Deciduous Forest", "Woody Wetlands")
-rownames(dist_land_table) <- c("Urban, High", "Urban, Medium", "Urban, Low", "Deciduous Forest", "Woody Wetlands")
-
-dist_land_table2 <- ggtexttable(dist_land_table,
-            theme = ttheme("blank", 
-                           rownames.style = rownames_style(color = "black", face = "plain", size = 10, fill = "white"),
-                           colnames.style = colnames_style(color = "black", face = "plain", size = 10, fill = "white"),                           tbody.style = tbody_style(color = "black", face = "plain", size = 12, fill = "white")))
-
-dist_land_table2 <- dist_land_table2 %>% 
-  tab_add_hline(at.row = c(1, 2), row.side = "top", linewidth = 3, linetype = 1) %>%
-  tab_add_hline(at.row = 6, row.side = "bottom", linewidth = 3, linetype = 1) %>%
-  tab_add_vline(at.column = 2, column.side = "left", from.row = 1, linewidth = 3, linetype = 1) %>% 
-  table_cell_bg(row = 2, column = c(3:6), linewidth = 0,
-                fill="lightgrey", color = "white") %>% 
-  table_cell_bg(row = 3, column = c(4:6), linewidth = 0,
-                fill="lightgrey", color = "white") %>% 
-  table_cell_bg(row = 4, column = c(5:6), linewidth = 0,
-                fill="lightgrey", color = "white") %>% 
-  table_cell_bg(row = 5, column = 6, linewidth = 0,
-                fill="lightgrey", color = "white") %>% 
-  tab_add_title(text = "      Nearest Neighbor Distance", face = "bold", size = 10)
-
-height_land_table <- data.frame(UH = c("", "", "", "", ""),
-                              UM = c("", "", "", "", ""),
-                              UL = c("", "", "", "", ""),
-                              DF = c("", "*", "", "", ""),
-                              WW = c("", "", "", "", ""))
-colnames(height_land_table) <- c("Urban, High", "Urban, Medium", "Urban, Low", "Deciduous Forest", "Woody Wetlands")
-rownames(height_land_table) <- c("Urban, High", "Urban, Medium", "Urban, Low", "Deciduous Forest", "Woody Wetlands")
-
-height_land_table2 <- ggtexttable(height_land_table,
-            theme = ttheme("blank", 
-                           rownames.style = rownames_style(color = "black", face = "plain", size = 10, fill = "white"),
-                           colnames.style = colnames_style(color = "black", face = "plain", size = 10, fill = "white"),                           tbody.style = tbody_style(color = "black", face = "plain", size = 12, fill = "white")))
-
-height_land_table2 <- height_land_table2 %>% 
-  tab_add_hline(at.row = c(1, 2), row.side = "top", linewidth = 3, linetype = 1) %>%
-  tab_add_hline(at.row = 6, row.side = "bottom", linewidth = 3, linetype = 1) %>%
-  tab_add_vline(at.column = 2, column.side = "left", from.row = 1, linewidth = 3, linetype = 1) %>% 
-  table_cell_bg(row = 2, column = c(3:6), linewidth = 0,
-                fill="lightgrey", color = "white") %>% 
-  table_cell_bg(row = 3, column = c(4:6), linewidth = 0,
-                fill="lightgrey", color = "white") %>% 
-  table_cell_bg(row = 4, column = c(5:6), linewidth = 0,
-                fill="lightgrey", color = "white") %>% 
-  table_cell_bg(row = 5, column = 6, linewidth = 0,
-                fill="lightgrey", color = "white") %>% 
-  tab_add_title(text = "      Web Height", face = "bold", size = 10)
-
-land_tables <- ggarrange(land_stat_table, webs_land_table2, spiders_land_table2, dist_land_table2, height_land_table2, nrow = 5, labels = c("a", "b", "c", "d", "e"), font.label = list(size = 12))
-
-jpeg(filename = "manuscript/figures/land_tables.jpeg", units = "cm", width = 17.4, height = 25, res = 300)
-print(land_tables)
-dev.off()
-```
-
-## Lit Review Table
-
-```{r references}
-mech <- c("Mechanisms of Aggregation", "Interspecific and Intraspecific Interactions", "Interspecific and Intraspecific Interactions", "Interspecific and Intraspecific Interactions", "Interspecific and Intraspecific Interactions", "Interspecific and Intraspecific Interactions", "Interspecific and Intraspecific Interactions", "Environmental Factors", "Environmental Factors", "Environmental Factors", "Dispersal", "Dispersal")
-
-mech2 <- c("Mechanisms of Aggregation", "Conspecific Attraction", "Lekking for Mates", "Heterospecific Attraction", "Predation Release", "Prey Chemical Cues", "Prey Abundance", "Light Cues", "Plant Cover", "Limited Shelter from Thermal Stress", "Limited Dispersal via Flooding", "Ontogenesis")
-
-rel <- c("Relationship with Spider Aggregation", "Following conspecific silk increased aggregation tendencies", "Larger female aggregations attract more males", "Spiders aggregate around heterospecific spiders", "Predation reduced when aggregated", "Spiders preferred areas with prey chemical cues", "Spider aggregations were denser in areas with more available prey", "Spiders were attracted to and gathered in areas with artificial light", "Spiders aggregated in an area dominated by cover of a specific plant", "Aggregations on  limited protective structures against high temperatures", "Flooding restricted ballooning to escape", "Temporary aggregation of sibblings following hatching from egg sac")
-
-urban <- c("Urban Habitat", "No", "No", "No", "No", "Yes", "Yes", "Yes", "No", "No", "No", "No")
-
-ref <- c("References", "Fitzgerald and Ives 2017; Hodge and Storfer-Isser 1997; Jeanson et al.
-2004", "Kasumovic and Jordan 2013; Lloyd and Elgar 1997", "Henaut and Machkour-M'Rabet 2010; Jeanson et al.
-2004", "Feree et al.
-2018; Lloyd and Elgar 1997", "Johnson et al.
-2011", "Trubl et al.
-2012", "Czaczkes et al.
-2018; Mammola et al.
-2018", "Petillon et al.
-2012", "Riechert 1974", "Piacentini et al.
-2021", "Marshall 1995; Mougenot et al.
-2012; Riechert 1974")
-
-references <- data.frame(mech, mech2, rel, urban, ref)
-
-flextable(references[ ,1:5]) %>% 
-  delete_part(part = "header") %>% 
-  autofit() %>% 
-  hline(i = c("1", "7", "10", "12"), part = "body", border = officer::fp_border(width = 2)) %>% 
-    hline(i = c("2", "3", "4", "5", "6", "8", "9", "11"), part = "body", border = officer::fp_border(width = 1)) %>% 
-  merge_h(part = "body") %>% 
-  merge_v(j = 1, part = "body") %>% 
-  bold(i = 1, bold = TRUE, part = "body") %>% 
-  fontsize(size = 14, part = "all") %>% 
-  align(align = "center", part = "all") %>% 
-  set_caption("") %>% 
-  save_as_image(path = here::here("manuscript/figures/references.png"))
-```
+  save_as_image(path = here::here("tables/tableS4.png"))
+```
